### 2018-02-26 scnn.tex
add must compare papers

%% 
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%% 
%% Template article for Elsevier's document class `elsarticle'
%% with harvard style bibliographic references
%% SP 2008/03/01

\documentclass[preprint,12pt,authoryear]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times,authoryear]{elsarticle}
%% \documentclass[final,1p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,3p,times,authoryear]{elsarticle}
%% \documentclass[final,3p,times,twocolumn,authoryear]{elsarticle}
%% \documentclass[final,5p,times,authoryear]{elsarticle}
%% \documentclass[final,5p,times,twocolumn,authoryear]{elsarticle}

\usepackage[utf8]{inputenc}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{color}
\usepackage{url}
\usepackage{hyperref}
\usepackage{graphicx,array}
\usepackage{amsmath}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\newcommand{\nati}[1]{{\color[rgb]{.1,.6,.1}{#1}}}

\newcommand{\todo}[1]{{\color[rgb]{.6,.1,.6}{#1}}}

\journal{Astronomy and Computing}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

\title{Efficient spherical Convolutional Neural Networks}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \address[label1]{}
%% \address[label2]{}

\author{}

\address{}

\begin{abstract}
%% Text of abstract

\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{Introduction}
\label{sec:intro}

\paragraph{Potential applications}
\begin{itemize}
	\item Efficient compression de-compression of 360 videos\cite{su2017learning}
	\item Analysis of spherical cosmological data such as the cosmic microwave background \cite{...}, already done in\cite{he2018analysis}.
\end{itemize}

\subsection{Related work}
\cite{cohen2017convolutional} \nati{+ add other graph CNN approaches \cite{...}}
\cite{cohen2018spherical}
\cite{boomsma2017spherical}
\cite{defferrard2016convolutional}

\section{Convolution neural networks on a sphere}

\section{Experiments}

\section*{Thanks}

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
\section*{Bibliography}
\bibliographystyle{elsarticle-harv} 
\bibliography{biblio}

\end{document}

\endinput
%%
%% End of file `elsarticle-template-harv.tex'.

### 2018-02-28 scnn.tex
put some structure into the paper

@@
 
-\paragraph{Potential applications}
+\subsection{Motivation}
+a) Cosmology has a lot of spherical data. Our solution is easy to use and is based on the widely used healpix sampling.
+b) It is the most efficient spherical convolution
+
+\subsection{Potential applications}
 \begin{itemize}
@@
 
-\section{Convolution neural networks on a sphere}
+\section{Spherical convolution on sphere using a graph}
+\begin{itemize}
+	\item We build a graph using the healpix sampling
+	\item Define Fourier transform and show that the harmonics are visually close to the spherical harmonics
+	\item Define spherical convolution using the graph Fourier transform and show heat diffusion example
+	\item Show the limits of the approach and explain why we cannot have a perfect spherical convolution with this technique
+\end{itemize}
+
+\section{Efficient spherical CNN}
+\begin{itemize}
+	\item We need efficient convolution, hence the Chebysheff trick
+	\item Define spherical CNN using graph CNN
+\end{itemize}
 
 \section{Experiments}
+\begin{itemize}
+	\item With the entire sphere / different PSD (The PSD features + linear SVM is equivalently good)
+	\item Without the entire sphere / same PSD (The histogram features + kernelized SVM is equivalently good)
+	\item ??
+\end{itemize}
 

### 2018-03-01 scnn.tex
meeting changes

@@
 
+\newcommand{\assign}[1]{{\color[rgb]{.8,.5,.8}{Assigned: #1 }}}
+
 \journal{Astronomy and Computing}
@@
 
-\title{Efficient spherical Convolutional Neural Networks}
+\title{Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications}
 
@@
 \subsection{Motivation}
+\assign{Tomek}
+
 a) Cosmology has a lot of spherical data. Our solution is easy to use and is based on the widely used healpix sampling.
@@
 \subsection{Potential applications}
+	\assign{Tomek, Nathanael}
+
 \begin{itemize}
+
 	\item Efficient compression de-compression of 360 videos\cite{su2017learning}
@@
 \subsection{Related work}
+\assign{Nathanael}
 \cite{cohen2017convolutional} \nati{+ add other graph CNN approaches \cite{...}}
@@
 \section{Spherical convolution on sphere using a graph}
+\assign{Nathanael}
+
 \begin{itemize}
@@
 \section{Efficient spherical CNN}
+\assign{Michael}
+
 \begin{itemize}
@@
 \section{Experiments}
+\assign{Nathanael, Tomek}
+
 \begin{itemize}
 	\item With the entire sphere / different PSD (The PSD features + linear SVM is equivalently good)
-	\item Without the entire sphere / same PSD (The histogram features + kernelized SVM is equivalently good)
+	\item Without the entire sphere / same PSD (1 sample: the histogram features + kernelized SVM is equivalently good)
 	\item ??

### 2018-03-06 scnn.tex
start working on section 2

@@
 \subsection{Potential applications}
-	\assign{Tomek, Nathanael}
+	\assign{Tomek, Nathanael, Michael}
 
@@
 \subsection{Related work}
-\assign{Nathanael}
-\cite{cohen2017convolutional} \nati{+ add other graph CNN approaches \cite{...}}
+\assign{Nathanael, Michael}
+\label{sec:related}
+\cite{cohen2017convolutional} 
 \cite{cohen2018spherical}
@@
 
+\nati{+ add other graph CNN approaches \cite{...}}
+
 \section{Spherical convolution on sphere using a graph}
 \assign{Nathanael}
+
+As presented in~\cite{cohen2018spherical}, the most mathematical approach to extend convolution on a sphere is to use a spherical Fourier transform.
+Convolution is then simply defined as the product in the spectral domain.
+This approach requires one Fourier and one inverse Fourier transform per convolution which can be, even with accelerated algorithm, rather expensive.
+For 2-dimensional images, efficient convolution can be achieved when the convolution kernel is localized (for example a 5x5 pixel patch) by doing the computation directly in the signal domain.
+Unfortunately, this approach cannot be directly extended to the spherical case.
+Hence, the main idea of this contribution is to leverage graph signal processing~\cite{shuman2013emerging} to define a spherical convolution that can be computed direcly in the signal domain.
+
+In this section, we follow classical constructions presented in~\cite{cohen2018spherical,...} and \nati{show} that the resulting spherical convolution is close to one corresponding to spherical approach.
+
+\paragraph{Graph creation.}
+As a hard constraint resulting from the cosmological applications, we are bound to use the HealPix sampling~\cite{gorski2005healpix} and we create a weighted undirected graph where each pixel is a node (vertex) that is connected to his $8$ or $7$ closest neighboors\footnote{For some pixels, the $8^{th}$ nearest neighboor is not well defined.}.
+Given the set of nearest neighboors, we define the weight matrix $W$ using the following scheme
+\begin{equation}
+W[i,j]=\begin{cases}
+e^{-\frac{\|x_i-x_j\|_2^2}{\sigma^2}} & \text{if pixels $i$ and $j$ are connected, and}\\
+0 & \text{otherwise.}\\
+\end{cases}
+\end{equation}
+Here $x_i$ is a 3-dimensional vector encoding the coordinate of the pixels $i$ on the sphere and $\sigma$ is the mean of $\|x_i-x_j\|_2$ over all connected pixels $i$ and $j$.
+The degree of a node (or a pixel) is defined as $d_i = \sum_j W[i,j]$.
+The degree matrix $D$ is the diagonal matrix where $D_ii=d_i$.
+
+\paragraph{Fourier transform.}
+The graph noramalized Laplacian defined as $L = I - D^{-1/2} W D^{-1/2}$ is a second order differential operator that can be used to define the Fourier transform.
 

### 2018-03-07 scnn.tex
last update

--- 2018-03-01 scnn.tex
@@
 
+\nati{+ add other graph CNN approaches \cite{...}}
+
 \section{Spherical convolution on sphere using a graph}
 \assign{Nathanael}
+
+As presented in~\cite{cohen2018spherical}, the most mathematical approach to extend the convolution on a sphere is to use a spherical Fourier transform.
+The convolution is then simply defined as the product in the spectral domain.
+This approach requires one Fourier and one inverse Fourier transform per convolution which is, even with accelerated algorithms, rather expensive.
+For 2-dimensional images, an efficient convolution can be achieved when the convolution kernel is localized (for example a 5x5 pixel patch) by doing the computation directly in the signal domain.
+Unfortunately, this approach cannot be directly extended to the spherical case.
+Hence, the main idea of this contribution is to leverage graph signal processing~\cite{shuman2013emerging} to define a spherical convolution that can be computed directly in the signal domain.
+
+In this section, we follow classical constructions presented in~\cite{cohen2018spherical,...} and \nati{show} that the resulting spherical convolution is close to one corresponding to spherical approach.
+
+\paragraph{Graph creation.}
+As a hard constraint resulting from the cosmological applications, we are bound to use the HealPix sampling~\cite{gorski2005healpix} and we create a weighted undirected graph where each pixel is a node (vertex) that is connected to his $8$ or $7$ closest neighboors\footnote{For some pixels, the $8^{th}$ nearest neighbor is not well defined.}.
+Given the set of nearest neighbors, we define the weight matrix $W$ using the following scheme
+\begin{equation}
+W[i,j]=\begin{cases}
+e^{-\frac{\|x_i-x_j\|_2^2}{\sigma^2}} & \text{if pixels $i$ and $j$ are connected, and}\\
+0 & \text{otherwise.}\\
+\end{cases}
+\end{equation}
+Here $x_i$ is a 3-dimensional vector encoding the coordinate of the pixels $i$ on the sphere and $\sigma$ is the mean of $\|x_i-x_j\|_2$ over all connected pixels $i$ and $j$.
+The degree of a node (or a pixel) is defined as $d_i = \sum_j W[i,j]$.
+The degree matrix $D$ is the diagonal matrix where $D_ii=d_i$.
+
+\paragraph{Graph Fourier Transform and spherical harmonics.}
+The graph normalized graph Laplacian defined as $L = I - D^{-1/2} W D^{-1/2}$ is a second order differential operator that can be used to define the graph Fourier basis.
 

### 2018-03-07 scnn.tex
title remark and related work

@@
 
+	\todo{(Michaël) I would not invent a new term, SCNN, but rather say that convolutional neural networks on graphs (or GCNs) can be efficiently applied to (spherical?) cosmological applications.
+	Arguments: the method is not new and hence don't deserve a new name. Emphasize that it is generic to the data structure, and that the sphere is simply a particular graph.
+	Ideas: Graph Convolutional Networks for efficient spherical ???, Efficient spherical ??? with GCNs and Healpix sampling
+}
+
 \end{abstract}
@@
 
+Note that those neural networks are not restricted to the sphere and can be applied to any problem where we have data on a graph, such as social, biological or infrastructure networks.
+
 \subsection{Related work}
@@
 \nati{+ add other graph CNN approaches \cite{...}}
+
+Previous work: [Bruna] which needed the full eigendecomposition of the Laplacian, costing $O(n^3)$ operations.
+
+Spatial definitions of graph convolutions, e.g.
+[Niepert] needs to define an orientation in order to match the edges with the filters.
+Most often the orientation is not given by the application, and one has to define it (for example by ordering by degree or any other measure, or by using a graph coloring).
+There is no good default good orientation on general graphs and the choice of an orientation is highly application dependent.
+
+Related to this, convolutional neural networks have been defined on manifolds and have achieved impressive results on shapes [Bronstein].
+They however too depend on an orientation, which a sphere do not possess.
 

### 2018-03-07 scnn.tex
edits in introduction

@@
 \usepackage{amsmath}
+\usepackage{siunitx}
 
@@
 
-a) Cosmology has a lot of spherical data. Our solution is easy to use and is based on the widely used healpix sampling.
-b) It is the most efficient spherical convolution
+a) Cosmology has a lot of spherical data. Our method is simple and easy to use. Moreover, it is based on the widely used healpix sampling.
+b) It is the most efficient spherical convolution\footnote{\todo{provably?
+cannot be faster than O(n) without approximations, e.g.
+sketching}}, requiring only $O(n)$ operations, where $n$ is the number of points.
 
@@
 
-\begin{itemize}
+The analysis of spherical cosmological data, such as the cosmic microwave background \cite{...}, as done in \cite{he2018analysis}, is the target application of our method.
 
-	\item Efficient compression de-compression of 360 videos\cite{su2017learning}
-	\item Analysis of spherical cosmological data such as the cosmic microwave background \cite{...}, already done in\cite{he2018analysis}.
-\end{itemize}
+While our method was developed with cosmology in mind, it can easily target any problem where data live on a sphere.
+Examples include, but are certainly not limited to, (i) efficient compression and decompression of \ang{360} videos (see \cite{su2017learning}), (ii) \todo{data analysis on planets?
+(climate, forecasting, temperature, wind)}, (iii) \todo{particle physics?
+(jets on detectors, but they are usually cylindrical)}, (iv) \todo{applications in Cohen's papers?}.
 
-Note that those neural networks are not restricted to the sphere and can be applied to any problem where we have data on a graph, such as social, biological or infrastructure networks.
+Finally, not that those neural networks are not restricted to the sphere and can be applied to any problem where we have data on a graph, such as social, biological or infrastructure networks [some citations, e.g.
+brain Alzeihmer, particle physics].
+% the convolution is not restricted to the sphere, the coarsening/pooling is
 

### 2018-03-07 scnn.tex
update structure: method section, separate related work

@@
 
-\subsection{Motivation}
+%\subsection{Motivation}
 \assign{Tomek}
@@
 \subsection{Potential applications}
-	\assign{Tomek, Nathanael, Michael}
+	\assign{Tomek, Nathanaël, Michaël}
 
@@
 Finally, not that those neural networks are not restricted to the sphere and can be applied to any problem where we have data on a graph, such as social, biological or infrastructure networks [some citations, e.g.
-brain Alzeihmer, particle physics].
+brain Alzeihmer, particle physics, computer graphics].
 % the convolution is not restricted to the sphere, the coarsening/pooling is
 
-\subsection{Related work}
-\assign{Nathanael, Michael}
+\section{Related work}
 \label{sec:related}
+
+\subsection{Spherical convolutions}
+\assign{Nathanaël}
+
 \cite{cohen2017convolutional} 
@@
 \cite{boomsma2017spherical}
-\cite{defferrard2016convolutional}
 
-\nati{+ add other graph CNN approaches \cite{...}}
+\subsection{Convolutions on graphs}
+\assign{Michaël}
+
+\todo{other approaches? GNNs, Kipf first order approx, message passing}
 
 Previous work: [Bruna] which needed the full eigendecomposition of the Laplacian, costing $O(n^3)$ operations.
+
+In this work, we are using the graph CNN formulation introduced in \cite{defferrard2016convolutional}.
 
@@
 
+\subsection{Convolutions on manifolds}
+
 Related to this, convolutional neural networks have been defined on manifolds and have achieved impressive results on shapes [Bronstein].
-They however too depend on an orientation, which a sphere do not possess.
+They however too depend on an orientation, which spheres do not possess.
 
-\section{Spherical convolution on sphere using a graph}
-\assign{Nathanael}
+\subsection{Convolutions on point clouds?}
+
+PointNet and co. Related but we are loosing the structure. Also coarsening.
+
+\section{Method}
+
+The gist of our method is to define the convolution on a sphere using a graph.
+The graph is here seen as a discrete approximation of the sphere $S^2$, a 2-dimensional manifold embedded in $\mathbb{R}^3$.
 
@@
 
-\paragraph{Graph creation.}
+\subsection{Graph creation}
+\assign{Nathanaël}
+
 As a hard constraint resulting from the cosmological applications, we are bound to use the HealPix sampling~\cite{gorski2005healpix} and we create a weighted undirected graph where each pixel is a node (vertex) that is connected to his $8$ or $7$ closest neighboors\footnote{For some pixels, the $8^{th}$ nearest neighbor is not well defined.}.
@@
 
-\paragraph{Graph Fourier Transform and spherical harmonics.}
+\subsection{Coarsening}
+\assign{Nathanaël}
+
+How we get coarser or finer sampling of the sphere with Healpix. The $2^k \cdot 12$ points.
+
+\subsection{Graph Fourier basis and spherical harmonics}
+\assign{Nathanaël}
+% TODO: basis or transform?
+
 The graph normalized graph Laplacian defined as $L = I - D^{-1/2} W D^{-1/2}$ is a second order differential operator that can be used to define the graph Fourier basis.
@@
 
-\section{Efficient spherical CNN}
-\assign{Michael}
+\subsection{Convolutions on graphs}
+\assign{Nathanaël, Michaël}
+
+With the Fourier basis. Because we don't have an FFT, that costs $O(n^3)$ for the eigendecomposition, plus $O(n^2)$ for the transform (to be done for each forward and backward pass).
+
+\subsection{Efficient convolutions}
+\assign{Michaël}
 
@@
 \section{Experiments}
-\assign{Nathanael, Tomek}
+\assign{Nathanaël, Tomek}
 
@@
 \end{itemize}
+
+\section{Conclusion}
+\assign{Nathanaël, Tomek, Michaël}
 

### 2018-03-07 scnn.tex
further edits

@@
 
-As a hard constraint resulting from the cosmological applications, we are bound to use the HealPix sampling~\cite{gorski2005healpix} and we create a weighted undirected graph where each pixel is a node (vertex) that is connected to his $8$ or $7$ closest neighboors\footnote{For some pixels, the $8^{th}$ nearest neighbor is not well defined.}.
-Given the set of nearest neighbors, we define the weight matrix $W$ using the following scheme
+From the ubiquitous HealPix sampling~\citep{gorski2005healpix}, we create a weighted undirected graph where each pixel is a node (vertex) that is connected to his $8$ or $7$ closest neighbors.\footnote{For some pixels, the $8^{th}$ nearest neighbor is not well defined.} Given the set of nearest neighbors, we define the weight matrix $W$ using the following scheme
 \begin{equation}
@@
 The degree of a node (or a pixel) is defined as $d_i = \sum_j W[i,j]$.
-The degree matrix $D$ is the diagonal matrix where $D_ii=d_i$.
+The degree matrix $D$ is the diagonal matrix where $D_{ii}=d_i$.
 

### 2018-03-08 scnn.tex
experiments & data

@@
 
+Show the spherical harmonics.
+
 \begin{itemize}
@@
 \section{Experiments}
+
+What do we want to show? The graph CNN is able to discriminate ??? using higher order statistics.
+
+\subsection{Data}
+\assign{Tomek}
+
+Our data comes from a simulation with software ???
+using the following parameters ???.
+All the data to reproduce our experiments are available online.\footnote{\url{https://doi.org/10.5281/zenodo.????} \todo{correct DOI}}
+
+\subsection{Results}
 \assign{Nathanaël, Tomek}
@@
 \end{itemize}
+
+\subsection{Interpretation}
+\assign{Nathanaël, Tomek, Michaël}
+
+Show the learned filters and feature maps and try to interpret them.
 

### 2018-03-13 scnn.tex
add info spherical CNN comparison

--- 2018-03-07 scnn.tex
@@
 \cite{cohen2018spherical}
+\nati{I meet one of the author of \cite{cohen2018spherical} and we talk for an hour. Here is what I learned}
+Very recently, a version of spherical convolutional neural networks have been proposed in~\cite{cohen2017convolutional,cohen2018spherical}.
+The main goal of this contribution is to develop a CNN with a convolution that is rotation-equivariant on the sphere, i.e.
+a rotation of the input implies the same rotation of the output.
+The resulting convolution is performed by a spherical Fourier transform (i.e.
+a projection on the spherical harmonics), a  multiplication in the spectral domain and an inverse spherical Fourier tranform.
+The approach is mathematically well justifed and illustrated with a few experiments.
+The main computational cost of the convultion comes from the two Fourier transforms.
+The Fourier transform can be accelerated for special samplings set (including the healpix).
+Nevertheless, even with these acceleration, the convolution seems to be more expensive than graph convolution.
+A comparizon would be very complicated because the author have focused on \nati{...} sampling set and do not provide any code for the Healpix one.
+
 \cite{boomsma2017spherical}
-
+,
 \subsection{Convolutions on graphs}

### 2018-04-05 scnn.tex
add a plot list

@@
 
+\todo{Cool to have a global illustration of the network (CNN like)}
+
 \subsection{Convolutions on manifolds}
@@
 
+Figure Graph (show also the triangle, separate plot?) + sampling
+
 \subsection{Coarsening}
@@
 How we get coarser or finer sampling of the sphere with Healpix. The $2^k \cdot 12$ points.
+
+Figure heaplix pooling.
 
@@
 
-Show the spherical harmonics.
+Figure our harmonics.
 
@@
 
+Example on the heat equation
+Figure filters
+Figure diffusion (unit of heat)
+
 \subsection{Efficient convolutions}
@@
 	\item We need efficient convolution, hence the Chebysheff trick
+	\item Explain the different between a polynomial filter convolution and a traditional patch restricted convolution
 	\item Define spherical CNN using graph CNN
@@
 
+Figure: part map plot
+
 \subsection{Results}
@@
 \end{itemize}
+
+Figure: Result curves
+
+Figure: Filter if they look good.
 

### 2018-04-10 scnn.tex
update plot list
include figures in tex

@@
 
+\subsection{Healpix sampling}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.95\textwidth]{figures/healpix-3layers.jpg}
+\caption{3 smaller sclales of the healpix sampling.}
+\label{fig:healpix_sampling}
+\end{figure}
+
 \section{Related work}
@@
 
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.45\textwidth]{figures/healpix_graph_4.pdf}
+\includegraphics[width=0.45\textwidth]{figures/half_graph_4.pdf}
+\caption{Left: Healpix graph for the full sphere using a nside parameter of $4$. Right: Top view of a Healpix graph for half the sphere using a nside parameter of $4$.}
+\label{fig:healpix_graph_4}
+\end{figure}
+
 From the ubiquitous HealPix sampling~\citep{gorski2005healpix}, we create a weighted undirected graph where each pixel is a node (vertex) that is connected to his $8$ or $7$ closest neighbors.\footnote{For some pixels, the $8^{th}$ nearest neighbor is not well defined.} Given the set of nearest neighbors, we define the weight matrix $W$ using the following scheme
@@
 
-Figure heaplix pooling.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.95\textwidth]{figures/pooling.pdf}
+\caption{Pooling, 1/12 of the sphere, 2 levels, molview projection.}
+\label{fig:pooling}
+\end{figure}
 
@@
 
-Figure our harmonics.
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.95\textwidth]{figures/eigenvectors.pdf}
+\caption{12 first graph Fourier eigenvectors.}
+\label{fig:graph_harmonics}
+\end{figure}
 
@@
 Example on the heat equation
-Figure filters
-Figure diffusion (unit of heat)
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_sphere.pdf}
+\caption{Top: Diffusion of a unit of heat for different time using the graph. Bottom: gaussian filtering on the sphere. Relative difference of the two diffusions: $13.5$\%, $6.1$\%, $5.2$\%, $3.8$\% }
+\label{fig:gaussian_filters_comparizon}
+\end{figure}
+
+Figure filters 3 representations for both graph + spherical Fourier
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_spectral.pdf}
+\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_gnomonic.pdf}
+\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_section.pdf}
+\caption{3 Different effet visualization of filters. Top: Graph spectral domain. Middle: gnomonic projection on the sphere. Bottom: section of filter.}
+\label{fig:gaussian_filters_visualization}
+\end{figure}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.45\textwidth]{figures/index_plotting_order20_nside16.pdf}
+
+\caption{Indexes selected for the section ploting of the filter.}
+\label{fig:index_section}
+\end{figure}
 
@@
 
-Figure: part map plot
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.45\textwidth]{figures/smooth_map_class_1.pdf}
+\includegraphics[width=0.45\textwidth]{figures/smooth_map_class_2.pdf}
+\caption{One sample of each class }
+\label{fig:map_sample}
+\end{figure}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.45\textwidth]{figures/part_sphere.pdf}
+\caption{3 subparts of the sphere with different sizes. Blue: order 1. Green: order 2. Yellow: order 3.}
+\label{fig:subpart_sphere}
+\end{figure}
 
@@
 
-Figure: Filter if they look good.
+Figure: Filters 1D and Gnonomic
 

### 2018-04-25 scnn.tex
add figure results
first version of the comparizon of spherical convolution

@@
 
+\todo{
 \subsection{Healpix sampling}
+Should we have this subsection to explain the advantages of Healpix?
+\begin{itemize}
+	\item Define the gedesic grid?
+	\item reference the "cubed sphere"~\cite{ronchi1996cubed}?
+\end{itemize}
+}
 
@@
 \subsection{Spherical convolutions} 
-\assign{Nathanaël}
+The major challenge to generalize CNN to a
+spherical domain is to generalize convolution. In the context of CNN, we found
+two particular approaches to address this issue.
 
-\cite{cohen2017convolutional} 
-\cite{cohen2018spherical}
-\nati{I meet one of the author of \cite{cohen2018spherical} and we talk for an hour. Here is what I learned}
-Very recently, a version of spherical convolutional neural networks have been proposed in~\cite{cohen2017convolutional,cohen2018spherical}.
-The main goal of this contribution is to develop a CNN with a convolution that is rotation-equivariant on the sphere, i.e.
-a rotation of the input implies the same rotation of the output.
-The resulting convolution is performed by a spherical Fourier transform (i.e.
-a projection on the spherical harmonics), a  multiplication in the spectral domain and an inverse spherical Fourier tranform.
-The approach is mathematically well justifed and illustrated with a few experiments.
-The main computational cost of the convultion comes from the two Fourier transforms.
-The Fourier transform can be accelerated for special samplings set (including the healpix).
-Nevertheless, even with these acceleration, the convolution seems to be more expensive than graph convolution.
-A comparizon would be very complicated because the author have focused on \nati{...} sampling set and do not provide any code for the Healpix one.
+The first approach, leveraging the continuous spherical convolution, has been
+proposed in~\cite{cohen2017convolutional,cohen2018spherical}. These
+contributions propose to use a convolution that is rotational equivariant on the
+sphere, i.e. a rotation of the input implies the same rotation of the output.
+The convolution is performed by a spherical Fourier transform (i.e. a projection
+on the spherical harmonics), a  multiplication in the spectral domain and an
+inverse spherical Fourier tranform. Hence the main computational cost of a
+convolution comes from the two Fourier transforms. Fortunately, the Fourier
+transform can be accelerated for special samplings set (theoretically including
+HealPix). The main advantage of this approach is that it provides a
+mathematically well defined rotational equivariant network. Nevertheless, even
+with these Fourier transform acceleration, the convolutions remain expensive in
+comparison to a traditional 2D convolution, limiting the practical use of this
+approach. While a comparison is theoretically possible, the experiments
+of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and
+do not provide any code for the Healpix one. Hence, a practical comparison is
+not possible.
 
-\cite{boomsma2017spherical}
-,
+A second direction has been followed in~\cite{boomsma2017spherical}. The idea is
+to use the traditional 2D convolution on an irregular grid defined on the
+sphere. In the paper, two grids are used: the geodesic grid and the “cubed
+sphere” grid defined by Ronchi et. al~\cite{ronchi1996cubed}. Because this
+approach is based on the traditional 2D convolution, it is very likely to be the
+most efficient one. However, it suffers that it can only be used using very
+specific grid sampling sets which are NOT including HealPix. Furthermore, the
+grid requirement makes it impossible for the convolution to capture the
+spherical properties of the domain, i.e. the "cubed sphere” sampling is by
+definition adapted to a cube and not to a sphere. \nati{Michael: Under some very
+specific hypothesis, this second approach is a particular case of our method,
+i.e. 1) our method with a stupid sampling, 2) assumption that graph convolution
+on a grid == 2d convolution. Do you think we should mention that? I think we
+should not.}
+
+In an attempt to get the best of the two approaches, we follow a third
+direction. We use a graph to adapt to the particular structure of the sphere.
+While the convolution remains efficient, it still captures well the spherical
+structure and is particularly adapted to the HealPix sampling.
+
 \subsection{Convolutions on graphs}
@@
 
-In this work, we are using the graph CNN formulation introduced in \cite{defferrard2016convolutional}.
+In this work, we are using the graph CNN formulation introduced in~\cite{defferrard2016convolutional}.
 
@@
 \subsection{Results}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.32\textwidth]{figures/result_order1.pdf}
+\includegraphics[width=0.32\textwidth]{figures/result_order2.pdf}
+\includegraphics[width=0.32\textwidth]{figures/result_order4.pdf}
+\caption{Classification errors for the 3 different problems.}
+\label{fig:results}
+\end{figure}
+
 \assign{Nathanaël, Tomek}

### 2018-04-25 scnn.tex
starting section graph

@@
 with these Fourier transform acceleration, the convolutions remain expensive in
-comparison to a traditional 2D convolution, limiting the practical use of this
+comparison to a traditional 2-dimensional convolution, limiting the practical use of this
 approach. While a comparison is theoretically possible, the experiments
@@
 A second direction has been followed in~\cite{boomsma2017spherical}. The idea is
-to use the traditional 2D convolution on an irregular grid defined on the
+to use the traditional 2-dimensional convolution on an irregular grid defined on the
 sphere. In the paper, two grids are used: the geodesic grid and the “cubed
 sphere” grid defined by Ronchi et. al~\cite{ronchi1996cubed}. Because this
-approach is based on the traditional 2D convolution, it is very likely to be the
+approach is based on the traditional 2-dimensional convolution, it is very likely to be the
 most efficient one. However, it suffers that it can only be used using very
@@
 The gist of our method is to define the convolution on a sphere using a graph.
-The graph is here seen as a discrete approximation of the sphere $S^2$, a 2-dimensional manifold embedded in $\mathbb{R}^3$.
+The graph is here seen as a discrete approximation of the sphere $S^2$, a
+2-dimensional manifold embedded in $\mathbb{R}^3$.
 
-As presented in~\cite{cohen2018spherical}, the most mathematical approach to extend the convolution on a sphere is to use a spherical Fourier transform.
-The convolution is then simply defined as the product in the spectral domain.
-This approach requires one Fourier and one inverse Fourier transform per convolution which is, even with accelerated algorithms, rather expensive.
-For 2-dimensional images, an efficient convolution can be achieved when the convolution kernel is localized (for example a 5x5 pixel patch) by doing the computation directly in the signal domain.
-Unfortunately, this approach cannot be directly extended to the spherical case.
-Hence, the main idea of this contribution is to leverage graph signal processing~\cite{shuman2013emerging} to define a spherical convolution that can be computed directly in the signal domain.
-
-In this section, we follow classical constructions presented in~\cite{cohen2018spherical,...} and \nati{show} that the resulting spherical convolution is close to one corresponding to spherical approach.
+As presented in~\cite{cohen2018spherical}, the most mathematical approach to
+extend the convolution on a sphere is to use a spherical Fourier transform. The
+convolution is then simply defined as the product in the spectral domain. This
+approach requires one Fourier and one inverse Fourier transform per convolution
+which remain, even with accelerated algorithms, expensive. For 2-dimensional
+images, an efficient convolution can be achieved when the convolution kernel is
+localized (for example a 5x5 pixel patch) by doing the computation directly in
+the signal domain. Unfortunately, this approach cannot be directly extended to
+the spherical case. Hence, the main idea of this contribution is to leverage
+graph signal processing~\cite{shuman2013emerging} to define a spherical
+convolution that can be computed directly in the signal domain.
 
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.45\textwidth]{figures/healpix_graph_4.pdf}
-\includegraphics[width=0.45\textwidth]{figures/half_graph_4.pdf}
-\caption{Left: Healpix graph for the full sphere using a nside parameter of $4$. Right: Top view of a Healpix graph for half the sphere using a nside parameter of $4$.}
-\label{fig:healpix_graph_4}
-\end{figure}
-
-From the ubiquitous HealPix sampling~\citep{gorski2005healpix}, we create a weighted undirected graph where each pixel is a node (vertex) that is connected to his $8$ or $7$ closest neighbors.\footnote{For some pixels, the $8^{th}$ nearest neighbor is not well defined.} Given the set of nearest neighbors, we define the weight matrix $W$ using the following scheme
+In the classical 2-dimenstional convolution, each pixel is connected with the
+same weight to its 4 closest neighbors. We use a graph to generalize this to the
+irregular sphear sampling. From the ubiquitous HealPix
+sampling~\citep{gorski2005healpix}, we create a weighted undirected graph where
+each pixel is a node (vertex) that is connected to his $8$ or $7$ closest
+neighbors.\footnote{For some pixels, the $8^{th}$ nearest neighbor is not well
+defined.} Given the set of nearest neighbors, we define the weight matrix $W$
+using the following scheme
 \begin{equation}
@@
 \end{equation}
-Here $x_i$ is a 3-dimensional vector encoding the coordinate of the pixels $i$ on the sphere and $\sigma$ is the mean of $\|x_i-x_j\|_2$ over all connected pixels $i$ and $j$.
-The degree of a node (or a pixel) is defined as $d_i = \sum_j W[i,j]$.
-The degree matrix $D$ is the diagonal matrix where $D_{ii}=d_i$.
-
-Figure Graph (show also the triangle, separate plot?) + sampling
-
-\subsection{Coarsening}
-\assign{Nathanaël}
-
-How we get coarser or finer sampling of the sphere with Healpix. The $2^k \cdot 12$ points.
+Here $x_i$ is a 3-dimensional vector encoding the coordinate of the pixels $i$
+on the sphere and $\sigma$ is the mean of $\|x_i-x_j\|_2$ over all connected
+pixels $i$ and $j$. The degree of a node (or a pixel) is defined as $d_i =
+\sum_j W[i,j]$. The degree matrix $D$ is the diagonal matrix where $D_{ii}=d_i$. 
+An example of the resulting graph is displayed in Figure~\ref{fig:healpix_graph_4}.
 
@@
 \centering
-\includegraphics[width=0.95\textwidth]{figures/pooling.pdf}
-\caption{Pooling, 1/12 of the sphere, 2 levels, molview projection.}
-\label{fig:pooling}
+% \includegraphics[width=0.45\textwidth]{figures/healpix_graph_4.pdf}
+\includegraphics[width=0.45\textwidth]{figures/half_graph_4.pdf}
+\caption{
+% Left: Healpix graph for the full sphere using a nside parameter of $4$. 
+Top view of a Healpix graph for half the sphere using a nside parameter of $4$.}
+\label{fig:healpix_graph_4}
 \end{figure}
@@
 \end{itemize}
+
+\subsection{Coarsening}
+\assign{Nathanaël}
+
+How we get coarser or finer sampling of the sphere with Healpix. The $2^k \cdot 12$ points.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.95\textwidth]{figures/pooling.pdf}
+\caption{Pooling, 1/12 of the sphere, 2 levels, molview projection.}
+\label{fig:pooling}
+\end{figure}
 

### 2018-04-26 scnn.tex
end of the day

@@
 In the classical 2-dimenstional convolution, each pixel is connected with the
-same weight to its 4 closest neighbors. We use a graph to generalize this to the
-irregular sphear sampling. From the ubiquitous HealPix
-sampling~\citep{gorski2005healpix}, we create a weighted undirected graph where
-each pixel is a node (vertex) that is connected to his $8$ or $7$ closest
-neighbors.\footnote{For some pixels, the $8^{th}$ nearest neighbor is not well
-defined.} Given the set of nearest neighbors, we define the weight matrix $W$
-using the following scheme
+same weight to its 4 closest neighbors. We use a weighted undirected graph to
+generalize this idea to the ubiquitous HealPix
+sampling~\citep{gorski2005healpix}.  Each pixel is represented by a node
+(vertex) connected to his $8$ or $7$ closest neighbors.\footnote{For some
+pixels, the $8^{th}$ nearest neighbor is not well defined.} Given the set of
+nearest neighbors, we define the weight matrix $W$ using the following scheme
 \begin{equation}
@@
 on the sphere and $\sigma$ is the mean of $\|x_i-x_j\|_2$ over all connected
-pixels $i$ and $j$. The degree of a node (or a pixel) is defined as $d_i =
+pixels $i$ and $j$. This weighting scheme is important as the distances between
+pixels varries du to the small sampling irregularities. Some of the
+irregularities have been highlighted in the graph displayed in
+Figure~\ref{fig:healpix_graph_4}.
+
+These small irregularities are important as they prevent our approach to be affect slightly the degree of a node (or a pixel), defined as $d_i =
 \sum_j W[i,j]$. The degree matrix $D$ is the diagonal matrix where $D_{ii}=d_i$.
-An example of the resulting graph is displayed in Figure~\ref{fig:healpix_graph_4}.
 

### 2018-04-27 scnn.tex
some more work

@@
 \section{Method}
+% \begin{itemize}
+% 	\item We build a graph using the healpix sampling
+% 	\item Define Fourier transform and show that the harmonics are visually close to the spherical harmonics
+% 	\item Define spherical convolution using the graph Fourier transform and show heat diffusion example
+% 	\item Show the limits of the approach and explain why we cannot have a perfect spherical convolution with this technique
+% \end{itemize}
 
@@
 \subsection{Graph creation}
-\assign{Nathanaël}
-
 In the classical 2-dimenstional convolution, each pixel is connected with the
@@
 
-These small irregularities are important as they prevent our approach to be affect slightly the degree of a node (or a pixel), defined as $d_i =
-\sum_j W[i,j]$. The degree matrix $D$ is the diagonal matrix where $D_{ii}=d_i$.
+These small irregularities are important and affect slightly the degree of a 
+node (or a pixel), defined as $d_i =\sum_j W[i,j]$.
 
@@
 % \includegraphics[width=0.45\textwidth]{figures/healpix_graph_4.pdf}
+\vspace{-0.5cm}
 \includegraphics[width=0.45\textwidth]{figures/half_graph_4.pdf}
+\vspace{-0.5cm}
 \caption{
@@
 \subsection{Graph Fourier basis and spherical harmonics}
-\assign{Nathanaël}
-% TODO: basis or transform?
 
-The graph normalized graph Laplacian defined as $L = I - D^{-1/2} W D^{-1/2}$ is a second order differential operator that can be used to define the graph Fourier basis.
+Because of the irregular sampling, there is no obvious way to define convolution
+directly from the pixel values. Hence we first define a Fourier transform on the
+graph.
+
+Following~\cite{shuman2013emerging}, the graph normalized graph Laplacian
+defined as $L = I - D^{-1/2} W D^{-1/2}$ is a second order differential operator
+that can be used to define the graph Fourier basis. Here $D$ is the diagonal
+matrix where $D_{ii}=d_i$. The graph Fourier basis is defined as the harmonic
+decomposition of the graph Laplacian $L=U \Lambda U^*$, where $U$ is the
+orthonormal matrix of eigenvectors and $\Lambda$, the diagonal matrix of
+eigenvalues.
 
@@
 
-\begin{itemize}
-	\item We build a graph using the healpix sampling
-	\item Define Fourier transform and show that the harmonics are visually close to the spherical harmonics
-	\item Define spherical convolution using the graph Fourier transform and show heat diffusion example
-	\item Show the limits of the approach and explain why we cannot have a perfect spherical convolution with this technique
-\end{itemize}
+As shown in Figure~\ref{fig:graph_harmonics}, it turns out that using the graph
+construction described above, the graph Fourier harmonics ressembles the
+classical spherical harmonics giving us an indication that the graph is able to
+capture the spherical properties of the HealPix sampling.
 
@@
 
-With the Fourier basis. Because we don't have an FFT, that costs $O(n^3)$ for the eigendecomposition, plus $O(n^2)$ for the transform (to be done for each forward and backward pass).
+Convolution
 
@@
 \includegraphics[width=0.45\textwidth]{figures/index_plotting_order20_nside16.pdf}
-
 \caption{Indexes selected for the section ploting of the filter.}
@@
 \assign{Michaël}
-
+With the Fourier basis. Because we don't have an FFT, that costs $O(n^3)$ for the eigendecomposition, plus $O(n^2)$ for the transform (to be done for each forward and backward pass).
 \begin{itemize}

### 2018-04-30 scnn.tex
end of the day

@@
 \usepackage{siunitx}
+\usepackage{bm}
 
@@
 \newcommand{\assign}[1]{{\color[rgb]{.8,.5,.8}{Assigned: #1 }}}
+
+\renewcommand{\b}[1]{{\bm{#1}}}   % bold symbol
+
+% MATH SYMBOLS
+\newcommand{\1}{\b{1}}              % all-ones vector
+\newcommand{\0}{\b{0}}              % all-zero vector
+\newcommand{\g}[1]{\b{#1}}
+\renewcommand{\L}{\b{L}} % the laplacian matrix
+\newcommand{\W}{\b{W}} 
+\newcommand{\I}{\b{I}} 
+\newcommand{\D}{\b{D}} 
+\newcommand{\U}{\b{U}}
+\newcommand{\bLambda}{\b{\Lambda}} 
+\newcommand{\blambda}{\b{\lambda}}
 
@@
 Following~\cite{shuman2013emerging}, the graph normalized graph Laplacian
-defined as $L = I - D^{-1/2} W D^{-1/2}$ is a second order differential operator
+defined as $\L = \I - \D^{-1/2} \W \D^{-1/2}$ is a second order differential operator
 that can be used to define the graph Fourier basis. Here $D$ is the diagonal
-matrix where $D_{ii}=d_i$. The graph Fourier basis is defined as the harmonic
-decomposition of the graph Laplacian $L=U \Lambda U^*$, where $U$ is the
-orthonormal matrix of eigenvectors and $\Lambda$, the diagonal matrix of
-eigenvalues.
+matrix where $\D_{ii}=\b{d}_i$. By construction the Laplacian is symetric postive
+semi-definite and hence can be decomposed as $\L=\U \bLambda \U^*$, where $U$ is an
+orthonormal matrix of eigenvectors and $\bLambda$, the diagonal matrix of
+eigenvalues. The graph Fourier basis is defined as the Laplacian eigenvectors.
+The graph Fourier transform of $f$ is simply its projection on $U$ given by 
+$\hat{\b{f}}=\U^*\b{f}$. Similarly the inverse graph Fourier transform reads $\b{f}=\U\hat{\b{f}}$.
+Note that instead of frequencies, the Fourier modes are crescently ordered with
+respect of the Laplacian eigenvalues $\bLambda$. In a sense, the Laplacian
+eigenvalues correspond to the squared frequencies.
 
@@
 
-Convolution
+Graph convolution is defined by generalizing the concept that convolution is a
+multiplication in the spectral domain. Given a convolution kernel 
+$h:\mathbb{R}_+\rightarrow\mathbb{R}$, the convolution of a signal $\b{f}$ 
+is defined as
+\begin{equation} \label{def:graph_convolution}
+h(L)\b{f} = \U h(\bLambda) \U^* \b{f},
+\end{equation}
+where $h(\bLambda)$ is a diagonal matrix where $h(\bLambda)_{ii}=h(\bLambda_{ii})$.
+Equation~\ref{def:graph_convolution} contains three parts: a) $\U^* \b{f}$, the 
+Fourier transform of $\b{f}$; b) $h(\bLambda)$ the multiplication with the Fourier 
+kernel $h(\blambda)$; and c) $\U$ the inverse Fourier transform.
+
+The major difference with classical convolution is that the convolution kernel
+$h$ cannot be thought as $n \times n$ pattern, but is a continuous function
+applied to the graph eigenvalues $\bLambda$. For visualization puposes, one can
+look at effect of the convolution on a dirac, i.e. one column of the matrix
+$h(\L)$. \nati{However, due to the non regularity of the graph (i.e. the fact
+that there is not perfect sampling on the sphere), this visualization will
+differ from one node to another. In the specific case of the full sphere, these
+difference are negligible in most of the cases. When considering only subpart of
+the sphere, one will observe important border effects.}
+
+\paragraph{Example: heat diffusion}
+Let us consider the heat diffusion problem 
+\begin{equation} \label{eq:heat_equation}
+\L \b{f}(t) = \tau \partial_t \b{f}(t),
+\end{equation}
+where $\b{f}(t): \mathbb{R}_+ \rightarrow \mathbb{R}^N$. Given the initial condition 
+$\b{f}(0)$, the solution of~\ref{eq:heat_equation} can be expressed as
+\begin{equation}
+\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U^* \g{f}(0) = K_t(\L) \b{f}(0), 
+\end{equation}
+which is a convolution of the signal $\b{f}(0)$ with the kernel 
+$K_t(x)=e^{-\tau t x}$. Here the kernel $K_t$ is applied to the correspond
+In Figure~\ref{fig:gaussian_filters_comparizon}, we show the effect of the convolution by diffusing a unit of heat for various amount of time.
 

### 2018-05-01 scnn.tex
update convolution

@@
 \subsection{Graph Fourier basis and spherical harmonics}
+\todo{Add a few extra references}
 
@@
 \subsection{Convolutions on graphs}
-\assign{Nathanaël, Michaël}
+\assign{Nathanaël, Michaël} \todo{Add a few extra references}
 
@@
 \end{equation}
-which is a convolution of the signal $\b{f}(0)$ with the kernel 
-$K_t(x)=e^{-\tau t x}$. Here the kernel $K_t$ is applied to the correspond
-In Figure~\ref{fig:gaussian_filters_comparizon}, we show the effect of the convolution by diffusing a unit of heat for various amount of time.
+which is a convolution of the signal $\b{f}(0)$ with the kernel $K_t(x)=e^{-\tau
+t x}$. Here the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$ that
+correspond to the squared frequencies and hence $K_t$ can be considered a
+Gaussian kernel. In Figure~\ref{fig:gaussian_filters_comparizon} top, we show
+the effect of the convolution by diffusing a unit of heat for $\tau=1$ and various 
+time $t$. In  Figure~\ref{fig:gaussian_filters_visualization} of
+Appendix~\ref{app:filter_visualization}, we show different visualizaton of the
+convolution kernel $K_t$. We also compare the graph convolution with the
+spherical symmetric Gaussian smoothing
+(Figure~\ref{fig:gaussian_filters_comparizon} bottom) and observe that both
+techniques lead to similar results. While the graph convolution is different
+from a true spherical convolution, it can, providing the correct
+parametrization, well approximate it.
 
-Example on the heat equation
 \begin{figure}[!ht]
@@
 \includegraphics[width=0.95\textwidth]{figures/gaussian_filters_sphere.pdf}
-\caption{Top: Diffusion of a unit of heat for different time using the graph. Bottom: gaussian filtering on the sphere. Relative difference of the two diffusions: $13.5$\%, $6.1$\%, $5.2$\%, $3.8$\% }
+\caption{Convolution comparizon (Nside=16). 
+Top: Diffusion of a unit of heat for different time $t$ using the graph. 
+Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin). 
+Relative difference between graph convolution and spherical smoothing: $10.4$\%, $5.7$\%, $4.8$\%, $3.8$\% }
 \label{fig:gaussian_filters_comparizon}
@@
 
-Figure filters 3 representations for both graph + spherical Fourier
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_spectral.pdf}
-\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_gnomonic.pdf}
-\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_section.pdf}
-\caption{3 Different effet visualization of filters. Top: Graph spectral domain. Middle: gnomonic projection on the sphere. Bottom: section of filter.}
-\label{fig:gaussian_filters_visualization}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.45\textwidth]{figures/index_plotting_order20_nside16.pdf}
-\caption{Indexes selected for the section ploting of the filter.}
-\label{fig:index_section}
-\end{figure}
+It is another sign that the constructed graph is able to capture the spherical
+structure of the healpix sampling. Furthemore, in some application, where the
+exactitude of the convolution is not requirement, such as de-noising, it means
+that we could use graph convolution instead. Depending on the convolution kernel
+this may reveal much more efficient. In the case of a neural network, the fact
+that both convolution are not identical is not very relevant since the network
+will adapt the convolution at use.
 
@@
 %% appendix sections are then done as normal sections
-%% \appendix
+\appendix
 
-%% \section{}
-%% \label{}
+\section{Filter visualization}
+\label{app:filter_visualization}
+
+In Figure~\ref{fig:gaussian_filters_visualization}, we present three different
+ways to plot the graph convolution kernel $K_t(x)=e^{-\tau t x}$.  First, it can
+be ploted in the graph spectral domain. In this case, we simply evaluate $K_t$
+at the graph eigenvalues $\text{diag}(\bLambda)$. Second, we can convolve a
+delta on the sphere and plot a gnomonic view of the results. Third, since we are
+working on the sphere, we can only plot the section of the convoluted delta. In
+Figure~\ref{fig:index_section}, we display the selected indexes for the section
+plotting. Note that, because of the small irregularities in the HealPix
+sampling, the second and the third methods are likely to change depending on the
+chosen delta.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_spectral.pdf}
+\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_gnomonic.pdf}
+\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_section.pdf}
+\caption{3 different visualizations of the convolution kernel $K_t(x)=e^{-\tau t x}$.  
+Top: graph spectral domain. 
+Middle: gnomonic projection.
+Bottom: section plot.}
+\label{fig:gaussian_filters_visualization}
+\end{figure}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.45\textwidth]{figures/index_plotting_order20_nside16.pdf}
+\caption{Indexes selected for the section ploting of Figure~\ref{fig:gaussian_filters_visualization} middle. The delta was placed on the yellow node.}
+\label{fig:index_section}
+\end{figure}
 

### 2018-05-01 scnn.tex
add pooling

@@
 \subsection{Coarsening}
-\assign{Nathanaël}
-
-How we get coarser or finer sampling of the sphere with Healpix. The $2^k \cdot 12$ points.
-
+The HealPix sampling present the advantage to have a natural corsening method
+based on its construction. Each nside level divides each pixel into 4 subpixels.
+We define the pooling process as the inverse operation grouping the 4 subpixels.
+Figure~\ref{fig:pooling} illustrates the process.
 \begin{figure}[!ht]
@@
 \includegraphics[width=0.95\textwidth]{figures/pooling.pdf}
-\caption{Pooling, 1/12 of the sphere, 2 levels, molview projection.}
+\caption{Pooling illustration for 2 levels using some part of the the mollview projection. 
+The final patch represent 1/12 of the sphere.}
 \label{fig:pooling}

### 2018-05-03 scnn.tex
start with experiment

@@
 
+\todo{Check this unpublished work \cite{khasanova2017graph}}
+
 In an attempt to get the best of the two approaches, we follow a third
@@
 
-What do we want to show? The graph CNN is able to discriminate ??? using higher order statistics.
+% Structure of the section
+% 1) Present the goal
+% 2) Explain briefly the dataset
+% 3) Present the setting
+% 4) Describe the result
+In this section, we demonstrate the usefulness of the spherical neural network
+on a discrimination problem. Our implementation is availlable as small python package at \url{https://our.code.link.com}. 
+Furthermore, all the data to reproduce our experiments are available online.\footnote{\url{https://doi.org/10.5281/zenodo.????} \todo{correct DOI}}
 
@@
 
-Our data comes from a simulation with software ???
-using the following parameters ???.
-All the data to reproduce our experiments are available online.\footnote{\url{https://doi.org/10.5281/zenodo.????} \todo{correct DOI}}
+Our data comes from a simulation with software ??? using the following parameters ???.
+
+As a preprocssing step, we first remove the mean of each sample and apply a
+spherical gaussian smoothing kernel with a radius of $1$ arcmin.
+
+We made 30 simulations for each class. Out of the 60 simulations, 20 are kept
+for the test set. The training and validation set are created later on.
 
@@
 \includegraphics[width=0.45\textwidth]{figures/smooth_map_class_2.pdf}
-\caption{One sample of each class }
+\caption{One sample of each class.}
 \label{fig:map_sample}
 \end{figure}
+
+\subsection{Problem formulation}
+
+Leveraging the properties of the HealPix sampling, we can split each simulation
+into $12*4^o$ ($o=0,1,2,\dots$) samples that span a smaller part of the sphere.
+As shown in Figure~\ref{fig:subpart_sphere}, we used $o=0,1,2$ as the resulting
+samples are large enough to suffer from the effet of the spherical geometry. We
+decided to only report simulation results for this specific setting as spherical
+cosmological data usually does not span the full sphere. However, our code
+includes an example using the full sphere.
 
@@
 \includegraphics[width=0.45\textwidth]{figures/part_sphere.pdf}
-\caption{3 subparts of the sphere with different sizes. Blue: order 1. Green: order 2. Yellow: order 3.}
+\caption{3 subparts of the sphere with different sizes. Blue: $o=0$. Green: order $o=1$. Yellow: order $o=2$.}
 \label{fig:subpart_sphere}

### 2018-05-07 scnn.tex
update template
a bit more

@@
 
-\documentclass[preprint,12pt,authoryear]{elsarticle}
+% \documentclass[preprint,12pt,authoryear]{elsarticle}
+\documentclass[final,twocolumn,3p,times,authoryear]{elsarticle}
 
@@
 
-\begin{figure}[!ht]
+\begin{figure*}[!ht]
 \centering
-\includegraphics[width=0.95\textwidth]{figures/healpix-3layers.jpg}
+\includegraphics[width=0.7\textwidth]{figures/healpix-3layers.jpg}
 \caption{3 smaller sclales of the healpix sampling.}
 \label{fig:healpix_sampling}
-\end{figure}
+\end{figure*}
 
@@
 \caption{
-% Left: Healpix graph for the full sphere using a nside parameter of $4$. 
-Top view of a Healpix graph for half the sphere using a nside parameter of $4$.}
+Top view of a Healpix graph for half the sphere using a nside parameter of $4$.
+Nodes with 7 neighboors are highlighted.
+}
 \label{fig:healpix_graph_4}
@@
 
-\begin{figure}[!ht]
+\begin{figure*}[!ht]
 \centering
@@
 \label{fig:graph_harmonics}
-\end{figure}
+\end{figure*}
 
@@
 \label{fig:gaussian_filters_comparizon}
-\end{figure}
+\end{figure*}
 
@@
 \centering
-\includegraphics[width=0.95\textwidth]{figures/pooling.pdf}
+\includegraphics[width=0.45\textwidth]{figures/pooling.pdf}
 \caption{Pooling illustration for 2 levels using some part of the the mollview projection. 
@@
 decided to only report simulation results for this specific setting as spherical
-cosmological data usually does not span the full sphere. However, our code
+cosmological data usually does not span the full sphere. Nevertheless, our code
 includes an example using the full sphere.
@@
 
+We would like to build a robust classifier, i.e. an automatic way to
+discriminate between the two classes with the presence of noise. For all the
+eperiment, we work with zero mean Gaussian noise. \todo{Tomek: could you put a
+justification.} All classifiers are trained with noisy samples. To improve the
+stability of the spherical CNN, we slowly increase the amount of noise added to
+the training data over the iterations. Furthermore in order to avoid
+overfitting, the noise is randomly produced at each iterations. We trained our
+model between $5$ and $40$ epochs depending of the complexity and the size of
+the problem. The testing set was simply used to assess the global performance of
+the network and if the it was overfitting. 
+Training took between $1$ and $10$ hours using a Nvidia 1080 TI.
+
+We compare the spherical CNN with a handcrafted feature classifier. \cite{...}
+\todo{Tomek: we need probably 1 or two other classifiers.} The features are
+constructed using a normalized histogram of the values. We then train a linear
+SVN classifier. We tried different kernels, but they where not leading to better
+results. For a fair comparizon, we increase the amount of training data of the
+SVN classifier until the testing error plateau to fix value.
+
 \subsection{Results}
+\assign{Nathanaël, Tomek}
+
+We present in Figure~\ref{fig:results} the results for 5 different noise levels and $3$ different data sizes.
+The spherical neural network is always significantly better than the hand-crafted classfier.
 
@@
 \includegraphics[width=0.32\textwidth]{figures/result_order4.pdf}
-\caption{Classification errors for the 3 different problems.}
+\caption{Classification errors for the 3 different problems. \nati{TODO: order is not correct} }
 \label{fig:results}
 \end{figure}
-
-\assign{Nathanaël, Tomek}
-
-\begin{itemize}
-	\item With the entire sphere / different PSD (The PSD features + linear SVM is equivalently good)
-	\item Without the entire sphere / same PSD (1 sample: the histogram features + kernelized SVM is equivalently good)
-	\item ??
-\end{itemize}
-
-Figure: Result curves
-
-Figure: Filters 1D and Gnonomic
 
@@
 Show the learned filters and feature maps and try to interpret them.
+
+Figure: Filters 1D and Gnonomic
 
@@
 \label{fig:gaussian_filters_visualization}
-\end{figure}
+\end{figure*}
 

### 2018-05-11 scnn.tex
small corrections

@@
 \begin{itemize}
-	\item Define the gedesic grid?
+	\item Define the spherical grid?
 	\item reference the "cubed sphere"~\cite{ronchi1996cubed}?
@@
 \subsection{Spherical convolutions} 
-The major challenge to generalize CNN to a
-spherical domain is to generalize convolution. In the context of CNN, we found
-two particular approaches to address this issue.
+The major challenge to define Convolution Neural Network (CNN) onto a
+spherical domain is to handle a convolution suitable for this irregular domain. 
+We found two particular approaches to address this issue.
 
@@
 spherical properties of the domain, i.e. the "cubed sphere” sampling is by
-definition adapted to a cube and not to a sphere. \nati{Michael: Under some very
-specific hypothesis, this second approach is a particular case of our method,
-i.e. 1) our method with a stupid sampling, 2) assumption that graph convolution
-on a grid == 2d convolution. Do you think we should mention that? I think we
-should not.}
-
-\todo{Check this unpublished work \cite{khasanova2017graph}}
+definition adapted to a cube and not to a sphere. 
+% \nati{Michael: Under some very
+% specific hypothesis, this second approach is a particular case of our method,
+% i.e. 1) our method with a stupid sampling, 2) assumption that graph convolution
+% on a grid == 2d convolution. Do you think we should mention that? I think we
+% should not.}
 
@@
 structure and is particularly adapted to the HealPix sampling.
+
+We are not the first one to leverage a graph to define a CNN on a sphere.
+\cite{khasanova2017graph} use the same idea to handle omnidirectional images.
+Besides the different application covered by the paper, there are two important
+differences. First the sampling is different as \cite{khasanova2017graph} uses a
+grid. Second, it uses a different graph CNN based on a different parameterization
+of the convolution kernel.
 
@@
 pixels $i$ and $j$. This weighting scheme is important as the distances between
-pixels varries du to the small sampling irregularities. Some of the
+pixels varies due to the small sampling irregularities. Some of the
 irregularities have been highlighted in the graph displayed in
@@
 \caption{
-Top view of a Healpix graph for half the sphere using a nside parameter of $4$.
-Nodes with 7 neighboors are highlighted.
+Top view of a Healpix graph for half the sphere using an nside parameter of $4$.
+Nodes with 7 neighbors are highlighted.
 }
@@
 
-Because of the irregular sampling, there is no obvious way to define convolution
+Because of the irregular sampling, there is no obvious way to define the convolution
 directly from the pixel values. Hence we first define a Fourier transform on the
@@
 that can be used to define the graph Fourier basis. Here $D$ is the diagonal
-matrix where $\D_{ii}=\b{d}_i$. By construction the Laplacian is symetric postive
+matrix where $\D_{ii}=\b{d}_i$. By construction the Laplacian is symetric positive
 semi-definite and hence can be decomposed as $\L=\U \bLambda \U^*$, where $U$ is an
@@
 As shown in Figure~\ref{fig:graph_harmonics}, it turns out that using the graph
-construction described above, the graph Fourier harmonics ressembles the
+construction described above, the graph Fourier harmonics resemble the
 classical spherical harmonics giving us an indication that the graph is able to
@@
 
-The major difference with classical convolution is that the convolution kernel
-$h$ cannot be thought as $n \times n$ pattern, but is a continuous function
-applied to the graph eigenvalues $\bLambda$. For visualization puposes, one can
-look at effect of the convolution on a dirac, i.e. one column of the matrix
-$h(\L)$. \nati{However, due to the non regularity of the graph (i.e. the fact
+The major difference with the classical convolution is that the convolution kernel
+$h$ cannot be thought as a $n \times n$ pattern, but is a continuous function
+applied to the graph eigenvalues $\bLambda$. For visualization purposes, one can
+look at the effect of the convolution on a Kronecker, i.e. one column of the matrix
+$h(\L)$. \nati{However, due to the non-regularity of the graph (i.e. the fact
 that there is not perfect sampling on the sphere), this visualization will
 differ from one node to another. In the specific case of the full sphere, these
-difference are negligible in most of the cases. When considering only subpart of
+differences are negligible in most of the cases. When considering only subpart of
 the sphere, one will observe important border effects.}
@@
 time $t$. In  Figure~\ref{fig:gaussian_filters_visualization} of
-Appendix~\ref{app:filter_visualization}, we show different visualizaton of the
+Appendix~\ref{app:filter_visualization}, we show different visualizations of the
 convolution kernel $K_t$. We also compare the graph convolution with the
@@
 from a true spherical convolution, it can, providing the correct
-parametrization, well approximate it.
+parameterization, well approximate it.
 
@@
 \includegraphics[width=0.95\textwidth]{figures/gaussian_filters_sphere.pdf}
-\caption{Convolution comparizon (Nside=16). 
-Top: Diffusion of a unit of heat for different time $t$ using the graph. 
+\caption{Convolution comparison (Nside=16). 
+Top: Diffusion of a unit of heat for different times $t$ using the graph. 
 Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin). 
@@
 It is another sign that the constructed graph is able to capture the spherical
-structure of the healpix sampling. Furthemore, in some application, where the
-exactitude of the convolution is not requirement, such as de-noising, it means
-that we could use graph convolution instead. Depending on the convolution kernel
+structure of the HealPix sampling. Furthermore, in some application, where the
+exactitude of the convolution is not a requirement, such as de-noising, it means
+that we could use the graph convolution instead. Depending on the convolution kernel
 this may reveal much more efficient. In the case of a neural network, the fact
@@
 \subsection{Coarsening}
-The HealPix sampling present the advantage to have a natural corsening method
-based on its construction. Each nside level divides each pixel into 4 subpixels.
+The HealPix sampling presents the advantage to have a natural coarsening method
+based on its construction. Each Nside level divides each pixel into 4 subpixels.
 We define the pooling process as the inverse operation grouping the 4 subpixels.
@@
 \includegraphics[width=0.45\textwidth]{figures/pooling.pdf}
-\caption{Pooling illustration for 2 levels using some part of the the mollview projection. 
-The final patch represent 1/12 of the sphere.}
+\caption{Pooling illustration for 2 levels using some part of the mollview projection. 
+The final patch represents 1/12 of the sphere.}
 \label{fig:pooling}
@@
 In this section, we demonstrate the usefulness of the spherical neural network
-on a discrimination problem. Our implementation is availlable as small python package at \url{https://our.code.link.com}. 
+on a discrimination problem. Our implementation is available as a small python package at \url{https://our.code.link.com}. 
 Furthermore, all the data to reproduce our experiments are available online.\footnote{\url{https://doi.org/10.5281/zenodo.????} \todo{correct DOI}}
@@
 
-As a preprocssing step, we first remove the mean of each sample and apply a
-spherical gaussian smoothing kernel with a radius of $1$ arcmin.
+As a pre-processing step, we first remove the mean of each sample and we apply a
+spherical Gaussian smoothing kernel with a radius of $1$ arcmin.
 
@@
 As shown in Figure~\ref{fig:subpart_sphere}, we used $o=0,1,2$ as the resulting
-samples are large enough to suffer from the effet of the spherical geometry. We
+samples are large enough to suffer from the effects of the spherical geometry. We
 decided to only report simulation results for this specific setting as spherical
@@
 discriminate between the two classes with the presence of noise. For all the
-eperiment, we work with zero mean Gaussian noise. \todo{Tomek: could you put a
+experiments, we work with zero mean Gaussian noise. \todo{Tomek: could you put a
 justification.} All classifiers are trained with noisy samples. To improve the
@@
 the training data over the iterations. Furthermore in order to avoid
-overfitting, the noise is randomly produced at each iterations. We trained our
-model between $5$ and $40$ epochs depending of the complexity and the size of
+overfitting, the noise is randomly produced at each iteration. We trained our
+model between $5$ and $40$ epochs depending on the complexity and the size of
 the problem. The testing set was simply used to assess the global performance of
-the network and if the it was overfitting. 
+the network and to assess if were overfitting. 
 Training took between $1$ and $10$ hours using a Nvidia 1080 TI.
@@
 We compare the spherical CNN with a handcrafted feature classifier. \cite{...}
-\todo{Tomek: we need probably 1 or two other classifiers.} The features are
+\todo{Tomek: we probably need 1 or two other classifiers.} The features are
 constructed using a normalized histogram of the values. We then train a linear
-SVN classifier. We tried different kernels, but they where not leading to better
-results. For a fair comparizon, we increase the amount of training data of the
+SVN classifier. We tried different kernels, but they were not leading to better
+results. For a fair comparison, we increase the amount of training data of the
 SVN classifier until the testing error plateau to fix value.
@@
 We present in Figure~\ref{fig:results} the results for 5 different noise levels and $3$ different data sizes.
-The spherical neural network is always significantly better than the hand-crafted classfier.
+The spherical neural network is always significantly better than the hand-crafted classifier.
 
@@
 In Figure~\ref{fig:gaussian_filters_visualization}, we present three different
-ways to plot the graph convolution kernel $K_t(x)=e^{-\tau t x}$.  First, it can
-be ploted in the graph spectral domain. In this case, we simply evaluate $K_t$
+ways to plot the graph convolution kernel $K_t(x)=e^{-\tau t x}$.  First, they can
+be plotted in the graph spectral domain. In this case, we simply evaluate $K_t$
 at the graph eigenvalues $\text{diag}(\bLambda)$. Second, we can convolve a

### 2018-05-11 scnn.tex
end of the day

@@
 spherical domain is to handle a convolution suitable for this irregular domain. 
-We found two particular approaches to address this issue.
+They exist three approaches to address this issue.
 
 The first approach, leveraging the continuous spherical convolution, has been
-proposed in~\cite{cohen2017convolutional,cohen2018spherical}. These
-contributions propose to use a convolution that is rotational equivariant on the
+proposed by~\cite{cohen2017convolutional,cohen2018spherical}. The goal of these
+contributions it to use a rotational equivariant convolution on the
 sphere, i.e. a rotation of the input implies the same rotation of the output.
-The convolution is performed by a spherical Fourier transform (i.e. a projection
+The resulting convolution is performed by a spherical Fourier transform (i.e. a projection
 on the spherical harmonics), a  multiplication in the spectral domain and an
-inverse spherical Fourier tranform. Hence the main computational cost of a
+inverse spherical Fourier transform. Hence the main computational cost of a
 convolution comes from the two Fourier transforms. Fortunately, the Fourier
 transform can be accelerated for special samplings set (theoretically including
-HealPix). The main advantage of this approach is that it provides a
+HealPix, \cite{...}). The main advantage of this approach is that it provides a
 mathematically well defined rotational equivariant network. Nevertheless, even

### 2018-05-14 scnn.tex
small changes

@@
 
-In an attempt to get the best of the two approaches, we follow a third
+In an attempt to get the best of the two first approaches, we follow a third
 direction. We use a graph to adapt to the particular structure of the sphere.
@@
 
-As presented in~\cite{cohen2018spherical}, the most mathematical approach to
+As presented by~\cite{cohen2018spherical}, the most mathematical approach to
 extend the convolution on a sphere is to use a spherical Fourier transform. The
@@
 graph signal processing~\cite{shuman2013emerging} to define a spherical
-convolution that can be computed directly in the signal domain.
+convolution that can be computed (and back-propagated) directly in the signal domain.
 
@@
 Because of the irregular sampling, there is no obvious way to define the convolution
-directly from the pixel values. Hence we first define a Fourier transform on the
+directly from the pixel values. Hence we will first make a detour and define a Fourier transform on the
 graph.
@@
 t x}$. Here the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$ that
-correspond to the squared frequencies and hence $K_t$ can be considered a
-Gaussian kernel. In Figure~\ref{fig:gaussian_filters_comparizon} top, we show
+are one generalization of the squared frequencies on the graph. Hence the kernel $K_t$ is also a generalization of the
+Gaussian kernel on the sphere. In Figure~\ref{fig:gaussian_filters_comparizon} top, we show
 the effect of the convolution by diffusing a unit of heat for $\tau=1$ and various 
@@
 
-It is another sign that the constructed graph is able to capture the spherical
+This result is another sign that the constructed graph is able to capture the spherical
 structure of the HealPix sampling. Furthermore, in some application, where the
@@
 discriminate between the two classes with the presence of noise. For all the
-experiments, we work with zero mean Gaussian noise. \todo{Tomek: could you put a
+experiments, we work with centered Gaussian noise. \todo{Tomek: could you put a
 justification.} All classifiers are trained with noisy samples. To improve the
@@
 the training data over the iterations. Furthermore in order to avoid
-overfitting, the noise is randomly produced at each iteration. We trained our
+overfitting, the noise is randomly produced during the training process. We trained our
 model between $5$ and $40$ epochs depending on the complexity and the size of
 the problem. The testing set was simply used to assess the global performance of
-the network and to assess if were overfitting. 
+the network and to assess if it was overfitting. 
 Training took between $1$ and $10$ hours using a Nvidia 1080 TI.
@@
 results. For a fair comparison, we increase the amount of training data of the
-SVN classifier until the testing error plateau to fix value.
+SVN classifier until the testing error plateau to a fix value.
 

### 2018-05-24 scnn.tex
adding refs

@@
 \usepackage{bm}
+\usepackage{aasmacros}
 
@@
 \assign{Tomek}
+
+Cosmological data often comes in a form of spherical sky maps.
+Observables such as the Cosmic Microwave Background (CMB) \citep{planck2015cosmologicalparameters,komatsu2011sevenyear,staggs2018recentdiscoveries}, neutral hydrogen \citep{santos2015cosmologySKA,HI4PI2016fullskyHI}, galaxy clustering \citep{alam2017clusteringgalaxies}, gravitational lensing \citep{troxel2017darkenergy,hildebrandt2017kidscosmological}, and others have been used to constrain cosmological models
+
+Cite the following papers:
+\begin{itemize}
+    \item Healpix paper \citep{gorski2005healpix}
+    \item First DES mass maps \citep{chang2017curvedsky}
+    \item Healpix convolutions with asymetric beams \citep{mitra2011fastpixel}
+    \item Mass mapping on the sphere \citep{wallis2017mappingdark}
+    \item Wavelets on the sphere \citep{leistedt2016wavelet}
+    \item Planck main result \citep{planck2015cosmologicalparameters,komatsu2011sevenyear}
+    \item HI map \citep{HI4PI2016fullskyHI,}
+    \item more radio maps from Adam+Hamsa \citep{santos2015cosmologySKA}
+    \item more astro science on the sphere, what other survey make maps?
+    \item alternative sampling on the sphere \citep{mcewen2011novelsampling} MW sampling
+    \item cite kids tomographic power spectrum \citep{koehlinger2017kidstomographic}
+\end{itemize}
 

### 2018-05-24 scnn.tex
writing intro + refs

@@
 \newcommand{\blambda}{\b{\lambda}}
+\newcommand{\pkg}[1]{\texttt{#1}}
 
@@
 
-Cosmological data often comes in a form of spherical sky maps.
-Observables such as the Cosmic Microwave Background (CMB) \citep{planck2015cosmologicalparameters,komatsu2011sevenyear,staggs2018recentdiscoveries}, neutral hydrogen \citep{santos2015cosmologySKA,HI4PI2016fullskyHI}, galaxy clustering \citep{alam2017clusteringgalaxies}, gravitational lensing \citep{troxel2017darkenergy,hildebrandt2017kidscosmological}, and others have been used to constrain cosmological models
+Cosmological and astrophysical data often comes in a form of spherical sky maps.
+Observables such as the Cosmic Microwave Background (CMB) \citep{planck2015cosmologicalparameters,komatsu2011sevenyear,staggs2018recentdiscoveries}, neutral hydrogen \citep{santos2015cosmologySKA,HI4PI2016fullskyHI}, galaxy clustering \citep{alam2017clusteringgalaxies}, gravitational lensing \citep{troxel2017darkenergy,hildebrandt2017kidscosmological}, and others have been used to constrain cosmological and astrophysical models.
+Deep Learning methods have recently started to gain popularity as an analysis tool in cosmology \citep{schmelze2017cosmologicalmodel,luciesmith2018machinelearning,gupta2018nongaussianinformation,gillet2018deeplearning,hassan2018reionizationmodels,aragoncalvo2018classyfyinglarge,ciuca2017cnnstring}.
+So far these algorithms have been demonstrated on the flat images.
+Analysis of larger survey area in this form requires dividing the data into smaller chunks and projecting them on a flat, 2D surface.
+While this process can work efficiently as already demonstrated, it may be more convenient do work with deep learning directly on the sphere.
+The most commonly used scheme in astrophysics to divide a sphere into pixels is \pkg{Healpix} \citep{gorski2005healpix}, which uses pixels with the same area.
+
+In this work we present an algorithm and software package to implement efficient deep convolutional neural networks on Healpix maps.
 
@@
     \item Mass mapping on the sphere \citep{wallis2017mappingdark}
-    \item Wavelets on the sphere \citep{leistedt2016wavelet}
+    \item Wavelets on the sphere \citep{leistedt2016wavelet} and ball \citep{leistedt2012exactwavelets}
     \item Planck main result \citep{planck2015cosmologicalparameters,komatsu2011sevenyear}

### 2018-05-25 scnn.tex
first pass at intro

--- 2018-05-14 scnn.tex
@@
 	Ideas: Graph Convolutional Networks for efficient spherical ???, Efficient spherical ??? with GCNs and Healpix sampling
+    We make the code publicly available.
 }
@@
 
-a) Cosmology has a lot of spherical data. Our method is simple and easy to use. Moreover, it is based on the widely used healpix sampling.
-b) It is the most efficient spherical convolution\footnote{\todo{provably?
+Cosmological and astrophysical data often comes in a form of spherical sky maps.
+Observables that cover large parts of the sky, such as the Cosmic Microwave Background (CMB) \citep{planck2015cosmologicalparameters,komatsu2011sevenyear,staggs2018recentdiscoveries}, neutral hydrogen \citep{santos2015cosmologySKA,HI4PI2016fullskyHI}, galaxy clustering \citep{alam2017clusteringgalaxies}, gravitational lensing \citep{troxel2017darkenergy,hildebrandt2017kidscosmological}, and others, have been used to constrain cosmological and astrophysical models.
+Deep Learning methods have recently started to gain popularity as an analysis tool in cosmology \citep{schmelze2017cosmologicalmodel,luciesmith2018machinelearning,gupta2018nongaussianinformation,gillet2018deeplearning,hassan2018reionizationmodels,aragoncalvo2018classyfyinglarge,ciuca2017cnnstring}.
+Convolutional Neural Networks (CNNs) are particularly well suited for analysis of astrophysical data due to their ability to capture complicated, non-linear patterns, which are often present in the data.
+
+So far these algorithms have been demonstrated on the flat images.
+Deep learning-based analysis of larger survey area form requires dividing the data into smaller chunks and projecting them on a flat, 2D surface.
+While this process can work efficiently as already demonstrated, it may be more convenient do work with deep learning directly on the sphere.
+The most commonly used scheme in astrophysics to divide a sphere into pixels is Healpix \citep{gorski2005healpix}, which uses isolatitude sampling and pixels with the same area.
+
+In this work we present an algorithm and software package \pkg{SCNN-temp-name}\footnote{github.com/SwissDataScienceCenter/scnn} which implements efficient deep convolutional neural networks on Healpix maps.
+To achieve this, we represent the sphere $S^2$ as a graph of connected pixels, which forms a 2D manifold embedded in 3D space $\mathbb{R}^3$.
+This approach is based on CNN formulations on graphs described by \citet{defferrard2016convolutional} and runs using the \pkg{TensorFlow} \citep{abadi2016tensorflow} engine.
+The flexibility of the graph approach allows for faster analysis when data spans only a part of the sphere.
+It is also possible to use multiple Healpix maps within our framework and use datasets in form of ``shells''.
+These shells can span the radial direction, so that a tomographic analysis can be performed, or different frequencies, in case of data from observations in radio frequencies.
+
+Formulations of deep learning on the sphere have been proposed by ~\citet{cohen2017convolutional,cohen2018spherical}.
+In that method, a different sphere pixelisation scheme is used: the sphere pixels are mapped to flat space (??) and then generalized Fast Fourier Transform (FFT) is used for convolutions.
+Other recently developed sampling methods include \citep{mcewen2011novelsampling}, where exact sampling theorem for equiangular MW sampling was presented.
+In our work we focused on the Healpix sampling, as it is the most commonly used in cosmology.
+It can be, however, extended to other sampling schemes, by straightforward change in definition of the graph.
+
+Another advantage of our method is the speed of the convolution operation.
+It is the most efficient spherical convolution\footnote{\todo{provably?
+cannot be faster than O(n) without approximations, e.g.
+sketching}}, requiring only $O(n)$ operations, where $n$ is the number of points.
+MORE HERE
+
+The method presented here restricts the shape of the filters learned by the network to be radial.
+While this may be a less general design compared to the one used by conventional CNNs on flat images, we found it to still work efficiently for our test cases.
+The layered structure of the network can partially compensate for that.
+Further generalisations to non-radial filters may be possible [cite?], but we leave it to future work.
+
+We give a practical demonstration of the application of our package to cosmological model discrimination using convergence maps, similar to \citep{schmelze2017cosmologicalmodel}.
+In a simplified scenario, we classify convergence maps on parts of a sphere into two cosmological models.
+These models were designed to have the same power spectrum in range $\ell < 1000$.
+We compare the performance of the spherical CNN to a baseline algorithm, a SVM classifier which takes pixel histograms of these maps as input.
+The comparison is made as a function of noise level on convergence maps and area of the sphere used.
+
+The paper is organised as follows.
+In Section \ref{sec:related} we describe existing approaches to convolutions on the sphere, graphs, and manifolds.
+Section \ref{sec:method} we show the way to construct a graph using Healpix sampling and define the convolution operation.
+The comparison between the spherical CNN and the benchmark method using the weak lensing mass map classification is presented in Section \ref{sec:experiments}.
+We conclude in Section \ref{sec:conclusion}.
+% Cite the following papers:
+% \begin{itemize}
+%     \item Healpix paper \citep{gorski2005healpix}
+%     \item First DES mass maps \citep{chang2017curvedsky}
+%     \item Healpix convolutions with asymetric beams \citep{mitra2011fastpixel}
+%     \item Mass mapping on the sphere \citep{wallis2017mappingdark}
+%     \item Wavelets on the sphere \citep{leistedt2016wavelet} and ball \citep{leistedt2012exactwavelets}
+%     \item Planck main result \citep{planck2015cosmologicalparameters,komatsu2011sevenyear}
+%     \item HI map \citep{HI4PI2016fullskyHI,}
+%     \item more radio maps from Adam+Hamsa \citep{santos2015cosmologySKA}
+%     \item more astro science on the sphere, what other survey make maps?
+%     \item alternative sampling on the sphere \citep{mcewen2011novelsampling} MW sampling
+%     \item cite kids tomographic power spectrum \citep{koehlinger2017kidstomographic}
+% \end{itemize}
+
+% a) Cosmology has a lot of spherical data. Our method is simple and easy to use. Moreover, it is based on the widely used healpix sampling.
+% b) It is the most efficient spherical convolution\footnote{\todo{provably?
 cannot be faster than O(n) without approximations, e.g.
@@
 
-\subsection{Potential applications}
-	\assign{Tomek, Nathanaël, Michaël}
+% \subsection{Potential applications}
+% 	\assign{Tomek, Nathanaël, Michaël}
 
-The analysis of spherical cosmological data, such as the cosmic microwave background \cite{...}, as done in \cite{he2018analysis}, is the target application of our method.
+% The analysis of spherical cosmological data, such as the cosmic microwave background \cite{...}, as done in \cite{he2018analysis}, is the target application of our method.
 
-While our method was developed with cosmology in mind, it can easily target any problem where data live on a sphere.
+% While our method was developed with cosmology in mind, it can easily target any problem where data live on a sphere.
 Examples include, but are certainly not limited to, (i) efficient compression and decompression of \ang{360} videos (see \cite{su2017learning}), (ii) \todo{data analysis on planets?
@@
 
-Finally, not that those neural networks are not restricted to the sphere and can be applied to any problem where we have data on a graph, such as social, biological or infrastructure networks [some citations, e.g.
+% Finally, not that those neural networks are not restricted to the sphere and can be applied to any problem where we have data on a graph, such as social, biological or infrastructure networks [some citations, e.g.
 brain Alzeihmer, particle physics, computer graphics].
@@
 
-\todo{
-\subsection{Healpix sampling}
-Should we have this subsection to explain the advantages of Healpix?
-\begin{itemize}
-	\item Define the spherical grid?
-	\item reference the "cubed sphere"~\cite{ronchi1996cubed}?
-\end{itemize}
-}
+% \section{Healpix sampling}
+% Should we have this subsection to explain the advantages of Healpix?
+% \begin{itemize}
+% 	\item Define the spherical grid?
+% 	\item reference the "cubed sphere"~\cite{ronchi1996cubed}?
+% \end{itemize}
 
-\begin{figure*}[!ht]
-\centering
-\includegraphics[width=0.7\textwidth]{figures/healpix-3layers.jpg}
-\caption{3 smaller sclales of the healpix sampling.}
-\label{fig:healpix_sampling}
-\end{figure*}
+% \begin{figure}[!ht]
+% \centering
+% \includegraphics[width=0.45\textwidth]{figures/healpix-3layers.jpg}
+% \caption{3 smaller sclales of the healpix sampling.}
+% \label{fig:healpix_sampling}
+% \end{figure}
 
@@
 \section{Method}
+\label{sec:method}
 % \begin{itemize}
@@
 \section{Experiments}
+\label{sec:experiments}
 
@@
 
-\begin{figure}[!ht]
+\begin{figure*}[!ht]
 \centering
-\includegraphics[width=0.45\textwidth]{figures/smooth_map_class_1.pdf}
-\includegraphics[width=0.45\textwidth]{figures/smooth_map_class_2.pdf}
+\includegraphics[width=0.95\textwidth]{figures/smooth_map_class_1.pdf}
+\includegraphics[width=0.95\textwidth]{figures/smooth_map_class_2.pdf}
 \caption{One sample of each class.}
 \label{fig:map_sample}
-\end{figure}
+\end{figure*}
 
@@
 \label{fig:results}
-\end{figure}
+\end{figure*}
 
@@
 \section{Conclusion}
+\label{sec:conclusion}
 \assign{Nathanaël, Tomek, Michaël}

### 2018-05-25 scnn.tex
starting to work on the data section

@@
 The major challenge to define Convolution Neural Network (CNN) onto a
-spherical domain is to handle a convolution suitable for this irregular domain.
-They exist three approaches to address this issue.
+spherical domain is to handle a convolution that is suitable for this irregular sampling domain.
+Three approaches exist to address this issue.
 
@@
 differences. First the sampling is different as \cite{khasanova2017graph} uses a
-grid. Second, it uses a different graph CNN based on a different parameterization
+grid. Second, it uses a different graph CNN based on a different parametrisation
 of the convolution kernel.
@@
 % 4) Describe the result
-In this section, we demonstrate the usefulness of the spherical neural network
-on a discrimination problem. Our implementation is available as a small python package at \url{https://our.code.link.com}.
-Furthermore, all the data to reproduce our experiments are available online.\footnote{\url{https://doi.org/10.5281/zenodo.????} \todo{correct DOI}}
+In this section, we demonstrate the performance of the spherical neural network on a discrimination problem.
+Our implementation is available as a small python package\url{https://our.code.link.com}.
+Furthermore, all the data to reproduce our experiments are available online.\footnote{\url{https://doi.org/10.5281/zenodo.????} \todo{correct DOI}}.
+
+In our experiment we classify convergence maps, similar to those created with gravitational lensing technique \citep{chang2017curvedsky}.
+We compare the performance of the spherical CNN to a simple benchmark algorithm.
+This algorithm is based on classification of histogram of pixels in the maps.
+We use an SVM to perform that task.
+The benchmark method uses the information about the distribution of pixels, but does not include any spatial information.
+The CNN can exploit the spatial information.
+The performance is assessed by measuring the classification error on the test set.
+
+Convergence maps represent the dimensionless distribution of over- and underdensities of mass in the universe, projected on the sky plane.
+The 3D structures are projected using a geometric kernel, value of which depends on the radial distance.
+In gravitational lensing, this kernel is dependent on the radial distances between the observer, the mass plane and the plane of source galaxies \citep[see][for review of gravitational lensing]{bartelman2010gravitationallensing}.
+The redshifts of the sources was set to $z=1$.
+
+We make full sky N-body simulations for two parameter set for $\Lambda \rm{CDM} $ cosmological model: model 1 ($\Omega_m=0.31, \sigma_8=0.82$) and model 2 ($\Omega_m=0.26, \sigma_8=0.91$), where $\Omega_m$ is the matter density in the universe and $\sigma_8$ is the normalisation of the matter power spectrum.
+Other parameter parameters were set to $h=0.7$ (MORE PARAMS HERE - CHECK WITH RAPHAEL).
+These parameters were chosen to have the same spherical harmonic power spectrum for $\ell<1000$.
+That means that it is not possible to distinguish between these cosmological models using these maps if the this range of scales is used.
+We found that for $\ell>1000$ the differences in power spectrum is $~5\%$.
+To remove this information, we additionally smooth the spherical maps with a Gaussian kernel.
 
 \subsection{Data}
-\assign{Tomek}
+\label{sec:data}
+
+The simulations are created using the fast lightcone method described in \citep{sgier2018fastgeneration}.
+However, we use only a single simulation box, as opposed to two used in \citep{sgier2018fastgeneration}, as we use source galaxies at lower redshift of $z=1$, instead of $z=1.5$.
+As a simulator we use \pkg{L-PICOLA} \citep{howlett2015lpicola}, a fast and approximate code for N-body simulations.
+For each class, we generate 30 simulations.
+In the experiment we use data on a parts of the sphere, and we check the performance as a function of the area used.
+We also test the performance as a function of noise level of the pixels.
+
+% sim1: planck
+% omega_m=0.31, pk_norm=0.82, h=0.7
+
+% sim2: alternative model
+% omega_m=0.26, sigma_8=0.91, h=0.7
 

### 2018-05-25 scnn.tex
writing data section

@@
 The simulations are created using the fast lightcone method described in \citep{sgier2018fastgeneration}.
-However, we use only a single simulation box, as opposed to two used in \citep{sgier2018fastgeneration}, as we use source galaxies at lower redshift of $z=1$, instead of $z=1.5$.
+However, we use only a single simulation box, as opposed to two used in that work, as we use source galaxies at lower redshift of $z=1$, instead of $z=1.5$.
 As a simulator we use \pkg{L-PICOLA} \citep{howlett2015lpicola}, a fast and approximate code for N-body simulations.
@@
 
-% sim1: planck
-% omega_m=0.31, pk_norm=0.82, h=0.7
-
-% sim2: alternative model
-% omega_m=0.26, sigma_8=0.91, h=0.7
-
-Our data comes from a simulation with software ??? using the following parameters ???.
-
-As a pre-processing step, we first remove the mean of each sample and we apply a
-spherical Gaussian smoothing kernel with a radius of $1$ arcmin.
-
-We made 30 simulations for each class. Out of the 60 simulations, 20 are kept
-for the test set. The training and validation set are created later on.
+As a pre-processing step, we first remove the mean of each sample and we apply a spherical Gaussian smoothing kernel with a radius of $1$ arcmin.
+Out of the 60 simulations, 20 are kept for the test set.
+% The training and validation set are created later on.
+Figure \ref{fig:map_sample} shows the full sky simulations and a zoom region for model 1 (top) and model 2 (bottom).
+Initial conditions for these simulations were the same, so the differences in structures can only be attributed to different cosmological parameters used to evolve the particle distribution.
 
@@
 \includegraphics[width=0.95\textwidth]{figures/smooth_map_class_2.pdf}
-\caption{One sample of each class.}
+\caption{Example maps from two classes. Top: model 1 ($\Omega_m=0.31, \sigma_8=0.82$). Bottom: model 2 ($\Omega_m=0.26, \sigma_8=0.91$).
+The initial conditions for these simulations were the same, so differences arise only due to different cosmological parameters.}
 \label{fig:map_sample}

### 2018-05-25 scnn.tex
abstract

@@
 
+Convolutional Neural Networks (CNNs) are becoming an important analysis tool in cosmology and astrophysics.
+In many applications, the data comes in a form of spherical maps.
+A popular format for these maps is Healpix, which uses equal-area, isolatitude sampling.
+We present a CNNs for analysis of full- and partial sky Healpix maps, which we call HealpixCNN (???).
+This approach is based on representing a sphere as a graph of connected nodes.
+We describe a convolution operation defined on that graph.
+HealpixCNN (???) uses Tensorflow as the underlying engine and can utilise most of it functionalities.
+Architectures can be designed in a similar way as standard CNNs used for image analysis.
+We find that the graph-based convolution is very efficient (MORE HERE)..
+The filters learned by the HealpixCNN are restricted to being radial.
+We demonstrate the method on a simple classification problem of mass maps from two cosmological models.
+We compare the performance to a simple benchmark classifier, which uses histograms of map pixel values.
+HealpixCNN achieves much better testing accuracy than the benchmark approach.
+We make the code and examples available to the public.
+
 	\todo{(Michaël) I would not invent a new term, SCNN, but rather say that convolutional neural networks on graphs (or GCNs) can be efficiently applied to (spherical?) cosmological applications.
@@
     We make the code publicly available.
+    \\
+    \todo{(Tomek) How about HealpixCNN? Or HealpixNet? Or HealNet?}
+
 }

### 2018-05-28 scnn.tex
added TODO at the beginning

@@
 
-\title{Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications}
+\title{HealpixNet: Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications}
 
@@
 %% \linenumbers
+
+\section{TODO list}
+\begin{itemize}
+    \item Michael, do you agree with the title HealpixNet
+    \item
+\end{itemize}
 
@@
 \subsection{Convolutions on manifolds}
+\todo{TK and NP: maybe we just describe convolutions on sphere and graph}
 
@@
 \subsection{Convolutions on point clouds?}
+\todo{TK and NP: maybe we just describe convolutions on sphere and graph}
 
@@
 
-We compare the spherical CNN with a handcrafted feature classifier. \cite{...}
+We compare the spherical CNN with a handcrafted feature classifier. CITE \cite{...}
 \todo{Tomek: we probably need 1 or two other classifiers.} The features are
@@
 Show the learned filters and feature maps and try to interpret them.
+\todo{\\ TK and NP: Figure of filters from the mass map clasification}
 

### 2018-05-28 scnn.tex
todo
added new todos

@@
     \item Michael, do you agree with the title HealpixNet
-    \item
+    \item Emphaise the novelty of using it on Helapix in abstract, into and rest of the paper
+    \item Finish section on Convolutions on graphs
+    \item Plot of filters from Mass maps
+    \item check the power spectrum after smoothing
+    \item upgrade the plot of pooling
+    \item new plot for network structure (teaser plot)
+    \item add info on comparison with histogram, so that it's just a demonstration
+    \item Figure 1 to be round
+    \item finish section on Efficient convolutions
+    \item conclusions
+    \item (done!) results
+    \item Results figure, add sigma8
+    \item possibly move the eigen decomposition and heat into appendix + add discussion
 \end{itemize}
@@
 
+\citep{patton2017cosmologicalconstraints}
+
 \subsection{Interpretation}

### 2018-06-19 scnn.tex
small text from the meeting
small update in plots

--- 2018-05-28 scnn.tex
@@
     \item Michael, do you agree with the title HealpixNet
-    \item
+    \item Emphaise the novelty of using it on Helapix in abstract, into and rest of the paper
+    \item Finish section on Convolutions on graphs (Michael - Nathanael)
+    \item Plot of the new filters from Mass maps (Michael)
+    \item (done!, plot to be added) check the power spectrum after smoothing
+    \item upgrade the plot of pooling (Nathanael)
+    \item new plot for network structure (teaser plot) (Michael)
+    \item add info on comparison with histogram, so that it's just a demonstration
+    \item (done!) Figure 1 to be round
+    \item finish section on Efficient convolutions (Nathanael)
+    \item conclusions
+    \item (done!) new simulations with 3 arcmin smoothing
+    \item (done!) simulation with cross-validation for the histogram
+    \item (Almost done!) Update result section according to the new simulations...
+    \item (Almost done!) simulation PSD
+    \item (done!) Results figure, add sigma8
+    \item possibly move the eigen decomposition and heat into appendix + add discussion (Nathanael)
 \end{itemize}
@@
 
+\begin{itemize}
+	\item Spherical CNN has the advantage to have some geometry information => one of the reason better than histogram
+	\item PSD...
+\end{itemize}
+
+\citep{patton2017cosmologicalconstraints}
+
 \subsection{Interpretation}

### 2018-06-20 scnn.tex
update pooling figure
update simulation results

@@
     \item (done!, plot to be added) check the power spectrum after smoothing
-    \item upgrade the plot of pooling (Nathanael)
+    \item (done!) upgrade the plot of pooling (Nathanael)
     \item new plot for network structure (teaser plot) (Michael)
@@
     \item (done!) Figure 1 to be round
-    \item finish section on Efficient convolutions (Nathanael)
+    \item finish section on Efficient convolutions (Michael)
     \item conclusions
@@
     \item (done!) simulation with cross-validation for the histogram
-    \item (Almost done!) Update result section according to the new simulations...
-    \item (Almost done!) simulation PSD
+    \item (done!) Update result section according to the new simulations...
+    \item (done!) simulation PSD
     \item (done!) Results figure, add sigma8

### 2018-06-20 scnn.tex
update simulation results
add new figures
lunch commit

@@
     \item (done!) simulation with cross-validation for the histogram
-    \item (done!) Update result section according to the new simulations...
+    \item Update result section according to the new simulations...
     \item (done!) simulation PSD
@@
 %\subsection{Motivation}
-\assign{Tomek}
 
@@
 The first approach, leveraging the continuous spherical convolution, has been
-proposed by~\cite{cohen2017convolutional,cohen2018spherical}. The goal of these
-contributions it to use a rotational equivariant convolution on the
+proposed by~\cite{cohen2017convolutional,cohen2018spherical}. The goal of
+these contributions it to use a rotational equivariant convolution on the
 sphere, i.e. a rotation of the input implies the same rotation of the output.
-The resulting convolution is performed by a spherical Fourier transform (i.e. a projection
-on the spherical harmonics), a  multiplication in the spectral domain and an
-inverse spherical Fourier transform. Hence the main computational cost of a
-convolution comes from the two Fourier transforms. Fortunately, the Fourier
-transform can be accelerated for special samplings set (theoretically including
-HealPix, \cite{...}). The main advantage of this approach is that it provides a
-mathematically well defined rotational equivariant network. Nevertheless, even
-with these Fourier transform acceleration, the convolutions remain expensive in
-comparison to a traditional 2-dimensional convolution, limiting the practical use of this
-approach. While a comparison is theoretically possible, the experiments
+The resulting convolution is performed by a spherical Fourier transform (i.e.
+a projection on the spherical harmonics), a  multiplication in the spectral
+domain and an inverse spherical Fourier transform. Hence the main
+computational cost of a convolution comes from the two Fourier transforms.
+Fortunately, the Fourier transform can be accelerated for special samplings
+set (theoretically including HealPix, \cite{...}). The main advantage of this
+approach is that it provides a mathematically well defined rotational
+equivariant network. Nevertheless, even with these Fourier transform
+acceleration, the convolutions remain expensive in comparison to a traditional
+2-dimensional convolution, limiting the practical use of this approach. While
+a comparison is theoretically possible, the experiments
 of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and
 do not provide any code for the Healpix one. Hence, a practical comparison is
-not possible.
+not possible. We also note that this approach cannot be trivially accelerated
+if only one part of the sphere is used. This is impractical in the field of
+cosmology as the data often observed only on a subpart of the sphere.
 
@@
 In our experiment we classify convergence maps, similar to those created with gravitational lensing technique \citep{chang2017curvedsky}.
-We compare the performance of the spherical CNN to a simple benchmark algorithm.
-This algorithm is based on classification of histogram of pixels in the maps.
-We use an SVM to perform that task.
-The benchmark method uses the information about the distribution of pixels, but does not include any spatial information.
-The CNN can exploit the spatial information.
-The performance is assessed by measuring the classification error on the test set.
+
+\subsection{Data}
+\label{sec:data}
 
@@
 We found that for $\ell>1000$ the differences in power spectrum is $~5\%$.
-To remove this information, we additionally smooth the spherical maps with a Gaussian kernel.
-
-\subsection{Data}
-\label{sec:data}
+To remove this information, we additionally smooth the spherical maps with a Gaussian kernel of radius $3$ arcmins. The resulting PSD are displayed in Figure~\ref{fig:psd_sigma3}.
 
@@
 \caption{Example maps from two classes. Top: model 1 ($\Omega_m=0.31, \sigma_8=0.82$). Bottom: model 2 ($\Omega_m=0.26, \sigma_8=0.91$).
-The initial conditions for these simulations were the same, so differences arise only due to different cosmological parameters.}
+The initial conditions for these simulations were the same, so differences arise only due to different cosmological parameters. \nati{Tomek: Is this correct?}}
 \label{fig:map_sample}
@@
 
-Leveraging the properties of the HealPix sampling, we can split each simulation
-into $12*4^o$ ($o=0,1,2,\dots$) samples that span a smaller part of the sphere.
-As shown in Figure~\ref{fig:subpart_sphere}, we used $o=0,1,2$ as the resulting
+Leveraging the properties of the HealPix sampling, we can split each maps
+into $12*o^2$ ($o=1,2,4,\dots$) samples that span a smaller part of the sphere. 
+The area of the pixels for an Nside of $o$ correspond to the different split of the data.
+As shown in Figure~\ref{fig:subpart_sphere}, we used $o=1,2,4$ as the resulting
 samples are large enough to suffer from the effects of the spherical geometry. We
@@
 \includegraphics[width=0.45\textwidth]{figures/part_sphere.pdf}
-\caption{3 subparts of the sphere with different sizes. Blue: $o=0$. Green: order $o=1$. Yellow: order $o=2$.}
+\caption{3 subparts of the sphere with different sizes. Blue: $o=1$. Green: order $o=2$. Yellow: order $o=4$.}
 \label{fig:subpart_sphere}
@@
 
-We would like to build a robust classifier, i.e. an automatic way to
-discriminate between the two classes with the presence of noise. For all the
+The goal is build a robust classifier, i.e. an automatic way to
+discriminate between the two classes in the presence of noise. For all the
 experiments, we work with centered Gaussian noise. \todo{Tomek: could you put a
@@
 overfitting, the noise is randomly produced during the training process. We trained our
-model between $5$ and $40$ epochs depending on the complexity and the size of
+model between $50$ and $200$ epochs depending on the complexity and the size of
 the problem. The testing set was simply used to assess the global performance of
 the network and to assess if it was overfitting.
-Training took between $1$ and $10$ hours using a Nvidia 1080 TI.
+Training took less that a day for each model using a Nvidia 1080 TI.
+
+We compare the performance of the spherical CNN to two simple benchmark algorithms.
+The two baselines are based on building features with a) the Power Spectral Densities or b) the histogram of pixels in the maps.
+Those features are then classified use a Support Vector Machine (SVM) with a linear kernel. Other kernels did provide better result while having worse scaling properties.
+For fairness, we augmented the dataset of the baseline in a similar way as for the network, i.e:
+
+The histogram features contains information about the distribution of pixels, but does not include any spatial information.
+Both the PSD features and the CNN can exploit the spatial information.
+
+For The maps
+The performance is assessed by measuring the classification error on a test set.
 
 We compare the spherical CNN with a handcrafted feature classifier. CITE \cite{...}
-\todo{Tomek: we probably need 1 or two other classifiers.} The features are
+The features are
 constructed using a normalized histogram of the values. We then train a linear
@@
 
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.45\textwidth]{figures/psd_sigma3.pdf}
+\caption{Power spectrum densities of the noiseless maps. The maps have be smoothed with a Gaussian kernel of radius $3$ arcmins in the preprocessing step.}
+\label{fig:psd_sigma3}
+\end{figure}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.45\textwidth]{figures/hist_error_order4_noise1_5.pdf}
+\caption{TODO}
+\label{fig:hist_error_evolution}
+\end{figure}
+
 %% If you have bibdatabase file and want bibtex to generate the

### 2018-06-20 scnn.tex
going further

@@
 
-We compare the performance of the spherical CNN to two simple benchmark algorithms.
-The two baselines are based on building features with a) the Power Spectral Densities or b) the histogram of pixels in the maps.
-Those features are then classified use a Support Vector Machine (SVM) with a linear kernel. Other kernels did provide better result while having worse scaling properties.
-For fairness, we augmented the dataset of the baseline in a similar way as for the network, i.e:
+We compare the performance of the spherical CNN to two simple benchmark
+algorithms. The two baselines are based on building features with a) the Power
+Spectral Densities or b) the histogram of pixels in the maps. CITE~\cite{...}
+After a normalization, those features are then classified use a Support Vector
+Machine (SVM) with a linear kernel. Other kernels did provide better result
+while having worse scaling properties. For fairness, we augmented the dataset
+of the baseline algorithm in a similar way as for the network, i.e, with
+created an "unlimited" number of samples by adding new random realizations of
+the noise. We stop adding new samples in the classifier once the validation
+error converge to a values. This process is depicted in
+Figure~\ref{fig:hist_error_evolution}.
 
-The histogram features contains information about the distribution of pixels, but does not include any spatial information.
-Both the PSD features and the CNN can exploit the spatial information.
-
-For The maps
-The performance is assessed by measuring the classification error on a test set.
-
-We compare the spherical CNN with a handcrafted feature classifier. CITE \cite{...}
-The features are
-constructed using a normalized histogram of the values. We then train a linear
-SVN classifier. We tried different kernels, but they were not leading to better
-results. For a fair comparison, we increase the amount of training data of the
-SVN classifier until the testing error plateau to a fix value.
+The maps are separated into a training and a testing set. The performance is
+assessed by measuring the classification error on a test set. Once the
+training maps are sliced into samples, we split them into a training samples
+and validation samples. The validation samples is used to tune the
+regularization parameter of the SVM using a standard cross-validation
+technique\footnote{We also give a small advantage to the SVM classifiers by
+using cross-validation on the testing set.}.
 
@@
 The spherical neural network is always significantly better than the hand-crafted classifier.
+
+The histogram features contains information about the distribution of pixels, but does not include any spatial information.
+In contrast, both the PSD features and the CNN can exploit the spatial information.
 

### 2018-06-20 scnn.tex
done for today

@@
 Convolutional Neural Networks (CNNs) are becoming an important analysis tool in cosmology and astrophysics.
-In many applications, the data comes in a form of spherical maps.
-A popular format for these maps is Healpix, which uses equal-area, isolatitude sampling.
-We present a CNNs for analysis of full- and partial sky Healpix maps, which we call HealpixCNN (???).
-This approach is based on representing a sphere as a graph of connected nodes.
+While CNN apply to images, in many applications, the data comes in a form of spherical maps with the popular Healpix format, which uses equal-area, isolatitude sampling.
+Hence, we present a spherical CNNs for analysis of full- and partial sky Healpix maps, which we call HealpixCNN (???) \nati{HealpixNet??? To be decided}.
+Our approach is based on representing a sphere as a graph of connected nodes.
 We describe a convolution operation defined on that graph.
-HealpixCNN (???) uses Tensorflow as the underlying engine and can utilise most of it functionalities.
+HealpixCNN (???) uses Tensorflow as the underlying engine and can utilize most of it functionalities.
 Architectures can be designed in a similar way as standard CNNs used for image analysis.
@@
 %% keywords here, in the form: keyword \sep keyword
-
-%% PACS codes here, in the form: \PACS code \sep code
-
-%% MSC codes here, in the form: \MSC code \sep code
-%% or \MSC[2008] code \sep code (2000 is the default)
+Spherical Convolutional Neural Network \sep SCNN \sep Healpix CNN \sep Graph CNN
 
@@
     \item Michael, do you agree with the title HealpixNet
-    \item Emphaise the novelty of using it on Helapix in abstract, into and rest of the paper
+    \item Emphasize the novelty of using it on Helapix in abstract, into and rest of the paper
     \item Finish section on Convolutions on graphs (Michael - Nathanael)
@@
     \item (done!) simulation with cross-validation for the histogram
-    \item Update result section according to the new simulations...
+    \item (done!) Update result section according to the new simulations...
     \item (done!) simulation PSD
     \item (done!) Results figure, add sigma8
-    \item possibly move the eigen decomposition and heat into appendix + add discussion (Nathanael)
+    \item (more or less done!) possibly move the eigen decomposition and heat into appendix + add discussion (Nathanael I am not sure about the heat diffusion example...)
 \end{itemize}
@@
 
-Formulations of deep learning on the sphere have been proposed by ~\citet{cohen2017convolutional,cohen2018spherical}.
-In that method, a different sphere pixelisation scheme is used: the sphere pixels are mapped to flat space (??) and then generalized Fast Fourier Transform (FFT) is used for convolutions.
-Other recently developed sampling methods include \citep{mcewen2011novelsampling}, where exact sampling theorem for equiangular MW sampling was presented.
-In our work we focused on the Healpix sampling, as it is the most commonly used in cosmology.
-It can be, however, extended to other sampling schemes, by straightforward change in definition of the graph.
+Different formulations of deep learning on the sphere have been proposed in~\citet{cohen2017convolutional,cohen2018spherical,boomsma2017spherical,khasanova2017graph}.
+In all of these methods, a different sphere pixelisation scheme is used, making them unsuitable for most cosmological application. 
+Hence, our work we focused on the Healpix sampling, as it is the most commonly used in cosmology.
+It can be, however, extended to other sampling schemes, by straightforward change in definition of the graph. These approach are discussed in Section~\ref{sec:spherical_conv}.
+%\nati{I am not sure this goes there...} Other recently developed sampling methods include \citep{mcewen2011novelsampling}, where exact sampling theorem for equiangular MW sampling was presented.
 
-Another advantage of our method is the speed of the convolution operation.
-It is the most efficient spherical convolution\footnote{\todo{provably?
-cannot be faster than O(n) without approximations, e.g.
-sketching}}, requiring only $O(n)$ operations, where $n$ is the number of points.
+An important advantage of our method is the speed of its convolution operation as it is of order $\mathcal{O}(n)$, where $n$ is the number of points, which is the lowest possible complexity for convolution without approximations, e.g.
+sketching.
+While our implementation is slower than traditional convolution on a 2 dimensional image, it remain in the same order of magnitude.
 MORE HERE
 
-The method presented here restricts the shape of the filters learned by the network to be radial.
+Because of the spherical domain, the method presented here restricts the shape of the filters learned by the network to be radial.
 While this may be a less general design compared to the one used by conventional CNNs on flat images, we found it to still work efficiently for our test cases.
 The layered structure of the network can partially compensate for that.
-Further generalisations to non-radial filters may be possible [cite?], but we leave it to future work.
+Further generalizations to non-radial filters may be possible [cite?], but we leave it to future work.
 
@@
 These models were designed to have the same power spectrum in range $\ell < 1000$.
-We compare the performance of the spherical CNN to a baseline algorithm, a SVM classifier which takes pixel histograms of these maps as input.
+We compare the performance of the spherical CNN to a baseline algorithm, an SVM classifier which takes pixel histograms or Power Spectrum Densities (PSD) of these maps as input.
 The comparison is made as a function of noise level on convergence maps and area of the sphere used.
@@
 The paper is organised as follows.
-In Section \ref{sec:related} we describe existing approaches to convolutions on the sphere, graphs, and manifolds.
-Section \ref{sec:method} we show the way to construct a graph using Healpix sampling and define the convolution operation.
-The comparison between the spherical CNN and the benchmark method using the weak lensing mass map classification is presented in Section \ref{sec:experiments}.
-We conclude in Section \ref{sec:conclusion}.
+In Section~\ref{sec:related}, we describe existing approaches to convolutions on the sphere, graphs, and manifolds.
+In Section~\ref{sec:method}, we show the way to construct a graph using Healpix sampling and define the convolution operation.
+The comparison between the spherical CNN and the benchmark method using the weak lensing mass map classification is presented in Section~\ref{sec:experiments}.
+We conclude in Section~\ref{sec:conclusion}.
+
 % Cite the following papers:
@@
 
-% a) Cosmology has a lot of spherical data. Our method is simple and easy to use. Moreover, it is based on the widely used healpix sampling.
-% b) It is the most efficient spherical convolution\footnote{\todo{provably?
-cannot be faster than O(n) without approximations, e.g.
-sketching}}, requiring only $O(n)$ operations, where $n$ is the number of points.
-
 % \subsection{Potential applications}
@@
 
-% \section{Healpix sampling}
-% Should we have this subsection to explain the advantages of Healpix?
+% About the the different sphere sampling.
 % \begin{itemize}
@@
 
-% \begin{figure}[!ht]
-% \centering
-% \includegraphics[width=0.45\textwidth]{figures/healpix-3layers.jpg}
-% \caption{3 smaller sclales of the healpix sampling.}
-% \label{fig:healpix_sampling}
-% \end{figure}
-
 \section{Related work}
@@
 \subsection{Spherical convolutions}
+\label{sec:spherical_conv}
 The major challenge to define Convolution Neural Network (CNN) onto a
@@
 Fortunately, the Fourier transform can be accelerated for special samplings
-set (theoretically including HealPix, \cite{...}). The main advantage of this
+set (theoretically including HealPix, \cite{mohlenkamp1999fast,rokhlin2006fast}). 
+The main advantage of this
 approach is that it provides a mathematically well defined rotational
@@
 approach is based on the traditional 2-dimensional convolution, it is very likely to be the
-most efficient one. However, it suffers that it can only be used using very
+most computationally efficient one. However, it suffers that it can only be used using very
 specific grid sampling sets which are NOT including HealPix. Furthermore, the
@@
 Besides the different application covered by the paper, there are two important
-differences. First the sampling is different as \cite{khasanova2017graph} uses a
-grid. Second, it uses a different graph CNN based on a different parametrisation
+differences. First the sampling is different as~\cite{khasanova2017graph} uses a
+grid. Second, it uses a different graph CNN based on a different parametrization
 of the convolution kernel.
+
+\todo{Cool to have a global illustration of the network (CNN like)}
 
@@
 
-\todo{Cool to have a global illustration of the network (CNN like)}
-
+\todo{Maybe we just describe convolutions on sphere and graph, i.e: do we really need this two subsections? Maybe simply merge them?}
 \subsection{Convolutions on manifolds}
-\todo{TK and NP: maybe we just describe convolutions on sphere and graph}
 
@@
 \subsection{Convolutions on point clouds?}
-\todo{TK and NP: maybe we just describe convolutions on sphere and graph}
 
@@
 \vspace{-0.5cm}
-\includegraphics[width=0.45\textwidth]{figures/half_graph_4.pdf}
+\includegraphics[width=0.35\textwidth]{figures/half_graph_4.pdf}
 \vspace{-0.5cm}
@@
 Top view of a Healpix graph for half the sphere using an nside parameter of $4$.
-Nodes with 7 neighbors are highlighted.
+Nodes with 7 neighbors are highlighted. \label{fig:healpix_graph_4}
 }
-\label{fig:healpix_graph_4}
+
 \end{figure}
@@
 
-\begin{figure*}[!ht]
-\centering
-\includegraphics[width=0.95\textwidth]{figures/eigenvectors.pdf}
-\caption{12 first graph Fourier eigenvectors.}
-\label{fig:graph_harmonics}
-\end{figure*}
-
 As shown in Figure~\ref{fig:graph_harmonics}, it turns out that using the graph
@@
 classical spherical harmonics giving us an indication that the graph is able to
-capture the spherical properties of the HealPix sampling.
+capture the spherical properties of the HealPix sampling. This topic is further discusses in Appendix~\ref{sec:spherical_harmonics}.
 
@@
 look at the effect of the convolution on a Kronecker, i.e. one column of the matrix
-$h(\L)$. \nati{However, due to the non-regularity of the graph (i.e. the fact
-that there is not perfect sampling on the sphere), this visualization will
+$h(\L)$. 
+Due to the non-regularity of the graph (i.e. the fact
+that there is not perfect sampling on the sphere), the convolution effect will slightly
 differ from one node to another. In the specific case of the full sphere, these
-differences are negligible in most of the cases. When considering only subpart of
-the sphere, one will observe important border effects.}
+differences are negligible in most of the cases. However, when considering only subpart of
+the sphere, one can observe important border effects.
 
-\paragraph{Example: heat diffusion}
+\paragraph{Example:}
 Let us consider the heat diffusion problem
@@
 
+\section{Spherical harmonics VS graph Fourier eigenvectors}
+Figure~\ref{fig:graph_harmonics} displays the first 16 eigenvectors of the
+graph Fourier basis used for the convolution. While their is a clear
+resemblance with the spherical harmonic, the small irregularities in the
+sampling (see~\ref{fig:healpix_graph_4}) have two important effects on the
+graph Fourier eigenvectors.  First, some graph eigenvectors will be
+localized~\cite{perraudin2018global}, i.e: they will span only a small subpart
+of the sphere.  Second, as Nside increase toward infinity and hence the number
+of pixel $n\rightarrow \infty$, we are still unsure if the graph eigenvectors
+converge toward the spherical harmonics. We believe that it might be the case
+for a different graph construction (fully connected) and that a proof could be
+built on top of the work of~\cite{belkin2007convergence}. This is obviously
+out of the scope of this contribution.
+
+\label{sec:spherical_harmonics}
+\begin{figure*}[!ht]
+\centering
+\includegraphics[width=0.95\textwidth]{figures/eigenvectors.pdf}
+\caption{12 first graph Fourier eigenvectors.}
+\label{fig:graph_harmonics}
+\end{figure*}
+
 \section{Filter visualization}

### 2018-06-21 scnn.tex
abstract

@@
 
-\title{HealpixNet: Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications}
+\title{HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications}
+% \title{HealpixNet: Efficient spherical Convolutional Neural Network with graphs and Healpix sampling for cosmological applications}
+%\title{HealpixNet: Graph Convolutional Neural Network for efficient spherical convolutions on Healpix sampling for cosmological applications}
+% Graph Convolutional Networks for efficient spherical ???
+% Efficient spherical ??? with GCNs and Healpix sampling
+% (Tomek) How about HealpixCNN? Or HealpixNet? Or HealNet?}
+% spherical convolutions with graphs
 
@@
 \begin{abstract}
-%% Text of abstract
 
-Convolutional Neural Networks (CNNs) are becoming an important analysis tool in cosmology and astrophysics.
-While CNN apply to images, in many applications, the data comes in a form of spherical maps with the popular Healpix format, which uses equal-area, isolatitude sampling.
-Hence, we present a spherical CNNs for analysis of full- and partial sky Healpix maps, which we call HealpixCNN (???) \nati{HealpixNet??? To be decided}.
-Our approach is based on representing a sphere as a graph of connected nodes.
-We describe a convolution operation defined on that graph.
-HealpixCNN (???) uses Tensorflow as the underlying engine and can utilize most of it functionalities.
-Architectures can be designed in a similar way as standard CNNs used for image analysis.
-We find that the graph-based convolution is very efficient (MORE HERE)..
-The filters learned by the HealpixCNN are restricted to being radial.
-We demonstrate the method on a simple classification problem of mass maps from two cosmological models.
-We compare the performance to a simple benchmark classifier, which uses histograms of map pixel values.
-HealpixCNN achieves much better testing accuracy than the benchmark approach.
-We make the code and examples available to the public.
+%Convolutional Neural Networks (CNNs) are becoming an important analysis tool in cosmology and astrophysics.
+% Michaël: useful info? To me this is not an argument for our approach. Maybe we have to expand it?
 
-	\todo{(Michaël) I would not invent a new term, SCNN, but rather say that convolutional neural networks on graphs (or GCNs) can be efficiently applied to (spherical?) cosmological applications.
-	Arguments: the method is not new and hence don't deserve a new name. Emphasize that it is generic to the data structure, and that the sphere is simply a particular graph.
-	Ideas: Graph Convolutional Networks for efficient spherical ???, Efficient spherical ??? with GCNs and Healpix sampling
-    We make the code publicly available.
-    \\
-    \todo{(Tomek) How about HealpixCNN? Or HealpixNet? Or HealNet?}
+% Architectures are then designed similarly to the classical CNNs used for image analysis.
+% HealpixCNN (???) uses Tensorflow as the underlying engine and can utilize most of it functionalities.
+% Michaël: not relevant for the abstract in my opinion
 
-}
-
+Convolutional Neural Networks (CNNs) are now a cornerstone of the Deep Learning toolbox and have led to many breakthroughs in Artificial Intelligence.
+Despite their successes, they still are mostly developed and applied to regular Euclidean domains such as those supporting images, audio, or video.
+For many applications however, the data domain is not regular.
+As a response to that fact, we are witnessing an increasing interest in the generalization of CNNs to graphs.
+Graphs are versatile data structures which can represent pairwise relationships between objects or act as a discrete representation of a continuous manifold.
+In this paper we take the latter view and represent a sampled sphere as a graph, for which we define the convolution and pooling operations.
+Spherical maps appear in many applications, such as the study of phenomena on the Earth for meteorologists or on the sky for cosmologists.
+A popular format for spherical maps is Healpix, which uses an equal-area, isolatitude sampling.
+Hence, we present a spherical CNN for analysis of full- and partial Healpix maps, which we call HealpixNet.
+While convolution on arbitrary graphs has mostly been sorted out, a general pooling operation has not been discovered.
+As such, while HealpixNet is a special case of a graph CNN, it is tailored to the Healpix sampling of the sphere.
+This approach is computationally much more efficient than using spherical harmonics to perform convolutions, an alternative that as been explored.
+% The filters learned by the HealpixNet are restricted to being radial.
+% Michaël: not necessary in the abstract?
+We demonstrate the method on a classification problem of mass maps from two cosmological models.
+A standard benchmark for that problem is to train an SVM on the histograms of map pixel values.
+Another is to use the power spectral density instead.
+HealpixNet achieves \todo{xx\%} better accuracy than those baselines, is more robust to noise, and is \todo{faster?}.
+Code and examples are available at \url{https://github.com/xxx}.
 \end{abstract}
@@
 \begin{keyword}
-%% keywords here, in the form: keyword \sep keyword
 Spherical Convolutional Neural Network \sep SCNN \sep Healpix CNN \sep Graph CNN 
-
 \end{keyword}
@@
 \begin{itemize}
-    \item Michael, do you agree with the title HealpixNet
+	\item (yes) Michael, do you agree with the title HealpixNet?
+I (Michaël) extensively modified the abstract to reflect that it is a special case of graph CNNs tailored to Healpix.
+Hence I now agree with the title.
+Feel free to edit.
+Ideally I'd like to have "graph" in the title (graph CNNs are quite hot these days), but I couldn't find how.
     \item Emphasize the novelty of using it on Helapix in abstract, into and rest of the paper
@@
 
-%% main text
 \section{Introduction}

### 2018-06-22 scnn.tex
commit before Lausanne

@@
 
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.45\textwidth]{figures/psd_sigma3.pdf}
+\caption{Power spectrum densities of the noiseless maps. The maps have be smoothed with a Gaussian kernel of radius $3$ arcmins in the preprocessing step.}
+\label{fig:psd_sigma3}
+\end{figure}
+
 The simulations are created using the fast lightcone method described in \citep{sgier2018fastgeneration}.
@@
 \centering
-\includegraphics[width=0.95\textwidth]{figures/smooth_map_class_1.pdf}
-\includegraphics[width=0.95\textwidth]{figures/smooth_map_class_2.pdf}
+\includegraphics[width=0.48\textwidth]{figures/smooth_map_class_1.pdf}
+\includegraphics[width=0.48\textwidth]{figures/smooth_map_class_2.pdf}
 \caption{Example maps from two classes. Top: model 1 ($\Omega_m=0.31, \sigma_8=0.82$). Bottom: model 2 ($\Omega_m=0.26, \sigma_8=0.91$).
@@
 algorithms. The two baselines are based on building features with a) the Power
-Spectral Densities or b) the histogram of pixels in the maps. CITE~\cite{...}
+Spectral Densities or b) the histogram of pixels in the maps~\cite{patton2017cosmologicalconstraints}.
 After a normalization, those features are then classified use a Support Vector
-Machine (SVM) with a linear kernel. Other kernels did provide better result
+Machine (SVM) with a linear kernel. Other kernels did not provide better result
 while having worse scaling properties. For fairness, we augmented the dataset
@@
 the noise. We stop adding new samples in the classifier once the validation
-error converge to a values. This process is depicted in
-Figure~\ref{fig:hist_error_evolution}.
+error converge to a value. This process is detailled in Appendix~\ref{sec:dataset_augmentation}.
 
@@
 regularization parameter of the SVM using a standard cross-validation
-technique\footnote{We also give a small advantage to the SVM classifiers by
+technique\footnote{We also give a small edge to the SVM classifiers by
 using cross-validation on the testing set.}.
@@
 
-We present in Figure~\ref{fig:results} the results for 5 different noise levels and $3$ different data sizes.
-The spherical neural network is always significantly better than the hand-crafted classifier.
+We present in Figure~\ref{fig:results} the results for 5 different noise
+levels and $3$ different data sizes.  We observe that the PSD features, i.e.
+one of the most used technique for model discrimination in cosmology is unable
+to perform the desired task. The main reason is that the two different model
+have very similar PSDs (see Figure~\ref{fig:psd_sigma3}).   As a result, one
+need to use other statistics to solve the problem. In this case, we use
+histogram features and observe a significant improvement over the PSD.  The
+SCNN present the advantage to learn automatically specific features for the
+task and also the usual Deep Learning performance bump.
 
-The histogram features contains information about the distribution of pixels, but does not include any spatial information.
-In contrast, both the PSD features and the CNN can exploit the spatial information.
+We also note that the histogram features contains information about the
+distribution of pixels, but does not include any spatial information. In
+contrast, both the PSD features and the SCNN can exploit the spatial
+information. Without this scructure, a non scallable fully connected neural network approach would have to be used.
 
@@
 \end{figure*}
-
-\begin{itemize}
-	\item Spherical CNN has the advantage to have some geometry information => one of the reason better than histogram
-	\item PSD...
-\end{itemize}
-
-\citep{patton2017cosmologicalconstraints}
 
@@
 \label{sec:spherical_harmonics}
-\begin{figure*}[!ht]
+\begin{figure*}[!htb]
 \centering
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=0.45\textwidth]{figures/psd_sigma3.pdf}
-\caption{Power spectrum densities of the noiseless maps. The maps have be smoothed with a Gaussian kernel of radius $3$ arcmins in the preprocessing step.}
-\label{fig:psd_sigma3}
-\end{figure}
+\section{Augementation of the dataset for the SVM classifier}
+\label{sec:dataset_augmentation} The original number of samples $480$, $1920$,
+$7680$ respectively for order $o=1,2,4$ is considered rather low for usual
+deep learning technique, especially when one desire to build a noise robust
+classifier. As a result, we use a classical dataset augmentation technique.
+Before entering the network for training each sample is added a random
+realization of Gaussian noise. The effect is twofold. First, the network never
+ends up seing the same sample and is less likely to overfit the training set.
+Second the trained network will be robust to Gaussian noise.
+
+When comparing the network, we want to ensure that the SVM classifier has
+access to the same amount of data that the network, i.e, potentially an
+infinite number of sample. Hence, we fit different linear SVM classifier using
+various amount of training set size until we oberve experimentally that
+increasing the amount of data does not improve the classifier. The validation
+set remain the same and is used for cross-validation to tune the L2
+penalization parameter of SVM. Eventually, we evaluate the final classifier on
+the testing set. An example of the evolution of the training and valdication
+error is show in Figure~\ref{fig:hist_error_evolution}.
 

### 2018-06-29 scnn.tex
update figures

@@
 \includegraphics[width=0.32\textwidth]{figures/result_order4.pdf}
-\caption{Classification errors for the 3 different problems. \nati{TODO: order is not correct} }
+\caption{Classification errors for the 3 different problems.}
 \label{fig:results}
@@
 Figure: Filters 1D and Gnonomic
+\begin{figure*}[!ht]
+\centering
+\includegraphics[width=0.45\textwidth]{figures/section_filter_last.pdf} 
+\includegraphics[width=0.45\textwidth]{figures/gnonomic_filter_last.pdf}
+\caption{24 learned filters selected from the last spherical convolutional layer. Left: section. Right: gnonomic view.}
+\label{fig:learned_filter}
+\end{figure*}
 

### 2018-06-29 scnn.tex
figref, tabref, eqnref, secref

@@
 \newcommand{\nati}[1]{{\color[rgb]{.1,.6,.1}{#1}}}
+\newcommand{\todo}[1]{{\color[rgb]{.6,.1,.6}{#1}}}
+\newcommand{\assign}[1]{{\color[rgb]{.8,.5,.8}{Assigned: #1 }}}
 
-\newcommand{\todo}[1]{{\color[rgb]{.6,.1,.6}{#1}}}
-
-\newcommand{\assign}[1]{{\color[rgb]{.8,.5,.8}{Assigned: #1 }}}
+\newcommand{\figref}[1]{Figure~\ref{fig:#1}}
+\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
+\newcommand{\secref}[1]{Section~\ref{sec:#1}}
+%\newcommand{\secref}[1]{\S\ref{sec:#1}}
+\newcommand{\eqnref}[1]{(\ref{eqn:#1})}
 
@@
 The paper is organised as follows.
-In Section~\ref{sec:related}, we describe existing approaches to convolutions on the sphere, graphs, and manifolds.
-In Section~\ref{sec:method}, we show the way to construct a graph using Healpix sampling and define the convolution operation.
-The comparison between the spherical CNN and the benchmark method using the weak lensing mass map classification is presented in Section~\ref{sec:experiments}.
-We conclude in Section~\ref{sec:conclusion}.
+In \secref{related}, we describe existing approaches to convolutions on spheres, graphs, and manifolds.
+\secref{method} exposes the construction of a graph given the Healpix sampling of a sphere and defines the convolution operation.
+Finally, \secref{experiments} presents our experimental results on the weak lensing mass map classification problem. There we compare our method to two standard benchmarks and show its superiority.
+%We conclude in \secref{conclusion}.
 
@@
 irregularities have been highlighted in the graph displayed in
-Figure~\ref{fig:healpix_graph_4}.
+\figref{healpix_graph_4}.
 
@@
 
-As shown in Figure~\ref{fig:graph_harmonics}, it turns out that using the graph
+As shown in \figref{graph_harmonics}, it turns out that using the graph
 construction described above, the graph Fourier harmonics resemble the
@@
 is defined as
-\begin{equation} \label{def:graph_convolution}
+\begin{equation} \label{eqn:graph_convolution}
 h(L)\b{f} = \U h(\bLambda) \U^* \b{f},
@@
 where $h(\bLambda)$ is a diagonal matrix where $h(\bLambda)_{ii}=h(\bLambda_{ii})$.
-Equation~\ref{def:graph_convolution} contains three parts: a) $\U^* \b{f}$, the
+Equation~\eqnref{graph_convolution} contains three parts: a) $\U^* \b{f}$, the
 Fourier transform of $\b{f}$; b) $h(\bLambda)$ the multiplication with the Fourier
@@
 Let us consider the heat diffusion problem
-\begin{equation} \label{eq:heat_equation}
+\begin{equation} \label{eqn:heat_equation}
 \L \b{f}(t) = \tau \partial_t \b{f}(t),
@@
 where $\b{f}(t): \mathbb{R}_+ \rightarrow \mathbb{R}^N$. Given the initial condition
-$\b{f}(0)$, the solution of~\ref{eq:heat_equation} can be expressed as
+$\b{f}(0)$, the solution of~\eqnref{heat_equation} can be expressed as
 \begin{equation}
@@
 are one generalization of the squared frequencies on the graph. Hence the kernel $K_t$ is also a generalization of the
-Gaussian kernel on the sphere. In Figure~\ref{fig:gaussian_filters_comparizon} top, we show
+Gaussian kernel on the sphere. In \figref{gaussian_filters_comparizon} top, we show
 the effect of the convolution by diffusing a unit of heat for $\tau=1$ and various
-time $t$. In  Figure~\ref{fig:gaussian_filters_visualization} of
-Appendix~\ref{app:filter_visualization}, we show different visualizations of the
+time $t$. In \figref{gaussian_filters_visualization} of
+Appendix~\ref{sec:filter_visualization}, we show different visualizations of the
 convolution kernel $K_t$. We also compare the graph convolution with the
 spherical symmetric Gaussian smoothing
-(Figure~\ref{fig:gaussian_filters_comparizon} bottom) and observe that both
+(\figref{gaussian_filters_comparizon} bottom) and observe that both
 techniques lead to similar results. While the graph convolution is different
@@
 We define the pooling process as the inverse operation grouping the 4 subpixels.
-Figure~\ref{fig:pooling} illustrates the process.
+\figref{pooling} illustrates the process.
 \begin{figure}[!ht]
@@
 We found that for $\ell>1000$ the differences in power spectrum is $~5\%$.
-To remove this information, we additionally smooth the spherical maps with a Gaussian kernel of radius $3$ arcmins. The resulting PSD are displayed in Figure~\ref{fig:psd_sigma3}.
+To remove this information, we additionally smooth the spherical maps with a Gaussian kernel of radius $3$ arcmins. The resulting PSD are displayed in \figref{psd_sigma3}.
 
@@
 % The training and validation set are created later on.
-Figure \ref{fig:map_sample} shows the full sky simulations and a zoom region for model 1 (top) and model 2 (bottom).
+\figref{map_sample} shows the full sky simulations and a zoom region for model 1 (top) and model 2 (bottom).
 Initial conditions for these simulations were the same, so the differences in structures can only be attributed to different cosmological parameters used to evolve the particle distribution.
@@
 The area of the pixels for an Nside of $o$ correspond to the different split of the data.
-As shown in Figure~\ref{fig:subpart_sphere}, we used $o=1,2,4$ as the resulting
+As shown in \figref{subpart_sphere}, we used $o=1,2,4$ as the resulting
 samples are large enough to suffer from the effects of the spherical geometry. We
@@
 
-We present in Figure~\ref{fig:results} the results for 5 different noise
+We present in \figref{results} the results for 5 different noise
 levels and $3$ different data sizes.  We observe that the PSD features, i.e.
@@
 to perform the desired task. The main reason is that the two different model
-have very similar PSDs (see Figure~\ref{fig:psd_sigma3}).   As a result, one
+have very similar PSDs (see \figref{psd_sigma3}).   As a result, one
 need to use other statistics to solve the problem. In this case, we use
@@
 \section{Spherical harmonics VS graph Fourier eigenvectors}
-Figure~\ref{fig:graph_harmonics} displays the first 16 eigenvectors of the
+\figref{g:graph_harmonics} displays the first 16 eigenvectors of the
 graph Fourier basis used for the convolution. While their is a clear
 resemblance with the spherical harmonic, the small irregularities in the
-sampling (see~\ref{fig:healpix_graph_4}) have two important effects on the
+sampling (see \figref{healpix_graph_4}) have two important effects on the
 graph Fourier eigenvectors.  First, some graph eigenvectors will be
@@
 \section{Filter visualization}
-\label{app:filter_visualization}
+\label{sec:filter_visualization}
 
-In Figure~\ref{fig:gaussian_filters_visualization}, we present three different
+In \figref{gaussian_filters_visualization}, we present three different
 ways to plot the graph convolution kernel $K_t(x)=e^{-\tau t x}$. First, they can
@@
 working on the sphere, we can only plot the section of the convoluted delta. In
-Figure~\ref{fig:index_section}, we display the selected indexes for the section
+\figref{index_section}, we display the selected indexes for the section
 plotting. Note that, because of the small irregularities in the HealPix
@@
 \includegraphics[width=0.45\textwidth]{figures/index_plotting_order20_nside16.pdf}
-\caption{Indexes selected for the section ploting of Figure~\ref{fig:gaussian_filters_visualization} middle. The delta was placed on the yellow node.}
+\caption{Indexes selected for the section ploting of \figref{gaussian_filters_visualization} middle. The delta was placed on the yellow node.}
 \label{fig:index_section}
@@
 the testing set. An example of the evolution of the training and valdication
-error is show in Figure~\ref{fig:hist_error_evolution}.
+error is show in \figref{hist_error_evolution}.
 

### 2018-07-02 scnn.tex
update appendix + results

@@
 
-\subsection{Interpretation}
+\subsection{Filter visualization}
 \assign{Nathanaël, Tomek, Michaël}
-
-Show the learned filters and feature maps and try to interpret them.
-\todo{\\ TK and NP: Figure of filters from the mass map clasification}
+One common visualization for CNN is to display the shape of the learned filters.
+Since our construction lead to almost (up to the sampling irregularities) spherical filters, we plot in \figref{learned_filter} both the section (on the sphere) and a gnomeview projection on a plane of a random selection of learned filters.
+The filters are selected from the last layer of the network corresponding the experiment with order $o=2$ for a relative noise level of $2$.
+Nevertheless, all networks presented similar pattern, at least from a human perspective.
+The gnomview projection clearly exibits the sampling issue of HealPix.
+For a detail, on how the filters are plot, please refer to Appendix~\ref{sec:filter_visualization}.
+\todo{Tomek: can you say something about the filters.}
 
@@
 \section{Spherical harmonics VS graph Fourier eigenvectors}
-\figref{g:graph_harmonics} displays the first 16 eigenvectors of the
+\ref{fig:graph_harmonics} displays the first 16 eigenvectors of the
 graph Fourier basis used for the convolution. While their is a clear
 resemblance with the spherical harmonic, the small irregularities in the
-sampling (see \figref{healpix_graph_4}) have two important effects on the
-graph Fourier eigenvectors.  First, some graph eigenvectors will be
+sampling (see \figref{healpix_graph_4}) have an effect on the
+graph Fourier eigenvectors. First, conterintuitively, some graph eigenvectors will be
 localized~\cite{perraudin2018global}, i.e: they will span only a small subpart
@@
 \includegraphics[width=0.95\textwidth]{figures/eigenvectors.pdf}
-\caption{12 first graph Fourier eigenvectors.}
+\caption{12 first graph Fourier eigenvectors.
+Eigenvectors 1-3 could be assotiated to spherical harmonics of order 1, eigenvectors 4-8 to order 2 and 9-15 to order 3.
+Nevertheless, the graph eigenvectors are only approximating the real spherical harmonics.}
 \label{fig:graph_harmonics}
@@
 In \figref{gaussian_filters_visualization}, we present three different
-ways to plot the graph convolution kernel $K_t(x)=e^{-\tau t x}$. First, they can
-be plotted in the graph spectral domain. In this case, we simply evaluate $K_t$
-at the graph eigenvalues $\text{diag}(\bLambda)$. Second, we can convolve a
-delta on the sphere and plot a gnomonic view of the results. Third, since we are
-working on the sphere, we can only plot the section of the convoluted delta. In
-\figref{index_section}, we display the selected indexes for the section
-plotting. Note that, because of the small irregularities in the HealPix
-sampling, the second and the third methods are likely to change depending on the
-chosen delta.
+visualization for the a healpix graph convolution kernel.
+The kernel used is defined in the graph spectral domain as $K_t(x)=e^{-\tau t x}$.
+This is the domain used for our first visualization.
+In this case, we simply evaluate $K_t$
+at the graph eigenvalues $\text{diag}(\bLambda)$. The lower eigenvalues $\lambda$ correspond to the lower frequencies, i.e. the spectral mode with less variation. 
+As a second visualization, we can observe the kernel directly on the sphere. To do so, we perform the convolution of a
+Kroneker on the sphere plot the result with gnomonic projection. Eventually, as we are
+working on the sphere with theoretically spherical filters (up the the irregularities of the sampling), we could only plot the section of the convoluted Kroneker.
+To do so, we convolve a Kroneker on the equator and use the equator for our section as shown in~\figref{index_section}.
+Note that, because of the small irregularities in the HealPix
+sampling, the second and the third methods are subject to small varation depending on the
+chosen Kroneker.
 

### 2018-07-02 scnn.tex
section result a bit further

@@
 In this section, we demonstrate the performance of the spherical neural network on a discrimination problem.
-Our implementation is available as a small python package\url{https://our.code.link.com}.
+Our implementation is available as a small python package \url{https://our.code.link.com}.
 Furthermore, all the data to reproduce our experiments are available online.\footnote{\url{https://doi.org/10.5281/zenodo.????} \todo{correct DOI}}.
@@
 
-We make full sky N-body simulations for two parameter set for $\Lambda \rm{CDM} $ cosmological model: model 1 ($\Omega_m=0.31, \sigma_8=0.82$) and model 2 ($\Omega_m=0.26, \sigma_8=0.91$), where $\Omega_m$ is the matter density in the universe and $\sigma_8$ is the normalisation of the matter power spectrum.
-Other parameter parameters were set to $h=0.7$ (MORE PARAMS HERE - CHECK WITH RAPHAEL).
+We make full sky N-body simulations for two parameter sets for $\Lambda \rm{CDM} $ cosmological model: model 1 ($\Omega_m=0.31, \sigma_8=0.82$) and model 2 ($\Omega_m=0.26, \sigma_8=0.91$), where $\Omega_m$ is the matter density in the universe and $\sigma_8$ is the normalisation of the matter power spectrum.
+Other parameter parameters were set to $h=0.7$ \todo{(MORE PARAMS HERE - CHECK WITH RAPHAEL)}.
 These parameters were chosen to have the same spherical harmonic power spectrum for $\ell<1000$.
@@
 We found that for $\ell>1000$ the differences in power spectrum is $~5\%$.
-To remove this information, we additionally smooth the spherical maps with a Gaussian kernel of radius $3$ arcmins. The resulting PSD are displayed in \figref{psd_sigma3}.
+To remove this information, we additionally smooth the spherical maps with a Gaussian kernel of radius $3$ arcmins.
+The resulting PSD are displayed in \figref{psd_sigma3}.
+In the pre-processing step, we also remove the mean of each map.
 
@@
 
-The simulations are created using the fast lightcone method described in \citep{sgier2018fastgeneration}.
+The simulations are created using the fast lightcone method described in~\citep{sgier2018fastgeneration}.
 However, we use only a single simulation box, as opposed to two used in that work, as we use source galaxies at lower redshift of $z=1$, instead of $z=1.5$.
@@
 For each class, we generate 30 simulations.
-In the experiment we use data on a parts of the sphere, and we check the performance as a function of the area used.
-We also test the performance as a function of noise level of the pixels.
 
-As a pre-processing step, we first remove the mean of each sample and we apply a spherical Gaussian smoothing kernel with a radius of $1$ arcmin.
 Out of the 60 simulations, 20 are kept for the test set.
-% The training and validation set are created later on.
 \figref{map_sample} shows the full sky simulations and a zoom region for model 1 (top) and model 2 (bottom).
@@
 \subsection{Problem formulation}
-
+While the number of maps might sound small for deep learning, the information contained in the maps is very recurrent, allowing us to use parts of the map as sample for our simulation.
 Leveraging the properties of the HealPix sampling, we can split each maps
 into $12*o^2$ ($o=1,2,4,\dots$) samples that span a smaller part of the sphere. 
-The area of the pixels for an Nside of $o$ correspond to the different split of the data.
 As shown in \figref{subpart_sphere}, we used $o=1,2,4$ as the resulting
@@
 The goal is build a robust classifier, i.e. an automatic way to
-discriminate between the two classes in the presence of noise. For all the
+discriminate between the two classes in the presence of noise. 
+We check the performance of the classifier as a function of the area used, i.e "the order" $o$ and also as a function of the relative level of the noise.
+
+For all the
 experiments, we work with centered Gaussian noise. \todo{Tomek: could you put a
-justification.} All classifiers are trained with noisy samples. To improve the
+justification.} To improve the
 stability of the spherical CNN, we slowly increase the amount of noise added to
@@
 overfitting, the noise is randomly produced during the training process. We trained our
-model between $50$ and $200$ epochs depending on the complexity and the size of
+model between \nati{$50$ and $200$} epochs depending on the complexity and the size of
 the problem. The testing set was simply used to assess the global performance of
@@
 Machine (SVM) with a linear kernel. Other kernels did not provide better result
-while having worse scaling properties. For fairness, we augmented the dataset
+while having worse scaling properties. All classifiers are trained with noisy samples. For fairness, we augmented the dataset
 of the baseline algorithm in a similar way as for the network, i.e, with
@@
 regularization parameter of the SVM using a standard cross-validation
-technique\footnote{We also give a small edge to the SVM classifiers by
-using cross-validation on the testing set.}.
+technique.
 
@@
 \assign{Nathanaël, Tomek, Michaël} 
-One common visualization for CNN is to display the shape of the learned filters.
-Since our construction lead to almost (up to the sampling irregularities) spherical filters, we plot in \figref{learned_filter} both the section (on the sphere) and a gnomeview projection on a plane of a random selection of learned filters.
-The filters are selected from the last layer of the network corresponding the experiment with order $o=2$ for a relative noise level of $2$.
-Nevertheless, all networks presented similar pattern, at least from a human perspective.
-The gnomview projection clearly exibits the sampling issue of HealPix.
-For a detail, on how the filters are plot, please refer to Appendix~\ref{sec:filter_visualization}.
+Onecommon visualization for CNN is to display the shape of the learned filters.
+Since our construction lead to almost (up to the sampling irregularities)
+spherical filters, we plot in \figref{learned_filter} both the section (on the
+sphere) and a gnomeview projection on a plane of a random selection of learned
+filters. The filters are selected from the last layer of the network
+corresponding the experiment with order $o=2$ for a relative noise level of
+$2$. Nevertheless, all networks presented similar gnomonic and section pattern, at least from a
+human perspective. The gnomonic projection clearly exibits the sampling issue
+of HealPix. For a detail, on how the convolution kernels are plot, please refer to
+Appendix~\ref{sec:filter_visualization}. 
 \todo{Tomek: can you say something about the filters.}
 
-Figure: Filters 1D and Gnonomic
 \begin{figure*}[!ht]

### 2018-07-03 scnn.tex
edits (mostly introduction and healpix sampling)

@@
 
+%\usepackage{lmodern}
+\usepackage[T1]{fontenc}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{graphicx,array}
+\usepackage{subcaption}
 \usepackage{amsmath}
@@
 \title{HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications}
+% \title{Efficient Spherical ConvNet with Graph Convolutions for Cosmological Applications}
 % \title{HealpixNet: Efficient spherical Convolutional Neural Network with graphs and Healpix sampling for cosmological applications}
@@
 A popular format for spherical maps is Healpix, which uses an equal-area, isolatitude sampling.
-Hence, we present a spherical CNN for analysis of full- and partial Healpix maps, which we call HealpixNet.
-While convolution on arbitrary graphs has mostly been sorted out, a general pooling operation has not been discovered.
+Hence, we present a spherical CNN for analysis of full and partial Healpix maps, which we call HealpixNet.
+While convolution on arbitrary graphs has mostly been sorted out, a general pooling operation has not been discovered so far.
 As such, while HealpixNet is a special case of a graph CNN, it is tailored to the Healpix sampling of the sphere.
-This approach is computationally much more efficient than using spherical harmonics to perform convolutions, an alternative that as been explored.
+This approach is computationally much more efficient than using spherical harmonics to perform convolutions, an alternative that as been explored previously.
 % The filters learned by the HealpixNet are restricted to being radial.
@@
 HealpixNet achieves \todo{xx\%} better accuracy than those baselines, is more robust to noise, and is \todo{faster?}.
-Code and examples are available at \url{https://github.com/xxx}.
+Code and examples are available at \todo{\url{https://github.com/xxx}}.
 \end{abstract}
@@
 
-Cosmological and astrophysical data often comes in a form of spherical sky maps.
+Cosmological and astrophysical data often comes in the form of spherical sky maps.
 Observables that cover large parts of the sky, such as the Cosmic Microwave Background (CMB) \citep{planck2015cosmologicalparameters,komatsu2011sevenyear,staggs2018recentdiscoveries}, neutral hydrogen \citep{santos2015cosmologySKA,HI4PI2016fullskyHI}, galaxy clustering \citep{alam2017clusteringgalaxies}, gravitational lensing \citep{troxel2017darkenergy,hildebrandt2017kidscosmological}, and others, have been used to constrain cosmological and astrophysical models.
-Deep Learning methods have recently started to gain popularity as an analysis tool in cosmology \citep{schmelze2017cosmologicalmodel,luciesmith2018machinelearning,gupta2018nongaussianinformation,gillet2018deeplearning,hassan2018reionizationmodels,aragoncalvo2018classyfyinglarge,ciuca2017cnnstring}.
-Convolutional Neural Networks (CNNs) are particularly well suited for analysis of astrophysical data due to their ability to capture complicated, non-linear patterns, which are often present in the data.
+Deep Learning has recently gained popularity as an analysis tool in cosmology \citep{schmelze2017cosmologicalmodel,luciesmith2018machinelearning,gupta2018nongaussianinformation,gillet2018deeplearning,hassan2018reionizationmodels,aragoncalvo2018classyfyinglarge,ciuca2017cnnstring}, thanks to its ability to capture complicated, non-linear patterns which are often present in the data.
+Convolutional Neural Networks (CNNs) are particularly well suited for analysis of astrophysical data due to the translation equivariance built into their architecture.
+Indeed, sky maps are translation equivariant, which means that rotating maps on the sphere doesn't change their interpretation (at least at the micro scale).
+As such, learned weights can be shared across the sphere: the network does not have to relearn to detect objects or features at every spatial location.
 
-So far these algorithms have been demonstrated on the flat images.
-Deep learning-based analysis of larger survey area form requires dividing the data into smaller chunks and projecting them on a flat, 2D surface.
-While this process can work efficiently as already demonstrated, it may be more convenient do work with deep learning directly on the sphere.
-The most commonly used scheme in astrophysics to divide a sphere into pixels is Healpix \citep{gorski2005healpix}, which uses isolatitude sampling and pixels with the same area.
+\todo{@Tomek: can you explain why we care about parts of the sphere? (that is an advantage of the graph model over the spherical harmonics)}
+\todo{@Tomek: How is the data acquired?
+Do telescopes and satellites take measurements according to the Healpix sampling?
+(it is also an advantage of our method to be agnostic to the sampling, which might be useful to researchers working with missing data or different models)}
 
-In this work we present an algorithm and software package \pkg{SCNN-temp-name}\footnote{github.com/SwissDataScienceCenter/scnn} which implements efficient deep convolutional neural networks on Healpix maps.
-To achieve this, we represent the sphere $S^2$ as a graph of connected pixels, which forms a 2D manifold embedded in 3D space $\mathbb{R}^3$.
-This approach is based on CNN formulations on graphs described by \citet{defferrard2016convolutional} and runs using the \pkg{TensorFlow} \citep{abadi2016tensorflow} engine.
-The flexibility of the graph approach allows for faster analysis when data spans only a part of the sphere.
+So far these algorithms have mostly been demonstrated on Euclidean domains, such as flat images.
+As such, perhaps the most straightforward approach to the analysis of spherical data is to divide it into small chunks and project those on flat 2D surfaces.
+While this mostly works, as demonstrated \todo{in ??? for example}, it is more natural and accurate to work directly on the sphere.
+
+% cohen2017convolutional (ICML workshop) and cohen2018spherical (ICLR best paper) are redundant
+A first attempt to generalize CNNs to spherical data was to apply a standard 2D CNN to a grid discretization of the sphere~\citep{boomsma2017spherical}.
+While this approach leverages the well-developed 2D convolution and hierarchical pooling, it is restricted to those very specific grid samplings.
+A second attempt by~\citet{cohen2018spherical} was to leverage the spherical Fourier transform and to perform the convolution in the spectral domain, thanks to the convolution theorem.
+While there exists fast Fourier transforms for some samplings, this approach is still computationally expensive.
+Finally, the use of a graph to model the discretized sphere was considered by~\citet{khasanova2017graph} as well, towards the goal of building invariances in the network.
+As~\citep{boomsma2017spherical}, they use an equirectangular grid sampling.
+Moreover, they did not take advantage of a hierarchical pixelization of the sphere and resorted to dynamic pooling~\citep{kalchbrenner2014dcnn}.
+
+To overcome those shortcomings, we introduce an efficient spherical CNN formulation which uses (i) convolutions on graphs and (ii) hierarchical pooling.
+The main idea is to represent the sphere $S^2$, a 2-dimensional manifold embedded in $\mathbb{R}^3$, as a graph of connected pixels.
+Our approach uses the graph CNN formulation introduced by \citet{defferrard2016convolutional}, which is efficient and can adapt to any sampling of the sphere.
+The convolution operation costs $\mathcal{O}(n)$ operations, where $n$ is the number of pixels.
+That is the lowest possible complexity for convolution without approximations (e.g.
+by sketching).
+The flexibility of modeling the data domain with a graph allows, for example, to easily model data which only spans a part of the sphere, or data which is not uniformly sampled.
+Our hierarchical pooling strategy exploits a hierarchical pixelization of the manifold to analyze the data at multiple scales. Such hierarchical pixelizations of the sphere have been well studied.
+
+In this work we present and release HealpixNet\footnote{\url{https://github.com/SwissDataScienceCenter/scnn} \todo{change location}}, an algorithm and software package which implements an efficient CNN on Healpix maps.
+It is implemented with \pkg{TensorFlow} \citep{abadi2016tensorflow} and is intended to be easy to use out-of-the box for cosmological applications.
+As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology and astrophysics, we tailored our method to that particular sampling.
+However, only two elements depend on the sampling: (i) the choice of neighboring pixels when building the graph, and (ii) the choice of parent pixels when building the hierarchy.
 It is also possible to use multiple Healpix maps within our framework and use datasets in form of ``shells''.
@@
 
-Different formulations of deep learning on the sphere have been proposed in~\citet{cohen2017convolutional,cohen2018spherical,boomsma2017spherical,khasanova2017graph}.
-In all of these methods, a different sphere pixelisation scheme is used, making them unsuitable for most cosmological application. 
-Hence, our work we focused on the Healpix sampling, as it is the most commonly used in cosmology.
-It can be, however, extended to other sampling schemes, by straightforward change in definition of the graph. These approach are discussed in Section~\ref{sec:spherical_conv}.
 %\nati{I am not sure this goes there...} Other recently developed sampling methods include \citep{mcewen2011novelsampling}, where exact sampling theorem for equiangular MW sampling was presented.
-
-An important advantage of our method is the speed of its convolution operation as it is of order $\mathcal{O}(n)$, where $n$ is the number of points, which is the lowest possible complexity for convolution without approximations, e.g.
-sketching.
-While our implementation is slower than traditional convolution on a 2 dimensional image, it remain in the same order of magnitude.
-MORE HERE
-
-Because of the spherical domain, the method presented here restricts the shape of the filters learned by the network to be radial.
-While this may be a less general design compared to the one used by conventional CNNs on flat images, we found it to still work efficiently for our test cases.
-The layered structure of the network can partially compensate for that.
-Further generalizations to non-radial filters may be possible [cite?], but we leave it to future work.
 
@@
 The comparison is made as a function of noise level on convergence maps and area of the sphere used.
+Results show that our model is better at discriminating the maps, is more resilient to noise, and \todo{is faster?}.
 
-The paper is organised as follows.
+The paper is organized as follows.
 In \secref{related}, we describe existing approaches to convolutions on spheres, graphs, and manifolds.
@@
 acceleration, the convolutions remain expensive in comparison to a traditional
-2-dimensional convolution, limiting the practical use of this approach. While
+2-dimensional convolution, limiting the practical use of this approach.
+\todo{to have numbers to back up our claim: have the theoretical complexities and measure the time needed for a convolution on graph and the healpix Fourier transform to get the constants}
+While
 a comparison is theoretically possible, the experiments
@@
 cosmology as the data often observed only on a subpart of the sphere.
+\todo{slow: full sky maps are composed of millions of points. partial maps are hard to process}
 
-A second direction has been followed in~\cite{boomsma2017spherical}. The idea is
+A second direction has been followed in~\citet{boomsma2017spherical}. The idea is
 to use the traditional 2-dimensional convolution on an irregular grid defined on the
-sphere. In the paper, two grids are used: the geodesic grid and the “cubed
-sphere” grid defined by Ronchi et. al~\cite{ronchi1996cubed}. Because this
+sphere. In the paper, two grids are used: the geodesic grid \todo{isn't it the equirectangular grid?} and the ``cubed
+sphere'' grid defined by~\citet{ronchi1996cubed}. Because this
 approach is based on the traditional 2-dimensional convolution, it is very likely to be the
@@
 definition adapted to a cube and not to a sphere.
+\todo{border effects?}
 % \nati{Michael: Under some very
@@
 % should not.}
+% I think we should!
 
@@
 
-We are not the first one to leverage a graph to define a CNN on a sphere.
-\cite{khasanova2017graph} use the same idea to handle omnidirectional images.
+The use of a graph to model the discretized sphere was considered by~\citet{khasanova2017graph} as well.
+The authors map omnidirectional images to the sphere, with the goal of correcting for distortions induced by the lens used for the acquisition.
 Besides the different application covered by the paper, there are two important
@@
 \todo{other approaches? GNNs, Kipf first order approx, message passing}
+
+The connection has recently been made between graph CNNs and group equivariant CNNs \cite{kondor2018equivariance}, justifying the use of graphs to gain rotation equivariance on the sphere.
 
@@
 
+\subsection{HEALPix sampling}
+\label{sec:healpix}
+
+Before doing any numerical analysis on the sphere, one first has to choose a tessellation, i.e., an exhaustive partition of the sphere into finite area elements, where the data under study is quantized.
+While our method is applicable to any pixelization of the sphere, two details depend on the chosen sampling: (i) the choice of neighbors in the construction of the graph, and (ii) the choice of parent nodes when coarsening the graph.
+As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology, our target application, we'll tailor the method to that particular sampling in the subsequent exposition.
+%We'll note in later sections where the method should be adapted for a different sampling.
+
+HEALPix is a particular case of a more general class of schemes which are based on a hierarchical subdivision of a base polyhedron.
+%Many discretized maps of the sphere are based on a hierarchical subdivision of a base polyhedron.
+Another example is the geodesic grids which are based on geodesic polyhedrons, i.e., polyhedrons made of triangular faces.
+A counter-example is the equirectangular projection, which is not constructed from a base polyhedron, although it can be subdivided.
+In the particular Healpix case, the base is a rhombic dodecahedron, i.e., a polyhedron made from 12 congruent rhombic faces.\footnote{A rhombus is a quadrilateral whose four sides all have the same length.} See \figref{pooling} for an illustration of the base rhombic dodecahedron and its subdivisions.
+
+HEALPix is an acronym for Hierarchical Equal Area isoLatitude Pixelization of a sphere.
+As suggested in the name, this pixelization produces a subdivision of a spherical surface in which each pixel covers the same surface area as every other pixel.
+The lowest possible resolution is given by the base partitioning of the surface into $N_{pix} = 12$ equal sized pixels (right-most sphere in \figref{pooling}).
+As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2 \cdot 12 = 2^2 \cdot 12 = 48$ pixels (middle sphere in \figref{pooling}), the third is $N_{pix} = N_{side}^2 \cdot 12 = 4^2 \cdot 12 = 192$ pixels, etc., where $N_{side} = 1, 2, 4, 8, \ldots$ is the grid resolution parameter.
+High-resolutions HEALPix maps easily reach millions of pixels. \figref{example_maps} shows two examples.
+Another property of the HEALPix grid is that the pixel centers, represented by the black dots in \figref{pooling}, occur on a discrete number of rings of constant latitude (the number of which depends on the resolution).
+
+\begin{figure}[ht]
+	\centering
+	\begin{subfigure}[b]{0.45\linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{figures/exampleEarthTopo}
+		\caption{}
+		\label{fig:example_earth}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}[b]{0.45\linewidth}
+		\centering
+		\includegraphics[width=\linewidth]{figures/exampleCMB}
+		\caption{}
+		\label{fig:example_cmb}
+	\end{subfigure}
+	\caption[]{Example of (a) an Earth topography map composed of \textasciitilde 3 million pixels (\textasciitilde 7 arcmin resolution) and (b) a model of the Cosmic Microwave Background (CMB) radiation temperature anisotropy, composed of \textasciitilde 13 million pixels (\textasciitilde 3.4 arcmin resolution).\footnotemark}
+	\label{fig:example_maps}
+\end{figure}
+
+\footnotetext{Figures from \url{https://healpix.jpl.nasa.gov/}.}
+
 \subsection{Graph creation}
+
+The graph approximates the 2D manifold that is the surface of the sphere. It can accommodate any sampling, regular or irregular.
+
 In the classical 2-dimenstional convolution, each pixel is connected with the
@@
 \end{equation}
+\todo{why not $1/d$? See Pascal's paper}
 Here $x_i$ is a 3-dimensional vector encoding the coordinate of the pixels $i$
@@
 
-\subsection{Coarsening}
-The HealPix sampling presents the advantage to have a natural coarsening method
-based on its construction. Each Nside level divides each pixel into 4 subpixels.
-We define the pooling process as the inverse operation grouping the 4 subpixels.
+\subsection{Coarsening and Pooling}
+
+Hierarchical pixelization schemes present a natural coarsening.
+Indeed, each subdivision divides a cell in an equal number of sub-cells.
+Coarsening is the reverse operation: merging the sub-cells to summarize the data supported on them.
+Merging cells lead to a coarser graph, hence the name coarsening.
+Pooling refers to the operation that summarizes the data supported on the merged sub-cells in one child cell.
+That operation is often taken as the maximum value, but it might be any permutation invariant operation such as the sum or the average.
 \figref{pooling} illustrates the process.
+
+% The advantage of schemes based on a base polyhedron is that cells are equal-area.
+While that is not required for the convolution operation when modeling with graphs (it can be corrected by setting edge weights appropriately, see \citet{khasanova2017graph})
+% nope: can also do a regular pooling on the equirectangular. It preserves the sampling, and the convolution is adapted to the sampling thanks to the edge weights.
+
 \begin{figure}[!ht]
@@
 	\includegraphics[width=0.45\textwidth]{figures/pooling.pdf}
-\caption{Pooling illustration for 2 levels using some part of the mollview projection.
-The final patch represents 1/12 of the sphere.}
+	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarser cell covers $1/12$ of the sphere.}
 	\label{fig:pooling}
@@
 
+\section{Discussion}
+
+Because of the spherical domain, the method presented here restricts the shape of the filters learned by the network to be radial.
+While this may be a less general design compared to the one used by conventional CNNs on flat images, we found it to still work efficiently for our test cases.
+The layered structure of the network can partially compensate for that.
+Further generalizations to non-radial filters may be possible [cite?], but we leave it to future work.
+
 \section{Conclusion}
@@
 
-\section{Augementation of the dataset for the SVM classifier}
+\section{Augmentation of the dataset for the SVM classifier}
 \label{sec:dataset_augmentation} The original number of samples $480$, $1920$,

### 2018-07-03 scnn.tex
figure of the network architecture

@@
 \usepackage{aasmacros}
+
+\usepackage{enumitem} % to remove when done with todo list
 
@@
 \section{TODO list}
-\begin{itemize}
+\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
 	\item (yes) Michael, do you agree with the title HealpixNet?
@@
     \item (done!) upgrade the plot of pooling (Nathanael)
-    \item new plot for network structure (teaser plot) (Michael)
+	\item (done!) new plot for network structure (teaser plot) (Michael) What do you think? Todo: link the points on the sphere to the fully connected
     \item add info on comparison with histogram, so that it's just a demonstration
@@
 \end{itemize}
+
+\begin{figure*}[!ht]
+	\centering
+	\includegraphics[width=\linewidth]{figures/architecture}
+	\caption{Overall network architecture, showing here two convolutional layers acting as feature extractors followed by a fully connected layer with softmax acting as the classifier.
+A convolutional layer is based on five operations: convolution, non-linearity, batch normalization, down-sampling, and pooling.
+While most operations are agnostic to the data domain, the convolution and down-sampling have to be adapted.
+In this paper, we propose first to model the sphere with a graph and to perform the convolution on the graph.
+Graphs are versatile data structures which can model any sampling, even irregular or partial.
+Second, we propose to exploit a hierarchical pixelization of the sphere for the pooling operation.
+It allows the network to analyze the data at multiple scales while preserving the spatial localization of features.}
+\end{figure*}
 

### 2018-07-04 scnn.tex
small edits

@@
 
-Following~\cite{shuman2013emerging}, the graph normalized graph Laplacian
-defined as $\L = \I - \D^{-1/2} \W \D^{-1/2}$ is a second order differential operator
-that can be used to define the graph Fourier basis. Here $D$ is the diagonal
+Following~\cite{shuman2013emerging}, the normalized graph Laplacian,
+defined as $\L = \I - \D^{-1/2} \W \D^{-1/2}$, is a second order differential operator
+that can be used to define a Fourier basis on the graph. Here $\D$ is the diagonal
 matrix where $\D_{ii}=\b{d}_i$. By construction the Laplacian is symetric positive
-semi-definite and hence can be decomposed as $\L=\U \bLambda \U^*$, where $U$ is an
+semi-definite and hence can be decomposed as $\L=\U \bLambda \U^*$, where $\U$ is an
 orthonormal matrix of eigenvectors and $\bLambda$, the diagonal matrix of
 eigenvalues. The graph Fourier basis is defined as the Laplacian eigenvectors.
-The graph Fourier transform of $f$ is simply its projection on $U$ given by
-$\hat{\b{f}}=\U^*\b{f}$. Similarly the inverse graph Fourier transform reads $\b{f}=\U\hat{\b{f}}$.
-Note that instead of frequencies, the Fourier modes are crescently ordered with
-respect of the Laplacian eigenvalues $\bLambda$. In a sense, the Laplacian
+The graph Fourier transform of $f$ is simply its projection on $\U$ given by
+$\hat{\b{f}}=\U^*\b{f}$. Similarly, the inverse graph Fourier transform reads $\b{f}=\U\hat{\b{f}}$.
+Note that instead of frequencies, the Fourier modes are ordered in the increasing order of the Laplacian eigenvalues $\bLambda$. In a sense, the Laplacian
 eigenvalues correspond to the squared frequencies.
@@
 classical spherical harmonics giving us an indication that the graph is able to
-capture the spherical properties of the HealPix sampling. This topic is further discusses in Appendix~\ref{sec:spherical_harmonics}.
+capture the spherical properties of the Healpix sampling. This topic is further discussed in \ref{sec:spherical_harmonics}.
 
@@
 applied to the graph eigenvalues $\bLambda$. For visualization purposes, one can
-look at the effect of the convolution on a Kronecker, i.e. one column of the matrix
+look at the effect of the convolution on a Kronecker delta, i.e., one column of the matrix
 $h(\L)$. 
 Due to the non-regularity of the graph (i.e. the fact
-that there is not perfect sampling on the sphere), the convolution effect will slightly
+that there is no perfect sampling on the sphere), the convolution effect will slightly
 differ from one node to another. In the specific case of the full sphere, these
-differences are negligible in most of the cases. However, when considering only subpart of
+differences are negligible in most of the cases. However, when considering only parts of
 the sphere, one can observe important border effects.
+\todo{can we show those?}
 
@@
 time $t$. In \figref{gaussian_filters_visualization} of
-Appendix~\ref{sec:filter_visualization}, we show different visualizations of the
+\ref{sec:filter_visualization}, we show different visualizations of the
 convolution kernel $K_t$. We also compare the graph convolution with the
@@
 	\includegraphics[width=0.45\textwidth]{figures/pooling.pdf}
-	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarser cell covers $1/12$ of the sphere.}
+	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarsest cell covers $1/12$ of the sphere.}
 	\label{fig:pooling}
@@
 \includegraphics[width=0.45\textwidth]{figures/psd_sigma3.pdf}
-\caption{Power spectrum densities of the noiseless maps. The maps have be smoothed with a Gaussian kernel of radius $3$ arcmins in the preprocessing step.}
+\caption{Power spectrum densities of the noiseless maps.
+The maps have been smoothed with a Gaussian kernel of radius $3$ arcmins to remove high frequencies.
+The cosmological models could otherwise have been distinguished by looking at the PSDs.}
 \label{fig:psd_sigma3}
@@
 the noise. We stop adding new samples in the classifier once the validation
-error converge to a value. This process is detailled in Appendix~\ref{sec:dataset_augmentation}.
+error converge to a value. This process is detailed in \ref{sec:dataset_augmentation}.
 
@@
 of HealPix. For a detail, on how the convolution kernels are plot, please refer to
-Appendix~\ref{sec:filter_visualization}. 
+\ref{sec:filter_visualization}. 
 \todo{Tomek: can you say something about the filters.}
@@
 \includegraphics[width=0.95\textwidth]{figures/eigenvectors.pdf}
-\caption{12 first graph Fourier eigenvectors.
-Eigenvectors 1-3 could be assotiated to spherical harmonics of order 1, eigenvectors 4-8 to order 2 and 9-15 to order 3.
+\caption{The 16 first Fourier modes (eigenvectors of the graph Laplacian) of a graph constructed from the Healpix sampling of the sphere.
+Eigenvectors 1--3 could be associated to spherical harmonics of degree $\ell=1$, eigenvectors 4--8 to degree $\ell=2$, and eigenvectors 9--15 to degree $\ell=3$.
 Nevertheless, the graph eigenvectors are only approximating the real spherical harmonics.}

### 2018-07-04 scnn.tex
add some comments

@@
 Hence, we present a spherical CNN for analysis of full and partial Healpix maps, which we call HealpixNet.
+\nati{I am not that we should talk about pooling in the abstract.
+Another angle would be to say that HealPix sampling is well suited for spherical CNN with graphs as a) it is very regular => the graph capture well the spherical Manifold structure and b) pooling is natural.}
 While convolution on arbitrary graphs has mostly been sorted out, a general pooling operation has not been discovered so far. 
@@
 We demonstrate the method on a classification problem of mass maps from two cosmological models. 
-A standard benchmark for that problem is to train an SVM on the histograms of map pixel values.
-Another is to use the power spectral density instead.
+\nati{Should we specify what are the baselines? I think not.}
+A standard benchmark for that problem is to train an SVM on the histograms of map pixel values. Another is to use the power spectral density instead.
 HealpixNet achieves \todo{xx\%} better accuracy than those baselines, is more robust to noise, and is \todo{faster?}.
@@
 (it is also an advantage of our method to be agnostic to the sampling, which might be useful to researchers working with missing data or different models)}
+\nati{@Tomek: I think what Michael has in mind is that the graph approach is very versatile and extendable.
+It can be used with other samplings (even irregular ones) or only part of the sphere.
+This flexibility might be an advantage to mention.
+In particular, compared to~\citet{cohen2018spherical} it allows us to do only do the required computation when only a part of the sphere is considered.}
 
@@
 As such, perhaps the most straightforward approach to the analysis of spherical data is to divide it into small chunks and project those on flat 2D surfaces.
-While this mostly works, as demonstrated \todo{in ??? for example}, it is more natural and accurate to work directly on the sphere.
+While this mostly works, as demonstrated \todo{in ???
+for example}, \nati{@Tomek, do you have a citation for that?
+Otherwise, we need to reformulate this.} it is more natural and accurate to work directly on the sphere.
 
@@
 Our approach uses the graph CNN formulation introduced by \citet{defferrard2016convolutional}, which is efficient and can adapt to any sampling of the sphere.
-The convolution operation costs $\mathcal{O}(n)$ operations, where $n$ is the number of pixels.
+Using a k-nearest neigboors graph, the convolution operation costs $\mathcal{O}(n)$ operations, where $n$ is the number of pixels.
 That is the lowest possible complexity for convolution without approximations (e.g.
@@
 Results show that our model is better at discriminating the maps, is more resilient to noise, and \todo{is faster?}.
+\nati{I do not think we should argue for speed gain in this paper.
+We are probably much more efficient than scnns with the convolution done in the spectral domain.
+However compared to tradiationl methods, we are in most of the case slower.}
 
@@
 
-% About the the different sphere sampling.
-% \begin{itemize}
-% 	\item Define the spherical grid?
-% 	\item reference the "cubed sphere"~\cite{ronchi1996cubed}?
-% \end{itemize}
-
 \section{Related work}
@@
 
-\subsection{Spherical convolutions}
+\subsection{Spherical convolutions and spherical CNNs}
 \label{sec:spherical_conv}
@@
 to use the traditional 2-dimensional convolution on an irregular grid defined on the
-sphere. In the paper, two grids are used: the geodesic grid \todo{isn't it the equirectangular grid?} and the ``cubed
-sphere'' grid defined by~\citet{ronchi1996cubed}. Because this
+sphere. In the paper, two grids are used: the equirectangular grid and the ``cubed
+sphere'' grid defined by~\citet{ronchi1996cubed}. \nati{Do we need a plot of the equirectangular and cubed sphere sampling?} Because this
 approach is based on the traditional 2-dimensional convolution, it is very likely to be the
@@
 
-\todo{Cool to have a global illustration of the network (CNN like)}
+\subsection{Convolutions on graphs}
+\todo{Maybe we just describe convolutions on sphere and graph, i.e: do we really need all these three subsections? Maybe simply merge them?}
 
-\subsection{Convolutions on graphs}
+\nati{I think that citing Bruna is to much... According to me, the goal of this subsection should not be to cite everything that exist. But should focus on
+1) be fair and say that they are other graph convolutions that can be used, 2) show some connections between graph CNNs ang group equivariant CNNs (Done), and 3) suggest that they are possible extensions of what we do.}
+
 \assign{Michaël}
@@
 
-\todo{Maybe we just describe convolutions on sphere and graph, i.e: do we really need this two subsections? Maybe simply merge them?}
 \subsection{Convolutions on manifolds}

### 2018-07-05 scnn.tex
add comments + work on Appendix

@@
 Second, we propose to exploit a hierarchical pixelization of the sphere for the pooling operation.
-It allows the network to analyze the data at multiple scales while preserving the spatial localization of features.}
+It allows the network to analyze the data at multiple scales while preserving the spatial localization of features.
+    \nati{Great plot! Could you make the sphere round? If you use the current code in paper plot, they will be.}
+    }
 \end{figure*}
@@
 2-dimensional convolution, limiting the practical use of this approach.
-\todo{to have numbers to back up our claim: have the theoretical complexities and measure the time needed for a convolution on graph and the healpix Fourier transform to get the constants}
-While
-a comparison is theoretically possible, the experiments
+\todo{to have numbers to back up our claim: have the theoretical complexities and measure the time needed for a convolution on graph and the healpix Fourier transform to get the constants
+\nati{@mdeff: for the complexity we probably have $\mathcal{O}(n)$ instead of $\mathcal{O}(n^{3/2})$ (let assume that we have $\approx n^{1/2}$ points allong both axis, computation of the SO3 FFT is composed of 1) $n^{1/2}$ FFTs for a total cost of $n \log (n)$ and 2) $n^{1/2}$ matrix multiplications of size $n^{1/2}$ for a total cost of $n^{3/2}$)}
+}
+While a comparison is theoretically possible, the experiments
 of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and
@@
 cosmology as the data often observed only on a subpart of the sphere. 
+One could still pad the unused part of the sphere with 0. However, this would significantly increase the computational cost of the method.
+\nati{@mdeff: do you think we can say the method would be too slow for our dataset even without trying it? I am not so sure...}
 \todo{slow: full sky maps are composed of millions of points. partial maps are hard to process}
@@
 definition adapted to a cube and not to a sphere.
-\todo{border effects?}
+\todo{border effects? \nati{@mdeff what are you thinking about here?}}
 % \nati{Michael: Under some very
@@
 Another property of the HEALPix grid is that the pixel centers, represented by the black dots in \figref{pooling}, occur on a discrete number of rings of constant latitude (the number of which depends on the resolution).
+\nati{The figure is beautiful, but should we really show it?
+If we target cosmologists, we can simply list some type of data.
+If we target a more broad audience, maybe it makes sense to provide some illustration.}
 
@@
 \end{equation}
-\todo{why not $1/d$? See Pascal's paper}
+\todo{why not $1/d$?
+See Pascal's paper, \nati{ The question is: is $1/d$ also good when we have 7/8 neighboors instead of 4?
+Practically, we can also use $1/d$, but that means changing the code and re-runing the experiment.
+We probably do not have to change any parameter though...
+@mdeff: do you think we should try this for this paper?
+Or we keep that for the next one.}}
 Here $x_i$ is a 3-dimensional vector encoding the coordinate of the pixels $i$
@@
 differences are negligible in most of the cases. However, when considering only parts of
-the sphere, one can observe important border effects.
-\todo{can we show those?}
+the sphere, one can observe important border effects (See \figref{border_effects} in Appendix~\ref{sec:border_effects}). 
+\todo{can we show those?\nati{Sure I just added a figure in the Appendix.}}
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{figures/index_plotting_order20_nside16.pdf}
+\includegraphics[width=0.3\textwidth]{figures/index_plotting_order20_nside16.pdf}
 \caption{Indexes selected for the section ploting of \figref{gaussian_filters_visualization} middle. The delta was placed on the yellow node.}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{figures/hist_error_order4_noise1_5.pdf}
-\caption{TODO}
+\includegraphics[width=0.45\textwidth]{figures/hist_error_order2_noise1.pdf}
+\caption{Evolution curve of the error with respect of the number of training sample for histogram features and a linear classifier (setting: order 2, relative noise level: 1).
+The validation error is slightly below the training error because we use the validation set for the cross-validation and hence we are probably slightly overfitting the validation set.}
 \label{fig:hist_error_evolution}
+\end{figure}
+
+\section{Border effects when only a part of the sphere is considered.}
+\label{sec:border_effects}
+The graph setting used through this contribution assumes reflective border conditions on a grid.
+While the complete sphere is not affected by this because it has no border, these border effects change slightly the effect of the convolution when working with only a part of the graph.
+As depicted in \figref{border_effects}, the convolution of a Krnoneker near the border filters may no longer have a spherical profile.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.45\textwidth]{figures/border_effects.pdf}
+\caption{Graph convolution of a Kroneker placed at two different spots on the graph.
+The graph build from $1/12$ of the sphere and an Nside of 16.
+When the Kroneker is placed on the left corner, the resulting convolution is not circular anymore due to border effect.
+The graph setting assume reflective border conditions.}
+\label{fig:border_effects}
 \end{figure}

### 2018-07-05 scnn.tex
add first version of the conclusion

@@
 \label{sec:experiments}
+\assign{Nathanaël, Tomek}
 
@@
 \subsection{Results}
-\assign{Nathanaël, Tomek}
 
@@
 \subsection{Filter visualization} 
-\assign{Nathanaël, Tomek, Michaël} 
 Onecommon visualization for CNN is to display the shape of the learned filters.
@@
 \label{sec:conclusion}
-\assign{Nathanaël, Tomek, Michaël}
+
+In this contribution, we presented HealPixNet, a spherical CNN for the HealPix sampling. The gist of our construction reside in using a graph to model the sphere. 
+This allows us to leverage the advantages of graph convolution as it is both efficient $\mathcal{O}(n)$ and flexible (allow to work only on a subpart of the sphere) while still well capturing the spherical properties of the domain.
+We also show on a range of classification problems that the neural network systematically significantly outperform classical methods.
+
+We provide HealPixNet as a small easy to use package availlable at \todo{\url{https://github.com/xxx}}. 
+As a futur work, we intend to 1) further investigate the link between the graph Fourier basis and the spherical harmonic and 2) compare HealPixNet to other spherical CNN using different sampling schemes.
 
@@
 \centering
-\includegraphics[width=0.45\textwidth]{figures/hist_error_order2_noise1.pdf}
-\caption{Evolution curve of the error with respect of the number of training sample for histogram features and a linear classifier (setting: order 2, relative noise level: 1).
-The validation error is slightly below the training error because we use the validation set for the cross-validation and hence we are probably slightly overfitting the validation set.}
+\includegraphics[width=0.45\textwidth]{figures/hist_error_order2_noise1_5.pdf}
+\caption{Evolution curve of the error with respect of the number of training sample for histogram features and a linear classifier (setting: order 2, relative noise level: 1.5).
+The validation error might be slightly below the training error because we use it for cross-validation.}
 \label{fig:hist_error_evolution}

### 2018-07-05 scnn.tex
samll changes

@@
 Despite their successes, they still are mostly developed and applied to regular Euclidean domains such as those supporting images, audio, or video.
-For many applications however, the data domain is not regular.
+Unfortunately, in many applications, the data domain is not regular.
 As a response to that fact, we are witnessing an increasing interest in the generalization of CNNs to graphs.
@@
 \nati{I am not that we should talk about pooling in the abstract.
-Another angle would be to say that HealPix sampling is well suited for spherical CNN with graphs as a) it is very regular => the graph capture well the spherical Manifold structure and b) pooling is natural.}
-While convolution on arbitrary graphs has mostly been sorted out, a general pooling operation has not been discovered so far. 
+Another angle would be to say that HealPix sampling is well suited for spherical CNN with graphs as a) it is very regular => the graph capture well the spherical structure of the Manifold and b) pooling is natural.}
+While the convolution on arbitrary graphs has mostly been sorted out, a general pooling operation has not been discovered so far. 
 As such, while HealpixNet is a special case of a graph CNN, it is tailored to the Healpix sampling of the sphere.
-This approach is computationally much more efficient than using spherical harmonics to perform convolutions, an alternative that as been explored previously.
+This approach is computationally much more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
 % The filters learned by the HealpixNet are restricted to being radial.
@@
 \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+    \item make the bibliography display only a few name	
 \item (yes) Michael, do you agree with the title HealpixNet?
@@
 Ideally I'd like to have "graph" in the title (graph CNNs are quite hot these days), but I couldn't find how.
-    \item Emphasize the novelty of using it on Helapix in abstract, into and rest of the paper
+    \item Emphasize the novelty of using it on Healpix in abstract, into and rest of the paper
+    \item add info on comparison with histograms, so that it's just a demonstration
     \item Finish section on Convolutions on graphs (Michael - Nathanael)
-    \item Plot of the new filters from Mass maps (Michael)
+    \item finish section on Efficient convolutions (Michael)
+    \item (done) Plot of the new filters from Mass maps
     \item (done!, plot to be added) check the power spectrum after smoothing
     \item (done!) upgrade the plot of pooling (Nathanael)
-	\item (done!) new plot for network structure (teaser plot) (Michael) What do you think? Todo: link the points on the sphere to the fully connected
-    \item add info on comparison with histogram, so that it's just a demonstration
+	\item (done!) new plot for network structure (teaser plot) (Michael) What do you think?
+Todo: link the points on the sphere to the fully connected \nati{I like the plot, but I am thinking about putting multiple spheres with different maps for the convolutiion instead…}
     \item (done!) Figure 1 to be round
-    \item finish section on Efficient convolutions (Michael)
-    \item conclusions
+    \item (first version done) conclusions
     \item (done!) new simulations with 3 arcmin smoothing
@@
 A convolutional layer is based on five operations: convolution, non-linearity, batch normalization, down-sampling, and pooling.
-While most operations are agnostic to the data domain, the convolution and down-sampling have to be adapted.
+While most operations are agnostic to the data domain, the convolution and the down-sampling have to be adapted.
 In this paper, we propose first to model the sphere with a graph and to perform the convolution on the graph.
@@
 It allows the network to analyze the data at multiple scales while preserving the spatial localization of features.
-    \nati{Great plot! Could you make the sphere round? If you use the current code in paper plot, they will be.}
+    \nati{Great plot! Could you make the sphere round? If you use the current code in paper plot notebook, they will be.}
     }
@@
 Using a k-nearest neigboors graph, the convolution operation costs $\mathcal{O}(n)$ operations, where $n$ is the number of pixels.
-That is the lowest possible complexity for convolution without approximations (e.g.
+This is the lowest possible complexity for a convolution operation without approximations (e.g.
 by sketching).
@@
 We compare the performance of the spherical CNN to a baseline algorithm, an SVM classifier which takes pixel histograms or Power Spectrum Densities (PSD) of these maps as input.
-The comparison is made as a function of noise level on convergence maps and area of the sphere used.
+The comparison is made as a function of the noise level on convergence maps and the area of the sphere used.
 Results show that our model is better at discriminating the maps, is more resilient to noise, and \todo{is faster?}.
@@
 We are probably much more efficient than scnns with the convolution done in the spectral domain.
-However compared to tradiationl methods, we are in most of the case slower.}
+However compared to tradiational methods, we are in most of the cases slower.}
 
@@
 \todo{to have numbers to back up our claim: have the theoretical complexities and measure the time needed for a convolution on graph and the healpix Fourier transform to get the constants
-\nati{@mdeff: for the complexity we probably have $\mathcal{O}(n)$ instead of $\mathcal{O}(n^{3/2})$ (let assume that we have $\approx n^{1/2}$ points allong both axis, computation of the SO3 FFT is composed of 1) $n^{1/2}$ FFTs for a total cost of $n \log (n)$ and 2) $n^{1/2}$ matrix multiplications of size $n^{1/2}$ for a total cost of $n^{3/2}$)}
+\nati{@mdeff: for the complexity we probably have $\mathcal{O}(n)$ instead of $\mathcal{O}(n^{3/2})$ (let assume that we have $\approx n^{1/2}$ points allong both axis, computation of the SO3 FFT is composed of 1) $n^{1/2}$ FFTs for a total cost of $n \log (n)$ and 2) $n^{1/2}$ matrix multiplications of size $n^{1/2}$ for a total cost of $n^{3/2}$) For the number, it is a bit more complicated… I guess it is for the next paper.}
 }
@@
 
-In an attempt to get the best of the two first approaches, we follow a third
+In an attempt to get the best of the first two approaches, we follow a third
 direction. We use a graph to adapt to the particular structure of the sphere.
@@
 differences. First the sampling is different as~\cite{khasanova2017graph} uses a
-grid. Second, it uses a different graph CNN based on a different parametrization
+grid. Second, it uses a different graph CNN based on a different parameterization
 of the convolution kernel.
@@
 If we target cosmologists, we can simply list some type of data.
-If we target a more broad audience, maybe it makes sense to provide some illustration.}
+If we target a broader audience, maybe it makes sense to provide some illustration.}
 
@@
 
-In the classical 2-dimenstional convolution, each pixel is connected with the
+In the classical 2-dimensional convolution, each pixel is connected with the
 same weight to its 4 closest neighbors. We use a weighted undirected graph to
@@
 \caption{
-Top view of a Healpix graph for half the sphere using an nside parameter of $4$.
+Top view of a Healpix graph for half the sphere using a HealPix nside parameter of $4$.
 Nodes with 7 neighbors are highlighted. \label{fig:healpix_graph_4}
@@
 classical spherical harmonics giving us an indication that the graph is able to
-capture the spherical properties of the Healpix sampling. This topic is further discussed in \ref{sec:spherical_harmonics}.
+capture the spherical properties of the Healpix sampling. This topic is further discussed in Appendix~\ref{sec:spherical_harmonics}.
 
@@
 \end{equation}
-which is a convolution of the signal $\b{f}(0)$ with the kernel $K_t(x)=e^{-\tau
-t x}$. Here the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$ that
-are one generalization of the squared frequencies on the graph. Hence the kernel $K_t$ is also a generalization of the
+which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(x)=e^{-\tau
+t x}$.
+Here the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$.
+They are a generalization of the squared frequencies in the graph setting.
+Hence the kernel $K_t$ can also be considered as a generalization of the
 Gaussian kernel on the sphere. In \figref{gaussian_filters_comparizon} top, we show
 the effect of the convolution by diffusing a unit of heat for $\tau=1$ and various
-time $t$. In \figref{gaussian_filters_visualization} of
-\ref{sec:filter_visualization}, we show different visualizations of the
-convolution kernel $K_t$. We also compare the graph convolution with the
+time $t$. We also compare the graph convolution with the
 spherical symmetric Gaussian smoothing
@@
 parameterization, well approximate it.
+In~\figref{gaussian_filters_visualization} of Appendix~\ref{sec:filter_visualization}, we provide additional visualizations of the
+convolution kernel $K_t$.
 

### 2018-07-05 scnn.tex
lots of changes in the result section

@@
 % 4) Describe the result
-In this section, we demonstrate the performance of the spherical neural network on a discrimination problem.
+In this section, we demonstrate the performance of the spherical neural network on a discrimination problem. Nevertheless, by simply changing the loss, one could use the network for regression.
 Our implementation is available as a small python package \url{https://our.code.link.com}.
-Furthermore, all the data to reproduce our experiments are available online.\footnote{\url{https://doi.org/10.5281/zenodo.????} \todo{correct DOI}}.
+Furthermore, all the data to reproduce our experiments are available online.\footnote{\url{https://doi.org/10.5281/zenodo.1303272} \todo{Check DOI}}.
 
-In our experiment we classify convergence maps, similar to those created with gravitational lensing technique \citep{chang2017curvedsky}.
+In our experiments we classify convergence maps, similar to those created with gravitational lensing technique \citep{chang2017curvedsky}.
 
@@
 As a simulator we use \pkg{L-PICOLA} \citep{howlett2015lpicola}, a fast and approximate code for N-body simulations.
-For each class, we generate 30 simulations.
+For each class, we generate $30$ simulations (both class have the same initial parameters).
 
-Out of the 60 simulations, 20 are kept for the test set.
+Out of the $60$ simulations, $20$ are kept for the test set.
 \figref{map_sample} shows the full sky simulations and a zoom region for model 1 (top) and model 2 (bottom).
@@
 \subsection{Problem formulation}
-While the number of maps might sound small for deep learning, the information contained in the maps is very recurrent, allowing us to use parts of the map as sample for our simulation.
+While the number of maps might sound small for deep learning, the information contained in the maps is very recurrent, allowing us to use parts of the map as samples for our simulation.
 Leveraging the properties of the HealPix sampling, we can split each maps
@@
 
-The goal is build a robust classifier, i.e. an automatic way to
+We build a robust classifier, i.e. an automatic way to
 discriminate between the two classes in the presence of noise. 
-We check the performance of the classifier as a function of the area used, i.e "the order" $o$ and also as a function of the relative level of the noise.
+We check the classification performance as a function of the area used, i.e "the order" $o$ and also as a function of the relative level of the noise added to the map.
 
@@
 overfitting, the noise is randomly produced during the training process. We trained our
-model between \nati{$50$ and $200$} epochs depending on the complexity and the size of
-the problem. The testing set was simply used to assess the global performance of
-the network and to assess if it was overfitting.
-Training took less that a day for each model using a Nvidia 1080 TI.
+model between $50$ and $290$ epochs depending on the complexity and the size of
+the problem. $20\%$ of the training set that we call "validation set" was left out of the training process and simply used to assess the global performance and overfitting of
+the network.
+Training took less than a day for each model using an NVIDIA Tesla K20.
 
-We compare the performance of the spherical CNN to two simple benchmark
+We compare the performance of the spherical CNN against two simple benchmark
 algorithms. The two baselines are based on building features with a) the Power
-Spectral Densities or b) the histogram of pixels in the maps~\cite{patton2017cosmologicalconstraints}.
+Spectral Densities (PSD) and b) the histogram of pixels in the maps~\cite{patton2017cosmologicalconstraints}.
 After a normalization, those features are then classified use a Support Vector
-Machine (SVM) with a linear kernel. Other kernels did not provide better result
+Machine (SVM) with a linear kernel. Other kernels did not provide better results
 while having worse scaling properties. All classifiers are trained with noisy samples. For fairness, we augmented the dataset
@@
 the noise. We stop adding new samples in the classifier once the validation
-error converge to a value. This process is detailed in \ref{sec:dataset_augmentation}.
-
-The maps are separated into a training and a testing set. The performance is
-assessed by measuring the classification error on a test set. Once the
-training maps are sliced into samples, we split them into a training samples
-and validation samples. The validation samples is used to tune the
-regularization parameter of the SVM using a standard cross-validation
-technique.
+error converge to a value. This process is detailed in Appendix~\ref{sec:dataset_augmentation}. We tuned the parameter using cross-validation with the validation set.
 
@@
 We present in \figref{results} the results for 5 different noise
-levels and $3$ different data sizes.  We observe that the PSD features, i.e.
-one of the most used technique for model discrimination in cosmology is unable
-to perform the desired task. The main reason is that the two different model
+levels and $3$ different sample areas. The spherical CNN has a significant lead for all levels of noise and sample areas. 
+In particular, the difference seems to increase as the problem becomes more complex, i.e as the order is increased and there is less information in each sample. 
+This is likely due to the fact that the SCNN can learn optimal features for the problem and do not rely on our humanly limited feature design.
+
+We observe that the PSD features, i.e.
+one of the most used techniques for model discrimination in cosmology, is unable
+to perform the desired task. The main reason is that the two different models
 have very similar PSDs (see \figref{psd_sigma3}). As a result, one
-need to use other statistics to solve the problem. In this case, we use
-histogram features and observe a significant improvement over the PSD.  The
-SCNN present the advantage to learn automatically specific features for the
-task and also the usual Deep Learning performance bump.
-
-We also note that the histogram features contains information about the
-distribution of pixels, but does not include any spatial information. In
+needs to use other statistics to solve the problem. In this case, the
+histogram features that have been built for the problem allow for a significant improvement over the PSD ones. 
+Unfortunately, while the histogram features contain information about the
+distribution of pixels, they do not include any spatial information. In
 contrast, both the PSD features and the SCNN can exploit the spatial
-information. Without this scructure, a non scallable fully connected neural network approach would have to be used.
+information. 
+Note that without this graph structure, a fully connected neural network approach would have to be used. Problematically, fully connected neural networks do not scale well with the number of pixels.
 
@@
 \subsection{Filter visualization} 
-Onecommon visualization for CNN is to display the shape of the learned filters.
-Since our construction lead to almost (up to the sampling irregularities)
+One common visualization for CNN is to observe the shape of the learned filters.
+Since our construction leads to almost (up to the sampling irregularities)
 spherical filters, we plot in \figref{learned_filter} both the section (on the
-sphere) and a gnomeview projection on a plane of a random selection of learned
+sphere) and a gnomonic projection on a plane of a random selection of learned
 filters. The filters are selected from the last layer of the network
@@
 human perspective. The gnomonic projection clearly exibits the sampling issue
-of HealPix. For a detail, on how the convolution kernels are plot, please refer to
-\ref{sec:filter_visualization}. 
+of HealPix. For a detail, on how the convolution kernels are plotted, please refer to Appendix~\ref{sec:filter_visualization}. 
 \todo{Tomek: can you say something about the filters.}
@@
 
+\nati{Should the discussion be merged with the result section?}
+
 \section{Conclusion}
@@
 
-In this contribution, we presented HealPixNet, a spherical CNN for the HealPix sampling. The gist of our construction reside in using a graph to model the sphere. 
-This allows us to leverage the advantages of graph convolution as it is both efficient $\mathcal{O}(n)$ and flexible (allow to work only on a subpart of the sphere) while still well capturing the spherical properties of the domain.
+In this contribution, we presented HealPixNet, a spherical CNN for the HealPix sampling. The gist of our construction resides in using a graph to model the sphere. 
+This allows us to leverage the advantages of the graph convolution, i.e it is both efficient (with a complexity of $\mathcal{O}(n)$) and flexible (allow to work only on a subpart of the sphere) while it still captures well the spherical properties of the domain.
 We also show on a range of classification problems that the neural network systematically significantly outperform classical methods.
 
-We provide HealPixNet as a small easy to use package availlable at \todo{\url{https://github.com/xxx}}. 
-As a futur work, we intend to 1) further investigate the link between the graph Fourier basis and the spherical harmonic and 2) compare HealPixNet to other spherical CNN using different sampling schemes.
+We provide HealPixNet as a small easy-to-use package available at \todo{\url{https://github.com/xxx}}. 
+As a future work, we intend to 1) further investigate the link between the graph Fourier basis and the spherical harmonic and 2) compare HealPixNet to other spherical CNN using different sampling schemes.
 
@@
 \ref{fig:graph_harmonics} displays the first 16 eigenvectors of the
-graph Fourier basis used for the convolution. While their is a clear
+graph Fourier basis used for the convolution. While there is a clear
 resemblance with the spherical harmonic, the small irregularities in the
@@
 of the sphere.  Second, as Nside increase toward infinity and hence the number
-of pixel $n\rightarrow \infty$, we are still unsure if the graph eigenvectors
+of pixels $n\rightarrow \infty$, we are still unsure if the graph eigenvectors
 converge toward the spherical harmonics. We believe that it might be the case
@@
 \includegraphics[width=0.95\textwidth]{figures/eigenvectors.pdf}
-\caption{The 16 first Fourier modes (eigenvectors of the graph Laplacian) of a graph constructed from the Healpix sampling of the sphere.
-Eigenvectors 1--3 could be associated to spherical harmonics of degree $\ell=1$, eigenvectors 4--8 to degree $\ell=2$, and eigenvectors 9--15 to degree $\ell=3$.
+\caption{The first 16 Fourier modes (eigenvectors of the graph Laplacian) of a graph constructed from the Healpix sampling of the sphere.
+Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$, eigenvectors 4--8 with degree $\ell=2$, and eigenvectors 9--15 with degree $\ell=3$.
 Nevertheless, the graph eigenvectors are only approximating the real spherical harmonics.}
@@
 In \figref{gaussian_filters_visualization}, we present three different
-visualization for the a healpix graph convolution kernel.
+visualization for a HealPix graph convolution kernel.
 The kernel used is defined in the graph spectral domain as $K_t(x)=e^{-\tau t x}$.
@@
 Kroneker on the sphere plot the result with gnomonic projection. Eventually, as we are
-working on the sphere with theoretically spherical filters (up the the irregularities of the sampling), we could only plot the section of the convoluted Kroneker.
+working on the sphere with theoretically spherical filters (up to the irregularities of the sampling), we could only plot the section of the convoluted Kroneker.
 To do so, we convolve a Kroneker on the equator and use the equator for our section as shown in~\figref{index_section}.
 Note that, because of the small irregularities in the HealPix
-sampling, the second and the third methods are subject to small varation depending on the
+sampling, the second and the third methods are subject to small variations depending on the
 chosen Kroneker.
@@
 access to the same amount of data that the network, i.e, potentially an
-infinite number of sample. Hence, we fit different linear SVM classifier using
-various amount of training set size until we oberve experimentally that
+infinite number of samples. Hence, we fit different linear SVM classifier using
+various training set size until we observe experimentally that
 increasing the amount of data does not improve the classifier. The validation
@@
 the testing set. An example of the evolution of the training and valdication
-error is show in \figref{hist_error_evolution}.
+error is shown in \figref{hist_error_evolution}.
 
@@
 \includegraphics[width=0.45\textwidth]{figures/hist_error_order2_noise1_5.pdf}
-\caption{Evolution curve of the error with respect of the number of training sample for histogram features and a linear classifier (setting: order 2, relative noise level: 1.5).
+\caption{Evolution curve of the error with respect to the number of training samples for histogram features and a linear classifier (setting: order 2, relative noise level: 1.5).
 The validation error might be slightly below the training error because we use it for cross-validation.}
@@
 When the Kroneker is placed on the left corner, the resulting convolution is not circular anymore due to border effect.
-The graph setting assume reflective border conditions.}
+The graph setting assumes reflective border conditions.}
 \label{fig:border_effects}

### 2018-07-06 scnn.tex
modified abstract

@@
 Convolutional Neural Networks (CNNs) are now a cornerstone of the Deep Learning toolbox and have led to many breakthroughs in Artificial Intelligence.
-Despite their successes, they still are mostly developed and applied to regular Euclidean domains such as those supporting images, audio, or video.
-Unfortunately, in many applications, the data domain is not regular.
-As a response to that fact, we are witnessing an increasing interest in the generalization of CNNs to graphs.
+These networks have so far been developed mostly for regular Euclidean domains such as those supporting images, audio, or video.
+CNN-based methods are becoming increasingly popular in Cosmology.
+Cosmological data often comes in a form of spherical maps, which makes the use of CNNs more complicated.
+A popular format for spherical maps is Healpix, which uses an equal-area, isolatitude sampling.
+We present a spherical CNN for analysis of full and partial Healpix maps, which we call HealpixNet.
+We construct a spherical CNNs by representing the sphere as a graph.
 Graphs are versatile data structures which can represent pairwise relationships between objects or act as a discrete representation of a continuous manifold.
-In this paper we take the latter view and represent a sampled sphere as a graph, for which we define the convolution and pooling operations.
-Spherical maps appear in many applications, such as the study of phenomena on the Earth for meteorologists or on the sky for cosmologists.
-A popular format for spherical maps is Healpix, which uses an equal-area, isolatitude sampling.
-Hence, we present a spherical CNN for analysis of full and partial Healpix maps, which we call HealpixNet.
-\nati{I am not that we should talk about pooling in the abstract.
+For that graph, we define many of the standard CNN operations, such as convolution and pooling, with the filters restricted to being radial.
+HealpixNet is a special case of a graph CNN, tailored to the Healpix sampling of the sphere.
+This approach is computationally more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
+We demonstrate the method on a classification problem of mass maps from two cosmological models.
+We compare the performance of the CNN with that of two baseline classifiers, based on the power spectrum and pixel density histogram.
+We find the performance of HealpixNet to always better or equal to both of these baselines.
+For high noise levels and for data covering only a smaller fraction of the sphere, HealpixNet achieves typically 10\% better classification accuracy than those baselines.
+Finally, we visualise filters learned by the HealpixNet from the mass maps.
+Code and examples are available at \todo{\url{https://github.com/xxx}}.
+
+%As a response to that fact, we are witnessing an increasing interest in the generalization of CNNs to graphs.
+% Graphs are versatile data structures which can represent pairwise relationships between objects or act as a discrete representation of a continuous manifold.
+% In this paper we take the latter view and represent a sampled sphere as a graph, for which we define the convolution and pooling operations.
+% Spherical maps appear in many applications, such as the study of phenomena on the Earth for meteorologists or on the sky for cosmologists.
+% A popular format for spherical maps is Healpix, which uses an equal-area, isolatitude sampling.
+% Hence, we present a spherical CNN for analysis of full and partial Healpix maps, which we call HealpixNet.
+% \nati{I am not that we should talk about pooling in the abstract.
 Another angle would be to say that HealPix sampling is well suited for spherical CNN with graphs as a) it is very regular => the graph capture well the spherical structure of the Manifold and b) pooling is natural.}
-While the convolution on arbitrary graphs has mostly been sorted out, a general pooling operation has not been discovered so far. 
-As such, while HealpixNet is a special case of a graph CNN, it is tailored to the Healpix sampling of the sphere.
-This approach is computationally much more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
+% While the convolution on arbitrary graphs has mostly been sorted out, a general pooling operation has not been discovered so far.
+% As such, while HealpixNet is a special case of a graph CNN, it is tailored to the Healpix sampling of the sphere.
+% This approach is computationally much more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
 % The filters learned by the HealpixNet are restricted to being radial.
 % Michaël: not necessary in the abstract?
-We demonstrate the method on a classification problem of mass maps from two cosmological models. 
-\nati{Should we specify what are the baselines? I think not.}
-A standard benchmark for that problem is to train an SVM on the histograms of map pixel values. Another is to use the power spectral density instead.
-HealpixNet achieves \todo{xx\%} better accuracy than those baselines, is more robust to noise, and is \todo{faster?}.
-Code and examples are available at \todo{\url{https://github.com/xxx}}.
+% We demonstrate the method on a classification problem of mass maps from two cosmological models.
+% \nati{Should we specify what are the baselines? I think not.}
+% A standard benchmark for that problem is to train an SVM on the histograms of map pixel values. Another is to use the power spectral density instead.
+% HealpixNet achieves \todo{xx\%} better accuracy than those baselines, is more robust to noise, and is \todo{faster?}.
+% Code and examples are available at \todo{\url{https://github.com/xxx}}.
 \end{abstract}

### 2018-07-06 scnn.tex
update todo

@@
 HealpixNet is a special case of a graph CNN, tailored to the Healpix sampling of the sphere.
-This approach is computationally more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
+% TBD if we include it
+% This approach is computationally more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
 We demonstrate the method on a classification problem of mass maps from two cosmological models.
@@
 Finally, we visualise filters learned by the HealpixNet from the mass maps.
-Code and examples are available at \todo{\url{https://github.com/xxx}}.
+Code and examples are available at \todo{\url{github.com/SwissDataScienceCenter/HealpixNet}}.
 
@@
 \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-    \item make the bibliography display only a few name
-\item (yes) Michael, do you agree with the title HealpixNet?
+
+    \item (TK) update the README for data zip - file from NP
+    \item Finalise readme on Github code
+    \item TK check part sphere notebook and whole sphere
+    \item branch with notebooks with plots (results) NP
+    \item Michael section 4.5 (efficient convolutions) and 3.2 (conv on graphs)
+    \item NP move the repo to HealpixNet
+
+    \item (TK) make the bibliography display only a few name
+    % \item (yes) Michael, do you agree with the title HealpixNet?
 I (Michaël) extensively modified the abstract to reflect that it is a special case of graph CNNs tailored to Healpix.
@@
 Ideally I'd like to have "graph" in the title (graph CNNs are quite hot these days), but I couldn't find how.
-    \item Emphasize the novelty of using it on Healpix in abstract, into and rest of the paper
-    \item add info on comparison with histograms, so that it's just a demonstration
-    \item Finish section on Convolutions on graphs (Michael - Nathanael)
-    \item finish section on Efficient convolutions (Michael)
-    \item (done) Plot of the new filters from Mass maps
-    \item (done!, plot to be added) check the power spectrum after smoothing
-    \item (done!) upgrade the plot of pooling (Nathanael)
-	\item (done!) new plot for network structure (teaser plot) (Michael) What do you think?
+    % \item Emphasize the novelty of using it on Healpix in abstract, into and rest of the paper
+    \item (TK) add info on comparison with histograms, so that it's just a demonstration
+    % \item Finish section on Convolutions on graphs (Michael - Nathanael)
+    % \item finish section on Efficient convolutions (Michael)
+    % \item (done) Plot of the new filters from Mass maps
+    % \item (done!, plot to be added) check the power spectrum after smoothing
+    % \item (done!) upgrade the plot of pooling (Nathanael)
+    \item (TK) possibly improve plot of pooling
+	% \item (done!) new plot for network structure (teaser plot) (Michael) What do you think?
 Todo: link the points on the sphere to the fully connected \nati{I like the plot, but I am thinking about putting multiple spheres with different maps for the convolutiion instead…}
-    \item (done!) Figure 1 to be round
+    \item (TK NP) if we have time make a new candidate for network plot (optional)
+    % \item (done!) Figure 1 to be round
     \item (first version done) conclusions
-    \item (done!) new simulations with 3 arcmin smoothing
-    \item (done!) simulation with cross-validation for the histogram
-    \item (done!) Update result section according to the new simulations...
-    \item (done!) simulation PSD
-    \item (done!) Results figure, add sigma8
-    \item (more or less done!) possibly move the eigen decomposition and heat into appendix + add discussion (Nathanael I am not sure about the heat diffusion example...)
+    % \item (done!) new simulations with 3 arcmin smoothing
+    % \item (done!) simulation with cross-validation for the histogram
+    % \item (done!) Update result section according to the new simulations...
+    % \item (done!) simulation PSD
+    % \item (done!) Results figure, add sigma8
+    % \item (more or less done!) possibly move the eigen decomposition and heat into appendix + add discussion (Nathanael I am not sure about the heat diffusion example...)
+    \item Should the heat example go to appendix
+    \item TK read the heat section again
+
 \end{itemize}
@@
 The flexibility of modeling the data domain with a graph allows, for example, to easily model data which only spans a part of the sphere, or data which is not uniformly sampled.
-Our hierarchical pooling strategy exploits a hierarchical pixelization of the manifold to analyze the data at multiple scales. Such hierarchical pixelizations of the sphere have been well studied.
+Our hierarchical pooling strategy exploits a hierarchical pixelization of the manifold to analyze the data at multiple scales.
+% Such hierarchical pixelizations of the sphere have been well studied.
+sdfsdfsd Such hierarchical pixelizations of the sphere have been well studied.
+%TK: chagned becasue of blahblah
 

### 2018-07-08 scnn.tex
update todolist
some edits of healpix sampling

@@
     \item (TK) update the README for data zip - file from NP
-    \item Finalise readme on Github code
+    \item (NP) Finalise readme on Github code
+    \item (NP) Finalize the data on zenodo
+    \item (NP) Do the download script
     \item TK check part sphere notebook and whole sphere
@@
     \item TK read the heat section again
-
+    \item TK read the result section
+    \item TK check the appendix
+    \item TK optional - example of data (CMB (mask) + mass map + radio intensity)
+    \item TK read everything
 \end{itemize}
@@
 Before doing any numerical analysis on the sphere, one first has to choose a tessellation, i.e., an exhaustive partition of the sphere into finite area elements, where the data under study is quantized.
+The simplicity of the spherical form belies the intricacy of global analysis on the sphere.
+There is no known point set which achieves the analogue of uniform sampling in Euclidean space and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions.
+Any existing proposition of practical schemes for the discrete treatment of such functions on the sphere introduces some systematic error dependent on the global properties of the point set.
 While our method is applicable to any pixelization of the sphere, two details depend on the chosen sampling: (i) the choice of neighbors in the construction of the graph, and (ii) the choice of parent nodes when coarsening the graph.
@@
 HEALPix is an acronym for Hierarchical Equal Area isoLatitude Pixelization of a sphere.
-As suggested in the name, this pixelization produces a subdivision of a spherical surface in which each pixel covers the same surface area as every other pixel.
+As suggested in the name, this pixelization produces a hierarchical subdivision of a spherical surface in which each pixel covers the same surface area as every other pixel.
+A hierarchy is desired for data locality in computer memory.
+Equal area is advantageous because white noise generated by the signal receiver gets integrated exactly into white noise in the pixel space.
+Isolatitude is essential for the implementation of a fast spherical transform.
+HEALPix is the sole pixelization scheme which satisfies those three properties.
+
 The lowest possible resolution is given by the base partitioning of the surface into $N_{pix} = 12$ equal sized pixels (right-most sphere in \figref{pooling}).
@@
 High-resolutions HEALPix maps easily reach millions of pixels. \figref{example_maps} shows two examples.
-Another property of the HEALPix grid is that the pixel centers, represented by the black dots in \figref{pooling}, occur on a discrete number of rings of constant latitude (the number of which depends on the resolution).
 \nati{The figure is beautiful, but should we really show it?
@@
 Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$, eigenvectors 4--8 with degree $\ell=2$, and eigenvectors 9--15 with degree $\ell=3$.
-Nevertheless, the graph eigenvectors are only approximating the real spherical harmonics.}
+Nevertheless, the graph eigenvectors are only approximating the real spherical harmonics.
+\todo{show group of eigenvectors as indication of mode $\ell$.
+Either show eigenvalues on this plot or add a plot of the eigenvalues themselves.}}
 \label{fig:graph_harmonics}

### 2018-07-12 scnn.tex
edits to the method

@@
 \newcommand{\U}{\b{U}}
+\newcommand{\R}{\mathbb{R}}
 \newcommand{\bLambda}{\b{\Lambda}}
@@
     }
+	\label{fig:architecture}
 \end{figure*}
@@
 Our hierarchical pooling strategy exploits a hierarchical pixelization of the manifold to analyze the data at multiple scales.
-% Such hierarchical pixelizations of the sphere have been well studied.
-sdfsdfsd Such hierarchical pixelizations of the sphere have been well studied.
-%TK: chagned becasue of blahblah
+Such hierarchical pixelizations of the sphere have been well studied.
 
@@
 
+% As presented by~\cite{cohen2018spherical}, the most mathematical approach to extend the convolution on a sphere is to use a spherical Fourier transform.
+The convolution is then simply defined as the product in the spectral domain.
+This approach requires one Fourier and one inverse Fourier transform per convolution which remain, even with accelerated algorithms, expensive.
+
 The first approach, leveraging the continuous spherical convolution, has been
-proposed by~\cite{cohen2017convolutional,cohen2018spherical}. The goal of
+proposed by~\cite{cohen2018spherical}. The goal of
 these contributions it to use a rotational equivariant convolution on the
@@
 
-The gist of our method is to define the convolution on a sphere using a graph.
-The graph is here seen as a discrete approximation of the sphere $S^2$, a
-2-dimensional manifold embedded in $\mathbb{R}^3$.
+\todo{Should we give a more general / high-level description of a CNN?}
 
-As presented by~\cite{cohen2018spherical}, the most mathematical approach to
-extend the convolution on a sphere is to use a spherical Fourier transform. The
-convolution is then simply defined as the product in the spectral domain. This
-approach requires one Fourier and one inverse Fourier transform per convolution
-which remain, even with accelerated algorithms, expensive. For 2-dimensional
-images, an efficient convolution can be achieved when the convolution kernel is
-localized (for example a 5x5 pixel patch) by doing the computation directly in
-the signal domain. Unfortunately, this approach cannot be directly extended to
-the spherical case. Hence, the main idea of this contribution is to leverage
-graph signal processing~\cite{shuman2013emerging} to define a spherical
-convolution that can be computed (and back-propagated) directly in the signal domain.
+A CNN is composed of the following main building blocks~\citep{lecun1998cnn}, illustrated in~\figref{architecture}: (i) a convolution, (ii) a non-linearity, (iii) a down-sampling operation, (iv) a pooling operation, and (v), optionally, some normalization.\footnote{A batch normalization has been shown to help the training.~\citep{ioffe2015batchnorm} We have verified this experimentally in our setting as well.} As operations (ii) and (v) are point-wise, they do not depend on the data domain.
+The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either.
+The convolution and down-sampling operations however need to be generalized from Euclidean domains to the sphere.
+
+On regular Euclidean domains, such as 1-dimensional time series or 2-dimensional images, a convolution can be efficiently implemented by sliding a localized convolution kernel (for example a patch 5x5 pixels) in the signal domain.
+Likewise, down-sampling can be achieved by taking one pixel out of $n$.
+Because of the irregular sampling, there is no straightforward way to define a convolution on the sphere directly in the pixel domain.
+
+We will hence make a detour by the spectrum to perform the convolution.\footnote{Note that we only use the spectrum to define the convolution.
+The implementation however does not need a direct access to the spectrum, which is much more computationally efficient.
+See \secref{sec:efficient_convolution}.}
+The gist of our method is to define the convolution on a sphere using a graph, and the down-sampling using a hierarchical pixelization of the sphere.
+This contribution leverages the emerging field of graph signal processing~\citep{shuman2013emerging} which defines fundamental signal processing tools such as the Fourier transform for signals defined on graphs.
 
@@
 }
-
 \end{figure}
@@
 \subsection{Graph Fourier basis and spherical harmonics}
-\todo{Add a few extra references}
-
-Because of the irregular sampling, there is no obvious way to define the convolution
-directly from the pixel values. Hence we will first make a detour and define a Fourier transform on the
-graph.
 
@@
 \subsection{Convolutions on graphs}
-\assign{Nathanaël, Michaël} \todo{Add a few extra references}
 
-Graph convolution is defined by generalizing the concept that convolution is a
+A convolution can be defined on graphs by the convolution theorem which states that a convolution in the vertex (or time, or spatial) domain is a
 multiplication in the spectral domain. Given a convolution kernel
-$h:\mathbb{R}_+\rightarrow\mathbb{R}$, the convolution of a signal $\b{f}$
+$h: \R_+ \rightarrow \R$, the convolution of a signal $\b{f}$
 is defined as
@@
 differences are negligible in most of the cases. However, when considering only parts of
-the sphere, one can observe important border effects (See \figref{border_effects} in Appendix~\ref{sec:border_effects}).
-\todo{can we show those?\nati{Sure I just added a figure in the Appendix.}}
+the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).
 
@@
 \subsection{Efficient convolutions}
+\label{sec:efficient_convolution}
 \assign{Michaël}
+
+Transition from spectral to spatial domain.
+
 With the Fourier basis. Because we don't have an FFT, that costs $O(n^3)$ for the eigendecomposition, plus $O(n^2)$ for the transform (to be done for each forward and backward pass).
@@
 Hierarchical pixelization schemes present a natural coarsening.
-Indeed, each subdivision divides a cell in an equal number of sub-cells.
-Coarsening is the reverse operation: merging the sub-cells to summarize the data supported on them.
+Indeed, each subdivision divides a cell in an equal number of child sub-cells.
+Coarsening is the reverse operation: merging the sub-cells toward the goal of summarizing the data supported on them.
 Merging cells lead to a coarser graph, hence the name coarsening.
-Pooling refers to the operation that summarizes the data supported on the merged sub-cells in one child cell.
-That operation is often taken as the maximum value, but it might be any permutation invariant operation such as the sum or the average.
+
+Pooling refers to the operation that summarizes the data supported on the merged sub-cells in one parent cell.
+That operation is often taken to be the maximum value, but it might be any permutation invariant operation such as the sum or the average.
 \figref{pooling} illustrates the process.

### 2018-07-13 scnn.tex
method: graph construction

@@
 \newcommand{\g}[1]{\b{#1}}
+\newcommand{\G}{\mathcal{G}}
+\newcommand{\V}{\mathcal{V}}
+\newcommand{\E}{\mathcal{E}}
 \renewcommand{\L}{\b{L}} % the laplacian matrix
@@
 \newcommand{\U}{\b{U}}
+\newcommand{\x}{\b{x}}
 \newcommand{\R}{\mathbb{R}}
@@
 Finally, we visualise filters learned by the HealpixNet from the mass maps.
-Code and examples are available at \todo{\url{github.com/SwissDataScienceCenter/HealpixNet}}.
+Code and examples are available at \todo{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}.
 
@@
 
-In this work we present and release HealpixNet\footnote{\url{https://github.com/SwissDataScienceCenter/scnn} \todo{change location}}, an algorithm and software package which implements an efficient CNN on Healpix maps.
+In this work we present and release HealpixNet\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}, an algorithm and software package which implements an efficient CNN on Healpix maps.
 It is implemented with \pkg{TensorFlow} \citep{abadi2016tensorflow} and is intended to be easy to use out-of-the box for cosmological applications.
@@
 
-A CNN is composed of the following main building blocks~\citep{lecun1998cnn}, illustrated in~\figref{architecture}: (i) a convolution, (ii) a non-linearity, (iii) a down-sampling operation, (iv) a pooling operation, and (v), optionally, some normalization.\footnote{A batch normalization has been shown to help the training.~\citep{ioffe2015batchnorm} We have verified this experimentally in our setting as well.} As operations (ii) and (v) are point-wise, they do not depend on the data domain.
+A CNN is composed of the following main building blocks~\citep{lecun1998cnn}, illustrated in~\figref{architecture}: (i) a convolution, (ii) a non-linearity, (iii) a down-sampling operation, (iv) a pooling operation, and (v), optionally, some normalization.\footnote{\citet{ioffe2015batchnorm} have shown that batch normalization helps training.
+We verified this experimentally in our setting as well.} As operations (ii) and (v) are point-wise, they do not depend on the data domain.
 The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either.
@@
 
-On regular Euclidean domains, such as 1-dimensional time series or 2-dimensional images, a convolution can be efficiently implemented by sliding a localized convolution kernel (for example a patch 5x5 pixels) in the signal domain.
+On regular Euclidean domains, such as 1-dimensional time series or 2-dimensional images, a convolution can be efficiently implemented by sliding a localized convolution kernel (for example a patch of 5x5 pixels) in the signal domain.
 Likewise, down-sampling can be achieved by taking one pixel out of $n$.
@@
 We will hence make a detour by the spectrum to perform the convolution.\footnote{Note that we only use the spectrum to define the convolution.
-The implementation however does not need a direct access to the spectrum, which is much more computationally efficient.
-See \secref{sec:efficient_convolution}.}
+The implementation however does not need a direct access to the spectrum, which is computationally much more efficient.
+See \secref{efficient_convolution}.}
 The gist of our method is to define the convolution on a sphere using a graph, and the down-sampling using a hierarchical pixelization of the sphere.
@@
 
-\begin{figure}[ht]
+\begin{figure}
 	\centering
@@
 
-\subsection{Graph creation}
+\subsection{Graph construction}
 
-The graph approximates the 2D manifold that is the surface of the sphere. It can accommodate any sampling, regular or irregular.
+Our graph is constructed as an approximation of the continuous 2D manifold that is the surface of the sphere.
+Indeed, \citet{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity.
+That construction can accommodate any sampling, regular or not.
 
-In the classical 2-dimensional convolution, each pixel is connected with the
-same weight to its 4 closest neighbors. We use a weighted undirected graph to
-generalize this idea to the ubiquitous HealPix
-sampling~\citep{gorski2005healpix}.  Each pixel is represented by a node
-(vertex) connected to his $8$ or $7$ closest neighbors.\footnote{For some
-pixels, the $8^{th}$ nearest neighbor is not well defined.} Given the set of
-nearest neighbors, we define the weight matrix $W$ using the following scheme
-\begin{equation}
-W[i,j]=\begin{cases}
-e^{-\frac{\|x_i-x_j\|_2^2}{\sigma^2}} & \text{if pixels $i$ and $j$ are connected, and}\\
-0 & \text{otherwise.}\\
+From the HEALPix pixelization, we build a weighted undirected graph $\G = (\V, \E, \W)$, where $\V$ is the set of $N_{pix} = |\V|$ nodes, $\E$ is the set of edges, and $\W$ is the weighted adjacency matrix.
+In our graph, each pixel $i$ is represented by a node (also called vertex) $v_i \in \V$.
+Each node $v_i$ is then connected to the $8$ (or $7$)\footnote{\label{neighbors}The $12 \cdot 4 = 48$ pixels at the corner of each rhombus of the base dodecahedron only have 7 neighboring pixels.
+See Figures~\ref{fig:healpix_graph_4} and~\ref{fig:pooling}.} nodes $v_j$ which represent the neighboring pixels $j$ of pixel $i$, forming edges $(v_i, v_j) \in \E$.
+Given those edges, we define the weighted adjacency matrix $\W$ as
+\begin{equation*}
+	\W_{ij} = \begin{cases}
+		\exp \left( -\frac{\|\x_i-\x_j\|_2^2}{\sigma^2} \right) & \text{if pixels $i$ and $j$ are neighbors,} \\
+		0 & \text{otherwise,} \\
 	\end{cases}
-\end{equation}
-\todo{why not $1/d$?
-See Pascal's paper, \nati{ The question is: is $1/d$ also good when we have 7/8 neighboors instead of 4?
+\end{equation*}
+where $\x_i$ is a vector encoding the 3-dimensional coordinates of pixel $i$, and
+\begin{equation*}
+	\sigma = \frac{1}{|\E|} \sum_{(v_i, v_j) \in \E} \|\x_i-\x_j\|_2
+\end{equation*}
+is the average Euclidean distance over all connected pixels.
+This weighting scheme is important as while pixel areas are equal, distances between pixels are not equal.
+\figref{healpix_graph_4} shows a graph constructed from the HEALPix sampling of a sphere.
+
+% mdeff: Why not $1/d$? See Pascal's paper
+% nati: The question is: is $1/d$ also good when we have 7/8 neighboors instead of 4?
 Practically, we can also use $1/d$, but that means changing the code and re-runing the experiment.
@@
 @mdeff: do you think we should try this for this paper?
-Or we keep that for the next one.}}
-Here $x_i$ is a 3-dimensional vector encoding the coordinate of the pixels $i$
-on the sphere and $\sigma$ is the mean of $\|x_i-x_j\|_2$ over all connected
-pixels $i$ and $j$. This weighting scheme is important as the distances between
-pixels varies due to the small sampling irregularities. Some of the
-irregularities have been highlighted in the graph displayed in
-\figref{healpix_graph_4}.
+Or we keep that for the next one.
+% mdeff: I tried and the eigenvectors and eigenvalues are mostly the same.
+To me, there is no point in trying for trying.
+We should rather come up with a definition of distance that will make the eigenvectors closer to the real spherical harmonics.
 
-These small irregularities are important and affect slightly the degree of a
-node (or a pixel), defined as $d_i =\sum_j W[i,j]$.
-
-\begin{figure}[!ht]
+\begin{figure}
 	\centering
 	% \includegraphics[width=0.45\textwidth]{figures/healpix_graph_4.pdf}
-\vspace{-0.5cm}
-\includegraphics[width=0.35\textwidth]{figures/half_graph_4.pdf}
-\vspace{-0.5cm}
-\caption{
-Top view of a Healpix graph for half the sphere using a HealPix nside parameter of $4$.
-Nodes with 7 neighbors are highlighted. \label{fig:healpix_graph_4}
-}
+	\includegraphics[width=0.8\linewidth]{figures/half_graph_4.pdf}
+	\caption[]{Graph built from an HEALPix pixelization of half the sphere ($N_{side} = 4$). By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[6]}
+	\label{fig:healpix_graph_4}
 \end{figure}
@@
 that can be used to define a Fourier basis on the graph. Here $\D$ is the diagonal
-matrix where $\D_{ii}=\b{d}_i$. By construction the Laplacian is symetric positive
+matrix where $\D_{ii} = \b{d}_i$ and $\b{d}_i = \sum_j \W_{ij}$ is the weighted degree of node $v_i$. By construction the Laplacian is symetric positive
 semi-definite and hence can be decomposed as $\L=\U \bLambda \U^*$, where $\U$ is an
@@
 
-We provide HealPixNet as a small easy-to-use package available at \todo{\url{https://github.com/xxx}}.
+The main product of this contribution is HealPixNet,\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} a small and easy-to-use python package for cosmologists to classify sky maps.
 As a future work, we intend to 1) further investigate the link between the graph Fourier basis and the spherical harmonic and 2) compare HealPixNet to other spherical CNN using different sampling schemes.

### 2018-07-13 scnn.tex
method: graph fourier basis

@@
 \newcommand{\E}{\mathcal{E}}
-\renewcommand{\L}{\b{L}} % the laplacian matrix
+\renewcommand{\L}{\b{L}}
 \newcommand{\W}{\b{W}}
@@
 \newcommand{\x}{\b{x}}
+\newcommand{\bu}{\b{u}}
+\newcommand{\f}{\b{f}}
+\newcommand{\trans}{^\intercal}
 \newcommand{\R}{\mathbb{R}}
@@
 See Figures~\ref{fig:healpix_graph_4} and~\ref{fig:pooling}.} nodes $v_j$ which represent the neighboring pixels $j$ of pixel $i$, forming edges $(v_i, v_j) \in \E$.
-Given those edges, we define the weighted adjacency matrix $\W$ as
+Given those edges, we define the weighted adjacency matrix $\W \in \R^{N_{pix} \times N_{pix}}$ as
 \begin{equation*}
@@
 
-\subsection{Graph Fourier basis and spherical harmonics}
+\subsection{Graph Fourier basis}
 
@@
 that can be used to define a Fourier basis on the graph. Here $\D$ is the diagonal
-matrix where $\D_{ii} = \b{d}_i$ and $\b{d}_i = \sum_j \W_{ij}$ is the weighted degree of node $v_i$. By construction the Laplacian is symetric positive
-semi-definite and hence can be decomposed as $\L=\U \bLambda \U^*$, where $\U$ is an
-orthonormal matrix of eigenvectors and $\bLambda$, the diagonal matrix of
-eigenvalues. The graph Fourier basis is defined as the Laplacian eigenvectors.
-The graph Fourier transform of $f$ is simply its projection on $\U$ given by
-$\hat{\b{f}}=\U^*\b{f}$. Similarly, the inverse graph Fourier transform reads $\b{f}=\U\hat{\b{f}}$.
-Note that instead of frequencies, the Fourier modes are ordered in the increasing order of the Laplacian eigenvalues $\bLambda$. In a sense, the Laplacian
-eigenvalues correspond to the squared frequencies.
+matrix where $\D_{ii} = \b{d}_i$ and $\b{d}_i = \sum_j \W_{ij}$ is the weighted degree of node $v_i$. By construction, the Laplacian is symmetric positive
+semi-definite and hence can be decomposed as $\L = \U \bLambda \U\trans$, where $\U = [\b u_1, \ldots, \b u_{N_{pix}}]$ is an
+orthonormal matrix of eigenvectors and $\bLambda$ is a diagonal matrix of
+eigenvalues. The graph Fourier basis is defined as the Laplacian eigenvectors, motivated by the fact that a Fourier basis should diagonalize the Laplacian operator.
+The graph Fourier transform of a signal $\f \in \R^{N_{pix}}$ is simply its projection on the eigenvectors given by
+$\hat{\f} = \mathcal{F}_\G \{\f\} = \U\trans \f$. It follows that the inverse graph Fourier transform reads $\mathcal{F}^{-1}_\G \{\hat{\f}\} = \U\hat{\f} = \U \U\trans \f = \f$.
+Note that the Fourier modes are ordered in the increasing order of the Laplacian eigenvalues $\bLambda$, which can be interpreted as squared frequencies.
+Indeed,
+\begin{equation*}
+	\bLambda_{ii} = \b u_i\trans \L \b u_i = \sum_{(v_j, v_k) \in \E} \frac{\W_{jk}}{\sqrt{\b d_j \b d_k}} (\U_{ji} - \U_{ki})^2
+\end{equation*}
+is a measure of how smooth the eigenvector $\b u_i$ is on the graph defined by the Laplacian $\L$.
 
-As shown in \figref{graph_harmonics}, it turns out that using the graph
-construction described above, the graph Fourier harmonics resemble the
-classical spherical harmonics giving us an indication that the graph is able to
-capture the spherical properties of the Healpix sampling. This topic is further discussed in Appendix~\ref{sec:spherical_harmonics}.
+It turns out that using the graph construction described above, the graph Fourier modes resemble the spherical harmonics (see \figref{graph_harmonics}).
+That is a strong hint that the graph is able to capture the spherical properties of the HEALPix sampling.
+This topic is further discussed in \ref{sec:spherical_harmonics}.
 
@@
 \begin{equation} \label{eqn:graph_convolution}
-h(L)\b{f} = \U h(\bLambda) \U^* \b{f},
+h(L)\b{f} = \U h(\bLambda) \U\trans \b{f},
 \end{equation}
 where $h(\bLambda)$ is a diagonal matrix where $h(\bLambda)_{ii}=h(\bLambda_{ii})$.
-Equation~\eqnref{graph_convolution} contains three parts: a) $\U^* \b{f}$, the
+Equation~\eqnref{graph_convolution} contains three parts: a) $\U\trans \b{f}$, the
 Fourier transform of $\b{f}$; b) $h(\bLambda)$ the multiplication with the Fourier
@@
 \begin{equation}
-\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U^* \g{f}(0) = K_t(\L) \b{f}(0),
+\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U\trans \g{f}(0) = K_t(\L) \b{f}(0),
 \end{equation}
@@
 \includegraphics[width=0.95\textwidth]{figures/eigenvectors.pdf}
-\caption{The first 16 Fourier modes (eigenvectors of the graph Laplacian) of a graph constructed from the Healpix sampling of the sphere.
-Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$, eigenvectors 4--8 with degree $\ell=2$, and eigenvectors 9--15 with degree $\ell=3$.
+\caption{The first 16 Fourier modes (eigenvectors of the graph Laplacian) of a graph constructed from the HEALPix sampling of the sphere.
+Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$ and order $m=(-1,0,1)$, eigenvectors 4--8 with degree $\ell=2$ and order $m=(-2,-1,0,1,2)$, and eigenvectors 9--15 with degree $\ell=3$ and order $m=(-3,\ldots,3)$.
 Nevertheless, the graph eigenvectors are only approximating the real spherical harmonics.

### 2018-07-13 scnn.tex
appendix: spherical harmonics

@@
     \item TK read everything
+	\item MD should we keep those small appendices rather than merging them in the main text?
 \end{itemize}
@@
 
-\section{Spherical harmonics VS graph Fourier eigenvectors}
-\ref{fig:graph_harmonics} displays the first 16 eigenvectors of the
-graph Fourier basis used for the convolution. While there is a clear
-resemblance with the spherical harmonic, the small irregularities in the
-sampling (see \figref{healpix_graph_4}) have an effect on the
-graph Fourier eigenvectors. First, conterintuitively, some graph eigenvectors will be
-localized~\cite{perraudin2018global}, i.e: they will span only a small subpart
-of the sphere.  Second, as Nside increase toward infinity and hence the number
-of pixels $n\rightarrow \infty$, we are still unsure if the graph eigenvectors
-converge toward the spherical harmonics. We believe that it might be the case
-for a different graph construction (fully connected) and that a proof could be
-built on top of the work of~\cite{belkin2007convergence}. This is obviously
-out of the scope of this contribution.
+\section{Graph Fourier eigenvectors and spherical harmonics}
+
+The first 16 eigenvectors of the graph graph Laplacian, forming the graph Fourier basis, are shown in \figref{graph_harmonics}.
+While there is a clear resemblance with the spherical harmonics, the small irregularities in the sampling (non-constant number of neighboring pixels and varying distance between pixels, see \figref{healpix_graph_4}) have an effect on the graph Fourier modes.
+First, counter-intuitively, some eigenvectors will be localized~\citep{perraudin2018global}, i.e, they will span a small part of the sphere.
+Second, as the resolution is increased with $N_{side} \rightarrow \infty$ and $N_{pix} \rightarrow \infty$, we are still unsure if the eigenvectors would converge towards the spherical harmonics.
+We believe that it might be the case for a different construction of the graph (fully connected) and that a proof could be built on top of the work of~\cite{belkin2007convergence}.
+That is however out of the scope of this contribution.
 

### 2018-07-13 scnn.tex
method: convolution on graphs

@@
 
-\subsection{Convolutions on graphs}
+\subsection{Convolution on graphs}
 
-A convolution can be defined on graphs by the convolution theorem which states that a convolution in the vertex (or time, or spatial) domain is a
-multiplication in the spectral domain. Given a convolution kernel
-$h: \R_+ \rightarrow \R$, the convolution of a signal $\b{f}$
-is defined as
-\begin{equation} \label{eqn:graph_convolution}
-h(L)\b{f} = \U h(\bLambda) \U\trans \b{f},
-\end{equation}
-where $h(\bLambda)$ is a diagonal matrix where $h(\bLambda)_{ii}=h(\bLambda_{ii})$.
-Equation~\eqnref{graph_convolution} contains three parts: a) $\U\trans \b{f}$, the
-Fourier transform of $\b{f}$; b) $h(\bLambda)$ the multiplication with the Fourier
-kernel $h(\blambda)$; and c) $\U$ the inverse Fourier transform.
+As there is no notion of translation on a graph, we cannot really convolve two graph signals.
+We can, however, convolve a signal with a kernel defined in the spectral domain.
+More precisely, we are filtering a graph signal by a kernel.
+Given the convolution kernel
+$h: \R_+ \rightarrow \R$, a signal $\f$ is filtered as
+\begin{equation*} \label{eqn:graph_convolution}
+	h(L) \f = \U h(\bLambda) \U\trans \f,
+\end{equation*}
+where $h(\bLambda)$ is a diagonal matrix where $h(\bLambda)_{ii} = h(\bLambda_{ii})$, and $h(\bLambda) \hat{\f}$ is the spectral representation of $\f$ after filtering.
 
-The major difference with the classical convolution is that the convolution kernel
-$h$ cannot be thought as a $n \times n$ pattern, but is a continuous function
-applied to the graph eigenvalues $\bLambda$. For visualization purposes, one can
-look at the effect of the convolution on a Kronecker delta, i.e., one column of the matrix
-$h(\L)$.
-Due to the non-regularity of the graph (i.e. the fact
-that there is no perfect sampling on the sphere), the convolution effect will slightly
-differ from one node to another. In the specific case of the full sphere, these
-differences are negligible in most of the cases. However, when considering only parts of
-the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).
+Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph.
+It can however be localized on any vertex $v_i$ by the convolution with a Kronecker delta $\b \delta_i \in \R^{N_{pix}}$,\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} that is $h(\L) \b \delta_i$, a column of $h(\L)$.
+That is useful to visualize kernels.
+If the graph is not regular, i.e., all nodes don't have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another.
+While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular.
+However, when considering only parts of the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).
+Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with all localizations of the kernel:
+\begin{equation*} \label{eqn:graph_convolution}
+	(h(L) \f)_i = \langle h(L) \b \delta_i, \f \rangle.
+\end{equation*}
 
-\paragraph{Example:}
+\paragraph{Example}
 Let us consider the heat diffusion problem
@@
 \end{equation}
-where $\b{f}(t): \mathbb{R}_+ \rightarrow \mathbb{R}^N$. Given the initial condition
+where $\b{f}: \R_+ \rightarrow \R^{N_{pix}}$. Given the initial condition
 $\b{f}(0)$, the solution of~\eqnref{heat_equation} can be expressed as
-\begin{equation}
+\begin{equation*}
 	\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U\trans \g{f}(0) = K_t(\L) \b{f}(0),
-\end{equation}
-which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(x)=e^{-\tau
-t x}$.
-Here the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$.
-They are a generalization of the squared frequencies in the graph setting.
-Hence the kernel $K_t$ can also be considered as a generalization of the
-Gaussian kernel on the sphere. In \figref{gaussian_filters_comparizon} top, we show
-the effect of the convolution by diffusing a unit of heat for $\tau=1$ and various
-time $t$. We also compare the graph convolution with the
-spherical symmetric Gaussian smoothing
-(\figref{gaussian_filters_comparizon} bottom) and observe that both
-techniques lead to similar results. While the graph convolution is different
-from a true spherical convolution, it can, providing the correct
-parameterization, well approximate it.
-In~\figref{gaussian_filters_visualization} of Appendix~\ref{sec:filter_visualization}, we provide additional visualizations of the
-convolution kernel $K_t$.
+\end{equation*}
+which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(\lambda)=e^{-\tau t \lambda}$.
+Here the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$, which are a generalization of squared frequencies.
+Hence, the kernel $K_t$ can also be considered as a generalization of the Gaussian kernel on the sphere.
+\figref{gaussian_filters_comparizon} shows the effect of the convolution by diffusing a unit of heat for $\tau=1$ at various times $t$.
+By comparing the graph convolution with the spherical symmetric Gaussian smoothing, we observe that both techniques lead to similar results (see \figref{gaussian_filters_comparizon}).
+While the graph convolution is different from a true spherical convolution, it can, providing the correct parameterization, well approximate it.
+\figref{gaussian_filters_visualization} provides additional visualizations of the convolution kernel $K_t$.
 
-\begin{figure*}[!ht]
+\begin{figure*}
 	\centering
 	\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_sphere.pdf}
-\caption{Convolution comparison (Nside=16).
+	\caption{Comparison of convolution with the graph and the spherical harmonics ($N_{side} = 16$).
 	Top: Diffusion of a unit of heat for different times $t$ using the graph.
@@
 This result is another sign that the constructed graph is able to capture the spherical
-structure of the HealPix sampling. Furthermore, in some application, where the
-exactitude of the convolution is not a requirement, such as de-noising, it means
-that we could use the graph convolution instead. Depending on the convolution kernel
-this may reveal much more efficient. In the case of a neural network, the fact
-that both convolution are not identical is not very relevant since the network
-will adapt the convolution at use.
+structure of the HEALPix sampling. In some applications, where the
+exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
+Depending on the convolution kernel, this may reveal much more efficient.
+\todo{Show the figure comparing speed of low-pass filtering? It's 10x faster.}
+The fact that both convolutions are not identical is not relevant in a neural network setting, as the convolution kernels are learned anyway.
+% not ideal as the graph convolution depends on the localization
 

### 2018-07-15 scnn.tex
fixed bug in new figure
new figures: graph eigenvalues & filtering speed

@@
 	\item MD should we keep those small appendices rather than merging them in the main text?
+	\item MD add eigenvalues, filtering speed, irregular (random) sampling) to comparison with spherical harmonics
 \end{itemize}
@@
 	\centering
-	\includegraphics[width=\linewidth]{figures/architecture}
+    % \includegraphics[width=\linewidth]{figures/architecture}
+	\includegraphics[width=\linewidth]{figures/figure_architecture.pdf}
 	\caption{Overall network architecture, showing here two convolutional layers acting as feature extractors followed by a fully connected layer with softmax acting as the classifier.
@@
 \section{Graph Fourier eigenvectors and spherical harmonics}
+\label{sec:spherical_harmonics}
 
-The first 16 eigenvectors of the graph graph Laplacian, forming the graph Fourier basis, are shown in \figref{graph_harmonics}.
-While there is a clear resemblance with the spherical harmonics, the small irregularities in the sampling (non-constant number of neighboring pixels and varying distance between pixels, see \figref{healpix_graph_4}) have an effect on the graph Fourier modes.
+The eigenvalues of the graph Laplacian $\L$, shown in \figref{graph_eigenvalues}, are clearly organized in frequency groups of $2\ell + 1$ orders for each degree $\ell$.
+The first 16 eigenvectors $[\b u_1, \ldots, \b u_{16}]$ of the graph graph Laplacian $\L$, forming the lower part of the graph Fourier basis $\U$, are shown in \figref{graph_harmonics}.
+While there is again a clear resemblance with the spherical harmonics, the small irregularities in the sampling (non-constant number of neighboring pixels and varying distance between pixels, see \figref{healpix_graph_4}) have an effect on the graph Fourier modes.
 First, counter-intuitively, some eigenvectors will be localized~\citep{perraudin2018global}, i.e, they will span a small part of the sphere.
@@
 
-\label{sec:spherical_harmonics}
 \begin{figure*}[!htb]
 \centering
-\includegraphics[width=0.95\textwidth]{figures/eigenvectors.pdf}
+\includegraphics[width=\linewidth]{figures/eigenvectors}
 \caption{The first 16 Fourier modes (eigenvectors of the graph Laplacian) of a graph constructed from the HEALPix sampling of the sphere.
 Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$ and order $m=(-1,0,1)$, eigenvectors 4--8 with degree $\ell=2$ and order $m=(-2,-1,0,1,2)$, and eigenvectors 9--15 with degree $\ell=3$ and order $m=(-3,\ldots,3)$.
-Nevertheless, the graph eigenvectors are only approximating the real spherical harmonics.
-\todo{show group of eigenvectors as indication of mode $\ell$.
-Either show eigenvalues on this plot or add a plot of the eigenvalues themselves.}}
+Nevertheless, the graph eigenvectors are only approximating the real spherical harmonics.}
 \label{fig:graph_harmonics}
 \end{figure*}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{figures/graph_eigenvalues}
+	\caption{The eigenvalues $\bLambda$ of the graph Laplacian $\L = \U \bLambda \U\trans$, corresponding to squared frequencies, are clearly organized in groups.
+Each group corresponds to a degree $\ell$ of the spherical harmonics.
+Each degree has $2\ell+1$ modes.
+See also \figref{graph_harmonics}.}
+	\label{fig:graph_eigenvalues}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{figures/filtering_speed}
+	\caption{Comparison of filtering speed for Gaussian smoothing of maps of various sizes.
+The fast spherical harmonic transform (SHT) is implemented by the healpy Python package (via the \texttt{healpy.sphtfunc.smoothing} function).
+The graph filtering is defined by \eqnref{graph_convolution_cheby} and implemented with the numpy and scipy Python packages.
+Both are executed on a single core.}
+	\label{fig:filtering_speed}
+\end{figure}
 

### 2018-07-15 scnn.tex
method: efficient convolution

@@
 \renewcommand{\L}{\b{L}}
+\newcommand{\tL}{\tilde{\L}}
 \newcommand{\W}{\b{W}}
@@
 \newcommand{\blambda}{\b{\lambda}}
+\newcommand{\bO}{\mathcal{O}}
 \newcommand{\pkg}[1]{\texttt{#1}}
@@
 Given the convolution kernel
-$h: \R_+ \rightarrow \R$, a signal $\f$ is filtered as
-\begin{equation*} \label{eqn:graph_convolution}
+$h: \R_+ \rightarrow \R$, a signal $\f \in \R^{N_{pix}}$ on the graph is filtered as
+\begin{equation} \label{eqn:graph_convolution}
 	h(L) \f = \U h(\bLambda) \U\trans \f,
-\end{equation*}
+\end{equation}
 where $h(\bLambda)$ is a diagonal matrix where $h(\bLambda)_{ii} = h(\bLambda_{ii})$, and $h(\bLambda) \hat{\f}$ is the spectral representation of $\f$ after filtering.
@@
 Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with all localizations of the kernel:
-\begin{equation*} \label{eqn:graph_convolution}
+\begin{equation*}
 	(h(L) \f)_i = \langle h(L) \b \delta_i, \f \rangle.
@@
 By comparing the graph convolution with the spherical symmetric Gaussian smoothing, we observe that both techniques lead to similar results (see \figref{gaussian_filters_comparizon}).
-While the graph convolution is different from a true spherical convolution, it can, providing the correct parameterization, well approximate it.
+While the graph convolution is different from a true spherical convolution, it can, provided the correct parameterization, well approximate it.
 \figref{gaussian_filters_visualization} provides additional visualizations of the convolution kernel $K_t$.
@@
 exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
-Depending on the convolution kernel, this may reveal much more efficient.
-\todo{Show the figure comparing speed of low-pass filtering? It's 10x faster.}
 The fact that both convolutions are not identical is not relevant in a neural network setting, as the convolution kernels are learned anyway.
-% not ideal as the graph convolution depends on the localization
+% not ideal tho as the graph convolution depends on the localization
 
@@
 \label{sec:efficient_convolution}
-\assign{Michaël}
-
-Transition from spectral to spatial domain.
-
-With the Fourier basis. Because we don't have an FFT, that costs $O(n^3)$ for the eigendecomposition, plus $O(n^2)$ for the transform (to be done for each forward and backward pass).
-\begin{itemize}
-	\item We need efficient convolution, hence the Chebysheff trick
-	\item Explain the different between a polynomial filter convolution and a traditional patch restricted convolution
-	\item Define spherical CNN using graph CNN
-\end{itemize}
+
+While \eqnref{graph_convolution} is a theoretically well justified definition of the convolution of a graph signal $\f$ by a kernel $h$, it is computationally cumbersome.
+As there exists no general fast Fourier transform (FFT) for graphs,\footnote{See \citep{le2018fgft} for a comparison between the polynomial definition of filters presented here and a class of fast graph Fourier transforms based on the approximation of the Fourier basis $\U$ by a product of sparse matrices.} the Fourier transform, i.e., the multiplication of the signal $\f$ by the dense matrix $\U$, costs $\bO(N_{pix}^2)$ operations.
+In a CNN, this operation has to be performed for each training step (forward and backward).
+As current training procedures are not data efficient and require a lot of samples, a quadratic computational cost in the sample size is a show stopper.
+Moreover, the eigendecomposition of the Laplacian $\L$ is needed to obtain the Fourier basis $\U$ in the first place. That has a unique cost of $\bO(N_{pix}^3)$ operations.
+
+To overcome those computational issues, the convolution kernel $h$ can be defined as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parameterized by $K+1$ coefficients $\theta$.
+The filtering operation \eqnref{graph_convolution} then becomes
+\begin{equation} \label{eqn:graph_convolution_polynomial}
+	h_\theta(\L) \f = \sum_{k=0}^K \theta_k \L^k \f.
+\end{equation}
+Here happens the transition from filtering in the spectral domain to filtering in the vertex domain.
+Note that $\L^k$ captures $k$-neighborhoods, i.e., $(\L^k)_{ij}$ is non-zero if and only if nodes $v_i$ and $v_j$ are connected by a path of length $k$.
+As such, filtering with a polynomial convolution kernel can be interpreted in the vertex domain as a local weighted linear combination of the signal's value.
+The weights are determined by the filter coefficients $\theta$ and the path weight, defined as the multiplication of all edge weights along the path.
+\todo{Better vertex domain explanation.}
+
+To make the parallel with classical Euclidean signal-domain convolution, i.e., filtering by multiplying the signal with translated versions of a patch, we here match our filter at the level of neighborhoods\footnote{The 1-neighborhood of a node is the set of nodes which are directly connected to it.
+The 2-neighborhood is the set of nodes which are connected through paths of length 2.} rather than individual nodes.
+That is required as there is no notion of ordering in a general graph.
+For example, in a classical convolution on the grid, the relative ordering of vertices is up, down, left, and right.
+There is no such ordering on the sphere either, especially if irregularly sampled.
+
+Following \citet{defferrard2016convolutional}, we define our filters as Chebyshev polynomials such as the convolution operation becomes
+\begin{equation} \label{eqn:graph_convolution_cheby}
+	h_\theta(\tL) \f = \sum_{k=0}^K \theta_k T_k(\tL) \f,
+\end{equation}
+where $\tL = \frac{2}{\lambda_{max}} \L - \b{I} = -\frac{2}{\lambda_{max}} \D^{-1/2} \W \D^{-1/2}$ is the rescaled Laplacian with eigenvalues in $[-1, 1]$ and $T_k(\cdot)$ is the Chebyshev polynomial of degree $k$, defined by the recursive relation $T_k(\tL) = 2\tL T_{k-1}(\tL) - T_{k-2}(\tL)$, $T_1(\tL) = \tL$, $T_0(\tL) = \b{I}$.
+While definitions \eqnref{graph_convolution_polynomial} and \eqnref{graph_convolution_cheby} both allow the representation of the same set of filters, Chebyshev polynomials are preferred as they form an orthogonal basis on the interval $[-1, 1]$.
+Moreover, they factor out $\tL^{k-2}$ from $T_k(\tL)$, e.g., the 3-neighborhood is not mixed with the 5-neighborhood.
+That results in easier learning when optimizing the parameters $\theta$.
+Finally, the coefficients can be computed such as the truncated Chebyshev expansions gives an approximate minimax polynomial of a given filter \citep{hammond2011wavelets}.
+While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
+
+Exploiting the recursive formulation of Chebyshev polynomials, evaluating \eqnref{graph_convolution_cheby} requires $\bO(K)$ multiplications of the dense vector $\f$ with the sparse matrix $\tL$.
+The cost of one such multiplication is $\bO(|\E|)$.
+By construction of our graph, $|\E| < 8 N_{pix}$.
+The overall computational cost of the convolution is thus reduced to $\bO(N_{pix})$ operations.
+That is much more efficient than filtering with spherical harmonics, even tho the HEALPix sampling was designed to leverage a fast spherical transform (by being iso-latitude).
+That is especially true for smooth kernels which require a low polynomial degree $K$.
+See \figref{filtering_speed} for a speed comparison of low-pass filtering for Gaussian smoothing using the spherical harmonics and the presented method.
+It is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively.
 

### 2018-07-15 scnn.tex
architecture subsection

@@
 
-\todo{Should we give a more general / high-level description of a CNN?}
-
-A CNN is composed of the following main building blocks~\citep{lecun1998cnn}, illustrated in~\figref{architecture}: (i) a convolution, (ii) a non-linearity, (iii) a down-sampling operation, (iv) a pooling operation, and (v), optionally, some normalization.\footnote{\citet{ioffe2015batchnorm} have shown that batch normalization helps training.
-We verified this experimentally in our setting as well.} As operations (ii) and (v) are point-wise, they do not depend on the data domain.
+A CNN is composed of the following main building blocks~\citep{lecun1998cnn}: (i) a convolution, (ii) a non-linearity, (iii) a down-sampling operation, (iv) a pooling operation, and (v), optionally, some normalization.\footnote{\citet{ioffe2015batchnorm} have shown that batch normalization helps training.
+We verified this experimentally in our setting as well.} Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}.
+As operations (ii) and (v) are point-wise, they do not depend on the data domain.
 The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either.
@@
 
-\begin{figure}[!ht]
+\begin{figure}
 	\centering
@@
 
+\subsection{Architecture}
+\label{sec:architecture}
+
+Now that all the building blocks are defined, let's discuss our proposed spherical CNN architecture, pictured in \figref{architecture}.
+
+\todo{present and discuss the whole CNN architecture.}
+
+Learning the $\theta_k$.
+
 \section{Experiments}
 \label{sec:experiments}
-\assign{Nathanaël, Tomek}
 
@@
 \includegraphics[width=0.48\textwidth]{figures/smooth_map_class_2.pdf}
-\caption{Example maps from two classes. Top: model 1 ($\Omega_m=0.31, \sigma_8=0.82$). Bottom: model 2 ($\Omega_m=0.26, \sigma_8=0.91$).
-The initial conditions for these simulations were the same, so differences arise only due to different cosmological parameters. \nati{Tomek: Is this correct?}}
+\caption{Example maps from two classes to be discriminated. Left: model 1 with $\Omega_m=0.31$ and $\sigma_8=0.82$. Right: model 2 with $\Omega_m=0.26$ and $\sigma_8=0.91$.
+The initial conditions for both simulations were the same, so differences only arise due to different cosmological parameters. \nati{Tomek: Is this correct?}}
 \label{fig:map_sample}

### 2018-07-15 scnn.tex
fix spelling of HEALPix and HealpixNet

@@
 Cosmological data often comes in a form of spherical maps, which makes the use of CNNs more complicated.
-A popular format for spherical maps is Healpix, which uses an equal-area, isolatitude sampling.
-We present a spherical CNN for analysis of full and partial Healpix maps, which we call HealpixNet.
+A popular format for spherical maps is HEALPix, which uses an equal-area, isolatitude sampling.
+We present a spherical CNN for analysis of full and partial HEALPix maps, which we call HealpixNet.
 We construct a spherical CNNs by representing the sphere as a graph.
@@
 For that graph, we define many of the standard CNN operations, such as convolution and pooling, with the filters restricted to being radial.
-HealpixNet is a special case of a graph CNN, tailored to the Healpix sampling of the sphere.
+HealpixNet is a special case of a graph CNN, tailored to the HEALPix sampling of the sphere.
 % TBD if we include it
@@
 % \nati{I am not that we should talk about pooling in the abstract.
-Another angle would be to say that HealPix sampling is well suited for spherical CNN with graphs as a) it is very regular => the graph capture well the spherical structure of the Manifold and b) pooling is natural.}
+Another angle would be to say that HEALPix sampling is well suited for spherical CNN with graphs as a) it is very regular => the graph capture well the spherical structure of the Manifold and b) pooling is natural.}
 % While the convolution on arbitrary graphs has mostly been sorted out, a general pooling operation has not been discovered so far.
@@
 \begin{keyword}
-Spherical Convolutional Neural Network \sep SCNN \sep Healpix CNN \sep Graph CNN
+Spherical Convolutional Neural Network \sep SCNN \sep HealpixNet \sep Graph CNN
 \end{keyword}
@@
 \todo{@Tomek: How is the data acquired?
-Do telescopes and satellites take measurements according to the Healpix sampling?
+Do telescopes and satellites take measurements according to the HEALPix sampling?
 (it is also an advantage of our method to be agnostic to the sampling, which might be useful to researchers working with missing data or different models)}
@@
 
-In this work we present and release HealpixNet\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}, an algorithm and software package which implements an efficient CNN on Healpix maps.
+In this work we present and release HealpixNet\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}, an algorithm and software package which implements an efficient CNN on HEALPix maps.
 It is implemented with \pkg{TensorFlow} \citep{abadi2016tensorflow} and is intended to be easy to use out-of-the box for cosmological applications.
@@
 However, only two elements depend on the sampling: (i) the choice of neighboring pixels when building the graph, and (ii) the choice of parent pixels when building the hierarchy.
-It is also possible to use multiple Healpix maps within our framework and use datasets in form of ``shells''.
+It is also possible to use multiple HEALPix maps within our framework and use datasets in form of ``shells''.
 These shells can span the radial direction, so that a tomographic analysis can be performed, or different frequencies, in case of data from observations in radio frequencies.
@@
 In \secref{related}, we describe existing approaches to convolutions on spheres, graphs, and manifolds.
-\secref{method} exposes the construction of a graph given the Healpix sampling of a sphere and defines the convolution operation.
+\secref{method} exposes the construction of a graph given the HEALPix sampling of a sphere and defines the convolution operation.
 Finally, \secref{experiments} presents our experimental results on the weak lensing mass map classification problem. There we compare our method to two standard benchmarks and show its superiority.
@@
 Fortunately, the Fourier transform can be accelerated for special samplings
-set (theoretically including HealPix, \cite{mohlenkamp1999fast,rokhlin2006fast}).
+set (theoretically including HEALPix, \cite{mohlenkamp1999fast,rokhlin2006fast}).
 The main advantage of this
@@
 of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and
-do not provide any code for the Healpix one. Hence, a practical comparison is
+do not provide any code for the HEALPix one. Hence, a practical comparison is
 not possible. We also note that this approach cannot be trivially accelerated
@@
 most computationally efficient one. However, it suffers that it can only be used using very
-specific grid sampling sets which are NOT including HealPix. Furthermore, the
+specific grid sampling sets which are not including HEALPix. Furthermore, the
 grid requirement makes it impossible for the convolution to capture the
@@
 While the convolution remains efficient, it still captures well the spherical
-structure and is particularly adapted to the HealPix sampling.
+structure and is particularly adapted to the HEALPix sampling.
 
@@
 A counter-example is the equirectangular projection, which is not constructed from a base polyhedron, although it can be subdivided.
-In the particular Healpix case, the base is a rhombic dodecahedron, i.e., a polyhedron made from 12 congruent rhombic faces.\footnote{A rhombus is a quadrilateral whose four sides all have the same length.} See \figref{pooling} for an illustration of the base rhombic dodecahedron and its subdivisions.
+In the particular HEALPix case, the base is a rhombic dodecahedron, i.e., a polyhedron made from 12 congruent rhombic faces.\footnote{A rhombus is a quadrilateral whose four sides all have the same length.} See \figref{pooling} for an illustration of the base rhombic dodecahedron and its subdivisions.
 
@@
 While the number of maps might sound small for deep learning, the information contained in the maps is very recurrent, allowing us to use parts of the map as samples for our simulation.
-Leveraging the properties of the HealPix sampling, we can split each maps
+Leveraging the properties of the HEALPix sampling, we can split each maps
 into $12*o^2$ ($o=1,2,4,\dots$) samples that span a smaller part of the sphere.
@@
 human perspective. The gnomonic projection clearly exibits the sampling issue
-of HealPix. For a detail, on how the convolution kernels are plotted, please refer to Appendix~\ref{sec:filter_visualization}.
+of HEALPix. For a detail, on how the convolution kernels are plotted, please refer to Appendix~\ref{sec:filter_visualization}.
 \todo{Tomek: can you say something about the filters.}
@@
 
-In this contribution, we presented HealPixNet, a spherical CNN for the HealPix sampling. The gist of our construction resides in using a graph to model the sphere.
+In this contribution, we presented HealpixNet, a spherical CNN for the HEALPix sampling. The gist of our construction resides in using a graph to model the sphere.
 This allows us to leverage the advantages of the graph convolution, i.e it is both efficient (with a complexity of $\mathcal{O}(n)$) and flexible (allow to work only on a subpart of the sphere) while it still captures well the spherical properties of the domain.
@@
 
-The main product of this contribution is HealPixNet,\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} a small and easy-to-use python package for cosmologists to classify sky maps.
-As a future work, we intend to 1) further investigate the link between the graph Fourier basis and the spherical harmonic and 2) compare HealPixNet to other spherical CNN using different sampling schemes.
+The main product of this contribution is HealpixNet,\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} a small and easy-to-use python package for cosmologists to classify sky maps.
+As a future work, we intend to 1) further investigate the link between the graph Fourier basis and the spherical harmonic and 2) compare HealpixNet to other spherical CNN using different sampling schemes.
 
@@
 In \figref{gaussian_filters_visualization}, we present three different
-visualization for a HealPix graph convolution kernel.
+visualization for a HEALPix graph convolution kernel.
 The kernel used is defined in the graph spectral domain as $K_t(x)=e^{-\tau t x}$.
@@
 To do so, we convolve a Kroneker on the equator and use the equator for our section as shown in~\figref{index_section}.
-Note that, because of the small irregularities in the HealPix
+Note that, because of the small irregularities in the HEALPix
 sampling, the second and the third methods are subject to small variations depending on the

### 2018-07-15 scnn.tex
fix usage of i.e.

@@
 these contributions it to use a rotational equivariant convolution on the
-sphere, i.e. a rotation of the input implies the same rotation of the output.
-The resulting convolution is performed by a spherical Fourier transform (i.e.
+sphere, i.e., a rotation of the input implies the same rotation of the output.
+The resulting convolution is performed by a spherical Fourier transform (i.e.,
 a projection on the spherical harmonics), a  multiplication in the spectral
@@
 grid requirement makes it impossible for the convolution to capture the
-spherical properties of the domain, i.e. the "cubed sphere” sampling is by
+spherical properties of the domain, i.e., the "cubed sphere” sampling is by
 definition adapted to a cube and not to a sphere.
@@
 \subsection{Convolutions on graphs}
-\todo{Maybe we just describe convolutions on sphere and graph, i.e: do we really need all these three subsections? Maybe simply merge them?}
+\todo{Maybe we just describe convolutions on sphere and graph, i.e.: do we really need all these three subsections? Maybe simply merge them?}
 
@@
 
-We build a robust classifier, i.e. an automatic way to
+We build a robust classifier, i.e., an automatic way to
 discriminate between the two classes in the presence of noise.
-We check the classification performance as a function of the area used, i.e "the order" $o$ and also as a function of the relative level of the noise added to the map.
+We check the classification performance as a function of the area used, i.e., "the order" $o$ and also as a function of the relative level of the noise added to the map.
 
@@
 levels and $3$ different sample areas. The spherical CNN has a significant lead for all levels of noise and sample areas.
-In particular, the difference seems to increase as the problem becomes more complex, i.e as the order is increased and there is less information in each sample.
+In particular, the difference seems to increase as the problem becomes more complex, i.e., as the order is increased and there is less information in each sample.
 This is likely due to the fact that the SCNN can learn optimal features for the problem and do not rely on our humanly limited feature design.
 
-We observe that the PSD features, i.e.
+We observe that the PSD features, i.e.,
 one of the most used techniques for model discrimination in cosmology, is unable
@@
 In this contribution, we presented HealpixNet, a spherical CNN for the HEALPix sampling. The gist of our construction resides in using a graph to model the sphere.
-This allows us to leverage the advantages of the graph convolution, i.e it is both efficient (with a complexity of $\mathcal{O}(n)$) and flexible (allow to work only on a subpart of the sphere) while it still captures well the spherical properties of the domain.
+This allows us to leverage the advantages of the graph convolution, i.e., it is both efficient (with a complexity of $\mathcal{O}(N_{pix})$) and flexible (allow to work only on a part of the sphere) while it still captures well the spherical properties of the domain.
 We also show on a range of classification problems that the neural network systematically significantly outperform classical methods.
@@
 In this case, we simply evaluate $K_t$
-at the graph eigenvalues $\text{diag}(\bLambda)$. The lower eigenvalues $\lambda$ correspond to the lower frequencies, i.e. the spectral mode with less variation.
+at the graph eigenvalues $\text{diag}(\bLambda)$. The lower eigenvalues $\lambda$ correspond to the lower frequencies, i.e., the spectral mode with less variation.
 As a second visualization, we can observe the kernel directly on the sphere. To do so, we perform the convolution of a

### 2018-07-15 scnn.tex
figures: textwidth => linewidth

@@
 grid requirement makes it impossible for the convolution to capture the
-spherical properties of the domain, i.e., the "cubed sphere” sampling is by
+spherical properties of the domain, i.e., the ``cubed sphere'' sampling is by
 definition adapted to a cube and not to a sphere.
@@
 % mdeff: Why not $1/d$? See Pascal's paper
-% nati: The question is: is $1/d$ also good when we have 7/8 neighboors instead of 4?
+% nati: The question is: is $1/d$ also good when we have 7/8 neighbors instead of 4?
 Practically, we can also use $1/d$, but that means changing the code and re-runing the experiment.
@@
 	\centering
-	% \includegraphics[width=0.45\textwidth]{figures/healpix_graph_4.pdf}
 	\includegraphics[width=0.8\linewidth]{figures/half_graph_4.pdf}
@@
 	\centering
-	\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_sphere.pdf}
+	\includegraphics[width=\linewidth]{figures/gaussian_filters_sphere.pdf}
 	\caption{Comparison of convolution with the graph and the spherical harmonics ($N_{side} = 16$).
@@
 	\centering
-	\includegraphics[width=0.45\textwidth]{figures/pooling.pdf}
+	\includegraphics[width=\linewidth]{figures/pooling.pdf}
 	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarsest cell covers $1/12$ of the sphere.}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{figures/psd_sigma3.pdf}
+\includegraphics[width=\linewidth]{figures/psd_sigma3.pdf}
 \caption{Power spectrum densities of the noiseless maps.
@@
 \centering
-\includegraphics[width=0.48\textwidth]{figures/smooth_map_class_1.pdf}
-\includegraphics[width=0.48\textwidth]{figures/smooth_map_class_2.pdf}
+\includegraphics[width=0.48\linewidth]{figures/smooth_map_class_1.pdf}
+\hfill
+\includegraphics[width=0.48\linewidth]{figures/smooth_map_class_2.pdf}
 \caption{Example maps from two classes to be discriminated. Left: model 1 with $\Omega_m=0.31$ and $\sigma_8=0.82$. Right: model 2 with $\Omega_m=0.26$ and $\sigma_8=0.91$.
@@
 \centering
-\includegraphics[width=0.45\textwidth]{figures/part_sphere.pdf}
-\caption{3 subparts of the sphere with different sizes. Blue: $o=1$. Green: order $o=2$. Yellow: order $o=4$.}
+\includegraphics[width=\linewidth]{figures/part_sphere.pdf}
+\caption{Three parts of the sphere with different sizes. Blue: $o=1$. Green: order $o=2$. Yellow: order $o=4$.}
 \label{fig:subpart_sphere}
@@
 \centering
-\includegraphics[width=0.32\textwidth]{figures/result_order1.pdf}
-\includegraphics[width=0.32\textwidth]{figures/result_order2.pdf}
-\includegraphics[width=0.32\textwidth]{figures/result_order4.pdf}
+\includegraphics[width=0.32\linewidth]{figures/result_order1.pdf}
+\hfill
+\includegraphics[width=0.32\linewidth]{figures/result_order2.pdf}
+\hfill
+\includegraphics[width=0.32\linewidth]{figures/result_order4.pdf}
 \caption{Classification errors for the 3 different problems.}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{figures/section_filter_last.pdf}
-\includegraphics[width=0.45\textwidth]{figures/gnonomic_filter_last.pdf}
+\includegraphics[width=0.47\linewidth]{figures/section_filter_last.pdf}
+\hfill
+\includegraphics[width=0.45\linewidth]{figures/gnonomic_filter_last.pdf}
 \caption{24 learned filters selected from the last spherical convolutional layer. Left: section. Right: gnonomic view.}
@@
 \centering
-\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_spectral.pdf}
-\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_gnomonic.pdf}
-\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_section.pdf}
-\caption{3 different visualizations of the convolution kernel $K_t(x)=e^{-\tau t x}$.
+\includegraphics[width=\linewidth]{figures/gaussian_filters_spectral.pdf}
+\includegraphics[width=\linewidth]{figures/gaussian_filters_gnomonic.pdf}
+\includegraphics[width=\linewidth]{figures/gaussian_filters_section.pdf}
+\caption{Three different visualizations of the convolution kernel $K_t(x)=e^{-\tau t x}$.
 Top: graph spectral domain.
@@
 \centering
-\includegraphics[width=0.3\textwidth]{figures/index_plotting_order20_nside16.pdf}
+\includegraphics[width=0.6\linewidth]{figures/index_plotting_order20_nside16.pdf}
 \caption{Indexes selected for the section ploting of \figref{gaussian_filters_visualization} middle. The delta was placed on the yellow node.}
@@
 \centering
-\includegraphics[width=0.45\textwidth]{figures/hist_error_order2_noise1_5.pdf}
+\includegraphics[width=\linewidth]{figures/hist_error_order2_noise1_5.pdf}
 \caption{Evolution curve of the error with respect to the number of training samples for histogram features and a linear classifier (setting: order 2, relative noise level: 1.5).
@@
 \centering
-\includegraphics[width=0.45\textwidth]{figures/border_effects.pdf}
+\includegraphics[width=\linewidth]{figures/border_effects.pdf}
 \caption{Graph convolution of a Kroneker placed at two different spots on the graph.

### 2018-07-15 scnn.tex
first draft of architecture subsection

@@
 \newcommand{\x}{\b{x}}
+\newcommand{\X}{\b{X}}
+\newcommand{\y}{\b{y}}
+\newcommand{\Y}{\b{Y}}
 \newcommand{\bu}{\b{u}}
@@
 The main idea is to represent the sphere $S^2$, a 2-dimensional manifold embedded in $\mathbb{R}^3$, as a graph of connected pixels.
+This contribution leverages the emerging field of graph signal processing which defines fundamental signal processing tools such as the Fourier transform for signals defined on graphs \citep{shuman2013emerging}.
 Our approach uses the graph CNN formulation introduced by \citet{defferrard2016convolutional}, which is efficient and can adapt to any sampling of the sphere.
-Using a k-nearest neigboors graph, the convolution operation costs $\mathcal{O}(n)$ operations, where $n$ is the number of pixels.
+Using a $k$-nearest neighbors graph, the convolution operation costs $\mathcal{O}(N_{pix})$ operations, where $N_{pix}$ is the number of pixels.
 This is the lowest possible complexity for a convolution operation without approximations (e.g.
@@
 The gist of our method is to define the convolution on a sphere using a graph, and the down-sampling using a hierarchical pixelization of the sphere.
-This contribution leverages the emerging field of graph signal processing~\citep{shuman2013emerging} which defines fundamental signal processing tools such as the Fourier transform for signals defined on graphs.
 
@@
 
-\subsection{Architecture}
+\subsection{Graph convolutional neural network}
 \label{sec:architecture}
 
-Now that all the building blocks are defined, let's discuss our proposed spherical CNN architecture, pictured in \figref{architecture}.
-
-\todo{present and discuss the whole CNN architecture.}
-
-Learning the $\theta_k$.
+A typical neural network is constructed as a stack of layers, which sequentially transform the input data.
+Our architecture, pictured in \figref{architecture}, is composed of the following types of layers: graph convolutional (GC) layers, non-linearity, pooling (P), batch normalization (BN), and fully connected (FC) layers.
+All GC and FC layers are always followed by a non-linearity.
+As such, we will not mention the non-linearity in the description of our architectures.
+
+A GC layer takes as input a data matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$ and outputs a data matrix $\Y = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels and nodes, $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
+Each output feature map $\y_i \in \R^{N_{pix}}$ is computed by
+\begin{equation*}
+	\y_i = \sum_{j=1}^{F_{in}} h_{\theta_{ij}}(\tL) \x_j.
+\end{equation*}
+As such, a GC layer is composed of $F_{in} \cdot F_{out}$ filters, each parameterized by $K$ numbers. All those parameters are learned during training via back-propagation of the error gradient.
+
+A FC layer takes as input $\x \in \R^{F_{in}}$ and outputs $\y \in \R^{F_{out}}$ as
+\begin{equation*}
+	\y = \b W \x,
+\end{equation*}
+where $\W \in \R^{F_{out} \times F_{in}}$ is the parameter matrix that is learned.
+Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last GC is vectorized as $\x \in \R^{F_{in}}$ before being fed to the first FC, where $F_{in} = N_{pix} \cdot F_{out}$.
+
+GC32 - P256 - FC10
+
+The whole network is then optimized to minimize the loss function over the training data.
+Describe the loss function.
 

### 2018-07-16 scnn.tex
move speed figure in main text & some edits about speed

@@
 A second attempt by~\citet{cohen2018spherical} was to leverage the spherical Fourier transform and to perform the convolution in the spectral domain, thanks to the convolution theorem.
-While there exists fast Fourier transforms for some samplings, this approach is still computationally expensive.
+While there exists fast spherical Fourier transforms for some samplings, this approach is still computationally expensive (see \figref{filtering_speed}).
 Finally, the use of a graph to model the discretized sphere was considered by~\citet{khasanova2017graph} as well, towards the goal of building invariances in the network.
@@
 We are probably much more efficient than scnns with the convolution done in the spectral domain.
-However compared to tradiational methods, we are in most of the cases slower.}
+However compared to traditional methods, we are in most of the cases slower.}
+\todo{I think we should, as that is our main argument against using the spherical harmonics.
+We are slower than 2D CNNs sure, but those are not adapted to the sphere.
+Or what do you mean by traditional methods?}
 
@@
 Fortunately, the Fourier transform can be accelerated for special samplings
-set (theoretically including HEALPix, \cite{mohlenkamp1999fast,rokhlin2006fast}).
+set (theoretically including HEALPix, \cite{mohlenkamp1999fast,rokhlin2006fast}). \todo{HEALPix was designed to have a fast SHT, by being iso-latitude.}
 The main advantage of this
@@
 equivariant network. Nevertheless, even with these Fourier transform
-acceleration, the convolutions remain expensive in comparison to a traditional
-2-dimensional convolution, limiting the practical use of this approach.
-\todo{to have numbers to back up our claim: have the theoretical complexities and measure the time needed for a convolution on graph and the healpix Fourier transform to get the constants
+acceleration, the convolutions remain expensive, limiting the practical use of this approach.
+\todo{to have numbers to back up our claim: have the theoretical complexities and measure the time needed for a convolution on graph and the HEALPix Fourier transform to get the constants.}
 \nati{@mdeff: for the complexity we probably have $\mathcal{O}(n)$ instead of $\mathcal{O}(n^{3/2})$ (let assume that we have $\approx n^{1/2}$ points allong both axis, computation of the SO3 FFT is composed of 1) $n^{1/2}$ FFTs for a total cost of $n \log (n)$ and 2) $n^{1/2}$ matrix multiplications of size $n^{1/2}$ for a total cost of $n^{3/2}$) For the number, it is a bit more complicated… I guess it is for the next paper.}
-}
+\todo{@nath: I found (i) $\bO(\ell_{max}^3)$ in \url{https://arxiv.org/pdf/1202.6522.pdf} and (ii) $O(N^2 \log(N) \log(1/\epsilon))$ for $N^2$ pixels and precision $\epsilon$ in \url{http://tygert.com/sph2.pdf}.
+From what I understood (ii) is asymptotically fast, but has large constants and as such (i) always wins in practice.
+Not sure what we should use here.
+And I don't know either what healpy is using.
+Maybe we can leave the complexity analysis for a more theoretical paper.}
+\figref{filtering_speed} shows that a naive implementation of our method is more than ten times faster than the wildly used \pkg{healpy} implementation which uses a fast spherical transform for which the HEALPix sampling was designed for.
 While a comparison is theoretically possible, the experiments
@@
 if only one part of the sphere is used. This is impractical in the field of
-cosmology as the data often observed only on a subpart of the sphere.
-One could still pad the unused part of the sphere with 0. However, this would significantly increase the computational cost of the method.
+cosmology as the data often observed only on some part of the sphere.
+One could still pad the unused part of the sphere with zeros. However, this would significantly increase the computational cost of the method.
 \nati{@mdeff: do you think we can say the method would be too slow for our dataset even without trying it? I am not so sure...}
@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{figures/filtering_speed}
+	\caption{Comparison of filtering speed for Gaussian smoothing of maps of various sizes.
+The fast spherical harmonic transform (SHT) is implemented by the healpy Python package (via the \texttt{healpy.sphtfunc.smoothing} function with $\ell_{max} = 3 N_{side} - 1$, the default.).
+The graph filtering is defined by \eqnref{graph_convolution_cheby} and implemented with the numpy and scipy Python packages.
+Both are executed on a single core.
+The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3)$ for the spherical harmonics, where $\ell_{max}$ is the largest degree (i.e., the spectrum is truncated at $\ell_{max}$).}
+	\label{fig:filtering_speed}
+\end{figure}
+
 \subsection{Coarsening and Pooling}
@@
 into $12*o^2$ ($o=1,2,4,\dots$) samples that span a smaller part of the sphere.
-As shown in \figref{subpart_sphere}, we used $o=1,2,4$ as the resulting
+As shown in \figref{part_sphere}, we used $o=1,2,4$ as the resulting
 samples are large enough to suffer from the effects of the spherical geometry. We
@@
 \caption{Three parts of the sphere with different sizes. Blue: $o=1$. Green: order $o=2$. Yellow: order $o=4$.}
-\label{fig:subpart_sphere}
+\label{fig:part_sphere}
 \end{figure}
@@
 	\label{fig:graph_eigenvalues}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{figures/filtering_speed}
-	\caption{Comparison of filtering speed for Gaussian smoothing of maps of various sizes.
-The fast spherical harmonic transform (SHT) is implemented by the healpy Python package (via the \texttt{healpy.sphtfunc.smoothing} function).
-The graph filtering is defined by \eqnref{graph_convolution_cheby} and implemented with the numpy and scipy Python packages.
-Both are executed on a single core.}
-	\label{fig:filtering_speed}
 \end{figure}

### 2018-07-16 scnn.tex
invariance

@@
 Deep Learning has recently gained popularity as an analysis tool in cosmology \citep{schmelze2017cosmologicalmodel,luciesmith2018machinelearning,gupta2018nongaussianinformation,gillet2018deeplearning,hassan2018reionizationmodels,aragoncalvo2018classyfyinglarge,ciuca2017cnnstring}, thanks to its ability to capture complicated, non-linear patterns which are often present in the data.
-Convolutional Neural Networks (CNNs) are particularly well suited for analysis of astrophysical data due to the translation equivariance built into their architecture.
-Indeed, sky maps are translation equivariant, which means that rotating maps on the sphere doesn't change their interpretation (at least at the micro scale).
+Convolutional Neural Networks (CNNs) are particularly well suited for analysis of cosmological data due to the translation equivariance built into their architecture.
+Indeed, sky maps are translation equivariant, which means that rotating maps on the sphere doesn't change their interpretation.
+Only the statistics of the maps is relevant.
+The location of the map on the sky is always fixed (by where the telescope was looking), and most of the models tested are homogeneous and isotropic (the cosmological principle).
 As such, learned weights can be shared across the sphere: the network does not have to relearn to detect objects or features at every spatial location.
@@
 A first attempt to generalize CNNs to spherical data was to apply a standard 2D CNN to a grid discretization of the sphere~\citep{boomsma2017spherical}.
-While this approach leverages the well-developed 2D convolution and hierarchical pooling, it is restricted to those very specific grid samplings.
+While this approach leverages the well-developed 2D convolution and hierarchical pooling, it is restricted to those very specific grid samplings which are highly irregular on the sphere.
 A second attempt by~\citet{cohen2018spherical} was to leverage the spherical Fourier transform and to perform the convolution in the spectral domain, thanks to the convolution theorem.
@@
 Finally, the use of a graph to model the discretized sphere was considered by~\citet{khasanova2017graph} as well, towards the goal of building invariances in the network.
-As~\citep{boomsma2017spherical}, they use an equirectangular grid sampling.
-Moreover, they did not take advantage of a hierarchical pixelization of the sphere and resorted to dynamic pooling~\citep{kalchbrenner2014dcnn}.
+While their architecture is fully invariant to translation and rotation on the sphere, they did not take advantage of a hierarchical pixelization of the sphere, and the statistical layer used to be invariant needs to be hand-crafted to capture statistics of interest.
 
@@
 of the convolution kernel.
+As~\citep{boomsma2017spherical}, they use an equirectangular grid sampling.
+Moreover, they did not take advantage of a hierarchical pixelization of the sphere and resorted to dynamic pooling~\citep{kalchbrenner2014dcnn}.
+Finally, while we do want our network to be rotation invariant, their statistical layer --- an operation which computes a set of spatially invariant statistics of the last feature map --- destroys a lot of information \todo{and hinders performance (should be empirically verified)}.
+While being completely invariant is a nice goal, CNNs for image recognition (arguably the most researched and developed architectures), are not built to be invariant to translation.
+As with the proposed spherical CNN, the fully connected layers at the end of the network depend on the spatial localization of features.
+While that may not be ideal, it was shown to work well in practice.
 

### 2018-07-17 scnn.tex
computational cost of spherical harmonic transform (SHT)

@@
 
-The first approach, leveraging the continuous spherical convolution, has been
-proposed by~\cite{cohen2018spherical}. The goal of
-these contributions it to use a rotational equivariant convolution on the
-sphere, i.e., a rotation of the input implies the same rotation of the output.
-The resulting convolution is performed by a spherical Fourier transform (i.e.,
-a projection on the spherical harmonics), a  multiplication in the spectral
-domain and an inverse spherical Fourier transform. Hence the main
-computational cost of a convolution comes from the two Fourier transforms.
-Fortunately, the Fourier transform can be accelerated for special samplings
-set (theoretically including HEALPix, \cite{mohlenkamp1999fast,rokhlin2006fast}). \todo{HEALPix was designed to have a fast SHT, by being iso-latitude.}
-The main advantage of this
-approach is that it provides a mathematically well defined rotational
-equivariant network. Nevertheless, even with these Fourier transform
-acceleration, the convolutions remain expensive, limiting the practical use of this approach.
-\todo{to have numbers to back up our claim: have the theoretical complexities and measure the time needed for a convolution on graph and the HEALPix Fourier transform to get the constants.}
-\nati{@mdeff: for the complexity we probably have $\mathcal{O}(n)$ instead of $\mathcal{O}(n^{3/2})$ (let assume that we have $\approx n^{1/2}$ points allong both axis, computation of the SO3 FFT is composed of 1) $n^{1/2}$ FFTs for a total cost of $n \log (n)$ and 2) $n^{1/2}$ matrix multiplications of size $n^{1/2}$ for a total cost of $n^{3/2}$) For the number, it is a bit more complicated… I guess it is for the next paper.}
-\todo{@nath: I found (i) $\bO(\ell_{max}^3)$ in \url{https://arxiv.org/pdf/1202.6522.pdf} and (ii) $O(N^2 \log(N) \log(1/\epsilon))$ for $N^2$ pixels and precision $\epsilon$ in \url{http://tygert.com/sph2.pdf}.
-From what I understood (ii) is asymptotically fast, but has large constants and as such (i) always wins in practice.
-Not sure what we should use here.
-And I don't know either what healpy is using.
-Maybe we can leave the complexity analysis for a more theoretical paper.}
-\figref{filtering_speed} shows that a naive implementation of our method is more than ten times faster than the wildly used \pkg{healpy} implementation which uses a fast spherical transform for which the HEALPix sampling was designed for.
+The first approach, leveraging the continuous spherical convolution, has been proposed by~\citet{cohen2018spherical}.
+The goal of this contribution was to define a rotation-equivariant convolution on the sphere, i.e., a rotation of the input implies the same rotation in the output.
+The resulting convolution is performed by (i) a spherical harmonic transform (SHT), i.e., a projection on the spherical harmonics, (ii) a  multiplication in the spectral domain, and (iii) an inverse SHT.
+Hence the computational cost of a convolution is essentially due to the two SHTs.
+A naive implementation of the SHT costs $\bO(N_{pix}^2)$ operations, where $N_{pix}$ is the number of pixels.
+There fortunately exists accelerated schemes for some sampling sets, see for example \citet{mohlenkamp1999fast} and \citet{rokhlin2006fast}.
+The main advantage of this approach is that it provides a mathematically well defined rotation-equivariant network.
+Nevertheless, even with accelerated SHTs, the convolutions remain expensive, limiting the practical use of this approach.
+For example with the HEALPix sampling, which was designed to have a fast SHT by being iso-latitude, the computational cost of the SHT is $\bO(N_{pix}^{3/2}) = \bO(N_{side}^3) = \bO(\ell_{max}^3)$, where $\ell_{max}$ is the largest order (angular frequency) \citep{gorski2005healpix}.\footnote{All pixels are placed on $N_{ring} = 4N_{side}-1 = \bO(\sqrt{N_{pix}})$ rings of constant latitude.
+Each ring has $\bO(\sqrt{N_{pix}})$ pixels.
+Thanks to this iso-latitude property, the SHT is computed using recurrence relations for Legendre polynomials on co-latitude and fast Fourier transforms (FFTs) on longitude.
+The computational cost is thus $\sqrt{N_{pix}}$ FFTs for a total cost of $\bO(N_{pix} \log(\sqrt{N_{pix}}))$, plus $\sqrt{N_{pix}}$ matrix multiplications of size $\sqrt{N_{pix}}$ for a total cost of $\bO(N_{pix}^{3/2})$.}
+In comparison, filtering with our method scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}).
+Moreover, \figref{filtering_speed} shows that a naive implementation of our method is more than ten times faster than the SHT implemented in HEALPix.
 While a comparison is theoretically possible, the experiments
@@
 definition adapted to a cube and not to a sphere.
-\todo{border effects? \nati{@mdeff what are you thinking about here?}}
+\todo{border effects? \nati{@mdeff what are you thinking about here?} I was thinking about irregularities in the sampling, i.e., the corners of the cube are much more sampled.}
 % \nati{Michael: Under some very

### 2018-07-17 scnn.tex
figures: omit path and extension

@@
 \usepackage{hyperref}
-\usepackage{graphicx,array}
+\usepackage{graphicx,array} \graphicspath{{figures/}}
 \usepackage{subcaption}
@@
 
-\begin{figure*}[!ht]
-	\centering
-    % \includegraphics[width=\linewidth]{figures/architecture}
-	\includegraphics[width=\linewidth]{figures/figure_architecture.pdf}
+\begin{figure*}
+	\centering
+    % \includegraphics[width=\linewidth]{architecture}
+	\includegraphics[width=\linewidth]{figure_architecture}
 	\caption{Overall network architecture, showing here two convolutional layers acting as feature extractors followed by a fully connected layer with softmax acting as the classifier.
@@
 		\centering
-		\includegraphics[width=\linewidth]{figures/exampleEarthTopo}
+		\includegraphics[width=\linewidth]{exampleEarthTopo}
 		\caption{}
@@
 		\centering
-		\includegraphics[width=\linewidth]{figures/exampleCMB}
+		\includegraphics[width=\linewidth]{exampleCMB}
 		\caption{}
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{figures/half_graph_4.pdf}
+	\includegraphics[width=0.8\linewidth]{half_graph_4}
 	\caption[]{Graph built from an HEALPix pixelization of half the sphere ($N_{side} = 4$). By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[6]}
@@
 	\centering
-	\includegraphics[width=\linewidth]{figures/gaussian_filters_sphere.pdf}
+	\includegraphics[width=\linewidth]{gaussian_filters_sphere}
 	\caption{Comparison of convolution with the graph and the spherical harmonics ($N_{side} = 16$).
@@
 	\centering
-	\includegraphics[width=\linewidth]{figures/filtering_speed}
+	\includegraphics[width=\linewidth]{filtering_speed}
 	\caption{Comparison of filtering speed for Gaussian smoothing of maps of various sizes.
@@
 	\centering
-	\includegraphics[width=\linewidth]{figures/pooling.pdf}
+	\includegraphics[width=\linewidth]{pooling}
 	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarsest cell covers $1/12$ of the sphere.}
@@
 \centering
-\includegraphics[width=\linewidth]{figures/psd_sigma3.pdf}
+\includegraphics[width=\linewidth]{psd_sigma3}
 \caption{Power spectrum densities of the noiseless maps.
@@
 \centering
-\includegraphics[width=0.48\linewidth]{figures/smooth_map_class_1.pdf}
+\includegraphics[width=0.48\linewidth]{smooth_map_class_1}
 \hfill
-\includegraphics[width=0.48\linewidth]{figures/smooth_map_class_2.pdf}
+\includegraphics[width=0.48\linewidth]{smooth_map_class_2}
 \caption{Example maps from two classes to be discriminated. Left: model 1 with $\Omega_m=0.31$ and $\sigma_8=0.82$. Right: model 2 with $\Omega_m=0.26$ and $\sigma_8=0.91$.
@@
 \centering
-\includegraphics[width=\linewidth]{figures/part_sphere.pdf}
+\includegraphics[width=\linewidth]{part_sphere}
 \caption{Three parts of the sphere with different sizes. Blue: $o=1$. Green: order $o=2$. Yellow: order $o=4$.}
@@
 \centering
-\includegraphics[width=0.32\linewidth]{figures/result_order1.pdf}
+\includegraphics[width=0.32\linewidth]{result_order1}
 \hfill
-\includegraphics[width=0.32\linewidth]{figures/result_order2.pdf}
+\includegraphics[width=0.32\linewidth]{result_order2}
 \hfill
-\includegraphics[width=0.32\linewidth]{figures/result_order4.pdf}
+\includegraphics[width=0.32\linewidth]{result_order4}
 \caption{Classification errors for the 3 different problems.}
@@
 \centering
-\includegraphics[width=0.47\linewidth]{figures/section_filter_last.pdf}
+\includegraphics[width=0.47\linewidth]{section_filter_last}
 \hfill
-\includegraphics[width=0.45\linewidth]{figures/gnonomic_filter_last.pdf}
+\includegraphics[width=0.45\linewidth]{gnonomic_filter_last}
 \caption{24 learned filters selected from the last spherical convolutional layer. Left: section. Right: gnonomic view.}
@@
 \centering
-\includegraphics[width=\linewidth]{figures/gaussian_filters_spectral.pdf}
-\includegraphics[width=\linewidth]{figures/gaussian_filters_gnomonic.pdf}
-\includegraphics[width=\linewidth]{figures/gaussian_filters_section.pdf}
+\includegraphics[width=\linewidth]{gaussian_filters_spectral}
+\includegraphics[width=\linewidth]{gaussian_filters_gnomonic}
+\includegraphics[width=\linewidth]{gaussian_filters_section}
 \caption{Three different visualizations of the convolution kernel $K_t(x)=e^{-\tau t x}$.
@@
 \centering
-\includegraphics[width=0.6\linewidth]{figures/index_plotting_order20_nside16.pdf}
+\includegraphics[width=0.6\linewidth]{index_plotting_order20_nside16}
 \caption{Indexes selected for the section ploting of \figref{gaussian_filters_visualization} middle. The delta was placed on the yellow node.}
@@
 \centering
-\includegraphics[width=\linewidth]{figures/hist_error_order2_noise1_5.pdf}
+\includegraphics[width=\linewidth]{hist_error_order2_noise1_5}
 \caption{Evolution curve of the error with respect to the number of training samples for histogram features and a linear classifier (setting: order 2, relative noise level: 1.5).

### 2018-07-17 scnn.tex
second draft of the architecture subsection

@@
 A GC layer takes as input a data matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$ and outputs a data matrix $\Y = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels and nodes, $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
+In the first GC layer, $F_{in} = 1$ if we have a single map, such as the CMB radiation temperature.
+For observations in radio frequencies, $F_{in}$ would be equal to the number of surveyed frequencies.
+$F_{in}$ might also be the number of slices in the radial direction.
 Each output feature map $\y_i \in \R^{N_{pix}}$ is computed by
 \begin{equation*}
-	\y_i = \sum_{j=1}^{F_{in}} h_{\theta_{ij}}(\tL) \x_j.
+	\y_i = \sum_{j=1}^{F_{in}} h_{\theta_{ij}}(\tL) \x_j + \b b_i, \ \ \forall i \in [F_{out}].
 \end{equation*}
-As such, a GC layer is composed of $F_{in} \cdot F_{out}$ filters, each parameterized by $K$ numbers. All those parameters are learned during training via back-propagation of the error gradient.
+As such, a GC layer is composed of $F_{in} \cdot F_{out}$ filters, each parameterized by $K$ numbers. A bias term $\b b \in \R^{F_{out}}$ is learned jointly.
+
+A non-linear function $\sigma(\cdot)$ is always applied after a linear GC or FC layer.
+The rectified linear unit (ReLU) $\sigma(\cdot) = \max(\cdot, 0)$ is a common choice.
+That operation is point-wise, i.e., $\Y_{ij} = \sigma(\X_{ij})$.
 
@@
 \begin{equation*}
-	\y = \b W \x,
+	\y = \b W \x + \b b,
 \end{equation*}
-where $\W \in \R^{F_{out} \times F_{in}}$ is the parameter matrix that is learned.
+where $\W \in \R^{F_{out} \times F_{in}}$ and $\b b \in \R^{F_{out}}$ are the parameters to be learned.
 Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last GC is vectorized as $\x \in \R^{F_{in}}$ before being fed to the first FC, where $F_{in} = N_{pix} \cdot F_{out}$.
 
+\figref{architecture} shows a network which operates on the whole sphere. The process is however the same when working on parts of sphere, except that the graph is only built for the part of interest.
+
 GC32 - P256 - FC10
 
+All those parameters are learned during training via back-propagation of the error gradient.
 The whole network is then optimized to minimize the loss function over the training data.
+The gradient w.r.t.\ all the parameters is computed by back-propagation, and the values are updated by stochastic gradient descent (SGD).
 Describe the loss function.

### 2018-07-18 scnn.tex
edits after meeting with Nathanaël

@@
     \item TK read everything
-	\item MD should we keep those small appendices rather than merging them in the main text?
-	\item MD add eigenvalues, filtering speed, irregular (random) sampling) to comparison with spherical harmonics
+	\item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings.
+	\item uniformize text size in figures
 \end{itemize}
@@
 Second, we propose to exploit a hierarchical pixelization of the sphere for the pooling operation.
-It allows the network to analyze the data at multiple scales while preserving the spatial localization of features.
-    \nati{Great plot! Could you make the sphere round? If you use the current code in paper plot notebook, they will be.}
-    }
+It allows the network to analyze the data at multiple scales while preserving the spatial localization of features.}
 	\label{fig:architecture}
@@
 These models were designed to have the same power spectrum in range $\ell < 1000$.
-We compare the performance of the spherical CNN to a baseline algorithm, an SVM classifier which takes pixel histograms or Power Spectrum Densities (PSD) of these maps as input.
-The comparison is made as a function of the noise level on convergence maps and the area of the sphere used.
-Results show that our model is better at discriminating the maps, is more resilient to noise, and \todo{is faster?}.
-\nati{I do not think we should argue for speed gain in this paper.
-We are probably much more efficient than scnns with the convolution done in the spectral domain.
-However compared to traditional methods, we are in most of the cases slower.}
-\todo{I think we should, as that is our main argument against using the spherical harmonics.
-We are slower than 2D CNNs sure, but those are not adapted to the sphere.
-Or what do you mean by traditional methods?}
+We compare the performance of our spherical CNN to a baseline algorithm, an SVM classifier which takes pixel histograms or power spectrum densities (PSDs) of these maps as input.
+The comparison is made as a function of the additive noise level and the used area of the sphere. Results show that our model is better at discriminating the maps and is more resilient to noise.
 
@@
 Moreover, \figref{filtering_speed} shows that a naive implementation of our method is more than ten times faster than the SHT implemented in HEALPix.
-While a comparison is theoretically possible, the experiments
-of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and
-do not provide any code for the HEALPix one. Hence, a practical comparison is
-not possible. We also note that this approach cannot be trivially accelerated
-if only one part of the sphere is used. This is impractical in the field of
-cosmology as the data often observed only on some part of the sphere.
-One could still pad the unused part of the sphere with zeros. However, this would significantly increase the computational cost of the method.
-\nati{@mdeff: do you think we can say the method would be too slow for our dataset even without trying it? I am not so sure...}
-\todo{slow: full sky maps are composed of millions of points. partial maps are hard to process}
+While a comparison is theoretically possible, the experiments of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and do not provide any code for the HEALPix one.
+Hence, a practical comparison is not possible.
+We also note that this approach cannot be easily accelerated when data lies on a part of the sphere only.
+That is an important use case in cosmology as measurements are often partial, i.e., full-sky maps are rare.
+One could still fill the unseen part of the sphere with zeros, and avoid to compute empty integrals (on the latitude or longitude).
+It is however not straightforward to identify those empty directions, and computations would still be wasted (consider for example a ring which mostly contains zeros but a few measurements).
+With graphs however, one only pays for the used pixels.
+The cost is some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}).
+Those can however be mitigated by padding with zeros a small area around the measurements.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{sphere_grids}
+	\caption{Two realizations of a grid on the sphere.
+Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system.
+Right: An equiangular cubed-sphere grid, as described in \citet{ronchi1996cubed}.
+Figure from \citet{boomsma2017spherical}.}
+	\label{fig:sphere_grids}
+\end{figure}
 
@@
 to use the traditional 2-dimensional convolution on an irregular grid defined on the
-sphere. In the paper, two grids are used: the equirectangular grid and the ``cubed
-sphere'' grid defined by~\citet{ronchi1996cubed}. \nati{Do we need a plot of the equirectangular and cubed sphere sampling?} Because this
-approach is based on the traditional 2-dimensional convolution, it is very likely to be the
-most computationally efficient one. However, it suffers that it can only be used using very
+sphere. In the paper, two grids are used: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}. See \figref{sphere_grids}. Because this
+approach is based on the classic 2-dimensional convolution, it benefits from all the optimizations developed for images and is very likely to be 
+the most computationally efficient one. However, it suffers that it can only be used using very
 specific grid sampling sets which are not including HEALPix. Furthermore, the
 grid requirement makes it impossible for the convolution to capture the
-spherical properties of the domain, i.e., the ``cubed sphere'' sampling is by
+spherical properties of the domain, i.e., the cubed-sphere sampling is by
 definition adapted to a cube and not to a sphere.
-\todo{border effects? \nati{@mdeff what are you thinking about here?} I was thinking about irregularities in the sampling, i.e., the corners of the cube are much more sampled.}
-% \nati{Michael: Under some very
-% specific hypothesis, this second approach is a particular case of our method,
-% i.e. 1) our method with a stupid sampling, 2) assumption that graph convolution
-% on a grid == 2d convolution. Do you think we should mention that? I think we
-% should not.}
-% I think we should!
+Those samplings are not ideal as their resolution is not constant across the sphere.
+Indeed, the singularities --- the poles for the equirectangular grid, the corners of the cube for the cubed-sphere --- are over-sampled.
+Equal areas of discrete elements is advantageous for physical measurements as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence.
+% \nati{Michael: Under some very specific hypothesis, this second approach is a particular case of our method, i.e.
+(i) our method with a stupid sampling, (ii) assumption that graph convolution on a grid == 2d convolution.
+Do you think we should mention that?
+I think we should not.}
 
@@
 Finally, while we do want our network to be rotation invariant, their statistical layer --- an operation which computes a set of spatially invariant statistics of the last feature map --- destroys a lot of information \todo{and hinders performance (should be empirically verified)}.
-While being completely invariant is a nice goal, CNNs for image recognition (arguably the most researched and developed architectures), are not built to be invariant to translation.
+Moreover, the chosen statistics have to be hand-crafted to capture statistics of interest.
+While developing completely invariant transforms is a  goal worth investigating, CNNs for image recognition (arguably the most researched and developed architectures), are not built to be fully invariant to translation.
 As with the proposed spherical CNN, the fully connected layers at the end of the network depend on the spatial localization of features.
 While that may not be ideal, it was shown to work well in practice.
+\todo{The statistical layer, an idea that we reused in this work. See xxx.}
 
@@
 High-resolutions HEALPix maps easily reach millions of pixels. \figref{example_maps} shows two examples.
-\nati{The figure is beautiful, but should we really show it?
-If we target cosmologists, we can simply list some type of data.
-If we target a broader audience, maybe it makes sense to provide some illustration.}
 
@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{eigenvectors}
+	\caption{The first 16 Fourier modes (eigenvectors of the graph Laplacian) of a graph constructed from the HEALPix sampling of the sphere.
+Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$ and order $m=(-1,0,1)$, eigenvectors 4--8 with degree $\ell=2$ and order $m=(-2,-1,0,1,2)$, and eigenvectors 9--15 with degree $\ell=3$ and order $m=(-3,\ldots,3)$.
+Nevertheless, the graph eigenvectors are only approximating the real spherical harmonics.}
+	\label{fig:graph_harmonics}
+\end{figure}
+
 It turns out that using the graph construction described above, the graph Fourier modes resemble the spherical harmonics (see \figref{graph_harmonics}).
 That is a strong hint that the graph is able to capture the spherical properties of the HEALPix sampling.
-This topic is further discussed in \ref{sec:spherical_harmonics}.
+This topic is further discussed in \ref{sec:comparison_spherical_harmonics}.
 
 \subsection{Convolution on graphs}
+\label{sec:graph_convolution}
 
@@
 It can however be localized on any vertex $v_i$ by the convolution with a Kronecker delta $\b \delta_i \in \R^{N_{pix}}$,\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} that is $h(\L) \b \delta_i$, a column of $h(\L)$.
-That is useful to visualize kernels.
+That is useful to visualize kernels. \todo{nath: link with appendix}
 If the graph is not regular, i.e., all nodes don't have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another.
@@
 Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with all localizations of the kernel:
-\begin{equation*}
+\begin{equation} \label{eqn:graph_convolution_spatial}
 	(h(L) \f)_i = \langle h(L) \b \delta_i, \f \rangle.
-\end{equation*}
+\end{equation}
 
@@
 
-\begin{figure*}
+\begin{figure}
 	\centering
@@
 	Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin).
-	Relative difference between graph convolution and spherical smoothing: $10.4$\%, $5.7$\%, $4.8$\%, $3.8$\% }
+	Relative difference between graph convolution and spherical smoothing: $10.4$\%, $5.7$\%, $4.8$\%, $3.8$\%.
+	\todo{(i) Only three diffusion steps to have a bigger figure?}
+\todo{(ii) The main issue with our filters is that their shape depends on the localization.
+It would be nice to measure the expectation and variance of the error over all locations.
+That would show how severe the distortion is.}}
 	\label{fig:gaussian_filters_comparizon}
-\end{figure*}
+\end{figure}
 
@@
 While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
+\todo{(i) scale of $\theta_k$: they are mostly constant for Chebyshev polynomials. How are they for monomials?}
+\todo{(ii) numerical stability of $\L^k \f$ v.s. $T_k(\L) \f$}
+\todo{(iii) in the code, initialize $\theta_k$ with stdev adapted to $F_{in}$ and $K$}
 
@@
 
+As shown in this contribution, modeling the discretized sphere, a 2D manifold in $\R^3$, by a graph enables an efficient convolution operation on any pixelization.
+Hence, it relaxes the iso-latitude constraint on sampling schemes who aim to enable fast convolutions.
+For applications which can tolerate small imprecisions in rotation invariance --- the fact that the action of a graph filter slightly depends on the location --- this relaxation might enable researchers to consider sampling sets with different properties.
+
 The main product of this contribution is HealpixNet,\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} a small and easy-to-use python package for cosmologists to classify sky maps.
-As a future work, we intend to 1) further investigate the link between the graph Fourier basis and the spherical harmonic and 2) compare HealpixNet to other spherical CNN using different sampling schemes.
+As a future work, we intend to (i) further investigate the link between the graph Fourier basis and the spherical harmonic and (ii) compare HealpixNet to other spherical CNN using different sampling schemes.
 
@@
 
-\section{Graph Fourier eigenvectors and spherical harmonics}
-\label{sec:spherical_harmonics}
+\section{Graph Fourier modes and spherical harmonics}
+\label{sec:comparison_spherical_harmonics}
+\label{sec:border_effects}
 
 The eigenvalues of the graph Laplacian $\L$, shown in \figref{graph_eigenvalues}, are clearly organized in frequency groups of $2\ell + 1$ orders for each degree $\ell$.
-The first 16 eigenvectors $[\b u_1, \ldots, \b u_{16}]$ of the graph graph Laplacian $\L$, forming the lower part of the graph Fourier basis $\U$, are shown in \figref{graph_harmonics}.
+The first 16 eigenvectors $[\b u_1, \ldots, \b u_{16}]$ of the graph Laplacian $\L$, forming the lower part of the graph Fourier basis $\U$, are shown in \figref{graph_harmonics}.
+\figref{subspace_harmonics_eigenvectors} shows the correspondence between the subspaces spanned by the graph Fourier modes and the spherical harmonics.
 While there is again a clear resemblance with the spherical harmonics, the small irregularities in the sampling (non-constant number of neighboring pixels and varying distance between pixels, see \figref{healpix_graph_4}) have an effect on the graph Fourier modes.
@@
 
-\begin{figure*}[!htb]
-\centering
-\includegraphics[width=\linewidth]{figures/eigenvectors}
-\caption{The first 16 Fourier modes (eigenvectors of the graph Laplacian) of a graph constructed from the HEALPix sampling of the sphere.
-Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$ and order $m=(-1,0,1)$, eigenvectors 4--8 with degree $\ell=2$ and order $m=(-2,-1,0,1,2)$, and eigenvectors 9--15 with degree $\ell=3$ and order $m=(-3,\ldots,3)$.
-Nevertheless, the graph eigenvectors are only approximating the real spherical harmonics.}
-\label{fig:graph_harmonics}
-\end{figure*}
-
 \begin{figure}
 	\centering
-	\includegraphics[width=\linewidth]{figures/graph_eigenvalues}
-	\caption{The eigenvalues $\bLambda$ of the graph Laplacian $\L = \U \bLambda \U\trans$, corresponding to squared frequencies, are clearly organized in groups.
+	\includegraphics[width=\linewidth]{graph_eigenvalues}
+	\caption{The eigenvalues $\bLambda$ of the graph Laplacian $\L = \U \bLambda \U\trans$, which corresponds to squared frequencies, are clearly organized in groups.
 Each group corresponds to a degree $\ell$ of the spherical harmonics.
-Each degree has $2\ell+1$ modes.
+Each degree has $2\ell + 1$ orders.
 See also \figref{graph_harmonics}.}
 	\label{fig:graph_eigenvalues}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{subspace_harmonics_eigenvectors}
+	\caption{Correspondence between the subspaces spanned by the graph Fourier modes and the spherical harmonics.
+Each pixel on the plot is the dot product between one spherical harmonic and one graph Fourier mode $\b u_i$.
+The plot clearly shows how the subspaces are aligned: modes and harmonics which correspond to different degrees $\ell$ are mostly orthogonal to each other, while modes and harmonics which correspond to the same degree $\ell$ are linearly dependent.
+There is $2 \ell + 1$ orders per degree $\ell$.}
+	\label{fig:subspace_harmonics_eigenvectors}
+\end{figure}
+
+The graph setting used through this contribution assumes reflective border conditions.
+That is irrelevant when working on the complete sphere as this surface has no border.
+When working with a part of the sphere however, its border slightly affects the convolution.
+As depicted in \figref{border_effects}, a filter localized near the border of a part of the sphere (via $h(\L) \b \delta_i$) no longer has an isotropic profile.
+These border effects can however be mitigated by padding with zeros a small area around the part of interest.
+
+\begin{figure}[!ht]
+	\centering
+	\includegraphics[width=\linewidth]{border_effects}
+	\caption{Convolution kernel (also called filter) $h$ localized in the center and left corner of a surface.
+A filter is localized on pixel $i$ as $h(\L) \b \delta_i$ (see \secref{graph_convolution} and \eqnref{graph_convolution_spatial}).
+The graph is built from $1/12^\text{th}$ of the sphere at $N_{side} = 16$.
+The filter is not isotropic anymore when localized on the left corner due to border effects.
+The graph representation of a manifold assumes reflective border conditions.}
+	\label{fig:border_effects}
 \end{figure}
@@
 
-\section{Border effects when only a part of the sphere is considered.}
-\label{sec:border_effects}
-The graph setting used through this contribution assumes reflective border conditions on a grid.
-While the complete sphere is not affected by this because it has no border, these border effects change slightly the effect of the convolution when working with only a part of the graph.
-As depicted in \figref{border_effects}, the convolution of a Krnoneker near the border filters may no longer have a spherical profile.
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\linewidth]{figures/border_effects.pdf}
-\caption{Graph convolution of a Kroneker placed at two different spots on the graph.
-The graph build from $1/12$ of the sphere and an Nside of 16.
-When the Kroneker is placed on the left corner, the resulting convolution is not circular anymore due to border effect.
-The graph setting assumes reflective border conditions.}
-\label{fig:border_effects}
-\end{figure}
-
 %% If you have bibdatabase file and want bibtex to generate the

### 2018-07-18 scnn.tex
libsharp

@@
 A naive implementation of the SHT costs $\bO(N_{pix}^2)$ operations, where $N_{pix}$ is the number of pixels.
-There fortunately exists accelerated schemes for some sampling sets, see for example \citet{mohlenkamp1999fast} and \citet{rokhlin2006fast}.
+There fortunately exists accelerated schemes for some sampling sets, see for example \citet{mohlenkamp1999fast, rokhlin2006fast, reinecke2013libsharp}.
 The main advantage of this approach is that it provides a mathematically well defined rotation-equivariant network.
 Nevertheless, even with accelerated SHTs, the convolutions remain expensive, limiting the practical use of this approach.
-For example with the HEALPix sampling, which was designed to have a fast SHT by being iso-latitude, the computational cost of the SHT is $\bO(N_{pix}^{3/2}) = \bO(N_{side}^3) = \bO(\ell_{max}^3)$, where $\ell_{max}$ is the largest order (angular frequency) \citep{gorski2005healpix}.\footnote{All pixels are placed on $N_{ring} = 4N_{side}-1 = \bO(\sqrt{N_{pix}})$ rings of constant latitude.
+For example with the HEALPix sampling, which was designed to have a fast SHT by being iso-latitude, the computational cost of the SHT is $\bO(N_{pix}^{3/2}) = \bO(N_{side}^3) = \bO(\ell_{max}^3)$, where $\ell_{max}$ is the largest order (angular frequency) \citep{gorski2005healpix, reinecke2013libsharp}.\footnote{All pixels are placed on $N_{ring} = 4N_{side}-1 = \bO(\sqrt{N_{pix}})$ rings of constant latitude.
 Each ring has $\bO(\sqrt{N_{pix}})$ pixels.
@@
 In comparison, filtering with our method scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}).
-Moreover, \figref{filtering_speed} shows that a naive implementation of our method is more than ten times faster than the SHT implemented in HEALPix.
+Moreover, \figref{filtering_speed} shows that a naive implementation of our method is more than ten times faster than the SHT implemented by the highly optimized \pkg{libsharp} library used by HEALPix \citep{reinecke2013libsharp}.
 While a comparison is theoretically possible, the experiments of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and do not provide any code for the HEALPix one.

### 2018-07-19 scnn.tex
symmetries of Fourier modes
statistical layer

@@
 \newcommand{\bO}{\mathcal{O}}
+\DeclareMathOperator*{\esp}{E}
+\DeclareMathOperator*{\var}{Var}
 \newcommand{\pkg}[1]{\texttt{#1}}
@@
     \item (TK) make the bibliography display only a few name
+	\item check if papers which appear as arxiv were not published in a conference or journal
     % \item (yes) Michael, do you agree with the title HealpixNet?
@@
 While there exists fast spherical Fourier transforms for some samplings, this approach is still computationally expensive (see \figref{filtering_speed}).
-Finally, the use of a graph to model the discretized sphere was considered by~\citet{khasanova2017graph} as well, towards the goal of building invariances in the network.
+Finally, the use of a graph to model the discretized sphere was considered by~\citet{khasanova2017graphomni} as well, towards the goal of building invariances in the network.
 While their architecture is fully invariant to translation and rotation on the sphere, they did not take advantage of a hierarchical pixelization of the sphere, and the statistical layer used to be invariant needs to be hand-crafted to capture statistics of interest.
@@
 
-The use of a graph to model the discretized sphere was considered by~\citet{khasanova2017graph} as well.
+The use of a graph to model the discretized sphere was considered by~\citet{khasanova2017graphomni} as well.
 The authors map omnidirectional images to the sphere, with the goal of correcting for distortions induced by the lens used for the acquisition.
 Besides the different application covered by the paper, there are two important
-differences. First the sampling is different as~\cite{khasanova2017graph} uses a
+differences. First the sampling is different as~\cite{khasanova2017graphomni} uses a
 grid. Second, it uses a different graph CNN based on a different parameterization
@@
 While that may not be ideal, it was shown to work well in practice.
-\todo{The statistical layer, an idea that we reused in this work. See xxx.}
+\todo{In this work we reused the idea of a statistical layer, described in \secref{stat_layer}, to provide invariance to isometric transformations such as translation and rotation on the sphere.
+While \citet{khasanova2017graphomni} uses the mean and variance of diffused versions of the last feature maps, we experimentally tested multiple variants and got good results by keeping all the statistical moments via a learned histogram.
+That is similar to the learnable histogram introduced by \citet{wang2016learnhist}, although for the orthogonal purpose of integrating global context in object detection and segmentation tasks.}
 
@@
 % The advantage of schemes based on a base polyhedron is that cells are equal-area.
-While that is not required for the convolution operation when modeling with graphs (it can be corrected by setting edge weights appropriately, see \citet{khasanova2017graph})
+While that is not required for the convolution operation when modeling with graphs (it can be corrected by setting edge weights appropriately, see \citet{khasanova2017graphomni})
 % nope: can also do a regular pooling on the equirectangular. It preserves the sampling, and the convolution is adapted to the sampling thanks to the edge weights.
@@
 
+\subsection{Statistical layer}
+\label{sec:stat_layer}
+% Or Global pooling?
+
+Following \citet{khasanova2017tigranet}, we use a statistical layer between the last graph convolutional layer and the first fully connected layer for the neural network to be invariant to isometric transformations such as rotation and translation of maps on the sphere.
+The role of the layer is to compute global and location independent statistics from feature maps.
+Besides providing invariance, the layer drastically compresses the representation of the data as the number of computed statistics $N_{stat}$ is usually much smaller than the size of the map, $N_{pix}$.
+That compression results in much smaller fully connected layers, the most parameter-hungry layers of a neural network.
+The invariance and reduced representation should help the network to learn from less samples and to generalize better to unseen data.
+Yet another advantage is that a network built with such a statistical layer is agnostic to the size of the input data, i.e., it can classify maps which do not have the same number of pixels.
+Indeed, such global summarization is invariant to node permutation and is commonly used along graph convolutions to classify graphs of varying sizes \citep{duvenaud2015gcn, li2015gatedgnn}.
+
+Given a feature map $\x \in \R^{N_{pix}}$, the statistical layer is defined as
+\begin{equation} \label{eqn:stat_layer}
+	\y = f(\x) \in \R^{N_{stat}},
+\end{equation}
+where $f$ computes $N_{stat}$ statistics which are independent from the size of the map, $N_{pix}$.
+An example is the global average pooling $f(\x) = \esp(\x)$, introduced by \citet{lin2013globalavgpooling}, where $\esp(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} x_i$ is the empirical mean.
+Another example is $f(\x) = [\esp(\x), \var(\x)]\trans$, where $\var(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} (x_i - \esp(\x))^2$ is the empirical variance.
+
+\todo{learned histogram \citep{wang2016learnhist} if it shows good results}
+
+\todo{stats of diffused maps \citep{khasanova2017tigranet}. Provides stats at multiple scales?}
+
+\todo{perf w.r.t. different functions $f$. Here or in the experiment section?}
+
 \subsection{Graph convolutional neural network}
@@
 
-A typical neural network is constructed as a stack of layers, which sequentially transform the input data.
-Our architecture, pictured in \figref{architecture}, is composed of the following types of layers: graph convolutional (GC) layers, non-linearity, pooling (P), batch normalization (BN), and fully connected (FC) layers.
+Neural networks are constructed as stacks of layers which sequentially transform the input data.
+Our architecture, pictured in \figref{architecture}, is composed of the following types of layers: graph convolutional (GC) layers, non-linearity, pooling (P), batch normalization (BN), statistical layer (ST), and fully connected (FC) layers.
 All GC and FC layers are always followed by a non-linearity.
@@
 That operation is point-wise, i.e., $\Y_{ij} = \sigma(\X_{ij})$.
+
+The ST layer, described by \eqnref{stat_layer}, independently transforms each of the $F$ feature maps of the input $\X \in \R^{N_{pix} \times F}$ into $\Y \in \R^{N_{stat} \times F}$, where $N_{stat}$ is the number of statistics.
+One may even omit the FC layers and directly fed the output of the ST layer into the softmax layer, as proposed by \citet{lin2013globalavgpooling}.
+In this regime, $N_{stat} = 1$ and $F$ should be equal to the number of classes to discriminate, i.e., the last GC layer outputs as many feature maps as there is classes.
 
@@
 The plot clearly shows how the subspaces are aligned: modes and harmonics which correspond to different degrees $\ell$ are mostly orthogonal to each other, while modes and harmonics which correspond to the same degree $\ell$ are linearly dependent.
-There is $2 \ell + 1$ orders per degree $\ell$.}
+There is $2 \ell + 1$ orders per degree $\ell$.
+Moreover, we see that the Fourier modes have the correct symmetries, indicated by the perfect orthogonality between even and odd functions.}
 	\label{fig:subspace_harmonics_eigenvectors}

### 2018-07-19 scnn.tex
softmax

@@
 Our architecture, pictured in \figref{architecture}, is composed of the following types of layers: graph convolutional (GC) layers, non-linearity, pooling (P), batch normalization (BN), statistical layer (ST), and fully connected (FC) layers.
-All GC and FC layers are always followed by a non-linearity.
-As such, we will not mention the non-linearity in the description of our architectures.
 
@@
 
-A non-linear function $\sigma(\cdot)$ is always applied after a linear GC or FC layer.
+% As such, we will not mention the non-linearity in the description of our architectures.
+A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer.
+That operation is point-wise, i.e., $\Y_{ij} = \sigma(\X_{ij})$.
 The rectified linear unit (ReLU) $\sigma(\cdot) = \max(\cdot, 0)$ is a common choice.
-That operation is point-wise, i.e., $\Y_{ij} = \sigma(\X_{ij})$.
 
@@
 
+The softmax layer is the last layer in a neural network engineered for classification.
+Given the output $\x \in \R^{N_{classes}}$ of the next to last layer, called the logits in the deep learning literature, the softmax layer outputs
+\begin{equation*}
+	y_i = \frac{\exp(x_i)}{\sum_{j=1}^{N_{classes}} \exp(x_j)} \in [0, 1], \ \forall i \in [N_{classes}],
+\end{equation*}
+where $N_{classes}$ is the number of classes to discriminate.
+Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the probability that the input sample belongs to class $i$.
+That last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.
+
 \figref{architecture} shows a network which operates on the whole sphere. The process is however the same when working on parts of sphere, except that the graph is only built for the part of interest.
@@
 The gradient w.r.t.\ all the parameters is computed by back-propagation, and the values are updated by stochastic gradient descent (SGD).
-Describe the loss function.
+Describe the loss function. It's a measure of how far the predictions $\y$ from the softmax are from the true labels $\b \delta_i$. KL-divergence.
 

### 2018-07-23 scnn.tex
architecture: pooling & batch normalization

@@
 \newcommand{\E}{\mathcal{E}}
+\newcommand{\C}{\mathcal{C}}
+\newcommand{\B}{\mathcal{B}}
 \renewcommand{\L}{\b{L}}
@@
 \DeclareMathOperator*{\var}{Var}
+\DeclareMathOperator*{\vect}{vec}
 \newcommand{\pkg}[1]{\texttt{#1}}
@@
 Second, we propose to exploit a hierarchical pixelization of the sphere for the pooling operation.
-It allows the network to analyze the data at multiple scales while preserving the spatial localization of features.}
+It allows the network to analyze the data at multiple scales while preserving the spatial localization of features.
+This figure shows a network which operates on the whole sphere.
+The process is however the same when working with parts of sphere, except that the graph is only built for the part of interest.}
 	\label{fig:architecture}
@@
 Merging cells lead to a coarser graph, hence the name coarsening.
-
-Pooling refers to the operation that summarizes the data supported on the merged sub-cells in one parent cell.
+Coarsening defines $\C(i)$, the set of children of node $v_i$.
+For the HEALPix subdivision scheme, the number of children is constant, i.e., $| \C(i) | = 4^k \ \forall i$, for some $k$.
+
+Pooling refers to the operation that summarizes the data supported on the merged sub-cells in one parent cell. Given a map $\x \in \R^{N_{pix}}$, pooling defines $\y \in \R^{N'_{pix}}$ such as
+\begin{equation} \label{eqn:pooling}
+	y_i = f \left( \left\{ x_j : j \in \C(i) \right\} \right), \ \forall i \in [N'_{pix}],
+\end{equation}
+where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix} / {N_{pix}}'$ is the down-sampling factor\footnote{$| \C(i) | = N_{pix} / {N_{pix}}' = (N_{side} / N'_{side})^2 = 4^k$ for HEALPix.}.
 That operation is often taken to be the maximum value, but it might be any permutation invariant operation such as the sum or the average.
@@
 
-Neural networks are constructed as stacks of layers which sequentially transform the input data.
-Our architecture, pictured in \figref{architecture}, is composed of the following types of layers: graph convolutional (GC) layers, non-linearity, pooling (P), batch normalization (BN), statistical layer (ST), and fully connected (FC) layers.
-
-A GC layer takes as input a data matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$ and outputs a data matrix $\Y = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels and nodes, $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
+Neural networks are constructed as stacks of layers which sequentially transform the data from its raw representation to a decision on the class label.
+Our architecture, pictured in \figref{architecture}, is composed of many layers.
+The convolutional part, the head of the neural network, is composed of graph convolutional layers (GC), pooling layers, and batch normalization layers.
+The tail is composed of multiple fully connected layers (FC) followed by a softmax layer.
+A statistical layer (ST) is optionally inserted between the convolutional head and the fully connected tail.
+
+% As such, we will not mention the non-linearity in the description of our architectures.
+A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer.
+That operation is point-wise, i.e., $y_{ij} = \sigma(x_{ij})$ and $y_i = \sigma(x_i)$ for matrices $\X, \Y$ and vectors $\x, \y$.
+The rectified linear unit (ReLU) $\sigma(\cdot) = \max(\cdot, 0)$ is a common choice.
+
+A GC layer takes as input a matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$ and outputs a matrix $\Y = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels and nodes, $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
 In the first GC layer, $F_{in} = 1$ if we have a single map, such as the CMB radiation temperature.
@@
 \begin{equation*}
-	\y_i = \sum_{j=1}^{F_{in}} h_{\theta_{ij}}(\tL) \x_j + \b b_i, \ \ \forall i \in [F_{out}].
+	\y_i = \sum_{j=1}^{F_{in}} h_{\theta_{ij}}(\tL) \x_j + b_i, \ \ \forall i \in [F_{out}].
 \end{equation*}
-As such, a GC layer is composed of $F_{in} \cdot F_{out}$ filters, each parameterized by $K$ numbers. A bias term $\b b \in \R^{F_{out}}$ is learned jointly.
-
-% As such, we will not mention the non-linearity in the description of our architectures.
-A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer.
-That operation is point-wise, i.e., $\Y_{ij} = \sigma(\X_{ij})$.
-The rectified linear unit (ReLU) $\sigma(\cdot) = \max(\cdot, 0)$ is a common choice.
-
-The ST layer, described by \eqnref{stat_layer}, independently transforms each of the $F$ feature maps of the input $\X \in \R^{N_{pix} \times F}$ into $\Y \in \R^{N_{stat} \times F}$, where $N_{stat}$ is the number of statistics.
+As such, a GC layer is composed of $F_{in} \cdot F_{out}$ filters, each parameterized by $K$ numbers (see \secref{efficient_convolution}). A bias term $\b b \in \R^{F_{out}}$ is jointly optimized.
+
+The pooling layer takes a matrix $\X \in \R^{N_{pix} \times F}$ and transforms it to $\Y \in \R^{N'_{pix} \times F}$ by reducing its spatial resolution ($N'_{pix} < N_{pix}$) according to \eqnref{pooling}.
+
+Given a matrix $\X \in \R^{N_{pix} \times F}$, a batch normalization layer \citep{ioffe2015batchnorm} computes
+\begin{equation*}
+	y_{ij} = \gamma_{ij} \frac{x_{ij} - \esp_\B(x_{ij})}{\sqrt{\var_\B(x_{ij}) + \epsilon}} + \beta_{ij}, \ \forall i,j \in [N_{pix}] \times [F],
+\end{equation*}
+where $\gamma_{ij}$ and $\beta_{ij}$ are parameters to be learned, $\epsilon$ is a constant added for numerical stability, and the empirical expectation and variance are taken over the training mini-batches $\B$.
+
+The ST layer, defined in \eqnref{stat_layer}, independently transforms each of the $F$ feature maps of the input $\X \in \R^{N_{pix} \times F}$ into $\Y \in \R^{N_{stat} \times F}$, where $N_{stat}$ is the number of statistics.
 One may even omit the FC layers and directly fed the output of the ST layer into the softmax layer, as proposed by \citet{lin2013globalavgpooling}.
@@
 where $\W \in \R^{F_{out} \times F_{in}}$ and $\b b \in \R^{F_{out}}$ are the parameters to be learned.
-Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last GC is vectorized as $\x \in \R^{F_{in}}$ before being fed to the first FC, where $F_{in} = N_{pix} \cdot F_{out}$.
+Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last GC (or the output $\Y \in \R^{N_{stat} \times F_{out}}$ of the ST), is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first FC, where $F_{in} = N_{pix} \cdot F_{out}$ (or $N_{stat} \cdot F_{out}$).
 
 The softmax layer is the last layer in a neural network engineered for classification.
-Given the output $\x \in \R^{N_{classes}}$ of the next to last layer, called the logits in the deep learning literature, the softmax layer outputs
+Given the output $\x \in \R^{N_{classes}}$ of the last FC, called the logits in the deep learning literature, the softmax layer outputs
 \begin{equation*}
@@
 That last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.
-
-\figref{architecture} shows a network which operates on the whole sphere. The process is however the same when working on parts of sphere, except that the graph is only built for the part of interest.
 

### 2018-07-24 scnn.tex
architecture: loss and optimization

@@
 \DeclareMathOperator*{\vect}{vec}
+\DeclareMathOperator*{\argmin}{arg \, min}
 \newcommand{\pkg}[1]{\texttt{#1}}
@@
 Our architecture, pictured in \figref{architecture}, is composed of many layers.
-The convolutional part, the head of the neural network, is composed of graph convolutional layers (GC), pooling layers, and batch normalization layers.
-The tail is composed of multiple fully connected layers (FC) followed by a softmax layer.
+The convolutional part, the head of the neural network, is composed of graph convolutional layers (GC), pooling layers (P), and batch normalization layers (BN).
+The tail is composed of multiple fully connected layers (FC) followed by a softmax layer (SM).
 A statistical layer (ST) is optionally inserted between the convolutional head and the fully connected tail.
@@
 % As such, we will not mention the non-linearity in the description of our architectures.
-A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer.
+A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer where it is set to the identity.
 That operation is point-wise, i.e., $y_{ij} = \sigma(x_{ij})$ and $y_i = \sigma(x_i)$ for matrices $\X, \Y$ and vectors $\x, \y$.
@@
 
-A GC layer takes as input a matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$ and outputs a matrix $\Y = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels and nodes, $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
-In the first GC layer, $F_{in} = 1$ if we have a single map, such as the CMB radiation temperature.
-For observations in radio frequencies, $F_{in}$ would be equal to the number of surveyed frequencies.
-$F_{in}$ might also be the number of slices in the radial direction.
-Each output feature map $\y_i \in \R^{N_{pix}}$ is computed by
+Given a matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$, a GC layer computes $\Y = GC(\X) = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels (and nodes), $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
+Using the efficient graph convolution from \eqnref{graph_convolution_cheby}, each output feature map is computed as
 \begin{equation*}
-	\y_i = \sum_{j=1}^{F_{in}} h_{\theta_{ij}}(\tL) \x_j + b_i, \ \ \forall i \in [F_{out}].
+	\y_i = \sum_{j=1}^{F_{in}} h_{\theta_{ij}}(\tL) \x_j + b_i \in \R^{N_{pix}}, \ \ \forall i \in [F_{out}].
 \end{equation*}
 As such, a GC layer is composed of $F_{in} \cdot F_{out}$ filters, each parameterized by $K$ numbers (see \secref{efficient_convolution}). A bias term $\b b \in \R^{F_{out}}$ is jointly optimized.
-
-The pooling layer takes a matrix $\X \in \R^{N_{pix} \times F}$ and transforms it to $\Y \in \R^{N'_{pix} \times F}$ by reducing its spatial resolution ($N'_{pix} < N_{pix}$) according to \eqnref{pooling}.
-
-Given a matrix $\X \in \R^{N_{pix} \times F}$, a batch normalization layer \citep{ioffe2015batchnorm} computes
+% only if batch normalization is not used
+
+Given a matrix $\X \in \R^{N_{pix} \times F}$, a pooling layer computes $\Y = P(\X) \in \R^{N'_{pix} \times F}$ by reducing its spatial resolution ($N'_{pix} < N_{pix}$) according to \eqnref{pooling}.
+
+Given a matrix $\X \in \R^{N_{pix} \times F}$, a batch normalization layer \citep{ioffe2015batchnorm} computes $\Y = BN(\X)$ such as
 \begin{equation*}
-	y_{ij} = \gamma_{ij} \frac{x_{ij} - \esp_\B(x_{ij})}{\sqrt{\var_\B(x_{ij}) + \epsilon}} + \beta_{ij}, \ \forall i,j \in [N_{pix}] \times [F],
+	\y_i = \gamma_i \frac{\x_i - \esp(\x_i)}{\sqrt{\var(\x_i) + \epsilon}} + \beta_i, \ \forall i \in [F],
 \end{equation*}
-where $\gamma_{ij}$ and $\beta_{ij}$ are parameters to be learned, $\epsilon$ is a constant added for numerical stability, and the empirical expectation and variance are taken over the training mini-batches $\B$.
-
-The ST layer, defined in \eqnref{stat_layer}, independently transforms each of the $F$ feature maps of the input $\X \in \R^{N_{pix} \times F}$ into $\Y \in \R^{N_{stat} \times F}$, where $N_{stat}$ is the number of statistics.
+where $\gamma_{j}$ and $\beta_{j}$ are parameters to be learned and $\epsilon$ is a constant added for numerical stability.
+The empirical expectation $\esp(\x_i) \in \R$ and variance $\var(\x_i) \in \R$ are taken across training examples and pixels.
+% the action of gamma can be done by the filters of the next layer
+
+The statistical layer, defined in \eqnref{stat_layer}, independently transforms each of the $F$ feature maps of the input $\X \in \R^{N_{pix} \times F}$ into $\Y = ST(\X) \in \R^{N_{stat} \times F}$, where $N_{stat}$ is the number of statistics.
 One may even omit the FC layers and directly fed the output of the ST layer into the softmax layer, as proposed by \citet{lin2013globalavgpooling}.
-In this regime, $N_{stat} = 1$ and $F$ should be equal to the number of classes to discriminate, i.e., the last GC layer outputs as many feature maps as there is classes.
-
-A FC layer takes as input $\x \in \R^{F_{in}}$ and outputs $\y \in \R^{F_{out}}$ as
+In this regime, $N_{stat} = 1$ and $F = N_{classes}$ is the number of classes to discriminate (i.e., the last GC layer outputs as many feature maps as there is classes).
+
+A FC layer takes as input $\x \in \R^{F_{in}}$ and outputs
 \begin{equation*}
-	\y = \b W \x + \b b,
+	\y = FC(\x) = \b W \x + \b b \in \R^{F_{out}} ,
 \end{equation*}
@@
 The softmax layer is the last layer in a neural network engineered for classification.
-Given the output $\x \in \R^{N_{classes}}$ of the last FC, called the logits in the deep learning literature, the softmax layer outputs
+Given the output $\x \in \R^{N_{classes}}$ of the last FC (or ST), called the logits in the deep learning literature, the softmax layer outputs $\y = SM(\x)$ such that
 \begin{equation*}
@@
 
-GC32 - P256 - FC10
-
-All those parameters are learned during training via back-propagation of the error gradient.
-The whole network is then optimized to minimize the loss function over the training data.
-The gradient w.r.t.\ all the parameters is computed by back-propagation, and the values are updated by stochastic gradient descent (SGD).
-Describe the loss function. It's a measure of how far the predictions $\y$ from the softmax are from the true labels $\b \delta_i$. KL-divergence.
+\todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
+
+Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers (an example is $NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC$) and $\theta$ is the set of all trainable parameters.
+The number of features $F$ depends on the data at hand.
+For the CMB radiation temperature, $F = 1$.
+For observations in radio frequencies, $F$ would be equal to the number of surveyed frequencies.
+$F$ might also be the number of slices in the radial direction.
+The loss function $\ell(\y) = \ell(NN_\theta(\X))$ is a measure of how good the prediction $\y$ is for the sample $\X$. For a classification task, the loss is usually taken to be the cross-entropy
+\begin{equation*}
+	\ell(\y) = -\log(y_i),
+\end{equation*}
+where $i$ is the correct class label.
+The parameters $\theta$ of the neural network are optimized to minimize the loss over the training dataset $\left\{ \X_i \right\}_{i=1}^{N_{samples}}$:
+\begin{equation*}
+	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell(NN_\theta(\X_i)).
+\end{equation*}
+The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
+\begin{equation*}
+	\theta^{(k+1)} = \theta^{(k)} - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
+\end{equation*}
+where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch. Batches are used instead of single samples for faster training.
 

### 2018-07-24 scnn.tex
update figure

@@
 Convolutional Neural Networks (CNNs) are now a cornerstone of the Deep Learning toolbox and have led to many breakthroughs in Artificial Intelligence.
-These networks have so far been developed mostly for regular Euclidean domains such as those supporting images, audio, or video.
-CNN-based methods are becoming increasingly popular in Cosmology.
-Cosmological data often comes in a form of spherical maps, which makes the use of CNNs more complicated.
-A popular format for spherical maps is HEALPix, which uses an equal-area, isolatitude sampling.
-We present a spherical CNN for analysis of full and partial HEALPix maps, which we call HealpixNet.
+So far, these networks have mostly been developed for regular Euclidean domains such as those supporting images, audio, or video.
+Because of their success, CNN-based methods are becoming increasingly popular in Cosmology.
+Nevertheless, cosmological data often comes in a form of spherical maps, which makes the use of traditional CNNs impractical and complicated.
+Typically, the spherical format for spherical maps is HEALPix, which uses an equal-area, isolatitude sampling.
+As a response to this gap, we present a spherical CNN for analysis of full and partial HEALPix maps, which we call HealpixNet.
 We construct a spherical CNNs by representing the sphere as a graph.
 Graphs are versatile data structures which can represent pairwise relationships between objects or act as a discrete representation of a continuous manifold.
-For that graph, we define many of the standard CNN operations, such as convolution and pooling, with the filters restricted to being radial.
+Leveraging the graph, we define many of the standard CNN operations, such as convolution and pooling, with the filters restricted to being radial.
 HealpixNet is a special case of a graph CNN, tailored to the HEALPix sampling of the sphere.
@@
 % This approach is computationally more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
-We demonstrate the method on a classification problem of mass maps from two cosmological models.
-We compare the performance of the CNN with that of two baseline classifiers, based on the power spectrum and pixel density histogram.
-We find the performance of HealpixNet to always better or equal to both of these baselines.
+We demonstrate the method on a classification problem of mass maps from two cosmological models and compare the performance of the CNN with that of two baseline classifiers, based on the power spectrum and pixel density histogram.
+Our experimental result show that the performance of HealpixNet to always better or equal to both of these baselines.
 For high noise levels and for data covering only a smaller fraction of the sphere, HealpixNet achieves typically 10\% better classification accuracy than those baselines.
-Finally, we visualise filters learned by the HealpixNet from the mass maps.
+Finally, we propose a visualization of filters learned by the HealpixNet from the mass maps as some analysis tool for the neural network.
 Code and examples are available at \todo{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}.
@@
 \begin{keyword}
-Spherical Convolutional Neural Network \sep SCNN \sep HealpixNet \sep Graph CNN
+Spherical Convolutional Neural Network \sep SCNN \sep HealpixNet \sep Graph CNN \sep \nati{@Tomek: could you put some cosmo keywords?}
 \end{keyword}
@@
 \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+    \item (TK) check all the colored stuff left for you
 
@@
     \item (NP) Finalise readme on Github code
-    \item (NP) Finalize the data on zenodo
-    \item (NP) Do the download script
+    \item (Waiting for Zenodo) (NP) Finalize the data on zenodo
+    % \item (Done) Do the download script
     \item TK check part sphere notebook and whole sphere
@@
 	\caption{Overall network architecture, showing here two convolutional layers acting as feature extractors followed by a fully connected layer with softmax acting as the classifier.
-A convolutional layer is based on five operations: convolution, non-linearity, batch normalization, down-sampling, and pooling.
+\nati{add the stat layer?} A convolutional layer is based on five operations: convolution, non-linearity, batch normalization, down-sampling, and pooling.
 While most operations are agnostic to the data domain, the convolution and the down-sampling have to be adapted.
@@
 for example}, \nati{@Tomek, do you have a citation for that?
-Otherwise, we need to reformulate this.} it is more natural and accurate to work directly on the sphere.
+Otherwise, we need to reformulate this.} \nati{Cite the paper of Janis?} it is more natural and accurate to work directly on the sphere.
 

### 2018-07-24 scnn.tex
small changes

@@
     \item (TK) check all the colored stuff left for you
-
+    \item (TK) add small description of maps\_downsampled_64.npz in the whole\_sphere notebook.
     \item (TK) update the README for data zip - file from NP
@@
     \item (Waiting for Zenodo) (NP) Finalize the data on zenodo
-    % \item (Done) Do the download script
     \item TK check part sphere notebook and whole sphere
@@
     \item NP move the repo to HealpixNet
-
     \item (TK) make the bibliography display only a few name
 	\item check if papers which appear as arxiv were not published in a conference or journal
-    % \item (yes) Michael, do you agree with the title HealpixNet?
-I (Michaël) extensively modified the abstract to reflect that it is a special case of graph CNNs tailored to Healpix.
-Hence I now agree with the title.
-Feel free to edit.
-Ideally I'd like to have "graph" in the title (graph CNNs are quite hot these days), but I couldn't find how.
-    % \item Emphasize the novelty of using it on Healpix in abstract, into and rest of the paper
     \item (TK) add info on comparison with histograms, so that it's just a demonstration
-    % \item Finish section on Convolutions on graphs (Michael - Nathanael)
-    % \item finish section on Efficient convolutions (Michael)
-    % \item (done) Plot of the new filters from Mass maps
-    % \item (done!, plot to be added) check the power spectrum after smoothing
-    % \item (done!) upgrade the plot of pooling (Nathanael)
     \item (TK) possibly improve plot of pooling
-	% \item (done!) new plot for network structure (teaser plot) (Michael) What do you think?
-Todo: link the points on the sphere to the fully connected \nati{I like the plot, but I am thinking about putting multiple spheres with different maps for the convolutiion instead…}
     \item (TK NP) if we have time make a new candidate for network plot (optional)
-    % \item (done!) Figure 1 to be round
     \item (first version done) conclusions
-    % \item (done!) new simulations with 3 arcmin smoothing
-    % \item (done!) simulation with cross-validation for the histogram
-    % \item (done!) Update result section according to the new simulations...
-    % \item (done!) simulation PSD
-    % \item (done!) Results figure, add sigma8
-    % \item (more or less done!) possibly move the eigen decomposition and heat into appendix + add discussion (Nathanael I am not sure about the heat diffusion example...)
-    \item Should the heat example go to appendix
+    \item Should the heat example go to appendix?
     \item TK read the heat section again
@@
 These shells can span the radial direction, so that a tomographic analysis can be performed, or different frequencies, in case of data from observations in radio frequencies.
+\nati{I do not know about that last point.
+Yes we can do it.
+But a) we did not do it and b) the filter will be spherical in all directions includeding the radial one...
+I am not sure this is a disirable features.}
 

### 2018-07-24 scnn.tex
small batch norm edit
small manifold edit

--- 2018-07-24 scnn.tex
@@
 The main idea is to represent the sphere $S^2$, a 2-dimensional manifold embedded in $\mathbb{R}^3$, as a graph of connected pixels.
+The length (or weight) of the shortest path between two pixels is an approximation of the geodesic distance between them on the manifold.
 This contribution leverages the emerging field of graph signal processing which defines fundamental signal processing tools such as the Fourier transform for signals defined on graphs \citep{shuman2013emerging}.
@@
 \begin{equation*}
-	\theta^{(k+1)} = \theta^{(k)} - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
+	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
 \end{equation*}
-where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch. Batches are used instead of single samples for faster training.
+where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch.
+Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.
 

### 2018-07-24 scnn.tex
small experiments edit

@@
 While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
-\todo{(i) scale of $\theta_k$: they are mostly constant for Chebyshev polynomials. How are they for monomials?}
+\todo{(i) scale of $\theta_k$: they are mostly uniform for Chebyshev polynomials, end exploding for monomials. Though SGD implicitly imposes a uniform prior on the learned parameters.}
 \todo{(ii) numerical stability of $\L^k \f$ v.s. $T_k(\L) \f$}
@@
 % 4) Describe the result
-In this section, we demonstrate the performance of the spherical neural network on a discrimination problem. Nevertheless, by simply changing the loss, one could use the network for regression.
-Our implementation is available as a small python package \url{https://our.code.link.com}.
-Furthermore, all the data to reproduce our experiments are available online.\footnote{\url{https://doi.org/10.5281/zenodo.1303272} \todo{Check DOI}}.
-
-In our experiments we classify convergence maps, similar to those created with gravitational lensing technique \citep{chang2017curvedsky}.
+In this section, we demonstrate the performance of the spherical neural network on a discrimination problem: the classification of convergence maps, similar to those created with gravitational lensing technique \citep{chang2017curvedsky}.
+Nevertheless, by simply changing the loss, one could use the network for regression.
+Both our Python implementation\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments is available online.
 

### 2018-07-24 scnn.tex
fix small bug

@@
     \item (TK) check all the colored stuff left for you
-
+    \item (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook.
     \item (TK) update the README for data zip - file from NP

### 2018-07-24 scnn.tex
draft related work

@@
 Deep Learning has recently gained popularity as an analysis tool in cosmology \citep{schmelze2017cosmologicalmodel,luciesmith2018machinelearning,gupta2018nongaussianinformation,gillet2018deeplearning,hassan2018reionizationmodels,aragoncalvo2018classyfyinglarge,ciuca2017cnnstring}, thanks to its ability to capture complicated, non-linear patterns which are often present in the data.
-Convolutional Neural Networks (CNNs) are particularly well suited for analysis of cosmological data due to the translation equivariance built into their architecture.
-Indeed, sky maps are translation equivariant, which means that rotating maps on the sphere doesn't change their interpretation.
+Convolutional Neural Networks (CNNs) are particularly well suited for analysis of cosmological data due to the translation invariance built into their architecture.
+Indeed, sky maps are translation invariant, which means that translating and rotating maps on the sphere doesn't change their interpretation.
 Only the statistics of the maps is relevant.
@@
 Otherwise, we need to reformulate this.} \nati{Cite the paper of Janis?} it is more natural and accurate to work directly on the sphere.
+The main challenge in designing a CNN on the sphere is to define a convolution which is suitable to this irregularly sampled domain.
 
@@
 A first attempt to generalize CNNs to spherical data was to apply a standard 2D CNN to a grid discretization of the sphere~\citep{boomsma2017spherical}.
-While this approach leverages the well-developed 2D convolution and hierarchical pooling, it is restricted to those very specific grid samplings which are highly irregular on the sphere.
+While this approach leverages the well-developed 2D convolution and hierarchical pooling, it is restricted to those specific grid samplings which are highly irregular on the sphere.
 A second attempt by~\citet{cohen2018spherical} was to leverage the spherical Fourier transform and to perform the convolution in the spectral domain, thanks to the convolution theorem.
@@
 
-\subsection{Spherical convolutions and spherical CNNs}
-\label{sec:spherical_conv}
-The major challenge to define Convolution Neural Network (CNN) onto a
-spherical domain is to handle a convolution that is suitable for this irregular sampling domain.
-Three approaches exist to address this issue.
+\citet{boomsma2017spherical} apply a standard 2D CNN to a grid discretization of the sphere.
+Two grids (illustrated in \figref{sphere_grids}) are used in their paper: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}.
+As this formulation leverages standard 2D convolutions, all the optimizations developed for images make it computationally very efficient.
+It is however restricted to those grid sampling sets.
+Similarly to the cubed-sphere, HEALPix is a composition of twelve grids.
+While each of those twelve grids can be independently fed to a 2D CNN, boundary conditions should be properly handled as those grids are not independent.
+\todo{How do thy handle boundaries?}
+% Furthermore, the grid requirement makes it impossible for the convolution to capture the spherical properties of the domain, i.e., the cubed-sphere sampling is by definition adapted to a cube and not to a sphere.
+Moreover, those samplings are not ideal as their resolution is not constant across the sphere.
+Indeed, the singularities --- the poles for the equirectangular grid, the corners of the cube for the cubed-sphere --- are over-sampled.
+Equal areas of discrete elements is advantageous for physical measurements as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence \citep{gorski2005healpix}.
+% \nati{Michael: Under some very specific hypothesis, this second approach is a particular case of our method, i.e.
+(i) our method with a stupid sampling, (ii) assumption that graph convolution on a grid == 2d convolution.
+Do you think we should mention that?
+I think we should not.}
+Finally, a 2D CNN learns directional filters which orientation is arbitrary.
+Indeed, directions, which make much sense for images (up, down, left, and right), are arbitrarily defined when setting the origin of the grids on the sphere.
+Any convolution using directions on the sphere is not equivariant to translation and rotation.
 
@@
 
-The first approach, leveraging the continuous spherical convolution, has been proposed by~\citet{cohen2018spherical}.
+\citet{cohen2018spherical} leverages the continuous spherical convolution.
 The goal of this contribution was to define a rotation-equivariant convolution on the sphere, i.e., a rotation of the input implies the same rotation in the output.
@@
 
-A second direction has been followed in~\citet{boomsma2017spherical}. The idea is
-to use the traditional 2-dimensional convolution on an irregular grid defined on the
-sphere. In the paper, two grids are used: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}. See \figref{sphere_grids}. Because this
-approach is based on the classic 2-dimensional convolution, it benefits from all the optimizations developed for images and is very likely to be 
-the most computationally efficient one. However, it suffers that it can only be used using very
-specific grid sampling sets which are not including HEALPix. Furthermore, the
-grid requirement makes it impossible for the convolution to capture the
-spherical properties of the domain, i.e., the cubed-sphere sampling is by
-definition adapted to a cube and not to a sphere.
-Those samplings are not ideal as their resolution is not constant across the sphere.
-Indeed, the singularities --- the poles for the equirectangular grid, the corners of the cube for the cubed-sphere --- are over-sampled.
-Equal areas of discrete elements is advantageous for physical measurements as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence.
-% \nati{Michael: Under some very specific hypothesis, this second approach is a particular case of our method, i.e.
-(i) our method with a stupid sampling, (ii) assumption that graph convolution on a grid == 2d convolution.
-Do you think we should mention that?
-I think we should not.}
-
 In an attempt to get the best of the first two approaches, we follow a third
@@
 
-\subsection{Convolutions on graphs}
-\todo{Maybe we just describe convolutions on sphere and graph, i.e.: do we really need all these three subsections? Maybe simply merge them?}
-
-\nati{I think that citing Bruna is to much... According to me, the goal of this subsection should not be to cite everything that exist. But should focus on
-1) be fair and say that they are other graph convolutions that can be used, 2) show some connections between graph CNNs ang group equivariant CNNs (Done), and 3) suggest that they are possible extensions of what we do.}
-
-\assign{Michaël}
-
-\todo{other approaches? GNNs, Kipf first order approx, message passing}
+There exists many formulations of graph neural networks, reviewed by \citet{bronstein2017review} and \citet{hamilton2017review}.
+For this contribution, we chose the formulation of \citet{defferrard2016convolutional} as its root on strong graph signal processing theory makes the concept of convolutions and filters explicit \citep{shuman2013emerging}.
+Its tie to a graph Fourier transform allows us to compare with the spherical harmonic transform, and study its invariance properties.
+More geometric than permutation invariant aggregation.
+A contrario, formulations with exploit the tengant space of manifolds define a local coordinate system.
+While this formulation of convolution can learn anisotropic filters, it is not equivariant to translation.
+\todo{better wording}
+\todo{three main interpretations: gsp, Bronstein manifold tangent plane, message passing, permutation invariant aggregation, spatial formulations}
+Bronstein is a spatial formulation where the registration is done by projection on the tangent plane.
+% Not Bronstein's manifold approach as we want a Fourier basis to compare to the spherical harmonics.
+% Be as close as possible to spherical harmonics.
+Related to this, convolutional neural networks have been defined on manifolds and have achieved impressive results on shapes [Bronstein].
+They however too depend on an orientation, which spheres do not possess.
+
+% Anisotropic cannot be invariant
 
 The connection has recently been made between graph CNNs and group equivariant CNNs \cite{kondor2018equivariance}, justifying the use of graphs to gain rotation equivariance on the sphere.
-
-Previous work: [Bruna] which needed the full eigendecomposition of the Laplacian, costing $O(n^3)$ operations.
 
@@
 There is no good default good orientation on general graphs and the choice of an orientation is highly application dependent.
-
-\subsection{Convolutions on manifolds}
-
-Related to this, convolutional neural networks have been defined on manifolds and have achieved impressive results on shapes [Bronstein].
-They however too depend on an orientation, which spheres do not possess.
-
-\subsection{Convolutions on point clouds?}
-
-PointNet and co. Related but we are loosing the structure. Also coarsening.
 

### 2018-07-24 scnn.tex
added figure

--- 2018-07-24 scnn.tex
@@
     % \includegraphics[width=\linewidth]{architecture}
-	\includegraphics[width=\linewidth]{figure_architecture}
+	\includegraphics[width=\linewidth]{figure_architecture_v2}
 	\caption{Overall network architecture, showing here two convolutional layers acting as feature extractors followed by a fully connected layer with softmax acting as the classifier.
@@
 The main idea is to represent the sphere $S^2$, a 2-dimensional manifold embedded in $\mathbb{R}^3$, as a graph of connected pixels.
-The length (or weight) of the shortest path between two pixels is an approximation of the geodesic distance between them on the manifold.
 This contribution leverages the emerging field of graph signal processing which defines fundamental signal processing tools such as the Fourier transform for signals defined on graphs \citep{shuman2013emerging}.
@@
 While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
-\todo{(i) scale of $\theta_k$: they are mostly uniform for Chebyshev polynomials, end exploding for monomials. Though SGD implicitly imposes a uniform prior on the learned parameters.}
+\todo{(i) scale of $\theta_k$: they are mostly constant for Chebyshev polynomials. How are they for monomials?}
 \todo{(ii) numerical stability of $\L^k \f$ v.s. $T_k(\L) \f$}
@@
 \begin{equation*}
-	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
+	\theta^{(k+1)} = \theta^{(k)} - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
 \end{equation*}
-where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch.
-Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.
+where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch. Batches are used instead of single samples for faster training.
 
@@
 % 4) Describe the result
-In this section, we demonstrate the performance of the spherical neural network on a discrimination problem: the classification of convergence maps, similar to those created with gravitational lensing technique \citep{chang2017curvedsky}.
-Nevertheless, by simply changing the loss, one could use the network for regression.
-Both our Python implementation\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments is available online.
+In this section, we demonstrate the performance of the spherical neural network on a discrimination problem. Nevertheless, by simply changing the loss, one could use the network for regression.
+Our implementation is available as a small python package \url{https://our.code.link.com}.
+Furthermore, all the data to reproduce our experiments are available online.\footnote{\url{https://doi.org/10.5281/zenodo.1303272} \todo{Check DOI}}.
+
+In our experiments we classify convergence maps, similar to those created with gravitational lensing technique \citep{chang2017curvedsky}.
 

### 2018-07-24 scnn.tex

--- 2018-07-24 scnn.tex
@@
 
+A second direction has been followed in~\citet{boomsma2017spherical}. The idea is
+to use the traditional 2-dimensional convolution on an irregular grid defined on the
+sphere. In the paper, two grids are used: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}. See \figref{sphere_grids}. Because this
+approach is based on the classic 2-dimensional convolution, it benefits from all the optimizations developed for images and is very likely to be
+the most computationally efficient one. However, it suffers that it can only be used using very
+specific grid sampling sets which are not including HEALPix. Furthermore, the
+grid requirement makes it impossible for the convolution to capture the
+spherical properties of the domain, i.e., the cubed-sphere sampling is by
+definition adapted to a cube and not to a sphere.
+Those samplings are not ideal as their resolution is not constant across the sphere.
+Indeed, the singularities --- the poles for the equirectangular grid, the corners of the cube for the cubed-sphere --- are over-sampled.
+Equal areas of discrete elements is advantageous for physical measurements as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence.
+% \nati{Michael: Under some very specific hypothesis, this second approach is a particular case of our method, i.e.
+(i) our method with a stupid sampling, (ii) assumption that graph convolution on a grid == 2d convolution.
+Do you think we should mention that?
+I think we should not.}
+
 In an attempt to get the best of the first two approaches, we follow a third

### 2018-07-25 scnn.tex
work in section 4

@@
 \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+    \item (NP) Figures  A.15, 6, 5
     \item (TK) check all the colored stuff left for you
@@
 \end{equation*}
-is the average Euclidean distance over all connected pixels.
-This weighting scheme is important as while pixel areas are equal, distances between pixels are not equal.
+is the average Euclidean distance over all connected pixels. This weighting scheme is important as while pixel areas are equal, distances between pixels are not.
+Other weighting schemes are possible. For example,~\cite{khasanova2017graphomni} uses the inverse of the distance instead. We found out that the one proposed above works fine for our purpose.
 \figref{healpix_graph_4} shows a graph constructed from the HEALPix sampling of a sphere.
@@
 We should rather come up with a definition of distance that will make the eigenvectors closer to the real spherical harmonics.
+% Agreed: I added a reference to Pascal paper.
 
@@
 \end{equation*}
-is a measure of how smooth the eigenvector $\b u_i$ is on the graph defined by the Laplacian $\L$.
+is a measure of the variation of the eigenvector $\b u_i$ is on the graph defined by the Laplacian $\L$.
 
@@
 	\caption{The first 16 Fourier modes (eigenvectors of the graph Laplacian) of a graph constructed from the HEALPix sampling of the sphere.
-Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$ and order $m=(-1,0,1)$, eigenvectors 4--8 with degree $\ell=2$ and order $m=(-2,-1,0,1,2)$, and eigenvectors 9--15 with degree $\ell=3$ and order $m=(-3,\ldots,3)$.
-Nevertheless, the graph eigenvectors are only approximating the real spherical harmonics.}
+Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$ and order $|m|=(0,1)$, eigenvectors 4--8 with degree $\ell=2$ and order $|m|=(0,1,2)$, and eigenvectors 9--15 with degree $\ell=3$ and order $|m|=(0,1,2,3)$.
+Nevertheless, the graph eigenvectors are \emph{only approximating} the real spherical harmonics.}
 	\label{fig:graph_harmonics}
@@
 \begin{equation} \label{eqn:graph_convolution}
-	h(L) \f = \U h(\bLambda) \U\trans \f,
+	h(\L) \f = \U h(\bLambda) \U\trans \f,
 \end{equation}
@@
 It can however be localized on any vertex $v_i$ by the convolution with a Kronecker delta $\b \delta_i \in \R^{N_{pix}}$,\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} that is $h(\L) \b \delta_i$, a column of $h(\L)$.
-That is useful to visualize kernels. \todo{nath: link with appendix}
+This localization can be useful to visualize kernels as explained in~\ref{sec:filter_visualization}.
 If the graph is not regular, i.e., all nodes don't have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another.
@@
 \begin{equation} \label{eqn:graph_convolution_spatial}
-	(h(L) \f)_i = \langle h(L) \b \delta_i, \f \rangle.
+	(h(\L) \f)_i = \langle h(\L) \b \delta_i, \f \rangle.
 \end{equation}
-
-\paragraph{Example}
+\textbf{Example.}
 Let us consider the heat diffusion problem
@@
 which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(\lambda)=e^{-\tau t \lambda}$.
-Here the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$, which are a generalization of squared frequencies.
-Hence, the kernel $K_t$ can also be considered as a generalization of the Gaussian kernel on the sphere.
+Since the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$, which can be interpreted as squared frequencies, it can also be considered as a generalization of the Gaussian kernel on the sphere.
 \figref{gaussian_filters_comparizon} shows the effect of the convolution by diffusing a unit of heat for $\tau=1$ at various times $t$.
 By comparing the graph convolution with the spherical symmetric Gaussian smoothing, we observe that both techniques lead to similar results (see \figref{gaussian_filters_comparizon}).
-While the graph convolution is different from a true spherical convolution, it can, provided the correct parameterization, well approximate it.
-\figref{gaussian_filters_visualization} provides additional visualizations of the convolution kernel $K_t$.
+While the graph convolution remains different from the spherical convolution, this small experiment shows that, providing the correct parameters, graph convolution can approximate spherical convolution.
+For additional insides about the graph kernel $K_t$, we refer to the \figref{gaussian_filters_visualization} and~\ref{sec:filter_visualization}.
 
@@
 	Relative difference between graph convolution and spherical smoothing: $10.4$\%, $5.7$\%, $4.8$\%, $3.8$\%.
-	\todo{(i) Only three diffusion steps to have a bigger figure?}
+	\todo{(i) Only three diffusion steps to have a bigger figure? \nati{Agreed! Will do soon!}}
 \todo{(ii) The main issue with our filters is that their shape depends on the localization.
 It would be nice to measure the expectation and variance of the error over all locations.
-That would show how severe the distortion is.}}
+That would show how severe the distortion is.}
+\nati{Let us keep that for the next paper. I am quite sure, it is negligible in this particular case.}}
 	\label{fig:gaussian_filters_comparizon}
@@
 
-This result is another sign that the constructed graph is able to capture the spherical
+Furthermore, this result is another sign that the constructed graph is able to capture the spherical
 structure of the HEALPix sampling. In some applications, where the
@@
 
-To overcome those computational issues, the convolution kernel $h$ can be defined as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parameterized by $K+1$ coefficients $\theta$.
-The filtering operation \eqnref{graph_convolution} then becomes
+Forunately, both of these computational issues can be overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parameterized by $K+1$ coefficients $\theta$.
+In that specific case, the filtering operation \eqnref{graph_convolution} becomes
 \begin{equation} \label{eqn:graph_convolution_polynomial}
-	h_\theta(\L) \f = \sum_{k=0}^K \theta_k \L^k \f.
+	h_\theta(\L) \f =  \U \left(\sum_{k=0}^K \theta_k \bLambda^k \right) \U\trans \f = \sum_{k=0}^K \theta_k \L^k \f,
 \end{equation}
+an operation requiring $k$ multiplication of the graph Laplacian matrix $\L$.
+In our case, the Laplacian is extremly sparse ($8-9$ entries per line), making the filtering operation for a fixed $k$ linear in the number of pixel $N_{pix}$.
 Here happens the transition from filtering in the spectral domain to filtering in the vertex domain.

### 2018-07-25 scnn.tex
work in section 4

@@
 In our case, the Laplacian is extremly sparse ($8-9$ entries per line), making the filtering operation for a fixed $k$ linear in the number of pixel $N_{pix}$.
-Here happens the transition from filtering in the spectral domain to filtering in the vertex domain.
-Note that $\L^k$ captures $k$-neighborhoods, i.e., $(\L^k)_{ij}$ is non-zero if and only if nodes $v_i$ and $v_j$ are connected by a path of length $k$.
-As such, filtering with a polynomial convolution kernel can be interpreted in the vertex domain as a local weighted linear combination of the signal's value.
-The weights are determined by the filter coefficients $\theta$ and the path weight, defined as the multiplication of all edge weights along the path.
-\todo{Better vertex domain explanation.}
+Moreover, here happens the transition from filtering in the spectral domain to filtering in the vertex domain.
+The matrix $\L^k$ captures $k$-neighborhoods of each pixel, i.e., $(\L^k)_{ij}$ is non-zero if and only if nodes $v_i$ and $v_j$ are connected by a path of length $k$.
+As such, filtering with a polynomial convolution kernel can be interpreted in the pixel (vertex) domain as a weighted linear combination of the pixels neighboors values.
+The weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$.
+\todo{Better vertex domain explanation. \nati{I gave it a try}}
 

### 2018-07-25 scnn.tex
update in section 4

@@
 an operation requiring $k$ multiplication of the graph Laplacian matrix $\L$. 
-In our case, the Laplacian is extremly sparse ($8-9$ entries per line), making the filtering operation for a fixed $k$ linear in the number of pixel $N_{pix}$.
+In our case, the Laplacian is extremly sparse ($8-9$ entries per line), making the filtering operation for a fixed $K$ linear in the number of pixel $N_{pix}$.
 Moreover, here happens the transition from filtering in the spectral domain to filtering in the vertex domain.
 The matrix $\L^k$ captures $k$-neighborhoods of each pixel, i.e., $(\L^k)_{ij}$ is non-zero if and only if nodes $v_i$ and $v_j$ are connected by a path of length $k$.
-As such, filtering with a polynomial convolution kernel can be interpreted in the pixel (vertex) domain as a weighted linear combination of the pixels neighboors values.
+As such, filtering with a polynomial convolution kernel can be interpreted in the pixel (vertex) domain as a weighted linear combination of the pixels neighbors values.
 The weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$.
-\todo{Better vertex domain explanation. \nati{I gave it a try}}
-
-To make the parallel with classical Euclidean signal-domain convolution, i.e., filtering by multiplying the signal with translated versions of a patch, we here match our filter at the level of neighborhoods\footnote{The 1-neighborhood of a node is the set of nodes which are directly connected to it.
+We note that restricting the graph convolutional kernel to a polynomial is similar to restricting the classical Euclidean signal-domain convolution to a patch.
+In the classical setting, the convolution with a patch is simply a weighted sum of the neighbors with the weights defined by the patch.
+Similarly, each lines of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an "irregular patch of radius $K$" for our irregular domain.
+\todo{Better vertex domain explanation. \nati{I gave it a try. Should we take a single vertex and explain what heppens to it? Note that I suppressed the following paragraph. }}
+
+% To make the parallel with classical Euclidean signal-domain convolution, i.e., filtering by multiplying the signal with translated versions of a patch, we here match our filter at the level of neighborhoods\footnote{The 1-neighborhood of a node is the set of nodes which are directly connected to it.
 The 2-neighborhood is the set of nodes which are connected through paths of length 2.} rather than individual nodes.
@@
 While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
+In practice, we found out that Chebyshev polynomials are slightly more stable in our experiment.
+We believe that this is due to their orthogonality (as explained above) and uniformity\footnote{The amplitude of Chebyshev polynomials is more or less constant over the domain $[-1, 1]$ independently of the order $k$.
+On the contrary the amplitude of $x^k$ is very different for $|x|\approx 0$ and $|x| \approx 1$.}.
+\nati{I added a sentence and I think we should not give much more details here. If we do an experiment, we can comment in the experiment section.}
 \todo{(i) scale of $\theta_k$: they are mostly uniform for Chebyshev polynomials, end exploding for monomials. Though SGD implicitly imposes a uniform prior on the learned parameters.}
@@
 Coarsening defines $\C(i)$, the set of children of node $v_i$.
-For the HEALPix subdivision scheme, the number of children is constant, i.e., $| \C(i) | = 4^k \ \forall i$, for some $k$.
+For the HEALPix subdivision scheme, the number of children is constant, i.e., $| \C(i) | = 4^p \ \forall i$, for some $p$.
 
@@
 \end{equation}
-where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix} / {N_{pix}}'$ is the down-sampling factor\footnote{$| \C(i) | = N_{pix} / {N_{pix}}' = (N_{side} / N'_{side})^2 = 4^k$ for HEALPix.}.
+where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix} / {N_{pix}}'$ is the down-sampling factor\footnote{$| \C(i) | = N_{pix} / {N_{pix}}' = (N_{side} / N'_{side})^2 = 4^p$ for HEALPix.}.
 That operation is often taken to be the maximum value, but it might be any permutation invariant operation such as the sum or the average.
@@
 Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the probability that the input sample belongs to class $i$.
-That last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.
-
-\todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
+This last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.
 
@@
 
+\nati{4.8 is long... Should we go in such details?}
+\todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
+
 \section{Experiments}

### 2018-07-25 scnn.tex
smaller sphere figures

@@
 
+\begin{figure}
+	\centering
+	\includegraphics[height=7em]{sphere_grid_equirectangular}
+	\hfill
+	\includegraphics[height=7em]{sphere_grid_cubedsphere}
+	\hfill
+	\includegraphics[height=7em]{half_graph_4}
+	\caption[]{Some pixelizations of the sphere.
+Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system.
+Middle: an equiangular cubed-sphere grid, as described in \citet{ronchi1996cubed}.
+Right: graph built from an HEALPix pixelization of half the sphere ($N_{side} = 4$).
+By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[7] Left and middle figures are taken from \citet{boomsma2017spherical}.}
+	\label{fig:sphere_grids}
+	\label{fig:healpix_graph_4}
+\end{figure}
+
 % As presented by~\cite{cohen2018spherical}, the most mathematical approach to extend the convolution on a sphere is to use a spherical Fourier transform.
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{sphere_grids}
-	\caption{Two realizations of a grid on the sphere.
-Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system.
-Right: An equiangular cubed-sphere grid, as described in \citet{ronchi1996cubed}.
-Figure from \citet{boomsma2017spherical}.}
-	\label{fig:sphere_grids}
-\end{figure}
-
 A second direction has been followed in~\citet{boomsma2017spherical}. The idea is
@@
 % Agreed: I added a reference to Pascal paper.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\linewidth]{half_graph_4}
-	\caption[]{Graph built from an HEALPix pixelization of half the sphere ($N_{side} = 4$). By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[6]}
-	\label{fig:healpix_graph_4}
-\end{figure}
 

### 2018-07-25 scnn.tex
update eqn 5

@@
 \begin{equation} \label{eqn:graph_convolution_cheby}
-	h_\theta(\tL) \f = \sum_{k=0}^K \theta_k T_k(\tL) \f,
+	h_\theta\left(\tL\right) \f = \U \left(\sum_{k=0}^K \theta_k T_k\left(\tilde{\bLambda}\right) \right) \U\trans \f = \sum_{k=0}^K \theta_k T_k\left(\tL\right) \f,
 \end{equation}
-where $\tL = \frac{2}{\lambda_{max}} \L - \b{I} = -\frac{2}{\lambda_{max}} \D^{-1/2} \W \D^{-1/2}$ is the rescaled Laplacian with eigenvalues in $[-1, 1]$ and $T_k(\cdot)$ is the Chebyshev polynomial of degree $k$, defined by the recursive relation $T_k(\tL) = 2\tL T_{k-1}(\tL) - T_{k-2}(\tL)$, $T_1(\tL) = \tL$, $T_0(\tL) = \b{I}$.
+where $\tL = \frac{2}{\lambda_{max}} \L - \b{I} = -\frac{2}{\lambda_{max}} \D^{-1/2} \W \D^{-1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\b \Lambda}$ in $[-1, 1]$ and $T_k(\cdot)$ is the Chebyshev polynomial of degree $k$, defined by the recursive relation $T_k(\tL) = 2\tL T_{k-1}(\tL) - T_{k-2}(\tL)$, $T_1(\tL) = \tL$, $T_0(\tL) = \b{I}$.
 While definitions \eqnref{graph_convolution_polynomial} and \eqnref{graph_convolution_cheby} both allow the representation of the same set of filters, Chebyshev polynomials are preferred as they form an orthogonal basis on the interval $[-1, 1]$.

### 2018-07-25 scnn.tex
updated refs

--- 2018-07-25 scnn.tex
@@
 \begin{keyword}
-Spherical Convolutional Neural Network \sep SCNN \sep HealpixNet \sep Graph CNN \sep \nati{@Tomek: could you put some cosmo keywords?}
+Spherical Convolutional Neural Network \sep
+HealpixNet \sep
+Graph CNN \sep
+Cosmological data analysis \sep
+Mass mapping
 \end{keyword}
@@
     \item (NP) Figures  A.15, 6, 5
-    \item (TK) check all the colored stuff left for you
     \item (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook.
@@
     \item NP move the repo to HealpixNet
-    \item (TK) make the bibliography display only a few name
 	\item check if papers which appear as arxiv were not published in a conference or journal
     \item (TK) add info on comparison with histograms, so that it's just a demonstration
-    \item (TK) possibly improve plot of pooling
     \item (TK NP) if we have time make a new candidate for network plot (optional)
@@
 
-\todo{@Tomek: can you explain why we care about parts of the sphere? (that is an advantage of the graph model over the spherical harmonics)}
-\todo{@Tomek: How is the data acquired?
+For cosmological observations it is often the case that the data covers only a part of the sphere.
+For ground-based observations this can be due to limited visibility of the sky from a particular telescope location and survey strategy, and for space-based imagers due to masking of the galactic plane area.
+
+% \todo{@Tomek: can you explain why we care about parts of the sphere? (that is an advantage of the graph model over the spherical harmonics)}
+% \todo{@Tomek: How is the data acquired?
 Do telescopes and satellites take measurements according to the HEALPix sampling?
 (it is also an advantage of our method to be agnostic to the sampling, which might be useful to researchers working with missing data or different models)}
-\nati{@Tomek: I think what Michael has in mind is that the graph approach is very versatile and extendable.
+% \nati{@Tomek: I think what Michael has in mind is that the graph approach is very versatile and extendable.
 It can be used with other samplings (even irregular ones) or only part of the sphere.
@@
 As such, perhaps the most straightforward approach to the analysis of spherical data is to divide it into small chunks and project those on flat 2D surfaces.
-While this mostly works, as demonstrated \todo{in ???
-for example}, \nati{@Tomek, do you have a citation for that?
-Otherwise, we need to reformulate this.} \nati{Cite the paper of Janis?} it is more natural and accurate to work directly on the sphere.
+While this mostly works, as demonstrated by \citep{fluri2018deep,gupta2018nongaussianinformation,schmelze2017cosmologicalmodel,gillet2018deeplearning}, it may be more natural for some applications and accurate to work directly on the sphere.
 The main challenge in designing a CNN on the sphere is to define a convolution which is suitable to this irregularly sampled domain.
@@
 
-For all the
-experiments, we work with centered Gaussian noise. \todo{Tomek: could you put a
-justification.} To improve the
-stability of the spherical CNN, we slowly increase the amount of noise added to
+For all the experiments, we work with centered Gaussian noise.
+While the noise model is real mass maps often has a slightly different distribution, Gaussian should be a sufficient model to demonstrate the performance of our method.
+To improve the stability of the spherical CNN, we slowly increase the amount of noise added to
 the training data over the iterations. Furthermore in order to avoid
@@
 human perspective. The gnomonic projection clearly exibits the sampling issue
-of HEALPix. For a detail, on how the convolution kernels are plotted, please refer to Appendix~\ref{sec:filter_visualization}.
-\todo{Tomek: can you say something about the filters.}
+of HEALPix.
+For a detail, on how the convolution kernels are plotted, please refer to Appendix~\ref{sec:filter_visualization}.
+While it is usually difficult to interpret the shape of the filters in the context of the type of data, we can notice that they often have a ``peak'' like structures.
+An example of filter interpretation was demonstrated in \citep{Ribli2018learningfrom}.
+% \todo{Tomek: can you say something about the filters.}
+% \TK{Done }
 
@@
 
-As shown in this contribution, modeling the discretized sphere, a 2D manifold in $\R^3$, by a graph enables an efficient convolution operation on any pixelization.
+As shown in this contribution, modelling the discretized sphere, a 2D manifold in $\R^3$, by a graph enables an efficient convolution operation on any pixelization.
 Hence, it relaxes the iso-latitude constraint on sampling schemes who aim to enable fast convolutions.

### 2018-07-25 scnn.tex
remove duplicate text

@@
 % Furthermore, the grid requirement makes it impossible for the convolution to capture the spherical properties of the domain, i.e., the cubed-sphere sampling is by definition adapted to a cube and not to a sphere.
+Nope, the graph can adapt to any sampling.
 Moreover, those samplings are not ideal as their resolution is not constant across the sphere.
@@
 Those can however be mitigated by padding with zeros a small area around the measurements.
-
-A second direction has been followed in~\citet{boomsma2017spherical}. The idea is
-to use the traditional 2-dimensional convolution on an irregular grid defined on the
-sphere. In the paper, two grids are used: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}. See \figref{sphere_grids}. Because this
-approach is based on the classic 2-dimensional convolution, it benefits from all the optimizations developed for images and is very likely to be
-the most computationally efficient one. However, it suffers that it can only be used using very
-specific grid sampling sets which are not including HEALPix. Furthermore, the
-grid requirement makes it impossible for the convolution to capture the
-spherical properties of the domain, i.e., the cubed-sphere sampling is by
-definition adapted to a cube and not to a sphere.
-Those samplings are not ideal as their resolution is not constant across the sphere.
-Indeed, the singularities --- the poles for the equirectangular grid, the corners of the cube for the cubed-sphere --- are over-sampled.
-Equal areas of discrete elements is advantageous for physical measurements as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence.
-% \nati{Michael: Under some very specific hypothesis, this second approach is a particular case of our method, i.e.
-(i) our method with a stupid sampling, (ii) assumption that graph convolution on a grid == 2d convolution.
-Do you think we should mention that?
-I think we should not.}
 

### 2018-07-27 scnn.tex
update figures
todos

@@
 \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-    \item (NP) Figures  A.15, 6, 5
     \item (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook.
@@
 I am not sure this is a disirable features.}
+\todo{I think you got it wrong there. I guess the idea is that each shell would be a feature map, i.e., the graph signal would be multi-dimensional.}
 
@@
 	Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin).
-	Relative difference between graph convolution and spherical smoothing: $10.4$\%, $5.7$\%, $4.8$\%, $3.8$\%.
-	\todo{(i) Only three diffusion steps to have a bigger figure? \nati{Agreed! Will do soon!}}
-\todo{(ii) The main issue with our filters is that their shape depends on the localization.
+	Relative difference between graph convolution and spherical smoothing: $10.4$\%, $4.8$\%, $3.8$\%.
+\todo{The main issue with our filters is that their shape depends on the localization.
 It would be nice to measure the expectation and variance of the error over all locations.
@@
 
-\begin{figure*}[!ht]
+\begin{figure}[!ht]
 \centering
@@
 \label{fig:gaussian_filters_visualization}
-\end{figure*}
+\end{figure}
 

### 2018-07-27 scnn.tex
small modification in result section

@@
 
-\todo{learned histogram \citep{wang2016learnhist} if it shows good results}
-
-\todo{stats of diffused maps \citep{khasanova2017tigranet}. Provides stats at multiple scales?}
-
-\todo{perf w.r.t. different functions $f$. Here or in the experiment section?}
+Other statistical layers are possible.
+In particular, we also implemented a learned histogram from \citep{wang2016learnhist}.
+Additionaly \citep{khasanova2017tigranet} propose to apply differen diffusion on the final maps to obtain statistics at different sclaes.
 
@@
 The resulting PSD are displayed in \figref{psd_sigma3}.
-In the pre-processing step, we also remove the mean of each map.
+In the pre-processing step, we also remove the mean of each map and downsample them to a resolution of of $Nside=1024$.
 
@@
 For all the experiments, we work with centered Gaussian noise.
-While the noise model is real mass maps often has a slightly different distribution, Gaussian should be a sufficient model to demonstrate the performance of our method.
+While the noise model of real mass maps often has a slightly different distribution, Gaussian should be a sufficient model to demonstrate the performance of our method.
 To improve the stability of the spherical CNN, we slowly increase the amount of noise added to
@@
 Spectral Densities (PSD) and b) the histogram of pixels in the maps~\cite{patton2017cosmologicalconstraints}.
-After a normalization, those features are then classified use a Support Vector
+After a normalization, those features are then classified using a Support Vector
 Machine (SVM) with a linear kernel. Other kernels did not provide better results
-while having worse scaling properties. All classifiers are trained with noisy samples. For fairness, we augmented the dataset
+while having significanly worse scaling properties. All classifiers are trained with noisy samples. For fairness, we augmented the dataset
 of the baseline algorithm in a similar way as for the network, i.e, with
@@
 the noise. We stop adding new samples in the classifier once the validation
-error converge to a value. This process is detailed in Appendix~\ref{sec:dataset_augmentation}. We tuned the parameter using cross-validation with the validation set.
+error converge to a value. This process is detailed in Appendix~\ref{sec:dataset_augmentation}. We tuned the regularization parameter by cross-validating with the validation set.
 
@@
 
-We present in \figref{results} the results for 5 different noise
+We present in \figref{results} the results for $5$ different noise
 levels and $3$ different sample areas. The spherical CNN has a significant lead for all levels of noise and sample areas.
@@
 needs to use other statistics to solve the problem. In this case, the
-histogram features that have been built for the problem allow for a significant improvement over the PSD ones.
+histogram features allow for a significant improvement over the PSD ones.
 Unfortunately, while the histogram features contain information about the
@@
 Note that without this graph structure, a fully connected neural network approach would have to be used. Problematically, fully connected neural networks do not scale well with the number of pixels.
+
+We have many different spherical neural network architectures and made a few empirical observations. 
+First Chebyshef polynomial seems more stable than monomials. Nevertheless once the network is trained, we could not observe a significant accuracy difference.
+Second, using a statistical layer improved slightly the result for our specific problem.
+We tried $4$ different layers `mean', `variance', `mean + variance' and `histogram'.
+All but the `variance' were providing the same range of accurancy, the variance being slightly worse.
+Third, dropout did not help in the precence of noise. This is probably du to the fact that the dataset was augmented indefinitely
+Fourth, especially for difficult problem (order 2 or 4, and the presence of large noise) having a large architecture (many filters) and doing many iterations were necessary to achieve the result presented.
 

### 2018-07-27 scnn.tex
small edit

@@
 The resulting PSD are displayed in \figref{psd_sigma3}.
-In the pre-processing step, we also remove the mean of each map and downsample them to a resolution of of $Nside=1024$.
+In the pre-processing step, we also remove the mean of each map and downsample them to a resolution of of $N_{side}=1024$.
 
@@
 the noise. We stop adding new samples in the classifier once the validation
-error converge to a value. This process is detailed in Appendix~\ref{sec:dataset_augmentation}. We tuned the regularization parameter by cross-validating with the validation set.
+error converge to a value. This process is detailed in \ref{sec:dataset_augmentation}. We tuned the regularization parameter by cross-validating with the validation set.
 
@@
 of HEALPix.
-For a detail, on how the convolution kernels are plotted, please refer to Appendix~\ref{sec:filter_visualization}.
+For a detail, on how the convolution kernels are plotted, please refer to \ref{sec:filter_visualization}.
 While it is usually difficult to interpret the shape of the filters in the context of the type of data, we can notice that they often have a ``peak'' like structures.
@@
 \label{sec:dataset_augmentation} The original number of samples $480$, $1920$,
-$7680$ respectively for order $o=1,2,4$ is considered rather low for usual
-deep learning technique, especially when one desire to build a noise robust
+$7680$ respectively for order $o=1,2,4$ is considered small to train deep a architecture, 
+especially when one desire to build a noise robust
 classifier. As a result, we use a classical dataset augmentation technique.
@@
 
-When comparing the network, we want to ensure that the SVM classifier has
+When comparing the network to the baselines, we want to ensure that the SVM classifier has
 access to the same amount of data that the network, i.e, potentially an
-infinite number of samples. Hence, we fit different linear SVM classifier using
+infinite number of samples. Hence, we fit different linear SVM classifiers using
 various training set size until we observe experimentally that
-increasing the amount of data does not improve the classifier. The validation
+increasing the amount of data does not improve the accuracy. The validation
 set remain the same and is used for cross-validation to tune the L2

### 2018-07-30 scnn.tex
working on intro

@@
 Because of their success, CNN-based methods are becoming increasingly popular in Cosmology.
-Nevertheless, cosmological data often comes in a form of spherical maps, which makes the use of traditional CNNs impractical and complicated.
-Typically, the spherical format for spherical maps is HEALPix, which uses an equal-area, isolatitude sampling.
-As a response to this gap, we present a spherical CNN for analysis of full and partial HEALPix maps, which we call HealpixNet.
+Cosmological data often comes in a form of spherical maps, which makes the use of traditional CNNs more complicated.
+The commonly used pixelzation scheme for spherical maps is HEALPix, which uses an equal-area, isolatitude sampling.
+We present a spherical CNN for analysis of full and partial HEALPix maps, which we call HealpixNet.
 We construct a spherical CNNs by representing the sphere as a graph.
 Graphs are versatile data structures which can represent pairwise relationships between objects or act as a discrete representation of a continuous manifold.
-Leveraging the graph, we define many of the standard CNN operations, such as convolution and pooling, with the filters restricted to being radial.
-HealpixNet is a special case of a graph CNN, tailored to the HEALPix sampling of the sphere.
+Using the graph-based representation, we define many of the standard CNN operations, such as convolution and pooling, with filters restricted to being radial.
+This way, HealpixNet is a special case of a graph CNN, tailored to the HEALPix sampling of the sphere.
 % TBD if we include it
-% This approach is computationally more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
+% This approach is very efficient computationally than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
+An advantage of this representation is that the convolution operations with this approach are very efficient, which enables the algorithm to run very fast.
 We demonstrate the method on a classification problem of mass maps from two cosmological models and compare the performance of the CNN with that of two baseline classifiers, based on the power spectrum and pixel density histogram.
@@
 	\caption{Overall network architecture, showing here two convolutional layers acting as feature extractors followed by a fully connected layer with softmax acting as the classifier.
-\nati{add the stat layer?} A convolutional layer is based on five operations: convolution, non-linearity, batch normalization, down-sampling, and pooling.
+    %\nati{add the stat layer?}
+    %\TK{added stats layer to figure text, hope that's OK}
+    A convolutional layer is based on five operations: convolution, non-linearity, batch normalization, down-sampling, and pooling.
 While most operations are agnostic to the data domain, the convolution and the down-sampling have to be adapted.
@@
 
-Cosmological and astrophysical data often comes in the form of spherical sky maps.
+Cosmological and astrophysical data often come in the form of spherical sky maps.
 Observables that cover large parts of the sky, such as the Cosmic Microwave Background (CMB) \citep{planck2015cosmologicalparameters,komatsu2011sevenyear,staggs2018recentdiscoveries}, neutral hydrogen \citep{santos2015cosmologySKA,HI4PI2016fullskyHI}, galaxy clustering \citep{alam2017clusteringgalaxies}, gravitational lensing \citep{troxel2017darkenergy,hildebrandt2017kidscosmological}, and others, have been used to constrain cosmological and astrophysical models.
-Deep Learning has recently gained popularity as an analysis tool in cosmology \citep{schmelze2017cosmologicalmodel,luciesmith2018machinelearning,gupta2018nongaussianinformation,gillet2018deeplearning,hassan2018reionizationmodels,aragoncalvo2018classyfyinglarge,ciuca2017cnnstring}, thanks to its ability to capture complicated, non-linear patterns which are often present in the data.
-Convolutional Neural Networks (CNNs) are particularly well suited for analysis of cosmological data due to the translation invariance built into their architecture.
-Indeed, sky maps are translation invariant, which means that translating and rotating maps on the sphere doesn't change their interpretation.
-Only the statistics of the maps is relevant.
-The location of the map on the sky is always fixed (by where the telescope was looking), and most of the models tested are homogeneous and isotropic (the cosmological principle).
-As such, learned weights can be shared across the sphere: the network does not have to relearn to detect objects or features at every spatial location.
-
-For cosmological observations it is often the case that the data covers only a part of the sphere.
-For ground-based observations this can be due to limited visibility of the sky from a particular telescope location and survey strategy, and for space-based imagers due to masking of the galactic plane area.
+Cosmological information contained in these maps is usually extracted using summary statistics, such as the power spectra or higher order correlation functions.
+Convolutional Neural Networks (CNN) have been proposed as an alternative analysis tool in cosmology thanks to its ability to automatically design relevant statistics to maximise the precision of the parameter estimation
+\citep{schmelze2017cosmologicalmodel,luciesmith2018machinelearning,gupta2018nongaussianinformation,gillet2018deeplearning,hassan2018reionizationmodels,aragoncalvo2018classyfyinglarge,ciuca2017cnnstring,ravanbakhsh2017estimating}.
+This is possible as CNNs have the capacity to build very rich models and capture complicated, non-linear patterns, which are often present in the data.
+
+% \TK{I would move the discussion about this to a later place in the paper}
+% Convolutional Neural Networks (CNNs) are particularly well suited for analysis of cosmological data due to the translation invariance built into their architecture.
+% Indeed, sky maps are translation invariant, which means that translating and rotating maps on the sphere doesn't change their interpretation.
+% Only the statistics of the maps is relevant.
+% The location of the map on the sky is always fixed (by where the telescope was looking), and most of the models tested are homogeneous and isotropic (the cosmological principle).
+% As such, learned weights can be shared across the sphere: the network does not have to relearn to detect objects or features at every spatial location.
 
@@
 The main challenge in designing a CNN on the sphere is to define a convolution which is suitable to this irregularly sampled domain.
+To be able to train the network efficiently, the convolution must also be efficient and fast to perform.
+Another important feature is for a CNN to be able to work on part-spheres, as for many cosmological observations cover only a part of the sky.
+For ground-based observations this can be due to limited visibility of the sky from a particular telescope location and survey strategy, and for space-based imagers due to masking of the galactic plane area.
 
@@
 A second attempt by~\citet{cohen2018spherical} was to leverage the spherical Fourier transform and to perform the convolution in the spectral domain, thanks to the convolution theorem.
-While there exists fast spherical Fourier transforms for some samplings, this approach is still computationally expensive (see \figref{filtering_speed}).
+While there exists fast spherical Fourier transforms for some samplings, this approach can still be computationally expensive.
 Finally, the use of a graph to model the discretized sphere was considered by~\citet{khasanova2017graphomni} as well, towards the goal of building invariances in the network.

### 2018-07-30 scnn.tex
finished a pass on intro

@@
 \newcommand{\nati}[1]{{\color[rgb]{.1,.6,.1}{#1}}}
+\newcommand{\TK}[1]{{\color{red}{#1}}}
 \newcommand{\todo}[1]{{\color[rgb]{.6,.1,.6}{#1}}}
@@
 So far these algorithms have mostly been demonstrated on Euclidean domains, such as flat images.
-As such, perhaps the most straightforward approach to the analysis of spherical data is to divide it into small chunks and project those on flat 2D surfaces.
-While this mostly works, as demonstrated by \citep{fluri2018deep,gupta2018nongaussianinformation,schmelze2017cosmologicalmodel,gillet2018deeplearning}, it may be more natural for some applications and accurate to work directly on the sphere.
-The main challenge in designing a CNN on the sphere is to define a convolution which is suitable to this irregularly sampled domain.
-To be able to train the network efficiently, the convolution must also be efficient and fast to perform.
+Perhaps the most straightforward approach to the analysis of spherical data is to divide it into small chunks and project those on flat 2D surfaces.
+While this approach has been demonstrated to work \citep{fluri2018deep,gupta2018nongaussianinformation,schmelze2017cosmologicalmodel,gillet2018deeplearning}, it may be more natural for some applications and accurate to work directly on the sphere.
+The main challenge in designing a CNN on the sphere is to define a convolution operation that is suitable for this irregularly sampled domain.
+To be able to train the network efficiently, the convolution has to be performed fast.
 Another important feature is for a CNN to be able to work on part-spheres, as for many cosmological observations cover only a part of the sky.
-For ground-based observations this can be due to limited visibility of the sky from a particular telescope location and survey strategy, and for space-based imagers due to masking of the galactic plane area.
+For ground-based observations this can be due to limited visibility of the sky from a particular telescope location, and for space-based instruments due to masking of the galactic plane area.
 
 % cohen2017convolutional (ICML workshop) and cohen2018spherical (ICLR best paper) are redundant
-A first attempt to generalize CNNs to spherical data was to apply a standard 2D CNN to a grid discretization of the sphere~\citep{boomsma2017spherical}.
-While this approach leverages the well-developed 2D convolution and hierarchical pooling, it is restricted to those specific grid samplings which are highly irregular on the sphere.
-A second attempt by~\citet{cohen2018spherical} was to leverage the spherical Fourier transform and to perform the convolution in the spectral domain, thanks to the convolution theorem.
+A first attempt to generalize CNNs to spherical data was to apply a standard 2D CNN to a grid discretisation of the sphere~\citep{boomsma2017spherical}.
+While this approach uses the well-developed 2D convolution and hierarchical pooling, it is restricted to those specific grid samplings which are highly irregular on the sphere.
+An attempt by~\citet{cohen2018spherical} was to leverage the spherical Fourier transform and to perform the convolution in the spectral domain, thanks to the convolution theorem.
 While there exists fast spherical Fourier transforms for some samplings, this approach can still be computationally expensive.
-Finally, the use of a graph to model the discretized sphere was considered by~\citet{khasanova2017graphomni} as well, towards the goal of building invariances in the network.
-While their architecture is fully invariant to translation and rotation on the sphere, they did not take advantage of a hierarchical pixelization of the sphere, and the statistical layer used to be invariant needs to be hand-crafted to capture statistics of interest.
+Finally, the use of a graph to model the discretised sphere was considered by~\citet{khasanova2017graphomni} as well, towards the goal of designing network that were invariant to rotations and translation.
+While their architecture accommodates these invariances on the sphere, they did not take advantage of a hierarchical pixelisation.
+Moreover, the statistical layer, which introduces the invariance, needs to be hand-crafted to capture statistics of interest.
 
@@
 The length (or weight) of the shortest path between two pixels is an approximation of the geodesic distance between them on the manifold.
-This contribution leverages the emerging field of graph signal processing which defines fundamental signal processing tools such as the Fourier transform for signals defined on graphs \citep{shuman2013emerging}.
-Our approach uses the graph CNN formulation introduced by \citet{defferrard2016convolutional}, which is efficient and can adapt to any sampling of the sphere.
-Using a $k$-nearest neighbors graph, the convolution operation costs $\mathcal{O}(N_{pix})$ operations, where $N_{pix}$ is the number of pixels.
-This is the lowest possible complexity for a convolution operation without approximations (e.g.
-by sketching).
-The flexibility of modeling the data domain with a graph allows, for example, to easily model data which only spans a part of the sphere, or data which is not uniformly sampled.
-Our hierarchical pooling strategy exploits a hierarchical pixelization of the manifold to analyze the data at multiple scales.
-Such hierarchical pixelizations of the sphere have been well studied.
+The use of this approach is enabled by recent developments in graph signal processing, where fundamental tools, such as for example the Fourier transform, were defined \citep{shuman2013emerging} for graphs.
+Our approach uses the graph CNN formulation introduced by \citet{defferrard2016convolutional}, which can be adapted to any sampling of the sphere.
+Using a $k$-nearest neighbours graph, the convolution operation costs $\mathcal{O}(N_{pix})$ operations, where $N_{pix}$ is the number of pixels.
+This is the lowest possible complexity for a convolution operation without approximations (e.g. by sketching).
+The flexibility of modelling the data domain with a graph allows to easily model data that spans only a part of the sphere, or data that is not uniformly sampled.
+Our hierarchical pooling strategy exploits a hierarchical pixelisation of the manifold to analyse the data at multiple scales.
+% Such hierarchical pixelisations of the sphere have been well studied.
 
@@
 As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology and astrophysics, we tailored our method to that particular sampling.
-However, only two elements depend on the sampling: (i) the choice of neighboring pixels when building the graph, and (ii) the choice of parent pixels when building the hierarchy.
-It is also possible to use multiple HEALPix maps within our framework and use datasets in form of ``shells''.
-These shells can span the radial direction, so that a tomographic analysis can be performed, or different frequencies, in case of data from observations in radio frequencies.
-\nati{I do not know about that last point.
+The elements of the graph that depend on the sampling are:
+(i) the choice of neighboring pixels when building the graph, and
+(ii) the choice of parent pixels when building the hierarchy of layers.
+% It is also possible to use multiple HEALPix maps within our framework and use datasets in form of ``shells''.
+% These shells can span the radial direction, so that a tomographic analysis can be performed, or different frequencies, in case of data from observations in radio frequencies.
+% \nati{I do not know about that last point.
 Yes we can do it.
@@
 I am not sure this is a disirable features.}
-\todo{I think you got it wrong there. I guess the idea is that each shell would be a feature map, i.e., the graph signal would be multi-dimensional.}
-
+% \todo{I think you got it wrong there. I guess the idea is that each shell would be a feature map, i.e., the graph signal would be multi-dimensional.}
+% \TK{OK, let's talk about it.}
 %\nati{I am not sure this goes there...} Other recently developed sampling methods include \citep{mcewen2011novelsampling}, where exact sampling theorem for equiangular MW sampling was presented.
 
-We give a practical demonstration of the application of our package to cosmological model discrimination using convergence maps, similar to \citep{schmelze2017cosmologicalmodel}.
+We give a practical demonstration of the application of our package to cosmological model discrimination using convergence maps, similar to the ones used by \citet{schmelze2017cosmologicalmodel}.
 In a simplified scenario, we classify convergence maps on parts of a sphere into two cosmological models.
@@
 \citet{boomsma2017spherical} apply a standard 2D CNN to a grid discretization of the sphere.
-Two grids (illustrated in \figref{sphere_grids}) are used in their paper: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}.
-As this formulation leverages standard 2D convolutions, all the optimizations developed for images make it computationally very efficient.
-It is however restricted to those grid sampling sets.
+Two grids, illustrated in \figref{sphere_grids}, are used in their work: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}.
+As this formulation uses the standard 2D convolutions, all the optimizations developed for 2D images can be applied, what make it computationally very efficient.
+It is, however, restricted to those grid sampling sets.
 Similarly to the cubed-sphere, HEALPix is a composition of twelve grids.
-While each of those twelve grids can be independently fed to a 2D CNN, boundary conditions should be properly handled as those grids are not independent.
+While each of those twelve grids could potentially be independently fed into a 2D CNN, boundary conditions would have to be properly handled, as those grids are not independent.
 \todo{How do thy handle boundaries?}
+\TK{+1,good question}
 % Furthermore, the grid requirement makes it impossible for the convolution to capture the spherical properties of the domain, i.e., the cubed-sphere sampling is by definition adapted to a cube and not to a sphere.
 Nope, the graph can adapt to any sampling.
-Moreover, those samplings are not ideal as their resolution is not constant across the sphere.
-Indeed, the singularities --- the poles for the equirectangular grid, the corners of the cube for the cubed-sphere --- are over-sampled.
-Equal areas of discrete elements is advantageous for physical measurements as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence \citep{gorski2005healpix}.
+% Moreover, those samplings are not ideal as their resolution is not constant across the sphere.
+Moreover, the pixel area is not constant across the sphere in those sampling schemes, which may limit their potential applications.
+Indeed, the singularities, such as the poles for the equirectangular grid, and the corners of the cube for the cubed-sphere, are over-sampled.
+Equal areas of discrete elements is advantageous for many physical measurements, as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence \citep{gorski2005healpix}.
 % \nati{Michael: Under some very specific hypothesis, this second approach is a particular case of our method, i.e.
@@
 
-\citet{cohen2018spherical} leverages the continuous spherical convolution.
+\citet{cohen2018spherical} uses the continuous spherical convolution.
 The goal of this contribution was to define a rotation-equivariant convolution on the sphere, i.e., a rotation of the input implies the same rotation in the output.

### 2018-07-30 scnn.tex
working on section 4

@@
 \newcommand{\nati}[1]{{\color[rgb]{.1,.6,.1}{#1}}}
-\newcommand{\TK}[1]{{\color{red}{#1}}}
+\newcommand{\TK}[1]{{\color{red}{TK:#1}}}
 \newcommand{\todo}[1]{{\color[rgb]{.6,.1,.6}{#1}}}
@@
 I think we should not.}
-Finally, a 2D CNN learns directional filters which orientation is arbitrary.
-Indeed, directions, which make much sense for images (up, down, left, and right), are arbitrarily defined when setting the origin of the grids on the sphere.
+Finally, a 2D CNN learns directional filters, which are well defined with respect of the image coordinates.
+Directions that make much sense for images (up, down, left, and right) are arbitrarily defined when setting the origin of the grids on the sphere.
 Any convolution using directions on the sphere is not equivariant to translation and rotation.
@@
 The resulting convolution is performed by (i) a spherical harmonic transform (SHT), i.e., a projection on the spherical harmonics, (ii) a  multiplication in the spectral domain, and (iii) an inverse SHT.
-Hence the computational cost of a convolution is essentially due to the two SHTs.
+Hence the computational cost of a convolution is dominated by the two SHTs.
 A naive implementation of the SHT costs $\bO(N_{pix}^2)$ operations, where $N_{pix}$ is the number of pixels.
-There fortunately exists accelerated schemes for some sampling sets, see for example \citet{mohlenkamp1999fast, rokhlin2006fast, reinecke2013libsharp}.
+Accelerated schemes exist for some sampling sets \citep[see][for examples]{mohlenkamp1999fast, rokhlin2006fast, reinecke2013libsharp}.
 The main advantage of this approach is that it provides a mathematically well defined rotation-equivariant network.
 Nevertheless, even with accelerated SHTs, the convolutions remain expensive, limiting the practical use of this approach.
-For example with the HEALPix sampling, which was designed to have a fast SHT by being iso-latitude, the computational cost of the SHT is $\bO(N_{pix}^{3/2}) = \bO(N_{side}^3) = \bO(\ell_{max}^3)$, where $\ell_{max}$ is the largest order (angular frequency) \citep{gorski2005healpix, reinecke2013libsharp}.\footnote{All pixels are placed on $N_{ring} = 4N_{side}-1 = \bO(\sqrt{N_{pix}})$ rings of constant latitude.
+For example with the HEALPix sampling, which was designed to have a fast SHT by being iso-latitude, the computational cost of the SHT is $\bO(N_{pix}^{3/2}) = \bO(N_{side}^3) = \bO(\ell_{max}^3)$, where $\ell_{max}$ is the largest angular frequency\footnote{All pixels are placed on $N_{ring} = 4N_{side}-1 = \bO(\sqrt{N_{pix}})$ rings of constant latitude.
 Each ring has $\bO(\sqrt{N_{pix}})$ pixels.
@@
 The computational cost is thus $\sqrt{N_{pix}}$ FFTs for a total cost of $\bO(N_{pix} \log(\sqrt{N_{pix}}))$, plus $\sqrt{N_{pix}}$ matrix multiplications of size $\sqrt{N_{pix}}$ for a total cost of $\bO(N_{pix}^{3/2})$.}
-In comparison, filtering with our method scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}).
-Moreover, \figref{filtering_speed} shows that a naive implementation of our method is more than ten times faster than the SHT implemented by the highly optimized \pkg{libsharp} library used by HEALPix \citep{reinecke2013libsharp}.
-While a comparison is theoretically possible, the experiments of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and do not provide any code for the HEALPix one.
+\citep{gorski2005healpix, reinecke2013libsharp}.
+In comparison, filtering with our HealpixNet method scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}).
+% Moreover, \figref{filtering_speed} shows that a naive implementation of our method is more than ten times faster than the SHT implemented by the highly optimized \pkg{libsharp} library used by HEALPix \citep{reinecke2013libsharp}.
+% While a comparison is theoretically possible, the experiments of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and do not provide any code for the HEALPix one.
 Hence, a practical comparison is not possible.
-We also note that this approach cannot be easily accelerated when data lies on a part of the sphere only.
+% \TK{This I would leave out here, as this is a "spoiler" of the results section.}
+
+Approaches by \citet{cohen2018spherical, boomsma2017spherical} can not be easily accelerated when the data lies on a part of the sphere only.
 That is an important use case in cosmology as measurements are often partial, i.e., full-sky maps are rare.
-One could still fill the unseen part of the sphere with zeros, and avoid to compute empty integrals (on the latitude or longitude).
-It is however not straightforward to identify those empty directions, and computations would still be wasted (consider for example a ring which mostly contains zeros but a few measurements).
-With graphs however, one only pays for the used pixels.
-The cost is some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}).
-Those can however be mitigated by padding with zeros a small area around the measurements.
-
-In an attempt to get the best of the first two approaches, we follow a third
-direction. We use a graph to adapt to the particular structure of the sphere.
-While the convolution remains efficient, it still captures well the spherical
-structure and is particularly adapted to the HEALPix sampling.
-
-The use of a graph to model the discretized sphere was considered by~\citet{khasanova2017graphomni} as well.
-The authors map omnidirectional images to the sphere, with the goal of correcting for distortions induced by the lens used for the acquisition.
-Besides the different application covered by the paper, there are two important
-differences. First the sampling is different as~\cite{khasanova2017graphomni} uses a
-grid. Second, it uses a different graph CNN based on a different parameterization
-of the convolution kernel.
-As~\citep{boomsma2017spherical}, they use an equirectangular grid sampling.
+One could still fill the unseen part of the sphere with zeros, and avoid to compute empty integrals, on the latitude or longitude.
+It is, however, not straightforward to identify those empty directions, and computations would still be wasted; consider, for example, a ring which mostly contains zeros but a few measurements.
+With graphs however, the computation is done only for the used pixels.
+This, however, results in some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}).
+These can be mitigated by padding with zeros a small area around the measurements.
+
+% In an attempt to get the best of the first two approaches, we follow a third
+% direction. We use a graph to adapt to the particular structure of the sphere.
+% While the convolution remains efficient, it still captures well the spherical
+% structure and is particularly adapted to the HEALPix sampling.
+% \TK{I am not sure what is the point of this paragraph, we described our approach already before}
+
+The use of a graph to model the discretised sphere was also considered by~\citet{khasanova2017graphomni}.
+The authors map omnidirectional images onto a sphere, with the goal of correcting for distortions induced by the lens, which was used for their acquisition.
+Besides a different practical application, for which the method was designed, there are two important differences.
+% First, a different sampling scheme is used: \cite{khasanova2017graphomni} uses a grid.
+First, similarly to~\citet{boomsma2017spherical}, they use an equirectangular grid sampling.
+% \TK{how is it different from us?}
+Second, it uses a graph CNN based on a different parameterisation of the convolution kernel.
 Moreover, they did not take advantage of a hierarchical pixelization of the sphere and resorted to dynamic pooling~\citep{kalchbrenner2014dcnn}.
-Finally, while we do want our network to be rotation invariant, their statistical layer --- an operation which computes a set of spatially invariant statistics of the last feature map --- destroys a lot of information \todo{and hinders performance (should be empirically verified)}.
+Finally, while the rotation invariance is desirable, the statistical layer used
+% --- an operation which computes a set of spatially invariant statistics of the last feature map ---
+% \{TK} this should be explained earlier
+may not capture the information in an optimal way
+\todo{and hinders performance (should be empirically verified)}.
+\TK{This is a strong claim, can we support this?}
 Moreover, the chosen statistics have to be hand-crafted to capture statistics of interest.
-While developing completely invariant transforms is a  goal worth investigating, CNNs for image recognition (arguably the most researched and developed architectures), are not built to be fully invariant to translation.
-As with the proposed spherical CNN, the fully connected layers at the end of the network depend on the spatial localization of features.
-While that may not be ideal, it was shown to work well in practice.
-\todo{In this work we reused the idea of a statistical layer, described in \secref{stat_layer}, to provide invariance to isometric transformations such as translation and rotation on the sphere.
-While \citet{khasanova2017graphomni} uses the mean and variance of diffused versions of the last feature maps, we experimentally tested multiple variants and got good results by keeping all the statistical moments via a learned histogram.
-That is similar to the learnable histogram introduced by \citet{wang2016learnhist}, although for the orthogonal purpose of integrating global context in object detection and segmentation tasks.}
+% While developing completely invariant transforms is a goal worth investigating, CNNs for image recognition, which are arguably the most researched and developed architectures, are not built to be fully invariant to translation.
+% As with the proposed spherical CNN, the fully connected layers at the end of the network depend on the spatial localization of features.
+% While that may not be ideal, it was shown to work well in practice.
+% \TK{The two sentences above look like a tangent to me.. can we skip it an go to the main point, which is I think the fact that we use the stat layer?}
+
+\todo{In HealpixNet we use the idea of a statistical layer, described in \secref{stat_layer}, to provide invariance to isometric transformations such as translation and rotation on the sphere.
+\TK{We would need to describe the idea of the statistical layer for the cosmology audience. They don't have a clue what it is.}
+The use of the statistical layer is optional.
+In our approach, we are keeping all the statistical moments by retaining a full, learned learned feature histogram, an approach that performed the best in our tests.
+That is similar to the learnable histogram introduced by \citet{wang2016learnhist}, although for a purpose of integrating global context in object detection and segmentation tasks.
+\citet{khasanova2017graphomni} uses the mean and variance of diffused versions of the last feature maps in their statistical layer.}
+\TK{why is this section in TODO?}
 
@@
 
-In this work, we are using the graph CNN formulation introduced in~\cite{defferrard2016convolutional}.
+% In this work, we are using the graph CNN formulation introduced in~\cite{defferrard2016convolutional}.
 
@@
 
-A CNN is composed of the following main building blocks~\citep{lecun1998cnn}: (i) a convolution, (ii) a non-linearity, (iii) a down-sampling operation, (iv) a pooling operation, and (v), optionally, some normalization.\footnote{\citet{ioffe2015batchnorm} have shown that batch normalization helps training.
-We verified this experimentally in our setting as well.} Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}.
+A CNN is composed of the following main building blocks~\citep{lecun1998cnn}:
+(i) a convolution,
+(ii) a non-linearity,
+(iii) a down-sampling operation,
+(iv) a pooling operation, and
+(v), optionally,  normalization.\footnote{\citet{ioffe2015batchnorm} have shown that batch normalization helps training. We verified this experimentally in our setting as well.}
+Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}.
 As operations (ii) and (v) are point-wise, they do not depend on the data domain.
@@
 Likewise, down-sampling can be achieved by taking one pixel out of $n$.
-Because of the irregular sampling, there is no straightforward way to define a convolution on the sphere directly in the pixel domain.
-
-We will hence make a detour by the spectrum to perform the convolution.\footnote{Note that we only use the spectrum to define the convolution.
-The implementation however does not need a direct access to the spectrum, which is computationally much more efficient.
-See \secref{efficient_convolution}.}
-The gist of our method is to define the convolution on a sphere using a graph, and the down-sampling using a hierarchical pixelization of the sphere.
+Because of the irregular sampling, there is no straightforward way to define a convolution on the sphere directly in the pixel domain; convolutions are most often performed using spherical harmonics.
+In our method we also use the spectral domain to define the convolution.
+The implementation, however, does not need a direct access to the spectrum, which is computationally more efficient (see \secref{efficient_convolution}).
+% We will therefore use the spectral domain to define the convolutions
+% \footnote{Note that we only use the spectrum to define the convolution.
+% The implementation however does not need a direct access to the spectrum, which is computationally much more efficient. See \secref{efficient_convolution}.}
+% \TK{moving footnote to the main text }
+The gist of our method is to define the convolution operation on a sphere using a graph, and the down-sampling operation using a hierarchical pixelisation of the sphere.
 
@@
 Any existing proposition of practical schemes for the discrete treatment of such functions on the sphere introduces some systematic error dependent on the global properties of the point set.
-While our method is applicable to any pixelization of the sphere, two details depend on the chosen sampling: (i) the choice of neighbors in the construction of the graph, and (ii) the choice of parent nodes when coarsening the graph.
+While our method is applicable to any pixelisation of the sphere, two details depend on the chosen sampling: (i) the choice of neighbours in the construction of the graph, and (ii) the choice of parent nodes when coarsening the graph.
 As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology, our target application, we'll tailor the method to that particular sampling in the subsequent exposition.
@@
 A counter-example is the equirectangular projection, which is not constructed from a base polyhedron, although it can be subdivided.
-In the particular HEALPix case, the base is a rhombic dodecahedron, i.e., a polyhedron made from 12 congruent rhombic faces.\footnote{A rhombus is a quadrilateral whose four sides all have the same length.} See \figref{pooling} for an illustration of the base rhombic dodecahedron and its subdivisions.
+In the particular HEALPix case, the base is a rhombic dodecahedron, i.e., a polyhedron made from 12 congruent rhombic faces.\footnote{A rhombus is a quadrilateral whose four sides all have the same length.}
+See \figref{pooling} for an illustration of the base rhombic dodecahedron and its subdivisions.
 
 HEALPix is an acronym for Hierarchical Equal Area isoLatitude Pixelization of a sphere.
-As suggested in the name, this pixelization produces a hierarchical subdivision of a spherical surface in which each pixel covers the same surface area as every other pixel.
+This pixelisation produces a hierarchical subdivision of a spherical surface where each pixel covers the same surface area as every other pixel.
 A hierarchy is desired for data locality in computer memory.
@@
 Isolatitude is essential for the implementation of a fast spherical transform.
-HEALPix is the sole pixelization scheme which satisfies those three properties.
+HEALPix is the sole pixelisation scheme which satisfies those three properties.
 
@@
 As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2 \cdot 12 = 2^2 \cdot 12 = 48$ pixels (middle sphere in \figref{pooling}), the third is $N_{pix} = N_{side}^2 \cdot 12 = 4^2 \cdot 12 = 192$ pixels, etc., where $N_{side} = 1, 2, 4, 8, \ldots$ is the grid resolution parameter.
-High-resolutions HEALPix maps easily reach millions of pixels. \figref{example_maps} shows two examples.
+High-resolutions HEALPix maps easily reach millions of pixels.
+\figref{example_maps} shows two examples of HEALPix maps: the Cosmic Microwave Background \citep{planck2015overview} and \TK{update}.
 
@@
 \end{equation*}
-is the average Euclidean distance over all connected pixels. This weighting scheme is important as while pixel areas are equal, distances between pixels are not.
-Other weighting schemes are possible. For example,~\cite{khasanova2017graphomni} uses the inverse of the distance instead. We found out that the one proposed above works fine for our purpose.
+is the average Euclidean distance over all connected pixels. This weighting scheme is important as distances between pixels are not equal.
+Other weighting schemes are possible.
+For example,~\cite{khasanova2017graphomni} uses the inverse of the distance instead.
+We found out that the one proposed above works well for our purpose, and did not investigate other approaches, leaving it to future work.
 \figref{healpix_graph_4} shows a graph constructed from the HEALPix sampling of a sphere.
@@
 	\includegraphics[width=\linewidth]{eigenvectors}
-	\caption{The first 16 Fourier modes (eigenvectors of the graph Laplacian) of a graph constructed from the HEALPix sampling of the sphere.
+	\caption{The first 16 eigenvectors of the graph Laplacian, an equivalent of Fourier modes, of a graph constructed from the HEALPix sampling of the sphere.
     Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$ and order $|m|=(0,1)$, eigenvectors 4--8 with degree $\ell=2$ and order $|m|=(0,1,2)$, and eigenvectors 9--15 with degree $\ell=3$ and order $|m|=(0,1,2,3)$.
-Nevertheless, the graph eigenvectors are \emph{only approximating} the real spherical harmonics.}
+    Nevertheless, the graph eigenvectors are only approximating spherical harmonics.}
 	\label{fig:graph_harmonics}
@@
 
-It turns out that using the graph construction described above, the graph Fourier modes resemble the spherical harmonics (see \figref{graph_harmonics}).
+Figure \figref{graph_harmonics} shows the Fourier modes of a HEALPix graph, created using the graph construction described above.
+The graph Fourier modes resemble the spherical harmonics.
 That is a strong hint that the graph is able to capture the spherical properties of the HEALPix sampling.
@@
 
-As there is no notion of translation on a graph, we cannot really convolve two graph signals.
+As there is no notion of translation on a graph, we cannot convolve two graph signals in a strict sense.
 We can, however, convolve a signal with a kernel defined in the spectral domain.
-More precisely, we are filtering a graph signal by a kernel.
+More precisely, we can filter a graph signal by a kernel.
 Given the convolution kernel
@@
 This localization can be useful to visualize kernels as explained in~\ref{sec:filter_visualization}.
-If the graph is not regular, i.e., all nodes don't have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another.
+If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another.
 While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular.
@@
 While \eqnref{graph_convolution} is a theoretically well justified definition of the convolution of a graph signal $\f$ by a kernel $h$, it is computationally cumbersome.
-As there exists no general fast Fourier transform (FFT) for graphs,\footnote{See \citep{le2018fgft} for a comparison between the polynomial definition of filters presented here and a class of fast graph Fourier transforms based on the approximation of the Fourier basis $\U$ by a product of sparse matrices.} the Fourier transform, i.e., the multiplication of the signal $\f$ by the dense matrix $\U$, costs $\bO(N_{pix}^2)$ operations.
-In a CNN, this operation has to be performed for each training step (forward and backward).
-As current training procedures are not data efficient and require a lot of samples, a quadratic computational cost in the sample size is a show stopper.
-Moreover, the eigendecomposition of the Laplacian $\L$ is needed to obtain the Fourier basis $\U$ in the first place. That has a unique cost of $\bO(N_{pix}^3)$ operations.
-
-Forunately, both of these computational issues can be overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parameterized by $K+1$ coefficients $\theta$.
+As no general Fast Fourier Transform (FFT) exist for graphs, the execution of the Fourier transform by multiplication of the signal $\f$ by the dense matrix $\U$ costs $\bO(N_{pix}^2)$ operations.
+% \footnote{See \citep{le2018fgft} for a comparison between the polynomial definition of filters presented here and a class of fast graph Fourier transforms based on the approximation of the Fourier basis $\U$ by a product of sparse matrices.}
+%\TK{I would just cite the paper, we have not introduced the polynomials at this stage yet.}
+In a CNN, this operation has to be performed for each training step: forward and backward.
+% As current training procedures are not data-efficient and require a lot of samples, a quadratic computational cost in the sample size is a .
+%\TK{what does "data-efficient mean"? removing for now}
+As current training procedures require processing of many samples, it would be very slow to perform them for a quadratic computational cost in the sample size.
+Moreover, the eigen-decomposition of the Laplacian $\L$ is needed to obtain the Fourier basis $\U$ in the first place.
+That has a unique cost of $\bO(N_{pix}^3)$ operations.
+
+Fortunately, both of these computational issues can be overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parametrised by $K+1$ coefficients $\theta$.
 In that specific case, the filtering operation \eqnref{graph_convolution} becomes
@@
 \end{equation}
-an operation requiring $k$ multiplication of the graph Laplacian matrix $\L$.
-In our case, the Laplacian is extremly sparse ($8-9$ entries per line), making the filtering operation for a fixed $K$ linear in the number of pixel $N_{pix}$.
-Moreover, here happens the transition from filtering in the spectral domain to filtering in the vertex domain.
+an operation requiring $k$ multiplications of the graph Laplacian matrix $\L$.
+In our case, the Laplacian is extremly sparse, with $8-9$ entries per line, making the filtering operation for a fixed $K$ linear in the number of pixel $N_{pix}$.
+% Moreover, here happens the transition from filtering in the spectral domain to filtering in the vertex domain.
+This operation is performed in the vertex domain.
 The matrix $\L^k$ captures $k$-neighborhoods of each pixel, i.e., $(\L^k)_{ij}$ is non-zero if and only if nodes $v_i$ and $v_j$ are connected by a path of length $k$.
@@
 \todo{Better vertex domain explanation. \nati{I gave it a try. Should we take a single vertex and explain what heppens to it? Note that I suppressed the following paragraph. }}
+\TK{For me it's understandable:)}
 
@@
 While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
-In practice, we found out that Chebyshev polynomials are slightly more stable in our experiment.
+In practice, we found out that Chebyshev polynomials are slightly more stable in our experiment \TK{slightly more stable than what?}.
 We believe that this is due to their orthogonality (as explained above) and uniformity\footnote{The amplitude of Chebyshev polynomials is more or less constant over the domain $[-1, 1]$ independently of the order $k$.
@@
 Exploiting the recursive formulation of Chebyshev polynomials, evaluating \eqnref{graph_convolution_cheby} requires $\bO(K)$ multiplications of the dense vector $\f$ with the sparse matrix $\tL$.
-The cost of one such multiplication is $\bO(|\E|)$.
-By construction of our graph, $|\E| < 8 N_{pix}$.
-The overall computational cost of the convolution is thus reduced to $\bO(N_{pix})$ operations.
-That is much more efficient than filtering with spherical harmonics, even tho the HEALPix sampling was designed to leverage a fast spherical transform (by being iso-latitude).
+The cost of one such multiplication is $\bO(|\E|)$. By construction of our graph, $|\E| < 8 N_{pix}$ and the overall computational cost of the convolution is thus reduced to $\bO(N_{pix})$ operations.
+That is much more efficient than filtering with spherical harmonics, even tho the HEALPix was designed as an iso-latitude sampling to leverage a fast spherical transform.
 That is especially true for smooth kernels which require a low polynomial degree $K$.
-See \figref{filtering_speed} for a speed comparison of low-pass filtering for Gaussian smoothing using the spherical harmonics and the presented method.
-It is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively.
+\figref{filtering_speed} demonstrates the speed comparison of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
+The performance of our approach is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively.
 
@@
 	\caption{Comparison of filtering speed for Gaussian smoothing of maps of various sizes.
-The fast spherical harmonic transform (SHT) is implemented by the healpy Python package (via the \texttt{healpy.sphtfunc.smoothing} function with $\ell_{max} = 3 N_{side} - 1$, the default.).
-The graph filtering is defined by \eqnref{graph_convolution_cheby} and implemented with the numpy and scipy Python packages.
+    The fast spherical harmonic transform (SHT) is implemented by the \texttt{healpy} Python package (via the \texttt{healpy.sphtfunc.smoothing} function with $\ell_{max} = 3 N_{side} - 1$, the default).
+    The graph filtering is defined by \eqnref{graph_convolution_cheby} and implemented with the \texttt{numpy} and \texttt{scipy} Python packages.
     Both are executed on a single core.
@@
 
-Hierarchical pixelization schemes present a natural coarsening.
-Indeed, each subdivision divides a cell in an equal number of child sub-cells.
+Coarsening can be naturally designed for hierarchical pixelisation schemes, as each subdivision divides a cell in an equal number of child sub-cells.
 Coarsening is the reverse operation: merging the sub-cells toward the goal of summarizing the data supported on them.
-Merging cells lead to a coarser graph, hence the name coarsening.
+Merging cells lead to a coarser graph.
 Coarsening defines $\C(i)$, the set of children of node $v_i$.
@@
 
-Pooling refers to the operation that summarizes the data supported on the merged sub-cells in one parent cell. Given a map $\x \in \R^{N_{pix}}$, pooling defines $\y \in \R^{N'_{pix}}$ such as
+Pooling refers to the operation that summarizes the data supported on the merged sub-cells in one parent cell.
+Given a map $\x \in \R^{N_{pix}}$, pooling defines $\y \in \R^{N'_{pix}}$ such as
 \begin{equation} \label{eqn:pooling}

### 2018-07-30 scnn.tex
made a pass all the way to conclusions

@@
 \end{equation}
-where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix} / {N_{pix}}'$ is the down-sampling factor\footnote{$| \C(i) | = N_{pix} / {N_{pix}}' = (N_{side} / N'_{side})^2 = 4^p$ for HEALPix.}.
-That operation is often taken to be the maximum value, but it might be any permutation invariant operation such as the sum or the average.
+where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix} / {N'_{pix}}$ is the down-sampling factor, which for HEALPix is $| \C(i) | = N_{pix} / {N_{pix}}' = (N_{side} / N'_{side})^2 = 4^p$.
+That operation is often taken to be the maximum value, but it can be any permutation invariant operation, such as a sum or an average.
 \figref{pooling} illustrates the process.
@@
 
-Following \citet{khasanova2017tigranet}, we use a statistical layer between the last graph convolutional layer and the first fully connected layer for the neural network to be invariant to isometric transformations such as rotation and translation of maps on the sphere.
+Following \citet{khasanova2017tigranet}, we implement an optional statistical layer between the last graph convolutional layer and the first fully connected layer for the neural network.
+This introduces the invariance of the output to isometric transformations, such as rotation and translation of maps on the sphere.
 The role of the layer is to compute global and location independent statistics from feature maps.
-Besides providing invariance, the layer drastically compresses the representation of the data as the number of computed statistics $N_{stat}$ is usually much smaller than the size of the map, $N_{pix}$.
-That compression results in much smaller fully connected layers, the most parameter-hungry layers of a neural network.
+Besides providing invariance, the layer drastically compresses the representation of the data as the number of computed statistics $N_{stat}$ is usually much smaller than the size of the map $N_{pix}$.
+That compression results in much smaller fully connected layers, which usually contain a significant fraction of trainable parameters of a neural network.
 The invariance and reduced representation should help the network to learn from less samples and to generalize better to unseen data.
@@
 Another example is $f(\x) = [\esp(\x), \var(\x)]\trans$, where $\var(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} (x_i - \esp(\x))^2$ is the empirical variance.
-
-Other statistical layers are possible.
-In particular, we also implemented a learned histogram from \citep{wang2016learnhist}.
-Additionaly \citep{khasanova2017tigranet} propose to apply differen diffusion on the final maps to obtain statistics at different sclaes.
+Other statistical layers are also possible.
+In particular, we also implement a \emph{learned histogram} statistic \citep{wang2016learnhist}.
+Other approaches, which we did not implement, may include applying different diffusion on the final maps to obtain statistics at different scales, as proposed by \citep{khasanova2017tigranet}.
 
@@
 Given a matrix $\X \in \R^{N_{pix} \times F}$, a pooling layer computes $\Y = P(\X) \in \R^{N'_{pix} \times F}$ by reducing its spatial resolution ($N'_{pix} < N_{pix}$) according to \eqnref{pooling}.
-
-Given a matrix $\X \in \R^{N_{pix} \times F}$, a batch normalization layer \citep{ioffe2015batchnorm} computes $\Y = BN(\X)$ such as
+% Given a matrix $\X \in \R^{N_{pix} \times F}$,
+The batch normalization layer \citep{ioffe2015batchnorm} computes $\Y = BN(\X)$ such as
 \begin{equation*}
@@
 
-Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers (an example is $NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC$) and $\theta$ is the set of all trainable parameters.
+Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
+An example network can be defined as
+\begin{equation}
+NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC
+\end{equation}
+\TK{what is the meaning of $\circ$ here?}
 The number of features $F$ depends on the data at hand.
@@
 \end{equation*}
+The same architecture with different loss function can also be used for parameter regression \citep{fluri2018deep,gupta2018nongaussianinformation}.
 The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
@@
 % 4) Describe the result
-In this section, we demonstrate the performance of the spherical neural network on a discrimination problem: the classification of convergence maps, similar to those created with gravitational lensing technique \citep{chang2017curvedsky}.
+In this section we demonstrate the performance of the spherical neural network on a discrimination problem: the classification of convergence maps into two cosmological model classes.
+These maps are similar to those created with gravitational lensing technique \citep{chang2017curvedsky}.
 Nevertheless, by simply changing the loss, one could use the network for regression.
@@
 \label{sec:data}
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{psd_sigma3}
+\caption{Power spectrum densities of the noiseless maps.
+The maps have been smoothed with a Gaussian kernel of radius $3$ arcmins to remove high frequencies.
+The cosmological models could otherwise have been distinguished by the power spectra alone.}
+\label{fig:psd_sigma3}
+\end{figure}
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.75\linewidth]{smooth_map_class_1}
+% \hfill
+\includegraphics[width=0.75\linewidth]{smooth_map_class_2}
+\caption{Example maps from two classes to be discriminated. Left: model 1 with $\Omega_m=0.31$ and $\sigma_8=0.82$. Right: model 2 with $\Omega_m=0.26$ and $\sigma_8=0.91$.
+The initial conditions for both simulations were the same, so differences only arise due to different cosmological parameters. \nati{Tomek: Is this correct?}}
+\label{fig:map_sample}
+\end{figure*}
 
@@
 
-We make full sky N-body simulations for two parameter sets for $\Lambda \rm{CDM} $ cosmological model: model 1 ($\Omega_m=0.31, \sigma_8=0.82$) and model 2 ($\Omega_m=0.26, \sigma_8=0.91$), where $\Omega_m$ is the matter density in the universe and $\sigma_8$ is the normalisation of the matter power spectrum.
-Other parameter parameters were set to $h=0.7$ \todo{(MORE PARAMS HERE - CHECK WITH RAPHAEL)}.
-These parameters were chosen to have the same spherical harmonic power spectrum for $\ell<1000$.
-That means that it is not possible to distinguish between these cosmological models using these maps if the this range of scales is used.
+We make full sky N-body simulations for two parameter sets for $\Lambda\rm{CDM} $ cosmological model: model 1 ($\Omega_m=0.31, \sigma_8=0.82$) and model 2 ($\Omega_m=0.26, \sigma_8=0.91$), where $\Omega_m$ is the matter density in the universe and $\sigma_8$ is the normalisation of the matter power spectrum.
+Other parameter parameters were set to: Hubble constant $H_0=70 km/s/Mpc$, spectral index $n_s=0.96$, and Baryon density today $\Omega_b=0.05$.
+The parameters $\Omega_m$ and $\sigma_8$ were chosen to have the same spherical harmonic power spectrum for $\ell<1000$.
+That means that it is very difficult to distinguish between these cosmological models using these maps if this range of scales is used.
 We found that for $\ell>1000$ the differences in power spectrum is $~5\%$.
-To remove this information, we additionally smooth the spherical maps with a Gaussian kernel of radius $3$ arcmins.
-The resulting PSD are displayed in \figref{psd_sigma3}.
+To remove this information, we additionally smooth the spherical maps with a Gaussian kernel of radius $3$ arcmin.
+The resulting Power Spectrum Density (PSD), computed using the \texttt{anafast} function in the HEALpix package, are displayed in \figref{psd_sigma3}.
 In the pre-processing step, we also remove the mean of each map and downsample them to a resolution of of $N_{side}=1024$.
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=\linewidth]{psd_sigma3}
-\caption{Power spectrum densities of the noiseless maps.
-The maps have been smoothed with a Gaussian kernel of radius $3$ arcmins to remove high frequencies.
-The cosmological models could otherwise have been distinguished by looking at the PSDs.}
-\label{fig:psd_sigma3}
-\end{figure}
 
@@
 As a simulator we use \pkg{L-PICOLA} \citep{howlett2015lpicola}, a fast and approximate code for N-body simulations.
-For each class, we generate $30$ simulations (both class have the same initial parameters).
-
-Out of the $60$ simulations, $20$ are kept for the test set.
+For each class, we generate $30$ simulations, with both classes having the same initial parameters.
+
+Out of the $60$ simulations, $20$ are kept as the test set.
 \figref{map_sample} shows the full sky simulations and a zoom region for model 1 (top) and model 2 (bottom).
@@
 
-\begin{figure*}[!ht]
-\centering
-\includegraphics[width=0.48\linewidth]{smooth_map_class_1}
-\hfill
-\includegraphics[width=0.48\linewidth]{smooth_map_class_2}
-\caption{Example maps from two classes to be discriminated. Left: model 1 with $\Omega_m=0.31$ and $\sigma_8=0.82$. Right: model 2 with $\Omega_m=0.26$ and $\sigma_8=0.91$.
-The initial conditions for both simulations were the same, so differences only arise due to different cosmological parameters. \nati{Tomek: Is this correct?}}
-\label{fig:map_sample}
-\end{figure*}
-
 \subsection{Problem formulation}
 While the number of maps might sound small for deep learning, the information contained in the maps is very recurrent, allowing us to use parts of the map as samples for our simulation.
-Leveraging the properties of the HEALPix sampling, we can split each maps
-into $12*o^2$ ($o=1,2,4,\dots$) samples that span a smaller part of the sphere.
-As shown in \figref{part_sphere}, we used $o=1,2,4$ as the resulting
-samples are large enough to suffer from the effects of the spherical geometry. We
-decided to only report simulation results for this specific setting as spherical
-cosmological data usually does not span the full sphere. Nevertheless, our code
-includes an example using the full sphere.
-
-\begin{figure}[!ht]
+Using the properties of the HEALPix sampling, we can split each maps into $12*o^2$ ($o=1,2,4,\dots$) samples that span a smaller part of the sphere.
+As shown in \figref{part_sphere}, we used $o=1,2,4$ as the resulting samples are large enough to suffer from the effects of the spherical geometry.
+We decided to only report simulation results for this specific setting as spherical cosmological data usually does not span the full sphere.
+Nevertheless, our code includes an example using the full sphere.
+
+\begin{figure}
 \centering
@@
 \end{figure}
-
-We build a robust classifier, i.e., an automatic way to
-discriminate between the two classes in the presence of noise.
-We check the classification performance as a function of the area used, i.e., "the order" $o$ and also as a function of the relative level of the noise added to the map.
-
-For all the experiments, we work with centered Gaussian noise.
+For all the experiments, we work with centred Gaussian noise.
 While the noise model of real mass maps often has a slightly different distribution, Gaussian should be a sufficient model to demonstrate the performance of our method.
-To improve the stability of the spherical CNN, we slowly increase the amount of noise added to
-the training data over the iterations. Furthermore in order to avoid
-overfitting, the noise is randomly produced during the training process. We trained our
-model between $50$ and $290$ epochs depending on the complexity and the size of
-the problem. $20\%$ of the training set that we call "validation set" was left out of the training process and simply used to assess the global performance and overfitting of
-the network.
-Training took less than a day for each model using an NVIDIA Tesla K20.
-
-We compare the performance of the spherical CNN against two simple benchmark
-algorithms. The two baselines are based on building features with a) the Power
-Spectral Densities (PSD) and b) the histogram of pixels in the maps~\cite{patton2017cosmologicalconstraints}.
-After a normalization, those features are then classified using a Support Vector
-Machine (SVM) with a linear kernel. Other kernels did not provide better results
-while having significanly worse scaling properties. All classifiers are trained with noisy samples. For fairness, we augmented the dataset
-of the baseline algorithm in a similar way as for the network, i.e, with
-created an "unlimited" number of samples by adding new random realizations of
-the noise. We stop adding new samples in the classifier once the validation
-error converge to a value. This process is detailed in \ref{sec:dataset_augmentation}. We tuned the regularization parameter by cross-validating with the validation set.
+The noise added to our maps had levels spanning the range between 0 and 2  $\times$ the standard deviation of the mass maps.
+
+We build a robust classifier, which automatically discriminates between the two classes in the presence of noise.
+We check the classification performance as a function of the area used, the order $o$, and the relative level of the noise added to the map.
+
+To improve the stability of the spherical CNN, we slowly increase the amount of noise added to the training data over the iterations.
+Furthermore in order to avoid overfitting, the noise is randomly produced during the training process.
+We trained our model between $50$ and $290$ epochs depending on the complexity and the size of the problem.
+The $20\%$ of the training set that we call \emph{validation set} was left out of the training process and simply used to assess the global performance of the network.
+Training took less than a day for each model using a single NVIDIA Tesla K20.
+
+We compare the performance of the spherical CNN against two simple benchmark algorithms.
+The two baselines are based on building features with
+(a) the Power Spectral Densities (PSD) and
+(b) the histogram of pixels in the maps~\cite{patton2017cosmologicalconstraints}.
+After a normalization, those features are then classified using a Support Vector Machine (SVM) with a linear kernel.
+Other kernels did not provide better results, while having significantly worse scaling properties.
+All classifiers are trained with noisy samples.
+For fairness, we augmented the dataset of the baseline algorithm in a similar way as for the network; we created samples by adding new random realizations of the noise.
+We stop adding new samples in the classifier once the validation error converges.
+This process is detailed in \ref{sec:dataset_augmentation}.
+We tune the regularization parameter by cross-validating with the validation set.
 
@@
 
-We present in \figref{results} the results for $5$ different noise
-levels and $3$ different sample areas. The spherical CNN has a significant lead for all levels of noise and sample areas.
-In particular, the difference seems to increase as the problem becomes more complex, i.e., as the order is increased and there is less information in each sample.
-This is likely due to the fact that the SCNN can learn optimal features for the problem and do not rely on our humanly limited feature design.
-
-We observe that the PSD features, i.e.,
-one of the most used techniques for model discrimination in cosmology, is unable
-to perform the desired task. The main reason is that the two different models
-have very similar PSDs (see \figref{psd_sigma3}). As a result, one
-needs to use other statistics to solve the problem. In this case, the
-histogram features allow for a significant improvement over the PSD ones.
-Unfortunately, while the histogram features contain information about the
-distribution of pixels, they do not include any spatial information. In
-contrast, both the PSD features and the SCNN can exploit the spatial
-information.
-Note that without this graph structure, a fully connected neural network approach would have to be used. Problematically, fully connected neural networks do not scale well with the number of pixels.
-
-We have many different spherical neural network architectures and made a few empirical observations.
-First Chebyshef polynomial seems more stable than monomials. Nevertheless once the network is trained, we could not observe a significant accuracy difference.
-Second, using a statistical layer improved slightly the result for our specific problem.
-We tried $4$ different layers `mean', `variance', `mean + variance' and `histogram'.
-All but the `variance' were providing the same range of accurancy, the variance being slightly worse.
-Third, dropout did not help in the precence of noise. This is probably du to the fact that the dataset was augmented indefinitely
-Fourth, especially for difficult problem (order 2 or 4, and the presence of large noise) having a large architecture (many filters) and doing many iterations were necessary to achieve the result presented.
-
-\begin{figure*}[!ht]
+\begin{figure*}
 \centering
@@
 \includegraphics[width=0.32\linewidth]{result_order4}
-\caption{Classification errors for the 3 different problems.}
+\caption{
+Classification errors for the 3 different areas of the sphere.
+Green lines show the performance of the CNN, blue of the PDF+SVM, and red of the histogram+SVM.
+Green dashed line corresponds to the performance of CNN without the statistical layer.
+The noise level was increased from zero to $2\times$ the standard deviation of the mass map.
+}
 \label{fig:results}
@@
 
+\figref{results} presents the results for $5$ different noise levels and $3$ different sample areas.
+The spherical CNN has a significant lead for all levels of noise and sample areas.
+In particular, the difference seems to increase as the problem becomes more complex; as the order is increased, there is less information in each sample.
+This is likely due to the fact that the HealpixNet can learn optimal features for the problem and does not rely on hand-designed features.
+
+We observe that the PSD is unable to perform the desired task.
+The main reason is that the two different models were designed to have very similar PSDs (see \figref{psd_sigma3}).
+As a result, one needs to use other statistics to solve the problem.
+In this case, the histogram features allow for a significant improvement over the PSD ones.
+Unfortunately, while the histogram features contain information about the distribution of pixels, they do not include any spatial information.
+In contrast, both the PSD features and the HealpixNet can exploit the spatial information.
+Note that without this graph structure, a fully connected neural network approach would have to be used.
+Problematically, fully connected neural networks do not scale well with the number of pixels.
+\TK{I don't understand this comment.}
+
+We tried several different spherical neural network architectures and observed the following results.
+First, Chebyshev polynomial seems more stable than monomials \TK{what are monomials? stable in what sense?}.
+Nevertheless once the network is trained, we could not observe a significant accuracy difference.
+Second, using a statistical layer improved the result unlimited for our problem.
+We tried $4$ different layers `mean', `variance', `mean + variance' and `histogram'.
+The `mean', `histogram' and `mean + variance' were providing the same level of accuracy, with pure `variance' being slightly worse.
+Third, the use of the dropout\TK{was dropout mentioned before?} layer did not help in the presence of noise.
+This is probably due to the fact that the dataset was augmented indefinitely through the addition of noise.
+Fourth, especially for the more difficult cases, orders 2 or 4 and large noise levels, a large architecture with many filters and many training iterations were necessary to achieve high accuracy levels.
+
 \subsection{Filter visualization}
 One common visualization for CNN is to observe the shape of the learned filters.
-Since our construction leads to almost (up to the sampling irregularities)
-spherical filters, we plot in \figref{learned_filter} both the section (on the
-sphere) and a gnomonic projection on a plane of a random selection of learned
-filters. The filters are selected from the last layer of the network
-corresponding the experiment with order $o=2$ for a relative noise level of
-$2$. Nevertheless, all networks presented similar gnomonic and section pattern, at least from a
-human perspective. The gnomonic projection clearly exibits the sampling issue
-of HEALPix.
-For a detail, on how the convolution kernels are plotted, please refer to \ref{sec:filter_visualization}.
+Since our construction leads to almost (up to the sampling irregularities) spherical filters, we plot in \figref{learned_filter} both the radial profile and a gnomonic projection on a plane of a random selection of learned filters.
+The filters are selected from the last layer of the network corresponding the experiment with order $o=2$ for a relative noise level of $2$.
+Nevertheless, all networks presented visually similar gnomonic and profile pattern.
+% The gnomonic projection clearly exibits the sampling issue of HEALPix.
+% \TK{what issue? Commenting out for now}
+Detail of how the convolution kernels are plotted are described in \ref{sec:filter_visualization}.
 While it is usually difficult to interpret the shape of the filters in the context of the type of data, we can notice that they often have a ``peak'' like structures.
@@
 % \todo{Tomek: can you say something about the filters.}
-% \TK{Done }
-
-\begin{figure*}[!ht]
+% \TK{Done}
+
+\begin{figure*}
 \centering
@@
 
-\section{Discussion}
-
-Because of the spherical domain, the method presented here restricts the shape of the filters learned by the network to be radial.
+% \section{Discussion}
+
+% Because of the spherical domain, the method presented here restricts the shape of the filters learned by the network to be radial.
+% While this may be a less general design compared to the one used by conventional CNNs on flat images, we found it to still work efficiently for our test cases.
+% The layered structure of the network can partially compensate for that.
+% Further generalizations to non-radial filters may be possible [cite?]\TK{update here}, but we leave it to future work.
+
+% \nati{Should the discussion be merged with the result section?}
+% \TK{I think yes!}
+
+\section{Conclusion}
+\label{sec:conclusion}
+
+In this contribution we presented HealpixNet: a spherical convolutional neural network for the HEALPix sampling.
+The core of our method is the use of a graph to represent the pixel grid on the sphere.
+This allows us to leverage the advantages of the graph convolution; it is both efficient, with a complexity of $\mathcal{O}(N_{pix})$, and flexible, which allows to work only on a part of the sphere.
+Spherical properties of the domain are still captured well.
+The method presented here restricts the shape of the filters learned by the network to be radial.
 While this may be a less general design compared to the one used by conventional CNNs on flat images, we found it to still work efficiently for our test cases.
 The layered structure of the network can partially compensate for that.
-Further generalizations to non-radial filters may be possible [cite?], but we leave it to future work.
-
-\nati{Should the discussion be merged with the result section?}
-
-\section{Conclusion}
-\label{sec:conclusion}
-
-In this contribution, we presented HealpixNet, a spherical CNN for the HEALPix sampling. The gist of our construction resides in using a graph to model the sphere.
-This allows us to leverage the advantages of the graph convolution, i.e., it is both efficient (with a complexity of $\mathcal{O}(N_{pix})$) and flexible (allow to work only on a part of the sphere) while it still captures well the spherical properties of the domain.
-We also show on a range of classification problems that the neural network systematically significantly outperform classical methods.
-
-As shown in this contribution, modelling the discretized sphere, a 2D manifold in $\R^3$, by a graph enables an efficient convolution operation on any pixelization.
-Hence, it relaxes the iso-latitude constraint on sampling schemes who aim to enable fast convolutions.
-For applications which can tolerate small imprecisions in rotation invariance --- the fact that the action of a graph filter slightly depends on the location --- this relaxation might enable researchers to consider sampling sets with different properties.
-
-The main product of this contribution is HealpixNet,\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} a small and easy-to-use python package for cosmologists to classify sky maps.
-As a future work, we intend to (i) further investigate the link between the graph Fourier basis and the spherical harmonic and (ii) compare HealpixNet to other spherical CNN using different sampling schemes.
-
-\section*{Thanks}
+Further generalizations to non-radial filters may be possible [cite?]\TK{update here}, but we leave it to future work.
+
+We demonstrate that the neural network systematically and significantly outperforms our benchmark methods on an example problem of cosmological model discrimination with weak lensing mass maps.
+Notably, HEALPix maintains good classification accuracy even for high noise levels and part-sky areas.
+
+We show that the modelling the discretised sphere by a graph enables an efficient convolution operation on HEALPix sampling.
+% Hence, it relaxes the iso-latitude constraint on sampling schemes who aim to enable fast convolutions.
+% \TK{I would move the info about possible relaxation of the iso-latitude thing to a separate paragraph at the end on conclusions - future prospects?}
+Graph-based representation of the sphere can display small imprecisions in rotation invariance, which results in the property that the action of a graph filter slightly depends on the location.
+For applications that can tolerate this property, an graph-based representation may be a worthwhile alternative.
+% this relaxation might enable researchers to consider sampling sets with different properties.
+% \TK{this I don't understand}
+For example, a machine learning based cosmological inference algorithm can in principle tolerate this property, as it requires the simulations to be represented the same way as observations anyway.
+This way, imperfections in representation will affect the simulations and real data in the same way, and will not cause biases in the analysis result.
+
+The main product of this contribution is HealpixNet a small and easy-to-use python package for cosmologists to classify sky maps.
+The code and data used in this work are publicly available\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}.
+
+As a future work, it would be interesting to further investigate the link between the graph Fourier basis and the spherical harmonics.
+Further comparison of HealpixNet to other spherical CNN algorithms, with different sampling schemes, would also be worthwhile.
+
+\section*{Acknowledgements}
 
@@
 
-\begin{figure}[!ht]
+\begin{figure}
 \centering

### 2018-07-30 scnn.tex
moved heat to appendix

@@
     \item branch with notebooks with plots (results) NP
-    \item Michael section 4.5 (efficient convolutions) and 3.2 (conv on graphs)
     \item NP move the repo to HealpixNet
@@
     \item (TK) add info on comparison with histograms, so that it's just a demonstration
-    \item (TK NP) if we have time make a new candidate for network plot (optional)
-    \item (first version done) conclusions
-    \item Should the heat example go to appendix?
-    \item TK read the heat section again
     \item TK read the result section
@@
     \item uniformize text size in figures
+    \item (done! first version done) conclusions
+    \item (done!) Michael section 4.5 (efficient convolutions) and 3.2 (conv on graphs)
+    \item (done!) (TK NP) if we have time make a new candidate for network plot (optional)
+    \item (done!) TK read the heat section again
+    \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
 \end{itemize}
@@
 \label{sec:related}
+
+\begin{figure}
+    \centering
+    \includegraphics[height=7em]{sphere_grid_equirectangular}
+    \hfill
+    \includegraphics[height=7em]{sphere_grid_cubedsphere}
+    \hfill
+    \includegraphics[height=7em]{half_graph_4}
+    \caption[]{Some pixelizations of the sphere.
+Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system.
+Middle: an equiangular cubed-sphere grid, as described in \citet{ronchi1996cubed}.
+Right: graph built from an HEALPix pixelization of half the sphere ($N_{side} = 4$).
+By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[7] Left and middle figures are taken from \citet{boomsma2017spherical}.}
+    \label{fig:sphere_grids}
+    \label{fig:healpix_graph_4}
+\end{figure}
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[height=7em]{sphere_grid_equirectangular}
-	\hfill
-	\includegraphics[height=7em]{sphere_grid_cubedsphere}
-	\hfill
-	\includegraphics[height=7em]{half_graph_4}
-	\caption[]{Some pixelizations of the sphere.
-Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system.
-Middle: an equiangular cubed-sphere grid, as described in \citet{ronchi1996cubed}.
-Right: graph built from an HEALPix pixelization of half the sphere ($N_{side} = 4$).
-By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[7] Left and middle figures are taken from \citet{boomsma2017spherical}.}
-	\label{fig:sphere_grids}
-	\label{fig:healpix_graph_4}
-\end{figure}
-
 % As presented by~\cite{cohen2018spherical}, the most mathematical approach to extend the convolution on a sphere is to use a spherical Fourier transform.
@@
 
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{exampleEarthTopo}
+        \caption{}
+        \label{fig:example_earth}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\linewidth}
+        \centering
+        \includegraphics[width=\linewidth]{exampleCMB}
+        \caption{}
+        \label{fig:example_cmb}
+    \end{subfigure}
+    \caption[]{Example of (a) an Earth topography map composed of \textasciitilde 3 million pixels (\textasciitilde 7 arcmin resolution) and (b) a model of the Cosmic Microwave Background (CMB) radiation temperature anisotropy, composed of \textasciitilde 13 million pixels (\textasciitilde 3.4 arcmin resolution).\footnotemark}
+    \label{fig:example_maps}
+\end{figure}
+
 Before doing any numerical analysis on the sphere, one first has to choose a tessellation, i.e., an exhaustive partition of the sphere into finite area elements, where the data under study is quantized.
@@
 \figref{example_maps} shows two examples of HEALPix maps: the Cosmic Microwave Background \citep{planck2015overview} and \TK{update}.
-
-\begin{figure}
-	\centering
-	\begin{subfigure}[b]{0.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{exampleEarthTopo}
-		\caption{}
-		\label{fig:example_earth}
-	\end{subfigure}
-	\hfill
-	\begin{subfigure}[b]{0.45\linewidth}
-		\centering
-		\includegraphics[width=\linewidth]{exampleCMB}
-		\caption{}
-		\label{fig:example_cmb}
-	\end{subfigure}
-	\caption[]{Example of (a) an Earth topography map composed of \textasciitilde 3 million pixels (\textasciitilde 7 arcmin resolution) and (b) a model of the Cosmic Microwave Background (CMB) radiation temperature anisotropy, composed of \textasciitilde 13 million pixels (\textasciitilde 3.4 arcmin resolution).\footnotemark}
-	\label{fig:example_maps}
-\end{figure}
 
@@
 \end{equation}
-\textbf{Example.}
-Let us consider the heat diffusion problem
-\begin{equation} \label{eqn:heat_equation}
-	\L \b{f}(t) = \tau \partial_t \b{f}(t),
-\end{equation}
-where $\b{f}: \R_+ \rightarrow \R^{N_{pix}}$. Given the initial condition
-$\b{f}(0)$, the solution of~\eqnref{heat_equation} can be expressed as
-\begin{equation*}
-	\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U\trans \g{f}(0) = K_t(\L) \b{f}(0),
-\end{equation*}
-which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(\lambda)=e^{-\tau t \lambda}$.
+In \ref{sec:heat_diffusion} we present an example application of graph-based convolution to a simple heat-diffusion problem.
+% \textbf{Example.}
+% Let us consider the heat diffusion problem
+% \begin{equation} \label{eqn:heat_equation}
+% 	\L \b{f}(t) = \tau \partial_t \b{f}(t),
+% \end{equation}
+% where $\b{f}: \R_+ \rightarrow \R^{N_{pix}}$. Given the initial condition
+% $\b{f}(0)$, the solution of~\eqnref{heat_equation} can be expressed as
+% \begin{equation*}
+% 	\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U\trans \g{f}(0) = K_t(\L) \b{f}(0),
+% \end{equation*}
+% which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(\lambda)=e^{-\tau t \lambda}$.
 Since the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$, which can be interpreted as squared frequencies, it can also be considered as a generalization of the Gaussian kernel on the sphere.
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{gaussian_filters_sphere}
-	\caption{Comparison of convolution with the graph and the spherical harmonics ($N_{side} = 16$).
-	Top: Diffusion of a unit of heat for different times $t$ using the graph.
-	Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin).
-	Relative difference between graph convolution and spherical smoothing: $10.4$\%, $4.8$\%, $3.8$\%.
-\todo{The main issue with our filters is that their shape depends on the localization.
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=\linewidth]{gaussian_filters_sphere}
+% 	\caption{Comparison of convolution with the graph and the spherical harmonics ($N_{side} = 16$).
+% 	Top: Diffusion of a unit of heat for different times $t$ using the graph.
+% 	Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin).
+% 	Relative difference between graph convolution and spherical smoothing: $10.4$\%, $4.8$\%, $3.8$\%.
+% \todo{The main issue with our filters is that their shape depends on the localization.
 It would be nice to measure the expectation and variance of the error over all locations.
 That would show how severe the distortion is.}
-\nati{Let us keep that for the next paper. I am quite sure, it is negligible in this particular case.}}
-	\label{fig:gaussian_filters_comparizon}
-\end{figure}
-
-Furthermore, this result is another sign that the constructed graph is able to capture the spherical
-structure of the HEALPix sampling. In some applications, where the
-exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
-The fact that both convolutions are not identical is not relevant in a neural network setting, as the convolution kernels are learned anyway.
+% \nati{Let us keep that for the next paper. I am quite sure, it is negligible in this particular case.}}
+% 	\label{fig:gaussian_filters_comparizon}
+% \end{figure}
+
+% Furthermore, this result is another sign that the constructed graph is able to capture the spherical
+% structure of the HEALPix sampling. In some applications, where the
+% exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
+% The fact that both convolutions are not identical is not relevant in a neural network setting, as the convolution kernels are learned anyway.
 % not ideal tho as the graph convolution depends on the localization
@@
 
+\section{Example: heat diffusion}
+\label{sec:heat_diffusion}
+Let us consider the heat diffusion problem
+\begin{equation} \label{eqn:heat_equation}
+  \L \b{f}(t) = \tau \partial_t \b{f}(t),
+\end{equation}
+where $\b{f}: \R_+ \rightarrow \R^{N_{pix}}$. Given the initial condition
+$\b{f}(0)$, the solution of~\eqnref{heat_equation} can be expressed as
+\begin{equation*}
+  \b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U\trans \g{f}(0) = K_t(\L) \b{f}(0),
+\end{equation*}
+which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(\lambda)=e^{-\tau t \lambda}$.
+Since the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$, which can be interpreted as squared frequencies, it can also be considered as a generalization of the Gaussian kernel on the sphere.
+\figref{gaussian_filters_comparizon} shows the effect of the convolution by diffusing a unit of heat for $\tau=1$ at various times $t$.
+By comparing the graph convolution with the spherical symmetric Gaussian smoothing, we observe that both techniques lead to similar results (see \figref{gaussian_filters_comparizon}).
+While the graph convolution remains different from the spherical convolution, this small experiment shows that, providing the correct parameters, graph convolution can approximate spherical convolution.
+For additional insides about the graph kernel $K_t$, we refer to the \figref{gaussian_filters_visualization} and~\ref{sec:filter_visualization}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\linewidth]{gaussian_filters_sphere}
+  \caption{Comparison of convolution with the graph and the spherical harmonics ($N_{side} = 16$).
+  Top: Diffusion of a unit of heat for different times $t$ using the graph.
+  Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin).
+  Relative difference between graph convolution and spherical smoothing: $10.4$\%, $4.8$\%, $3.8$\%.
+\todo{The main issue with our filters is that their shape depends on the localization.
+It would be nice to measure the expectation and variance of the error over all locations.
+That would show how severe the distortion is.}
+\nati{Let us keep that for the next paper. I am quite sure, it is negligible in this particular case.}}
+  \label{fig:gaussian_filters_comparizon}
+\end{figure}
+
+Furthermore, this result is another sign that the constructed graph is able to capture the spherical
+structure of the HEALPix sampling. In some applications, where the
+exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
+The fact that both convolutions are not identical is not relevant in a neural network setting, as the convolution kernels are learned anyway.
+not ideal tho as the graph convolution depends on the localization
+
 \section{Filter visualization}

### 2018-07-30 scnn.tex
updated todo
added acknowledgements

@@
 \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+    \item (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
     \item (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook.
@@
 \section*{Acknowledgements}
+This work was supported by a grant from the Swiss Data Science Centre (SDCS) under project ID \textit{sd01 - DLOC:  Deep Learning for Observational Cosmology} and grant number 200021\_169130 from the Swiss National Science Foundation.
 

### 2018-07-31 scnn.tex
small edits

@@
 While each of those twelve grids could potentially be independently fed into a 2D CNN, boundary conditions would have to be properly handled, as those grids are not independent.
-\todo{How do thy handle boundaries?}
+\todo{How do they handle boundaries?}
 \TK{+1,good question}
+\nati{They are almost not talking about that. For the cubed sphere, the only reference I could found was: 
+\emph{"When implementing convolutions and pooling operations for the cubed-sphere grid, one has to be careful in padding each patch with the contents of the four neighbouring patches, in order to preserve the wrapped topology of the sphere (figure 2, right)."}
+Note that for the cubed sphere sampling each pixel has exactly four neighboors which make the problem of border effect handable.
+As for the equirectangular grid, it is equivalent to a cylinder.
+So I guess they take the standard image processing border conditions (reflective).
+I do not think we should mention any of that in the paper.
+}
 % Furthermore, the grid requirement makes it impossible for the convolution to capture the spherical properties of the domain, i.e., the cubed-sphere sampling is by definition adapted to a cube and not to a sphere.
@@
 \todo{and hinders performance (should be empirically verified)}.
-\TK{This is a strong claim, can we support this?}
+\TK{This is a strong claim, can we support this?} \nati{It is not that strong as we use "may" right?
+We should probably soften it a bit.
+However the main idea is correct.
+If you compute some statistics on some features, you lose some information and may get worse results.
+}
 Moreover, the chosen statistics have to be hand-crafted to capture statistics of interest.
@@
 \todo{In HealpixNet we use the idea of a statistical layer, described in \secref{stat_layer}, to provide invariance to isometric transformations such as translation and rotation on the sphere.
-\TK{We would need to describe the idea of the statistical layer for the cosmology audience. They don't have a clue what it is.}
+\TK{We would need to describe the idea of the statistical layer for the cosmology audience. They don't have a clue what it is.}\nati{Can't they just wait for \secref{stat_layer}? }
 The use of the statistical layer is optional.
@@
 \citet{khasanova2017graphomni} uses the mean and variance of diffused versions of the last feature maps in their statistical layer.}
-\TK{why is this section in TODO?}
+\TK{why is this section in TODO?\nati{Probably because, we have not decided if we use the histogram yet. This paragraph needs to be rewritten once we are clear with the code.}}
 
@@
 \end{equation}
-In \ref{sec:heat_diffusion} we present an example application of graph-based convolution to a simple heat-diffusion problem.
+In \ref{sec:heat_diffusion}, we present an example application of graph-based convolution to a simple heat-diffusion problem in order to shed some light on what is the convolution on a graph.
 % \textbf{Example.}
@@
 While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
-In practice, we found out that Chebyshev polynomials are slightly more stable in our experiment \TK{slightly more stable than what?}.
+In practice, we found out in our experiment that Chebyshev polynomials are slightly more stable than the monomials used in~\cite{khasanova2017graphomni}(i.e.
+optimizing directly the $\theta_k$ in \eqnref{graph_convolution_polynomial}).
 We believe that this is due to their orthogonality (as explained above) and uniformity\footnote{The amplitude of Chebyshev polynomials is more or less constant over the domain $[-1, 1]$ independently of the order $k$.
@@
 \begin{equation}
-NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC
+NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC,
 \end{equation}
-\TK{what is the meaning of $\circ$ here?}
+\TK{what is the meaning of $\circ$ here?}\nati{where $\circ$ is the composition operator between two layers.}
 The number of features $F$ depends on the data at hand.
@@
 Note that without this graph structure, a fully connected neural network approach would have to be used.
-Problematically, fully connected neural networks do not scale well with the number of pixels.
-\TK{I don't understand this comment.}
+Problematically, fully connected neural networks generally scales squarely with their number of inputs.
+\TK{I don't understand this comment.} \nati{Maybe we should leave it out then. It is not that important.}
 
 We tried several different spherical neural network architectures and observed the following results.
-First, Chebyshev polynomial seems more stable than monomials \TK{what are monomials? stable in what sense?}.
+First, Chebyshev polynomial seems more stable than monomials ($\theta_k$ in \eqnref{graph_convolution_polynomial}), in the sense that the training loss had a more steadily decrease.
+%\TK{what are monomials? stable in what sense?}
 Nevertheless once the network is trained, we could not observe a significant accuracy difference.
@@
 The `mean', `histogram' and `mean + variance' were providing the same level of accuracy, with pure `variance' being slightly worse.
-Third, the use of the dropout\TK{was dropout mentioned before?} layer did not help in the presence of noise.
+Third, the use of the dropout\TK{was dropout mentioned before?} \nati{Probably not. But to keep it simple, we may just add a footnote or a reference.} layer did not help in the presence of noise.
 This is probably due to the fact that the dataset was augmented indefinitely through the addition of noise.

### 2018-08-01 scnn.tex
added caption to example maps

--- 2018-07-30 scnn.tex
@@
 
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.45\linewidth}
-        \centering
-        \includegraphics[width=\linewidth]{exampleEarthTopo}
-        \caption{}
-        \label{fig:example_earth}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.45\linewidth}
-        \centering
-        \includegraphics[width=\linewidth]{exampleCMB}
-        \caption{}
-        \label{fig:example_cmb}
-    \end{subfigure}
-    \caption[]{Example of (a) an Earth topography map composed of \textasciitilde 3 million pixels (\textasciitilde 7 arcmin resolution) and (b) a model of the Cosmic Microwave Background (CMB) radiation temperature anisotropy, composed of \textasciitilde 13 million pixels (\textasciitilde 3.4 arcmin resolution).\footnotemark}
+\begin{figure*}
+\includegraphics[width=\linewidth]{figures/figure_example_maps.pdf}
+\caption{Exmaple maps on the sphere:
+(left) the CMB temperature (K) map from Planck \citep{planck2015overview}, with galactic plane masked,
+(middle) map of galaxy number counts (number of galaxies per arcmin$^2$) in SDSS DR14 \citep{abolfathi2017sdssDR14},
+and (right) simulated weak lensing convergence map (dimensionless) simulated with DES DR1 mask \citep{des2018dr1}.
+These maps were pixelised using \texttt{nside}=512.
+The CMB and weak lensing mass maps were smoothed with Gaussian kernels with FWHM=1 deg, and the galaxy count map with FWHM=0.5 deg.
+}
 \label{fig:example_maps}
-\end{figure}
+\end{figure*}
+
+% \begin{figure}
+%     \centering
+%     \begin{subfigure}[b]{0.45\linewidth}
+%         \centering
+%         \includegraphics[width=\linewidth]{exampleEarthTopo}
+%         \caption{}
+%         \label{fig:example_earth}
+%     \end{subfigure}
+%     \hfill
+%     \begin{subfigure}[b]{0.45\linewidth}
+%         \centering
+%         \includegraphics[width=\linewidth]{exampleCMB}
+%         \caption{}
+%         \label{fig:example_cmb}
+%     \end{subfigure}
+%     \caption[]{Example of (a) an Earth topography map composed of \textasciitilde 3 million pixels (\textasciitilde 7 arcmin resolution) and (b) a model of the Cosmic Microwave Background (CMB) radiation temperature anisotropy, composed of \textasciitilde 13 million pixels (\textasciitilde 3.4 arcmin resolution).\footnotemark}
+%     \label{fig:example_maps}
+% \end{figure}
 

### 2018-08-02 scnn.tex
added figure pooling
updated plots

@@
 \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-    \item (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
     \item (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook.
@@
     \item TK check the appendix
-    \item TK optional - example of data (CMB (mask) + mass map + radio intensity)
-    \item TK read everything
+    \item (almost done) TK optional - example of data (CMB (mask) + mass map + radio intensity)
+    \item (almost done) TK read everything
     \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings.
@@
     \item (done!) TK read the heat section again
+    \item (done!) (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
     \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
@@
     % \includegraphics[width=\linewidth]{architecture}
-	\includegraphics[width=\linewidth]{figure_architecture_v2}
+	\includegraphics[width=\linewidth]{figure_architecture_v3.pdf}
 	\caption{Overall network architecture, showing here two convolutional layers acting as feature extractors followed by a fully connected layer with softmax acting as the classifier.
@@
 	\centering
-	\includegraphics[width=\linewidth]{pooling}
+    % \includegraphics[width=\linewidth]{pooling}
+	\includegraphics[trim=1.1cm 0cm 0cm 0cm, width=\linewidth]{figures/figure_pooling_svg.pdf}
 	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarsest cell covers $1/12$ of the sphere.}
@@
 \centering
-\includegraphics[width=0.75\linewidth]{smooth_map_class_1}
+% \includegraphics[width=0.75\linewidth]{smooth_map_class_1}
+% trim=left botm right top
+\includegraphics[trim=1cm 0cm 0cm 0cm, width=0.49\linewidth]{figures/figure_kappa_diff_model1.pdf}
 % \hfill
-\includegraphics[width=0.75\linewidth]{smooth_map_class_2}
+% \includegraphics[width=0.75\linewidth]{smooth_map_class_2}
+\includegraphics[trim=0cm 0cm 1cm 0cm, width=0.49\linewidth]{figures/figure_kappa_diff_model2.pdf}
 \caption{Example maps from two classes to be discriminated. Left: model 1 with $\Omega_m=0.31$ and $\sigma_8=0.82$. Right: model 2 with $\Omega_m=0.26$ and $\sigma_8=0.91$.
@@
 Using the properties of the HEALPix sampling, we can split each maps into $12*o^2$ ($o=1,2,4,\dots$) samples that span a smaller part of the sphere.
-As shown in \figref{part_sphere}, we used $o=1,2,4$ as the resulting samples are large enough to suffer from the effects of the spherical geometry.
+% As shown in \figref{part_sphere}, we used $o=1,2,4$ as the resulting samples are large enough to suffer from the effects of the spherical geometry.
+The resulting maps are large enough to suffer from the effects of the spherical geometry, and cover 8.3\%, 2.1\% and 0.5\% of the total sphere area for $o=1,2,4$, respectively.
 We decided to only report simulation results for this specific setting as spherical cosmological data usually does not span the full sphere.
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{part_sphere}
-\caption{Three parts of the sphere with different sizes. Blue: $o=1$. Green: order $o=2$. Yellow: order $o=4$.}
-\label{fig:part_sphere}
-\end{figure}
+% \begin{figure}
+% \centering
+% \includegraphics[width=\linewidth]{part_sphere}
+% \caption{Three parts of the sphere with different sizes. Blue: $o=1$. Green: order $o=2$. Yellow: order $o=4$.}
+% \label{fig:part_sphere}
+% \end{figure}
 For all the experiments, we work with centred Gaussian noise.
@@
 working on the sphere with theoretically spherical filters (up to the irregularities of the sampling), we could only plot the section of the convoluted Kroneker.
-To do so, we convolve a Kroneker on the equator and use the equator for our section as shown in~\figref{index_section}.
-Note that, because of the small irregularities in the HEALPix
-sampling, the second and the third methods are subject to small variations depending on the
-chosen Kroneker.
+% To do so, we convolve a Kroneker on the equator and use the equator for our section as shown in~\figref{index_section}.
+To do so, we convolve a Kroneker on the nodes along the equator and use the equator for our section.
+Note that, because of the small irregularities in the HEALPix sampling, the second and the third methods are subject to small variations depending on the chosen position of the Kroneker.
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.6\linewidth]{index_plotting_order20_nside16}
-\caption{Indexes selected for the section ploting of \figref{gaussian_filters_visualization} middle. The delta was placed on the yellow node.}
-\label{fig:index_section}
-\end{figure}
+% \begin{figure}
+% \centering
+% \includegraphics[width=0.6\linewidth]{index_plotting_order20_nside16}
+% \caption{Indexes selected for the section ploting of \figref{gaussian_filters_visualization} middle. The delta was placed on the yellow node.}
+% \label{fig:index_section}
+% \end{figure}
 

### 2018-08-03 scnn.tex
small modification

@@
 Hence, a practical comparison is not possible.
-% \TK{This I would leave out here, as this is a "spoiler" of the results section.}
+% \TK{I would leave out here, as this is a "spoiler" of the results section.}
 
 Approaches by \citet{cohen2018spherical, boomsma2017spherical} can not be easily accelerated when the data lies on a part of the sphere only.
+ \nati{Why is \citet{boomsma2017spherical} here?
+I think it can be trivally accelerated.}
 That is an important use case in cosmology as measurements are often partial, i.e., full-sky maps are rare.
@@
 If you compute some statistics on some features, you lose some information and may get worse results.
-}
+Nevertheless, since we are also using a statistical layer, I would juste remove this.}
 Moreover, the chosen statistics have to be hand-crafted to capture statistics of interest.
@@
 
+\subsection{Selected architecture}
+\todo{Describe our fully convolutional architecture}
+
 \subsection{Results}

### 2018-08-03 scnn.tex
editing the todo list

--- 2018-08-02 scnn.tex
@@
 \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+
+    \item (TK) add section in conclusions/ paragraph on possible extensions to the code: dense output, regression, GANs, segmentation
+    \item (NP+MD)  paragraph on our chosen architecture in the Experiments sections
+    \item (TK) add reference to figure (pooling) to the area of orders
+    \item (NP+MD) move the Related Work section after the Method section
+
     \item (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook.

### 2018-08-03 scnn.tex
composition operator

@@
 Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
-An example network can be defined as
-\begin{equation}
+An example network is
+\begin{equation*}
 NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC,
-\end{equation}
-\TK{what is the meaning of $\circ$ here?}\nati{where $\circ$ is the composition operator between two layers.}
+\end{equation*}
+where $\circ$ denotes composition, i.e., $f \circ g = f(g(\cdot))$.
 The number of features $F$ depends on the data at hand.

### 2018-08-03 scnn.tex
move related work
updated example maps figure +todo

--- 2018-08-03 scnn.tex
@@
 
+    \item (MD+NP) talk about the loss in 3.8 (old 4.8)
+    \item (NP) make figure A.13 remove white space
+    \item (TK) re-make figures to make the labels/legend/titles the same font size as the main text
     \item (TK) add section in conclusions/ paragraph on possible extensions to the code: dense output, regression, GANs, segmentation
@@
     \item (NP+MD) move the Related Work section after the Method section
+    \item (NP) vertex interpretation
 
@@
     \item uniformize text size in figures
-    \item (done! first version done) conclusions
-    \item (done!) Michael section 4.5 (efficient convolutions) and 3.2 (conv on graphs)
-    \item (done!) (TK NP) if we have time make a new candidate for network plot (optional)
-    \item (done!) TK read the heat section again
-    \item (done!) (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
-    \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
+    % \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
+    % \item (done! first version done) conclusions
+    % \item (done!) Michael section 4.5 (efficient convolutions) and 3.2 (conv on graphs)
+    % \item (done!) (TK NP) if we have time make a new candidate for network plot (optional)
+    % \item (done!) TK read the heat section again
+    % \item (done!) (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
 \end{itemize}
@@
 % \TK{I would leave out here, as this is a "spoiler" of the results section.}
-
-Approaches by \citet{cohen2018spherical, boomsma2017spherical} can not be easily accelerated when the data lies on a part of the sphere only.
- \nati{Why is \citet{boomsma2017spherical} here?
-I think it can be trivally accelerated.}
+Approaches by \citet{cohen2018spherical,boomsma2017spherical} can not be easily accelerated when the data lies on a part of the sphere only.
+\nati{Why is \citet{boomsma2017spherical} here? I think it can be trivally accelerated.}
 That is an important use case in cosmology as measurements are often partial, i.e., full-sky maps are rare.
@@
 \label{sec:heat_diffusion}
+
 Let us consider the heat diffusion problem
-\begin{equation} \label{eqn:heat_equation}
+\begin{equation}
   \L \b{f}(t) = \tau \partial_t \b{f}(t),
+  \label{eqn:heat_equation}
 \end{equation}

### 2018-08-03 scnn.tex

@@
 
-\footnotetext{Figures from \url{https://healpix.jpl.nasa.gov/}.}
-
 \subsection{Graph construction}
@@
 
+\section{Related work}
+\label{sec:related}
+
+\begin{figure}
+    \centering
+    \includegraphics[height=7em]{sphere_grid_equirectangular}
+    \hfill
+    \includegraphics[height=7em]{sphere_grid_cubedsphere}
+    \hfill
+    \includegraphics[height=7em]{half_graph_4}
+    \caption[]{Some pixelizations of the sphere.
+Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system.
+Middle: an equiangular cubed-sphere grid, as described in \citet{ronchi1996cubed}.
+Right: graph built from an HEALPix pixelization of half the sphere ($N_{side} = 4$).
+By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[7] Left and middle figures are taken from \citet{boomsma2017spherical}.}
+    \label{fig:sphere_grids}
+    \label{fig:healpix_graph_4}
+\end{figure}
+
+\citet{boomsma2017spherical} apply a standard 2D CNN to a grid discretization of the sphere.
+Two grids, illustrated in \figref{sphere_grids}, are used in their work: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}.
+As this formulation uses the standard 2D convolutions, all the optimizations developed for 2D images can be applied, what make it computationally very efficient.
+It is, however, restricted to those grid sampling sets.
+Similarly to the cubed-sphere, HEALPix is a composition of twelve grids.
+While each of those twelve grids could potentially be independently fed into a 2D CNN, boundary conditions would have to be properly handled, as those grids are not independent.
+\todo{How do they handle boundaries?}
+\TK{+1,good question}
+\nati{They are almost not talking about that. For the cubed sphere, the only reference I could found was:
+\emph{"When implementing convolutions and pooling operations for the cubed-sphere grid, one has to be careful in padding each patch with the contents of the four neighbouring patches, in order to preserve the wrapped topology of the sphere (figure 2, right)."}
+Note that for the cubed sphere sampling each pixel has exactly four neighboors which make the problem of border effect handable.
+As for the equirectangular grid, it is equivalent to a cylinder.
+So I guess they take the standard image processing border conditions (reflective).
+I do not think we should mention any of that in the paper.
+}
+% Furthermore, the grid requirement makes it impossible for the convolution to capture the spherical properties of the domain, i.e., the cubed-sphere sampling is by definition adapted to a cube and not to a sphere.
+Nope, the graph can adapt to any sampling.
+% Moreover, those samplings are not ideal as their resolution is not constant across the sphere.
+Moreover, the pixel area is not constant across the sphere in those sampling schemes, which may limit their potential applications.
+Indeed, the singularities, such as the poles for the equirectangular grid, and the corners of the cube for the cubed-sphere, are over-sampled.
+Equal areas of discrete elements is advantageous for many physical measurements, as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence \citep{gorski2005healpix}.
+% \nati{Michael: Under some very specific hypothesis, this second approach is a particular case of our method, i.e.
+(i) our method with a stupid sampling, (ii) assumption that graph convolution on a grid == 2d convolution.
+Do you think we should mention that?
+I think we should not.}
+Finally, a 2D CNN learns directional filters, which are well defined with respect of the image coordinates.
+Directions that make much sense for images (up, down, left, and right) are arbitrarily defined when setting the origin of the grids on the sphere.
+Any convolution using directions on the sphere is not equivariant to translation and rotation.
+
+% As presented by~\cite{cohen2018spherical}, the most mathematical approach to extend the convolution on a sphere is to use a spherical Fourier transform.
+The convolution is then simply defined as the product in the spectral domain.
+This approach requires one Fourier and one inverse Fourier transform per convolution which remain, even with accelerated algorithms, expensive.
+
+\citet{cohen2018spherical} uses the continuous spherical convolution.
+The goal of this contribution was to define a rotation-equivariant convolution on the sphere, i.e., a rotation of the input implies the same rotation in the output.
+The resulting convolution is performed by (i) a spherical harmonic transform (SHT), i.e., a projection on the spherical harmonics, (ii) a  multiplication in the spectral domain, and (iii) an inverse SHT.
+Hence the computational cost of a convolution is dominated by the two SHTs.
+A naive implementation of the SHT costs $\bO(N_{pix}^2)$ operations, where $N_{pix}$ is the number of pixels.
+Accelerated schemes exist for some sampling sets \citep[see][for examples]{mohlenkamp1999fast, rokhlin2006fast, reinecke2013libsharp}.
+The main advantage of this approach is that it provides a mathematically well defined rotation-equivariant network.
+Nevertheless, even with accelerated SHTs, the convolutions remain expensive, limiting the practical use of this approach.
+For example with the HEALPix sampling, which was designed to have a fast SHT by being iso-latitude, the computational cost of the SHT is $\bO(N_{pix}^{3/2}) = \bO(N_{side}^3) = \bO(\ell_{max}^3)$, where $\ell_{max}$ is the largest angular frequency\footnote{All pixels are placed on $N_{ring} = 4N_{side}-1 = \bO(\sqrt{N_{pix}})$ rings of constant latitude.
+Each ring has $\bO(\sqrt{N_{pix}})$ pixels.
+Thanks to this iso-latitude property, the SHT is computed using recurrence relations for Legendre polynomials on co-latitude and fast Fourier transforms (FFTs) on longitude.
+The computational cost is thus $\sqrt{N_{pix}}$ FFTs for a total cost of $\bO(N_{pix} \log(\sqrt{N_{pix}}))$, plus $\sqrt{N_{pix}}$ matrix multiplications of size $\sqrt{N_{pix}}$ for a total cost of $\bO(N_{pix}^{3/2})$.}
+\citep{gorski2005healpix, reinecke2013libsharp}.
+In comparison, filtering with our HealpixNet method scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}).
+% Moreover, \figref{filtering_speed} shows that a naive implementation of our method is more than ten times faster than the SHT implemented by the highly optimized \pkg{libsharp} library used by HEALPix \citep{reinecke2013libsharp}.
+% While a comparison is theoretically possible, the experiments of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and do not provide any code for the HEALPix one.
+Hence, a practical comparison is not possible.
+% \TK{I would leave out here, as this is a "spoiler" of the results section.}
+
+Approaches by \citet{cohen2018spherical, boomsma2017spherical} can not be easily accelerated when the data lies on a part of the sphere only.
+ \nati{Why is \citet{boomsma2017spherical} here?
+I think it can be trivally accelerated.}
+That is an important use case in cosmology as measurements are often partial, i.e., full-sky maps are rare.
+One could still fill the unseen part of the sphere with zeros, and avoid to compute empty integrals, on the latitude or longitude.
+It is, however, not straightforward to identify those empty directions, and computations would still be wasted; consider, for example, a ring which mostly contains zeros but a few measurements.
+With graphs however, the computation is done only for the used pixels.
+This, however, results in some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}).
+These can be mitigated by padding with zeros a small area around the measurements.
+
+% In an attempt to get the best of the first two approaches, we follow a third
+% direction. We use a graph to adapt to the particular structure of the sphere.
+% While the convolution remains efficient, it still captures well the spherical
+% structure and is particularly adapted to the HEALPix sampling.
+% \TK{I am not sure what is the point of this paragraph, we described our approach already before}
+
+The use of a graph to model the discretised sphere was also considered by~\citet{khasanova2017graphomni}.
+The authors map omnidirectional images onto a sphere, with the goal of correcting for distortions induced by the lens, which was used for their acquisition.
+Besides a different practical application, for which the method was designed, there are two important differences.
+% First, a different sampling scheme is used: \cite{khasanova2017graphomni} uses a grid.
+First, similarly to~\citet{boomsma2017spherical}, they use an equirectangular grid sampling.
+% \TK{how is it different from us?}
+Second, it uses a graph CNN based on a different parameterisation of the convolution kernel.
+Moreover, they did not take advantage of a hierarchical pixelization of the sphere and resorted to dynamic pooling~\citep{kalchbrenner2014dcnn}.
+Finally, while the rotation invariance is desirable, the statistical layer used
+% --- an operation which computes a set of spatially invariant statistics of the last feature map ---
+% \{TK} this should be explained earlier
+may not capture the information in an optimal way
+\todo{and hinders performance (should be empirically verified)}.
+\TK{This is a strong claim, can we support this?} \nati{It is not that strong as we use "may" right?
+We should probably soften it a bit.
+However the main idea is correct.
+If you compute some statistics on some features, you lose some information and may get worse results.
+Nevertheless, since we are also using a statistical layer, I would juste remove this.}
+Moreover, the chosen statistics have to be hand-crafted to capture statistics of interest.
+% While developing completely invariant transforms is a goal worth investigating, CNNs for image recognition, which are arguably the most researched and developed architectures, are not built to be fully invariant to translation.
+% As with the proposed spherical CNN, the fully connected layers at the end of the network depend on the spatial localization of features.
+% While that may not be ideal, it was shown to work well in practice.
+% \TK{The two sentences above look like a tangent to me.. can we skip it an go to the main point, which is I think the fact that we use the stat layer?}
+
+\todo{In HealpixNet we use the idea of a statistical layer, described in \secref{stat_layer}, to provide invariance to isometric transformations such as translation and rotation on the sphere.
+\TK{We would need to describe the idea of the statistical layer for the cosmology audience. They don't have a clue what it is.}\nati{Can't they just wait for \secref{stat_layer}? }
+The use of the statistical layer is optional.
+In our approach, we are keeping all the statistical moments by retaining a full, learned learned feature histogram, an approach that performed the best in our tests.
+That is similar to the learnable histogram introduced by \citet{wang2016learnhist}, although for a purpose of integrating global context in object detection and segmentation tasks.
+\citet{khasanova2017graphomni} uses the mean and variance of diffused versions of the last feature maps in their statistical layer.}
+\TK{why is this section in TODO?\nati{Probably because, we have not decided if we use the histogram yet. This paragraph needs to be rewritten once we are clear with the code.}}
+
+There exists many formulations of graph neural networks, reviewed by \citet{bronstein2017review} and \citet{hamilton2017review}.
+For this contribution, we chose the formulation of \citet{defferrard2016convolutional} as its root on strong graph signal processing theory makes the concept of convolutions and filters explicit \citep{shuman2013emerging}.
+Its tie to a graph Fourier transform allows us to compare with the spherical harmonic transform, and study its invariance properties.
+More geometric than permutation invariant aggregation.
+A contrario, formulations with exploit the tengant space of manifolds define a local coordinate system.
+While this formulation of convolution can learn anisotropic filters, it is not equivariant to translation.
+\todo{better wording}
+\todo{three main interpretations: gsp, Bronstein manifold tangent plane, message passing, permutation invariant aggregation, spatial formulations}
+Bronstein is a spatial formulation where the registration is done by projection on the tangent plane.
+% Not Bronstein's manifold approach as we want a Fourier basis to compare to the spherical harmonics.
+% Be as close as possible to spherical harmonics.
+Related to this, convolutional neural networks have been defined on manifolds and have achieved impressive results on shapes [Bronstein].
+They however too depend on an orientation, which spheres do not possess.
+
+% Anisotropic cannot be invariant
+
+The connection has recently been made between graph CNNs and group equivariant CNNs \cite{kondor2018equivariance}, justifying the use of graphs to gain rotation equivariance on the sphere.
+
+% In this work, we are using the graph CNN formulation introduced in~\cite{defferrard2016convolutional}.
+
+Spatial definitions of graph convolutions, e.g.
+[Niepert] needs to define an orientation in order to match the edges with the filters.
+Most often the orientation is not given by the application, and one has to define it (for example by ordering by degree or any other measure, or by using a graph coloring).
+There is no good default good orientation on general graphs and the choice of an orientation is highly application dependent.
+
 \section{Experiments}

### 2018-08-03 scnn.tex
some strange symbol
add architecture

--- 2018-08-03 scnn.tex
@@
     \item (NP) Finalise readme on Github code
-    \item (Waiting for Zenodo) (NP) Finalize the data on zenodo
     \item TK check part sphere notebook and whole sphere
@@
 % the convolution is not restricted to the sphere, the coarsening/pooling is
+
+\section{Method}
+\label{sec:method}
+% \begin{itemize}
+% 	\item We build a graph using the healpix sampling
+% 	\item Define Fourier transform and show that the harmonics are visually close to the spherical harmonics
+% 	\item Define spherical convolution using the graph Fourier transform and show heat diffusion example
+% 	\item Show the limits of the approach and explain why we cannot have a perfect spherical convolution with this technique
+% \end{itemize}
+
+A CNN is composed of the following main building blocks~\citep{lecun1998cnn}:
+(i) a convolution,
+(ii) a non-linearity,
+(iii) a down-sampling operation,
+(iv) a pooling operation, and
+(v), optionally,  normalization.\footnote{\citet{ioffe2015batchnorm} have shown that batch normalization helps training. We verified this experimentally in our setting as well.}
+Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}.
+As operations (ii) and (v) are point-wise, they do not depend on the data domain.
+The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either.
+The convolution and down-sampling operations however need to be generalized from Euclidean domains to the sphere.
+
+On regular Euclidean domains, such as 1-dimensional time series or 2-dimensional images, a convolution can be efficiently implemented by sliding a localized convolution kernel (for example a patch of 5x5 pixels) in the signal domain.
+Likewise, down-sampling can be achieved by taking one pixel out of $n$.
+Because of the irregular sampling, there is no straightforward way to define a convolution on the sphere directly in the pixel domain; convolutions are most often performed using spherical harmonics.
+In our method we also use the spectral domain to define the convolution.
+The implementation, however, does not need a direct access to the spectrum, which is computationally more efficient (see \secref{efficient_convolution}).
+% We will therefore use the spectral domain to define the convolutions
+% \footnote{Note that we only use the spectrum to define the convolution.
+% The implementation however does not need a direct access to the spectrum, which is computationally much more efficient. See \secref{efficient_convolution}.}
+% \TK{moving footnote to the main text }
+The gist of our method is to define the convolution operation on a sphere using a graph, and the down-sampling operation using a hierarchical pixelisation of the sphere.
+
+\subsection{HEALPix sampling}
+\label{sec:healpix}
+
+\begin{figure*}
+\includegraphics[width=\linewidth]{figures/figure_example_maps.pdf}
+\caption{Exmaple maps on the sphere:
+(left) the CMB temperature (K) map from Planck \citep{planck2015overview}, with galactic plane masked,
+(middle) map of galaxy number counts (number of galaxies per arcmin$^2$) in SDSS DR14 \citep{abolfathi2017sdssDR14},
+and (right) simulated weak lensing convergence map (dimensionless) simulated with DES DR1 mask \citep{des2018dr1}.
+These maps were pixelised using \texttt{nside}=512.
+The CMB and weak lensing mass maps were smoothed with Gaussian kernels with FWHM=1 deg, and the galaxy count map with FWHM=0.5 deg.
+}
+\label{fig:example_maps}
+\end{figure*}
+
+% \begin{figure}
+%     \centering
+%     \begin{subfigure}[b]{0.45\linewidth}
+%         \centering
+%         \includegraphics[width=\linewidth]{exampleEarthTopo}
+%         \caption{}
+%         \label{fig:example_earth}
+%     \end{subfigure}
+%     \hfill
+%     \begin{subfigure}[b]{0.45\linewidth}
+%         \centering
+%         \includegraphics[width=\linewidth]{exampleCMB}
+%         \caption{}
+%         \label{fig:example_cmb}
+%     \end{subfigure}
+%     \caption[]{Example of (a) an Earth topography map composed of \textasciitilde 3 million pixels (\textasciitilde 7 arcmin resolution) and (b) a model of the Cosmic Microwave Background (CMB) radiation temperature anisotropy, composed of \textasciitilde 13 million pixels (\textasciitilde 3.4 arcmin resolution).\footnotemark}
+%     \label{fig:example_maps}
+% \end{figure}
+
+Before doing any numerical analysis on the sphere, one first has to choose a tessellation, i.e., an exhaustive partition of the sphere into finite area elements, where the data under study is quantized.
+The simplicity of the spherical form belies the intricacy of global analysis on the sphere.
+There is no known point set which achieves the analogue of uniform sampling in Euclidean space and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions.
+Any existing proposition of practical schemes for the discrete treatment of such functions on the sphere introduces some systematic error dependent on the global properties of the point set.
+While our method is applicable to any pixelisation of the sphere, two details depend on the chosen sampling: (i) the choice of neighbours in the construction of the graph, and (ii) the choice of parent nodes when coarsening the graph.
+As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology, our target application, we'll tailor the method to that particular sampling in the subsequent exposition.
+%We'll note in later sections where the method should be adapted for a different sampling.
+
+HEALPix is a particular case of a more general class of schemes which are based on a hierarchical subdivision of a base polyhedron.
+%Many discretized maps of the sphere are based on a hierarchical subdivision of a base polyhedron.
+Another example is the geodesic grids which are based on geodesic polyhedrons, i.e., polyhedrons made of triangular faces.
+A counter-example is the equirectangular projection, which is not constructed from a base polyhedron, although it can be subdivided.
+In the particular HEALPix case, the base is a rhombic dodecahedron, i.e., a polyhedron made from 12 congruent rhombic faces.\footnote{A rhombus is a quadrilateral whose four sides all have the same length.}
+See \figref{pooling} for an illustration of the base rhombic dodecahedron and its subdivisions.
+
+HEALPix is an acronym for Hierarchical Equal Area isoLatitude Pixelization of a sphere.
+This pixelisation produces a hierarchical subdivision of a spherical surface where each pixel covers the same surface area as every other pixel.
+A hierarchy is desired for data locality in computer memory.
+Equal area is advantageous because white noise generated by the signal receiver gets integrated exactly into white noise in the pixel space.
+Isolatitude is essential for the implementation of a fast spherical transform.
+HEALPix is the sole pixelisation scheme which satisfies those three properties.
+
+The lowest possible resolution is given by the base partitioning of the surface into $N_{pix} = 12$ equal sized pixels (right-most sphere in \figref{pooling}).
+As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2 \cdot 12 = 2^2 \cdot 12 = 48$ pixels (middle sphere in \figref{pooling}), the third is $N_{pix} = N_{side}^2 \cdot 12 = 4^2 \cdot 12 = 192$ pixels, etc., where $N_{side} = 1, 2, 4, 8, \ldots$ is the grid resolution parameter.
+High-resolutions HEALPix maps easily reach millions of pixels.
+\figref{example_maps} shows two examples of HEALPix maps: the Cosmic Microwave Background \citep{planck2015overview} and \TK{update}.
+
+\subsection{Graph construction}
+
+Our graph is constructed as an approximation of the continuous 2D manifold that is the surface of the sphere.
+Indeed, \citet{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity.
+That construction can accommodate any sampling, regular or not.
+
+From the HEALPix pixelization, we build a weighted undirected graph $\G = (\V, \E, \W)$, where $\V$ is the set of $N_{pix} = |\V|$ nodes, $\E$ is the set of edges, and $\W$ is the weighted adjacency matrix.
+In our graph, each pixel $i$ is represented by a node (also called vertex) $v_i \in \V$.
+Each node $v_i$ is then connected to the $8$ (or $7$)\footnote{\label{neighbors}The $12 \cdot 4 = 48$ pixels at the corner of each rhombus of the base dodecahedron only have 7 neighboring pixels.
+See Figures~\ref{fig:healpix_graph_4} and~\ref{fig:pooling}.} nodes $v_j$ which represent the neighboring pixels $j$ of pixel $i$, forming edges $(v_i, v_j) \in \E$.
+Given those edges, we define the weighted adjacency matrix $\W \in \R^{N_{pix} \times N_{pix}}$ as
+\begin{equation*}
+	\W_{ij} = \begin{cases}
+		\exp \left( -\frac{\|\x_i-\x_j\|_2^2}{\rho^2} \right) & \text{if pixels $i$ and $j$ are neighbors,} \\
+		0 & \text{otherwise,} \\
+	\end{cases}
+\end{equation*}
+where $\x_i$ is a vector encoding the 3-dimensional coordinates of pixel $i$, and
+\begin{equation*}
+	\rho = \frac{1}{|\E|} \sum_{(v_i, v_j) \in \E} \|\x_i-\x_j\|_2
+\end{equation*}
+is the average Euclidean distance over all connected pixels. This weighting scheme is important as distances between pixels are not equal.
+Other weighting schemes are possible.
+For example,~\cite{khasanova2017graphomni} uses the inverse of the distance instead.
+We found out that the one proposed above works well for our purpose, and did not investigate other approaches, leaving it to future work.
+\figref{healpix_graph_4} shows a graph constructed from the HEALPix sampling of a sphere.
+
+% mdeff: Why not $1/d$? See Pascal's paper
+% nati: The question is: is $1/d$ also good when we have 7/8 neighbors instead of 4?
+Practically, we can also use $1/d$, but that means changing the code and re-runing the experiment.
+We probably do not have to change any parameter though...
+@mdeff: do you think we should try this for this paper?
+Or we keep that for the next one.
+% mdeff: I tried and the eigenvectors and eigenvalues are mostly the same.
+To me, there is no point in trying for trying.
+We should rather come up with a definition of distance that will make the eigenvectors closer to the real spherical harmonics.
+% Agreed: I added a reference to Pascal paper.
+
+\subsection{Graph Fourier basis}
+
+Following~\cite{shuman2013emerging}, the normalized graph Laplacian,
+defined as $\L = \I - \D^{-1/2} \W \D^{-1/2}$, is a second order differential operator
+that can be used to define a Fourier basis on the graph. Here $\D$ is the diagonal
+matrix where $\D_{ii} = \b{d}_i$ and $\b{d}_i = \sum_j \W_{ij}$ is the weighted degree of node $v_i$. By construction, the Laplacian is symmetric positive
+semi-definite and hence can be decomposed as $\L = \U \bLambda \U\trans$, where $\U = [\b u_1, \ldots, \b u_{N_{pix}}]$ is an
+orthonormal matrix of eigenvectors and $\bLambda$ is a diagonal matrix of
+eigenvalues. The graph Fourier basis is defined as the Laplacian eigenvectors, motivated by the fact that a Fourier basis should diagonalize the Laplacian operator.
+The graph Fourier transform of a signal $\f \in \R^{N_{pix}}$ is simply its projection on the eigenvectors given by
+$\hat{\f} = \mathcal{F}_\G \{\f\} = \U\trans \f$. It follows that the inverse graph Fourier transform reads $\mathcal{F}^{-1}_\G \{\hat{\f}\} = \U\hat{\f} = \U \U\trans \f = \f$.
+Note that the Fourier modes are ordered in the increasing order of the Laplacian eigenvalues $\bLambda$, which can be interpreted as squared frequencies.
+Indeed,
+\begin{equation*}
+	\bLambda_{ii} = \b u_i\trans \L \b u_i = \sum_{(v_j, v_k) \in \E} \frac{\W_{jk}}{\sqrt{\b d_j \b d_k}} (\U_{ji} - \U_{ki})^2
+\end{equation*}
+is a measure of the variation of the eigenvector $\b u_i$ is on the graph defined by the Laplacian $\L$.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{eigenvectors}
+	\caption{The first 16 eigenvectors of the graph Laplacian, an equivalent of Fourier modes, of a graph constructed from the HEALPix sampling of the sphere.
+    Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$ and order $|m|=(0,1)$, eigenvectors 4--8 with degree $\ell=2$ and order $|m|=(0,1,2)$, and eigenvectors 9--15 with degree $\ell=3$ and order $|m|=(0,1,2,3)$.
+    Nevertheless, the graph eigenvectors are only approximating spherical harmonics.}
+	\label{fig:graph_harmonics}
+\end{figure}
+
+Figure \figref{graph_harmonics} shows the Fourier modes of a HEALPix graph, created using the graph construction described above.
+The graph Fourier modes resemble the spherical harmonics.
+That is a strong hint that the graph is able to capture the spherical properties of the HEALPix sampling.
+This topic is further discussed in \ref{sec:comparison_spherical_harmonics}.
+
+\subsection{Convolution on graphs}
+\label{sec:graph_convolution}
+
+As there is no notion of translation on a graph, we cannot convolve two graph signals in a strict sense.
+We can, however, convolve a signal with a kernel defined in the spectral domain.
+More precisely, we can filter a graph signal by a kernel.
+Given the convolution kernel
+$h: \R_+ \rightarrow \R$, a signal $\f \in \R^{N_{pix}}$ on the graph is filtered as
+\begin{equation} \label{eqn:graph_convolution}
+	h(\L) \f = \U h(\bLambda) \U\trans \f,
+\end{equation}
+where $h(\bLambda)$ is a diagonal matrix where $h(\bLambda)_{ii} = h(\bLambda_{ii})$, and $h(\bLambda) \hat{\f}$ is the spectral representation of $\f$ after filtering.
+
+Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph.
+It can however be localized on any vertex $v_i$ by the convolution with a Kronecker delta $\b \delta_i \in \R^{N_{pix}}$,\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} that is $h(\L) \b \delta_i$, a column of $h(\L)$.
+This localization can be useful to visualize kernels as explained in~\ref{sec:filter_visualization}.
+If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another.
+While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular.
+However, when considering only parts of the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).
+Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with all localizations of the kernel:
+\begin{equation} \label{eqn:graph_convolution_spatial}
+	(h(\L) \f)_i = \langle h(\L) \b \delta_i, \f \rangle.
+\end{equation}
+In \ref{sec:heat_diffusion}, we present an example application of graph-based convolution to a simple heat-diffusion problem in order to shed some light on what is the convolution on a graph.
+% \textbf{Example.}
+% Let us consider the heat diffusion problem
+% \begin{equation} \label{eqn:heat_equation}
+% 	\L \b{f}(t) = \tau \partial_t \b{f}(t),
+% \end{equation}
+% where $\b{f}: \R_+ \rightarrow \R^{N_{pix}}$. Given the initial condition
+% $\b{f}(0)$, the solution of~\eqnref{heat_equation} can be expressed as
+% \begin{equation*}
+% 	\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U\trans \g{f}(0) = K_t(\L) \b{f}(0),
+% \end{equation*}
+% which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(\lambda)=e^{-\tau t \lambda}$.
+Since the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$, which can be interpreted as squared frequencies, it can also be considered as a generalization of the Gaussian kernel on the sphere.
+\figref{gaussian_filters_comparizon} shows the effect of the convolution by diffusing a unit of heat for $\tau=1$ at various times $t$.
+By comparing the graph convolution with the spherical symmetric Gaussian smoothing, we observe that both techniques lead to similar results (see \figref{gaussian_filters_comparizon}).
+While the graph convolution remains different from the spherical convolution, this small experiment shows that, providing the correct parameters, graph convolution can approximate spherical convolution.
+For additional insides about the graph kernel $K_t$, we refer to the \figref{gaussian_filters_visualization} and~\ref{sec:filter_visualization}.
+
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=\linewidth]{gaussian_filters_sphere}
+% 	\caption{Comparison of convolution with the graph and the spherical harmonics ($N_{side} = 16$).
+% 	Top: Diffusion of a unit of heat for different times $t$ using the graph.
+% 	Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin).
+% 	Relative difference between graph convolution and spherical smoothing: $10.4$\%, $4.8$\%, $3.8$\%.
+% \todo{The main issue with our filters is that their shape depends on the localization.
+It would be nice to measure the expectation and variance of the error over all locations.
+That would show how severe the distortion is.}
+% \nati{Let us keep that for the next paper. I am quite sure, it is negligible in this particular case.}}
+% 	\label{fig:gaussian_filters_comparizon}
+% \end{figure}
+
+% Furthermore, this result is another sign that the constructed graph is able to capture the spherical
+% structure of the HEALPix sampling. In some applications, where the
+% exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
+% The fact that both convolutions are not identical is not relevant in a neural network setting, as the convolution kernels are learned anyway.
+% not ideal tho as the graph convolution depends on the localization
+
+\subsection{Efficient convolutions}
+\label{sec:efficient_convolution}
+
+While \eqnref{graph_convolution} is a theoretically well justified definition of the convolution of a graph signal $\f$ by a kernel $h$, it is computationally cumbersome.
+As no general Fast Fourier Transform (FFT) exist for graphs, the execution of the Fourier transform by multiplication of the signal $\f$ by the dense matrix $\U$ costs $\bO(N_{pix}^2)$ operations.
+% \footnote{See \citep{le2018fgft} for a comparison between the polynomial definition of filters presented here and a class of fast graph Fourier transforms based on the approximation of the Fourier basis $\U$ by a product of sparse matrices.}
+%\TK{I would just cite the paper, we have not introduced the polynomials at this stage yet.}
+In a CNN, this operation has to be performed for each training step: forward and backward.
+% As current training procedures are not data-efficient and require a lot of samples, a quadratic computational cost in the sample size is a .
+%\TK{what does "data-efficient mean"? removing for now}
+As current training procedures require processing of many samples, it would be very slow to perform them for a quadratic computational cost in the sample size.
+Moreover, the eigen-decomposition of the Laplacian $\L$ is needed to obtain the Fourier basis $\U$ in the first place.
+That has a unique cost of $\bO(N_{pix}^3)$ operations.
+
+Fortunately, both of these computational issues can be overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parametrised by $K+1$ coefficients $\theta$.
+In that specific case, the filtering operation \eqnref{graph_convolution} becomes
+\begin{equation} \label{eqn:graph_convolution_polynomial}
+	h_\theta(\L) \f =  \U \left(\sum_{k=0}^K \theta_k \bLambda^k \right) \U\trans \f = \sum_{k=0}^K \theta_k \L^k \f,
+\end{equation}
+an operation requiring $k$ multiplications of the graph Laplacian matrix $\L$.
+In our case, the Laplacian is extremly sparse, with $8-9$ entries per line, making the filtering operation for a fixed $K$ linear in the number of pixel $N_{pix}$.
+% Moreover, here happens the transition from filtering in the spectral domain to filtering in the vertex domain.
+This operation is performed in the vertex domain.
+The matrix $\L^k$ captures $k$-neighborhoods of each pixel, i.e., $(\L^k)_{ij}$ is non-zero if and only if nodes $v_i$ and $v_j$ are connected by a path of length $k$.
+As such, filtering with a polynomial convolution kernel can be interpreted in the pixel (vertex) domain as a weighted linear combination of the pixels neighbors values.
+The weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$.
+We note that restricting the graph convolutional kernel to a polynomial is similar to restricting the classical Euclidean signal-domain convolution to a patch.
+In the classical setting, the convolution with a patch is simply a weighted sum of the neighbors with the weights defined by the patch.
+Similarly, each lines of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an "irregular patch of radius $K$" for our irregular domain.
+\todo{Better vertex domain explanation. \nati{I gave it a try. Should we take a single vertex and explain what heppens to it? Note that I suppressed the following paragraph. }}
+\TK{For me it's understandable:)}
+
+% To make the parallel with classical Euclidean signal-domain convolution, i.e., filtering by multiplying the signal with translated versions of a patch, we here match our filter at the level of neighborhoods\footnote{The 1-neighborhood of a node is the set of nodes which are directly connected to it.
+The 2-neighborhood is the set of nodes which are connected through paths of length 2.} rather than individual nodes.
+That is required as there is no notion of ordering in a general graph.
+For example, in a classical convolution on the grid, the relative ordering of vertices is up, down, left, and right.
+There is no such ordering on the sphere either, especially if irregularly sampled.
+
+Following \citet{defferrard2016convolutional}, we define our filters as Chebyshev polynomials such as the convolution operation becomes
+\begin{equation} \label{eqn:graph_convolution_cheby}
+	h_\theta\left(\tL\right) \f = \U \left(\sum_{k=0}^K \theta_k T_k\left(\tilde{\bLambda}\right) \right) \U\trans \f = \sum_{k=0}^K \theta_k T_k\left(\tL\right) \f,
+\end{equation}
+where $\tL = \frac{2}{\lambda_{max}} \L - \b{I} = -\frac{2}{\lambda_{max}} \D^{-1/2} \W \D^{-1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\b \Lambda}$ in $[-1, 1]$ and $T_k(\cdot)$ is the Chebyshev polynomial of degree $k$, defined by the recursive relation $T_k(\tL) = 2\tL T_{k-1}(\tL) - T_{k-2}(\tL)$, $T_1(\tL) = \tL$, $T_0(\tL) = \b{I}$.
+While definitions \eqnref{graph_convolution_polynomial} and \eqnref{graph_convolution_cheby} both allow the representation of the same set of filters, Chebyshev polynomials are preferred as they form an orthogonal basis on the interval $[-1, 1]$.
+Moreover, they factor out $\tL^{k-2}$ from $T_k(\tL)$, e.g., the 3-neighborhood is not mixed with the 5-neighborhood.
+That results in easier learning when optimizing the parameters $\theta$.
+Finally, the coefficients can be computed such as the truncated Chebyshev expansions gives an approximate minimax polynomial of a given filter \citep{hammond2011wavelets}.
+While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
+In practice, we found out in our experiment that Chebyshev polynomials are slightly more stable than the monomials used in~\cite{khasanova2017graphomni}(i.e.
+optimizing directly the $\theta_k$ in \eqnref{graph_convolution_polynomial}).
+We believe that this is due to their orthogonality (as explained above) and uniformity\footnote{The amplitude of Chebyshev polynomials is more or less constant over the domain $[-1, 1]$ independently of the order $k$.
+On the contrary the amplitude of $x^k$ is very different for $|x|\approx 0$ and $|x| \approx 1$.}.
+\nati{I added a sentence and I think we should not give much more details here. If we do an experiment, we can comment in the experiment section.}
+\todo{(i) scale of $\theta_k$: they are mostly uniform for Chebyshev polynomials, end exploding for monomials. Though SGD implicitly imposes a uniform prior on the learned parameters.}
+\todo{(ii) numerical stability of $\L^k \f$ v.s. $T_k(\L) \f$}
+\todo{(iii) in the code, initialize $\theta_k$ with stdev adapted to $F_{in}$ and $K$}
+
+Exploiting the recursive formulation of Chebyshev polynomials, evaluating \eqnref{graph_convolution_cheby} requires $\bO(K)$ multiplications of the dense vector $\f$ with the sparse matrix $\tL$.
+The cost of one such multiplication is $\bO(|\E|)$. By construction of our graph, $|\E| < 8 N_{pix}$ and the overall computational cost of the convolution is thus reduced to $\bO(N_{pix})$ operations.
+That is much more efficient than filtering with spherical harmonics, even tho the HEALPix was designed as an iso-latitude sampling to leverage a fast spherical transform.
+That is especially true for smooth kernels which require a low polynomial degree $K$.
+\figref{filtering_speed} demonstrates the speed comparison of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
+The performance of our approach is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{filtering_speed}
+	\caption{Comparison of filtering speed for Gaussian smoothing of maps of various sizes.
+    The fast spherical harmonic transform (SHT) is implemented by the \texttt{healpy} Python package (via the \texttt{healpy.sphtfunc.smoothing} function with $\ell_{max} = 3 N_{side} - 1$, the default).
+    The graph filtering is defined by \eqnref{graph_convolution_cheby} and implemented with the \texttt{numpy} and \texttt{scipy} Python packages.
+    Both are executed on a single core.
+    The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3)$ for the spherical harmonics, where $\ell_{max}$ is the largest degree (i.e., the spectrum is truncated at $\ell_{max}$).}
+	\label{fig:filtering_speed}
+\end{figure}
+
+\subsection{Coarsening and Pooling}
+
+Coarsening can be naturally designed for hierarchical pixelisation schemes, as each subdivision divides a cell in an equal number of child sub-cells.
+Coarsening is the reverse operation: merging the sub-cells toward the goal of summarizing the data supported on them.
+Merging cells lead to a coarser graph.
+Coarsening defines $\C(i)$, the set of children of node $v_i$.
+For the HEALPix subdivision scheme, the number of children is constant, i.e., $| \C(i) | = 4^p \ \forall i$, for some $p$.
+
+Pooling refers to the operation that summarizes the data supported on the merged sub-cells in one parent cell.
+Given a map $\x \in \R^{N_{pix}}$, pooling defines $\y \in \R^{N'_{pix}}$ such as
+\begin{equation} \label{eqn:pooling}
+	y_i = f \left( \left\{ x_j : j \in \C(i) \right\} \right), \ \forall i \in [N'_{pix}],
+\end{equation}
+where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix} / {N'_{pix}}$ is the down-sampling factor, which for HEALPix is $| \C(i) | = N_{pix} / {N_{pix}}' = (N_{side} / N'_{side})^2 = 4^p$.
+That operation is often taken to be the maximum value, but it can be any permutation invariant operation, such as a sum or an average.
+\figref{pooling} illustrates the process.
+
+% The advantage of schemes based on a base polyhedron is that cells are equal-area.
+While that is not required for the convolution operation when modeling with graphs (it can be corrected by setting edge weights appropriately, see \citet{khasanova2017graphomni})
+% nope: can also do a regular pooling on the equirectangular. It preserves the sampling, and the convolution is adapted to the sampling thanks to the edge weights.
+
+\begin{figure}
+	\centering
+    % \includegraphics[width=\linewidth]{pooling}
+	\includegraphics[trim=1.1cm 0cm 0cm 0cm, width=\linewidth]{figures/figure_pooling_svg.pdf}
+	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarsest cell covers $1/12$ of the sphere.}
+	\label{fig:pooling}
+\end{figure}
+
+\subsection{Statistical layer}
+\label{sec:stat_layer}
+% Or Global pooling?
+
+Following \citet{khasanova2017tigranet}, we implement an optional statistical layer between the last graph convolutional layer and the first fully connected layer for the neural network.
+This introduces the invariance of the output to isometric transformations, such as rotation and translation of maps on the sphere.
+The role of the layer is to compute global and location independent statistics from feature maps.
+Besides providing invariance, the layer drastically compresses the representation of the data as the number of computed statistics $N_{stat}$ is usually much smaller than the size of the map $N_{pix}$.
+That compression results in much smaller fully connected layers, which usually contain a significant fraction of trainable parameters of a neural network.
+The invariance and reduced representation should help the network to learn from less samples and to generalize better to unseen data.
+Yet another advantage is that a network built with such a statistical layer is agnostic to the size of the input data, i.e., it can classify maps which do not have the same number of pixels.
+Indeed, such global summarization is invariant to node permutation and is commonly used along graph convolutions to classify graphs of varying sizes \citep{duvenaud2015gcn, li2015gatedgnn}.
+
+Given a feature map $\x \in \R^{N_{pix}}$, the statistical layer is defined as
+\begin{equation} \label{eqn:stat_layer}
+	\y = f(\x) \in \R^{N_{stat}},
+\end{equation}
+where $f$ computes $N_{stat}$ statistics which are independent from the size of the map, $N_{pix}$.
+An example is the global average pooling $f(\x) = \esp(\x)$, introduced by \citet{lin2013globalavgpooling}, where $\esp(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} x_i$ is the empirical mean.
+Another example is $f(\x) = [\esp(\x), \var(\x)]\trans$, where $\var(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} (x_i - \esp(\x))^2$ is the empirical variance.
+Other statistical layers are also possible.
+In particular, we also implement a \emph{learned histogram} statistic \citep{wang2016learnhist}.
+Other approaches, which we did not implement, may include applying different diffusion on the final maps to obtain statistics at different scales, as proposed by \citep{khasanova2017tigranet}.
+
+\subsection{Graph convolutional neural network}
+\label{sec:architecture}
+
+Neural networks are constructed as stacks of layers which sequentially transform the data from its raw representation to a decision on the class label.
+Our architecture, pictured in \figref{architecture}, is composed of many layers.
+The convolutional part, the head of the neural network, is composed of graph convolutional layers (GC), pooling layers (P), and batch normalization layers (BN).
+The tail is composed of multiple fully connected layers (FC) followed by a softmax layer (SM).
+A statistical layer (ST) is optionally inserted between the convolutional head and the fully connected tail.
+
+% As such, we will not mention the non-linearity in the description of our architectures.
+A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer where it is set to the identity.
+That operation is point-wise, i.e., $y_{ij} = \sigma(x_{ij})$ and $y_i = \sigma(x_i)$ for matrices $\X, \Y$ and vectors $\x, \y$.
+The rectified linear unit (ReLU) $\sigma(\cdot) = \max(\cdot, 0)$ is a common choice.
+
+Given a matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$, a GC layer computes $\Y = GC(\X) = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels (and nodes), $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
+Using the efficient graph convolution from \eqnref{graph_convolution_cheby}, each output feature map is computed as
+\begin{equation*}
+	\y_i = \sum_{j=1}^{F_{in}} h_{\theta_{ij}}(\tL) \x_j + b_i \in \R^{N_{pix}}, \ \ \forall i \in [F_{out}].
+\end{equation*}
+As such, a GC layer is composed of $F_{in} \cdot F_{out}$ filters, each parameterized by $K$ numbers (see \secref{efficient_convolution}). A bias term $\b b \in \R^{F_{out}}$ is jointly optimized.
+% only if batch normalization is not used
+
+Given a matrix $\X \in \R^{N_{pix} \times F}$, a pooling layer computes $\Y = P(\X) \in \R^{N'_{pix} \times F}$ by reducing its spatial resolution ($N'_{pix} < N_{pix}$) according to \eqnref{pooling}.
+% Given a matrix $\X \in \R^{N_{pix} \times F}$,
+The batch normalization layer \citep{ioffe2015batchnorm} computes $\Y = BN(\X)$ such as
+\begin{equation*}
+	\y_i = \gamma_i \frac{\x_i - \esp(\x_i)}{\sqrt{\var(\x_i) + \epsilon}} + \beta_i, \ \forall i \in [F],
+\end{equation*}
+where $\gamma_{j}$ and $\beta_{j}$ are parameters to be learned and $\epsilon$ is a constant added for numerical stability.
+The empirical expectation $\esp(\x_i) \in \R$ and variance $\var(\x_i) \in \R$ are taken across training examples and pixels.
+% the action of gamma can be done by the filters of the next layer
+
+The statistical layer, defined in \eqnref{stat_layer}, independently transforms each of the $F$ feature maps of the input $\X \in \R^{N_{pix} \times F}$ into $\Y = ST(\X) \in \R^{N_{stat} \times F}$, where $N_{stat}$ is the number of statistics.
+One may even omit the FC layers and directly fed the output of the ST layer into the softmax layer, as proposed by \citet{lin2013globalavgpooling}.
+In this regime, $N_{stat} = 1$ and $F = N_{classes}$ is the number of classes to discriminate (i.e., the last GC layer outputs as many feature maps as there is classes).
+
+A FC layer takes as input $\x \in \R^{F_{in}}$ and outputs
+\begin{equation*}
+	\y = FC(\x) = \b W \x + \b b \in \R^{F_{out}} ,
+\end{equation*}
+where $\W \in \R^{F_{out} \times F_{in}}$ and $\b b \in \R^{F_{out}}$ are the parameters to be learned.
+Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last GC (or the output $\Y \in \R^{N_{stat} \times F_{out}}$ of the ST), is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first FC, where $F_{in} = N_{pix} \cdot F_{out}$ (or $N_{stat} \cdot F_{out}$).
+
+The softmax layer is the last layer in a neural network engineered for classification.
+Given the output $\x \in \R^{N_{classes}}$ of the last FC (or ST), called the logits in the deep learning literature, the softmax layer outputs $\y = SM(\x)$ such that
+\begin{equation*}
+	y_i = \frac{\exp(x_i)}{\sum_{j=1}^{N_{classes}} \exp(x_j)} \in [0, 1], \ \forall i \in [N_{classes}],
+\end{equation*}
+where $N_{classes}$ is the number of classes to discriminate.
+Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the probability that the input sample belongs to class $i$.
+This last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.
+
+Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
+An example network is
+\begin{equation*}
+NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC,
+\end{equation*}
+where $\circ$ denotes composition, i.e., $f \circ g = f(g(\cdot))$.
+The number of features $F$ depends on the data at hand.
+For the CMB radiation temperature, $F = 1$.
+For observations in radio frequencies, $F$ would be equal to the number of surveyed frequencies.
+$F$ might also be the number of slices in the radial direction.
+The loss function $\ell(\y) = \ell(NN_\theta(\X))$ is a measure of how good the prediction $\y$ is for the sample $\X$. For a classification task, the loss is usually taken to be the cross-entropy
+\begin{equation*}
+	\ell(\y) = -\log(y_i),
+\end{equation*}
+where $i$ is the correct class label.
+The parameters $\theta$ of the neural network are optimized to minimize the loss over the training dataset $\left\{ \X_i \right\}_{i=1}^{N_{samples}}$:
+\begin{equation*}
+	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell(NN_\theta(\X_i)).
+\end{equation*}
+The same architecture with different loss function can also be used for parameter regression \citep{fluri2018deep,gupta2018nongaussianinformation}.
+The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
+\begin{equation*}
+	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
+\end{equation*}
+where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch.
+Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.
+
+\todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
 
@@
 
-\section{Method}
-\label{sec:method}
-% \begin{itemize}
-% 	\item We build a graph using the healpix sampling
-% 	\item Define Fourier transform and show that the harmonics are visually close to the spherical harmonics
-% 	\item Define spherical convolution using the graph Fourier transform and show heat diffusion example
-% 	\item Show the limits of the approach and explain why we cannot have a perfect spherical convolution with this technique
-% \end{itemize}
-
-A CNN is composed of the following main building blocks~\citep{lecun1998cnn}:
-(i) a convolution,
-(ii) a non-linearity,
-(iii) a down-sampling operation,
-(iv) a pooling operation, and
-(v), optionally,  normalization.\footnote{\citet{ioffe2015batchnorm} have shown that batch normalization helps training. We verified this experimentally in our setting as well.}
-Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}.
-As operations (ii) and (v) are point-wise, they do not depend on the data domain.
-The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either.
-The convolution and down-sampling operations however need to be generalized from Euclidean domains to the sphere.
-
-On regular Euclidean domains, such as 1-dimensional time series or 2-dimensional images, a convolution can be efficiently implemented by sliding a localized convolution kernel (for example a patch of 5x5 pixels) in the signal domain.
-Likewise, down-sampling can be achieved by taking one pixel out of $n$.
-Because of the irregular sampling, there is no straightforward way to define a convolution on the sphere directly in the pixel domain; convolutions are most often performed using spherical harmonics.
-In our method we also use the spectral domain to define the convolution.
-The implementation, however, does not need a direct access to the spectrum, which is computationally more efficient (see \secref{efficient_convolution}).
-% We will therefore use the spectral domain to define the convolutions
-% \footnote{Note that we only use the spectrum to define the convolution.
-% The implementation however does not need a direct access to the spectrum, which is computationally much more efficient. See \secref{efficient_convolution}.}
-% \TK{moving footnote to the main text }
-The gist of our method is to define the convolution operation on a sphere using a graph, and the down-sampling operation using a hierarchical pixelisation of the sphere.
-
-\subsection{HEALPix sampling}
-\label{sec:healpix}
-
-\begin{figure*}
-\includegraphics[width=\linewidth]{figures/figure_example_maps.pdf}
-\caption{Exmaple maps on the sphere:
-(left) the CMB temperature (K) map from Planck \citep{planck2015overview}, with galactic plane masked,
-(middle) map of galaxy number counts (number of galaxies per arcmin$^2$) in SDSS DR14 \citep{abolfathi2017sdssDR14},
-and (right) simulated weak lensing convergence map (dimensionless) simulated with DES DR1 mask \citep{des2018dr1}.
-These maps were pixelised using \texttt{nside}=512.
-The CMB and weak lensing mass maps were smoothed with Gaussian kernels with FWHM=1 deg, and the galaxy count map with FWHM=0.5 deg.
-}
-\label{fig:example_maps}
-\end{figure*}
-
-% \begin{figure}
-%     \centering
-%     \begin{subfigure}[b]{0.45\linewidth}
-%         \centering
-%         \includegraphics[width=\linewidth]{exampleEarthTopo}
-%         \caption{}
-%         \label{fig:example_earth}
-%     \end{subfigure}
-%     \hfill
-%     \begin{subfigure}[b]{0.45\linewidth}
-%         \centering
-%         \includegraphics[width=\linewidth]{exampleCMB}
-%         \caption{}
-%         \label{fig:example_cmb}
-%     \end{subfigure}
-%     \caption[]{Example of (a) an Earth topography map composed of \textasciitilde 3 million pixels (\textasciitilde 7 arcmin resolution) and (b) a model of the Cosmic Microwave Background (CMB) radiation temperature anisotropy, composed of \textasciitilde 13 million pixels (\textasciitilde 3.4 arcmin resolution).\footnotemark}
-%     \label{fig:example_maps}
-% \end{figure}
-
-Before doing any numerical analysis on the sphere, one first has to choose a tessellation, i.e., an exhaustive partition of the sphere into finite area elements, where the data under study is quantized.
-The simplicity of the spherical form belies the intricacy of global analysis on the sphere.
-There is no known point set which achieves the analogue of uniform sampling in Euclidean space and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions.
-Any existing proposition of practical schemes for the discrete treatment of such functions on the sphere introduces some systematic error dependent on the global properties of the point set.
-While our method is applicable to any pixelisation of the sphere, two details depend on the chosen sampling: (i) the choice of neighbours in the construction of the graph, and (ii) the choice of parent nodes when coarsening the graph.
-As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology, our target application, we'll tailor the method to that particular sampling in the subsequent exposition.
-%We'll note in later sections where the method should be adapted for a different sampling.
-
-HEALPix is a particular case of a more general class of schemes which are based on a hierarchical subdivision of a base polyhedron.
-%Many discretized maps of the sphere are based on a hierarchical subdivision of a base polyhedron.
-Another example is the geodesic grids which are based on geodesic polyhedrons, i.e., polyhedrons made of triangular faces.
-A counter-example is the equirectangular projection, which is not constructed from a base polyhedron, although it can be subdivided.
-In the particular HEALPix case, the base is a rhombic dodecahedron, i.e., a polyhedron made from 12 congruent rhombic faces.\footnote{A rhombus is a quadrilateral whose four sides all have the same length.}
-See \figref{pooling} for an illustration of the base rhombic dodecahedron and its subdivisions.
-
-HEALPix is an acronym for Hierarchical Equal Area isoLatitude Pixelization of a sphere.
-This pixelisation produces a hierarchical subdivision of a spherical surface where each pixel covers the same surface area as every other pixel.
-A hierarchy is desired for data locality in computer memory.
-Equal area is advantageous because white noise generated by the signal receiver gets integrated exactly into white noise in the pixel space.
-Isolatitude is essential for the implementation of a fast spherical transform.
-HEALPix is the sole pixelisation scheme which satisfies those three properties.
-
-The lowest possible resolution is given by the base partitioning of the surface into $N_{pix} = 12$ equal sized pixels (right-most sphere in \figref{pooling}).
-As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2 \cdot 12 = 2^2 \cdot 12 = 48$ pixels (middle sphere in \figref{pooling}), the third is $N_{pix} = N_{side}^2 \cdot 12 = 4^2 \cdot 12 = 192$ pixels, etc., where $N_{side} = 1, 2, 4, 8, \ldots$ is the grid resolution parameter.
-High-resolutions HEALPix maps easily reach millions of pixels.
-\figref{example_maps} shows two examples of HEALPix maps: the Cosmic Microwave Background \citep{planck2015overview} and \TK{update}.
-
-\footnotetext{Figures from \url{https://healpix.jpl.nasa.gov/}.}
-
-\subsection{Graph construction}
-
-Our graph is constructed as an approximation of the continuous 2D manifold that is the surface of the sphere.
-Indeed, \citet{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity.
-That construction can accommodate any sampling, regular or not.
-
-From the HEALPix pixelization, we build a weighted undirected graph $\G = (\V, \E, \W)$, where $\V$ is the set of $N_{pix} = |\V|$ nodes, $\E$ is the set of edges, and $\W$ is the weighted adjacency matrix.
-In our graph, each pixel $i$ is represented by a node (also called vertex) $v_i \in \V$.
-Each node $v_i$ is then connected to the $8$ (or $7$)\footnote{\label{neighbors}The $12 \cdot 4 = 48$ pixels at the corner of each rhombus of the base dodecahedron only have 7 neighboring pixels.
-See Figures~\ref{fig:healpix_graph_4} and~\ref{fig:pooling}.} nodes $v_j$ which represent the neighboring pixels $j$ of pixel $i$, forming edges $(v_i, v_j) \in \E$.
-Given those edges, we define the weighted adjacency matrix $\W \in \R^{N_{pix} \times N_{pix}}$ as
-\begin{equation*}
-	\W_{ij} = \begin{cases}
-		\exp \left( -\frac{\|\x_i-\x_j\|_2^2}{\sigma^2} \right) & \text{if pixels $i$ and $j$ are neighbors,} \\
-		0 & \text{otherwise,} \\
-	\end{cases}
-\end{equation*}
-where $\x_i$ is a vector encoding the 3-dimensional coordinates of pixel $i$, and
-\begin{equation*}
-	\sigma = \frac{1}{|\E|} \sum_{(v_i, v_j) \in \E} \|\x_i-\x_j\|_2
-\end{equation*}
-is the average Euclidean distance over all connected pixels. This weighting scheme is important as distances between pixels are not equal.
-Other weighting schemes are possible.
-For example,~\cite{khasanova2017graphomni} uses the inverse of the distance instead.
-We found out that the one proposed above works well for our purpose, and did not investigate other approaches, leaving it to future work.
-\figref{healpix_graph_4} shows a graph constructed from the HEALPix sampling of a sphere.
-
-% mdeff: Why not $1/d$? See Pascal's paper
-% nati: The question is: is $1/d$ also good when we have 7/8 neighbors instead of 4?
-Practically, we can also use $1/d$, but that means changing the code and re-runing the experiment.
-We probably do not have to change any parameter though...
-@mdeff: do you think we should try this for this paper?
-Or we keep that for the next one.
-% mdeff: I tried and the eigenvectors and eigenvalues are mostly the same.
-To me, there is no point in trying for trying.
-We should rather come up with a definition of distance that will make the eigenvectors closer to the real spherical harmonics.
-% Agreed: I added a reference to Pascal paper.
-
-\subsection{Graph Fourier basis}
-
-Following~\cite{shuman2013emerging}, the normalized graph Laplacian,
-defined as $\L = \I - \D^{-1/2} \W \D^{-1/2}$, is a second order differential operator
-that can be used to define a Fourier basis on the graph. Here $\D$ is the diagonal
-matrix where $\D_{ii} = \b{d}_i$ and $\b{d}_i = \sum_j \W_{ij}$ is the weighted degree of node $v_i$. By construction, the Laplacian is symmetric positive
-semi-definite and hence can be decomposed as $\L = \U \bLambda \U\trans$, where $\U = [\b u_1, \ldots, \b u_{N_{pix}}]$ is an
-orthonormal matrix of eigenvectors and $\bLambda$ is a diagonal matrix of
-eigenvalues. The graph Fourier basis is defined as the Laplacian eigenvectors, motivated by the fact that a Fourier basis should diagonalize the Laplacian operator.
-The graph Fourier transform of a signal $\f \in \R^{N_{pix}}$ is simply its projection on the eigenvectors given by
-$\hat{\f} = \mathcal{F}_\G \{\f\} = \U\trans \f$. It follows that the inverse graph Fourier transform reads $\mathcal{F}^{-1}_\G \{\hat{\f}\} = \U\hat{\f} = \U \U\trans \f = \f$.
-Note that the Fourier modes are ordered in the increasing order of the Laplacian eigenvalues $\bLambda$, which can be interpreted as squared frequencies.
-Indeed,
-\begin{equation*}
-	\bLambda_{ii} = \b u_i\trans \L \b u_i = \sum_{(v_j, v_k) \in \E} \frac{\W_{jk}}{\sqrt{\b d_j \b d_k}} (\U_{ji} - \U_{ki})^2
-\end{equation*}
-is a measure of the variation of the eigenvector $\b u_i$ is on the graph defined by the Laplacian $\L$.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{eigenvectors}
-	\caption{The first 16 eigenvectors of the graph Laplacian, an equivalent of Fourier modes, of a graph constructed from the HEALPix sampling of the sphere.
-    Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$ and order $|m|=(0,1)$, eigenvectors 4--8 with degree $\ell=2$ and order $|m|=(0,1,2)$, and eigenvectors 9--15 with degree $\ell=3$ and order $|m|=(0,1,2,3)$.
-    Nevertheless, the graph eigenvectors are only approximating spherical harmonics.}
-	\label{fig:graph_harmonics}
-\end{figure}
-
-Figure \figref{graph_harmonics} shows the Fourier modes of a HEALPix graph, created using the graph construction described above.
-The graph Fourier modes resemble the spherical harmonics.
-That is a strong hint that the graph is able to capture the spherical properties of the HEALPix sampling.
-This topic is further discussed in \ref{sec:comparison_spherical_harmonics}.
-
-\subsection{Convolution on graphs}
-\label{sec:graph_convolution}
-
-As there is no notion of translation on a graph, we cannot convolve two graph signals in a strict sense.
-We can, however, convolve a signal with a kernel defined in the spectral domain.
-More precisely, we can filter a graph signal by a kernel.
-Given the convolution kernel
-$h: \R_+ \rightarrow \R$, a signal $\f \in \R^{N_{pix}}$ on the graph is filtered as
-\begin{equation} \label{eqn:graph_convolution}
-	h(\L) \f = \U h(\bLambda) \U\trans \f,
-\end{equation}
-where $h(\bLambda)$ is a diagonal matrix where $h(\bLambda)_{ii} = h(\bLambda_{ii})$, and $h(\bLambda) \hat{\f}$ is the spectral representation of $\f$ after filtering.
-
-Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph.
-It can however be localized on any vertex $v_i$ by the convolution with a Kronecker delta $\b \delta_i \in \R^{N_{pix}}$,\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} that is $h(\L) \b \delta_i$, a column of $h(\L)$.
-This localization can be useful to visualize kernels as explained in~\ref{sec:filter_visualization}.
-If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another.
-While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular.
-However, when considering only parts of the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).
-Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with all localizations of the kernel:
-\begin{equation} \label{eqn:graph_convolution_spatial}
-	(h(\L) \f)_i = \langle h(\L) \b \delta_i, \f \rangle.
-\end{equation}
-In \ref{sec:heat_diffusion}, we present an example application of graph-based convolution to a simple heat-diffusion problem in order to shed some light on what is the convolution on a graph.
-% \textbf{Example.}
-% Let us consider the heat diffusion problem
-% \begin{equation} \label{eqn:heat_equation}
-% 	\L \b{f}(t) = \tau \partial_t \b{f}(t),
-% \end{equation}
-% where $\b{f}: \R_+ \rightarrow \R^{N_{pix}}$. Given the initial condition
-% $\b{f}(0)$, the solution of~\eqnref{heat_equation} can be expressed as
-% \begin{equation*}
-% 	\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U\trans \g{f}(0) = K_t(\L) \b{f}(0),
-% \end{equation*}
-% which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(\lambda)=e^{-\tau t \lambda}$.
-Since the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$, which can be interpreted as squared frequencies, it can also be considered as a generalization of the Gaussian kernel on the sphere.
-\figref{gaussian_filters_comparizon} shows the effect of the convolution by diffusing a unit of heat for $\tau=1$ at various times $t$.
-By comparing the graph convolution with the spherical symmetric Gaussian smoothing, we observe that both techniques lead to similar results (see \figref{gaussian_filters_comparizon}).
-While the graph convolution remains different from the spherical convolution, this small experiment shows that, providing the correct parameters, graph convolution can approximate spherical convolution.
-For additional insides about the graph kernel $K_t$, we refer to the \figref{gaussian_filters_visualization} and~\ref{sec:filter_visualization}.
-
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=\linewidth]{gaussian_filters_sphere}
-% 	\caption{Comparison of convolution with the graph and the spherical harmonics ($N_{side} = 16$).
-% 	Top: Diffusion of a unit of heat for different times $t$ using the graph.
-% 	Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin).
-% 	Relative difference between graph convolution and spherical smoothing: $10.4$\%, $4.8$\%, $3.8$\%.
-% \todo{The main issue with our filters is that their shape depends on the localization.
-It would be nice to measure the expectation and variance of the error over all locations.
-That would show how severe the distortion is.}
-% \nati{Let us keep that for the next paper. I am quite sure, it is negligible in this particular case.}}
-% 	\label{fig:gaussian_filters_comparizon}
-% \end{figure}
-
-% Furthermore, this result is another sign that the constructed graph is able to capture the spherical
-% structure of the HEALPix sampling. In some applications, where the
-% exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
-% The fact that both convolutions are not identical is not relevant in a neural network setting, as the convolution kernels are learned anyway.
-% not ideal tho as the graph convolution depends on the localization
-
-\subsection{Efficient convolutions}
-\label{sec:efficient_convolution}
-
-While \eqnref{graph_convolution} is a theoretically well justified definition of the convolution of a graph signal $\f$ by a kernel $h$, it is computationally cumbersome.
-As no general Fast Fourier Transform (FFT) exist for graphs, the execution of the Fourier transform by multiplication of the signal $\f$ by the dense matrix $\U$ costs $\bO(N_{pix}^2)$ operations.
-% \footnote{See \citep{le2018fgft} for a comparison between the polynomial definition of filters presented here and a class of fast graph Fourier transforms based on the approximation of the Fourier basis $\U$ by a product of sparse matrices.}
-%\TK{I would just cite the paper, we have not introduced the polynomials at this stage yet.}
-In a CNN, this operation has to be performed for each training step: forward and backward.
-% As current training procedures are not data-efficient and require a lot of samples, a quadratic computational cost in the sample size is a .
-%\TK{what does "data-efficient mean"? removing for now}
-As current training procedures require processing of many samples, it would be very slow to perform them for a quadratic computational cost in the sample size.
-Moreover, the eigen-decomposition of the Laplacian $\L$ is needed to obtain the Fourier basis $\U$ in the first place.
-That has a unique cost of $\bO(N_{pix}^3)$ operations.
-
-Fortunately, both of these computational issues can be overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parametrised by $K+1$ coefficients $\theta$.
-In that specific case, the filtering operation \eqnref{graph_convolution} becomes
-\begin{equation} \label{eqn:graph_convolution_polynomial}
-	h_\theta(\L) \f =  \U \left(\sum_{k=0}^K \theta_k \bLambda^k \right) \U\trans \f = \sum_{k=0}^K \theta_k \L^k \f,
-\end{equation}
-an operation requiring $k$ multiplications of the graph Laplacian matrix $\L$.
-In our case, the Laplacian is extremly sparse, with $8-9$ entries per line, making the filtering operation for a fixed $K$ linear in the number of pixel $N_{pix}$.
-% Moreover, here happens the transition from filtering in the spectral domain to filtering in the vertex domain.
-This operation is performed in the vertex domain.
-The matrix $\L^k$ captures $k$-neighborhoods of each pixel, i.e., $(\L^k)_{ij}$ is non-zero if and only if nodes $v_i$ and $v_j$ are connected by a path of length $k$.
-As such, filtering with a polynomial convolution kernel can be interpreted in the pixel (vertex) domain as a weighted linear combination of the pixels neighbors values.
-The weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$.
-We note that restricting the graph convolutional kernel to a polynomial is similar to restricting the classical Euclidean signal-domain convolution to a patch.
-In the classical setting, the convolution with a patch is simply a weighted sum of the neighbors with the weights defined by the patch.
-Similarly, each lines of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an "irregular patch of radius $K$" for our irregular domain.
-\todo{Better vertex domain explanation. \nati{I gave it a try. Should we take a single vertex and explain what heppens to it? Note that I suppressed the following paragraph. }}
-\TK{For me it's understandable:)}
-
-% To make the parallel with classical Euclidean signal-domain convolution, i.e., filtering by multiplying the signal with translated versions of a patch, we here match our filter at the level of neighborhoods\footnote{The 1-neighborhood of a node is the set of nodes which are directly connected to it.
-The 2-neighborhood is the set of nodes which are connected through paths of length 2.} rather than individual nodes.
-That is required as there is no notion of ordering in a general graph.
-For example, in a classical convolution on the grid, the relative ordering of vertices is up, down, left, and right.
-There is no such ordering on the sphere either, especially if irregularly sampled.
-
-Following \citet{defferrard2016convolutional}, we define our filters as Chebyshev polynomials such as the convolution operation becomes
-\begin{equation} \label{eqn:graph_convolution_cheby}
-	h_\theta\left(\tL\right) \f = \U \left(\sum_{k=0}^K \theta_k T_k\left(\tilde{\bLambda}\right) \right) \U\trans \f = \sum_{k=0}^K \theta_k T_k\left(\tL\right) \f,
-\end{equation}
-where $\tL = \frac{2}{\lambda_{max}} \L - \b{I} = -\frac{2}{\lambda_{max}} \D^{-1/2} \W \D^{-1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\b \Lambda}$ in $[-1, 1]$ and $T_k(\cdot)$ is the Chebyshev polynomial of degree $k$, defined by the recursive relation $T_k(\tL) = 2\tL T_{k-1}(\tL) - T_{k-2}(\tL)$, $T_1(\tL) = \tL$, $T_0(\tL) = \b{I}$.
-While definitions \eqnref{graph_convolution_polynomial} and \eqnref{graph_convolution_cheby} both allow the representation of the same set of filters, Chebyshev polynomials are preferred as they form an orthogonal basis on the interval $[-1, 1]$.
-Moreover, they factor out $\tL^{k-2}$ from $T_k(\tL)$, e.g., the 3-neighborhood is not mixed with the 5-neighborhood.
-That results in easier learning when optimizing the parameters $\theta$.
-Finally, the coefficients can be computed such as the truncated Chebyshev expansions gives an approximate minimax polynomial of a given filter \citep{hammond2011wavelets}.
-While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
-In practice, we found out in our experiment that Chebyshev polynomials are slightly more stable than the monomials used in~\cite{khasanova2017graphomni}(i.e.
-optimizing directly the $\theta_k$ in \eqnref{graph_convolution_polynomial}).
-We believe that this is due to their orthogonality (as explained above) and uniformity\footnote{The amplitude of Chebyshev polynomials is more or less constant over the domain $[-1, 1]$ independently of the order $k$.
-On the contrary the amplitude of $x^k$ is very different for $|x|\approx 0$ and $|x| \approx 1$.}.
-\nati{I added a sentence and I think we should not give much more details here. If we do an experiment, we can comment in the experiment section.}
-\todo{(i) scale of $\theta_k$: they are mostly uniform for Chebyshev polynomials, end exploding for monomials. Though SGD implicitly imposes a uniform prior on the learned parameters.}
-\todo{(ii) numerical stability of $\L^k \f$ v.s. $T_k(\L) \f$}
-\todo{(iii) in the code, initialize $\theta_k$ with stdev adapted to $F_{in}$ and $K$}
-
-Exploiting the recursive formulation of Chebyshev polynomials, evaluating \eqnref{graph_convolution_cheby} requires $\bO(K)$ multiplications of the dense vector $\f$ with the sparse matrix $\tL$.
-The cost of one such multiplication is $\bO(|\E|)$. By construction of our graph, $|\E| < 8 N_{pix}$ and the overall computational cost of the convolution is thus reduced to $\bO(N_{pix})$ operations.
-That is much more efficient than filtering with spherical harmonics, even tho the HEALPix was designed as an iso-latitude sampling to leverage a fast spherical transform.
-That is especially true for smooth kernels which require a low polynomial degree $K$.
-\figref{filtering_speed} demonstrates the speed comparison of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
-The performance of our approach is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{filtering_speed}
-	\caption{Comparison of filtering speed for Gaussian smoothing of maps of various sizes.
-    The fast spherical harmonic transform (SHT) is implemented by the \texttt{healpy} Python package (via the \texttt{healpy.sphtfunc.smoothing} function with $\ell_{max} = 3 N_{side} - 1$, the default).
-    The graph filtering is defined by \eqnref{graph_convolution_cheby} and implemented with the \texttt{numpy} and \texttt{scipy} Python packages.
-    Both are executed on a single core.
-    The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3)$ for the spherical harmonics, where $\ell_{max}$ is the largest degree (i.e., the spectrum is truncated at $\ell_{max}$).}
-	\label{fig:filtering_speed}
-\end{figure}
-
-\subsection{Coarsening and Pooling}
-
-Coarsening can be naturally designed for hierarchical pixelisation schemes, as each subdivision divides a cell in an equal number of child sub-cells.
-Coarsening is the reverse operation: merging the sub-cells toward the goal of summarizing the data supported on them.
-Merging cells lead to a coarser graph.
-Coarsening defines $\C(i)$, the set of children of node $v_i$.
-For the HEALPix subdivision scheme, the number of children is constant, i.e., $| \C(i) | = 4^p \ \forall i$, for some $p$.
-
-Pooling refers to the operation that summarizes the data supported on the merged sub-cells in one parent cell.
-Given a map $\x \in \R^{N_{pix}}$, pooling defines $\y \in \R^{N'_{pix}}$ such as
-\begin{equation} \label{eqn:pooling}
-	y_i = f \left( \left\{ x_j : j \in \C(i) \right\} \right), \ \forall i \in [N'_{pix}],
-\end{equation}
-where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix} / {N'_{pix}}$ is the down-sampling factor, which for HEALPix is $| \C(i) | = N_{pix} / {N_{pix}}' = (N_{side} / N'_{side})^2 = 4^p$.
-That operation is often taken to be the maximum value, but it can be any permutation invariant operation, such as a sum or an average.
-\figref{pooling} illustrates the process.
-
-% The advantage of schemes based on a base polyhedron is that cells are equal-area.
-While that is not required for the convolution operation when modeling with graphs (it can be corrected by setting edge weights appropriately, see \citet{khasanova2017graphomni})
-% nope: can also do a regular pooling on the equirectangular. It preserves the sampling, and the convolution is adapted to the sampling thanks to the edge weights.
-
-\begin{figure}
-	\centering
-    % \includegraphics[width=\linewidth]{pooling}
-	\includegraphics[trim=1.1cm 0cm 0cm 0cm, width=\linewidth]{figures/figure_pooling_svg.pdf}
-	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarsest cell covers $1/12$ of the sphere.}
-	\label{fig:pooling}
-\end{figure}
-
-\subsection{Statistical layer}
-\label{sec:stat_layer}
-% Or Global pooling?
-
-Following \citet{khasanova2017tigranet}, we implement an optional statistical layer between the last graph convolutional layer and the first fully connected layer for the neural network.
-This introduces the invariance of the output to isometric transformations, such as rotation and translation of maps on the sphere.
-The role of the layer is to compute global and location independent statistics from feature maps.
-Besides providing invariance, the layer drastically compresses the representation of the data as the number of computed statistics $N_{stat}$ is usually much smaller than the size of the map $N_{pix}$.
-That compression results in much smaller fully connected layers, which usually contain a significant fraction of trainable parameters of a neural network.
-The invariance and reduced representation should help the network to learn from less samples and to generalize better to unseen data.
-Yet another advantage is that a network built with such a statistical layer is agnostic to the size of the input data, i.e., it can classify maps which do not have the same number of pixels.
-Indeed, such global summarization is invariant to node permutation and is commonly used along graph convolutions to classify graphs of varying sizes \citep{duvenaud2015gcn, li2015gatedgnn}.
-
-Given a feature map $\x \in \R^{N_{pix}}$, the statistical layer is defined as
-\begin{equation} \label{eqn:stat_layer}
-	\y = f(\x) \in \R^{N_{stat}},
-\end{equation}
-where $f$ computes $N_{stat}$ statistics which are independent from the size of the map, $N_{pix}$.
-An example is the global average pooling $f(\x) = \esp(\x)$, introduced by \citet{lin2013globalavgpooling}, where $\esp(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} x_i$ is the empirical mean.
-Another example is $f(\x) = [\esp(\x), \var(\x)]\trans$, where $\var(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} (x_i - \esp(\x))^2$ is the empirical variance.
-Other statistical layers are also possible.
-In particular, we also implement a \emph{learned histogram} statistic \citep{wang2016learnhist}.
-Other approaches, which we did not implement, may include applying different diffusion on the final maps to obtain statistics at different scales, as proposed by \citep{khasanova2017tigranet}.
-
-\subsection{Graph convolutional neural network}
-\label{sec:architecture}
-
-Neural networks are constructed as stacks of layers which sequentially transform the data from its raw representation to a decision on the class label.
-Our architecture, pictured in \figref{architecture}, is composed of many layers.
-The convolutional part, the head of the neural network, is composed of graph convolutional layers (GC), pooling layers (P), and batch normalization layers (BN).
-The tail is composed of multiple fully connected layers (FC) followed by a softmax layer (SM).
-A statistical layer (ST) is optionally inserted between the convolutional head and the fully connected tail.
-
-% As such, we will not mention the non-linearity in the description of our architectures.
-A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer where it is set to the identity.
-That operation is point-wise, i.e., $y_{ij} = \sigma(x_{ij})$ and $y_i = \sigma(x_i)$ for matrices $\X, \Y$ and vectors $\x, \y$.
-The rectified linear unit (ReLU) $\sigma(\cdot) = \max(\cdot, 0)$ is a common choice.
-
-Given a matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$, a GC layer computes $\Y = GC(\X) = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels (and nodes), $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
-Using the efficient graph convolution from \eqnref{graph_convolution_cheby}, each output feature map is computed as
-\begin{equation*}
-	\y_i = \sum_{j=1}^{F_{in}} h_{\theta_{ij}}(\tL) \x_j + b_i \in \R^{N_{pix}}, \ \ \forall i \in [F_{out}].
-\end{equation*}
-As such, a GC layer is composed of $F_{in} \cdot F_{out}$ filters, each parameterized by $K$ numbers (see \secref{efficient_convolution}). A bias term $\b b \in \R^{F_{out}}$ is jointly optimized.
-% only if batch normalization is not used
-
-Given a matrix $\X \in \R^{N_{pix} \times F}$, a pooling layer computes $\Y = P(\X) \in \R^{N'_{pix} \times F}$ by reducing its spatial resolution ($N'_{pix} < N_{pix}$) according to \eqnref{pooling}.
-% Given a matrix $\X \in \R^{N_{pix} \times F}$,
-The batch normalization layer \citep{ioffe2015batchnorm} computes $\Y = BN(\X)$ such as
-\begin{equation*}
-	\y_i = \gamma_i \frac{\x_i - \esp(\x_i)}{\sqrt{\var(\x_i) + \epsilon}} + \beta_i, \ \forall i \in [F],
-\end{equation*}
-where $\gamma_{j}$ and $\beta_{j}$ are parameters to be learned and $\epsilon$ is a constant added for numerical stability.
-The empirical expectation $\esp(\x_i) \in \R$ and variance $\var(\x_i) \in \R$ are taken across training examples and pixels.
-% the action of gamma can be done by the filters of the next layer
-
-The statistical layer, defined in \eqnref{stat_layer}, independently transforms each of the $F$ feature maps of the input $\X \in \R^{N_{pix} \times F}$ into $\Y = ST(\X) \in \R^{N_{stat} \times F}$, where $N_{stat}$ is the number of statistics.
-One may even omit the FC layers and directly fed the output of the ST layer into the softmax layer, as proposed by \citet{lin2013globalavgpooling}.
-In this regime, $N_{stat} = 1$ and $F = N_{classes}$ is the number of classes to discriminate (i.e., the last GC layer outputs as many feature maps as there is classes).
-
-A FC layer takes as input $\x \in \R^{F_{in}}$ and outputs
-\begin{equation*}
-	\y = FC(\x) = \b W \x + \b b \in \R^{F_{out}} ,
-\end{equation*}
-where $\W \in \R^{F_{out} \times F_{in}}$ and $\b b \in \R^{F_{out}}$ are the parameters to be learned.
-Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last GC (or the output $\Y \in \R^{N_{stat} \times F_{out}}$ of the ST), is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first FC, where $F_{in} = N_{pix} \cdot F_{out}$ (or $N_{stat} \cdot F_{out}$).
-
-The softmax layer is the last layer in a neural network engineered for classification.
-Given the output $\x \in \R^{N_{classes}}$ of the last FC (or ST), called the logits in the deep learning literature, the softmax layer outputs $\y = SM(\x)$ such that
-\begin{equation*}
-	y_i = \frac{\exp(x_i)}{\sum_{j=1}^{N_{classes}} \exp(x_j)} \in [0, 1], \ \forall i \in [N_{classes}],
-\end{equation*}
-where $N_{classes}$ is the number of classes to discriminate.
-Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the probability that the input sample belongs to class $i$.
-This last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.
-
-Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
-An example network is
-\begin{equation*}
-NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC,
-\end{equation*}
-where $\circ$ denotes composition, i.e., $f \circ g = f(g(\cdot))$.
-The number of features $F$ depends on the data at hand.
-For the CMB radiation temperature, $F = 1$.
-For observations in radio frequencies, $F$ would be equal to the number of surveyed frequencies.
-$F$ might also be the number of slices in the radial direction.
-The loss function $\ell(\y) = \ell(NN_\theta(\X))$ is a measure of how good the prediction $\y$ is for the sample $\X$. For a classification task, the loss is usually taken to be the cross-entropy
-\begin{equation*}
-	\ell(\y) = -\log(y_i),
-\end{equation*}
-where $i$ is the correct class label.
-The parameters $\theta$ of the neural network are optimized to minimize the loss over the training dataset $\left\{ \X_i \right\}_{i=1}^{N_{samples}}$:
-\begin{equation*}
-	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell(NN_\theta(\X_i)).
-\end{equation*}
-The same architecture with different loss function can also be used for parameter regression \citep{fluri2018deep,gupta2018nongaussianinformation}.
-The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
-\begin{equation*}
-	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
-\end{equation*}
-where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch.
-Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.
-
-\nati{4.8 is long... Should we go in such details?}
-\todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
-
 \section{Experiments}
@@
 \subsection{Selected architecture}
-\todo{Describe our fully convolutional architecture}
+The design of an neural network architecture highly depends on the problem at hand.
+In our case, we are trying to discriminate samples of two distributions cosmologicals maps.
+Hence, we assume that each pixel carries some information about the distribution.
+Thanks to 6 graph convolution layers (GC sizes: 16, 32, 64, 64, 64, 2) we first build the stistical evidence of each distribution for each pixel of a downsampled sphere.
+The last graph convolution layer is compose of 2 channels as we have 2 distributions.
+Then we use a statistical 'mean' layer (SL) to average the evidence for each distribution and we compute the probabilities thanks to a softmax layer (SM).
+We use batch normalization (BN), pooling (P) and relu non-linearity $\sigma$ for each convolutional layer.
+The network can be summarized as
+\begin{equation}
+NN = SM \circ ST_{\text{mean}} \circ L_6 \circ L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1
+\end{equation}
+where
+\begin{itemize}
+    \item layer 1: $L_1 = P  \circ \sigma \circ BN  \circ GC_{16}$,
+    \item layer 2: $L_2 = P  \circ \sigma \circ BN  \circ GC_{32}$,
+    \item layer 3-5: $L_3 = L_4 = L_5= P \circ  \sigma \circ BN  \circ GC_{64}$,
+    \item layer 6: $L_6 = \sigma \circ BN  \circ GC_{2}$.
+\end{itemize}
+
+\todo{We use the ADAM optimizer, \cite{kingma2014adam}, with an initial learning rate of $2e-4$ that is exponentially decreased by $0.98$ a $100$ times to end at $2.7e-5$.}
 

### 2018-08-05 scnn.tex

@@
 % the convolution is not restricted to the sphere, the coarsening/pooling is
-
-\section{Method}
-\label{sec:method}
-% \begin{itemize}
-% 	\item We build a graph using the healpix sampling
-% 	\item Define Fourier transform and show that the harmonics are visually close to the spherical harmonics
-% 	\item Define spherical convolution using the graph Fourier transform and show heat diffusion example
-% 	\item Show the limits of the approach and explain why we cannot have a perfect spherical convolution with this technique
-% \end{itemize}
-
-A CNN is composed of the following main building blocks~\citep{lecun1998cnn}:
-(i) a convolution,
-(ii) a non-linearity,
-(iii) a down-sampling operation,
-(iv) a pooling operation, and
-(v), optionally,  normalization.\footnote{\citet{ioffe2015batchnorm} have shown that batch normalization helps training. We verified this experimentally in our setting as well.}
-Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}.
-As operations (ii) and (v) are point-wise, they do not depend on the data domain.
-The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either.
-The convolution and down-sampling operations however need to be generalized from Euclidean domains to the sphere.
-
-On regular Euclidean domains, such as 1-dimensional time series or 2-dimensional images, a convolution can be efficiently implemented by sliding a localized convolution kernel (for example a patch of 5x5 pixels) in the signal domain.
-Likewise, down-sampling can be achieved by taking one pixel out of $n$.
-Because of the irregular sampling, there is no straightforward way to define a convolution on the sphere directly in the pixel domain; convolutions are most often performed using spherical harmonics.
-In our method we also use the spectral domain to define the convolution.
-The implementation, however, does not need a direct access to the spectrum, which is computationally more efficient (see \secref{efficient_convolution}).
-% We will therefore use the spectral domain to define the convolutions
-% \footnote{Note that we only use the spectrum to define the convolution.
-% The implementation however does not need a direct access to the spectrum, which is computationally much more efficient. See \secref{efficient_convolution}.}
-% \TK{moving footnote to the main text }
-The gist of our method is to define the convolution operation on a sphere using a graph, and the down-sampling operation using a hierarchical pixelisation of the sphere.
-
-\subsection{HEALPix sampling}
-\label{sec:healpix}
-
-\begin{figure*}
-\includegraphics[width=\linewidth]{figures/figure_example_maps.pdf}
-\caption{Exmaple maps on the sphere:
-(left) the CMB temperature (K) map from Planck \citep{planck2015overview}, with galactic plane masked,
-(middle) map of galaxy number counts (number of galaxies per arcmin$^2$) in SDSS DR14 \citep{abolfathi2017sdssDR14},
-and (right) simulated weak lensing convergence map (dimensionless) simulated with DES DR1 mask \citep{des2018dr1}.
-These maps were pixelised using \texttt{nside}=512.
-The CMB and weak lensing mass maps were smoothed with Gaussian kernels with FWHM=1 deg, and the galaxy count map with FWHM=0.5 deg.
-}
-\label{fig:example_maps}
-\end{figure*}
-
-% \begin{figure}
-%     \centering
-%     \begin{subfigure}[b]{0.45\linewidth}
-%         \centering
-%         \includegraphics[width=\linewidth]{exampleEarthTopo}
-%         \caption{}
-%         \label{fig:example_earth}
-%     \end{subfigure}
-%     \hfill
-%     \begin{subfigure}[b]{0.45\linewidth}
-%         \centering
-%         \includegraphics[width=\linewidth]{exampleCMB}
-%         \caption{}
-%         \label{fig:example_cmb}
-%     \end{subfigure}
-%     \caption[]{Example of (a) an Earth topography map composed of \textasciitilde 3 million pixels (\textasciitilde 7 arcmin resolution) and (b) a model of the Cosmic Microwave Background (CMB) radiation temperature anisotropy, composed of \textasciitilde 13 million pixels (\textasciitilde 3.4 arcmin resolution).\footnotemark}
-%     \label{fig:example_maps}
-% \end{figure}
-
-Before doing any numerical analysis on the sphere, one first has to choose a tessellation, i.e., an exhaustive partition of the sphere into finite area elements, where the data under study is quantized.
-The simplicity of the spherical form belies the intricacy of global analysis on the sphere.
-There is no known point set which achieves the analogue of uniform sampling in Euclidean space and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions.
-Any existing proposition of practical schemes for the discrete treatment of such functions on the sphere introduces some systematic error dependent on the global properties of the point set.
-While our method is applicable to any pixelisation of the sphere, two details depend on the chosen sampling: (i) the choice of neighbours in the construction of the graph, and (ii) the choice of parent nodes when coarsening the graph.
-As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology, our target application, we'll tailor the method to that particular sampling in the subsequent exposition.
-%We'll note in later sections where the method should be adapted for a different sampling.
-
-HEALPix is a particular case of a more general class of schemes which are based on a hierarchical subdivision of a base polyhedron.
-%Many discretized maps of the sphere are based on a hierarchical subdivision of a base polyhedron.
-Another example is the geodesic grids which are based on geodesic polyhedrons, i.e., polyhedrons made of triangular faces.
-A counter-example is the equirectangular projection, which is not constructed from a base polyhedron, although it can be subdivided.
-In the particular HEALPix case, the base is a rhombic dodecahedron, i.e., a polyhedron made from 12 congruent rhombic faces.\footnote{A rhombus is a quadrilateral whose four sides all have the same length.}
-See \figref{pooling} for an illustration of the base rhombic dodecahedron and its subdivisions.
-
-HEALPix is an acronym for Hierarchical Equal Area isoLatitude Pixelization of a sphere.
-This pixelisation produces a hierarchical subdivision of a spherical surface where each pixel covers the same surface area as every other pixel.
-A hierarchy is desired for data locality in computer memory.
-Equal area is advantageous because white noise generated by the signal receiver gets integrated exactly into white noise in the pixel space.
-Isolatitude is essential for the implementation of a fast spherical transform.
-HEALPix is the sole pixelisation scheme which satisfies those three properties.
-
-The lowest possible resolution is given by the base partitioning of the surface into $N_{pix} = 12$ equal sized pixels (right-most sphere in \figref{pooling}).
-As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2 \cdot 12 = 2^2 \cdot 12 = 48$ pixels (middle sphere in \figref{pooling}), the third is $N_{pix} = N_{side}^2 \cdot 12 = 4^2 \cdot 12 = 192$ pixels, etc., where $N_{side} = 1, 2, 4, 8, \ldots$ is the grid resolution parameter.
-High-resolutions HEALPix maps easily reach millions of pixels.
-\figref{example_maps} shows two examples of HEALPix maps: the Cosmic Microwave Background \citep{planck2015overview} and \TK{update}.
-
-\subsection{Graph construction}
-
-Our graph is constructed as an approximation of the continuous 2D manifold that is the surface of the sphere.
-Indeed, \citet{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity.
-That construction can accommodate any sampling, regular or not.
-
-From the HEALPix pixelization, we build a weighted undirected graph $\G = (\V, \E, \W)$, where $\V$ is the set of $N_{pix} = |\V|$ nodes, $\E$ is the set of edges, and $\W$ is the weighted adjacency matrix.
-In our graph, each pixel $i$ is represented by a node (also called vertex) $v_i \in \V$.
-Each node $v_i$ is then connected to the $8$ (or $7$)\footnote{\label{neighbors}The $12 \cdot 4 = 48$ pixels at the corner of each rhombus of the base dodecahedron only have 7 neighboring pixels.
-See Figures~\ref{fig:healpix_graph_4} and~\ref{fig:pooling}.} nodes $v_j$ which represent the neighboring pixels $j$ of pixel $i$, forming edges $(v_i, v_j) \in \E$.
-Given those edges, we define the weighted adjacency matrix $\W \in \R^{N_{pix} \times N_{pix}}$ as
-\begin{equation*}
-	\W_{ij} = \begin{cases}
-		\exp \left( -\frac{\|\x_i-\x_j\|_2^2}{\rho^2} \right) & \text{if pixels $i$ and $j$ are neighbors,} \\
-		0 & \text{otherwise,} \\
-	\end{cases}
-\end{equation*}
-where $\x_i$ is a vector encoding the 3-dimensional coordinates of pixel $i$, and
-\begin{equation*}
-	\rho = \frac{1}{|\E|} \sum_{(v_i, v_j) \in \E} \|\x_i-\x_j\|_2
-\end{equation*}
-is the average Euclidean distance over all connected pixels. This weighting scheme is important as distances between pixels are not equal.
-Other weighting schemes are possible.
-For example,~\cite{khasanova2017graphomni} uses the inverse of the distance instead.
-We found out that the one proposed above works well for our purpose, and did not investigate other approaches, leaving it to future work.
-\figref{healpix_graph_4} shows a graph constructed from the HEALPix sampling of a sphere.
-
-% mdeff: Why not $1/d$? See Pascal's paper
-% nati: The question is: is $1/d$ also good when we have 7/8 neighbors instead of 4?
-Practically, we can also use $1/d$, but that means changing the code and re-runing the experiment.
-We probably do not have to change any parameter though...
-@mdeff: do you think we should try this for this paper?
-Or we keep that for the next one.
-% mdeff: I tried and the eigenvectors and eigenvalues are mostly the same.
-To me, there is no point in trying for trying.
-We should rather come up with a definition of distance that will make the eigenvectors closer to the real spherical harmonics.
-% Agreed: I added a reference to Pascal paper.
-
-\subsection{Graph Fourier basis}
-
-Following~\cite{shuman2013emerging}, the normalized graph Laplacian,
-defined as $\L = \I - \D^{-1/2} \W \D^{-1/2}$, is a second order differential operator
-that can be used to define a Fourier basis on the graph. Here $\D$ is the diagonal
-matrix where $\D_{ii} = \b{d}_i$ and $\b{d}_i = \sum_j \W_{ij}$ is the weighted degree of node $v_i$. By construction, the Laplacian is symmetric positive
-semi-definite and hence can be decomposed as $\L = \U \bLambda \U\trans$, where $\U = [\b u_1, \ldots, \b u_{N_{pix}}]$ is an
-orthonormal matrix of eigenvectors and $\bLambda$ is a diagonal matrix of
-eigenvalues. The graph Fourier basis is defined as the Laplacian eigenvectors, motivated by the fact that a Fourier basis should diagonalize the Laplacian operator.
-The graph Fourier transform of a signal $\f \in \R^{N_{pix}}$ is simply its projection on the eigenvectors given by
-$\hat{\f} = \mathcal{F}_\G \{\f\} = \U\trans \f$. It follows that the inverse graph Fourier transform reads $\mathcal{F}^{-1}_\G \{\hat{\f}\} = \U\hat{\f} = \U \U\trans \f = \f$.
-Note that the Fourier modes are ordered in the increasing order of the Laplacian eigenvalues $\bLambda$, which can be interpreted as squared frequencies.
-Indeed,
-\begin{equation*}
-	\bLambda_{ii} = \b u_i\trans \L \b u_i = \sum_{(v_j, v_k) \in \E} \frac{\W_{jk}}{\sqrt{\b d_j \b d_k}} (\U_{ji} - \U_{ki})^2
-\end{equation*}
-is a measure of the variation of the eigenvector $\b u_i$ is on the graph defined by the Laplacian $\L$.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{eigenvectors}
-	\caption{The first 16 eigenvectors of the graph Laplacian, an equivalent of Fourier modes, of a graph constructed from the HEALPix sampling of the sphere.
-    Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$ and order $|m|=(0,1)$, eigenvectors 4--8 with degree $\ell=2$ and order $|m|=(0,1,2)$, and eigenvectors 9--15 with degree $\ell=3$ and order $|m|=(0,1,2,3)$.
-    Nevertheless, the graph eigenvectors are only approximating spherical harmonics.}
-	\label{fig:graph_harmonics}
-\end{figure}
-
-Figure \figref{graph_harmonics} shows the Fourier modes of a HEALPix graph, created using the graph construction described above.
-The graph Fourier modes resemble the spherical harmonics.
-That is a strong hint that the graph is able to capture the spherical properties of the HEALPix sampling.
-This topic is further discussed in \ref{sec:comparison_spherical_harmonics}.
-
-\subsection{Convolution on graphs}
-\label{sec:graph_convolution}
-
-As there is no notion of translation on a graph, we cannot convolve two graph signals in a strict sense.
-We can, however, convolve a signal with a kernel defined in the spectral domain.
-More precisely, we can filter a graph signal by a kernel.
-Given the convolution kernel
-$h: \R_+ \rightarrow \R$, a signal $\f \in \R^{N_{pix}}$ on the graph is filtered as
-\begin{equation} \label{eqn:graph_convolution}
-	h(\L) \f = \U h(\bLambda) \U\trans \f,
-\end{equation}
-where $h(\bLambda)$ is a diagonal matrix where $h(\bLambda)_{ii} = h(\bLambda_{ii})$, and $h(\bLambda) \hat{\f}$ is the spectral representation of $\f$ after filtering.
-
-Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph.
-It can however be localized on any vertex $v_i$ by the convolution with a Kronecker delta $\b \delta_i \in \R^{N_{pix}}$,\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} that is $h(\L) \b \delta_i$, a column of $h(\L)$.
-This localization can be useful to visualize kernels as explained in~\ref{sec:filter_visualization}.
-If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another.
-While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular.
-However, when considering only parts of the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).
-Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with all localizations of the kernel:
-\begin{equation} \label{eqn:graph_convolution_spatial}
-	(h(\L) \f)_i = \langle h(\L) \b \delta_i, \f \rangle.
-\end{equation}
-In \ref{sec:heat_diffusion}, we present an example application of graph-based convolution to a simple heat-diffusion problem in order to shed some light on what is the convolution on a graph.
-% \textbf{Example.}
-% Let us consider the heat diffusion problem
-% \begin{equation} \label{eqn:heat_equation}
-% 	\L \b{f}(t) = \tau \partial_t \b{f}(t),
-% \end{equation}
-% where $\b{f}: \R_+ \rightarrow \R^{N_{pix}}$. Given the initial condition
-% $\b{f}(0)$, the solution of~\eqnref{heat_equation} can be expressed as
-% \begin{equation*}
-% 	\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U\trans \g{f}(0) = K_t(\L) \b{f}(0),
-% \end{equation*}
-% which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(\lambda)=e^{-\tau t \lambda}$.
-Since the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$, which can be interpreted as squared frequencies, it can also be considered as a generalization of the Gaussian kernel on the sphere.
-\figref{gaussian_filters_comparizon} shows the effect of the convolution by diffusing a unit of heat for $\tau=1$ at various times $t$.
-By comparing the graph convolution with the spherical symmetric Gaussian smoothing, we observe that both techniques lead to similar results (see \figref{gaussian_filters_comparizon}).
-While the graph convolution remains different from the spherical convolution, this small experiment shows that, providing the correct parameters, graph convolution can approximate spherical convolution.
-For additional insides about the graph kernel $K_t$, we refer to the \figref{gaussian_filters_visualization} and~\ref{sec:filter_visualization}.
-
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=\linewidth]{gaussian_filters_sphere}
-% 	\caption{Comparison of convolution with the graph and the spherical harmonics ($N_{side} = 16$).
-% 	Top: Diffusion of a unit of heat for different times $t$ using the graph.
-% 	Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin).
-% 	Relative difference between graph convolution and spherical smoothing: $10.4$\%, $4.8$\%, $3.8$\%.
-% \todo{The main issue with our filters is that their shape depends on the localization.
-It would be nice to measure the expectation and variance of the error over all locations.
-That would show how severe the distortion is.}
-% \nati{Let us keep that for the next paper. I am quite sure, it is negligible in this particular case.}}
-% 	\label{fig:gaussian_filters_comparizon}
-% \end{figure}
-
-% Furthermore, this result is another sign that the constructed graph is able to capture the spherical
-% structure of the HEALPix sampling. In some applications, where the
-% exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
-% The fact that both convolutions are not identical is not relevant in a neural network setting, as the convolution kernels are learned anyway.
-% not ideal tho as the graph convolution depends on the localization
-
-\subsection{Efficient convolutions}
-\label{sec:efficient_convolution}
-
-While \eqnref{graph_convolution} is a theoretically well justified definition of the convolution of a graph signal $\f$ by a kernel $h$, it is computationally cumbersome.
-As no general Fast Fourier Transform (FFT) exist for graphs, the execution of the Fourier transform by multiplication of the signal $\f$ by the dense matrix $\U$ costs $\bO(N_{pix}^2)$ operations.
-% \footnote{See \citep{le2018fgft} for a comparison between the polynomial definition of filters presented here and a class of fast graph Fourier transforms based on the approximation of the Fourier basis $\U$ by a product of sparse matrices.}
-%\TK{I would just cite the paper, we have not introduced the polynomials at this stage yet.}
-In a CNN, this operation has to be performed for each training step: forward and backward.
-% As current training procedures are not data-efficient and require a lot of samples, a quadratic computational cost in the sample size is a .
-%\TK{what does "data-efficient mean"? removing for now}
-As current training procedures require processing of many samples, it would be very slow to perform them for a quadratic computational cost in the sample size.
-Moreover, the eigen-decomposition of the Laplacian $\L$ is needed to obtain the Fourier basis $\U$ in the first place.
-That has a unique cost of $\bO(N_{pix}^3)$ operations.
-
-Fortunately, both of these computational issues can be overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parametrised by $K+1$ coefficients $\theta$.
-In that specific case, the filtering operation \eqnref{graph_convolution} becomes
-\begin{equation} \label{eqn:graph_convolution_polynomial}
-	h_\theta(\L) \f =  \U \left(\sum_{k=0}^K \theta_k \bLambda^k \right) \U\trans \f = \sum_{k=0}^K \theta_k \L^k \f,
-\end{equation}
-an operation requiring $k$ multiplications of the graph Laplacian matrix $\L$.
-In our case, the Laplacian is extremly sparse, with $8-9$ entries per line, making the filtering operation for a fixed $K$ linear in the number of pixel $N_{pix}$.
-% Moreover, here happens the transition from filtering in the spectral domain to filtering in the vertex domain.
-This operation is performed in the vertex domain.
-The matrix $\L^k$ captures $k$-neighborhoods of each pixel, i.e., $(\L^k)_{ij}$ is non-zero if and only if nodes $v_i$ and $v_j$ are connected by a path of length $k$.
-As such, filtering with a polynomial convolution kernel can be interpreted in the pixel (vertex) domain as a weighted linear combination of the pixels neighbors values.
-The weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$.
-We note that restricting the graph convolutional kernel to a polynomial is similar to restricting the classical Euclidean signal-domain convolution to a patch.
-In the classical setting, the convolution with a patch is simply a weighted sum of the neighbors with the weights defined by the patch.
-Similarly, each lines of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an "irregular patch of radius $K$" for our irregular domain.
-\todo{Better vertex domain explanation. \nati{I gave it a try. Should we take a single vertex and explain what heppens to it? Note that I suppressed the following paragraph. }}
-\TK{For me it's understandable:)}
-
-% To make the parallel with classical Euclidean signal-domain convolution, i.e., filtering by multiplying the signal with translated versions of a patch, we here match our filter at the level of neighborhoods\footnote{The 1-neighborhood of a node is the set of nodes which are directly connected to it.
-The 2-neighborhood is the set of nodes which are connected through paths of length 2.} rather than individual nodes.
-That is required as there is no notion of ordering in a general graph.
-For example, in a classical convolution on the grid, the relative ordering of vertices is up, down, left, and right.
-There is no such ordering on the sphere either, especially if irregularly sampled.
-
-Following \citet{defferrard2016convolutional}, we define our filters as Chebyshev polynomials such as the convolution operation becomes
-\begin{equation} \label{eqn:graph_convolution_cheby}
-	h_\theta\left(\tL\right) \f = \U \left(\sum_{k=0}^K \theta_k T_k\left(\tilde{\bLambda}\right) \right) \U\trans \f = \sum_{k=0}^K \theta_k T_k\left(\tL\right) \f,
-\end{equation}
-where $\tL = \frac{2}{\lambda_{max}} \L - \b{I} = -\frac{2}{\lambda_{max}} \D^{-1/2} \W \D^{-1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\b \Lambda}$ in $[-1, 1]$ and $T_k(\cdot)$ is the Chebyshev polynomial of degree $k$, defined by the recursive relation $T_k(\tL) = 2\tL T_{k-1}(\tL) - T_{k-2}(\tL)$, $T_1(\tL) = \tL$, $T_0(\tL) = \b{I}$.
-While definitions \eqnref{graph_convolution_polynomial} and \eqnref{graph_convolution_cheby} both allow the representation of the same set of filters, Chebyshev polynomials are preferred as they form an orthogonal basis on the interval $[-1, 1]$.
-Moreover, they factor out $\tL^{k-2}$ from $T_k(\tL)$, e.g., the 3-neighborhood is not mixed with the 5-neighborhood.
-That results in easier learning when optimizing the parameters $\theta$.
-Finally, the coefficients can be computed such as the truncated Chebyshev expansions gives an approximate minimax polynomial of a given filter \citep{hammond2011wavelets}.
-While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
-In practice, we found out in our experiment that Chebyshev polynomials are slightly more stable than the monomials used in~\cite{khasanova2017graphomni}(i.e.
-optimizing directly the $\theta_k$ in \eqnref{graph_convolution_polynomial}).
-We believe that this is due to their orthogonality (as explained above) and uniformity\footnote{The amplitude of Chebyshev polynomials is more or less constant over the domain $[-1, 1]$ independently of the order $k$.
-On the contrary the amplitude of $x^k$ is very different for $|x|\approx 0$ and $|x| \approx 1$.}.
-\nati{I added a sentence and I think we should not give much more details here. If we do an experiment, we can comment in the experiment section.}
-\todo{(i) scale of $\theta_k$: they are mostly uniform for Chebyshev polynomials, end exploding for monomials. Though SGD implicitly imposes a uniform prior on the learned parameters.}
-\todo{(ii) numerical stability of $\L^k \f$ v.s. $T_k(\L) \f$}
-\todo{(iii) in the code, initialize $\theta_k$ with stdev adapted to $F_{in}$ and $K$}
-
-Exploiting the recursive formulation of Chebyshev polynomials, evaluating \eqnref{graph_convolution_cheby} requires $\bO(K)$ multiplications of the dense vector $\f$ with the sparse matrix $\tL$.
-The cost of one such multiplication is $\bO(|\E|)$. By construction of our graph, $|\E| < 8 N_{pix}$ and the overall computational cost of the convolution is thus reduced to $\bO(N_{pix})$ operations.
-That is much more efficient than filtering with spherical harmonics, even tho the HEALPix was designed as an iso-latitude sampling to leverage a fast spherical transform.
-That is especially true for smooth kernels which require a low polynomial degree $K$.
-\figref{filtering_speed} demonstrates the speed comparison of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
-The performance of our approach is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{filtering_speed}
-	\caption{Comparison of filtering speed for Gaussian smoothing of maps of various sizes.
-    The fast spherical harmonic transform (SHT) is implemented by the \texttt{healpy} Python package (via the \texttt{healpy.sphtfunc.smoothing} function with $\ell_{max} = 3 N_{side} - 1$, the default).
-    The graph filtering is defined by \eqnref{graph_convolution_cheby} and implemented with the \texttt{numpy} and \texttt{scipy} Python packages.
-    Both are executed on a single core.
-    The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3)$ for the spherical harmonics, where $\ell_{max}$ is the largest degree (i.e., the spectrum is truncated at $\ell_{max}$).}
-	\label{fig:filtering_speed}
-\end{figure}
-
-\subsection{Coarsening and Pooling}
-
-Coarsening can be naturally designed for hierarchical pixelisation schemes, as each subdivision divides a cell in an equal number of child sub-cells.
-Coarsening is the reverse operation: merging the sub-cells toward the goal of summarizing the data supported on them.
-Merging cells lead to a coarser graph.
-Coarsening defines $\C(i)$, the set of children of node $v_i$.
-For the HEALPix subdivision scheme, the number of children is constant, i.e., $| \C(i) | = 4^p \ \forall i$, for some $p$.
-
-Pooling refers to the operation that summarizes the data supported on the merged sub-cells in one parent cell.
-Given a map $\x \in \R^{N_{pix}}$, pooling defines $\y \in \R^{N'_{pix}}$ such as
-\begin{equation} \label{eqn:pooling}
-	y_i = f \left( \left\{ x_j : j \in \C(i) \right\} \right), \ \forall i \in [N'_{pix}],
-\end{equation}
-where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix} / {N'_{pix}}$ is the down-sampling factor, which for HEALPix is $| \C(i) | = N_{pix} / {N_{pix}}' = (N_{side} / N'_{side})^2 = 4^p$.
-That operation is often taken to be the maximum value, but it can be any permutation invariant operation, such as a sum or an average.
-\figref{pooling} illustrates the process.
-
-% The advantage of schemes based on a base polyhedron is that cells are equal-area.
-While that is not required for the convolution operation when modeling with graphs (it can be corrected by setting edge weights appropriately, see \citet{khasanova2017graphomni})
-% nope: can also do a regular pooling on the equirectangular. It preserves the sampling, and the convolution is adapted to the sampling thanks to the edge weights.
-
-\begin{figure}
-	\centering
-    % \includegraphics[width=\linewidth]{pooling}
-	\includegraphics[trim=1.1cm 0cm 0cm 0cm, width=\linewidth]{figures/figure_pooling_svg.pdf}
-	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarsest cell covers $1/12$ of the sphere.}
-	\label{fig:pooling}
-\end{figure}
-
-\subsection{Statistical layer}
-\label{sec:stat_layer}
-% Or Global pooling?
-
-Following \citet{khasanova2017tigranet}, we implement an optional statistical layer between the last graph convolutional layer and the first fully connected layer for the neural network.
-This introduces the invariance of the output to isometric transformations, such as rotation and translation of maps on the sphere.
-The role of the layer is to compute global and location independent statistics from feature maps.
-Besides providing invariance, the layer drastically compresses the representation of the data as the number of computed statistics $N_{stat}$ is usually much smaller than the size of the map $N_{pix}$.
-That compression results in much smaller fully connected layers, which usually contain a significant fraction of trainable parameters of a neural network.
-The invariance and reduced representation should help the network to learn from less samples and to generalize better to unseen data.
-Yet another advantage is that a network built with such a statistical layer is agnostic to the size of the input data, i.e., it can classify maps which do not have the same number of pixels.
-Indeed, such global summarization is invariant to node permutation and is commonly used along graph convolutions to classify graphs of varying sizes \citep{duvenaud2015gcn, li2015gatedgnn}.
-
-Given a feature map $\x \in \R^{N_{pix}}$, the statistical layer is defined as
-\begin{equation} \label{eqn:stat_layer}
-	\y = f(\x) \in \R^{N_{stat}},
-\end{equation}
-where $f$ computes $N_{stat}$ statistics which are independent from the size of the map, $N_{pix}$.
-An example is the global average pooling $f(\x) = \esp(\x)$, introduced by \citet{lin2013globalavgpooling}, where $\esp(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} x_i$ is the empirical mean.
-Another example is $f(\x) = [\esp(\x), \var(\x)]\trans$, where $\var(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} (x_i - \esp(\x))^2$ is the empirical variance.
-Other statistical layers are also possible.
-In particular, we also implement a \emph{learned histogram} statistic \citep{wang2016learnhist}.
-Other approaches, which we did not implement, may include applying different diffusion on the final maps to obtain statistics at different scales, as proposed by \citep{khasanova2017tigranet}.
-
-\subsection{Graph convolutional neural network}
-\label{sec:architecture}
-
-Neural networks are constructed as stacks of layers which sequentially transform the data from its raw representation to a decision on the class label.
-Our architecture, pictured in \figref{architecture}, is composed of many layers.
-The convolutional part, the head of the neural network, is composed of graph convolutional layers (GC), pooling layers (P), and batch normalization layers (BN).
-The tail is composed of multiple fully connected layers (FC) followed by a softmax layer (SM).
-A statistical layer (ST) is optionally inserted between the convolutional head and the fully connected tail.
-
-% As such, we will not mention the non-linearity in the description of our architectures.
-A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer where it is set to the identity.
-That operation is point-wise, i.e., $y_{ij} = \sigma(x_{ij})$ and $y_i = \sigma(x_i)$ for matrices $\X, \Y$ and vectors $\x, \y$.
-The rectified linear unit (ReLU) $\sigma(\cdot) = \max(\cdot, 0)$ is a common choice.
-
-Given a matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$, a GC layer computes $\Y = GC(\X) = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels (and nodes), $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
-Using the efficient graph convolution from \eqnref{graph_convolution_cheby}, each output feature map is computed as
-\begin{equation*}
-	\y_i = \sum_{j=1}^{F_{in}} h_{\theta_{ij}}(\tL) \x_j + b_i \in \R^{N_{pix}}, \ \ \forall i \in [F_{out}].
-\end{equation*}
-As such, a GC layer is composed of $F_{in} \cdot F_{out}$ filters, each parameterized by $K$ numbers (see \secref{efficient_convolution}). A bias term $\b b \in \R^{F_{out}}$ is jointly optimized.
-% only if batch normalization is not used
-
-Given a matrix $\X \in \R^{N_{pix} \times F}$, a pooling layer computes $\Y = P(\X) \in \R^{N'_{pix} \times F}$ by reducing its spatial resolution ($N'_{pix} < N_{pix}$) according to \eqnref{pooling}.
-% Given a matrix $\X \in \R^{N_{pix} \times F}$,
-The batch normalization layer \citep{ioffe2015batchnorm} computes $\Y = BN(\X)$ such as
-\begin{equation*}
-	\y_i = \gamma_i \frac{\x_i - \esp(\x_i)}{\sqrt{\var(\x_i) + \epsilon}} + \beta_i, \ \forall i \in [F],
-\end{equation*}
-where $\gamma_{j}$ and $\beta_{j}$ are parameters to be learned and $\epsilon$ is a constant added for numerical stability.
-The empirical expectation $\esp(\x_i) \in \R$ and variance $\var(\x_i) \in \R$ are taken across training examples and pixels.
-% the action of gamma can be done by the filters of the next layer
-
-The statistical layer, defined in \eqnref{stat_layer}, independently transforms each of the $F$ feature maps of the input $\X \in \R^{N_{pix} \times F}$ into $\Y = ST(\X) \in \R^{N_{stat} \times F}$, where $N_{stat}$ is the number of statistics.
-One may even omit the FC layers and directly fed the output of the ST layer into the softmax layer, as proposed by \citet{lin2013globalavgpooling}.
-In this regime, $N_{stat} = 1$ and $F = N_{classes}$ is the number of classes to discriminate (i.e., the last GC layer outputs as many feature maps as there is classes).
-
-A FC layer takes as input $\x \in \R^{F_{in}}$ and outputs
-\begin{equation*}
-	\y = FC(\x) = \b W \x + \b b \in \R^{F_{out}} ,
-\end{equation*}
-where $\W \in \R^{F_{out} \times F_{in}}$ and $\b b \in \R^{F_{out}}$ are the parameters to be learned.
-Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last GC (or the output $\Y \in \R^{N_{stat} \times F_{out}}$ of the ST), is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first FC, where $F_{in} = N_{pix} \cdot F_{out}$ (or $N_{stat} \cdot F_{out}$).
-
-The softmax layer is the last layer in a neural network engineered for classification.
-Given the output $\x \in \R^{N_{classes}}$ of the last FC (or ST), called the logits in the deep learning literature, the softmax layer outputs $\y = SM(\x)$ such that
-\begin{equation*}
-	y_i = \frac{\exp(x_i)}{\sum_{j=1}^{N_{classes}} \exp(x_j)} \in [0, 1], \ \forall i \in [N_{classes}],
-\end{equation*}
-where $N_{classes}$ is the number of classes to discriminate.
-Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the probability that the input sample belongs to class $i$.
-This last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.
-
-Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
-An example network is
-\begin{equation*}
-NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC,
-\end{equation*}
-where $\circ$ denotes composition, i.e., $f \circ g = f(g(\cdot))$.
-The number of features $F$ depends on the data at hand.
-For the CMB radiation temperature, $F = 1$.
-For observations in radio frequencies, $F$ would be equal to the number of surveyed frequencies.
-$F$ might also be the number of slices in the radial direction.
-The loss function $\ell(\y) = \ell(NN_\theta(\X))$ is a measure of how good the prediction $\y$ is for the sample $\X$. For a classification task, the loss is usually taken to be the cross-entropy
-\begin{equation*}
-	\ell(\y) = -\log(y_i),
-\end{equation*}
-where $i$ is the correct class label.
-The parameters $\theta$ of the neural network are optimized to minimize the loss over the training dataset $\left\{ \X_i \right\}_{i=1}^{N_{samples}}$:
-\begin{equation*}
-	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell(NN_\theta(\X_i)).
-\end{equation*}
-The same architecture with different loss function can also be used for parameter regression \citep{fluri2018deep,gupta2018nongaussianinformation}.
-The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
-\begin{equation*}
-	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
-\end{equation*}
-where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch.
-Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.
-
-\todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
 
@@
 
+\section{Method}
+\label{sec:method}
+% \begin{itemize}
+% 	\item We build a graph using the healpix sampling
+% 	\item Define Fourier transform and show that the harmonics are visually close to the spherical harmonics
+% 	\item Define spherical convolution using the graph Fourier transform and show heat diffusion example
+% 	\item Show the limits of the approach and explain why we cannot have a perfect spherical convolution with this technique
+% \end{itemize}
+
+A CNN is composed of the following main building blocks~\citep{lecun1998cnn}:
+(i) a convolution,
+(ii) a non-linearity,
+(iii) a down-sampling operation,
+(iv) a pooling operation, and
+(v), optionally,  normalization.\footnote{\citet{ioffe2015batchnorm} have shown that batch normalization helps training. We verified this experimentally in our setting as well.}
+Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}.
+As operations (ii) and (v) are point-wise, they do not depend on the data domain.
+The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either.
+The convolution and down-sampling operations however need to be generalized from Euclidean domains to the sphere.
+
+On regular Euclidean domains, such as 1-dimensional time series or 2-dimensional images, a convolution can be efficiently implemented by sliding a localized convolution kernel (for example a patch of 5x5 pixels) in the signal domain.
+Likewise, down-sampling can be achieved by taking one pixel out of $n$.
+Because of the irregular sampling, there is no straightforward way to define a convolution on the sphere directly in the pixel domain; convolutions are most often performed using spherical harmonics.
+In our method we also use the spectral domain to define the convolution.
+The implementation, however, does not need a direct access to the spectrum, which is computationally more efficient (see \secref{efficient_convolution}).
+% We will therefore use the spectral domain to define the convolutions
+% \footnote{Note that we only use the spectrum to define the convolution.
+% The implementation however does not need a direct access to the spectrum, which is computationally much more efficient. See \secref{efficient_convolution}.}
+% \TK{moving footnote to the main text }
+The gist of our method is to define the convolution operation on a sphere using a graph, and the down-sampling operation using a hierarchical pixelisation of the sphere.
+
+\subsection{HEALPix sampling}
+\label{sec:healpix}
+
+\begin{figure*}
+\includegraphics[width=\linewidth]{figures/figure_example_maps.pdf}
+\caption{Exmaple maps on the sphere:
+(left) the CMB temperature (K) map from Planck \citep{planck2015overview}, with galactic plane masked,
+(middle) map of galaxy number counts (number of galaxies per arcmin$^2$) in SDSS DR14 \citep{abolfathi2017sdssDR14},
+and (right) simulated weak lensing convergence map (dimensionless) simulated with DES DR1 mask \citep{des2018dr1}.
+These maps were pixelised using \texttt{nside}=512.
+The CMB and weak lensing mass maps were smoothed with Gaussian kernels with FWHM=1 deg, and the galaxy count map with FWHM=0.5 deg.
+}
+\label{fig:example_maps}
+\end{figure*}
+
+% \begin{figure}
+%     \centering
+%     \begin{subfigure}[b]{0.45\linewidth}
+%         \centering
+%         \includegraphics[width=\linewidth]{exampleEarthTopo}
+%         \caption{}
+%         \label{fig:example_earth}
+%     \end{subfigure}
+%     \hfill
+%     \begin{subfigure}[b]{0.45\linewidth}
+%         \centering
+%         \includegraphics[width=\linewidth]{exampleCMB}
+%         \caption{}
+%         \label{fig:example_cmb}
+%     \end{subfigure}
+%     \caption[]{Example of (a) an Earth topography map composed of \textasciitilde 3 million pixels (\textasciitilde 7 arcmin resolution) and (b) a model of the Cosmic Microwave Background (CMB) radiation temperature anisotropy, composed of \textasciitilde 13 million pixels (\textasciitilde 3.4 arcmin resolution).\footnotemark}
+%     \label{fig:example_maps}
+% \end{figure}
+
+Before doing any numerical analysis on the sphere, one first has to choose a tessellation, i.e., an exhaustive partition of the sphere into finite area elements, where the data under study is quantized.
+The simplicity of the spherical form belies the intricacy of global analysis on the sphere.
+There is no known point set which achieves the analogue of uniform sampling in Euclidean space and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions.
+Any existing proposition of practical schemes for the discrete treatment of such functions on the sphere introduces some systematic error dependent on the global properties of the point set.
+While our method is applicable to any pixelisation of the sphere, two details depend on the chosen sampling: (i) the choice of neighbours in the construction of the graph, and (ii) the choice of parent nodes when coarsening the graph.
+As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology, our target application, we'll tailor the method to that particular sampling in the subsequent exposition.
+%We'll note in later sections where the method should be adapted for a different sampling.
+
+HEALPix is a particular case of a more general class of schemes which are based on a hierarchical subdivision of a base polyhedron.
+%Many discretized maps of the sphere are based on a hierarchical subdivision of a base polyhedron.
+Another example is the geodesic grids which are based on geodesic polyhedrons, i.e., polyhedrons made of triangular faces.
+A counter-example is the equirectangular projection, which is not constructed from a base polyhedron, although it can be subdivided.
+In the particular HEALPix case, the base is a rhombic dodecahedron, i.e., a polyhedron made from 12 congruent rhombic faces.\footnote{A rhombus is a quadrilateral whose four sides all have the same length.}
+See \figref{pooling} for an illustration of the base rhombic dodecahedron and its subdivisions.
+
+HEALPix is an acronym for Hierarchical Equal Area isoLatitude Pixelization of a sphere.
+This pixelisation produces a hierarchical subdivision of a spherical surface where each pixel covers the same surface area as every other pixel.
+A hierarchy is desired for data locality in computer memory.
+Equal area is advantageous because white noise generated by the signal receiver gets integrated exactly into white noise in the pixel space.
+Isolatitude is essential for the implementation of a fast spherical transform.
+HEALPix is the sole pixelisation scheme which satisfies those three properties.
+
+The lowest possible resolution is given by the base partitioning of the surface into $N_{pix} = 12$ equal sized pixels (right-most sphere in \figref{pooling}).
+As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2 \cdot 12 = 2^2 \cdot 12 = 48$ pixels (middle sphere in \figref{pooling}), the third is $N_{pix} = N_{side}^2 \cdot 12 = 4^2 \cdot 12 = 192$ pixels, etc., where $N_{side} = 1, 2, 4, 8, \ldots$ is the grid resolution parameter.
+High-resolutions HEALPix maps easily reach millions of pixels.
+\figref{example_maps} shows two examples of HEALPix maps: the Cosmic Microwave Background \citep{planck2015overview} and \TK{update}.
+
+\subsection{Graph construction}
+
+Our graph is constructed as an approximation of the continuous 2D manifold that is the surface of the sphere.
+Indeed, \citet{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity.
+That construction can accommodate any sampling, regular or not.
+
+From the HEALPix pixelization, we build a weighted undirected graph $\G = (\V, \E, \W)$, where $\V$ is the set of $N_{pix} = |\V|$ nodes, $\E$ is the set of edges, and $\W$ is the weighted adjacency matrix.
+In our graph, each pixel $i$ is represented by a node (also called vertex) $v_i \in \V$.
+Each node $v_i$ is then connected to the $8$ (or $7$)\footnote{\label{neighbors}The $12 \cdot 4 = 48$ pixels at the corner of each rhombus of the base dodecahedron only have 7 neighboring pixels.
+See Figures~\ref{fig:healpix_graph_4} and~\ref{fig:pooling}.} nodes $v_j$ which represent the neighboring pixels $j$ of pixel $i$, forming edges $(v_i, v_j) \in \E$.
+Given those edges, we define the weighted adjacency matrix $\W \in \R^{N_{pix} \times N_{pix}}$ as
+\begin{equation*}
+	\W_{ij} = \begin{cases}
+		\exp \left( -\frac{\|\x_i-\x_j\|_2^2}{\rho^2} \right) & \text{if pixels $i$ and $j$ are neighbors,} \\
+		0 & \text{otherwise,} \\
+	\end{cases}
+\end{equation*}
+where $\x_i$ is a vector encoding the 3-dimensional coordinates of pixel $i$, and
+\begin{equation*}
+	\rho = \frac{1}{|\E|} \sum_{(v_i, v_j) \in \E} \|\x_i-\x_j\|_2
+\end{equation*}
+is the average Euclidean distance over all connected pixels. This weighting scheme is important as distances between pixels are not equal.
+Other weighting schemes are possible.
+For example,~\cite{khasanova2017graphomni} uses the inverse of the distance instead.
+We found out that the one proposed above works well for our purpose, and did not investigate other approaches, leaving it to future work.
+\figref{healpix_graph_4} shows a graph constructed from the HEALPix sampling of a sphere.
+
+% mdeff: Why not $1/d$? See Pascal's paper
+% nati: The question is: is $1/d$ also good when we have 7/8 neighbors instead of 4?
+Practically, we can also use $1/d$, but that means changing the code and re-runing the experiment.
+We probably do not have to change any parameter though...
+@mdeff: do you think we should try this for this paper?
+Or we keep that for the next one.
+% mdeff: I tried and the eigenvectors and eigenvalues are mostly the same.
+To me, there is no point in trying for trying.
+We should rather come up with a definition of distance that will make the eigenvectors closer to the real spherical harmonics.
+% Agreed: I added a reference to Pascal paper.
+
+\subsection{Graph Fourier basis}
+
+Following~\cite{shuman2013emerging}, the normalized graph Laplacian,
+defined as $\L = \I - \D^{-1/2} \W \D^{-1/2}$, is a second order differential operator
+that can be used to define a Fourier basis on the graph. Here $\D$ is the diagonal
+matrix where $\D_{ii} = \b{d}_i$ and $\b{d}_i = \sum_j \W_{ij}$ is the weighted degree of node $v_i$. By construction, the Laplacian is symmetric positive
+semi-definite and hence can be decomposed as $\L = \U \bLambda \U\trans$, where $\U = [\b u_1, \ldots, \b u_{N_{pix}}]$ is an
+orthonormal matrix of eigenvectors and $\bLambda$ is a diagonal matrix of
+eigenvalues. The graph Fourier basis is defined as the Laplacian eigenvectors, motivated by the fact that a Fourier basis should diagonalize the Laplacian operator.
+The graph Fourier transform of a signal $\f \in \R^{N_{pix}}$ is simply its projection on the eigenvectors given by
+$\hat{\f} = \mathcal{F}_\G \{\f\} = \U\trans \f$. It follows that the inverse graph Fourier transform reads $\mathcal{F}^{-1}_\G \{\hat{\f}\} = \U\hat{\f} = \U \U\trans \f = \f$.
+Note that the Fourier modes are ordered in the increasing order of the Laplacian eigenvalues $\bLambda$, which can be interpreted as squared frequencies.
+Indeed,
+\begin{equation*}
+	\bLambda_{ii} = \b u_i\trans \L \b u_i = \sum_{(v_j, v_k) \in \E} \frac{\W_{jk}}{\sqrt{\b d_j \b d_k}} (\U_{ji} - \U_{ki})^2
+\end{equation*}
+is a measure of the variation of the eigenvector $\b u_i$ is on the graph defined by the Laplacian $\L$.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{eigenvectors}
+	\caption{The first 16 eigenvectors of the graph Laplacian, an equivalent of Fourier modes, of a graph constructed from the HEALPix sampling of the sphere.
+    Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$ and order $|m|=(0,1)$, eigenvectors 4--8 with degree $\ell=2$ and order $|m|=(0,1,2)$, and eigenvectors 9--15 with degree $\ell=3$ and order $|m|=(0,1,2,3)$.
+    Nevertheless, the graph eigenvectors are only approximating spherical harmonics.}
+	\label{fig:graph_harmonics}
+\end{figure}
+
+Figure \figref{graph_harmonics} shows the Fourier modes of a HEALPix graph, created using the graph construction described above.
+The graph Fourier modes resemble the spherical harmonics.
+That is a strong hint that the graph is able to capture the spherical properties of the HEALPix sampling.
+This topic is further discussed in \ref{sec:comparison_spherical_harmonics}.
+
+\subsection{Convolution on graphs}
+\label{sec:graph_convolution}
+
+As there is no notion of translation on a graph, we cannot convolve two graph signals in a strict sense.
+We can, however, convolve a signal with a kernel defined in the spectral domain.
+More precisely, we can filter a graph signal by a kernel.
+Given the convolution kernel
+$h: \R_+ \rightarrow \R$, a signal $\f \in \R^{N_{pix}}$ on the graph is filtered as
+\begin{equation} \label{eqn:graph_convolution}
+	h(\L) \f = \U h(\bLambda) \U\trans \f,
+\end{equation}
+where $h(\bLambda)$ is a diagonal matrix where $h(\bLambda)_{ii} = h(\bLambda_{ii})$, and $h(\bLambda) \hat{\f}$ is the spectral representation of $\f$ after filtering.
+
+Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph.
+It can however be localized on any vertex $v_i$ by the convolution with a Kronecker delta $\b \delta_i \in \R^{N_{pix}}$,\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} that is $h(\L) \b \delta_i$, a column of $h(\L)$.
+This localization can be useful to visualize kernels as explained in~\ref{sec:filter_visualization}.
+If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another.
+While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular.
+However, when considering only parts of the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).
+Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with all localizations of the kernel:
+\begin{equation} \label{eqn:graph_convolution_spatial}
+	(h(\L) \f)_i = \langle h(\L) \b \delta_i, \f \rangle.
+\end{equation}
+In \ref{sec:heat_diffusion}, we present an example application of graph-based convolution to a simple heat-diffusion problem in order to shed some light on what is the convolution on a graph.
+% \textbf{Example.}
+% Let us consider the heat diffusion problem
+% \begin{equation} \label{eqn:heat_equation}
+% 	\L \b{f}(t) = \tau \partial_t \b{f}(t),
+% \end{equation}
+% where $\b{f}: \R_+ \rightarrow \R^{N_{pix}}$. Given the initial condition
+% $\b{f}(0)$, the solution of~\eqnref{heat_equation} can be expressed as
+% \begin{equation*}
+% 	\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U\trans \g{f}(0) = K_t(\L) \b{f}(0),
+% \end{equation*}
+% which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(\lambda)=e^{-\tau t \lambda}$.
+Since the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$, which can be interpreted as squared frequencies, it can also be considered as a generalization of the Gaussian kernel on the sphere.
+\figref{gaussian_filters_comparizon} shows the effect of the convolution by diffusing a unit of heat for $\tau=1$ at various times $t$.
+By comparing the graph convolution with the spherical symmetric Gaussian smoothing, we observe that both techniques lead to similar results (see \figref{gaussian_filters_comparizon}).
+While the graph convolution remains different from the spherical convolution, this small experiment shows that, providing the correct parameters, graph convolution can approximate spherical convolution.
+For additional insides about the graph kernel $K_t$, we refer to the \figref{gaussian_filters_visualization} and~\ref{sec:filter_visualization}.
+
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=\linewidth]{gaussian_filters_sphere}
+% 	\caption{Comparison of convolution with the graph and the spherical harmonics ($N_{side} = 16$).
+% 	Top: Diffusion of a unit of heat for different times $t$ using the graph.
+% 	Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin).
+% 	Relative difference between graph convolution and spherical smoothing: $10.4$\%, $4.8$\%, $3.8$\%.
+% \todo{The main issue with our filters is that their shape depends on the localization.
+It would be nice to measure the expectation and variance of the error over all locations.
+That would show how severe the distortion is.}
+% \nati{Let us keep that for the next paper. I am quite sure, it is negligible in this particular case.}}
+% 	\label{fig:gaussian_filters_comparizon}
+% \end{figure}
+
+% Furthermore, this result is another sign that the constructed graph is able to capture the spherical
+% structure of the HEALPix sampling. In some applications, where the
+% exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
+% The fact that both convolutions are not identical is not relevant in a neural network setting, as the convolution kernels are learned anyway.
+% not ideal tho as the graph convolution depends on the localization
+
+\subsection{Efficient convolutions}
+\label{sec:efficient_convolution}
+
+While \eqnref{graph_convolution} is a theoretically well justified definition of the convolution of a graph signal $\f$ by a kernel $h$, it is computationally cumbersome.
+As no general Fast Fourier Transform (FFT) exist for graphs, the execution of the Fourier transform by multiplication of the signal $\f$ by the dense matrix $\U$ costs $\bO(N_{pix}^2)$ operations.
+% \footnote{See \citep{le2018fgft} for a comparison between the polynomial definition of filters presented here and a class of fast graph Fourier transforms based on the approximation of the Fourier basis $\U$ by a product of sparse matrices.}
+%\TK{I would just cite the paper, we have not introduced the polynomials at this stage yet.}
+In a CNN, this operation has to be performed for each training step: forward and backward.
+% As current training procedures are not data-efficient and require a lot of samples, a quadratic computational cost in the sample size is a .
+%\TK{what does "data-efficient mean"? removing for now}
+As current training procedures require processing of many samples, it would be very slow to perform them for a quadratic computational cost in the sample size.
+Moreover, the eigen-decomposition of the Laplacian $\L$ is needed to obtain the Fourier basis $\U$ in the first place.
+That has a unique cost of $\bO(N_{pix}^3)$ operations.
+
+Fortunately, both of these computational issues can be overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parametrised by $K+1$ coefficients $\theta$.
+In that specific case, the filtering operation \eqnref{graph_convolution} becomes
+\begin{equation} \label{eqn:graph_convolution_polynomial}
+	h_\theta(\L) \f =  \U \left(\sum_{k=0}^K \theta_k \bLambda^k \right) \U\trans \f = \sum_{k=0}^K \theta_k \L^k \f,
+\end{equation}
+an operation requiring $k$ multiplications of the graph Laplacian matrix $\L$.
+In our case, the Laplacian is extremly sparse, with $8-9$ entries per line, making the filtering operation for a fixed $K$ linear in the number of pixel $N_{pix}$.
+% Moreover, here happens the transition from filtering in the spectral domain to filtering in the vertex domain.
+This operation is performed in the vertex domain.
+The matrix $\L^k$ captures $k$-neighborhoods of each pixel, i.e., $(\L^k)_{ij}$ is non-zero if and only if nodes $v_i$ and $v_j$ are connected by a path of length $k$.
+As such, filtering with a polynomial convolution kernel can be interpreted in the pixel (vertex) domain as a weighted linear combination of the pixels neighbors values.
+The weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$.
+We note that restricting the graph convolutional kernel to a polynomial is similar to restricting the classical Euclidean signal-domain convolution to a patch.
+In the classical setting, the convolution with a patch is simply a weighted sum of the neighbors with the weights defined by the patch.
+Similarly, each lines of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an "irregular patch of radius $K$" for our irregular domain.
+\todo{Better vertex domain explanation. \nati{I gave it a try. Should we take a single vertex and explain what heppens to it? Note that I suppressed the following paragraph. }}
+\TK{For me it's understandable:)}
+
+% To make the parallel with classical Euclidean signal-domain convolution, i.e., filtering by multiplying the signal with translated versions of a patch, we here match our filter at the level of neighborhoods\footnote{The 1-neighborhood of a node is the set of nodes which are directly connected to it.
+The 2-neighborhood is the set of nodes which are connected through paths of length 2.} rather than individual nodes.
+That is required as there is no notion of ordering in a general graph.
+For example, in a classical convolution on the grid, the relative ordering of vertices is up, down, left, and right.
+There is no such ordering on the sphere either, especially if irregularly sampled.
+
+Following \citet{defferrard2016convolutional}, we define our filters as Chebyshev polynomials such as the convolution operation becomes
+\begin{equation} \label{eqn:graph_convolution_cheby}
+	h_\theta\left(\tL\right) \f = \U \left(\sum_{k=0}^K \theta_k T_k\left(\tilde{\bLambda}\right) \right) \U\trans \f = \sum_{k=0}^K \theta_k T_k\left(\tL\right) \f,
+\end{equation}
+where $\tL = \frac{2}{\lambda_{max}} \L - \b{I} = -\frac{2}{\lambda_{max}} \D^{-1/2} \W \D^{-1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\b \Lambda}$ in $[-1, 1]$ and $T_k(\cdot)$ is the Chebyshev polynomial of degree $k$, defined by the recursive relation $T_k(\tL) = 2\tL T_{k-1}(\tL) - T_{k-2}(\tL)$, $T_1(\tL) = \tL$, $T_0(\tL) = \b{I}$.
+While definitions \eqnref{graph_convolution_polynomial} and \eqnref{graph_convolution_cheby} both allow the representation of the same set of filters, Chebyshev polynomials are preferred as they form an orthogonal basis on the interval $[-1, 1]$.
+Moreover, they factor out $\tL^{k-2}$ from $T_k(\tL)$, e.g., the 3-neighborhood is not mixed with the 5-neighborhood.
+That results in easier learning when optimizing the parameters $\theta$.
+Finally, the coefficients can be computed such as the truncated Chebyshev expansions gives an approximate minimax polynomial of a given filter \citep{hammond2011wavelets}.
+While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
+In practice, we found out in our experiment that Chebyshev polynomials are slightly more stable than the monomials used in~\cite{khasanova2017graphomni}(i.e.
+optimizing directly the $\theta_k$ in \eqnref{graph_convolution_polynomial}).
+We believe that this is due to their orthogonality (as explained above) and uniformity\footnote{The amplitude of Chebyshev polynomials is more or less constant over the domain $[-1, 1]$ independently of the order $k$.
+On the contrary the amplitude of $x^k$ is very different for $|x|\approx 0$ and $|x| \approx 1$.}.
+\nati{I added a sentence and I think we should not give much more details here. If we do an experiment, we can comment in the experiment section.}
+\todo{(i) scale of $\theta_k$: they are mostly uniform for Chebyshev polynomials, end exploding for monomials. Though SGD implicitly imposes a uniform prior on the learned parameters.}
+\todo{(ii) numerical stability of $\L^k \f$ v.s. $T_k(\L) \f$}
+\todo{(iii) in the code, initialize $\theta_k$ with stdev adapted to $F_{in}$ and $K$}
+
+Exploiting the recursive formulation of Chebyshev polynomials, evaluating \eqnref{graph_convolution_cheby} requires $\bO(K)$ multiplications of the dense vector $\f$ with the sparse matrix $\tL$.
+The cost of one such multiplication is $\bO(|\E|)$. By construction of our graph, $|\E| < 8 N_{pix}$ and the overall computational cost of the convolution is thus reduced to $\bO(N_{pix})$ operations.
+That is much more efficient than filtering with spherical harmonics, even tho the HEALPix was designed as an iso-latitude sampling to leverage a fast spherical transform.
+That is especially true for smooth kernels which require a low polynomial degree $K$.
+\figref{filtering_speed} demonstrates the speed comparison of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
+The performance of our approach is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{filtering_speed}
+	\caption{Comparison of filtering speed for Gaussian smoothing of maps of various sizes.
+    The fast spherical harmonic transform (SHT) is implemented by the \texttt{healpy} Python package (via the \texttt{healpy.sphtfunc.smoothing} function with $\ell_{max} = 3 N_{side} - 1$, the default).
+    The graph filtering is defined by \eqnref{graph_convolution_cheby} and implemented with the \texttt{numpy} and \texttt{scipy} Python packages.
+    Both are executed on a single core.
+    The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3)$ for the spherical harmonics, where $\ell_{max}$ is the largest degree (i.e., the spectrum is truncated at $\ell_{max}$).}
+	\label{fig:filtering_speed}
+\end{figure}
+
+\subsection{Coarsening and Pooling}
+
+Coarsening can be naturally designed for hierarchical pixelisation schemes, as each subdivision divides a cell in an equal number of child sub-cells.
+Coarsening is the reverse operation: merging the sub-cells toward the goal of summarizing the data supported on them.
+Merging cells lead to a coarser graph.
+Coarsening defines $\C(i)$, the set of children of node $v_i$.
+For the HEALPix subdivision scheme, the number of children is constant, i.e., $| \C(i) | = 4^p \ \forall i$, for some $p$.
+
+Pooling refers to the operation that summarizes the data supported on the merged sub-cells in one parent cell.
+Given a map $\x \in \R^{N_{pix}}$, pooling defines $\y \in \R^{N'_{pix}}$ such as
+\begin{equation} \label{eqn:pooling}
+	y_i = f \left( \left\{ x_j : j \in \C(i) \right\} \right), \ \forall i \in [N'_{pix}],
+\end{equation}
+where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix} / {N'_{pix}}$ is the down-sampling factor, which for HEALPix is $| \C(i) | = N_{pix} / {N_{pix}}' = (N_{side} / N'_{side})^2 = 4^p$.
+That operation is often taken to be the maximum value, but it can be any permutation invariant operation, such as a sum or an average.
+\figref{pooling} illustrates the process.
+
+% The advantage of schemes based on a base polyhedron is that cells are equal-area.
+While that is not required for the convolution operation when modeling with graphs (it can be corrected by setting edge weights appropriately, see \citet{khasanova2017graphomni})
+% nope: can also do a regular pooling on the equirectangular. It preserves the sampling, and the convolution is adapted to the sampling thanks to the edge weights.
+
+\begin{figure}
+	\centering
+    % \includegraphics[width=\linewidth]{pooling}
+	\includegraphics[trim=1.1cm 0cm 0cm 0cm, width=\linewidth]{figures/figure_pooling_svg.pdf}
+	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarsest cell covers $1/12$ of the sphere.}
+	\label{fig:pooling}
+\end{figure}
+
+\subsection{Statistical layer}
+\label{sec:stat_layer}
+% Or Global pooling?
+
+Following \citet{khasanova2017tigranet}, we implement an optional statistical layer between the last graph convolutional layer and the first fully connected layer for the neural network.
+This introduces the invariance of the output to isometric transformations, such as rotation and translation of maps on the sphere.
+The role of the layer is to compute global and location independent statistics from feature maps.
+Besides providing invariance, the layer drastically compresses the representation of the data as the number of computed statistics $N_{stat}$ is usually much smaller than the size of the map $N_{pix}$.
+That compression results in much smaller fully connected layers, which usually contain a significant fraction of trainable parameters of a neural network.
+The invariance and reduced representation should help the network to learn from less samples and to generalize better to unseen data.
+Yet another advantage is that a network built with such a statistical layer is agnostic to the size of the input data, i.e., it can classify maps which do not have the same number of pixels.
+Indeed, such global summarization is invariant to node permutation and is commonly used along graph convolutions to classify graphs of varying sizes \citep{duvenaud2015gcn, li2015gatedgnn}.
+
+Given a feature map $\x \in \R^{N_{pix}}$, the statistical layer is defined as
+\begin{equation} \label{eqn:stat_layer}
+	\y = f(\x) \in \R^{N_{stat}},
+\end{equation}
+where $f$ computes $N_{stat}$ statistics which are independent from the size of the map, $N_{pix}$.
+An example is the global average pooling $f(\x) = \esp(\x)$, introduced by \citet{lin2013globalavgpooling}, where $\esp(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} x_i$ is the empirical mean.
+Another example is $f(\x) = [\esp(\x), \var(\x)]\trans$, where $\var(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} (x_i - \esp(\x))^2$ is the empirical variance.
+Other statistical layers are also possible.
+In particular, we also implement a \emph{learned histogram} statistic \citep{wang2016learnhist}.
+Other approaches, which we did not implement, may include applying different diffusion on the final maps to obtain statistics at different scales, as proposed by \citep{khasanova2017tigranet}.
+
+\subsection{Graph convolutional neural network}
+\label{sec:architecture}
+
+Neural networks are constructed as stacks of layers which sequentially transform the data from its raw representation to a decision on the class label.
+Our architecture, pictured in \figref{architecture}, is composed of many layers.
+The convolutional part, the head of the neural network, is composed of graph convolutional layers (GC), pooling layers (P), and batch normalization layers (BN).
+The tail is composed of multiple fully connected layers (FC) followed by a softmax layer (SM).
+A statistical layer (ST) is optionally inserted between the convolutional head and the fully connected tail.
+
+% As such, we will not mention the non-linearity in the description of our architectures.
+A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer where it is set to the identity.
+That operation is point-wise, i.e., $y_{ij} = \sigma(x_{ij})$ and $y_i = \sigma(x_i)$ for matrices $\X, \Y$ and vectors $\x, \y$.
+The rectified linear unit (ReLU) $\sigma(\cdot) = \max(\cdot, 0)$ is a common choice.
+
+Given a matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$, a GC layer computes $\Y = GC(\X) = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels (and nodes), $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
+Using the efficient graph convolution from \eqnref{graph_convolution_cheby}, each output feature map is computed as
+\begin{equation*}
+	\y_i = \sum_{j=1}^{F_{in}} h_{\theta_{ij}}(\tL) \x_j + b_i \in \R^{N_{pix}}, \ \ \forall i \in [F_{out}].
+\end{equation*}
+As such, a GC layer is composed of $F_{in} \cdot F_{out}$ filters, each parameterized by $K$ numbers (see \secref{efficient_convolution}). A bias term $\b b \in \R^{F_{out}}$ is jointly optimized.
+% only if batch normalization is not used
+
+Given a matrix $\X \in \R^{N_{pix} \times F}$, a pooling layer computes $\Y = P(\X) \in \R^{N'_{pix} \times F}$ by reducing its spatial resolution ($N'_{pix} < N_{pix}$) according to \eqnref{pooling}.
+% Given a matrix $\X \in \R^{N_{pix} \times F}$,
+The batch normalization layer \citep{ioffe2015batchnorm} computes $\Y = BN(\X)$ such as
+\begin{equation*}
+	\y_i = \gamma_i \frac{\x_i - \esp(\x_i)}{\sqrt{\var(\x_i) + \epsilon}} + \beta_i, \ \forall i \in [F],
+\end{equation*}
+where $\gamma_{j}$ and $\beta_{j}$ are parameters to be learned and $\epsilon$ is a constant added for numerical stability.
+The empirical expectation $\esp(\x_i) \in \R$ and variance $\var(\x_i) \in \R$ are taken across training examples and pixels.
+% the action of gamma can be done by the filters of the next layer
+
+The statistical layer, defined in \eqnref{stat_layer}, independently transforms each of the $F$ feature maps of the input $\X \in \R^{N_{pix} \times F}$ into $\Y = ST(\X) \in \R^{N_{stat} \times F}$, where $N_{stat}$ is the number of statistics.
+One may even omit the FC layers and directly fed the output of the ST layer into the softmax layer, as proposed by \citet{lin2013globalavgpooling}.
+In this regime, $N_{stat} = 1$ and $F = N_{classes}$ is the number of classes to discriminate (i.e., the last GC layer outputs as many feature maps as there is classes).
+
+A FC layer takes as input $\x \in \R^{F_{in}}$ and outputs
+\begin{equation*}
+	\y = FC(\x) = \b W \x + \b b \in \R^{F_{out}} ,
+\end{equation*}
+where $\W \in \R^{F_{out} \times F_{in}}$ and $\b b \in \R^{F_{out}}$ are the parameters to be learned.
+Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last GC (or the output $\Y \in \R^{N_{stat} \times F_{out}}$ of the ST), is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first FC, where $F_{in} = N_{pix} \cdot F_{out}$ (or $N_{stat} \cdot F_{out}$).
+
+The softmax layer is the last layer in a neural network engineered for classification.
+Given the output $\x \in \R^{N_{classes}}$ of the last FC (or ST), called the logits in the deep learning literature, the softmax layer outputs $\y = SM(\x)$ such that
+\begin{equation*}
+	y_i = \frac{\exp(x_i)}{\sum_{j=1}^{N_{classes}} \exp(x_j)} \in [0, 1], \ \forall i \in [N_{classes}],
+\end{equation*}
+where $N_{classes}$ is the number of classes to discriminate.
+Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the probability that the input sample belongs to class $i$.
+This last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.
+
+Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
+An example network is
+\begin{equation*}
+NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC,
+\end{equation*}
+where $\circ$ denotes composition, i.e., $f \circ g = f(g(\cdot))$.
+The number of features $F$ depends on the data at hand.
+For the CMB radiation temperature, $F = 1$.
+For observations in radio frequencies, $F$ would be equal to the number of surveyed frequencies.
+$F$ might also be the number of slices in the radial direction.
+The loss function $\ell(\y) = \ell(NN_\theta(\X))$ is a measure of how good the prediction $\y$ is for the sample $\X$. For a classification task, the loss is usually taken to be the cross-entropy
+\begin{equation*}
+	\ell(\y) = -\log(y_i),
+\end{equation*}
+where $i$ is the correct class label.
+The parameters $\theta$ of the neural network are optimized to minimize the loss over the training dataset $\left\{ \X_i \right\}_{i=1}^{N_{samples}}$:
+\begin{equation*}
+	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell(NN_\theta(\X_i)).
+\end{equation*}
+The same architecture with different loss function can also be used for parameter regression \citep{fluri2018deep,gupta2018nongaussianinformation}.
+The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
+\begin{equation*}
+	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
+\end{equation*}
+where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch.
+Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.
+
+\todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
+
+\section{Related work}
+\label{sec:related}
+
+\begin{figure}
+    \centering
+    \includegraphics[height=7em]{sphere_grid_equirectangular}
+    \hfill
+    \includegraphics[height=7em]{sphere_grid_cubedsphere}
+    \hfill
+    \includegraphics[height=7em]{half_graph_4}
+    \caption[]{Some pixelizations of the sphere.
+Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system.
+Middle: an equiangular cubed-sphere grid, as described in \citet{ronchi1996cubed}.
+Right: graph built from an HEALPix pixelization of half the sphere ($N_{side} = 4$).
+By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[7] Left and middle figures are taken from \citet{boomsma2017spherical}.}
+    \label{fig:sphere_grids}
+    \label{fig:healpix_graph_4}
+\end{figure}
+
+\citet{boomsma2017spherical} apply a standard 2D CNN to a grid discretization of the sphere.
+Two grids, illustrated in \figref{sphere_grids}, are used in their work: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}.
+As this formulation uses the standard 2D convolutions, all the optimizations developed for 2D images can be applied, what make it computationally very efficient.
+It is, however, restricted to those grid sampling sets.
+Similarly to the cubed-sphere, HEALPix is a composition of twelve grids.
+While each of those twelve grids could potentially be independently fed into a 2D CNN, boundary conditions would have to be properly handled, as those grids are not independent.
+\todo{How do they handle boundaries?}
+\TK{+1,good question}
+\nati{They are almost not talking about that. For the cubed sphere, the only reference I could found was:
+\emph{"When implementing convolutions and pooling operations for the cubed-sphere grid, one has to be careful in padding each patch with the contents of the four neighbouring patches, in order to preserve the wrapped topology of the sphere (figure 2, right)."}
+Note that for the cubed sphere sampling each pixel has exactly four neighboors which make the problem of border effect handable.
+As for the equirectangular grid, it is equivalent to a cylinder.
+So I guess they take the standard image processing border conditions (reflective).
+I do not think we should mention any of that in the paper.
+}
+% Furthermore, the grid requirement makes it impossible for the convolution to capture the spherical properties of the domain, i.e., the cubed-sphere sampling is by definition adapted to a cube and not to a sphere.
+Nope, the graph can adapt to any sampling.
+% Moreover, those samplings are not ideal as their resolution is not constant across the sphere.
+Moreover, the pixel area is not constant across the sphere in those sampling schemes, which may limit their potential applications.
+Indeed, the singularities, such as the poles for the equirectangular grid, and the corners of the cube for the cubed-sphere, are over-sampled.
+Equal areas of discrete elements is advantageous for many physical measurements, as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence \citep{gorski2005healpix}.
+% \nati{Michael: Under some very specific hypothesis, this second approach is a particular case of our method, i.e.
+(i) our method with a stupid sampling, (ii) assumption that graph convolution on a grid == 2d convolution.
+Do you think we should mention that?
+I think we should not.}
+Finally, a 2D CNN learns directional filters, which are well defined with respect of the image coordinates.
+Directions that make much sense for images (up, down, left, and right) are arbitrarily defined when setting the origin of the grids on the sphere.
+Any convolution using directions on the sphere is not equivariant to translation and rotation.
+
+% As presented by~\cite{cohen2018spherical}, the most mathematical approach to extend the convolution on a sphere is to use a spherical Fourier transform.
+The convolution is then simply defined as the product in the spectral domain.
+This approach requires one Fourier and one inverse Fourier transform per convolution which remain, even with accelerated algorithms, expensive.
+
+\citet{cohen2018spherical} uses the continuous spherical convolution.
+The goal of this contribution was to define a rotation-equivariant convolution on the sphere, i.e., a rotation of the input implies the same rotation in the output.
+The resulting convolution is performed by (i) a spherical harmonic transform (SHT), i.e., a projection on the spherical harmonics, (ii) a  multiplication in the spectral domain, and (iii) an inverse SHT.
+Hence the computational cost of a convolution is dominated by the two SHTs.
+A naive implementation of the SHT costs $\bO(N_{pix}^2)$ operations, where $N_{pix}$ is the number of pixels.
+Accelerated schemes exist for some sampling sets \citep[see][for examples]{mohlenkamp1999fast, rokhlin2006fast, reinecke2013libsharp}.
+The main advantage of this approach is that it provides a mathematically well defined rotation-equivariant network.
+Nevertheless, even with accelerated SHTs, the convolutions remain expensive, limiting the practical use of this approach.
+For example with the HEALPix sampling, which was designed to have a fast SHT by being iso-latitude, the computational cost of the SHT is $\bO(N_{pix}^{3/2}) = \bO(N_{side}^3) = \bO(\ell_{max}^3)$, where $\ell_{max}$ is the largest angular frequency\footnote{All pixels are placed on $N_{ring} = 4N_{side}-1 = \bO(\sqrt{N_{pix}})$ rings of constant latitude.
+Each ring has $\bO(\sqrt{N_{pix}})$ pixels.
+Thanks to this iso-latitude property, the SHT is computed using recurrence relations for Legendre polynomials on co-latitude and fast Fourier transforms (FFTs) on longitude.
+The computational cost is thus $\sqrt{N_{pix}}$ FFTs for a total cost of $\bO(N_{pix} \log(\sqrt{N_{pix}}))$, plus $\sqrt{N_{pix}}$ matrix multiplications of size $\sqrt{N_{pix}}$ for a total cost of $\bO(N_{pix}^{3/2})$.}
+\citep{gorski2005healpix, reinecke2013libsharp}.
+In comparison, filtering with our HealpixNet method scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}).
+% Moreover, \figref{filtering_speed} shows that a naive implementation of our method is more than ten times faster than the SHT implemented by the highly optimized \pkg{libsharp} library used by HEALPix \citep{reinecke2013libsharp}.
+% While a comparison is theoretically possible, the experiments of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and do not provide any code for the HEALPix one.
+Hence, a practical comparison is not possible.
+% \TK{I would leave out here, as this is a "spoiler" of the results section.}
+
+Approaches by \citet{cohen2018spherical,boomsma2017spherical} can not be easily accelerated when the data lies on a part of the sphere only.
+
+\nati{Why is \citet{boomsma2017spherical} here? I think it can be trivally accelerated.}
+That is an important use case in cosmology as measurements are often partial, i.e., full-sky maps are rare.
+One could still fill the unseen part of the sphere with zeros, and avoid to compute empty integrals, on the latitude or longitude.
+It is, however, not straightforward to identify those empty directions, and computations would still be wasted; consider, for example, a ring which mostly contains zeros but a few measurements.
+With graphs however, the computation is done only for the used pixels.
+This, however, results in some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}).
+These can be mitigated by padding with zeros a small area around the measurements.
+
+% In an attempt to get the best of the first two approaches, we follow a third
+% direction. We use a graph to adapt to the particular structure of the sphere.
+% While the convolution remains efficient, it still captures well the spherical
+% structure and is particularly adapted to the HEALPix sampling.
+% \TK{I am not sure what is the point of this paragraph, we described our approach already before}
+
+The use of a graph to model the discretised sphere was also considered by~\citet{khasanova2017graphomni}.
+The authors map omnidirectional images onto a sphere, with the goal of correcting for distortions induced by the lens, which was used for their acquisition.
+Besides a different practical application, for which the method was designed, there are two important differences.
+% First, a different sampling scheme is used: \cite{khasanova2017graphomni} uses a grid.
+First, similarly to~\citet{boomsma2017spherical}, they use an equirectangular grid sampling.
+% \TK{how is it different from us?}
+Second, it uses a graph CNN based on a different parameterisation of the convolution kernel.
+Moreover, they did not take advantage of a hierarchical pixelization of the sphere and resorted to dynamic pooling~\citep{kalchbrenner2014dcnn}.
+Finally, while the rotation invariance is desirable, the statistical layer used
+% --- an operation which computes a set of spatially invariant statistics of the last feature map ---
+% \{TK} this should be explained earlier
+may not capture the information in an optimal way
+\todo{and hinders performance (should be empirically verified)}.
+\TK{This is a strong claim, can we support this?} \nati{It is not that strong as we use "may" right?
+We should probably soften it a bit.
+However the main idea is correct.
+If you compute some statistics on some features, you lose some information and may get worse results.
+Nevertheless, since we are also using a statistical layer, I would juste remove this.}
+Moreover, the chosen statistics have to be hand-crafted to capture statistics of interest.
+% While developing completely invariant transforms is a goal worth investigating, CNNs for image recognition, which are arguably the most researched and developed architectures, are not built to be fully invariant to translation.
+% As with the proposed spherical CNN, the fully connected layers at the end of the network depend on the spatial localization of features.
+% While that may not be ideal, it was shown to work well in practice.
+% \TK{The two sentences above look like a tangent to me.. can we skip it an go to the main point, which is I think the fact that we use the stat layer?}
+
+\todo{In HealpixNet we use the idea of a statistical layer, described in \secref{stat_layer}, to provide invariance to isometric transformations such as translation and rotation on the sphere.
+\TK{We would need to describe the idea of the statistical layer for the cosmology audience. They don't have a clue what it is.}\nati{Can't they just wait for \secref{stat_layer}? }
+The use of the statistical layer is optional.
+In our approach, we are keeping all the statistical moments by retaining a full, learned learned feature histogram, an approach that performed the best in our tests.
+That is similar to the learnable histogram introduced by \citet{wang2016learnhist}, although for a purpose of integrating global context in object detection and segmentation tasks.
+\citet{khasanova2017graphomni} uses the mean and variance of diffused versions of the last feature maps in their statistical layer.}
+\TK{why is this section in TODO?\nati{Probably because, we have not decided if we use the histogram yet. This paragraph needs to be rewritten once we are clear with the code.}}
+
+There exists many formulations of graph neural networks, reviewed by \citet{bronstein2017review} and \citet{hamilton2017review}.
+For this contribution, we chose the formulation of \citet{defferrard2016convolutional} as its root on strong graph signal processing theory makes the concept of convolutions and filters explicit \citep{shuman2013emerging}.
+Its tie to a graph Fourier transform allows us to compare with the spherical harmonic transform, and study its invariance properties.
+More geometric than permutation invariant aggregation.
+A contrario, formulations with exploit the tengant space of manifolds define a local coordinate system.
+While this formulation of convolution can learn anisotropic filters, it is not equivariant to translation.
+\todo{better wording}
+\todo{three main interpretations: gsp, Bronstein manifold tangent plane, message passing, permutation invariant aggregation, spatial formulations}
+Bronstein is a spatial formulation where the registration is done by projection on the tangent plane.
+% Not Bronstein's manifold approach as we want a Fourier basis to compare to the spherical harmonics.
+% Be as close as possible to spherical harmonics.
+Related to this, convolutional neural networks have been defined on manifolds and have achieved impressive results on shapes [Bronstein].
+They however too depend on an orientation, which spheres do not possess.
+
+% Anisotropic cannot be invariant
+
+The connection has recently been made between graph CNNs and group equivariant CNNs \cite{kondor2018equivariance}, justifying the use of graphs to gain rotation equivariance on the sphere.
+
+% In this work, we are using the graph CNN formulation introduced in~\cite{defferrard2016convolutional}.
+
+Spatial definitions of graph convolutions, e.g.
+[Niepert] needs to define an orientation in order to match the edges with the filters.
+Most often the orientation is not given by the application, and one has to define it (for example by ordering by degree or any other measure, or by using a graph coloring).
+There is no good default good orientation on general graphs and the choice of an orientation is highly application dependent.
+
 \section{Experiments}

### 2018-08-05 scnn.tex
updated + commented out double related work section

@@
     \item (TK) re-make figures to make the labels/legend/titles the same font size as the main text
-    \item (TK) add section in conclusions/ paragraph on possible extensions to the code: dense output, regression, GANs, segmentation
     \item (NP+MD)  paragraph on our chosen architecture in the Experiments sections
-    \item (TK) add reference to figure (pooling) to the area of orders
     \item (NP+MD) move the Related Work section after the Method section
     \item (NP) vertex interpretation
-
     \item (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook.
@@
     \item TK check part sphere notebook and whole sphere
+    \item (TK) uniformize text size in figures
     \item branch with notebooks with plots (results) NP
@@
     \item check if papers which appear as arxiv were not published in a conference or journal
-    \item (TK) add info on comparison with histograms, so that it's just a demonstration
-    \item TK read the result section
-    \item TK check the appendix
-    \item (almost done) TK optional - example of data (CMB (mask) + mass map + radio intensity)
     \item (almost done) TK read everything
     \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings.
-    \item uniformize text size in figures
+    \item (done!) TK check the appendix
+    \item (done!) TK optional - example of data (CMB (mask) + mass map + radio intensity)
+    \item (done!) (TK) add info on comparison with histograms, so that it's just a demonstration
+    \item (done!) TK read the result section
+    \item (done!) (TK) add reference to figure (pooling) to the area of orders
+    \item (done!) (TK) add section in conclusions/ paragraph on possible extensions to the code: dense output, regression, GANs, segmentation
     % \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
@@
 % the convolution is not restricted to the sphere, the coarsening/pooling is
+
+% \section{Related work}
+% \label{sec:related}
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[height=7em]{sphere_grid_equirectangular}
+%     \hfill
+%     \includegraphics[height=7em]{sphere_grid_cubedsphere}
+%     \hfill
+%     \includegraphics[height=7em]{half_graph_4}
+%     \caption[]{Some pixelizations of the sphere.
+Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system.
+Middle: an equiangular cubed-sphere grid, as described in \citet{ronchi1996cubed}.
+Right: graph built from an HEALPix pixelization of half the sphere ($N_{side} = 4$).
+By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[7] Left and middle figures are taken from \citet{boomsma2017spherical}.}
+%     \label{fig:sphere_grids}
+%     \label{fig:healpix_graph_4}
+% \end{figure}
+
+% \citet{boomsma2017spherical} apply a standard 2D CNN to a grid discretization of the sphere.
+Two grids, illustrated in \figref{sphere_grids}, are used in their work: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}.
+% As this formulation uses the standard 2D convolutions, all the optimizations developed for 2D images can be applied, what make it computationally very efficient.
+% It is, however, restricted to those grid sampling sets.
+Similarly to the cubed-sphere, HEALPix is a composition of twelve grids.
+While each of those twelve grids could potentially be independently fed into a 2D CNN, boundary conditions would have to be properly handled, as those grids are not independent.
+% \todo{How do they handle boundaries?}
+% \TK{+1,good question}
+% \nati{They are almost not talking about that. For the cubed sphere, the only reference I could found was:
+% \emph{"When implementing convolutions and pooling operations for the cubed-sphere grid, one has to be careful in padding each patch with the contents of the four neighbouring patches, in order to preserve the wrapped topology of the sphere (figure 2, right)."}
+% Note that for the cubed sphere sampling each pixel has exactly four neighboors which make the problem of border effect handable.
+As for the equirectangular grid, it is equivalent to a cylinder.
+So I guess they take the standard image processing border conditions (reflective).
+% I do not think we should mention any of that in the paper.
+% }
+% % Furthermore, the grid requirement makes it impossible for the convolution to capture the spherical properties of the domain, i.e., the cubed-sphere sampling is by definition adapted to a cube and not to a sphere.
+Nope, the graph can adapt to any sampling.
+% % Moreover, those samplings are not ideal as their resolution is not constant across the sphere.
+% Moreover, the pixel area is not constant across the sphere in those sampling schemes, which may limit their potential applications.
+% Indeed, the singularities, such as the poles for the equirectangular grid, and the corners of the cube for the cubed-sphere, are over-sampled.
+% Equal areas of discrete elements is advantageous for many physical measurements, as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence \citep{gorski2005healpix}.
+% % \nati{Michael: Under some very specific hypothesis, this second approach is a particular case of our method, i.e.
+(i) our method with a stupid sampling, (ii) assumption that graph convolution on a grid == 2d convolution.
+Do you think we should mention that?
+I think we should not.}
+% Finally, a 2D CNN learns directional filters, which are well defined with respect of the image coordinates.
+% Directions that make much sense for images (up, down, left, and right) are arbitrarily defined when setting the origin of the grids on the sphere.
+% Any convolution using directions on the sphere is not equivariant to translation and rotation.
+
+% % As presented by~\cite{cohen2018spherical}, the most mathematical approach to extend the convolution on a sphere is to use a spherical Fourier transform.
+The convolution is then simply defined as the product in the spectral domain.
+This approach requires one Fourier and one inverse Fourier transform per convolution which remain, even with accelerated algorithms, expensive.
+
+% \citet{cohen2018spherical} uses the continuous spherical convolution.
+% The goal of this contribution was to define a rotation-equivariant convolution on the sphere, i.e., a rotation of the input implies the same rotation in the output.
+% The resulting convolution is performed by (i) a spherical harmonic transform (SHT), i.e., a projection on the spherical harmonics, (ii) a  multiplication in the spectral domain, and (iii) an inverse SHT.
+Hence the computational cost of a convolution is dominated by the two SHTs.
+% A naive implementation of the SHT costs $\bO(N_{pix}^2)$ operations, where $N_{pix}$ is the number of pixels.
+% Accelerated schemes exist for some sampling sets \citep[see][for examples]{mohlenkamp1999fast, rokhlin2006fast, reinecke2013libsharp}.
+% The main advantage of this approach is that it provides a mathematically well defined rotation-equivariant network.
+Nevertheless, even with accelerated SHTs, the convolutions remain expensive, limiting the practical use of this approach.
+% For example with the HEALPix sampling, which was designed to have a fast SHT by being iso-latitude, the computational cost of the SHT is $\bO(N_{pix}^{3/2}) = \bO(N_{side}^3) = \bO(\ell_{max}^3)$, where $\ell_{max}$ is the largest angular frequency\footnote{All pixels are placed on $N_{ring} = 4N_{side}-1 = \bO(\sqrt{N_{pix}})$ rings of constant latitude.
+Each ring has $\bO(\sqrt{N_{pix}})$ pixels.
+Thanks to this iso-latitude property, the SHT is computed using recurrence relations for Legendre polynomials on co-latitude and fast Fourier transforms (FFTs) on longitude.
+The computational cost is thus $\sqrt{N_{pix}}$ FFTs for a total cost of $\bO(N_{pix} \log(\sqrt{N_{pix}}))$, plus $\sqrt{N_{pix}}$ matrix multiplications of size $\sqrt{N_{pix}}$ for a total cost of $\bO(N_{pix}^{3/2})$.}
+% \citep{gorski2005healpix, reinecke2013libsharp}.
+% In comparison, filtering with our HealpixNet method scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}).
+% % Moreover, \figref{filtering_speed} shows that a naive implementation of our method is more than ten times faster than the SHT implemented by the highly optimized \pkg{libsharp} library used by HEALPix \citep{reinecke2013libsharp}.
+% % While a comparison is theoretically possible, the experiments of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and do not provide any code for the HEALPix one.
+Hence, a practical comparison is not possible.
+% % \TK{I would leave out here, as this is a "spoiler" of the results section.}
+% Approaches by \citet{cohen2018spherical,boomsma2017spherical} can not be easily accelerated when the data lies on a part of the sphere only.
+% \nati{Why is \citet{boomsma2017spherical} here? I think it can be trivally accelerated.}
+% That is an important use case in cosmology as measurements are often partial, i.e., full-sky maps are rare.
+% One could still fill the unseen part of the sphere with zeros, and avoid to compute empty integrals, on the latitude or longitude.
+% It is, however, not straightforward to identify those empty directions, and computations would still be wasted; consider, for example, a ring which mostly contains zeros but a few measurements.
+% With graphs however, the computation is done only for the used pixels.
+% This, however, results in some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}).
+% These can be mitigated by padding with zeros a small area around the measurements.
+
+% % In an attempt to get the best of the first two approaches, we follow a third
+% % direction. We use a graph to adapt to the particular structure of the sphere.
+% % While the convolution remains efficient, it still captures well the spherical
+% % structure and is particularly adapted to the HEALPix sampling.
+% % \TK{I am not sure what is the point of this paragraph, we described our approach already before}
+
+% The use of a graph to model the discretised sphere was also considered by~\citet{khasanova2017graphomni}.
+% The authors map omnidirectional images onto a sphere, with the goal of correcting for distortions induced by the lens, which was used for their acquisition.
+% Besides a different practical application, for which the method was designed, there are two important differences.
+% % First, a different sampling scheme is used: \cite{khasanova2017graphomni} uses a grid.
+% First, similarly to~\citet{boomsma2017spherical}, they use an equirectangular grid sampling.
+% % \TK{how is it different from us?}
+% Second, it uses a graph CNN based on a different parameterisation of the convolution kernel.
+% Moreover, they did not take advantage of a hierarchical pixelization of the sphere and resorted to dynamic pooling~\citep{kalchbrenner2014dcnn}.
+% Finally, while the rotation invariance is desirable, the statistical layer used
+% % --- an operation which computes a set of spatially invariant statistics of the last feature map ---
+% % \{TK} this should be explained earlier
+% may not capture the information in an optimal way
+% \todo{and hinders performance (should be empirically verified)}.
+% \TK{This is a strong claim, can we support this?} \nati{It is not that strong as we use "may" right?
+We should probably soften it a bit.
+However the main idea is correct.
+If you compute some statistics on some features, you lose some information and may get worse results.
+Nevertheless, since we are also using a statistical layer, I would juste remove this.}
+% Moreover, the chosen statistics have to be hand-crafted to capture statistics of interest.
+% % While developing completely invariant transforms is a goal worth investigating, CNNs for image recognition, which are arguably the most researched and developed architectures, are not built to be fully invariant to translation.
+% % As with the proposed spherical CNN, the fully connected layers at the end of the network depend on the spatial localization of features.
+% % While that may not be ideal, it was shown to work well in practice.
+% % \TK{The two sentences above look like a tangent to me.. can we skip it an go to the main point, which is I think the fact that we use the stat layer?}
+
+% \todo{In HealpixNet we use the idea of a statistical layer, described in \secref{stat_layer}, to provide invariance to isometric transformations such as translation and rotation on the sphere.
+% \TK{We would need to describe the idea of the statistical layer for the cosmology audience. They don't have a clue what it is.}\nati{Can't they just wait for \secref{stat_layer}? }
+% The use of the statistical layer is optional.
+% In our approach, we are keeping all the statistical moments by retaining a full, learned learned feature histogram, an approach that performed the best in our tests.
+% That is similar to the learnable histogram introduced by \citet{wang2016learnhist}, although for a purpose of integrating global context in object detection and segmentation tasks.
+% \citet{khasanova2017graphomni} uses the mean and variance of diffused versions of the last feature maps in their statistical layer.}
+% \TK{why is this section in TODO?\nati{Probably because, we have not decided if we use the histogram yet. This paragraph needs to be rewritten once we are clear with the code.}}
+
+% There exists many formulations of graph neural networks, reviewed by \citet{bronstein2017review} and \citet{hamilton2017review}.
+For this contribution, we chose the formulation of \citet{defferrard2016convolutional} as its root on strong graph signal processing theory makes the concept of convolutions and filters explicit \citep{shuman2013emerging}.
+Its tie to a graph Fourier transform allows us to compare with the spherical harmonic transform, and study its invariance properties.
+More geometric than permutation invariant aggregation.
+A contrario, formulations with exploit the tengant space of manifolds define a local coordinate system.
+While this formulation of convolution can learn anisotropic filters, it is not equivariant to translation.
+\todo{better wording}
+% \todo{three main interpretations: gsp, Bronstein manifold tangent plane, message passing, permutation invariant aggregation, spatial formulations}
+% Bronstein is a spatial formulation where the registration is done by projection on the tangent plane.
+% % Not Bronstein's manifold approach as we want a Fourier basis to compare to the spherical harmonics.
+% % Be as close as possible to spherical harmonics.
+% Related to this, convolutional neural networks have been defined on manifolds and have achieved impressive results on shapes [Bronstein].
+They however too depend on an orientation, which spheres do not possess.
+
+% % Anisotropic cannot be invariant
+
+% The connection has recently been made between graph CNNs and group equivariant CNNs \cite{kondor2018equivariance}, justifying the use of graphs to gain rotation equivariance on the sphere.
+
+% % In this work, we are using the graph CNN formulation introduced in~\cite{defferrard2016convolutional}.
+
+% Spatial definitions of graph convolutions, e.g.
+[Niepert] needs to define an orientation in order to match the edges with the filters.
+Most often the orientation is not given by the application, and one has to define it (for example by ordering by degree or any other measure, or by using a graph coloring).
+There is no good default good orientation on general graphs and the choice of an orientation is highly application dependent.
+
+\section{Method}
+\label{sec:method}
+% \begin{itemize}
+% 	\item We build a graph using the healpix sampling
+% 	\item Define Fourier transform and show that the harmonics are visually close to the spherical harmonics
+% 	\item Define spherical convolution using the graph Fourier transform and show heat diffusion example
+% 	\item Show the limits of the approach and explain why we cannot have a perfect spherical convolution with this technique
+% \end{itemize}
+
+A CNN is composed of the following main building blocks~\citep{lecun1998cnn}:
+(i) a convolution,
+(ii) a non-linearity,
+(iii) a down-sampling operation,
+(iv) a pooling operation, and
+(v), optionally,  normalization.\footnote{\citet{ioffe2015batchnorm} have shown that batch normalization helps training. We verified this experimentally in our setting as well.}
+Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}.
+As operations (ii) and (v) are point-wise, they do not depend on the data domain.
+The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either.
+The convolution and down-sampling operations however need to be generalized from Euclidean domains to the sphere.
+
+On regular Euclidean domains, such as 1-dimensional time series or 2-dimensional images, a convolution can be efficiently implemented by sliding a localized convolution kernel (for example a patch of 5x5 pixels) in the signal domain.
+Likewise, down-sampling can be achieved by taking one pixel out of $n$.
+Because of the irregular sampling, there is no straightforward way to define a convolution on the sphere directly in the pixel domain; convolutions are most often performed using spherical harmonics.
+In our method we also use the spectral domain to define the convolution.
+The implementation, however, does not need a direct access to the spectrum, which is computationally more efficient (see \secref{efficient_convolution}).
+% We will therefore use the spectral domain to define the convolutions
+% \footnote{Note that we only use the spectrum to define the convolution.
+% The implementation however does not need a direct access to the spectrum, which is computationally much more efficient. See \secref{efficient_convolution}.}
+% \TK{moving footnote to the main text }
+The gist of our method is to define the convolution operation on a sphere using a graph, and the down-sampling operation using a hierarchical pixelisation of the sphere.
+
+\subsection{HEALPix sampling}
+\label{sec:healpix}
+
+\begin{figure*}
+\includegraphics[width=\linewidth]{figures/figure_example_maps.pdf}
+\caption{Exmaple maps on the sphere:
+(left) the CMB temperature (K) map from Planck \citep{planck2015overview}, with galactic plane masked,
+(middle) map of galaxy number counts (number of galaxies per arcmin$^2$) in SDSS DR14 \citep{abolfathi2017sdssDR14},
+and (right) simulated weak lensing convergence map (dimensionless) simulated with DES DR1 mask \citep{des2018dr1}.
+These maps were pixelised using \texttt{nside}=512.
+The CMB and weak lensing mass maps were smoothed with Gaussian kernels with FWHM=1 deg, and the galaxy count map with FWHM=0.5 deg.
+}
+\label{fig:example_maps}
+\end{figure*}
+
+% \begin{figure}
+%     \centering
+%     \begin{subfigure}[b]{0.45\linewidth}
+%         \centering
+%         \includegraphics[width=\linewidth]{exampleEarthTopo}
+%         \caption{}
+%         \label{fig:example_earth}
+%     \end{subfigure}
+%     \hfill
+%     \begin{subfigure}[b]{0.45\linewidth}
+%         \centering
+%         \includegraphics[width=\linewidth]{exampleCMB}
+%         \caption{}
+%         \label{fig:example_cmb}
+%     \end{subfigure}
+%     \caption[]{Example of (a) an Earth topography map composed of \textasciitilde 3 million pixels (\textasciitilde 7 arcmin resolution) and (b) a model of the Cosmic Microwave Background (CMB) radiation temperature anisotropy, composed of \textasciitilde 13 million pixels (\textasciitilde 3.4 arcmin resolution).\footnotemark}
+%     \label{fig:example_maps}
+% \end{figure}
+
+Before doing any numerical analysis on the sphere, one first has to choose a tessellation, i.e., an exhaustive partition of the sphere into finite area elements, where the data under study is quantized.
+The simplicity of the spherical form belies the intricacy of global analysis on the sphere.
+There is no known point set which achieves the analogue of uniform sampling in Euclidean space and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions.
+Any existing proposition of practical schemes for the discrete treatment of such functions on the sphere introduces some systematic error dependent on the global properties of the point set.
+While our method is applicable to any pixelisation of the sphere, two details depend on the chosen sampling: (i) the choice of neighbours in the construction of the graph, and (ii) the choice of parent nodes when coarsening the graph.
+As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology, our target application, we'll tailor the method to that particular sampling in the subsequent exposition.
+%We'll note in later sections where the method should be adapted for a different sampling.
+
+HEALPix is a particular case of a more general class of schemes which are based on a hierarchical subdivision of a base polyhedron.
+%Many discretized maps of the sphere are based on a hierarchical subdivision of a base polyhedron.
+Another example is the geodesic grids which are based on geodesic polyhedrons, i.e., polyhedrons made of triangular faces.
+A counter-example is the equirectangular projection, which is not constructed from a base polyhedron, although it can be subdivided.
+In the particular HEALPix case, the base is a rhombic dodecahedron, i.e., a polyhedron made from 12 congruent rhombic faces.\footnote{A rhombus is a quadrilateral whose four sides all have the same length.}
+See \figref{pooling} for an illustration of the base rhombic dodecahedron and its subdivisions.
+
+HEALPix is an acronym for Hierarchical Equal Area isoLatitude Pixelization of a sphere.
+This pixelisation produces a hierarchical subdivision of a spherical surface where each pixel covers the same surface area as every other pixel.
+A hierarchy is desired for data locality in computer memory.
+Equal area is advantageous because white noise generated by the signal receiver gets integrated exactly into white noise in the pixel space.
+Isolatitude is essential for the implementation of a fast spherical transform.
+HEALPix is the sole pixelisation scheme which satisfies those three properties.
+
+The lowest possible resolution is given by the base partitioning of the surface into $N_{pix} = 12$ equal sized pixels (right-most sphere in \figref{pooling}).
+As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2 \cdot 12 = 2^2 \cdot 12 = 48$ pixels (middle sphere in \figref{pooling}), the third is $N_{pix} = N_{side}^2 \cdot 12 = 4^2 \cdot 12 = 192$ pixels, etc., where $N_{side} = 1, 2, 4, 8, \ldots$ is the grid resolution parameter.
+High-resolutions HEALPix maps easily reach millions of pixels.
+\figref{example_maps} shows two examples of HEALPix maps: the Cosmic Microwave Background \citep{planck2015overview}, galaxies found in Sloan Digital Sky Survey Data Release 14 \citep{abolfathi2017sdssDR14}, and an example simulated mass map on the footprint of Dark Energy Survey Data Release 1 \citep{des2018dr1}.
+
+\subsection{Graph construction}
+
+Our graph is constructed as an approximation of the continuous 2D manifold that is the surface of the sphere.
+Indeed, \citet{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity.
+That construction can accommodate any sampling, regular or not.
+
+From the HEALPix pixelization, we build a weighted undirected graph $\G = (\V, \E, \W)$, where $\V$ is the set of $N_{pix} = |\V|$ nodes, $\E$ is the set of edges, and $\W$ is the weighted adjacency matrix.
+In our graph, each pixel $i$ is represented by a node (also called vertex) $v_i \in \V$.
+Each node $v_i$ is then connected to the $8$ (or $7$)\footnote{\label{neighbors}The $12 \cdot 4 = 48$ pixels at the corner of each rhombus of the base dodecahedron only have 7 neighboring pixels.
+See Figures~\ref{fig:healpix_graph_4} and~\ref{fig:pooling}.} nodes $v_j$ which represent the neighboring pixels $j$ of pixel $i$, forming edges $(v_i, v_j) \in \E$.
+Given those edges, we define the weighted adjacency matrix $\W \in \R^{N_{pix} \times N_{pix}}$ as
+\begin{equation*}
+	\W_{ij} = \begin{cases}
+		\exp \left( -\frac{\|\x_i-\x_j\|_2^2}{\rho^2} \right) & \text{if pixels $i$ and $j$ are neighbors,} \\
+		0 & \text{otherwise,} \\
+	\end{cases}
+\end{equation*}
+where $\x_i$ is a vector encoding the 3-dimensional coordinates of pixel $i$, and
+\begin{equation*}
+	\rho = \frac{1}{|\E|} \sum_{(v_i, v_j) \in \E} \|\x_i-\x_j\|_2
+\end{equation*}
+is the average Euclidean distance over all connected pixels. This weighting scheme is important as distances between pixels are not equal.
+Other weighting schemes are possible.
+For example,~\cite{khasanova2017graphomni} uses the inverse of the distance instead.
+We found out that the one proposed above works well for our purpose, and did not investigate other approaches, leaving it to future work.
+\figref{healpix_graph_4} shows a graph constructed from the HEALPix sampling of a sphere.
+
+% mdeff: Why not $1/d$? See Pascal's paper
+% nati: The question is: is $1/d$ also good when we have 7/8 neighbors instead of 4?
+Practically, we can also use $1/d$, but that means changing the code and re-runing the experiment.
+We probably do not have to change any parameter though...
+@mdeff: do you think we should try this for this paper?
+Or we keep that for the next one.
+% mdeff: I tried and the eigenvectors and eigenvalues are mostly the same.
+To me, there is no point in trying for trying.
+We should rather come up with a definition of distance that will make the eigenvectors closer to the real spherical harmonics.
+% Agreed: I added a reference to Pascal paper.
+
+\subsection{Graph Fourier basis}
+
+Following~\cite{shuman2013emerging}, the normalized graph Laplacian,
+defined as $\L = \I - \D^{-1/2} \W \D^{-1/2}$, is a second order differential operator
+that can be used to define a Fourier basis on the graph. Here $\D$ is the diagonal
+matrix where $\D_{ii} = \b{d}_i$ and $\b{d}_i = \sum_j \W_{ij}$ is the weighted degree of node $v_i$. By construction, the Laplacian is symmetric positive
+semi-definite and hence can be decomposed as $\L = \U \bLambda \U\trans$, where $\U = [\b u_1, \ldots, \b u_{N_{pix}}]$ is an
+orthonormal matrix of eigenvectors and $\bLambda$ is a diagonal matrix of
+eigenvalues. The graph Fourier basis is defined as the Laplacian eigenvectors, motivated by the fact that a Fourier basis should diagonalize the Laplacian operator.
+The graph Fourier transform of a signal $\f \in \R^{N_{pix}}$ is simply its projection on the eigenvectors given by
+$\hat{\f} = \mathcal{F}_\G \{\f\} = \U\trans \f$. It follows that the inverse graph Fourier transform reads $\mathcal{F}^{-1}_\G \{\hat{\f}\} = \U\hat{\f} = \U \U\trans \f = \f$.
+Note that the Fourier modes are ordered in the increasing order of the Laplacian eigenvalues $\bLambda$, which can be interpreted as squared frequencies.
+Indeed,
+\begin{equation*}
+	\bLambda_{ii} = \b u_i\trans \L \b u_i = \sum_{(v_j, v_k) \in \E} \frac{\W_{jk}}{\sqrt{\b d_j \b d_k}} (\U_{ji} - \U_{ki})^2
+\end{equation*}
+is a measure of the variation of the eigenvector $\b u_i$ is on the graph defined by the Laplacian $\L$.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{eigenvectors}
+	\caption{The first 16 eigenvectors of the graph Laplacian, an equivalent of Fourier modes, of a graph constructed from the HEALPix sampling of the sphere.
+    Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$ and order $|m|=(0,1)$, eigenvectors 4--8 with degree $\ell=2$ and order $|m|=(0,1,2)$, and eigenvectors 9--15 with degree $\ell=3$ and order $|m|=(0,1,2,3)$.
+    Nevertheless, the graph eigenvectors are only approximating spherical harmonics.}
+	\label{fig:graph_harmonics}
+\end{figure}
+
+Figure \figref{graph_harmonics} shows the Fourier modes of a HEALPix graph, created using the graph construction described above.
+The graph Fourier modes resemble the spherical harmonics.
+That is a strong hint that the graph is able to capture the spherical properties of the HEALPix sampling.
+This topic is further discussed in \ref{sec:comparison_spherical_harmonics}.
+
+\subsection{Convolution on graphs}
+\label{sec:graph_convolution}
+
+As there is no notion of translation on a graph, we cannot convolve two graph signals in a strict sense.
+We can, however, convolve a signal with a kernel defined in the spectral domain.
+More precisely, we can filter a graph signal by a kernel.
+Given the convolution kernel
+$h: \R_+ \rightarrow \R$, a signal $\f \in \R^{N_{pix}}$ on the graph is filtered as
+\begin{equation} \label{eqn:graph_convolution}
+	h(\L) \f = \U h(\bLambda) \U\trans \f,
+\end{equation}
+where $h(\bLambda)$ is a diagonal matrix where $h(\bLambda)_{ii} = h(\bLambda_{ii})$, and $h(\bLambda) \hat{\f}$ is the spectral representation of $\f$ after filtering.
+
+Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph.
+It can however be localized on any vertex $v_i$ by the convolution with a Kronecker delta $\b \delta_i \in \R^{N_{pix}}$,\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} that is $h(\L) \b \delta_i$, a column of $h(\L)$.
+This localization can be useful to visualize kernels as explained in~\ref{sec:filter_visualization}.
+If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another.
+While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular.
+However, when considering only parts of the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).
+Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with all localizations of the kernel:
+\begin{equation} \label{eqn:graph_convolution_spatial}
+	(h(\L) \f)_i = \langle h(\L) \b \delta_i, \f \rangle.
+\end{equation}
+In \ref{sec:heat_diffusion}, we present an example application of graph-based convolution to a simple heat-diffusion problem in order to shed some light on what is the convolution on a graph.
+% \textbf{Example.}
+% Let us consider the heat diffusion problem
+% \begin{equation} \label{eqn:heat_equation}
+% 	\L \b{f}(t) = \tau \partial_t \b{f}(t),
+% \end{equation}
+% where $\b{f}: \R_+ \rightarrow \R^{N_{pix}}$. Given the initial condition
+% $\b{f}(0)$, the solution of~\eqnref{heat_equation} can be expressed as
+% \begin{equation*}
+% 	\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U\trans \g{f}(0) = K_t(\L) \b{f}(0),
+% \end{equation*}
+% which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(\lambda)=e^{-\tau t \lambda}$.
+Since the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$, which can be interpreted as squared frequencies, it can also be considered as a generalization of the Gaussian kernel on the sphere.
+\figref{gaussian_filters_comparizon} shows the effect of the convolution by diffusing a unit of heat for $\tau=1$ at various times $t$.
+By comparing the graph convolution with the spherical symmetric Gaussian smoothing, we observe that both techniques lead to similar results (see \figref{gaussian_filters_comparizon}).
+While the graph convolution remains different from the spherical convolution, this small experiment shows that, providing the correct parameters, graph convolution can approximate spherical convolution.
+For additional insides about the graph kernel $K_t$, we refer to the \figref{gaussian_filters_visualization} and~\ref{sec:filter_visualization}.
+
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=\linewidth]{gaussian_filters_sphere}
+% 	\caption{Comparison of convolution with the graph and the spherical harmonics ($N_{side} = 16$).
+% 	Top: Diffusion of a unit of heat for different times $t$ using the graph.
+% 	Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin).
+% 	Relative difference between graph convolution and spherical smoothing: $10.4$\%, $4.8$\%, $3.8$\%.
+% \todo{The main issue with our filters is that their shape depends on the localization.
+It would be nice to measure the expectation and variance of the error over all locations.
+That would show how severe the distortion is.}
+% \nati{Let us keep that for the next paper. I am quite sure, it is negligible in this particular case.}}
+% 	\label{fig:gaussian_filters_comparizon}
+% \end{figure}
+
+% Furthermore, this result is another sign that the constructed graph is able to capture the spherical
+% structure of the HEALPix sampling. In some applications, where the
+% exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
+% The fact that both convolutions are not identical is not relevant in a neural network setting, as the convolution kernels are learned anyway.
+% not ideal tho as the graph convolution depends on the localization
+
+\subsection{Efficient convolutions}
+\label{sec:efficient_convolution}
+
+While \eqnref{graph_convolution} is a theoretically well justified definition of the convolution of a graph signal $\f$ by a kernel $h$, it is computationally cumbersome.
+As no general Fast Fourier Transform (FFT) exist for graphs, the execution of the Fourier transform by multiplication of the signal $\f$ by the dense matrix $\U$ costs $\bO(N_{pix}^2)$ operations.
+% \footnote{See \citep{le2018fgft} for a comparison between the polynomial definition of filters presented here and a class of fast graph Fourier transforms based on the approximation of the Fourier basis $\U$ by a product of sparse matrices.}
+%\TK{I would just cite the paper, we have not introduced the polynomials at this stage yet.}
+In a CNN, this operation has to be performed for each training step: forward and backward.
+% As current training procedures are not data-efficient and require a lot of samples, a quadratic computational cost in the sample size is a .
+%\TK{what does "data-efficient mean"? removing for now}
+As current training procedures require processing of many samples, it would be very slow to perform them for a quadratic computational cost in the sample size.
+Moreover, the eigen-decomposition of the Laplacian $\L$ is needed to obtain the Fourier basis $\U$ in the first place.
+That has a unique cost of $\bO(N_{pix}^3)$ operations.
+
+Fortunately, both of these computational issues can be overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parametrised by $K+1$ coefficients $\theta$.
+In that specific case, the filtering operation \eqnref{graph_convolution} becomes
+\begin{equation} \label{eqn:graph_convolution_polynomial}
+	h_\theta(\L) \f =  \U \left(\sum_{k=0}^K \theta_k \bLambda^k \right) \U\trans \f = \sum_{k=0}^K \theta_k \L^k \f,
+\end{equation}
+an operation requiring $k$ multiplications of the graph Laplacian matrix $\L$.
+In our case, the Laplacian is extremly sparse, with $8-9$ entries per line, making the filtering operation for a fixed $K$ linear in the number of pixel $N_{pix}$.
+% Moreover, here happens the transition from filtering in the spectral domain to filtering in the vertex domain.
+This operation is performed in the vertex domain.
+The matrix $\L^k$ captures $k$-neighborhoods of each pixel, i.e., $(\L^k)_{ij}$ is non-zero if and only if nodes $v_i$ and $v_j$ are connected by a path of length $k$.
+As such, filtering with a polynomial convolution kernel can be interpreted in the pixel (vertex) domain as a weighted linear combination of the pixels neighbors values.
+The weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$.
+We note that restricting the graph convolutional kernel to a polynomial is similar to restricting the classical Euclidean signal-domain convolution to a patch.
+In the classical setting, the convolution with a patch is simply a weighted sum of the neighbors with the weights defined by the patch.
+Similarly, each lines of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an "irregular patch of radius $K$" for our irregular domain.
+\todo{Better vertex domain explanation. \nati{I gave it a try. Should we take a single vertex and explain what heppens to it? Note that I suppressed the following paragraph. }}
+\TK{For me it's understandable:)}
+
+% To make the parallel with classical Euclidean signal-domain convolution, i.e., filtering by multiplying the signal with translated versions of a patch, we here match our filter at the level of neighborhoods\footnote{The 1-neighborhood of a node is the set of nodes which are directly connected to it.
+The 2-neighborhood is the set of nodes which are connected through paths of length 2.} rather than individual nodes.
+That is required as there is no notion of ordering in a general graph.
+For example, in a classical convolution on the grid, the relative ordering of vertices is up, down, left, and right.
+There is no such ordering on the sphere either, especially if irregularly sampled.
+
+Following \citet{defferrard2016convolutional}, we define our filters as Chebyshev polynomials such as the convolution operation becomes
+\begin{equation} \label{eqn:graph_convolution_cheby}
+	h_\theta\left(\tL\right) \f = \U \left(\sum_{k=0}^K \theta_k T_k\left(\tilde{\bLambda}\right) \right) \U\trans \f = \sum_{k=0}^K \theta_k T_k\left(\tL\right) \f,
+\end{equation}
+where $\tL = \frac{2}{\lambda_{max}} \L - \b{I} = -\frac{2}{\lambda_{max}} \D^{-1/2} \W \D^{-1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\b \Lambda}$ in $[-1, 1]$ and $T_k(\cdot)$ is the Chebyshev polynomial of degree $k$, defined by the recursive relation $T_k(\tL) = 2\tL T_{k-1}(\tL) - T_{k-2}(\tL)$, $T_1(\tL) = \tL$, $T_0(\tL) = \b{I}$.
+While definitions \eqnref{graph_convolution_polynomial} and \eqnref{graph_convolution_cheby} both allow the representation of the same set of filters, Chebyshev polynomials are preferred as they form an orthogonal basis on the interval $[-1, 1]$.
+Moreover, they factor out $\tL^{k-2}$ from $T_k(\tL)$, e.g., the 3-neighborhood is not mixed with the 5-neighborhood.
+That results in easier learning when optimizing the parameters $\theta$.
+Finally, the coefficients can be computed such as the truncated Chebyshev expansions gives an approximate minimax polynomial of a given filter \citep{hammond2011wavelets}.
+While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
+In practice, we found out in our experiment that Chebyshev polynomials are slightly more stable than the monomials used in~\cite{khasanova2017graphomni}(i.e.
+optimizing directly the $\theta_k$ in \eqnref{graph_convolution_polynomial}).
+We believe that this is due to their orthogonality (as explained above) and uniformity\footnote{The amplitude of Chebyshev polynomials is more or less constant over the domain $[-1, 1]$ independently of the order $k$.
+On the contrary the amplitude of $x^k$ is very different for $|x|\approx 0$ and $|x| \approx 1$.}.
+\nati{I added a sentence and I think we should not give much more details here. If we do an experiment, we can comment in the experiment section.}
+\todo{(i) scale of $\theta_k$: they are mostly uniform for Chebyshev polynomials, end exploding for monomials. Though SGD implicitly imposes a uniform prior on the learned parameters.}
+\todo{(ii) numerical stability of $\L^k \f$ v.s. $T_k(\L) \f$}
+\todo{(iii) in the code, initialize $\theta_k$ with stdev adapted to $F_{in}$ and $K$}
+
+Exploiting the recursive formulation of Chebyshev polynomials, evaluating \eqnref{graph_convolution_cheby} requires $\bO(K)$ multiplications of the dense vector $\f$ with the sparse matrix $\tL$.
+The cost of one such multiplication is $\bO(|\E|)$. By construction of our graph, $|\E| < 8 N_{pix}$ and the overall computational cost of the convolution is thus reduced to $\bO(N_{pix})$ operations.
+That is much more efficient than filtering with spherical harmonics, even tho the HEALPix was designed as an iso-latitude sampling to leverage a fast spherical transform.
+That is especially true for smooth kernels which require a low polynomial degree $K$.
+\figref{filtering_speed} demonstrates the speed comparison of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
+The performance of our approach is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{filtering_speed}
+	\caption{Comparison of filtering speed for Gaussian smoothing of maps of various sizes.
+    The fast spherical harmonic transform (SHT) is implemented by the \texttt{healpy} Python package (via the \texttt{healpy.sphtfunc.smoothing} function with $\ell_{max} = 3 N_{side} - 1$, the default).
+    The graph filtering is defined by \eqnref{graph_convolution_cheby} and implemented with the \texttt{numpy} and \texttt{scipy} Python packages.
+    Both are executed on a single core.
+    The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3)$ for the spherical harmonics, where $\ell_{max}$ is the largest degree (i.e., the spectrum is truncated at $\ell_{max}$).}
+	\label{fig:filtering_speed}
+\end{figure}
+
+\subsection{Coarsening and Pooling}
+
+Coarsening can be naturally designed for hierarchical pixelisation schemes, as each subdivision divides a cell in an equal number of child sub-cells.
+Coarsening is the reverse operation: merging the sub-cells toward the goal of summarizing the data supported on them.
+Merging cells lead to a coarser graph.
+Coarsening defines $\C(i)$, the set of children of node $v_i$.
+For the HEALPix subdivision scheme, the number of children is constant, i.e., $| \C(i) | = 4^p \ \forall i$, for some $p$.
+
+Pooling refers to the operation that summarizes the data supported on the merged sub-cells in one parent cell.
+Given a map $\x \in \R^{N_{pix}}$, pooling defines $\y \in \R^{N'_{pix}}$ such as
+\begin{equation} \label{eqn:pooling}
+	y_i = f \left( \left\{ x_j : j \in \C(i) \right\} \right), \ \forall i \in [N'_{pix}],
+\end{equation}
+where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix} / {N'_{pix}}$ is the down-sampling factor, which for HEALPix is $| \C(i) | = N_{pix} / {N_{pix}}' = (N_{side} / N'_{side})^2 = 4^p$.
+That operation is often taken to be the maximum value, but it can be any permutation invariant operation, such as a sum or an average.
+\figref{pooling} illustrates the process.
+
+% The advantage of schemes based on a base polyhedron is that cells are equal-area.
+While that is not required for the convolution operation when modeling with graphs (it can be corrected by setting edge weights appropriately, see \citet{khasanova2017graphomni})
+% nope: can also do a regular pooling on the equirectangular. It preserves the sampling, and the convolution is adapted to the sampling thanks to the edge weights.
+
+\begin{figure}
+	\centering
+    % \includegraphics[width=\linewidth]{pooling}
+	\includegraphics[trim=1.1cm 0cm 0cm 0cm, width=\linewidth]{figures/figure_pooling_svg.pdf}
+	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarsest cell covers $1/12$ of the sphere.}
+	\label{fig:pooling}
+\end{figure}
+
+\subsection{Statistical layer}
+\label{sec:stat_layer}
+% Or Global pooling?
+
+Following \citet{khasanova2017tigranet}, we implement an optional statistical layer between the last graph convolutional layer and the first fully connected layer for the neural network.
+This introduces the invariance of the output to isometric transformations, such as rotation and translation of maps on the sphere.
+The role of the layer is to compute global and location independent statistics from feature maps.
+Besides providing invariance, the layer drastically compresses the representation of the data as the number of computed statistics $N_{stat}$ is usually much smaller than the size of the map $N_{pix}$.
+That compression results in much smaller fully connected layers, which usually contain a significant fraction of trainable parameters of a neural network.
+The invariance and reduced representation should help the network to learn from less samples and to generalize better to unseen data.
+Yet another advantage is that a network built with such a statistical layer is agnostic to the size of the input data, i.e., it can classify maps which do not have the same number of pixels.
+Indeed, such global summarization is invariant to node permutation and is commonly used along graph convolutions to classify graphs of varying sizes \citep{duvenaud2015gcn, li2015gatedgnn}.
+
+Given a feature map $\x \in \R^{N_{pix}}$, the statistical layer is defined as
+\begin{equation} \label{eqn:stat_layer}
+	\y = f(\x) \in \R^{N_{stat}},
+\end{equation}
+where $f$ computes $N_{stat}$ statistics which are independent from the size of the map, $N_{pix}$.
+An example is the global average pooling $f(\x) = \esp(\x)$, introduced by \citet{lin2013globalavgpooling}, where $\esp(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} x_i$ is the empirical mean.
+Another example is $f(\x) = [\esp(\x), \var(\x)]\trans$, where $\var(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} (x_i - \esp(\x))^2$ is the empirical variance.
+Other statistical layers are also possible.
+In particular, we also implement a \emph{learned histogram} statistic \citep{wang2016learnhist}.
+Other approaches, which we did not implement, may include applying different diffusion on the final maps to obtain statistics at different scales, as proposed by \citep{khasanova2017tigranet}.
+
+\subsection{Graph convolutional neural network}
+\label{sec:architecture}
+
+Neural networks are constructed as stacks of layers which sequentially transform the data from its raw representation to a decision on the class label.
+Our architecture, pictured in \figref{architecture}, is composed of many layers.
+The convolutional part, the head of the neural network, is composed of graph convolutional layers (GC), pooling layers (P), and batch normalization layers (BN).
+The tail is composed of multiple fully connected layers (FC) followed by a softmax layer (SM).
+A statistical layer (ST) is optionally inserted between the convolutional head and the fully connected tail.
+
+% As such, we will not mention the non-linearity in the description of our architectures.
+A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer where it is set to the identity.
+That operation is point-wise, i.e., $y_{ij} = \sigma(x_{ij})$ and $y_i = \sigma(x_i)$ for matrices $\X, \Y$ and vectors $\x, \y$.
+The rectified linear unit (ReLU) $\sigma(\cdot) = \max(\cdot, 0)$ is a common choice.
+
+Given a matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$, a GC layer computes $\Y = GC(\X) = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels (and nodes), $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
+Using the efficient graph convolution from \eqnref{graph_convolution_cheby}, each output feature map is computed as
+\begin{equation*}
+	\y_i = \sum_{j=1}^{F_{in}} h_{\theta_{ij}}(\tL) \x_j + b_i \in \R^{N_{pix}}, \ \ \forall i \in [F_{out}].
+\end{equation*}
+As such, a GC layer is composed of $F_{in} \cdot F_{out}$ filters, each parameterized by $K$ numbers (see \secref{efficient_convolution}). A bias term $\b b \in \R^{F_{out}}$ is jointly optimized.
+% only if batch normalization is not used
+
+Given a matrix $\X \in \R^{N_{pix} \times F}$, a pooling layer computes $\Y = P(\X) \in \R^{N'_{pix} \times F}$ by reducing its spatial resolution ($N'_{pix} < N_{pix}$) according to \eqnref{pooling}.
+% Given a matrix $\X \in \R^{N_{pix} \times F}$,
+The batch normalization layer \citep{ioffe2015batchnorm} computes $\Y = BN(\X)$ such as
+\begin{equation*}
+	\y_i = \gamma_i \frac{\x_i - \esp(\x_i)}{\sqrt{\var(\x_i) + \epsilon}} + \beta_i, \ \forall i \in [F],
+\end{equation*}
+where $\gamma_{j}$ and $\beta_{j}$ are parameters to be learned and $\epsilon$ is a constant added for numerical stability.
+The empirical expectation $\esp(\x_i) \in \R$ and variance $\var(\x_i) \in \R$ are taken across training examples and pixels.
+% the action of gamma can be done by the filters of the next layer
+
+The statistical layer, defined in \eqnref{stat_layer}, independently transforms each of the $F$ feature maps of the input $\X \in \R^{N_{pix} \times F}$ into $\Y = ST(\X) \in \R^{N_{stat} \times F}$, where $N_{stat}$ is the number of statistics.
+One may even omit the FC layers and directly fed the output of the ST layer into the softmax layer, as proposed by \citet{lin2013globalavgpooling}.
+In this regime, $N_{stat} = 1$ and $F = N_{classes}$ is the number of classes to discriminate (i.e., the last GC layer outputs as many feature maps as there is classes).
+
+A FC layer takes as input $\x \in \R^{F_{in}}$ and outputs
+\begin{equation*}
+	\y = FC(\x) = \b W \x + \b b \in \R^{F_{out}} ,
+\end{equation*}
+where $\W \in \R^{F_{out} \times F_{in}}$ and $\b b \in \R^{F_{out}}$ are the parameters to be learned.
+Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last GC (or the output $\Y \in \R^{N_{stat} \times F_{out}}$ of the ST), is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first FC, where $F_{in} = N_{pix} \cdot F_{out}$ (or $N_{stat} \cdot F_{out}$).
+
+The softmax layer is the last layer in a neural network engineered for classification.
+Given the output $\x \in \R^{N_{classes}}$ of the last FC (or ST), called the logits in the deep learning literature, the softmax layer outputs $\y = SM(\x)$ such that
+\begin{equation*}
+	y_i = \frac{\exp(x_i)}{\sum_{j=1}^{N_{classes}} \exp(x_j)} \in [0, 1], \ \forall i \in [N_{classes}],
+\end{equation*}
+where $N_{classes}$ is the number of classes to discriminate.
+Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the probability that the input sample belongs to class $i$.
+This last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.
+
+Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
+An example network is
+\begin{equation*}
+NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC,
+\end{equation*}
+where $\circ$ denotes composition, i.e., $f \circ g = f(g(\cdot))$.
+The number of features $F$ depends on the data at hand.
+For the CMB radiation temperature, $F = 1$.
+For observations in radio frequencies, $F$ would be equal to the number of surveyed frequencies.
+$F$ might also be the number of slices in the radial direction.
+The loss function $\ell(\y) = \ell(NN_\theta(\X))$ is a measure of how good the prediction $\y$ is for the sample $\X$. For a classification task, the loss is usually taken to be the cross-entropy
+\begin{equation*}
+	\ell(\y) = -\log(y_i),
+\end{equation*}
+where $i$ is the correct class label.
+The parameters $\theta$ of the neural network are optimized to minimize the loss over the training dataset $\left\{ \X_i \right\}_{i=1}^{N_{samples}}$:
+\begin{equation*}
+	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell(NN_\theta(\X_i)).
+\end{equation*}
+The same architecture with different loss function can also be used for parameter regression \citep{fluri2018deep,gupta2018nongaussianinformation}.
+The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
+\begin{equation*}
+	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
+\end{equation*}
+where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch.
+Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.
+
+\todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
 
@@
 % \TK{I would leave out here, as this is a "spoiler" of the results section.}
+
 Approaches by \citet{cohen2018spherical,boomsma2017spherical} can not be easily accelerated when the data lies on a part of the sphere only.
+
 \nati{Why is \citet{boomsma2017spherical} here? I think it can be trivally accelerated.}
@@
 
-\section{Method}
-\label{sec:method}
-% \begin{itemize}
-% 	\item We build a graph using the healpix sampling
-% 	\item Define Fourier transform and show that the harmonics are visually close to the spherical harmonics
-% 	\item Define spherical convolution using the graph Fourier transform and show heat diffusion example
-% 	\item Show the limits of the approach and explain why we cannot have a perfect spherical convolution with this technique
-% \end{itemize}
-
-A CNN is composed of the following main building blocks~\citep{lecun1998cnn}:
-(i) a convolution,
-(ii) a non-linearity,
-(iii) a down-sampling operation,
-(iv) a pooling operation, and
-(v), optionally,  normalization.\footnote{\citet{ioffe2015batchnorm} have shown that batch normalization helps training. We verified this experimentally in our setting as well.}
-Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}.
-As operations (ii) and (v) are point-wise, they do not depend on the data domain.
-The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either.
-The convolution and down-sampling operations however need to be generalized from Euclidean domains to the sphere.
-
-On regular Euclidean domains, such as 1-dimensional time series or 2-dimensional images, a convolution can be efficiently implemented by sliding a localized convolution kernel (for example a patch of 5x5 pixels) in the signal domain.
-Likewise, down-sampling can be achieved by taking one pixel out of $n$.
-Because of the irregular sampling, there is no straightforward way to define a convolution on the sphere directly in the pixel domain; convolutions are most often performed using spherical harmonics.
-In our method we also use the spectral domain to define the convolution.
-The implementation, however, does not need a direct access to the spectrum, which is computationally more efficient (see \secref{efficient_convolution}).
-% We will therefore use the spectral domain to define the convolutions
-% \footnote{Note that we only use the spectrum to define the convolution.
-% The implementation however does not need a direct access to the spectrum, which is computationally much more efficient. See \secref{efficient_convolution}.}
-% \TK{moving footnote to the main text }
-The gist of our method is to define the convolution operation on a sphere using a graph, and the down-sampling operation using a hierarchical pixelisation of the sphere.
-
-\subsection{HEALPix sampling}
-\label{sec:healpix}
-
-\begin{figure*}
-\includegraphics[width=\linewidth]{figures/figure_example_maps.pdf}
-\caption{Exmaple maps on the sphere:
-(left) the CMB temperature (K) map from Planck \citep{planck2015overview}, with galactic plane masked,
-(middle) map of galaxy number counts (number of galaxies per arcmin$^2$) in SDSS DR14 \citep{abolfathi2017sdssDR14},
-and (right) simulated weak lensing convergence map (dimensionless) simulated with DES DR1 mask \citep{des2018dr1}.
-These maps were pixelised using \texttt{nside}=512.
-The CMB and weak lensing mass maps were smoothed with Gaussian kernels with FWHM=1 deg, and the galaxy count map with FWHM=0.5 deg.
-}
-\label{fig:example_maps}
-\end{figure*}
-
-% \begin{figure}
-%     \centering
-%     \begin{subfigure}[b]{0.45\linewidth}
-%         \centering
-%         \includegraphics[width=\linewidth]{exampleEarthTopo}
-%         \caption{}
-%         \label{fig:example_earth}
-%     \end{subfigure}
-%     \hfill
-%     \begin{subfigure}[b]{0.45\linewidth}
-%         \centering
-%         \includegraphics[width=\linewidth]{exampleCMB}
-%         \caption{}
-%         \label{fig:example_cmb}
-%     \end{subfigure}
-%     \caption[]{Example of (a) an Earth topography map composed of \textasciitilde 3 million pixels (\textasciitilde 7 arcmin resolution) and (b) a model of the Cosmic Microwave Background (CMB) radiation temperature anisotropy, composed of \textasciitilde 13 million pixels (\textasciitilde 3.4 arcmin resolution).\footnotemark}
-%     \label{fig:example_maps}
-% \end{figure}
-
-Before doing any numerical analysis on the sphere, one first has to choose a tessellation, i.e., an exhaustive partition of the sphere into finite area elements, where the data under study is quantized.
-The simplicity of the spherical form belies the intricacy of global analysis on the sphere.
-There is no known point set which achieves the analogue of uniform sampling in Euclidean space and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions.
-Any existing proposition of practical schemes for the discrete treatment of such functions on the sphere introduces some systematic error dependent on the global properties of the point set.
-While our method is applicable to any pixelisation of the sphere, two details depend on the chosen sampling: (i) the choice of neighbours in the construction of the graph, and (ii) the choice of parent nodes when coarsening the graph.
-As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology, our target application, we'll tailor the method to that particular sampling in the subsequent exposition.
-%We'll note in later sections where the method should be adapted for a different sampling.
-
-HEALPix is a particular case of a more general class of schemes which are based on a hierarchical subdivision of a base polyhedron.
-%Many discretized maps of the sphere are based on a hierarchical subdivision of a base polyhedron.
-Another example is the geodesic grids which are based on geodesic polyhedrons, i.e., polyhedrons made of triangular faces.
-A counter-example is the equirectangular projection, which is not constructed from a base polyhedron, although it can be subdivided.
-In the particular HEALPix case, the base is a rhombic dodecahedron, i.e., a polyhedron made from 12 congruent rhombic faces.\footnote{A rhombus is a quadrilateral whose four sides all have the same length.}
-See \figref{pooling} for an illustration of the base rhombic dodecahedron and its subdivisions.
-
-HEALPix is an acronym for Hierarchical Equal Area isoLatitude Pixelization of a sphere.
-This pixelisation produces a hierarchical subdivision of a spherical surface where each pixel covers the same surface area as every other pixel.
-A hierarchy is desired for data locality in computer memory.
-Equal area is advantageous because white noise generated by the signal receiver gets integrated exactly into white noise in the pixel space.
-Isolatitude is essential for the implementation of a fast spherical transform.
-HEALPix is the sole pixelisation scheme which satisfies those three properties.
-
-The lowest possible resolution is given by the base partitioning of the surface into $N_{pix} = 12$ equal sized pixels (right-most sphere in \figref{pooling}).
-As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2 \cdot 12 = 2^2 \cdot 12 = 48$ pixels (middle sphere in \figref{pooling}), the third is $N_{pix} = N_{side}^2 \cdot 12 = 4^2 \cdot 12 = 192$ pixels, etc., where $N_{side} = 1, 2, 4, 8, \ldots$ is the grid resolution parameter.
-High-resolutions HEALPix maps easily reach millions of pixels.
-\figref{example_maps} shows two examples of HEALPix maps: the Cosmic Microwave Background \citep{planck2015overview} and \TK{update}.
-
-\subsection{Graph construction}
-
-Our graph is constructed as an approximation of the continuous 2D manifold that is the surface of the sphere.
-Indeed, \citet{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity.
-That construction can accommodate any sampling, regular or not.
-
-From the HEALPix pixelization, we build a weighted undirected graph $\G = (\V, \E, \W)$, where $\V$ is the set of $N_{pix} = |\V|$ nodes, $\E$ is the set of edges, and $\W$ is the weighted adjacency matrix.
-In our graph, each pixel $i$ is represented by a node (also called vertex) $v_i \in \V$.
-Each node $v_i$ is then connected to the $8$ (or $7$)\footnote{\label{neighbors}The $12 \cdot 4 = 48$ pixels at the corner of each rhombus of the base dodecahedron only have 7 neighboring pixels.
-See Figures~\ref{fig:healpix_graph_4} and~\ref{fig:pooling}.} nodes $v_j$ which represent the neighboring pixels $j$ of pixel $i$, forming edges $(v_i, v_j) \in \E$.
-Given those edges, we define the weighted adjacency matrix $\W \in \R^{N_{pix} \times N_{pix}}$ as
-\begin{equation*}
-	\W_{ij} = \begin{cases}
-		\exp \left( -\frac{\|\x_i-\x_j\|_2^2}{\rho^2} \right) & \text{if pixels $i$ and $j$ are neighbors,} \\
-		0 & \text{otherwise,} \\
-	\end{cases}
-\end{equation*}
-where $\x_i$ is a vector encoding the 3-dimensional coordinates of pixel $i$, and
-\begin{equation*}
-	\rho = \frac{1}{|\E|} \sum_{(v_i, v_j) \in \E} \|\x_i-\x_j\|_2
-\end{equation*}
-is the average Euclidean distance over all connected pixels. This weighting scheme is important as distances between pixels are not equal.
-Other weighting schemes are possible.
-For example,~\cite{khasanova2017graphomni} uses the inverse of the distance instead.
-We found out that the one proposed above works well for our purpose, and did not investigate other approaches, leaving it to future work.
-\figref{healpix_graph_4} shows a graph constructed from the HEALPix sampling of a sphere.
-
-% mdeff: Why not $1/d$? See Pascal's paper
-% nati: The question is: is $1/d$ also good when we have 7/8 neighbors instead of 4?
-Practically, we can also use $1/d$, but that means changing the code and re-runing the experiment.
-We probably do not have to change any parameter though...
-@mdeff: do you think we should try this for this paper?
-Or we keep that for the next one.
-% mdeff: I tried and the eigenvectors and eigenvalues are mostly the same.
-To me, there is no point in trying for trying.
-We should rather come up with a definition of distance that will make the eigenvectors closer to the real spherical harmonics.
-% Agreed: I added a reference to Pascal paper.
-
-\subsection{Graph Fourier basis}
-
-Following~\cite{shuman2013emerging}, the normalized graph Laplacian,
-defined as $\L = \I - \D^{-1/2} \W \D^{-1/2}$, is a second order differential operator
-that can be used to define a Fourier basis on the graph. Here $\D$ is the diagonal
-matrix where $\D_{ii} = \b{d}_i$ and $\b{d}_i = \sum_j \W_{ij}$ is the weighted degree of node $v_i$. By construction, the Laplacian is symmetric positive
-semi-definite and hence can be decomposed as $\L = \U \bLambda \U\trans$, where $\U = [\b u_1, \ldots, \b u_{N_{pix}}]$ is an
-orthonormal matrix of eigenvectors and $\bLambda$ is a diagonal matrix of
-eigenvalues. The graph Fourier basis is defined as the Laplacian eigenvectors, motivated by the fact that a Fourier basis should diagonalize the Laplacian operator.
-The graph Fourier transform of a signal $\f \in \R^{N_{pix}}$ is simply its projection on the eigenvectors given by
-$\hat{\f} = \mathcal{F}_\G \{\f\} = \U\trans \f$. It follows that the inverse graph Fourier transform reads $\mathcal{F}^{-1}_\G \{\hat{\f}\} = \U\hat{\f} = \U \U\trans \f = \f$.
-Note that the Fourier modes are ordered in the increasing order of the Laplacian eigenvalues $\bLambda$, which can be interpreted as squared frequencies.
-Indeed,
-\begin{equation*}
-	\bLambda_{ii} = \b u_i\trans \L \b u_i = \sum_{(v_j, v_k) \in \E} \frac{\W_{jk}}{\sqrt{\b d_j \b d_k}} (\U_{ji} - \U_{ki})^2
-\end{equation*}
-is a measure of the variation of the eigenvector $\b u_i$ is on the graph defined by the Laplacian $\L$.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{eigenvectors}
-	\caption{The first 16 eigenvectors of the graph Laplacian, an equivalent of Fourier modes, of a graph constructed from the HEALPix sampling of the sphere.
-    Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$ and order $|m|=(0,1)$, eigenvectors 4--8 with degree $\ell=2$ and order $|m|=(0,1,2)$, and eigenvectors 9--15 with degree $\ell=3$ and order $|m|=(0,1,2,3)$.
-    Nevertheless, the graph eigenvectors are only approximating spherical harmonics.}
-	\label{fig:graph_harmonics}
-\end{figure}
-
-Figure \figref{graph_harmonics} shows the Fourier modes of a HEALPix graph, created using the graph construction described above.
-The graph Fourier modes resemble the spherical harmonics.
-That is a strong hint that the graph is able to capture the spherical properties of the HEALPix sampling.
-This topic is further discussed in \ref{sec:comparison_spherical_harmonics}.
-
-\subsection{Convolution on graphs}
-\label{sec:graph_convolution}
-
-As there is no notion of translation on a graph, we cannot convolve two graph signals in a strict sense.
-We can, however, convolve a signal with a kernel defined in the spectral domain.
-More precisely, we can filter a graph signal by a kernel.
-Given the convolution kernel
-$h: \R_+ \rightarrow \R$, a signal $\f \in \R^{N_{pix}}$ on the graph is filtered as
-\begin{equation} \label{eqn:graph_convolution}
-	h(\L) \f = \U h(\bLambda) \U\trans \f,
-\end{equation}
-where $h(\bLambda)$ is a diagonal matrix where $h(\bLambda)_{ii} = h(\bLambda_{ii})$, and $h(\bLambda) \hat{\f}$ is the spectral representation of $\f$ after filtering.
-
-Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph.
-It can however be localized on any vertex $v_i$ by the convolution with a Kronecker delta $\b \delta_i \in \R^{N_{pix}}$,\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} that is $h(\L) \b \delta_i$, a column of $h(\L)$.
-This localization can be useful to visualize kernels as explained in~\ref{sec:filter_visualization}.
-If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another.
-While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular.
-However, when considering only parts of the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).
-Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with all localizations of the kernel:
-\begin{equation} \label{eqn:graph_convolution_spatial}
-	(h(\L) \f)_i = \langle h(\L) \b \delta_i, \f \rangle.
-\end{equation}
-In \ref{sec:heat_diffusion}, we present an example application of graph-based convolution to a simple heat-diffusion problem in order to shed some light on what is the convolution on a graph.
-% \textbf{Example.}
-% Let us consider the heat diffusion problem
-% \begin{equation} \label{eqn:heat_equation}
-% 	\L \b{f}(t) = \tau \partial_t \b{f}(t),
-% \end{equation}
-% where $\b{f}: \R_+ \rightarrow \R^{N_{pix}}$. Given the initial condition
-% $\b{f}(0)$, the solution of~\eqnref{heat_equation} can be expressed as
-% \begin{equation*}
-% 	\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U\trans \g{f}(0) = K_t(\L) \b{f}(0),
-% \end{equation*}
-% which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(\lambda)=e^{-\tau t \lambda}$.
-Since the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$, which can be interpreted as squared frequencies, it can also be considered as a generalization of the Gaussian kernel on the sphere.
-\figref{gaussian_filters_comparizon} shows the effect of the convolution by diffusing a unit of heat for $\tau=1$ at various times $t$.
-By comparing the graph convolution with the spherical symmetric Gaussian smoothing, we observe that both techniques lead to similar results (see \figref{gaussian_filters_comparizon}).
-While the graph convolution remains different from the spherical convolution, this small experiment shows that, providing the correct parameters, graph convolution can approximate spherical convolution.
-For additional insides about the graph kernel $K_t$, we refer to the \figref{gaussian_filters_visualization} and~\ref{sec:filter_visualization}.
-
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=\linewidth]{gaussian_filters_sphere}
-% 	\caption{Comparison of convolution with the graph and the spherical harmonics ($N_{side} = 16$).
-% 	Top: Diffusion of a unit of heat for different times $t$ using the graph.
-% 	Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin).
-% 	Relative difference between graph convolution and spherical smoothing: $10.4$\%, $4.8$\%, $3.8$\%.
-% \todo{The main issue with our filters is that their shape depends on the localization.
-It would be nice to measure the expectation and variance of the error over all locations.
-That would show how severe the distortion is.}
-% \nati{Let us keep that for the next paper. I am quite sure, it is negligible in this particular case.}}
-% 	\label{fig:gaussian_filters_comparizon}
-% \end{figure}
-
-% Furthermore, this result is another sign that the constructed graph is able to capture the spherical
-% structure of the HEALPix sampling. In some applications, where the
-% exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
-% The fact that both convolutions are not identical is not relevant in a neural network setting, as the convolution kernels are learned anyway.
-% not ideal tho as the graph convolution depends on the localization
-
-\subsection{Efficient convolutions}
-\label{sec:efficient_convolution}
-
-While \eqnref{graph_convolution} is a theoretically well justified definition of the convolution of a graph signal $\f$ by a kernel $h$, it is computationally cumbersome.
-As no general Fast Fourier Transform (FFT) exist for graphs, the execution of the Fourier transform by multiplication of the signal $\f$ by the dense matrix $\U$ costs $\bO(N_{pix}^2)$ operations.
-% \footnote{See \citep{le2018fgft} for a comparison between the polynomial definition of filters presented here and a class of fast graph Fourier transforms based on the approximation of the Fourier basis $\U$ by a product of sparse matrices.}
-%\TK{I would just cite the paper, we have not introduced the polynomials at this stage yet.}
-In a CNN, this operation has to be performed for each training step: forward and backward.
-% As current training procedures are not data-efficient and require a lot of samples, a quadratic computational cost in the sample size is a .
-%\TK{what does "data-efficient mean"? removing for now}
-As current training procedures require processing of many samples, it would be very slow to perform them for a quadratic computational cost in the sample size.
-Moreover, the eigen-decomposition of the Laplacian $\L$ is needed to obtain the Fourier basis $\U$ in the first place.
-That has a unique cost of $\bO(N_{pix}^3)$ operations.
-
-Fortunately, both of these computational issues can be overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parametrised by $K+1$ coefficients $\theta$.
-In that specific case, the filtering operation \eqnref{graph_convolution} becomes
-\begin{equation} \label{eqn:graph_convolution_polynomial}
-	h_\theta(\L) \f =  \U \left(\sum_{k=0}^K \theta_k \bLambda^k \right) \U\trans \f = \sum_{k=0}^K \theta_k \L^k \f,
-\end{equation}
-an operation requiring $k$ multiplications of the graph Laplacian matrix $\L$.
-In our case, the Laplacian is extremly sparse, with $8-9$ entries per line, making the filtering operation for a fixed $K$ linear in the number of pixel $N_{pix}$.
-% Moreover, here happens the transition from filtering in the spectral domain to filtering in the vertex domain.
-This operation is performed in the vertex domain.
-The matrix $\L^k$ captures $k$-neighborhoods of each pixel, i.e., $(\L^k)_{ij}$ is non-zero if and only if nodes $v_i$ and $v_j$ are connected by a path of length $k$.
-As such, filtering with a polynomial convolution kernel can be interpreted in the pixel (vertex) domain as a weighted linear combination of the pixels neighbors values.
-The weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$.
-We note that restricting the graph convolutional kernel to a polynomial is similar to restricting the classical Euclidean signal-domain convolution to a patch.
-In the classical setting, the convolution with a patch is simply a weighted sum of the neighbors with the weights defined by the patch.
-Similarly, each lines of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an "irregular patch of radius $K$" for our irregular domain.
-\todo{Better vertex domain explanation. \nati{I gave it a try. Should we take a single vertex and explain what heppens to it? Note that I suppressed the following paragraph. }}
-\TK{For me it's understandable:)}
-
-% To make the parallel with classical Euclidean signal-domain convolution, i.e., filtering by multiplying the signal with translated versions of a patch, we here match our filter at the level of neighborhoods\footnote{The 1-neighborhood of a node is the set of nodes which are directly connected to it.
-The 2-neighborhood is the set of nodes which are connected through paths of length 2.} rather than individual nodes.
-That is required as there is no notion of ordering in a general graph.
-For example, in a classical convolution on the grid, the relative ordering of vertices is up, down, left, and right.
-There is no such ordering on the sphere either, especially if irregularly sampled.
-
-Following \citet{defferrard2016convolutional}, we define our filters as Chebyshev polynomials such as the convolution operation becomes
-\begin{equation} \label{eqn:graph_convolution_cheby}
-	h_\theta\left(\tL\right) \f = \U \left(\sum_{k=0}^K \theta_k T_k\left(\tilde{\bLambda}\right) \right) \U\trans \f = \sum_{k=0}^K \theta_k T_k\left(\tL\right) \f,
-\end{equation}
-where $\tL = \frac{2}{\lambda_{max}} \L - \b{I} = -\frac{2}{\lambda_{max}} \D^{-1/2} \W \D^{-1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\b \Lambda}$ in $[-1, 1]$ and $T_k(\cdot)$ is the Chebyshev polynomial of degree $k$, defined by the recursive relation $T_k(\tL) = 2\tL T_{k-1}(\tL) - T_{k-2}(\tL)$, $T_1(\tL) = \tL$, $T_0(\tL) = \b{I}$.
-While definitions \eqnref{graph_convolution_polynomial} and \eqnref{graph_convolution_cheby} both allow the representation of the same set of filters, Chebyshev polynomials are preferred as they form an orthogonal basis on the interval $[-1, 1]$.
-Moreover, they factor out $\tL^{k-2}$ from $T_k(\tL)$, e.g., the 3-neighborhood is not mixed with the 5-neighborhood.
-That results in easier learning when optimizing the parameters $\theta$.
-Finally, the coefficients can be computed such as the truncated Chebyshev expansions gives an approximate minimax polynomial of a given filter \citep{hammond2011wavelets}.
-While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
-In practice, we found out in our experiment that Chebyshev polynomials are slightly more stable than the monomials used in~\cite{khasanova2017graphomni}(i.e.
-optimizing directly the $\theta_k$ in \eqnref{graph_convolution_polynomial}).
-We believe that this is due to their orthogonality (as explained above) and uniformity\footnote{The amplitude of Chebyshev polynomials is more or less constant over the domain $[-1, 1]$ independently of the order $k$.
-On the contrary the amplitude of $x^k$ is very different for $|x|\approx 0$ and $|x| \approx 1$.}.
-\nati{I added a sentence and I think we should not give much more details here. If we do an experiment, we can comment in the experiment section.}
-\todo{(i) scale of $\theta_k$: they are mostly uniform for Chebyshev polynomials, end exploding for monomials. Though SGD implicitly imposes a uniform prior on the learned parameters.}
-\todo{(ii) numerical stability of $\L^k \f$ v.s. $T_k(\L) \f$}
-\todo{(iii) in the code, initialize $\theta_k$ with stdev adapted to $F_{in}$ and $K$}
-
-Exploiting the recursive formulation of Chebyshev polynomials, evaluating \eqnref{graph_convolution_cheby} requires $\bO(K)$ multiplications of the dense vector $\f$ with the sparse matrix $\tL$.
-The cost of one such multiplication is $\bO(|\E|)$. By construction of our graph, $|\E| < 8 N_{pix}$ and the overall computational cost of the convolution is thus reduced to $\bO(N_{pix})$ operations.
-That is much more efficient than filtering with spherical harmonics, even tho the HEALPix was designed as an iso-latitude sampling to leverage a fast spherical transform.
-That is especially true for smooth kernels which require a low polynomial degree $K$.
-\figref{filtering_speed} demonstrates the speed comparison of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
-The performance of our approach is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{filtering_speed}
-	\caption{Comparison of filtering speed for Gaussian smoothing of maps of various sizes.
-    The fast spherical harmonic transform (SHT) is implemented by the \texttt{healpy} Python package (via the \texttt{healpy.sphtfunc.smoothing} function with $\ell_{max} = 3 N_{side} - 1$, the default).
-    The graph filtering is defined by \eqnref{graph_convolution_cheby} and implemented with the \texttt{numpy} and \texttt{scipy} Python packages.
-    Both are executed on a single core.
-    The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3)$ for the spherical harmonics, where $\ell_{max}$ is the largest degree (i.e., the spectrum is truncated at $\ell_{max}$).}
-	\label{fig:filtering_speed}
-\end{figure}
-
-\subsection{Coarsening and Pooling}
-
-Coarsening can be naturally designed for hierarchical pixelisation schemes, as each subdivision divides a cell in an equal number of child sub-cells.
-Coarsening is the reverse operation: merging the sub-cells toward the goal of summarizing the data supported on them.
-Merging cells lead to a coarser graph.
-Coarsening defines $\C(i)$, the set of children of node $v_i$.
-For the HEALPix subdivision scheme, the number of children is constant, i.e., $| \C(i) | = 4^p \ \forall i$, for some $p$.
-
-Pooling refers to the operation that summarizes the data supported on the merged sub-cells in one parent cell.
-Given a map $\x \in \R^{N_{pix}}$, pooling defines $\y \in \R^{N'_{pix}}$ such as
-\begin{equation} \label{eqn:pooling}
-	y_i = f \left( \left\{ x_j : j \in \C(i) \right\} \right), \ \forall i \in [N'_{pix}],
-\end{equation}
-where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix} / {N'_{pix}}$ is the down-sampling factor, which for HEALPix is $| \C(i) | = N_{pix} / {N_{pix}}' = (N_{side} / N'_{side})^2 = 4^p$.
-That operation is often taken to be the maximum value, but it can be any permutation invariant operation, such as a sum or an average.
-\figref{pooling} illustrates the process.
-
-% The advantage of schemes based on a base polyhedron is that cells are equal-area.
-While that is not required for the convolution operation when modeling with graphs (it can be corrected by setting edge weights appropriately, see \citet{khasanova2017graphomni})
-% nope: can also do a regular pooling on the equirectangular. It preserves the sampling, and the convolution is adapted to the sampling thanks to the edge weights.
-
-\begin{figure}
-	\centering
-    % \includegraphics[width=\linewidth]{pooling}
-	\includegraphics[trim=1.1cm 0cm 0cm 0cm, width=\linewidth]{figures/figure_pooling_svg.pdf}
-	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarsest cell covers $1/12$ of the sphere.}
-	\label{fig:pooling}
-\end{figure}
-
-\subsection{Statistical layer}
-\label{sec:stat_layer}
-% Or Global pooling?
-
-Following \citet{khasanova2017tigranet}, we implement an optional statistical layer between the last graph convolutional layer and the first fully connected layer for the neural network.
-This introduces the invariance of the output to isometric transformations, such as rotation and translation of maps on the sphere.
-The role of the layer is to compute global and location independent statistics from feature maps.
-Besides providing invariance, the layer drastically compresses the representation of the data as the number of computed statistics $N_{stat}$ is usually much smaller than the size of the map $N_{pix}$.
-That compression results in much smaller fully connected layers, which usually contain a significant fraction of trainable parameters of a neural network.
-The invariance and reduced representation should help the network to learn from less samples and to generalize better to unseen data.
-Yet another advantage is that a network built with such a statistical layer is agnostic to the size of the input data, i.e., it can classify maps which do not have the same number of pixels.
-Indeed, such global summarization is invariant to node permutation and is commonly used along graph convolutions to classify graphs of varying sizes \citep{duvenaud2015gcn, li2015gatedgnn}.
-
-Given a feature map $\x \in \R^{N_{pix}}$, the statistical layer is defined as
-\begin{equation} \label{eqn:stat_layer}
-	\y = f(\x) \in \R^{N_{stat}},
-\end{equation}
-where $f$ computes $N_{stat}$ statistics which are independent from the size of the map, $N_{pix}$.
-An example is the global average pooling $f(\x) = \esp(\x)$, introduced by \citet{lin2013globalavgpooling}, where $\esp(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} x_i$ is the empirical mean.
-Another example is $f(\x) = [\esp(\x), \var(\x)]\trans$, where $\var(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} (x_i - \esp(\x))^2$ is the empirical variance.
-Other statistical layers are also possible.
-In particular, we also implement a \emph{learned histogram} statistic \citep{wang2016learnhist}.
-Other approaches, which we did not implement, may include applying different diffusion on the final maps to obtain statistics at different scales, as proposed by \citep{khasanova2017tigranet}.
-
-\subsection{Graph convolutional neural network}
-\label{sec:architecture}
-
-Neural networks are constructed as stacks of layers which sequentially transform the data from its raw representation to a decision on the class label.
-Our architecture, pictured in \figref{architecture}, is composed of many layers.
-The convolutional part, the head of the neural network, is composed of graph convolutional layers (GC), pooling layers (P), and batch normalization layers (BN).
-The tail is composed of multiple fully connected layers (FC) followed by a softmax layer (SM).
-A statistical layer (ST) is optionally inserted between the convolutional head and the fully connected tail.
-
-% As such, we will not mention the non-linearity in the description of our architectures.
-A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer where it is set to the identity.
-That operation is point-wise, i.e., $y_{ij} = \sigma(x_{ij})$ and $y_i = \sigma(x_i)$ for matrices $\X, \Y$ and vectors $\x, \y$.
-The rectified linear unit (ReLU) $\sigma(\cdot) = \max(\cdot, 0)$ is a common choice.
-
-Given a matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$, a GC layer computes $\Y = GC(\X) = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels (and nodes), $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
-Using the efficient graph convolution from \eqnref{graph_convolution_cheby}, each output feature map is computed as
-\begin{equation*}
-	\y_i = \sum_{j=1}^{F_{in}} h_{\theta_{ij}}(\tL) \x_j + b_i \in \R^{N_{pix}}, \ \ \forall i \in [F_{out}].
-\end{equation*}
-As such, a GC layer is composed of $F_{in} \cdot F_{out}$ filters, each parameterized by $K$ numbers (see \secref{efficient_convolution}). A bias term $\b b \in \R^{F_{out}}$ is jointly optimized.
-% only if batch normalization is not used
-
-Given a matrix $\X \in \R^{N_{pix} \times F}$, a pooling layer computes $\Y = P(\X) \in \R^{N'_{pix} \times F}$ by reducing its spatial resolution ($N'_{pix} < N_{pix}$) according to \eqnref{pooling}.
-% Given a matrix $\X \in \R^{N_{pix} \times F}$,
-The batch normalization layer \citep{ioffe2015batchnorm} computes $\Y = BN(\X)$ such as
-\begin{equation*}
-	\y_i = \gamma_i \frac{\x_i - \esp(\x_i)}{\sqrt{\var(\x_i) + \epsilon}} + \beta_i, \ \forall i \in [F],
-\end{equation*}
-where $\gamma_{j}$ and $\beta_{j}$ are parameters to be learned and $\epsilon$ is a constant added for numerical stability.
-The empirical expectation $\esp(\x_i) \in \R$ and variance $\var(\x_i) \in \R$ are taken across training examples and pixels.
-% the action of gamma can be done by the filters of the next layer
-
-The statistical layer, defined in \eqnref{stat_layer}, independently transforms each of the $F$ feature maps of the input $\X \in \R^{N_{pix} \times F}$ into $\Y = ST(\X) \in \R^{N_{stat} \times F}$, where $N_{stat}$ is the number of statistics.
-One may even omit the FC layers and directly fed the output of the ST layer into the softmax layer, as proposed by \citet{lin2013globalavgpooling}.
-In this regime, $N_{stat} = 1$ and $F = N_{classes}$ is the number of classes to discriminate (i.e., the last GC layer outputs as many feature maps as there is classes).
-
-A FC layer takes as input $\x \in \R^{F_{in}}$ and outputs
-\begin{equation*}
-	\y = FC(\x) = \b W \x + \b b \in \R^{F_{out}} ,
-\end{equation*}
-where $\W \in \R^{F_{out} \times F_{in}}$ and $\b b \in \R^{F_{out}}$ are the parameters to be learned.
-Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last GC (or the output $\Y \in \R^{N_{stat} \times F_{out}}$ of the ST), is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first FC, where $F_{in} = N_{pix} \cdot F_{out}$ (or $N_{stat} \cdot F_{out}$).
-
-The softmax layer is the last layer in a neural network engineered for classification.
-Given the output $\x \in \R^{N_{classes}}$ of the last FC (or ST), called the logits in the deep learning literature, the softmax layer outputs $\y = SM(\x)$ such that
-\begin{equation*}
-	y_i = \frac{\exp(x_i)}{\sum_{j=1}^{N_{classes}} \exp(x_j)} \in [0, 1], \ \forall i \in [N_{classes}],
-\end{equation*}
-where $N_{classes}$ is the number of classes to discriminate.
-Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the probability that the input sample belongs to class $i$.
-This last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.
-
-Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
-An example network is
-\begin{equation*}
-NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC,
-\end{equation*}
-where $\circ$ denotes composition, i.e., $f \circ g = f(g(\cdot))$.
-The number of features $F$ depends on the data at hand.
-For the CMB radiation temperature, $F = 1$.
-For observations in radio frequencies, $F$ would be equal to the number of surveyed frequencies.
-$F$ might also be the number of slices in the radial direction.
-The loss function $\ell(\y) = \ell(NN_\theta(\X))$ is a measure of how good the prediction $\y$ is for the sample $\X$. For a classification task, the loss is usually taken to be the cross-entropy
-\begin{equation*}
-	\ell(\y) = -\log(y_i),
-\end{equation*}
-where $i$ is the correct class label.
-The parameters $\theta$ of the neural network are optimized to minimize the loss over the training dataset $\left\{ \X_i \right\}_{i=1}^{N_{samples}}$:
-\begin{equation*}
-	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell(NN_\theta(\X_i)).
-\end{equation*}
-The same architecture with different loss function can also be used for parameter regression \citep{fluri2018deep,gupta2018nongaussianinformation}.
-The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
-\begin{equation*}
-	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
-\end{equation*}
-where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch.
-Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.
-
-\todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
-
-\section{Related work}
-\label{sec:related}
-
-\begin{figure}
-    \centering
-    \includegraphics[height=7em]{sphere_grid_equirectangular}
-    \hfill
-    \includegraphics[height=7em]{sphere_grid_cubedsphere}
-    \hfill
-    \includegraphics[height=7em]{half_graph_4}
-    \caption[]{Some pixelizations of the sphere.
-Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system.
-Middle: an equiangular cubed-sphere grid, as described in \citet{ronchi1996cubed}.
-Right: graph built from an HEALPix pixelization of half the sphere ($N_{side} = 4$).
-By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[7] Left and middle figures are taken from \citet{boomsma2017spherical}.}
-    \label{fig:sphere_grids}
-    \label{fig:healpix_graph_4}
-\end{figure}
-
-\citet{boomsma2017spherical} apply a standard 2D CNN to a grid discretization of the sphere.
-Two grids, illustrated in \figref{sphere_grids}, are used in their work: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}.
-As this formulation uses the standard 2D convolutions, all the optimizations developed for 2D images can be applied, what make it computationally very efficient.
-It is, however, restricted to those grid sampling sets.
-Similarly to the cubed-sphere, HEALPix is a composition of twelve grids.
-While each of those twelve grids could potentially be independently fed into a 2D CNN, boundary conditions would have to be properly handled, as those grids are not independent.
-\todo{How do they handle boundaries?}
-\TK{+1,good question}
-\nati{They are almost not talking about that. For the cubed sphere, the only reference I could found was:
-\emph{"When implementing convolutions and pooling operations for the cubed-sphere grid, one has to be careful in padding each patch with the contents of the four neighbouring patches, in order to preserve the wrapped topology of the sphere (figure 2, right)."}
-Note that for the cubed sphere sampling each pixel has exactly four neighboors which make the problem of border effect handable.
-As for the equirectangular grid, it is equivalent to a cylinder.
-So I guess they take the standard image processing border conditions (reflective).
-I do not think we should mention any of that in the paper.
-}
-% Furthermore, the grid requirement makes it impossible for the convolution to capture the spherical properties of the domain, i.e., the cubed-sphere sampling is by definition adapted to a cube and not to a sphere.
-Nope, the graph can adapt to any sampling.
-% Moreover, those samplings are not ideal as their resolution is not constant across the sphere.
-Moreover, the pixel area is not constant across the sphere in those sampling schemes, which may limit their potential applications.
-Indeed, the singularities, such as the poles for the equirectangular grid, and the corners of the cube for the cubed-sphere, are over-sampled.
-Equal areas of discrete elements is advantageous for many physical measurements, as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence \citep{gorski2005healpix}.
-% \nati{Michael: Under some very specific hypothesis, this second approach is a particular case of our method, i.e.
-(i) our method with a stupid sampling, (ii) assumption that graph convolution on a grid == 2d convolution.
-Do you think we should mention that?
-I think we should not.}
-Finally, a 2D CNN learns directional filters, which are well defined with respect of the image coordinates.
-Directions that make much sense for images (up, down, left, and right) are arbitrarily defined when setting the origin of the grids on the sphere.
-Any convolution using directions on the sphere is not equivariant to translation and rotation.
-
-% As presented by~\cite{cohen2018spherical}, the most mathematical approach to extend the convolution on a sphere is to use a spherical Fourier transform.
-The convolution is then simply defined as the product in the spectral domain.
-This approach requires one Fourier and one inverse Fourier transform per convolution which remain, even with accelerated algorithms, expensive.
-
-\citet{cohen2018spherical} uses the continuous spherical convolution.
-The goal of this contribution was to define a rotation-equivariant convolution on the sphere, i.e., a rotation of the input implies the same rotation in the output.
-The resulting convolution is performed by (i) a spherical harmonic transform (SHT), i.e., a projection on the spherical harmonics, (ii) a  multiplication in the spectral domain, and (iii) an inverse SHT.
-Hence the computational cost of a convolution is dominated by the two SHTs.
-A naive implementation of the SHT costs $\bO(N_{pix}^2)$ operations, where $N_{pix}$ is the number of pixels.
-Accelerated schemes exist for some sampling sets \citep[see][for examples]{mohlenkamp1999fast, rokhlin2006fast, reinecke2013libsharp}.
-The main advantage of this approach is that it provides a mathematically well defined rotation-equivariant network.
-Nevertheless, even with accelerated SHTs, the convolutions remain expensive, limiting the practical use of this approach.
-For example with the HEALPix sampling, which was designed to have a fast SHT by being iso-latitude, the computational cost of the SHT is $\bO(N_{pix}^{3/2}) = \bO(N_{side}^3) = \bO(\ell_{max}^3)$, where $\ell_{max}$ is the largest angular frequency\footnote{All pixels are placed on $N_{ring} = 4N_{side}-1 = \bO(\sqrt{N_{pix}})$ rings of constant latitude.
-Each ring has $\bO(\sqrt{N_{pix}})$ pixels.
-Thanks to this iso-latitude property, the SHT is computed using recurrence relations for Legendre polynomials on co-latitude and fast Fourier transforms (FFTs) on longitude.
-The computational cost is thus $\sqrt{N_{pix}}$ FFTs for a total cost of $\bO(N_{pix} \log(\sqrt{N_{pix}}))$, plus $\sqrt{N_{pix}}$ matrix multiplications of size $\sqrt{N_{pix}}$ for a total cost of $\bO(N_{pix}^{3/2})$.}
-\citep{gorski2005healpix, reinecke2013libsharp}.
-In comparison, filtering with our HealpixNet method scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}).
-% Moreover, \figref{filtering_speed} shows that a naive implementation of our method is more than ten times faster than the SHT implemented by the highly optimized \pkg{libsharp} library used by HEALPix \citep{reinecke2013libsharp}.
-% While a comparison is theoretically possible, the experiments of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and do not provide any code for the HEALPix one.
-Hence, a practical comparison is not possible.
-% \TK{I would leave out here, as this is a "spoiler" of the results section.}
-
-Approaches by \citet{cohen2018spherical,boomsma2017spherical} can not be easily accelerated when the data lies on a part of the sphere only.
-
-\nati{Why is \citet{boomsma2017spherical} here? I think it can be trivally accelerated.}
-That is an important use case in cosmology as measurements are often partial, i.e., full-sky maps are rare.
-One could still fill the unseen part of the sphere with zeros, and avoid to compute empty integrals, on the latitude or longitude.
-It is, however, not straightforward to identify those empty directions, and computations would still be wasted; consider, for example, a ring which mostly contains zeros but a few measurements.
-With graphs however, the computation is done only for the used pixels.
-This, however, results in some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}).
-These can be mitigated by padding with zeros a small area around the measurements.
-
-% In an attempt to get the best of the first two approaches, we follow a third
-% direction. We use a graph to adapt to the particular structure of the sphere.
-% While the convolution remains efficient, it still captures well the spherical
-% structure and is particularly adapted to the HEALPix sampling.
-% \TK{I am not sure what is the point of this paragraph, we described our approach already before}
-
-The use of a graph to model the discretised sphere was also considered by~\citet{khasanova2017graphomni}.
-The authors map omnidirectional images onto a sphere, with the goal of correcting for distortions induced by the lens, which was used for their acquisition.
-Besides a different practical application, for which the method was designed, there are two important differences.
-% First, a different sampling scheme is used: \cite{khasanova2017graphomni} uses a grid.
-First, similarly to~\citet{boomsma2017spherical}, they use an equirectangular grid sampling.
-% \TK{how is it different from us?}
-Second, it uses a graph CNN based on a different parameterisation of the convolution kernel.
-Moreover, they did not take advantage of a hierarchical pixelization of the sphere and resorted to dynamic pooling~\citep{kalchbrenner2014dcnn}.
-Finally, while the rotation invariance is desirable, the statistical layer used
-% --- an operation which computes a set of spatially invariant statistics of the last feature map ---
-% \{TK} this should be explained earlier
-may not capture the information in an optimal way
-\todo{and hinders performance (should be empirically verified)}.
-\TK{This is a strong claim, can we support this?} \nati{It is not that strong as we use "may" right?
-We should probably soften it a bit.
-However the main idea is correct.
-If you compute some statistics on some features, you lose some information and may get worse results.
-Nevertheless, since we are also using a statistical layer, I would juste remove this.}
-Moreover, the chosen statistics have to be hand-crafted to capture statistics of interest.
-% While developing completely invariant transforms is a goal worth investigating, CNNs for image recognition, which are arguably the most researched and developed architectures, are not built to be fully invariant to translation.
-% As with the proposed spherical CNN, the fully connected layers at the end of the network depend on the spatial localization of features.
-% While that may not be ideal, it was shown to work well in practice.
-% \TK{The two sentences above look like a tangent to me.. can we skip it an go to the main point, which is I think the fact that we use the stat layer?}
-
-\todo{In HealpixNet we use the idea of a statistical layer, described in \secref{stat_layer}, to provide invariance to isometric transformations such as translation and rotation on the sphere.
-\TK{We would need to describe the idea of the statistical layer for the cosmology audience. They don't have a clue what it is.}\nati{Can't they just wait for \secref{stat_layer}? }
-The use of the statistical layer is optional.
-In our approach, we are keeping all the statistical moments by retaining a full, learned learned feature histogram, an approach that performed the best in our tests.
-That is similar to the learnable histogram introduced by \citet{wang2016learnhist}, although for a purpose of integrating global context in object detection and segmentation tasks.
-\citet{khasanova2017graphomni} uses the mean and variance of diffused versions of the last feature maps in their statistical layer.}
-\TK{why is this section in TODO?\nati{Probably because, we have not decided if we use the histogram yet. This paragraph needs to be rewritten once we are clear with the code.}}
-
-There exists many formulations of graph neural networks, reviewed by \citet{bronstein2017review} and \citet{hamilton2017review}.
-For this contribution, we chose the formulation of \citet{defferrard2016convolutional} as its root on strong graph signal processing theory makes the concept of convolutions and filters explicit \citep{shuman2013emerging}.
-Its tie to a graph Fourier transform allows us to compare with the spherical harmonic transform, and study its invariance properties.
-More geometric than permutation invariant aggregation.
-A contrario, formulations with exploit the tengant space of manifolds define a local coordinate system.
-While this formulation of convolution can learn anisotropic filters, it is not equivariant to translation.
-\todo{better wording}
-\todo{three main interpretations: gsp, Bronstein manifold tangent plane, message passing, permutation invariant aggregation, spatial formulations}
-Bronstein is a spatial formulation where the registration is done by projection on the tangent plane.
-% Not Bronstein's manifold approach as we want a Fourier basis to compare to the spherical harmonics.
-% Be as close as possible to spherical harmonics.
-Related to this, convolutional neural networks have been defined on manifolds and have achieved impressive results on shapes [Bronstein].
-They however too depend on an orientation, which spheres do not possess.
-
-% Anisotropic cannot be invariant
-
-The connection has recently been made between graph CNNs and group equivariant CNNs \cite{kondor2018equivariance}, justifying the use of graphs to gain rotation equivariance on the sphere.
-
-% In this work, we are using the graph CNN formulation introduced in~\cite{defferrard2016convolutional}.
-
-Spatial definitions of graph convolutions, e.g.
-[Niepert] needs to define an orientation in order to match the edges with the filters.
-Most often the orientation is not given by the application, and one has to define it (for example by ordering by degree or any other measure, or by using a graph coloring).
-There is no good default good orientation on general graphs and the choice of an orientation is highly application dependent.
-
 \section{Experiments}
@@
 These maps are similar to those created with gravitational lensing technique \citep{chang2017curvedsky}.
-Nevertheless, by simply changing the loss, one could use the network for regression.
+The experiment presented here is similar the one by \citet{schmelze2017cosmologicalmodel}.
+The two set of maps were created using the standard cosmological model with two sets of cosmological parameters.
+The classification methods were trained to assign a predicted label using the Healpix maps.
 Both our Python implementation\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments is available online.
+
+We use the classification scenario in this work.
+Extensions to other tasks, such as regression or segmentation, is also possible; we do not, however, demonstrate it here.
+The regression task will most likely be the most practical cosmological applications, as described in \citep{gupta2018nongaussianinformation,fluri2018deep}.
+Implementation of full cosmological inference requires, however, many more simulations, building the likelihood function, and several other auxiliary tasks.
+The classification problem is much more straightforward to implement and execute, and can be used to fairly compare the accuracy of the algorithm against benchmarks \citep{schmelze2017cosmologicalmodel}.
+For these reasons we decided to use the classification problem in this work, and we expect the relative performance of the methods to generalise to the regression scenario.
 
@@
 The resulting maps are large enough to suffer from the effects of the spherical geometry, and cover 8.3\%, 2.1\% and 0.5\% of the total sphere area for $o=1,2,4$, respectively.
+The areas on the sphere corresponding to these orders can be seen in \figref{pooling}: the pixels in the left, middle and right spheres correspond to $o=4,2,1$, respectively.
 We decided to only report simulation results for this specific setting as spherical cosmological data usually does not span the full sphere.
@@
 
-We demonstrate that the neural network systematically and significantly outperforms our benchmark methods on an example problem of cosmological model discrimination with weak lensing mass maps.
+We demonstrate that the neural network systematically and significantly outperforms our benchmark methods on an example problem of cosmological model discrimination with weak lensing mass maps, designed similarly to \citep{schmelze2017cosmologicalmodel}.
+The maps were produced from two cosmological models with varying $\sigma_8$ and $\Omega_m$, chosen to follow the typical weak lensing degeneracy in these parameters, so that the power spectra for these models are very similar.
+We compared the performance of the HealpixNet CNN versus that of two SVM-based classifiers: one trained on the spherical harmonics power spectrum, and the other on the pixel density histogram.
 Notably, HEALPix maintains good classification accuracy even for high noise levels and part-sky areas.
@@
 % \TK{I would move the info about possible relaxation of the iso-latitude thing to a separate paragraph at the end on conclusions - future prospects?}
-Graph-based representation of the sphere can display small imprecisions in rotation invariance, which results in the property that the action of a graph filter slightly depends on the location.
-For applications that can tolerate this property, an graph-based representation may be a worthwhile alternative.
+Graph-based representation of the sphere can display small imprecisions in rotation invariance, the result of which is that an action of a graph filter slightly depends on the location.
+For applications that can tolerate this property, a graph-based representation may be a worthwhile alternative.
 % this relaxation might enable researchers to consider sampling sets with different properties.
@@
 
-The main product of this contribution is HealpixNet a small and easy-to-use python package for cosmologists to classify sky maps.
+The main product of this contribution is HealpixNet: a small and easy-to-use python package for spherical analysis of cosmological data.
 The code and data used in this work are publicly available\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}.
+The code was designed in a way to enable straightforward modifications of the architectures, so that HealpixNet can easily be used for a number of typical machine learning tasks, such as classification, regression, or segmentation.
+Notably, for a problem of cosmological parameter estimation \citep{fluri2018deep,gupta2018nongaussianinformation}, it is easy to replace the classification loss task with a regression loss.
+It should also be possible use dense layer for an output and perform segmentation tasks, such as masking, flagging, or object detection.
 

### 2018-08-06 scnn.tex
moved plots around so they are nicely positioned
updated figures, not sure if they are a lot better though

@@
 
-A CNN is composed of the following main building blocks~\citep{lecun1998cnn}:
-(i) a convolution,
-(ii) a non-linearity,
-(iii) a down-sampling operation,
-(iv) a pooling operation, and
-(v), optionally,  normalization.\footnote{\citet{ioffe2015batchnorm} have shown that batch normalization helps training. We verified this experimentally in our setting as well.}
-Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}.
-As operations (ii) and (v) are point-wise, they do not depend on the data domain.
-The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either.
-The convolution and down-sampling operations however need to be generalized from Euclidean domains to the sphere.
-
-On regular Euclidean domains, such as 1-dimensional time series or 2-dimensional images, a convolution can be efficiently implemented by sliding a localized convolution kernel (for example a patch of 5x5 pixels) in the signal domain.
-Likewise, down-sampling can be achieved by taking one pixel out of $n$.
-Because of the irregular sampling, there is no straightforward way to define a convolution on the sphere directly in the pixel domain; convolutions are most often performed using spherical harmonics.
-In our method we also use the spectral domain to define the convolution.
-The implementation, however, does not need a direct access to the spectrum, which is computationally more efficient (see \secref{efficient_convolution}).
-% We will therefore use the spectral domain to define the convolutions
-% \footnote{Note that we only use the spectrum to define the convolution.
-% The implementation however does not need a direct access to the spectrum, which is computationally much more efficient. See \secref{efficient_convolution}.}
-% \TK{moving footnote to the main text }
-The gist of our method is to define the convolution operation on a sphere using a graph, and the down-sampling operation using a hierarchical pixelisation of the sphere.
-
-\subsection{HEALPix sampling}
-\label{sec:healpix}
-
 \begin{figure*}
@@
 \end{figure*}
+
+A CNN is composed of the following main building blocks~\citep{lecun1998cnn}:
+(i) a convolution,
+(ii) a non-linearity,
+(iii) a down-sampling operation,
+(iv) a pooling operation, and
+(v), optionally,  normalization.\footnote{\citet{ioffe2015batchnorm} have shown that batch normalization helps training. We verified this experimentally in our setting as well.}
+Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}.
+As operations (ii) and (v) are point-wise, they do not depend on the data domain.
+The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either.
+The convolution and down-sampling operations however need to be generalized from Euclidean domains to the sphere.
+
+On regular Euclidean domains, such as 1-dimensional time series or 2-dimensional images, a convolution can be efficiently implemented by sliding a localized convolution kernel (for example a patch of 5x5 pixels) in the signal domain.
+Likewise, down-sampling can be achieved by taking one pixel out of $n$.
+Because of the irregular sampling, there is no straightforward way to define a convolution on the sphere directly in the pixel domain; convolutions are most often performed using spherical harmonics.
+In our method we also use the spectral domain to define the convolution.
+The implementation, however, does not need a direct access to the spectrum, which is computationally more efficient (see \secref{efficient_convolution}).
+% We will therefore use the spectral domain to define the convolutions
+% \footnote{Note that we only use the spectrum to define the convolution.
+% The implementation however does not need a direct access to the spectrum, which is computationally much more efficient. See \secref{efficient_convolution}.}
+% \TK{moving footnote to the main text }
+The gist of our method is to define the convolution operation on a sphere using a graph, and the down-sampling operation using a hierarchical pixelisation of the sphere.
+
+\subsection{HEALPix sampling}
+\label{sec:healpix}
 
@@
 
+Figure \figref{graph_harmonics} shows the Fourier modes of a HEALPix graph, created using the graph construction described above.
+The graph Fourier modes resemble the spherical harmonics.
+That is a strong hint that the graph is able to capture the spherical properties of the HEALPix sampling.
+This topic is further discussed in \ref{sec:comparison_spherical_harmonics}.
+
 \begin{figure}
@@
 \end{figure}
-
-Figure \figref{graph_harmonics} shows the Fourier modes of a HEALPix graph, created using the graph construction described above.
-The graph Fourier modes resemble the spherical harmonics.
-That is a strong hint that the graph is able to capture the spherical properties of the HEALPix sampling.
-This topic is further discussed in \ref{sec:comparison_spherical_harmonics}.
 
@@
 
+\begin{figure}
+    \centering
+    \includegraphics[width=\linewidth]{filtering_speed}
+    \caption{Comparison of filtering speed for Gaussian smoothing of maps of various sizes.
+    The fast spherical harmonic transform (SHT) is implemented by the \texttt{healpy} Python package (via the \texttt{healpy.sphtfunc.smoothing} function with $\ell_{max} = 3 N_{side} - 1$, the default).
+    The graph filtering is defined by \eqnref{graph_convolution_cheby} and implemented with the \texttt{numpy} and \texttt{scipy} Python packages.
+    Both are executed on a single core.
+    The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3)$ for the spherical harmonics, where $\ell_{max}$ is the largest degree (i.e., the spectrum is truncated at $\ell_{max}$).}
+    \label{fig:filtering_speed}
+\end{figure}
+
 While \eqnref{graph_convolution} is a theoretically well justified definition of the convolution of a graph signal $\f$ by a kernel $h$, it is computationally cumbersome.
@@
 The performance of our approach is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{filtering_speed}
-	\caption{Comparison of filtering speed for Gaussian smoothing of maps of various sizes.
-    The fast spherical harmonic transform (SHT) is implemented by the \texttt{healpy} Python package (via the \texttt{healpy.sphtfunc.smoothing} function with $\ell_{max} = 3 N_{side} - 1$, the default).
-    The graph filtering is defined by \eqnref{graph_convolution_cheby} and implemented with the \texttt{numpy} and \texttt{scipy} Python packages.
-    Both are executed on a single core.
-    The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3)$ for the spherical harmonics, where $\ell_{max}$ is the largest degree (i.e., the spectrum is truncated at $\ell_{max}$).}
-	\label{fig:filtering_speed}
-\end{figure}
 
@@
 
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{gaussian_filters_spectral}
+\caption{Visualization of the convolution kernel $K_t(x)=e^{-\tau t x}$ in spectral domain.}
+\vspace{0.3in}
+\includegraphics[width=\linewidth]{gaussian_filters_gnomonic}
+\caption{Visualization of the convolution kernel $K_t(x)=e^{-\tau t x}$: cross-section of the kernel through the pixels along the equator.}
+\vspace{0.3in}
+\includegraphics[width=\linewidth]{gaussian_filters_section}
+\caption{Visualization of the convolution kernel $K_t(x)=e^{-\tau t x}$ in a gnomonic projection.}
+\label{fig:gaussian_filters_visualization}
+\end{figure}
+
 In \figref{gaussian_filters_visualization}, we present three different
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=\linewidth]{gaussian_filters_spectral}
-\includegraphics[width=\linewidth]{gaussian_filters_gnomonic}
-\includegraphics[width=\linewidth]{gaussian_filters_section}
-\caption{Three different visualizations of the convolution kernel $K_t(x)=e^{-\tau t x}$.
-Top: graph spectral domain.
-Middle: gnomonic projection.
-Bottom: section plot.}
-\label{fig:gaussian_filters_visualization}
-\end{figure}
-
 % \begin{figure}

### 2018-08-06 scnn.tex
update in result section

@@
 
-To improve the stability of the spherical CNN, we slowly increase the amount of noise added to the training data over the iterations.
+% Nati: Not done anymore
+% To improve the stability of the spherical CNN, we slowly increase the amount of noise added to the training data over the iterations.
 Furthermore in order to avoid overfitting, the noise is randomly produced during the training process.
-We trained our model between $50$ and $290$ epochs depending on the complexity and the size of the problem.
 The $20\%$ of the training set that we call \emph{validation set} was left out of the training process and simply used to assess the global performance of the network.
-Training took less than a day for each model using a single NVIDIA Tesla K20.
 
@@
 This process is detailed in \ref{sec:dataset_augmentation}.
-We tune the regularization parameter by cross-validating with the validation set.
+We tune the SVM regularization parameter by cross-validating with the validation set.
 
@@
 
-\todo{We use the ADAM optimizer, \cite{kingma2014adam}, with an initial learning rate of $2e-4$ that is exponentially decreased by $0.98$ a $100$ times to end at $2.7e-5$.}
+\todo{We use the ADAM optimizer, \cite{kingma2014adam}, with an initial learning rate of $2e-4$ that is exponentially decreased by $0.98$ a $100$ times to end at $2.7e-5$.
+All models where trained $80$ epochs with a batch size of $16\times o^2$. With this choice, all models recieve an identical amount of data within a batch and were trained with $1920$ gradient steps.}
+Training took less \nati{queue bottleneck to be fixed} than $3$ hours for each model using a single NVIDIA Tesla K20.
 
@@
 Green lines show the performance of the CNN, blue of the PDF+SVM, and red of the histogram+SVM.
-Green dashed line corresponds to the performance of CNN without the statistical layer.
+% Green dashed line corresponds to the performance of CNN without the statistical layer.
 The noise level was increased from zero to $2\times$ the standard deviation of the mass map.
@@
 In contrast, both the PSD features and the HealpixNet can exploit the spatial information.
-Note that without this graph structure, a fully connected neural network approach would have to be used.
-Problematically, fully connected neural networks generally scales squarely with their number of inputs.
-\TK{I don't understand this comment.} \nati{Maybe we should leave it out then. It is not that important.}
+% Note that without this graph structure, a fully connected neural network approach would have to be used.
+% Problematically, fully connected neural networks generally scales squarely with their number of inputs.
+% \TK{I don't understand this comment.} \nati{Maybe we should leave it out then. It is not that important.}
 
@@
 First, Chebyshev polynomial seems more stable than monomials ($\theta_k$ in \eqnref{graph_convolution_polynomial}), in the sense that the training loss had a more steadily decrease.
-%\TK{what are monomials? stable in what sense?}
 Nevertheless once the network is trained, we could not observe a significant accuracy difference.
-Second, using a statistical layer improved the result unlimited for our problem.
+Second, using a statistical layer slightly improved the accuracy in our problem.
 We tried $4$ different layers `mean', `variance', `mean + variance' and `histogram'.
-The `mean', `histogram' and `mean + variance' were providing the same level of accuracy, with pure `variance' being slightly worse.
-Third, the use of the dropout\TK{was dropout mentioned before?} \nati{Probably not. But to keep it simple, we may just add a footnote or a reference.} layer did not help in the presence of noise.
-This is probably due to the fact that the dataset was augmented indefinitely through the addition of noise.
-Fourth, especially for the more difficult cases, orders 2 or 4 and large noise levels, a large architecture with many filters and many training iterations were necessary to achieve high accuracy levels.
+The `mean', `histogram' and `mean + variance' were providing the same level of accuracy, with pure `variance' being slightly worse. Hence we chose to simply use the `mean' statistic.
+Third, adding fully connected layers after the statistical layer does not improve the performance, but lead to models requiring more training steps and regularization.
+\todo{Fourth, using $\ell_2$ regularization does not help neither with the performance nor the training of the models, but slightly reduce the performance variance between different runs due to the random initialization.
+Eventually, recommend to ignitialize the Chebyshev coeffecient with a centered Gaussian distribution with standart deviation $2/(F * (K + 0.5))$, where $K$ is the Chebyshef order and $F$ the number of input channels.
+The
+}
 
@@
 The layered structure of the network can partially compensate for that.
-Further generalizations to non-radial filters may be possible [cite?]\TK{update here}, but we leave it to future work.
+% Further generalizations to non-radial filters may be possible [cite?]\TK{update here}, but we leave it to future work.
 

### 2018-08-07 scnn.tex
update todo

@@
     \item (NP) make figure A.13 remove white space
-    \item (TK) re-make figures to make the labels/legend/titles the same font size as the main text
     \item (NP+MD)  paragraph on our chosen architecture in the Experiments sections
@@
     \item (NP) vertex interpretation
-    \item (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook.
-    \item (TK) update the README for data zip - file from NP
     \item (NP) Finalise readme on Github code
-    \item TK check part sphere notebook and whole sphere
-    \item (TK) uniformize text size in figures
     \item branch with notebooks with plots (results) NP
@@
     \item check if papers which appear as arxiv were not published in a conference or journal
+    \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings.
+    \item TK check part sphere notebook and whole sphere
+    \item (done!) (TK) update the README for data zip - file from NP
     \item (almost done) TK read everything
-    \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings.
+    \item (done!) (TK) uniformize text size in figures
+    \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook.
+    \item (done!) (TK) re-make figures to make the labels/legend/titles the same font size as the main text
     \item (done!) TK check the appendix

### 2018-08-07 scnn.tex
related work was moved already
fix size of parenthesis

@@
     \item (NP+MD)  paragraph on our chosen architecture in the Experiments sections
-    \item (NP+MD) move the Related Work section after the Method section
     \item (NP) vertex interpretation
@@
 % the convolution is not restricted to the sphere, the coarsening/pooling is
-
-% \section{Related work}
-% \label{sec:related}
-
-% \begin{figure}
-%     \centering
-%     \includegraphics[height=7em]{sphere_grid_equirectangular}
-%     \hfill
-%     \includegraphics[height=7em]{sphere_grid_cubedsphere}
-%     \hfill
-%     \includegraphics[height=7em]{half_graph_4}
-%     \caption[]{Some pixelizations of the sphere.
-Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system.
-Middle: an equiangular cubed-sphere grid, as described in \citet{ronchi1996cubed}.
-Right: graph built from an HEALPix pixelization of half the sphere ($N_{side} = 4$).
-By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[7] Left and middle figures are taken from \citet{boomsma2017spherical}.}
-%     \label{fig:sphere_grids}
-%     \label{fig:healpix_graph_4}
-% \end{figure}
-
-% \citet{boomsma2017spherical} apply a standard 2D CNN to a grid discretization of the sphere.
-Two grids, illustrated in \figref{sphere_grids}, are used in their work: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}.
-% As this formulation uses the standard 2D convolutions, all the optimizations developed for 2D images can be applied, what make it computationally very efficient.
-% It is, however, restricted to those grid sampling sets.
-Similarly to the cubed-sphere, HEALPix is a composition of twelve grids.
-While each of those twelve grids could potentially be independently fed into a 2D CNN, boundary conditions would have to be properly handled, as those grids are not independent.
-% \todo{How do they handle boundaries?}
-% \TK{+1,good question}
-% \nati{They are almost not talking about that. For the cubed sphere, the only reference I could found was:
-% \emph{"When implementing convolutions and pooling operations for the cubed-sphere grid, one has to be careful in padding each patch with the contents of the four neighbouring patches, in order to preserve the wrapped topology of the sphere (figure 2, right)."}
-% Note that for the cubed sphere sampling each pixel has exactly four neighboors which make the problem of border effect handable.
-As for the equirectangular grid, it is equivalent to a cylinder.
-So I guess they take the standard image processing border conditions (reflective).
-% I do not think we should mention any of that in the paper.
-% }
-% % Furthermore, the grid requirement makes it impossible for the convolution to capture the spherical properties of the domain, i.e., the cubed-sphere sampling is by definition adapted to a cube and not to a sphere.
-Nope, the graph can adapt to any sampling.
-% % Moreover, those samplings are not ideal as their resolution is not constant across the sphere.
-% Moreover, the pixel area is not constant across the sphere in those sampling schemes, which may limit their potential applications.
-% Indeed, the singularities, such as the poles for the equirectangular grid, and the corners of the cube for the cubed-sphere, are over-sampled.
-% Equal areas of discrete elements is advantageous for many physical measurements, as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence \citep{gorski2005healpix}.
-% % \nati{Michael: Under some very specific hypothesis, this second approach is a particular case of our method, i.e.
-(i) our method with a stupid sampling, (ii) assumption that graph convolution on a grid == 2d convolution.
-Do you think we should mention that?
-I think we should not.}
-% Finally, a 2D CNN learns directional filters, which are well defined with respect of the image coordinates.
-% Directions that make much sense for images (up, down, left, and right) are arbitrarily defined when setting the origin of the grids on the sphere.
-% Any convolution using directions on the sphere is not equivariant to translation and rotation.
-
-% % As presented by~\cite{cohen2018spherical}, the most mathematical approach to extend the convolution on a sphere is to use a spherical Fourier transform.
-The convolution is then simply defined as the product in the spectral domain.
-This approach requires one Fourier and one inverse Fourier transform per convolution which remain, even with accelerated algorithms, expensive.
-
-% \citet{cohen2018spherical} uses the continuous spherical convolution.
-% The goal of this contribution was to define a rotation-equivariant convolution on the sphere, i.e., a rotation of the input implies the same rotation in the output.
-% The resulting convolution is performed by (i) a spherical harmonic transform (SHT), i.e., a projection on the spherical harmonics, (ii) a  multiplication in the spectral domain, and (iii) an inverse SHT.
-Hence the computational cost of a convolution is dominated by the two SHTs.
-% A naive implementation of the SHT costs $\bO(N_{pix}^2)$ operations, where $N_{pix}$ is the number of pixels.
-% Accelerated schemes exist for some sampling sets \citep[see][for examples]{mohlenkamp1999fast, rokhlin2006fast, reinecke2013libsharp}.
-% The main advantage of this approach is that it provides a mathematically well defined rotation-equivariant network.
-Nevertheless, even with accelerated SHTs, the convolutions remain expensive, limiting the practical use of this approach.
-% For example with the HEALPix sampling, which was designed to have a fast SHT by being iso-latitude, the computational cost of the SHT is $\bO(N_{pix}^{3/2}) = \bO(N_{side}^3) = \bO(\ell_{max}^3)$, where $\ell_{max}$ is the largest angular frequency\footnote{All pixels are placed on $N_{ring} = 4N_{side}-1 = \bO(\sqrt{N_{pix}})$ rings of constant latitude.
-Each ring has $\bO(\sqrt{N_{pix}})$ pixels.
-Thanks to this iso-latitude property, the SHT is computed using recurrence relations for Legendre polynomials on co-latitude and fast Fourier transforms (FFTs) on longitude.
-The computational cost is thus $\sqrt{N_{pix}}$ FFTs for a total cost of $\bO(N_{pix} \log(\sqrt{N_{pix}}))$, plus $\sqrt{N_{pix}}$ matrix multiplications of size $\sqrt{N_{pix}}$ for a total cost of $\bO(N_{pix}^{3/2})$.}
-% \citep{gorski2005healpix, reinecke2013libsharp}.
-% In comparison, filtering with our HealpixNet method scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}).
-% % Moreover, \figref{filtering_speed} shows that a naive implementation of our method is more than ten times faster than the SHT implemented by the highly optimized \pkg{libsharp} library used by HEALPix \citep{reinecke2013libsharp}.
-% % While a comparison is theoretically possible, the experiments of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and do not provide any code for the HEALPix one.
-Hence, a practical comparison is not possible.
-% % \TK{I would leave out here, as this is a "spoiler" of the results section.}
-% Approaches by \citet{cohen2018spherical,boomsma2017spherical} can not be easily accelerated when the data lies on a part of the sphere only.
-% \nati{Why is \citet{boomsma2017spherical} here? I think it can be trivally accelerated.}
-% That is an important use case in cosmology as measurements are often partial, i.e., full-sky maps are rare.
-% One could still fill the unseen part of the sphere with zeros, and avoid to compute empty integrals, on the latitude or longitude.
-% It is, however, not straightforward to identify those empty directions, and computations would still be wasted; consider, for example, a ring which mostly contains zeros but a few measurements.
-% With graphs however, the computation is done only for the used pixels.
-% This, however, results in some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}).
-% These can be mitigated by padding with zeros a small area around the measurements.
-
-% % In an attempt to get the best of the first two approaches, we follow a third
-% % direction. We use a graph to adapt to the particular structure of the sphere.
-% % While the convolution remains efficient, it still captures well the spherical
-% % structure and is particularly adapted to the HEALPix sampling.
-% % \TK{I am not sure what is the point of this paragraph, we described our approach already before}
-
-% The use of a graph to model the discretised sphere was also considered by~\citet{khasanova2017graphomni}.
-% The authors map omnidirectional images onto a sphere, with the goal of correcting for distortions induced by the lens, which was used for their acquisition.
-% Besides a different practical application, for which the method was designed, there are two important differences.
-% % First, a different sampling scheme is used: \cite{khasanova2017graphomni} uses a grid.
-% First, similarly to~\citet{boomsma2017spherical}, they use an equirectangular grid sampling.
-% % \TK{how is it different from us?}
-% Second, it uses a graph CNN based on a different parameterisation of the convolution kernel.
-% Moreover, they did not take advantage of a hierarchical pixelization of the sphere and resorted to dynamic pooling~\citep{kalchbrenner2014dcnn}.
-% Finally, while the rotation invariance is desirable, the statistical layer used
-% % --- an operation which computes a set of spatially invariant statistics of the last feature map ---
-% % \{TK} this should be explained earlier
-% may not capture the information in an optimal way
-% \todo{and hinders performance (should be empirically verified)}.
-% \TK{This is a strong claim, can we support this?} \nati{It is not that strong as we use "may" right?
-We should probably soften it a bit.
-However the main idea is correct.
-If you compute some statistics on some features, you lose some information and may get worse results.
-Nevertheless, since we are also using a statistical layer, I would juste remove this.}
-% Moreover, the chosen statistics have to be hand-crafted to capture statistics of interest.
-% % While developing completely invariant transforms is a goal worth investigating, CNNs for image recognition, which are arguably the most researched and developed architectures, are not built to be fully invariant to translation.
-% % As with the proposed spherical CNN, the fully connected layers at the end of the network depend on the spatial localization of features.
-% % While that may not be ideal, it was shown to work well in practice.
-% % \TK{The two sentences above look like a tangent to me.. can we skip it an go to the main point, which is I think the fact that we use the stat layer?}
-
-% \todo{In HealpixNet we use the idea of a statistical layer, described in \secref{stat_layer}, to provide invariance to isometric transformations such as translation and rotation on the sphere.
-% \TK{We would need to describe the idea of the statistical layer for the cosmology audience. They don't have a clue what it is.}\nati{Can't they just wait for \secref{stat_layer}? }
-% The use of the statistical layer is optional.
-% In our approach, we are keeping all the statistical moments by retaining a full, learned learned feature histogram, an approach that performed the best in our tests.
-% That is similar to the learnable histogram introduced by \citet{wang2016learnhist}, although for a purpose of integrating global context in object detection and segmentation tasks.
-% \citet{khasanova2017graphomni} uses the mean and variance of diffused versions of the last feature maps in their statistical layer.}
-% \TK{why is this section in TODO?\nati{Probably because, we have not decided if we use the histogram yet. This paragraph needs to be rewritten once we are clear with the code.}}
-
-% There exists many formulations of graph neural networks, reviewed by \citet{bronstein2017review} and \citet{hamilton2017review}.
-For this contribution, we chose the formulation of \citet{defferrard2016convolutional} as its root on strong graph signal processing theory makes the concept of convolutions and filters explicit \citep{shuman2013emerging}.
-Its tie to a graph Fourier transform allows us to compare with the spherical harmonic transform, and study its invariance properties.
-More geometric than permutation invariant aggregation.
-A contrario, formulations with exploit the tengant space of manifolds define a local coordinate system.
-While this formulation of convolution can learn anisotropic filters, it is not equivariant to translation.
-\todo{better wording}
-% \todo{three main interpretations: gsp, Bronstein manifold tangent plane, message passing, permutation invariant aggregation, spatial formulations}
-% Bronstein is a spatial formulation where the registration is done by projection on the tangent plane.
-% % Not Bronstein's manifold approach as we want a Fourier basis to compare to the spherical harmonics.
-% % Be as close as possible to spherical harmonics.
-% Related to this, convolutional neural networks have been defined on manifolds and have achieved impressive results on shapes [Bronstein].
-They however too depend on an orientation, which spheres do not possess.
-
-% % Anisotropic cannot be invariant
-
-% The connection has recently been made between graph CNNs and group equivariant CNNs \cite{kondor2018equivariance}, justifying the use of graphs to gain rotation equivariance on the sphere.
-
-% % In this work, we are using the graph CNN formulation introduced in~\cite{defferrard2016convolutional}.
-
-% Spatial definitions of graph convolutions, e.g.
-[Niepert] needs to define an orientation in order to match the edges with the filters.
-Most often the orientation is not given by the application, and one has to define it (for example by ordering by degree or any other measure, or by using a graph coloring).
-There is no good default good orientation on general graphs and the choice of an orientation is highly application dependent.
 
@@
 Nevertheless, even with accelerated SHTs, the convolutions remain expensive, limiting the practical use of this approach.
-For example with the HEALPix sampling, which was designed to have a fast SHT by being iso-latitude, the computational cost of the SHT is $\bO(N_{pix}^{3/2}) = \bO(N_{side}^3) = \bO(\ell_{max}^3)$, where $\ell_{max}$ is the largest angular frequency\footnote{All pixels are placed on $N_{ring} = 4N_{side}-1 = \bO(\sqrt{N_{pix}})$ rings of constant latitude.
-Each ring has $\bO(\sqrt{N_{pix}})$ pixels.
+For example with the HEALPix sampling, which was designed to have a fast SHT by being iso-latitude, the computational cost of the SHT is $\bO(N_{pix}^{3/2}) = \bO(N_{side}^3) = \bO(\ell_{max}^3)$, where $\ell_{max}$ is the largest angular frequency\footnote{All pixels are placed on $N_{ring} = 4N_{side}-1 = \bO\left(\sqrt{N_{pix}}\right)$ rings of constant latitude.
+Each ring has $\bO\left(\sqrt{N_{pix}}\right)$ pixels.
 Thanks to this iso-latitude property, the SHT is computed using recurrence relations for Legendre polynomials on co-latitude and fast Fourier transforms (FFTs) on longitude.
-The computational cost is thus $\sqrt{N_{pix}}$ FFTs for a total cost of $\bO(N_{pix} \log(\sqrt{N_{pix}}))$, plus $\sqrt{N_{pix}}$ matrix multiplications of size $\sqrt{N_{pix}}$ for a total cost of $\bO(N_{pix}^{3/2})$.}
+The computational cost is thus $\sqrt{N_{pix}}$ FFTs for a total cost of $\bO\left( N_{pix} \log \sqrt{N_{pix}} \right)$, plus $\sqrt{N_{pix}}$ matrix multiplications of size $\sqrt{N_{pix}}$ for a total cost of $\bO\left(N_{pix}^{3/2}\right)$.}
 \citep{gorski2005healpix, reinecke2013libsharp}.

### 2018-08-08 scnn.tex
night changes

@@
 \usepackage{url}
-\usepackage{hyperref}
+% \usepackage{hyperref}
+\usepackage[draft]{hyperref}
 \usepackage{graphicx,array} \graphicspath{{figures/}}
@@
     \item (MD+NP) talk about the loss in 3.8 (old 4.8)
-    \item (NP) make figure A.13 remove white space
-    \item (NP+MD)  paragraph on our chosen architecture in the Experiments sections
+    \item (done!) (NP) make figure A.13 remove white space
+    \item (firsr version done!)(NP+MD)  paragraph on our chosen architecture in the Experiments sections
     \item (NP) vertex interpretation
+    \item (MD) Are you happy with the vertex interpretation in section 3.5 Efficient convolutions?
     \item (NP) Finalise readme on Github code
@@
     \item check if papers which appear as arxiv were not published in a conference or journal
-    \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings.
+    \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings. \nati{I think this is too much for this paper.}
     \item TK check part sphere notebook and whole sphere
@@
     \item (done!) (TK) uniformize text size in figures
-    \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook.
+    \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
     \item (done!) (TK) re-make figures to make the labels/legend/titles the same font size as the main text
@@
     % \item (done!) (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
+    % \item \todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
+    % Nati: I did it without this notation. Since we have two architectures, I think it is OK.
 \end{itemize}
@@
 \end{equation}
+We would like to emphasis that traditional convolution can be written in the same form as \eqnref{graph_convolution_spatial}.
+Given $f,g$ two 1 dimentional discrete signals, their convolution can be written as
+\begin{equation}
+(f \ast g) (n) = \sum_{m=-\infty}^\infty f(m) g(n-m) = \langle T_n g,  f \rangle,
+\end{equation}
+where $T_n g(m)=g(n-m)$ is (up to a flip) a translation operator.
+
 In \ref{sec:heat_diffusion}, we present an example application of graph-based convolution to a simple heat-diffusion problem in order to shed some light on what is the convolution on a graph.
-% \textbf{Example.}
-% Let us consider the heat diffusion problem
-% \begin{equation} \label{eqn:heat_equation}
-% 	\L \b{f}(t) = \tau \partial_t \b{f}(t),
-% \end{equation}
-% where $\b{f}: \R_+ \rightarrow \R^{N_{pix}}$. Given the initial condition
-% $\b{f}(0)$, the solution of~\eqnref{heat_equation} can be expressed as
-% \begin{equation*}
-% 	\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U\trans \g{f}(0) = K_t(\L) \b{f}(0),
-% \end{equation*}
-% which is, by definition, the convolution of the signal $\b{f}(0)$ with the kernel $K_t(\lambda)=e^{-\tau t \lambda}$.
-Since the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$, which can be interpreted as squared frequencies, it can also be considered as a generalization of the Gaussian kernel on the sphere.
-\figref{gaussian_filters_comparizon} shows the effect of the convolution by diffusing a unit of heat for $\tau=1$ at various times $t$.
-By comparing the graph convolution with the spherical symmetric Gaussian smoothing, we observe that both techniques lead to similar results (see \figref{gaussian_filters_comparizon}).
-While the graph convolution remains different from the spherical convolution, this small experiment shows that, providing the correct parameters, graph convolution can approximate spherical convolution.
-For additional insides about the graph kernel $K_t$, we refer to the \figref{gaussian_filters_visualization} and~\ref{sec:filter_visualization}.
-
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=\linewidth]{gaussian_filters_sphere}
-% 	\caption{Comparison of convolution with the graph and the spherical harmonics ($N_{side} = 16$).
-% 	Top: Diffusion of a unit of heat for different times $t$ using the graph.
-% 	Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin).
-% 	Relative difference between graph convolution and spherical smoothing: $10.4$\%, $4.8$\%, $3.8$\%.
-% \todo{The main issue with our filters is that their shape depends on the localization.
-It would be nice to measure the expectation and variance of the error over all locations.
-That would show how severe the distortion is.}
-% \nati{Let us keep that for the next paper. I am quite sure, it is negligible in this particular case.}}
-% 	\label{fig:gaussian_filters_comparizon}
-% \end{figure}
-
-% Furthermore, this result is another sign that the constructed graph is able to capture the spherical
-% structure of the HEALPix sampling. In some applications, where the
-% exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
-% The fact that both convolutions are not identical is not relevant in a neural network setting, as the convolution kernels are learned anyway.
-% not ideal tho as the graph convolution depends on the localization
 
@@
 Similarly, each lines of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an "irregular patch of radius $K$" for our irregular domain.
-\todo{Better vertex domain explanation. \nati{I gave it a try. Should we take a single vertex and explain what heppens to it? Note that I suppressed the following paragraph. }}
-\TK{For me it's understandable:)}
+% \todo{Better vertex domain explanation. 
+% \nati{I gave it a try. Should we take a single vertex and explain what heppens to it? Note that I suppressed the following paragraph. }}
+% \TK{For me it's understandable:)}
 
@@
 On the contrary the amplitude of $x^k$ is very different for $|x|\approx 0$ and $|x| \approx 1$.}.
-\nati{I added a sentence and I think we should not give much more details here. If we do an experiment, we can comment in the experiment section.}
-\todo{(i) scale of $\theta_k$: they are mostly uniform for Chebyshev polynomials, end exploding for monomials. Though SGD implicitly imposes a uniform prior on the learned parameters.}
-\todo{(ii) numerical stability of $\L^k \f$ v.s. $T_k(\L) \f$}
-\todo{(iii) in the code, initialize $\theta_k$ with stdev adapted to $F_{in}$ and $K$}
+% \nati{I added a sentence and I think we should not give much more details here. If we do an experiment, we can comment in the experiment section.}
+% \todo{(i) scale of $\theta_k$: they are mostly uniform for Chebyshev polynomials, end exploding for monomials. Though SGD implicitly imposes a uniform prior on the learned parameters.}
+% \todo{(ii) numerical stability of $\L^k \f$ v.s. $T_k(\L) \f$}
+% \todo{(iii) in the code, initialize $\theta_k$ with stdev adapted to $F_{in}$ and $K$}
 
@@
 
-\todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
-
 \section{Related work}
@@
 While each of those twelve grids could potentially be independently fed into a 2D CNN, boundary conditions would have to be properly handled, as those grids are not independent.
-\todo{How do they handle boundaries?}
-\TK{+1,good question}
-\nati{They are almost not talking about that. For the cubed sphere, the only reference I could found was:
-\emph{"When implementing convolutions and pooling operations for the cubed-sphere grid, one has to be careful in padding each patch with the contents of the four neighbouring patches, in order to preserve the wrapped topology of the sphere (figure 2, right)."}
-Note that for the cubed sphere sampling each pixel has exactly four neighboors which make the problem of border effect handable.
+% \todo{How do they handle boundaries?}
+% \TK{+1,good question}
+% \nati{They are almost not talking about that. For the cubed sphere, the only reference I could found was:
+% \emph{"When implementing convolutions and pooling operations for the cubed-sphere grid, one has to be careful in padding each patch with the contents of the four neighbouring patches, in order to preserve the wrapped topology of the sphere (figure 2, right)."}
+% Note that for the cubed sphere sampling each pixel has exactly four neighboors which make the problem of border effect handable.
 As for the equirectangular grid, it is equivalent to a cylinder.
 So I guess they take the standard image processing border conditions (reflective).
-I do not think we should mention any of that in the paper.
-}
+% I do not think we should mention any of that in the paper.
+% }
 % Furthermore, the grid requirement makes it impossible for the convolution to capture the spherical properties of the domain, i.e., the cubed-sphere sampling is by definition adapted to a cube and not to a sphere.
@@
 
+\nati{There is a break here...}
 The graph setting used through this contribution assumes reflective border conditions.

### 2018-08-08 scnn.tex
update link convolution

@@
     \item (firsr version done!)(NP+MD)  paragraph on our chosen architecture in the Experiments sections
-    \item (NP) vertex interpretation
-    \item (MD) Are you happy with the vertex interpretation in section 3.5 Efficient convolutions?
+    \item (Done) (NP) vertex interpretation 
+    \item (MD) Are you happy with the vertex interpretation in section 3.5 Efficient convolutions? Also do you like the end of 3.4?
     \item (NP) Finalise readme on Github code
@@
 It can however be localized on any vertex $v_i$ by the convolution with a Kronecker delta $\b \delta_i \in \R^{N_{pix}}$,\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} that is $h(\L) \b \delta_i$, a column of $h(\L)$.
-This localization can be useful to visualize kernels as explained in~\ref{sec:filter_visualization}.
+This localization of the kernel $h$ can be useful to visualize kernels as explained in~\ref{sec:filter_visualization}.
 If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another.
@@
 However, when considering only parts of the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).
-Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with all localizations of the kernel:
+Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with the localizations of the kernel $h$, i.e. 
 \begin{equation} \label{eqn:graph_convolution_spatial}
@@
 Given $f,g$ two 1 dimentional discrete signals, their convolution can be written as
-\begin{equation}
+\begin{equation} \label{eqn:standard_convolution}
 (f \ast g) (n) = \sum_{m=-\infty}^\infty f(m) g(n-m) = \langle T_n g,  f \rangle,
 \end{equation}
-where $T_n g(m)=g(n-m)$ is (up to a flip) a translation operator.
+where $T_n g(m)=g(n-m)$ is, up to a flip, a translation operator. As a result, the convolution is simply the scalar product with the translated kernel $g$.
+Additionally to the fact that \eqnref{graph_convolution_spatial} and \eqnref{standard_convolution} are both scalar product, it turns out that the localization operator $h(\L) \b \delta_i$ is some generalization of the translation for graphs.
+Furthermore that in the particular case where the Laplacian matrix $\L$ is circulant, $h(\L) \b \delta_i$ is a translated version of $h(\L) \b \delta_j$ for all $i,j$ and both convolution are equivalent.
+For a detailled explanation of the connection between translation and localization, refer to \citep[Sec 2.2]{perraudin2017stationary}.
 

### 2018-08-08 scnn.tex
update appendix

@@
 
-\author{}
+\author{Nathanaël Perraudin, Michaël Defferrard and Tomasz Kacprzak}
 
@@
 \label{sec:comparison_spherical_harmonics}
-\label{sec:border_effects}
-
-The eigenvalues of the graph Laplacian $\L$, shown in \figref{graph_eigenvalues}, are clearly organized in frequency groups of $2\ell + 1$ orders for each degree $\ell$.
 The first 16 eigenvectors $[\b u_1, \ldots, \b u_{16}]$ of the graph Laplacian $\L$, forming the lower part of the graph Fourier basis $\U$, are shown in \figref{graph_harmonics}. 
-\figref{subspace_harmonics_eigenvectors} shows the correspondence between the subspaces spanned by the graph Fourier modes and the spherical harmonics.
-While there is again a clear resemblance with the spherical harmonics, the small irregularities in the sampling (non-constant number of neighboring pixels and varying distance between pixels, see \figref{healpix_graph_4}) have an effect on the graph Fourier modes.
-First, counter-intuitively, some eigenvectors will be localized~\citep{perraudin2018global}, i.e, they will span a small part of the sphere.
+Let us further observe the spectral properties of our constructed spherical graph laplacian $\L$. 
+Its eigenvalues, shown in \figref{graph_eigenvalues}, are clearly organized in frequency groups of $2\ell + 1$ orders for each degree $\ell$.
+We remind the reader that the amplitude of the Laplacian eigenvalue is proportional to the sum of the variations of its associated eigenvector.
+Furthermore, all spherical harmonics with the same order $\ell$ have the same variation.
+Hence, the fact that the Laplacian eigenvalues are grouped by $2\ell + 1$ is an hint that the graph eigenvectors approximate the spherical harmonics.
+In order to push the comparison one step further, we shows the correspondence (scalar product) between the subspaces spanned by the graph Fourier modes and the spherical harmonics in \figref{subspace_harmonics_eigenvectors}.
+The block-diagonal structure of the matrix, as opposed to diagonal, results the fact that the phase of the graph eigenvector is not aligned with the one of the spherical harmonics.
+
+While these indications show that the constructed graph Fourier basis approximates well the spherical harmonics, one should not forget that the small irregularities in the sampling (non-constant number of neighboring pixels and varying distance between pixels, see \figref{healpix_graph_4}) have an important effect on the graph Fourier modes.
+First, we believe that they are responsible for energy leaking outside of the block diagonal in \figref{subspace_harmonics_eigenvectors}. 
 Second, as the resolution is increased with $N_{side} \rightarrow \infty$ and $N_{pix} \rightarrow \infty$, we are still unsure if the eigenvectors would converge towards the spherical harmonics.
@@
 That is however out of the scope of this contribution.
+Third, counter-intuitively, some eigenvectors will be localized~\citep{perraudin2018global}, i.e, they will span a small part of the sphere. 
+Nevertheless, our experiments suggest that the theses downsides do not have an important effect on the convolution nor hinder the performance of the neural network.
 
@@
 
-\nati{There is a break here...}
-The graph setting used through this contribution assumes reflective border conditions.
-That is irrelevant when working on the complete sphere as this surface has no border.
-When working with a part of the sphere however, its border slightly affects the convolution.
+\section{Border effects}
+\label{sec:border_effects}
+
+One should not forget that a significant part of our analysis is done with a full sphere and that in practice we often use only part of the graph as the data may be incomplete (see \figref{example_maps}).
+In this case, the graph setting used through this contribution correspond to assume reflective border conditions.
+It is irrelevant when working on the complete sphere as this surface has no border. Nevertheless, dealing working with a subpart of the sphere, its border slightly affects the convolution. 
 As depicted in \figref{border_effects}, a filter localized near the border of a part of the sphere (via $h(\L) \b \delta_i$) no longer has an isotropic profile. 
@@
 \label{sec:heat_diffusion}
+\label{sec:filter_visualization}
 
@@
 While the graph convolution remains different from the spherical convolution, this small experiment shows that, providing the correct parameters, graph convolution can approximate spherical convolution.
-For additional insides about the graph kernel $K_t$, we refer to the \figref{gaussian_filters_visualization} and~\ref{sec:filter_visualization}.
+For additional insides about the graph kernel $K_t$, we refer to the \figref{gaussian_filters_visualization}.
+% and~\ref{sec:filter_visualization}.
 
@@
   Relative difference between graph convolution and spherical smoothing: $10.4$\%, $4.8$\%, $3.8$\%.
-\todo{The main issue with our filters is that their shape depends on the localization.
+% nati: I commented this issue as this is already in appendix and it will go a bit too far. We will not do an appendix of appendix :-).
+% \todo{The main issue with our filters is that their shape depends on the localization.
 It would be nice to measure the expectation and variance of the error over all locations.
 That would show how severe the distortion is.}
-\nati{Let us keep that for the next paper. I am quite sure, it is negligible in this particular case.}}
+% \nati{Let us keep that for the next paper. I am quite sure, it is negligible in this particular case.}
+}
   \label{fig:gaussian_filters_comparizon}
@@
 
-\section{Filter visualization}
-\label{sec:filter_visualization}
+% \section{Filter visualization}
+% \label{sec:filter_visualization}
 
@@
 
-In \figref{gaussian_filters_visualization}, we present three different
-visualization for a HEALPix graph convolution kernel.
-The kernel used is defined in the graph spectral domain as $K_t(x)=e^{-\tau t x}$.
-This is the domain used for our first visualization.
-In this case, we simply evaluate $K_t$
-at the graph eigenvalues $\text{diag}(\bLambda)$. The lower eigenvalues $\lambda$ correspond to the lower frequencies, i.e., the spectral mode with less variation.
-As a second visualization, we can observe the kernel directly on the sphere. To do so, we perform the convolution of a
-Kroneker on the sphere plot the result with gnomonic projection. Eventually, as we are
-working on the sphere with theoretically spherical filters (up to the irregularities of the sampling), we could only plot the section of the convoluted Kroneker.
+In \figref{gaussian_filters_visualization}, we further leverage this example to present the three visualization of a HEALPix graph convolution kernel.
+We remember that the convolution kernel resulting from the heat diffusion is defined as $K_t(x)=e^{-\tau t x}$. For our visualization, we simply plot this function, i.e., we evaluate $K_t$
+at the graph eigenvalues $\text{diag}(\bLambda)$. Note that, the lower eigenvalues $\lambda$ correspond to the lower frequencies, i.e., the spectral mode with less variation.
+As a second visualization, we observe the kernel directly on the sphere.
+As the kernel $K_t$ is defined in the graph spectral domain, we convolve a Kroneker to obtain a representation on the sphere.
+We then plot the result with gnomonic projection.
+For our third visualization, we leverage the fact that we are working on the sphere and hence theoretically have  spherical filters (up to the irregularities of the sampling).
+We plot the section of the convoluted Kroneker.
 % To do so, we convolve a Kroneker on the equator and use the equator for our section as shown in~\figref{index_section}.

### 2018-08-08 scnn.tex
finish pass on Appendix

@@
     \item (done!) (NP) make figure A.13 remove white space
-    \item (firsr version done!)(NP+MD)  paragraph on our chosen architecture in the Experiments sections
+    \item (first version done!)(NP+MD) paragraph on our chosen architecture in the Experiments sections
     \item (Done) (NP) vertex interpretation 
@@
 
-We show that the modelling the discretised sphere by a graph enables an efficient convolution operation on HEALPix sampling.
+We show that the modeling the discretised sphere by a graph enables an efficient convolution operation on HEALPix sampling.
 % Hence, it relaxes the iso-latitude constraint on sampling schemes who aim to enable fast convolutions.
@@
 This work was supported by a grant from the Swiss Data Science Centre (SDCS) under project ID \textit{sd01 - DLOC:  Deep Learning for Observational Cosmology} and grant number 200021\_169130 from the Swiss National Science Foundation.
-
+\nati{@Tomek: do we need to thank Janis?}
 %% The Appendices part is started with the command \appendix;
@@
 When comparing the network to the baselines, we want to ensure that the SVM classifier has
-access to the same amount of data that the network, i.e, potentially an
+access to the same amount of data than the network, i.e, potentially an
 infinite number of samples. Hence, we fit different linear SVM classifiers using
-various training set size until we observe experimentally that
+various training set size until we experimentally observe that
 increasing the amount of data does not improve the accuracy. The validation

### 2018-08-08 scnn.tex
small update

@@
 
-    \item (MD+NP) talk about the loss in 3.8 (old 4.8)
+    \item (MD+NP) talk about the loss in 3.8 (old 4.8) \nati{I was very brief. In color for now.}
     \item (done!) (NP) make figure A.13 remove white space
@@
 where $i$ is the correct class label.
+\todo{For a regression task, the most common choice is the $L^2$ norm $\ell(\y) = \|\y-\bar{\y}\|_2^2$, where $\bar{\y}$ is the desired output, as it minimize the mean square error.
+We emphasis that by sole change of the loss, one can solve regularization instead of classification.}
+
 The parameters $\theta$ of the neural network are optimized to minimize the loss over the training dataset $\left\{ \X_i \right\}_{i=1}^{N_{samples}}$:

### 2018-08-08 scnn.tex
draft related work

@@
     \item (done!) (TK) add section in conclusions/ paragraph on possible extensions to the code: dense output, regression, GANs, segmentation
+	\item Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
     % \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
@@
 
-\citet{boomsma2017spherical} apply a standard 2D CNN to a grid discretization of the sphere.
-Two grids, illustrated in \figref{sphere_grids}, are used in their work: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}.
-As this formulation uses the standard 2D convolutions, all the optimizations developed for 2D images can be applied, what make it computationally very efficient.
-It is, however, restricted to those grid sampling sets.
-Similarly to the cubed-sphere, HEALPix is a composition of twelve grids.
-While each of those twelve grids could potentially be independently fed into a 2D CNN, boundary conditions would have to be properly handled, as those grids are not independent.
-% \todo{How do they handle boundaries?}
-% \TK{+1,good question}
-% \nati{They are almost not talking about that. For the cubed sphere, the only reference I could found was:
-% \emph{"When implementing convolutions and pooling operations for the cubed-sphere grid, one has to be careful in padding each patch with the contents of the four neighbouring patches, in order to preserve the wrapped topology of the sphere (figure 2, right)."}
-% Note that for the cubed sphere sampling each pixel has exactly four neighboors which make the problem of border effect handable.
-As for the equirectangular grid, it is equivalent to a cylinder.
-So I guess they take the standard image processing border conditions (reflective).
-% I do not think we should mention any of that in the paper.
-% }
+\citet{boomsma2017spherical} propose to apply a standard 2D CNN to a grid discretization of the sphere.
+Two pixelisations, illustrated in \figref{sphere_grids}, were used: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}.
+As this formulation uses the standard 2D convolutions, all the optimizations developed for 2D images can be applied, what make it computationally efficient.
+Some losses are due to the handling of boundary conditions, for example by padding a grid with the content of the opposite side (equirectangular) or of the neighboring grids (cubed-sphere, HEALPix).
+%It is, however, restricted to those grid sampling sets.
+As many pixelizations are based on the subdivision of a base polyhedron
+Similarly to the cubed-sphere, HEALPix is made of twelve grids. As those grids are not independent, each grid has to be  to handle , .
 % Furthermore, the grid requirement makes it impossible for the convolution to capture the spherical properties of the domain, i.e., the cubed-sphere sampling is by definition adapted to a cube and not to a sphere.
@@
 % Moreover, those samplings are not ideal as their resolution is not constant across the sphere.
-Moreover, the pixel area is not constant across the sphere in those sampling schemes, which may limit their potential applications.
-Indeed, the singularities, such as the poles for the equirectangular grid, and the corners of the cube for the cubed-sphere, are over-sampled.
-Equal areas of discrete elements is advantageous for many physical measurements, as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence \citep{gorski2005healpix}.
+
+% Moreover, the pixel area is not constant across the sphere in those sampling schemes, which may limit their potential applications.
+% Indeed, the singularities, such as the poles for the equirectangular grid, and the corners of the cube for the cubed-sphere, are over-sampled.
+% Equal areas of discrete elements is advantageous for many physical measurements, as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence \citep{gorski2005healpix}.
+% => 2D CNN can be applied on HEALPix as well.
+
 % \nati{Michael: Under some very specific hypothesis, this second approach is a particular case of our method, i.e.
@@
 To remove this information, we additionally smooth the spherical maps with a Gaussian kernel of radius $3$ arcmin.
-The resulting Power Spectrum Density (PSD), computed using the \texttt{anafast} function in the HEALpix package, are displayed in \figref{psd_sigma3}.
+The resulting Power Spectrum Density (PSD), computed using the \texttt{anafast} function in the HEALPix package, are displayed in \figref{psd_sigma3}.
 In the pre-processing step, we also remove the mean of each map and downsample them to a resolution of of $N_{side}=1024$.
@@
 We show that the modeling the discretised sphere by a graph enables an efficient convolution operation on HEALPix sampling.
-% Hence, it relaxes the iso-latitude constraint on sampling schemes who aim to enable fast convolutions.
-% \TK{I would move the info about possible relaxation of the iso-latitude thing to a separate paragraph at the end on conclusions - future prospects?}
 Graph-based representation of the sphere can display small imprecisions in rotation invariance, the result of which is that an action of a graph filter slightly depends on the location.
 For applications that can tolerate this property, a graph-based representation may be a worthwhile alternative.
-% this relaxation might enable researchers to consider sampling sets with different properties.
-% \TK{this I don't understand}
 For example, a machine learning based cosmological inference algorithm can in principle tolerate this property, as it requires the simulations to be represented the same way as observations anyway.
@@
 
+% Hence, it relaxes the iso-latitude constraint on sampling schemes who aim to enable fast convolutions.
+% \TK{I would move the info about possible relaxation of the iso-latitude thing to a separate paragraph at the end on conclusions - future prospects?}
+% this relaxation might enable researchers to consider sampling sets with different properties.
+% \TK{this I don't understand}
+
 \section*{Acknowledgements}
+
 This work was supported by a grant from the Swiss Data Science Centre (SDCS) under project ID \textit{sd01 - DLOC:  Deep Learning for Observational Cosmology} and grant number 200021\_169130 from the Swiss National Science Foundation.
 \nati{@Tomek: do we need to thank Janis?}
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
+We would like to thank Jean-François Cardoso for helpful discussions about the spherical harmonics.
+
 \appendix

### 2018-08-09 scnn.tex
update in result section

@@
 Hence, we assume that each pixel carries some information about the distribution.
-Thanks to 6 graph convolution layers (GC sizes: 16, 32, 64, 64, 64, 2) we first build the stistical evidence of each distribution for each pixel of a downsampled sphere.
+Our principal architecture is a fully convolutional network (FCN).
+Thanks to 6 graph convolution layers (GC sizes: 16, 32, 64, 64, 64, 2) we first build the statistical evidence of each distribution for each pixel of a downsampled sphere.
 The last graph convolution layer is compose of 2 channels as we have 2 distributions.
@@
 \begin{equation}
-NN = SM \circ ST_{\text{mean}} \circ L_6 \circ L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1
+FCN = SM \circ ST_{\text{mean}} \circ L_6 \circ L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1
 \end{equation}
 where
-\begin{itemize}
-    \item layer 1: $L_1 = P  \circ \sigma \circ BN  \circ GC_{16}$,
-    \item layer 2: $L_2 = P  \circ \sigma \circ BN  \circ GC_{32}$,
-    \item layer 3-5: $L_3 = L_4 = L_5= P \circ  \sigma \circ BN  \circ GC_{64}$,
-    \item layer 6: $L_6 = \sigma \circ BN  \circ GC_{2}$.
-\end{itemize}
-
-\todo{We use the ADAM optimizer, \cite{kingma2014adam}, with an initial learning rate of $2e-4$ that is exponentially decreased by $0.98$ a $100$ times to end at $2.7e-5$.
-All models where trained $80$ epochs with a batch size of $16\times o^2$. With this choice, all models recieve an identical amount of data within a batch and were trained with $1920$ gradient steps.}
-Training took less \nati{queue bottleneck to be fixed} than $3$ hours for each model using a single NVIDIA Tesla K20.
+\begin{tabular}{lll}
+   $L_1$ & $ = P  \circ \sigma \circ BN  \circ GC_{16}$ \\
+   $L_2$ & $ = P  \circ \sigma \circ BN  \circ GC_{32}$ \\
+   $L_3,L_4,L_5$ & $= P \circ  \sigma \circ BN  \circ GC_{64}$ \\
+   $L_6$ & $ = \sigma \circ BN  \circ GC_{2}$ \\
+\end{tabular}
+Thanks to its statistical layer, the FCN architecture is almost (because of the sampling irregularities) equivariant to rotation.
+We also tried a more traditional architecture, where the statistical and last convolutional layers are replaced by a fully connected layer.
+Hence we end up with a convolutional neural network (CNN) that is not equivariant to rotation anymore.
+The network can be summarized as
+\begin{equation}
+CNN = SM \circ \sigma \circ FC_2 \circ L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1.
+\end{equation}
+We use the ADAM optimizer, \cite{kingma2014adam}, with $\beta_1=0.9$, $\beta_2=0.999$ and an initial learning rate of $2e-4$ that is exponentially decreased by $0.999$ at each step.
+All models where trained $80$ epochs with a batch size of $16\times o^2$. With this choice, all models receive an identical amount of data within a batch and were trained with $1920$ gradient steps.
+Training took less than $4$ hours for each model using a single NVIDIA Tesla K20.
 
@@
 Classification errors for the 3 different areas of the sphere.
-Green lines show the performance of the CNN, blue of the PDF+SVM, and red of the histogram+SVM.
+Green lines show the performance of the FCN,CNN, blue of the PDF+SVM, and red of the histogram+SVM.
 % Green dashed line corresponds to the performance of CNN without the statistical layer.
@@
 \figref{results} presents the results for $5$ different noise levels and $3$ different sample areas.
-The spherical CNN has a significant lead for all levels of noise and sample areas.
+HealPixNet (FCN and CNN) has a significant lead for all levels of noise and sample areas.
 In particular, the difference seems to increase as the problem becomes more complex; as the order is increased, there is less information in each sample.
@@
 In contrast, both the PSD features and the HealpixNet can exploit the spatial information.
+
 % Note that without this graph structure, a fully connected neural network approach would have to be used.
@@
 
-We tried several different spherical neural network architectures and observed the following results.
+While testing the FCN and CNN architecture we made the following empirical observations:
 First, Chebyshev polynomial seems more stable than monomials ($\theta_k$ in \eqnref{graph_convolution_polynomial}), in the sense that the training loss had a more steadily decrease.
 Nevertheless once the network is trained, we could not observe a significant accuracy difference.
-Second, using a statistical layer slightly improved the accuracy in our problem.
+Second, using a statistical layer (FCN) to get equivariant features slightly improved the accuracy in our problem.
 We tried $4$ different layers `mean', `variance', `mean + variance' and `histogram'.
@@
 Third, adding fully connected layers after the statistical layer does not improve the performance, but lead to models requiring more training steps and regularization.
-\todo{Fourth, using $\ell_2$ regularization does not help neither with the performance nor the training of the models, but slightly reduce the performance variance between different runs due to the random initialization.
-Eventually, recommend to ignitialize the Chebyshev coeffecient with a centered Gaussian distribution with standart deviation $2/(F * (K + 0.5))$, where $K$ is the Chebyshef order and $F$ the number of input channels.
-The
-}
+Fourth, using $\ell_2$ regularization does not help neither with the performance nor the training of the models.
+Fifth, we recommend to initialize the Chebyshev coefficients with a centered Gaussian distribution with standard deviation $\sqrt{2/(F * (K + 0.5))}$, where $K$ is the Chebyshev order and $F$ the number of input channels.
+This standard deviation has the property to keep the energy of the signal more or less at the same level between the different layers.
+Eventually, we observe that rescaling the Laplacian eigenvalues between $[-a,a]$, where $1<a\leq1$ significantly helps to stabilize the optimization. For our experiment we use $a=0.75$.
 
@@
 \includegraphics[width=0.45\linewidth]{gnonomic_filter_last}
-\caption{24 learned filters selected from the last spherical convolutional layer. Left: section. Right: gnonomic view.}
+\caption{24 learned filters selected from the fifth spherical convolutional layer $L_5$. Left: section. Right: gnonomic view.}
 \label{fig:learned_filter}

### 2018-08-09 scnn.tex
correct typos

@@
 We demonstrate the method on a classification problem of mass maps from two cosmological models and compare the performance of the CNN with that of two baseline classifiers, based on the power spectrum and pixel density histogram.
-Our experimental result show that the performance of HealpixNet to always better or equal to both of these baselines.
+Our experimental result shows that the performance of HealpixNet to always be better or equal to both of these baselines.
 For high noise levels and for data covering only a smaller fraction of the sphere, HealpixNet achieves typically 10\% better classification accuracy than those baselines.
@@
 The resulting Power Spectrum Density (PSD), computed using the \texttt{anafast} function in the HEALPix package, are displayed in \figref{psd_sigma3}.
-In the pre-processing step, we also remove the mean of each map and downsample them to a resolution of of $N_{side}=1024$.
+In the pre-processing step, we also remove the mean of each map and down-sample them to a resolution of of $N_{side}=1024$.
 
@@
 % \end{figure}
-For all the experiments, we work with centred Gaussian noise.
+For all the experiments, we work with centered Gaussian noise.
 While the noise model of real mass maps often has a slightly different distribution, Gaussian should be a sufficient model to demonstrate the performance of our method.
@@
 % To improve the stability of the spherical CNN, we slowly increase the amount of noise added to the training data over the iterations.
-Furthermore in order to avoid overfitting, the noise is randomly produced during the training process.
+Furthermore in order to avoid over-fitting, the noise is randomly produced during the training process.
 The $20\%$ of the training set that we call \emph{validation set} was left out of the training process and simply used to assess the global performance of the network.
@@
 \subsection{Selected architecture}
-The design of an neural network architecture highly depends on the problem at hand.
-In our case, we are trying to discriminate samples of two distributions cosmologicals maps.
+The design of a neural network architecture highly depends on the problem at hand.
+In our case, we are trying to discriminate samples of two cosmological maps.
 Hence, we assume that each pixel carries some information about the distribution.
 Our principal architecture is a fully convolutional network (FCN).
-Thanks to 6 graph convolution layers (GC sizes: 16, 32, 64, 64, 64, 2) we first build the statistical evidence of each distribution for each pixel of a downsampled sphere.
-The last graph convolution layer is compose of 2 channels as we have 2 distributions.
+Thanks to 6 graph convolution layers (GC sizes: 16, 32, 64, 64, 64, 2) we first build the statistical evidence of each distribution for each pixel of a down-sampled sphere.
+The last graph convolution layer is composed of 2 channels as we have 2 distributions.
 Then we use a statistical 'mean' layer (SL) to average the evidence for each distribution and we compute the probabilities thanks to a softmax layer (SM).
@@
 We use the ADAM optimizer, \cite{kingma2014adam}, with $\beta_1=0.9$, $\beta_2=0.999$ and an initial learning rate of $2e-4$ that is exponentially decreased by $0.999$ at each step.
-All models where trained $80$ epochs with a batch size of $16\times o^2$. With this choice, all models receive an identical amount of data within a batch and were trained with $1920$ gradient steps.
+All models were trained $80$ epochs with a batch size of $16\times o^2$. With this choice, all models receive an identical amount of data within a batch and were trained with $1920$ gradient steps.
 Training took less than $4$ hours for each model using a single NVIDIA Tesla K20.
@@
 
-While testing the FCN and CNN architecture we made the following empirical observations:
-First, Chebyshev polynomial seems more stable than monomials ($\theta_k$ in \eqnref{graph_convolution_polynomial}), in the sense that the training loss had a more steadily decrease.
+While testing the FCN and CNN architectures, we made the following empirical observations:
+First, Chebyshev polynomial seems more stable than monomials ($\theta_k$ in \eqnref{graph_convolution_polynomial}), in the sense that the training loss had a more monotone decrease.
 Nevertheless once the network is trained, we could not observe a significant accuracy difference.
@@
 Third, adding fully connected layers after the statistical layer does not improve the performance, but lead to models requiring more training steps and regularization.
-Fourth, using $\ell_2$ regularization does not help neither with the performance nor the training of the models.
-Fifth, we recommend to initialize the Chebyshev coefficients with a centered Gaussian distribution with standard deviation $\sqrt{2/(F * (K + 0.5))}$, where $K$ is the Chebyshev order and $F$ the number of input channels.
+Fourth, using $\ell_2$ regularization does not help either with the performance or the training of the models.
+Fifth, we recommend initializing the Chebyshev coefficients with a centered Gaussian distribution with standard deviation $\sqrt{2/(F * (K + 0.5))}$, where $K$ is the Chebyshev order and $F$ the number of input channels.
 This standard deviation has the property to keep the energy of the signal more or less at the same level between the different layers.
@@
 The filters are selected from the last layer of the network corresponding the experiment with order $o=2$ for a relative noise level of $2$.
-Nevertheless, all networks presented visually similar gnomonic and profile pattern.
+Nevertheless, all networks presented visually similar gnomonic and profile patterns.
 % The gnomonic projection clearly exibits the sampling issue of HEALPix.
 % \TK{what issue? Commenting out for now}
-Detail of how the convolution kernels are plotted are described in \ref{sec:filter_visualization}.
+Details of how the convolution kernels are plotted are described in \ref{sec:filter_visualization}.
 While it is usually difficult to interpret the shape of the filters in the context of the type of data, we can notice that they often have a ``peak'' like structures.
@@
 Furthermore, all spherical harmonics with the same order $\ell$ have the same variation.
-Hence, the fact that the Laplacian eigenvalues are grouped by $2\ell + 1$ is an hint that the graph eigenvectors approximate the spherical harmonics.
-In order to push the comparison one step further, we shows the correspondence (scalar product) between the subspaces spanned by the graph Fourier modes and the spherical harmonics in \figref{subspace_harmonics_eigenvectors}.
+Hence, the fact that the Laplacian eigenvalues are grouped in blocks of size $2\ell + 1$ is a hint that the graph eigenvectors approximate the spherical harmonics.
+In order to push the comparison one step further, we show the correspondence (scalar product) between the subspaces spanned by the graph Fourier modes and the spherical harmonics in \figref{subspace_harmonics_eigenvectors}.
 The block-diagonal structure of the matrix, as opposed to diagonal, results the fact that the phase of the graph eigenvector is not aligned with the one of the spherical harmonics.
@@
 We believe that it might be the case for a different construction of the graph (fully connected) and that a proof could be built on top of the work of~\cite{belkin2007convergence}.
-That is however out of the scope of this contribution.
+That is, however, out of the scope of this contribution.
 Third, counter-intuitively, some eigenvectors will be localized~\citep{perraudin2018global}, i.e, they will span a small part of the sphere. 
-Nevertheless, our experiments suggest that the theses downsides do not have an important effect on the convolution nor hinder the performance of the neural network.
+Nevertheless, our experiments suggest that these downsides do not have an important effect on the convolution nor hinder the performance of the neural network.
 
@@
 The plot clearly shows how the subspaces are aligned: modes and harmonics which correspond to different degrees $\ell$ are mostly orthogonal to each other, while modes and harmonics which correspond to the same degree $\ell$ are linearly dependent.
-There is $2 \ell + 1$ orders per degree $\ell$.
+There are $2 \ell + 1$ orders per degree $\ell$.
 Moreover, we see that the Fourier modes have the correct symmetries, indicated by the perfect orthogonality between even and odd functions.}
@@
 As depicted in \figref{border_effects}, a filter localized near the border of a part of the sphere (via $h(\L) \b \delta_i$) no longer has an isotropic profile. 
-These border effects can however be mitigated by padding with zeros a small area around the part of interest.
+These border effects can, however, be mitigated by padding with zeros a small area around the part of interest.
 
@@
 By comparing the graph convolution with the spherical symmetric Gaussian smoothing, we observe that both techniques lead to similar results (see \figref{gaussian_filters_comparizon}).
-While the graph convolution remains different from the spherical convolution, this small experiment shows that, providing the correct parameters, graph convolution can approximate spherical convolution.
-For additional insides about the graph kernel $K_t$, we refer to the \figref{gaussian_filters_visualization}.
+While the graph convolution remains different from the spherical convolution, this small experiment shows that, providing the correct parameters, the graph convolution can approximate the spherical convolution.
+For additional insights about the graph kernel $K_t$, we refer to the \figref{gaussian_filters_visualization}.
 % and~\ref{sec:filter_visualization}.
@@
 exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
-The fact that both convolutions are not identical is not relevant in a neural network setting, as the convolution kernels are learned anyway.
-not ideal tho as the graph convolution depends on the localization
+The fact that the graph convolution is not exactly rotational equivariant is probably compensated by the fact that in a neural network setting the convolution kernels are learned.
+\todo{not ideal tho as the graph convolution depends on the localization}
 
@@
 
-In \figref{gaussian_filters_visualization}, we further leverage this example to present the three visualization of a HEALPix graph convolution kernel.
+In \figref{gaussian_filters_visualization}, we further leverage this example to present the three visualizations of a HEALPix graph convolution kernel.
 We remember that the convolution kernel resulting from the heat diffusion is defined as $K_t(x)=e^{-\tau t x}$. For our visualization, we simply plot this function, i.e., we evaluate $K_t$
@@
 As the kernel $K_t$ is defined in the graph spectral domain, we convolve a Kroneker to obtain a representation on the sphere.
-We then plot the result with gnomonic projection.
+We then plot the result with a gnomonic projection.
 For our third visualization, we leverage the fact that we are working on the sphere and hence theoretically have  spherical filters (up to the irregularities of the sampling).
@@
 \label{sec:dataset_augmentation} The original number of samples $480$, $1920$,
-$7680$ respectively for order $o=1,2,4$ is considered small to train deep a architecture,
+$7680$ respectively for order $o=1,2,4$ is considered small to train a deep architecture,
 especially when one desire to build a noise robust
@@
 realization of Gaussian noise. The effect is twofold. First, the network never
-ends up seing the same sample and is less likely to overfit the training set.
+ends up seeing the same sample and is less likely to over-fit the training set.
 Second the trained network will be robust to Gaussian noise.
@@
 When comparing the network to the baselines, we want to ensure that the SVM classifier has
-access to the same amount of data than the network, i.e, potentially an
+access to the same amount of data as the network, i.e, potentially an
 infinite number of samples. Hence, we fit different linear SVM classifiers using

### 2018-08-09 scnn.tex
small modifications

@@
 \usepackage{url}
-% \usepackage{hyperref}
-\usepackage[draft]{hyperref}
+\usepackage{hyperref}
+% \usepackage[draft]{hyperref}
 \usepackage{graphicx,array} \graphicspath{{figures/}}
@@
 
-\section{TODO list}
+\section*{TODO list}
 \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
 
-    \item (MD+NP) talk about the loss in 3.8 (old 4.8) \nati{I was very brief. In color for now.}
+    \item (MD+NP) talk about the loss in 2.8 (old 4.8) \nati{I was very brief. In color for now.}
     \item (done!) (NP) make figure A.13 remove white space
@@
     \item (Done) (NP) vertex interpretation 
-    \item (MD) Are you happy with the vertex interpretation in section 3.5 Efficient convolutions? Also do you like the end of 3.4?
+    \item (MD) Are you happy with the vertex interpretation in section 2.5 Efficient convolutions? Also do you like the end of 2.4?
     \item (NP) Finalise readme on Github code
@@
 	\item Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
+    \item Check names: HealpixNet, Healpix CNN, Healpix FCN
+    \item Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
     % \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
@@
 While this approach uses the well-developed 2D convolution and hierarchical pooling, it is restricted to those specific grid samplings which are highly irregular on the sphere.
-An attempt by~\citet{cohen2018spherical} was to leverage the spherical Fourier transform and to perform the convolution in the spectral domain, thanks to the convolution theorem.
+An attempt by~\citet{cohen2018spherical} was to leverage the spherical Fourier transform and to perform the SO(3) convolution in the spectral domain, thanks to the convolution theorem. 
+The resulting convolution is rotational equivariant, meaning that a rotation of the input implies the same rotation of the output.
 While there exists fast spherical Fourier transforms for some samplings, this approach can still be computationally expensive.
+\todo{Add here the paper of Risi?}
 Finally, the use of a graph to model the discretised sphere was considered by~\citet{khasanova2017graphomni} as well, towards the goal of designing network that were invariant to rotations and translation.
@@
 The design of a neural network architecture highly depends on the problem at hand.
+Convolution layers construct \emph{almost} rotational equivariant features and the statistical layer can turn them into rotational invariant ones.
 In our case, we are trying to discriminate samples of two cosmological maps.
@@
 As a future work, it would be interesting to further investigate the link between the graph Fourier basis and the spherical harmonics.
+Furthermore, the influence of the irregular sampling on the rotational equivariance should be quantified empirically and ideally bounded theoretically.
 Further comparison of HealpixNet to other spherical CNN algorithms, with different sampling schemes, would also be worthwhile.

### 2018-08-09 scnn.tex
final results in the paper

@@
 	\item Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
-    \item Check names: HealpixNet, Healpix CNN, Healpix FCN
+    \item Check names: HealpixNet, HealpixCNN, HealpixFCN
     \item Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
@@
 \subsection{Selected architecture}
-The design of a neural network architecture highly depends on the problem at hand.
+The choice of a particular HealPixNet architecture highly depends on the problem at hand.
 Convolution layers construct \emph{almost} rotational equivariant features and the statistical layer can turn them into rotational invariant ones.
@@
 Hence, we assume that each pixel carries some information about the distribution.
-Our principal architecture is a fully convolutional network (FCN).
+Our principal architecture is a fully convolutional network referred as HealPixFCN.
 Thanks to 6 graph convolution layers (GC sizes: 16, 32, 64, 64, 64, 2) we first build the statistical evidence of each distribution for each pixel of a down-sampled sphere.
@@
 Hence we end up with a convolutional neural network (CNN) that is not equivariant to rotation anymore.
-The network can be summarized as
+The network is referred as HealPixCNN and can be summarized as
 \begin{equation}
@@
 All models were trained $80$ epochs with a batch size of $16\times o^2$. With this choice, all models receive an identical amount of data within a batch and were trained with $1920$ gradient steps.
-Training took less than $4$ hours for each model using a single NVIDIA Tesla K20.
+Training took less than $5$ hours for each model using a single NVIDIA Tesla K20.
+% The CPU is probably slow which explain the 5 hours.
+I believe we could be much faster than that by computer less summaries and improving the data.
+But, Michael, is OKAY to have to margin of improvement :-)
 
@@
 Classification errors for the 3 different areas of the sphere.
-Green lines show the performance of the FCN,CNN, blue of the PDF+SVM, and red of the histogram+SVM.
+Green lines show the performance of the two HealPixNet architectures, blue of the PDF+SVM, and red of the histogram+SVM.
 % Green dashed line corresponds to the performance of CNN without the statistical layer.

### 2018-08-09 scnn.tex
samll edit

@@
 \end{equation}
-where
-\begin{tabular}{lll}
-   $L_1$ & $ = P  \circ \sigma \circ BN  \circ GC_{16}$ \\
-   $L_2$ & $ = P  \circ \sigma \circ BN  \circ GC_{32}$ \\
-   $L_3,L_4,L_5$ & $= P \circ  \sigma \circ BN  \circ GC_{64}$ \\
-   $L_6$ & $ = \sigma \circ BN  \circ GC_{2}$ \\
+\begin{center}
+where \hspace{0.5cm} \begin{tabular}{lll}
+   $L_1$ &  $=$ &$ P  \circ \sigma \circ BN  \circ GC_{16}$ \\
+   $L_2$ &  $=$ &$ P  \circ \sigma \circ BN  \circ GC_{32}$ \\
+   $L_3,L_4,L_5$ & $=$ &$ P \circ  \sigma \circ BN  \circ GC_{64}$ \\
+   $L_6$ &  $=$& $ \sigma \circ BN  \circ GC_{2}$ \\
 \end{tabular}
-Thanks to its statistical layer, the FCN architecture is almost (because of the sampling irregularities) equivariant to rotation.
+\end{center}
+Thanks to its statistical layer, the FCN architecture is close invariant to rotation.
 We also tried a more traditional architecture, where the statistical and last convolutional layers are replaced by a fully connected layer.
-Hence we end up with a convolutional neural network (CNN) that is not equivariant to rotation anymore.
+Hence we end up with a convolutional neural network (CNN) that is not invariant to rotation anymore.
 The network is referred as HealPixCNN and can be summarized as
@@
 
-While testing the FCN and CNN architectures, we made the following empirical observations:
+\nati{Michael: I am highly uncertain of what should be kept in the following paragraph. Maybe the full paragraph should be left out!}
+While testing the FCN and CNN architectures, we made the following empirical observations.
 First, Chebyshev polynomial seems more stable than monomials ($\theta_k$ in \eqnref{graph_convolution_polynomial}), in the sense that the training loss had a more monotone decrease.
@@
 This standard deviation has the property to keep the energy of the signal more or less at the same level between the different layers.
+% Nati to Michael: The problem with the previous claim is that it depends on the non-linarity. Furthermore, does it make sense to make such a claim if we use batch norm?
 Eventually, we observe that rescaling the Laplacian eigenvalues between $[-a,a]$, where $1<a\leq1$ significantly helps to stabilize the optimization. For our experiment we use $a=0.75$.

### 2018-08-09 scnn.tex
update filter figure
four tasks: global and dense classification and prediction

@@
 
-    \item (MD+NP) talk about the loss in 2.8 (old 4.8) \nati{I was very brief. In color for now.}
+	\item (MD) distinction between CNN and FCN
     \item (done!) (NP) make figure A.13 remove white space
@@
 This is the lowest possible complexity for a convolution operation without approximations (e.g. by sketching).
-The flexibility of modelling the data domain with a graph allows to easily model data that spans only a part of the sphere, or data that is not uniformly sampled.
+The flexibility of modeling the data domain with a graph allows to easily model data that spans only a part of the sphere, or data that is not uniformly sampled.
 Our hierarchical pooling strategy exploits a hierarchical pixelisation of the manifold to analyse the data at multiple scales.
@@
 In this work we present and release HealpixNet\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}, an algorithm and software package which implements an efficient CNN on HEALPix maps.
-It is implemented with \pkg{TensorFlow} \citep{abadi2016tensorflow} and is intended to be easy to use out-of-the box for cosmological applications.
+It is implemented with \pkg{TensorFlow} \citep{abadi2016tensorflow} and is intended to be easy to use out-of-the-box for cosmological applications.
+HealpixNet is readily apt to solve four tasks: (i) global classification (i.e., predict a class from a map), (ii) global regression (i.e., predict a set of parameters from a map), (iii) dense classification (i.e., predict a class for each pixel of a map), and (iv) dense regression, (i.e., predict a set of maps from a map).
 As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology and astrophysics, we tailored our method to that particular sampling.
@@
 
-Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
-An example network is
+Given a map $\X \in \R^{N_{pix} \times F_{in}}$, a neural network for global prediction is computing $\y = NN_\theta(\X) \in R^{F_{out}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
+Two example networks for global classification, a CNN and a FCN, are
+\begin{align*}
+	NN &= SM \circ FC \circ \sigma \circ FC \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC, \\
+	NN &= \underbrace{SM \circ ST \circ \sigma \circ GC}_{\text{classifier}} \circ \underbrace{\sigma \circ GC \circ P \circ \sigma \circ BN \circ GC}_{\text{feature extractor}},
+\end{align*}
+where $\circ$ denotes composition, i.e., $(f \circ g)(x) = f(g(x))$.
+The number of features $F_{in}$ depends on the data at hand.
+For the CMB radiation temperature, $F_{in} = 1$.
+For observations in radio frequencies, $F_{in}$ would be equal to the number of surveyed frequencies.
+$F_{in}$ might also be the number of slices in the radial direction.
+The number of predictions $F_{out}$ is either equal to the number of classes $N_{classes}$ for a classification task, or the number of variables to be predicted for a regression task.
+A typical global classification task is to classify maps into cosmological model classes \citep{schmelze2017cosmologicalmodel}.
+A typical global regression task is to infer the parameters of a cosmological model  from maps \citep{fluri2018deep,gupta2018nongaussianinformation}.
+Dense prediction, i.e., predicting $F_{out}$ values per pixel, is obtained by omitting ST and FC layers (P layers, if used, have to be inverted via up-sampling in an encoder-decoder architecture).
+An example network for dense regression is
 \begin{equation*}
-NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC,
+	\Y = NN(\X) = (GC \circ \sigma \circ BN \circ GC)(\X) \in \R^{N_{pix} \times F_{out}}.
 \end{equation*}
-where $\circ$ denotes composition, i.e., $f \circ g = f(g(\cdot))$.
-The number of features $F$ depends on the data at hand.
-For the CMB radiation temperature, $F = 1$.
-For observations in radio frequencies, $F$ would be equal to the number of surveyed frequencies.
-$F$ might also be the number of slices in the radial direction.
-The loss function $\ell(\y) = \ell(NN_\theta(\X))$ is a measure of how good the prediction $\y$ is for the sample $\X$. For a classification task, the loss is usually taken to be the cross-entropy
+Such networks are useful for (i) dense regression, such as denoising a map, interpolating missing values, or predicting a density map given the CMB, or (ii) dense classification, such as segmenting galactic clusters in a \todo{xx} map.
+\todo{TK: please find better cosmological applications.
+Maybe some refs?} We emphasize that the use of FC and ST layers is the sole difference between a neural network engineered for global or dense prediction.
+
+The loss function $\ell(\Y, \bar \Y) = \ell(NN_\theta(\X), \bar \Y)$ measures how good the prediction $\Y$ is for sample $\X$, given the ground truth $\bar \Y$.
+For a classification task, the loss is usually taken to be the cross-entropy
 \begin{equation*}
-	\ell(\y) = -\log(y_i),
+	\ell(\Y, \bar \Y) = - \sum_{i=1}^{N_{pix}} \sum_{j=1}^{N_{classes}} \bar y_{ij} \log(y_{ij}),
 \end{equation*}
-where $i$ is the correct class label.
-\todo{For a regression task, the most common choice is the $L^2$ norm $\ell(\y) = \|\y-\bar{\y}\|_2^2$, where $\bar{\y}$ is the desired output, as it minimize the mean square error.
-We emphasis that by sole change of the loss, one can solve regularization instead of classification.}
-
-The parameters $\theta$ of the neural network are optimized to minimize the loss over the training dataset $\left\{ \X_i \right\}_{i=1}^{N_{samples}}$:
+where $\bar \Y \in \R^{N_{pix} \times N_{classes}}$ is the ground truth label indicator, i.e., $\bar y_{ij} = 1$ if pixel $i$ of sample $\X$ belongs to class $j$ and is zero otherwise.
+For global prediction, the loss is as if $N_{pix} = 1$.
+For a regression task, a common choice is the mean squared error (MSE)
 \begin{equation*}
-	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell(NN_\theta(\X_i)).
+	\ell(\Y, \bar \Y) = \frac{\|\Y-\bar{\Y}\|_2^2}{N_{pix} F_{out}} = \frac{1}{N_{pix} F_{out}} \sum_{i=1}^{N_{pix}} \sum_{j=1}^{F_{out}} (y_{ij} - \bar y_{ij})^2,
 \end{equation*}
-The same architecture with different loss function can also be used for parameter regression \citep{fluri2018deep,gupta2018nongaussianinformation}.
+where $\bar{\Y}$ is the desired output.
+Again, take $N_{pix} = 1$ for global regression.
+We emphasize that the loss and the SM layer is the sole difference between a neural network engineered for classification or regression.
+
+The goal of learning is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = \esp \left[ \ell \left( NN_\theta(\X), \bar \Y \right) \right]$.
+In general, that expectation cannot be computed as the data distribution is unknown.
+We can however minimize an approximation, the empirical risk over the training set $\left\{ \left( \X_i, \bar \Y_i \right) \right\}_{i=1}^{N_{samples}}$:
+\begin{equation*}
+	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell \left(NN_\theta(\X_i), \bar \Y_i \right).
+\end{equation*}
 The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
 \begin{equation*}
-	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
+	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell \left( NN_\theta(\X_i), \bar \Y_i \right)}{\partial \theta} ,
 \end{equation*}
@@
 We use batch normalization (BN), pooling (P) and relu non-linearity $\sigma$ for each convolutional layer.
+The order of the convolution kernel was set to $K=5$.
 The network can be summarized as
@@
 % \TK{Done}
+% Nati: Note that filer are almost not evolving during the training process.
+It is not surprising as our architecture is likely to be overparametrized.
+If we want to have interpretable filters, we probably have to use a much smaller architecture.
 

### 2018-08-09 scnn.tex
fix spelling of HEALPix and HealpixNet

@@
 
-\title{HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications}
+\title{HealpixNet: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications}
 % \title{Efficient Spherical ConvNet with Graph Convolutions for Cosmological Applications}
-% \title{HealpixNet: Efficient spherical Convolutional Neural Network with graphs and Healpix sampling for cosmological applications}
-%\title{HealpixNet: Graph Convolutional Neural Network for efficient spherical convolutions on Healpix sampling for cosmological applications}
+% \title{HealpixNet: Efficient spherical Convolutional Neural Network with graphs and HEALPix sampling for cosmological applications}
+%\title{HealpixNet: Graph Convolutional Neural Network for efficient spherical convolutions on HEALPix sampling for cosmological applications}
 % Graph Convolutional Networks for efficient spherical ???
-% Efficient spherical ??? with GCNs and Healpix sampling
+% Efficient spherical ??? with GCNs and HEALPix sampling
 % (Tomek) How about HealpixCNN? Or HealpixNet? Or HealNet?}
@@
 % Spherical maps appear in many applications, such as the study of phenomena on the Earth for meteorologists or on the sky for cosmologists.
-% A popular format for spherical maps is Healpix, which uses an equal-area, isolatitude sampling.
-% Hence, we present a spherical CNN for analysis of full and partial Healpix maps, which we call HealpixNet.
+% A popular format for spherical maps is HEALPix, which uses an equal-area, isolatitude sampling.
+% Hence, we present a spherical CNN for analysis of full and partial HEALPix maps, which we call HealpixNet.
 % \nati{I am not that we should talk about pooling in the abstract.
@@
 % While the convolution on arbitrary graphs has mostly been sorted out, a general pooling operation has not been discovered so far.
-% As such, while HealpixNet is a special case of a graph CNN, it is tailored to the Healpix sampling of the sphere.
+% As such, while HealpixNet is a special case of a graph CNN, it is tailored to the HEALPix sampling of the sphere.
 % This approach is computationally much more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
@@
 % \begin{itemize}
-%     \item Healpix paper \citep{gorski2005healpix}
+%     \item HEALPix paper \citep{gorski2005healpix}
 %     \item First DES mass maps \citep{chang2017curvedsky}
-%     \item Healpix convolutions with asymetric beams \citep{mitra2011fastpixel}
+%     \item HEALPix convolutions with asymetric beams \citep{mitra2011fastpixel}
 %     \item Mass mapping on the sphere \citep{wallis2017mappingdark}
@@
 The two set of maps were created using the standard cosmological model with two sets of cosmological parameters.
-The classification methods were trained to assign a predicted label using the Healpix maps.
-Both our Python implementation\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments is available online.
+The classification methods were trained to assign a predicted label using the HEALPix maps.
+Both our Python implementation\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are available online.
 
@@
 \figref{results} presents the results for $5$ different noise levels and $3$ different sample areas.
-HealPixNet (FCN and CNN) has a significant lead for all levels of noise and sample areas.
+HealpixNet (FCN and CNN) has a significant lead for all levels of noise and sample areas.
 In particular, the difference seems to increase as the problem becomes more complex; as the order is increased, there is less information in each sample.

### 2018-08-09 scnn.tex
update name HealpixNet

@@
 Hence, we assume that each pixel carries some information about the distribution.
-Our principal architecture is a fully convolutional network referred as HealPixFCN.
+Our principal architecture is a fully convolutional network referred as the FCN variant of HealPixNet.
 Thanks to 6 graph convolution layers (GC sizes: 16, 32, 64, 64, 64, 2) we first build the statistical evidence of each distribution for each pixel of a down-sampled sphere.
@@
 Hence we end up with a convolutional neural network (CNN) that is not invariant to rotation anymore.
-The network is referred as HealPixCNN and can be summarized as
+The network is referred as CNN variant of HealPixNet and can be summarized as
 \begin{equation}

### 2018-08-10 scnn.tex
equivariant to rotation not translation

@@
 % Convolutional Neural Networks (CNNs) are particularly well suited for analysis of cosmological data due to the translation invariance built into their architecture.
-% Indeed, sky maps are translation invariant, which means that translating and rotating maps on the sphere doesn't change their interpretation.
+% Indeed, sky maps are rotation invariant, which means that rotating maps on the sphere doesn't change their interpretation.
 % Only the statistics of the maps is relevant.
@@
 \todo{Add here the paper of Risi?}
-Finally, the use of a graph to model the discretised sphere was considered by~\citet{khasanova2017graphomni} as well, towards the goal of designing network that were invariant to rotations and translation.
+Finally, the use of a graph to model the discretised sphere was considered by~\citet{khasanova2017graphomni} as well, towards the goal of designing network that were invariant to rotations.
 While their architecture accommodates these invariances on the sphere, they did not take advantage of a hierarchical pixelisation.
@@
 Following \citet{khasanova2017tigranet}, we implement an optional statistical layer between the last graph convolutional layer and the first fully connected layer for the neural network.
-This introduces the invariance of the output to isometric transformations, such as rotation and translation of maps on the sphere.
+This introduces the invariance of the output to isometric transformations, such as rotation of maps on the sphere.
 The role of the layer is to compute global and location independent statistics from feature maps.
@@
 Directions that make much sense for images (up, down, left, and right) are arbitrarily defined when setting the origin of the grids on the sphere.
-Any convolution using directions on the sphere is not equivariant to translation and rotation.
+Any convolution using directions on the sphere is not equivariant to rotation.
 
@@
 
-\todo{In HealpixNet we use the idea of a statistical layer, described in \secref{stat_layer}, to provide invariance to isometric transformations such as translation and rotation on the sphere.
+\todo{In HealpixNet we use the idea of a statistical layer, described in \secref{stat_layer}, to provide invariance to isometric transformations such as rotation on the sphere.
 \TK{We would need to describe the idea of the statistical layer for the cosmology audience. They don't have a clue what it is.}\nati{Can't they just wait for \secref{stat_layer}? }
@@
 A contrario, formulations with exploit the tengant space of manifolds define a local coordinate system.
-While this formulation of convolution can learn anisotropic filters, it is not equivariant to translation.
+While this formulation of convolution can learn anisotropic filters, it is not equivariant to rotation.
 \todo{better wording}

### 2018-08-10 scnn.tex
localization and translation

@@
 \newcommand{\bO}{\mathcal{O}}
+\newcommand{\T}{\mathcal{T}}
 \DeclareMathOperator*{\esp}{E}
@@
     \item Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
+	\item Have a "Contributions" paragraph?
+	\item Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices.
     % \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
@@
 Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph.
-It can however be localized on any vertex $v_i$ by the convolution with a Kronecker delta $\b \delta_i \in \R^{N_{pix}}$,\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} that is $h(\L) \b \delta_i$, a column of $h(\L)$.
-This localization of the kernel $h$ can be useful to visualize kernels as explained in~\ref{sec:filter_visualization}.
+It can however be \textit{localized} on any vertex $v_i$ by the convolution with a Kronecker delta\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} $\b \delta_i \in \R^{N_{pix}}$.
+The localization operator $\T_i$ reads $\T_i h = h(\L) \b \delta_i = (h(\L))_i$, the $i$th column of $h(\L)$.
+This localization of the kernel $h$ can be useful to visualize kernels, as explained in~\ref{sec:filter_visualization}.
 If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another.
@@
 However, when considering only parts of the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).
-Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with the localizations of the kernel $h$, i.e. 
+
+Finally, the graph convolution can be interpreted in the vertex domain as a scalar product with localizations $\T_i h$ of the kernel $h$.
+Indeed, the result of the convolution of the signal $\f$ with the kernel $h$ is
 \begin{equation} \label{eqn:graph_convolution_spatial}
-	(h(\L) \f)_i = \langle h(\L) \b \delta_i, \f \rangle.
+	(h(\L) \f)_i = \langle \T_i h(\L), \f \rangle = \langle h(\L) \b \delta_i, \f \rangle.
 \end{equation}
-We would like to emphasis that traditional convolution can be written in the same form as \eqnref{graph_convolution_spatial}.
-Given $f,g$ two 1 dimentional discrete signals, their convolution can be written as
-\begin{equation} \label{eqn:standard_convolution}
-(f \ast g) (n) = \sum_{m=-\infty}^\infty f(m) g(n-m) = \langle T_n g,  f \rangle,
-\end{equation}
-where $T_n g(m)=g(n-m)$ is, up to a flip, a translation operator. As a result, the convolution is simply the scalar product with the translated kernel $g$.
-Additionally to the fact that \eqnref{graph_convolution_spatial} and \eqnref{standard_convolution} are both scalar product, it turns out that the localization operator $h(\L) \b \delta_i$ is some generalization of the translation for graphs.
-Furthermore that in the particular case where the Laplacian matrix $\L$ is circulant, $h(\L) \b \delta_i$ is a translated version of $h(\L) \b \delta_j$ for all $i,j$ and both convolution are equivalent.
-For a detailled explanation of the connection between translation and localization, refer to \citep[Sec 2.2]{perraudin2017stationary}.
-
-In \ref{sec:heat_diffusion}, we present an example application of graph-based convolution to a simple heat-diffusion problem in order to shed some light on what is the convolution on a graph.
+To make the parallel with the classical 1D convolution, let $f, g$ be two 1D discrete signals. Their convolution can be written in the same form as \eqnref{graph_convolution_spatial}:
+\begin{equation*}
+	(f \ast g) (i) = \sum_{j=-\infty}^\infty f(j) g(i-j) = \langle T_i g,  f \rangle,
+\end{equation*}
+where $T_i g(j) = g(i-j)$ is, up to a flip, a translation operator.
+Similarly as \eqnref{graph_convolution_spatial}, the convolution of the signal $f$ by a kernel $g$ is the scalar product of $f$ with translated versions $T_i g$ of the kernel $g$.
+% Signals and kernels are the same thing in classical signal processing precisely because there exists a proper definition of translation.
+Additionally, it turns out that the localization operator $\T_i h$ is a generalization of the translation operator on graphs.
+In the particular case where the Laplacian matrix $\L$ is circulant, $\T_i h$ is a translated version of $\T_j h$ for all $i, j$ and both convolutions are equivalent.
+We refer the reader to \citet[Sec 2.2]{perraudin2017stationary} for a detailed discussion of the connection between translation $T_i$ and localization $\T_i$.
+
+In \ref{sec:heat_diffusion}, we show that the diffusion of heat on a graph can be expressed as the convolution of an initial condition $f$ with a heat kernel $h$.
+It should hopefully shed some light on the meaning of the convolution on a graph.
 

### 2018-08-10 scnn.tex
related work in good shape

@@
 \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-
+	\item (TK) Related work in cosmo.
+The only cosmological applications of spherical CNNs in the related work are about projection on the tangent plane \citep{schmelze2017cosmologicalmodel, fluri2018deep, gupta2018nongaussianinformation}.
+Aren't there applications in cosmology for the other (c.f.
+related work section) approaches?
+Most of them are illustrated in omnidirectional imagery.
 	\item (MD) distinction between CNN and FCN
@@
 This flexibility might be an advantage to mention.
-In particular, compared to~\citet{cohen2018spherical} it allows us to do only do the required computation when only a part of the sphere is considered.}
+In particular, compared to~\citet{cohen2018sphericalcnn} it allows us to do only do the required computation when only a part of the sphere is considered.}
 
@@
 Perhaps the most straightforward approach to the analysis of spherical data is to divide it into small chunks and project those on flat 2D surfaces.
+\todo{Tune according to the story in the related work.}
 While this approach has been demonstrated to work \citep{fluri2018deep,gupta2018nongaussianinformation,schmelze2017cosmologicalmodel,gillet2018deeplearning}, it may be more natural for some applications and accurate to work directly on the sphere.
@@
 
-% cohen2017convolutional (ICML workshop) and cohen2018spherical (ICLR best paper) are redundant
+% cohen2017convolutional (ICML workshop) and cohen2018sphericalcnn (ICLR best paper) are redundant
 A first attempt to generalize CNNs to spherical data was to apply a standard 2D CNN to a grid discretisation of the sphere~\citep{boomsma2017spherical}.
 While this approach uses the well-developed 2D convolution and hierarchical pooling, it is restricted to those specific grid samplings which are highly irregular on the sphere.
-An attempt by~\citet{cohen2018spherical} was to leverage the spherical Fourier transform and to perform the SO(3) convolution in the spectral domain, thanks to the convolution theorem. 
+An attempt by~\citet{cohen2018sphericalcnn} was to leverage the spherical Fourier transform and to perform the SO(3) convolution in the spectral domain, thanks to the convolution theorem.
 The resulting convolution is rotational equivariant, meaning that a rotation of the input implies the same rotation of the output.
 While there exists fast spherical Fourier transforms for some samplings, this approach can still be computationally expensive.
-\todo{Add here the paper of Risi?}
 Finally, the use of a graph to model the discretised sphere was considered by~\citet{khasanova2017graphomni} as well, towards the goal of designing network that were invariant to rotations.
@@
 Moreover, the statistical layer, which introduces the invariance, needs to be hand-crafted to capture statistics of interest.
+\todo{better identify the shortcomings: (i) part of sphere / missing data, (ii) computational efficiency, (iii) equivarience}
 
@@
 The length (or weight) of the shortest path between two pixels is an approximation of the geodesic distance between them on the manifold.
-The use of this approach is enabled by recent developments in graph signal processing, where fundamental tools, such as for example the Fourier transform, were defined \citep{shuman2013emerging} for graphs.
-Our approach uses the graph CNN formulation introduced by \citet{defferrard2016convolutional}, which can be adapted to any sampling of the sphere.
+The use of this approach is enabled by recent developments in graph signal processing, where fundamental tools, such as for example the Fourier transform, were defined for graphs \citep{shuman2013emerging}.
+Our approach uses the graph CNN formulation introduced by \citet{defferrard2016convolutional}, which can accommodate any sampling of the sphere.
 Using a $k$-nearest neighbours graph, the convolution operation costs $\mathcal{O}(N_{pix})$ operations, where $N_{pix}$ is the number of pixels.
-This is the lowest possible complexity for a convolution operation without approximations (e.g. by sketching).
+This is the lowest possible complexity for a convolution operation without approximations (e.g., by sketching).
 The flexibility of modeling the data domain with a graph allows to easily model data that spans only a part of the sphere, or data that is not uniformly sampled.
@@
 $h: \R_+ \rightarrow \R$, a signal $\f \in \R^{N_{pix}}$ on the graph is filtered as
-\begin{equation} \label{eqn:graph_convolution}
+\begin{equation} \label{eqn:graph_convolution_fourier}
 	h(\L) \f = \U h(\bLambda) \U\trans \f,
@@
     Both are executed on a single core.
-    The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3)$ for the spherical harmonics, where $\ell_{max}$ is the largest degree (i.e., the spectrum is truncated at $\ell_{max}$).}
+	The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3) = \bO(N_{pix}^{3/2})$ for the spherical harmonics, where $\ell_{max}$ is the largest angular frequency.}
     \label{fig:filtering_speed}
@@
 
-While \eqnref{graph_convolution} is a theoretically well justified definition of the convolution of a graph signal $\f$ by a kernel $h$, it is computationally cumbersome.
+While \eqnref{graph_convolution_fourier} is a theoretically well justified definition of the convolution of a graph signal $\f$ by a kernel $h$, it is computationally cumbersome.
 As no general Fast Fourier Transform (FFT) exist for graphs, the execution of the Fourier transform by multiplication of the signal $\f$ by the dense matrix $\U$ costs $\bO(N_{pix}^2)$ operations.
@@
 Fortunately, both of these computational issues can be overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parametrised by $K+1$ coefficients $\theta$.
-In that specific case, the filtering operation \eqnref{graph_convolution} becomes
-\begin{equation} \label{eqn:graph_convolution_polynomial}
+In that specific case, the filtering operation \eqnref{graph_convolution_fourier} becomes
+\begin{equation} \label{eqn:graph_convolution_monomial}
 	h_\theta(\L) \f =  \U \left(\sum_{k=0}^K \theta_k \bLambda^k \right) \U\trans \f = \sum_{k=0}^K \theta_k \L^k \f,
@@
 where $\tL = \frac{2}{\lambda_{max}} \L - \b{I} = -\frac{2}{\lambda_{max}} \D^{-1/2} \W \D^{-1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\b \Lambda}$ in $[-1, 1]$ and $T_k(\cdot)$ is the Chebyshev polynomial of degree $k$, defined by the recursive relation $T_k(\tL) = 2\tL T_{k-1}(\tL) - T_{k-2}(\tL)$, $T_1(\tL) = \tL$, $T_0(\tL) = \b{I}$.
-While definitions \eqnref{graph_convolution_polynomial} and \eqnref{graph_convolution_cheby} both allow the representation of the same set of filters, Chebyshev polynomials are preferred as they form an orthogonal basis on the interval $[-1, 1]$.
+While definitions \eqnref{graph_convolution_monomial} and \eqnref{graph_convolution_cheby} both allow the representation of the same set of filters, Chebyshev polynomials are preferred as they form an orthogonal basis on the interval $[-1, 1]$.
 Moreover, they factor out $\tL^{k-2}$ from $T_k(\tL)$, e.g., the 3-neighborhood is not mixed with the 5-neighborhood.
@@
 In practice, we found out in our experiment that Chebyshev polynomials are slightly more stable than the monomials used in~\cite{khasanova2017graphomni}(i.e.
-optimizing directly the $\theta_k$ in \eqnref{graph_convolution_polynomial}).
+optimizing directly the $\theta_k$ in \eqnref{graph_convolution_monomial}).
 We believe that this is due to their orthogonality (as explained above) and uniformity\footnote{The amplitude of Chebyshev polynomials is more or less constant over the domain $[-1, 1]$ independently of the order $k$.
@@
 That is especially true for smooth kernels which require a low polynomial degree $K$.
-\figref{filtering_speed} demonstrates the speed comparison of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
-The performance of our approach is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively.
+\figref{filtering_speed} compares the speed of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
+A naive implementation of our method is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively, than using the spherical harmonic transform implemented by the highly optimized library used by HEALPix, \pkg{libsharp} \citep{reinecke2013libsharp}.
 
@@
 
-\citet{boomsma2017spherical} propose to apply a standard 2D CNN to a grid discretization of the sphere.
-Two pixelisations, illustrated in \figref{sphere_grids}, were used: the equirectangular grid, and the cubed-sphere grid defined by~\citet{ronchi1996cubed}.
-As this formulation uses the standard 2D convolutions, all the optimizations developed for 2D images can be applied, what make it computationally efficient.
-Some losses are due to the handling of boundary conditions, for example by padding a grid with the content of the opposite side (equirectangular) or of the neighboring grids (cubed-sphere, HEALPix).
-%It is, however, restricted to those grid sampling sets.
-As many pixelizations are based on the subdivision of a base polyhedron
-Similarly to the cubed-sphere, HEALPix is made of twelve grids. As those grids are not independent, each grid has to be  to handle , .
+A first approach, explored by \citet{boomsma2017spherical} for molecular modeling and \citet{su2017sphericalconv, coors2018spherenet} for omnidirectional imaging, is to use a 2D CNN on a discretization of the sphere that is a grid, such as the equirectangular projection (\figref{sphere_grids} left), or a set of grids, such as the cubed-sphere defined by~\citet{ronchi1996cubed} (\figref{sphere_grids} middle).
+As this formulation uses the standard 2D convolution, all the optimizations developed for images can be applied, what make it computationally efficient.
+This approach is applicable to the many pixelizations that are based on a regular subdivision of a base polyhedron, such as HEALPix. Each base polyhedron then forms a grid.
+Care has to be taken to handle boundary conditions: for example by padding a grid with the content of the opposite side (equirectangular) or of the neighboring grids (cubed-sphere, HEALPix).
+That incures some computational losses.
+For samplings that are not equal area, such as the equirectangular projection, the convolution operation can be adjusted to take the induced distortion into account \citep{su2017sphericalconv, coors2018spherenet}.
 % Furthermore, the grid requirement makes it impossible for the convolution to capture the spherical properties of the domain, i.e., the cubed-sphere sampling is by definition adapted to a cube and not to a sphere.
 Nope, the graph can adapt to any sampling.
-% Moreover, those samplings are not ideal as their resolution is not constant across the sphere.
-
-% Moreover, the pixel area is not constant across the sphere in those sampling schemes, which may limit their potential applications.
-% Indeed, the singularities, such as the poles for the equirectangular grid, and the corners of the cube for the cubed-sphere, are over-sampled.
-% Equal areas of discrete elements is advantageous for many physical measurements, as white noise at the sampling frequency of the instrument gets integrated exactly into white noise in the pixel space, and sky signals are sampled without regional dependence \citep{gorski2005healpix}.
-% => 2D CNN can be applied on HEALPix as well.
-
-% \nati{Michael: Under some very specific hypothesis, this second approach is a particular case of our method, i.e.
-(i) our method with a stupid sampling, (ii) assumption that graph convolution on a grid == 2d convolution.
-Do you think we should mention that?
-I think we should not.}
-Finally, a 2D CNN learns directional filters, which are well defined with respect of the image coordinates.
-Directions that make much sense for images (up, down, left, and right) are arbitrarily defined when setting the origin of the grids on the sphere.
-Any convolution using directions on the sphere is not equivariant to rotation.
-
-% As presented by~\cite{cohen2018spherical}, the most mathematical approach to extend the convolution on a sphere is to use a spherical Fourier transform.
-The convolution is then simply defined as the product in the spectral domain.
-This approach requires one Fourier and one inverse Fourier transform per convolution which remain, even with accelerated algorithms, expensive.
-
-\citet{cohen2018spherical} uses the continuous spherical convolution.
-The goal of this contribution was to define a rotation-equivariant convolution on the sphere, i.e., a rotation of the input implies the same rotation in the output.
+
+Another approach to leverage 2D CNNs is to project spherical data onto many tangent planes, which are flat 2D surfaces.
+This approach has been extensively used for cosmological maps \citep{fluri2018deep, gupta2018nongaussianinformation, schmelze2017cosmologicalmodel, gillet2018deeplearning} and omnidirectional imaging \citep{xiao2012recognizing, zhang2014panocontext}.
+This idea has been generalized to arbitrary 2D manifolds for shape alignment and retrieval \citep{masci2015gcnn, boscaini2016acnn, monti2017monet}.
+
+The main issue with the above two approaches is that they depend on a (local) coordinate system to define anisotropic filters, i.e., filters which are direction dependent.
+Direction is well defined and matters for some applications, such as the analysis of weather and climate data on the Earth (north, south, east, west), and omnidirectional imaging (up, down).
+Indeed, full rotation invariance has been shown to reduce discriminative power for omnidirectional imaging \citep{coors2018spherenet}.
+Some problems are however intrinsically invariant to rotation, such as the analysis of cosmological maps, or the modeling of atoms and molecules.
+In such cases, directions are arbitrarily defined when setting the origin of the pixelization.
+A rotation equivariant convolution, i.e., a rotation of the input implies the same rotation in the output, thus has to be isotropic.
+
+% Moreover, when different grids require different filters as their orientation is not compatible.
+% => same as for tangent planes
+
+\citet{cohen2018sphericalcnn} and \citet{esteves2017sphericalcnn} addressed the problem of rotation equivariance by defining the convolution on the 3D rotation group SO(3), with applications to atomization energy regression and 3D model classification, alignment and retrieval.
 The resulting convolution is performed by (i) a spherical harmonic transform (SHT), i.e., a projection on the spherical harmonics, (ii) a  multiplication in the spectral domain, and (iii) an inverse SHT.
@@
 A naive implementation of the SHT costs $\bO(N_{pix}^2)$ operations, where $N_{pix}$ is the number of pixels.
+Note the similarity with the naive graph convolution defined in \eqnref{graph_convolution_fourier}.
 Accelerated schemes exist for some sampling sets \citep[see][for examples]{mohlenkamp1999fast, rokhlin2006fast, reinecke2013libsharp}.
@@
 In comparison, filtering with our HealpixNet method scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}).
-% Moreover, \figref{filtering_speed} shows that a naive implementation of our method is more than ten times faster than the SHT implemented by the highly optimized \pkg{libsharp} library used by HEALPix \citep{reinecke2013libsharp}.
-% While a comparison is theoretically possible, the experiments of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and do not provide any code for the HEALPix one.
+\citet{kondor2018clebsch} proposed to use the Clebsh-Gordan transform to perform a non-linear transformation in the spectral domain.
+As such, a SHT only has to be performed once to transform the data in the spectral domain.
+No need to transform back and forth between every layer.
+While a clever trick, it is unclear if it results in any speed gain in practice.
+\todo{computation complexity?
+no speed comparison in paper?}
+\todo{Polynomial formulation enforces locality, which otherwise has to be enforced by smoothness in the spectral domain.}
+\todo{Pooling in the spectral domain? \citet{esteves2017sphericalcnn} do something.}
+% While a comparison is theoretically possible, the experiments of~\cite{cohen2018sphericalcnn} are done using the geodesic grid sampling set and do not provide any code for the HEALPix one.
 Hence, a practical comparison is not possible.
-% \TK{I would leave out here, as this is a "spoiler" of the results section.}
-
-Approaches by \citet{cohen2018spherical,boomsma2017spherical} can not be easily accelerated when the data lies on a part of the sphere only.
-
-\nati{Why is \citet{boomsma2017spherical} here? I think it can be trivally accelerated.}
-That is an important use case in cosmology as measurements are often partial, i.e., full-sky maps are rare.
-One could still fill the unseen part of the sphere with zeros, and avoid to compute empty integrals, on the latitude or longitude.
-It is, however, not straightforward to identify those empty directions, and computations would still be wasted; consider, for example, a ring which mostly contains zeros but a few measurements.
+
+All the above methods can not easily be accelerated when the data lies on a part of the sphere only.
+That is however an important use case in cosmology as measurements are often partial, i.e., full-sky maps are rare.
+One could still fill the unseen part of the sphere with zeros, and avoid to compute empty integrals.
+% on the latitude or longitude for SHTs, on square holes for 2D CNNs
+It is, however, not straightforward to identify empty space, and computations would still be wasted; consider, for example, a ring which mostly contains zeros but a few measurements.
 With graphs however, the computation is done only for the used pixels.
-This, however, results in some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}).
-These can be mitigated by padding with zeros a small area around the measurements.
-
-% In an attempt to get the best of the first two approaches, we follow a third
-% direction. We use a graph to adapt to the particular structure of the sphere.
-% While the convolution remains efficient, it still captures well the spherical
-% structure and is particularly adapted to the HEALPix sampling.
-% \TK{I am not sure what is the point of this paragraph, we described our approach already before}
-
-The use of a graph to model the discretised sphere was also considered by~\citet{khasanova2017graphomni}.
-The authors map omnidirectional images onto a sphere, with the goal of correcting for distortions induced by the lens, which was used for their acquisition.
-Besides a different practical application, for which the method was designed, there are two important differences.
-% First, a different sampling scheme is used: \cite{khasanova2017graphomni} uses a grid.
-First, similarly to~\citet{boomsma2017spherical}, they use an equirectangular grid sampling.
-% \TK{how is it different from us?}
-Second, it uses a graph CNN based on a different parameterisation of the convolution kernel.
-Moreover, they did not take advantage of a hierarchical pixelization of the sphere and resorted to dynamic pooling~\citep{kalchbrenner2014dcnn}.
-Finally, while the rotation invariance is desirable, the statistical layer used
-% --- an operation which computes a set of spatially invariant statistics of the last feature map ---
-% \{TK} this should be explained earlier
-may not capture the information in an optimal way
-\todo{and hinders performance (should be empirically verified)}.
-\TK{This is a strong claim, can we support this?} \nati{It is not that strong as we use "may" right?
-We should probably soften it a bit.
-However the main idea is correct.
-If you compute some statistics on some features, you lose some information and may get worse results.
-Nevertheless, since we are also using a statistical layer, I would juste remove this.}
-Moreover, the chosen statistics have to be hand-crafted to capture statistics of interest.
-% While developing completely invariant transforms is a goal worth investigating, CNNs for image recognition, which are arguably the most researched and developed architectures, are not built to be fully invariant to translation.
-% As with the proposed spherical CNN, the fully connected layers at the end of the network depend on the spatial localization of features.
-% While that may not be ideal, it was shown to work well in practice.
-% \TK{The two sentences above look like a tangent to me.. can we skip it an go to the main point, which is I think the fact that we use the stat layer?}
-
-\todo{In HealpixNet we use the idea of a statistical layer, described in \secref{stat_layer}, to provide invariance to isometric transformations such as rotation on the sphere.
-\TK{We would need to describe the idea of the statistical layer for the cosmology audience. They don't have a clue what it is.}\nati{Can't they just wait for \secref{stat_layer}? }
-The use of the statistical layer is optional.
-In our approach, we are keeping all the statistical moments by retaining a full, learned learned feature histogram, an approach that performed the best in our tests.
-That is similar to the learnable histogram introduced by \citet{wang2016learnhist}, although for a purpose of integrating global context in object detection and segmentation tasks.
-\citet{khasanova2017graphomni} uses the mean and variance of diffused versions of the last feature maps in their statistical layer.}
-\TK{why is this section in TODO?\nati{Probably because, we have not decided if we use the histogram yet. This paragraph needs to be rewritten once we are clear with the code.}}
-
-There exists many formulations of graph neural networks, reviewed by \citet{bronstein2017review} and \citet{hamilton2017review}.
+While it results in some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}), these can be mitigated by padding with zeros a small area around the measurements.
+
+The use of a graph to model the discretised sphere was also considered by \citet{khasanova2017graphomni} for omnidirectional imaging.
+% The authors map omnidirectional images onto a sphere, with the goal of correcting for distortions induced by the lens, which was used for their acquisition.
+% First, similarly to~\citet{boomsma2017spherical}, they use an equirectangular grid sampling.
+This work is the closest to our method, with three differences.
+First, they parametrise their convolution kernel with \eqnref{graph_convolution_monomial} instead of \eqnref{graph_convolution_cheby} (see \secref{efficient_convolution} for a discussion and comparison).
+Second, they did not take advantage of a hierarchical pixelization of the sphere and resorted to dynamic pooling \citep{kalchbrenner2014dcnn}.
+While that operation is useful for sequences of varying length, such as sentences in language models, it is overkill in our context as it is not local and destroys spatial coherence.
+Third, they introduced a statistical layer --- an operation that computes a set of statistics from the last feature maps --- to provide full rotation invariance.
+We propose to use the idea of fully convolutional networks (FCNs) instead (see \secref{selected_architecture}).
+While statistics have to be hand-chosen to capture relevant information for the task, the filters in a FCN are trained end-to-end to capture relevant information.
+
+The connection has been made between graph CNNs and group equivariant CNNs by \citet{kondor2018equivariance}, justifying the use of graphs to gain rotation equivariance on the sphere.
+\todo{More here.}
+
+Many formulations of graph neural networks, reviewed by \citet{bronstein2017review} and \citet{hamilton2017review}, have been proposed.
 For this contribution, we chose the formulation of \citet{defferrard2016convolutional} as its root on strong graph signal processing theory makes the concept of convolutions and filters explicit \citep{shuman2013emerging}.
-Its tie to a graph Fourier transform allows us to compare with the spherical harmonic transform, and study its invariance properties.
-More geometric than permutation invariant aggregation.
-A contrario, formulations with exploit the tengant space of manifolds define a local coordinate system.
-While this formulation of convolution can learn anisotropic filters, it is not equivariant to rotation.
-\todo{better wording}
-\todo{three main interpretations: gsp, Bronstein manifold tangent plane, message passing, permutation invariant aggregation, spatial formulations}
-Bronstein is a spatial formulation where the registration is done by projection on the tangent plane.
-% Not Bronstein's manifold approach as we want a Fourier basis to compare to the spherical harmonics.
-% Be as close as possible to spherical harmonics.
-Related to this, convolutional neural networks have been defined on manifolds and have achieved impressive results on shapes [Bronstein].
-They however too depend on an orientation, which spheres do not possess.
-
-% Anisotropic cannot be invariant
-
-The connection has recently been made between graph CNNs and group equivariant CNNs \cite{kondor2018equivariance}, justifying the use of graphs to gain rotation equivariance on the sphere.
-
-% In this work, we are using the graph CNN formulation introduced in~\cite{defferrard2016convolutional}.
-
-Spatial definitions of graph convolutions, e.g.
-[Niepert] needs to define an orientation in order to match the edges with the filters.
-Most often the orientation is not given by the application, and one has to define it (for example by ordering by degree or any other measure, or by using a graph coloring).
-There is no good default good orientation on general graphs and the choice of an orientation is highly application dependent.
+As the convolution is motivated by a multiplication in the graph Fourier spectrum, it is close in spirit, and empirically, to the formulation based on the spherical harmonics, which is the ideal rotation equivariant formulation.
+% and study its equivariance properties.
+
+% Main interpretations: GSP, Bronstein manifold tangent plane, message passing, permutation invariant aggregation, spatial ordering and matching
+
+Thanks to their versatility, graph neural networks have been used in a variety of tasks, such as identifying diseases from brain connectivity networks \citep{ktena2018metriclearning} or population graphs \citep{parisot2017disease}, designing drugs using molecular graphs \citep{hop2018drugdesign},
+segmenting 3D point clouds \citep{qi2017pointcloudsegmentation}, optimizing shapes to be aerodynamic \citep{baque2018shape}, etc.
+By adding a recurrent neural network on top \citep{seo2016gcrn}, they can for example model time series such as traffic on road networks \citep{li2018traffic}, or recursively complete matrices for recommendation \citep{monti2017recommendation}.
+% scientifically and industrially motivated applications
 
@@
 \subsection{Selected architecture}
+\label{sec:selected_architecture}
+
 The choice of a particular HealPixNet architecture highly depends on the problem at hand.

### 2018-08-10 scnn.tex
clean todo list

@@
 	\item (MD) distinction between CNN and FCN
-    \item (done!) (NP) make figure A.13 remove white space
     \item (first version done!)(NP+MD) paragraph on our chosen architecture in the Experiments sections
     \item (Done) (NP) vertex interpretation
-    \item (MD) Are you happy with the vertex interpretation in section 2.5 Efficient convolutions? Also do you like the end of 2.4?
+    \item (MD) Are you happy with the vertex interpretation in section 2.5 Efficient convolutions?
     \item (NP) Finalise readme on Github code
@@
     \item check if papers which appear as arxiv were not published in a conference or journal
-    \item MD add irregular (random) sampling to comparison with spherical harmonics? Could motivate people to think about different samplings. \nati{I think this is too much for this paper.}
     \item TK check part sphere notebook and whole sphere
@@
     \item (almost done) TK read everything
-    \item (done!) (TK) uniformize text size in figures
     \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
     \item (done!) (TK) re-make figures to make the labels/legend/titles the same font size as the main text
-    \item (done!) TK check the appendix
-    \item (done!) TK optional - example of data (CMB (mask) + mass map + radio intensity)
     \item (done!) (TK) add info on comparison with histograms, so that it's just a demonstration
-    \item (done!) TK read the result section
     \item (done!) (TK) add reference to figure (pooling) to the area of orders
@@
 	\item Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices.
-    % \item (TK took exec decision and moved it :D) Should the heat example go to appendix?
-    % \item (done! first version done) conclusions
-    % \item (done!) Michael section 4.5 (efficient convolutions) and 3.2 (conv on graphs)
-    % \item (done!) (TK NP) if we have time make a new candidate for network plot (optional)
-    % \item (done!) TK read the heat section again
-    % \item (done!) (TK) make a new proposition for a plot Figure 6: Two levels of coarsening and pooling
-    % \item \todo{Notation GC32 - P256 - FC10 to describe an architecture? Maybe more useful in Experiments where we describe the architecture used for each experiment.}
-    % Nati: I did it without this notation. Since we have two architectures, I think it is OK.
+	\item Try to make the paper shorter?
 \end{itemize}

### 2018-08-10 scnn.tex
todo: font
avoid clash of notation: loss function => cost function

@@
 	\item Try to make the paper shorter?
+	\item Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly.
 \end{itemize}
@@
 
-The loss function $\ell(\Y, \bar \Y) = \ell(NN_\theta(\X), \bar \Y)$ measures how good the prediction $\Y$ is for sample $\X$, given the ground truth $\bar \Y$.
-For a classification task, the loss is usually taken to be the cross-entropy
+The cost (or loss) function $C(\Y, \bar \Y) = C(NN_\theta(\X), \bar \Y)$ measures how good the prediction $\Y$ is for sample $\X$, given the ground truth $\bar \Y$.
+For a classification task, the cost is usually taken to be the cross-entropy
 \begin{equation*}
-	\ell(\Y, \bar \Y) = - \sum_{i=1}^{N_{pix}} \sum_{j=1}^{N_{classes}} \bar y_{ij} \log(y_{ij}),
+	C(\Y, \bar \Y) = - \sum_{i=1}^{N_{pix}} \sum_{j=1}^{N_{classes}} \bar y_{ij} \log(y_{ij}),
 \end{equation*}
 where $\bar \Y \in \R^{N_{pix} \times N_{classes}}$ is the ground truth label indicator, i.e., $\bar y_{ij} = 1$ if pixel $i$ of sample $\X$ belongs to class $j$ and is zero otherwise.
-For global prediction, the loss is as if $N_{pix} = 1$.
+For global prediction, the cost is as if $N_{pix} = 1$.
 For a regression task, a common choice is the mean squared error (MSE)
 \begin{equation*}
-	\ell(\Y, \bar \Y) = \frac{\|\Y-\bar{\Y}\|_2^2}{N_{pix} F_{out}} = \frac{1}{N_{pix} F_{out}} \sum_{i=1}^{N_{pix}} \sum_{j=1}^{F_{out}} (y_{ij} - \bar y_{ij})^2,
+	C(\Y, \bar \Y) = \frac{\|\Y-\bar{\Y}\|_2^2}{N_{pix} F_{out}} = \frac{1}{N_{pix} F_{out}} \sum_{i=1}^{N_{pix}} \sum_{j=1}^{F_{out}} (y_{ij} - \bar y_{ij})^2,
 \end{equation*}
@@
 Again, take $N_{pix} = 1$ for global regression.
-We emphasize that the loss and the SM layer is the sole difference between a neural network engineered for classification or regression.
-
-The goal of learning is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = \esp \left[ \ell \left( NN_\theta(\X), \bar \Y \right) \right]$.
+We emphasize that the cost function and the SM layer is the sole difference between a neural network engineered for classification or regression.
+
+The goal of learning is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = \esp \left[ C \left( NN_\theta(\X), \bar \Y \right) \right]$.
 In general, that expectation cannot be computed as the data distribution is unknown.
@@
 \begin{equation*}
-	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell \left(NN_\theta(\X_i), \bar \Y_i \right).
+	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} C \left(NN_\theta(\X_i), \bar \Y_i \right).
 \end{equation*}
@@
 \begin{equation*}
-	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell \left( NN_\theta(\X_i), \bar \Y_i \right)}{\partial \theta} ,
+	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial C \left( NN_\theta(\X_i), \bar \Y_i \right)}{\partial \theta} ,
 \end{equation*}

### 2018-08-10 scnn.tex
related work: relational reasoning

@@
 
-Thanks to their versatility, graph neural networks have been used in a variety of tasks, such as identifying diseases from brain connectivity networks \citep{ktena2018metriclearning} or population graphs \citep{parisot2017disease}, designing drugs using molecular graphs \citep{hop2018drugdesign},
-segmenting 3D point clouds \citep{qi2017pointcloudsegmentation}, optimizing shapes to be aerodynamic \citep{baque2018shape}, etc.
-By adding a recurrent neural network on top \citep{seo2016gcrn}, they can for example model time series such as traffic on road networks \citep{li2018traffic}, or recursively complete matrices for recommendation \citep{monti2017recommendation}.
+Thanks to their versatility, graph neural networks have been used in a variety of tasks, such as identifying diseases from brain connectivity networks \citep{ktena2018metriclearning} or population graphs \citep{parisot2017disease}, designing drugs using molecular graphs \citep{hop2018drugdesign}, segmenting 3D point clouds \citep{qi2017pointcloudsegmentation}, optimizing shapes to be aerodynamic \citep{baque2018shape}, and many more.
+By interwinding graph convolutional layers and recurrent layers \citep{seo2016gcrn}, they can for example model structured time series such as traffic on road networks \citep{li2018traffic}, or recursively complete matrices for recommendation \citep{monti2017recommendation}.
+Another trend, parallel to the modeling of structured data, is the use of graph neural networks for relational reasoning \citep{battaglia2018review}.
 % scientifically and industrially motivated applications

### 2018-08-10 scnn.tex
change during the call

@@
 \usepackage{url}
-\usepackage{hyperref}
-% \usepackage[draft]{hyperref}
+% \usepackage{hyperref}
+\usepackage[draft]{hyperref}
 \usepackage{graphicx,array} \graphicspath{{figures/}}
@@
 \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+    \item (TK) check text figure 1
 	\item (TK) Related work in cosmo.
@@
     \item (first version done!)(NP+MD) paragraph on our chosen architecture in the Experiments sections
-    \item (Done) (NP) vertex interpretation
     \item (MD) Are you happy with the vertex interpretation in section 2.5 Efficient convolutions?
-    \item (NP) Finalise readme on Github code
-    \item branch with notebooks with plots (results) NP
-    \item NP move the repo to HealpixNet
-    \item check if papers which appear as arxiv were not published in a conference or journal
-    \item TK check part sphere notebook and whole sphere
-    \item (done!) (TK) update the README for data zip - file from NP
-    \item (almost done) TK read everything
+    \item (TK) check if papers which appear as arxiv were not published in a conference or journal
+    \item (TK) check part sphere notebook and whole sphere
+    \item (TK) read everything
+    \item (NP) Put Raphael in the dataset author. 
     \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
-    \item (done!) (TK) re-make figures to make the labels/legend/titles the same font size as the main text
-    \item (done!) (TK) add info on comparison with histograms, so that it's just a demonstration
-    \item (done!) (TK) add reference to figure (pooling) to the area of orders
-    \item (done!) (TK) add section in conclusions/ paragraph on possible extensions to the code: dense output, regression, GANs, segmentation
+    \item (TK) color text in 2.8
+    \item (NP) D.18 text size bigger
+    \item (NP) Remove caption B.13
 	\item Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
     \item Check names: HealpixNet, HealpixCNN, HealpixFCN
-    \item Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
-	\item Have a "Contributions" paragraph?
+    \item (NP) Check the wording.
+Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
+    \item Change equation after (2) and check all kroneker
 	\item Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices.
 	\item Try to make the paper shorter?
-	\item Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly.
+	\item (TK) Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly.
+    \item (TK) fix the bibliography
+    \item Check links in footnotes.
 \end{itemize}

### 2018-08-10 scnn.tex
small edit and merge

@@
 	\item Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
-    \item Check names: HealpixNet, HealpixCNN, HealpixFCN
+    \item Check names: we use HealpixNet, HealpixNet variant CNN, HealpixNet variant FCN
     \item (NP) Check the wording.
@@
     \item Check links in footnotes.
+
 \end{itemize}
@@
 This figure shows a network which operates on the whole sphere.
-The process is however the same when working with parts of sphere, except that the graph is only built for the part of interest.}
+The process is, however, the same when working with parts of sphere, except that the graph is only built for the part of interest.}
 	\label{fig:architecture}
@@
 To be able to train the network efficiently, the convolution has to be performed fast.
-Another important feature is for a CNN to be able to work on part-spheres, as for many cosmological observations cover only a part of the sky.
+Another important feature is for a CNN to be able to work on subpart of the sphere, as for many cosmological observations cover only a part of the sky.
 For ground-based observations this can be due to limited visibility of the sky from a particular telescope location, and for space-based instruments due to masking of the galactic plane area.
@@
 \citet{kondor2018clebsch} proposed to use the Clebsh-Gordan transform to perform a non-linear transformation in the spectral domain.
-As such, a SHT only has to be performed once to transform the data in the spectral domain.
-No need to transform back and forth between every layer.
-While a clever trick, it is unclear if it results in any speed gain in practice.
+As such, a SHT only has to be performed once at the input of the network and the back and forth SHT between every layer are no longer required.
+While this clever trick make the convolution complexity $\bO(N_{pix})$, the non-linearity\nati{ scales as the squared of the number of channels and as }.
+As a result, it is yet unclear which speed gain is obtained in practice.
 \todo{computation complexity?
@@
 While testing the FCN and CNN architectures, we made the following empirical observations.
-First, Chebyshev polynomial seems more stable than monomials ($\theta_k$ in \eqnref{graph_convolution_polynomial}), in the sense that the training loss had a more monotone decrease.
+First, Chebyshev polynomial seems more stable than monomials ($\theta_k$ in \eqnref{graph_convolution_monomial}), in the sense that the training loss had a more monotone decrease.
 Nevertheless once the network is trained, we could not observe a significant accuracy difference.

### 2018-08-10 scnn.tex
todo & typo

@@
 Most of them are illustrated in omnidirectional imagery.
+If none, say it and mention some alternatives, e.g., wavelets?
 	\item (MD) distinction between CNN and FCN
-    \item (first version done!)(NP+MD) paragraph on our chosen architecture in the Experiments sections
-    \item (MD) Are you happy with the vertex interpretation in section 2.5 Efficient convolutions?
+	\item (MD) check paragraph on our chosen architecture in the Experiments sections
+    \item (MD) check vertex interpretation in Efficient convolutions. Powers of L are weights of paths.
     \item (TK) check if papers which appear as arxiv were not published in a conference or journal
@@
     \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
-    \item (TK) color text in 2.8
+	\item (TK) Example applications for dense prediction (classification and regression) for cosmology (color text in 2.8)
     \item (NP) D.18 text size bigger
@@
 	\item Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
-    \item Check names: we use HealpixNet, HealpixNet variant CNN, HealpixNet variant FCN
+	\item Check names: we use HealpixNet, HealpixNet (CNN variant), HealpixNet (FCN variant)
     \item (NP) Check the wording.
 Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
-    \item Change equation after (2) and check all kroneker
-	\item Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices.
-	\item Try to make the paper shorter?
+	\item (NP) Change equation after (2) and check all kroneker
+	\item Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
 	\item (TK) Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly.
@@
 an operation requiring $k$ multiplications of the graph Laplacian matrix $\L$.
-In our case, the Laplacian is extremly sparse, with $8-9$ entries per line, making the filtering operation for a fixed $K$ linear in the number of pixel $N_{pix}$.
+In our case, the Laplacian is extremely sparse, with $8-9$ entries per line, making the filtering operation for a fixed $K$ linear in the number of pixel $N_{pix}$.
 % Moreover, here happens the transition from filtering in the spectral domain to filtering in the vertex domain.
@@
 	\caption{Convolution kernel (also called filter) $h$ localized in the center and left corner of a surface.
-A filter is localized on pixel $i$ as $h(\L) \b \delta_i$ (see \secref{graph_convolution} and \eqnref{graph_convolution_spatial}).
+A filter is localized on pixel $i$ as $\T_i h = h(\L) \b \delta_i$ (see \secref{graph_convolution} and \eqnref{graph_convolution_spatial}).
 The graph is built from $1/12^\text{th}$ of the sphere at $N_{side} = 16$.

### 2018-08-12 scnn.tex
address the color points

@@
 Perhaps the most straightforward approach to the analysis of spherical data is to divide it into small chunks and project those on flat 2D surfaces. 
-\todo{Tune according to the story in the related work.}
+% \todo{Tune according to the story in the related work.}
 While this approach has been demonstrated to work \citep{fluri2018deep,gupta2018nongaussianinformation,schmelze2017cosmologicalmodel,gillet2018deeplearning}, it may be more natural for some applications and accurate to work directly on the sphere.
-The main challenge in designing a CNN on the sphere is to define a convolution operation that is suitable for this irregularly sampled domain.
-To be able to train the network efficiently, the convolution has to be performed fast.
+The main challenge in designing a CNN on the sphere is to define a convolution operation that is suitable for this domain, while taking care of the necessary irregular sampling.
+Furthermore, to be able to train the network efficiently, the convolution has to be performed fast.
 Another important feature is for a CNN to be able to work on subpart of the sphere, as for many cosmological observations cover only a part of the sky.
-For ground-based observations this can be due to limited visibility of the sky from a particular telescope location, and for space-based instruments due to masking of the galactic plane area.
+For ground-based observations this can be due to limited visibility of the sky from a particular telescope location, and for space-based instruments due to masking of the galactic plane area (see for example \figref{example_maps}).
 
 % cohen2017convolutional (ICML workshop) and cohen2018sphericalcnn (ICLR best paper) are redundant
-A first attempt to generalize CNNs to spherical data was to apply a standard 2D CNN to a grid discretisation of the sphere~\citep{boomsma2017spherical}.
-While this approach uses the well-developed 2D convolution and hierarchical pooling, it is restricted to those specific grid samplings which are highly irregular on the sphere.
-An attempt by~\citet{cohen2018sphericalcnn} was to leverage the spherical Fourier transform and to perform the SO(3) convolution in the spectral domain, thanks to the convolution theorem.
-The resulting convolution is rotational equivariant, meaning that a rotation of the input implies the same rotation of the output.
-While there exists fast spherical Fourier transforms for some samplings, this approach can still be computationally expensive.
+A first direction to generalize CNNs to spherical data was to apply a standard 2D CNN to a grid discretisation of the sphere~\citep{boomsma2017spherical,su2017sphericalconv,coors2018spherenet}.
+While this approach uses the well-developed 2D convolution and hierarchical pooling, it is restricted to those specific grid samplings which are highly irregular on the sphere and hence inherently deform the domain where the data is supported.
+A second direction attempted by~\citet{cohen2018sphericalcnn} was to leverage the spherical Fourier transform and to perform the SO(3) convolution in the spectral domain, thanks to the convolution theorem.
+Contrarily to the first direction, the resulting convolution is rotational equivariant, meaning that a rotation of the input implies the same rotation of the output.
+This is an important property as translation invariance is probably one of the main reason why classic CNN were successful in the first place.
+Nevertheless, this approach is computationally expensive even if a fast spherical Fourier transforms is used. 
+%(They exist for particular samplings.)
 Finally, the use of a graph to model the discretised sphere was considered by~\citet{khasanova2017graphomni} as well, towards the goal of designing network that were invariant to rotations.
-While their architecture accommodates these invariances on the sphere, they did not take advantage of a hierarchical pixelisation.
+While their architecture accommodates these invariances on the sphere and remains fairly efficient, they did not take advantage of a hierarchical pixelisation and use a grid discretisation of the sphere.
 Moreover, the statistical layer, which introduces the invariance, needs to be hand-crafted to capture statistics of interest.
-\todo{better identify the shortcomings: (i) part of sphere / missing data, (ii) computational efficiency, (iii) equivarience}
-
-To overcome those shortcomings, we introduce an efficient spherical CNN formulation which uses (i) convolutions on graphs and (ii) hierarchical pooling.
+
+%\todo{better identify the shortcomings: (i) part of sphere / missing data, (ii) computational efficiency, (iii) equivarience}
+\nati{The part of the sphere/missing data is not really there, but I still do not know how to include it!}
+
+To overcome those shortcomings, we introduce an efficient spherical CNN formulation which uses (i) convolutions on graphs and (ii) hierarchical pooling, while working with the HEALPix sampling.
 The main idea is to represent the sphere $S^2$, a 2-dimensional manifold embedded in $\mathbb{R}^3$, as a graph of connected pixels.
@@
 
-\citet{cohen2018sphericalcnn} and \citet{esteves2017sphericalcnn} addressed the problem of rotation equivariance by defining the convolution on the 3D rotation group SO(3), with applications to atomization energy regression and 3D model classification, alignment and retrieval.
+\citet{cohen2018sphericalcnn} and \citet{esteves2017sphericalcnn} addressed the problem of rotation equivariance leveraging the convolution associated to the the 3D rotation group SO(3), with applications to atomization energy regression and 3D model classification, alignment and retrieval.
 The resulting convolution is performed by (i) a spherical harmonic transform (SHT), i.e., a projection on the spherical harmonics, (ii) a  multiplication in the spectral domain, and (iii) an inverse SHT.
@@
 As such, a SHT only has to be performed once at the input of the network and the back and forth SHT between every layer are no longer required.
-While this clever trick make the convolution complexity $\bO(N_{pix})$, the non-linearity\nati{ scales as the squared of the number of channels and as }.
-As a result, it is yet unclear which speed gain is obtained in practice.
-\todo{computation complexity?
-no speed comparison in paper?}
-\todo{Polynomial formulation enforces locality, which otherwise has to be enforced by smoothness in the spectral domain.}
-\todo{Pooling in the spectral domain? \citet{esteves2017sphericalcnn} do something.}
+While this clever trick makes the convolution complexity $\bO(N_{pix})$, the non-linearity scales, to the best of our understanding, as  $\bO(N_{pix}^{3/2})$.
+At the time of writing this paper, computation time is unfortunately not reported, hence making unclear which speed gain is obtained in practice.
+While the convolution in the spectral domain avoid all sampling problems, one of its downside might the lack of natural locality, a property that is naturally obtained by the polynomial approach of graph convolution.
+Because the convolution is at the begging of the neural network, we believe that is should focus on local correlations first before exacting more complex structures.
+%\todo{Polynomial formulation enforces locality, which otherwise has to be enforced by smoothness in the spectral domain.}
+%\todo{Pooling in the spectral domain? \citet{esteves2017sphericalcnn} do something.}
 % While a comparison is theoretically possible, the experiments of~\cite{cohen2018sphericalcnn} are done using the geodesic grid sampling set and do not provide any code for the HEALPix one.
@@
 This work is the closest to our method, with three differences.
-First, they parametrise their convolution kernel with \eqnref{graph_convolution_monomial} instead of \eqnref{graph_convolution_cheby} (see \secref{efficient_convolution} for a discussion and comparison).
+First, they parametrize their convolution kernel with \eqnref{graph_convolution_monomial} instead of \eqnref{graph_convolution_cheby} (see \secref{efficient_convolution} for a discussion and comparison).
 Second, they did not take advantage of a hierarchical pixelization of the sphere and resorted to dynamic pooling \citep{kalchbrenner2014dcnn}.

### 2018-08-12 scnn.tex
small changes

@@
 	\item (TK) Example applications for dense prediction (classification and regression) for cosmology (color text in 2.8)
-    \item (NP) D.18 text size bigger
-    \item (NP) Remove caption B.13
-	\item Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
-	\item Check names: we use HealpixNet, HealpixNet (CNN variant), HealpixNet (FCN variant)
-    \item (NP) Check the wording.
+	\item (Probably OK) Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
+	\item (Should be done) Check names: we use HealpixNet, HealpixNet (CNN variant), HealpixNet (FCN variant)
+    \item (I think it is OK) (NP) Check the wording.
 Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
-	\item (NP) Change equation after (2) and check all kroneker
-	\item Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
+	\item (Done) (NP) Change equation after (2) and check all kroneker
+	\item (Everyone should check this) Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
 	\item (TK) Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly.
@@
 While this approach uses the well-developed 2D convolution and hierarchical pooling, it is restricted to those specific grid samplings which are highly irregular on the sphere and hence inherently deform the domain where the data is supported.
-A second direction attempted by~\citet{cohen2018sphericalcnn} was to leverage the spherical Fourier transform and to perform the SO(3) convolution in the spectral domain, thanks to the convolution theorem.
+A second direction attempted by~\citet{cohen2018sphericalcnn} was to leverage the spherical Fourier transform and to perform the convolution associated to the SO(3) rotation group in the spectral domain, thanks to the convolution theorem.
 Contrarily to the first direction, the resulting convolution is rotational equivariant, meaning that a rotation of the input implies the same rotation of the output.
@@
 \end{equation}
-To make the parallel with the classical 1D convolution, let $f, g$ be two 1D discrete signals. Their convolution can be written in the same form as \eqnref{graph_convolution_spatial}:
+To make the parallel with the classical 1D convolution, let $f, g\in \mathbb{Z} \rightarrow \mathbb{R}$ be two 1D discrete signals.
+Their convolution can be written in the same form as \eqnref{graph_convolution_spatial}:
 \begin{equation*}
-	(f \ast g) (i) = \sum_{j=-\infty}^\infty f(j) g(i-j) = \langle T_i g,  f \rangle,
+	(f \ast g) [i] = \sum_{j=-\infty}^\infty f[j] g[i-j] = \langle T_i g,  f \rangle,
 \end{equation*}
-where $T_i g(j) = g(i-j)$ is, up to a flip, a translation operator.
+where $T_i g[j] = g[i-j]$ is, up to a flip, a translation operator. 
+% nati: I think now the indexing is clear and will not confuse with the rest of the paper.
 Similarly as \eqnref{graph_convolution_spatial}, the convolution of the signal $f$ by a kernel $g$ is the scalar product of $f$ with translated versions $T_i g$ of the kernel $g$.
 % Signals and kernels are the same thing in classical signal processing precisely because there exists a proper definition of translation.
+% For Michael: I know what you mean here, but it is slightly more complicated than that. 
 Additionally, it turns out that the localization operator $\T_i h$ is a generalization of the translation operator on graphs.
@@
 
-The choice of a particular HealPixNet architecture highly depends on the problem at hand.
+The choice of a particular HealpixNet architecture highly depends on the problem at hand.
 Convolution layers construct \emph{almost} rotational equivariant features and the statistical layer can turn them into rotational invariant ones.
@@
 Hence, we assume that each pixel carries some information about the distribution.
-Our principal architecture is a fully convolutional network referred as the FCN variant of HealPixNet.
+Our principal architecture is a fully convolutional network referred as the FCN variant of HealpixNet.
 Thanks to 6 graph convolution layers (GC sizes: 16, 32, 64, 64, 64, 2) we first build the statistical evidence of each distribution for each pixel of a down-sampled sphere.
@@
 Hence we end up with a convolutional neural network (CNN) that is not invariant to rotation anymore.
-The network is referred as CNN variant of HealPixNet and can be summarized as
+The network is referred as CNN variant of HealpixNet and can be summarized as
 \begin{equation}
@@
 Classification errors for the 3 different areas of the sphere.
-Green lines show the performance of the two HealPixNet architectures, blue of the PDF+SVM, and red of the histogram+SVM.
+Green lines show the performance of the two HealpixNet architectures, blue of the PDF+SVM, and red of the histogram+SVM.
 % Green dashed line corresponds to the performance of CNN without the statistical layer.

### 2018-08-12 scnn.tex
nati pass 1st part

@@
 Contrarily to the first direction, the resulting convolution is rotational equivariant, meaning that a rotation of the input implies the same rotation of the output.
-This is an important property as translation invariance is probably one of the main reason why classic CNN were successful in the first place.
+This is an important property as translation invariance is probably one of the main reasons why classic CNNs are successful in the first place.
 Nevertheless, this approach is computationally expensive even if a fast spherical Fourier transforms is used. 
 %(They exist for particular samplings.)
-Finally, the use of a graph to model the discretised sphere was considered by~\citet{khasanova2017graphomni} as well, towards the goal of designing network that were invariant to rotations.
-While their architecture accommodates these invariances on the sphere and remains fairly efficient, they did not take advantage of a hierarchical pixelisation and use a grid discretisation of the sphere.
+Finally, the use of a graph to model the discretised sphere was considered by~\citet{khasanova2017graphomni} as well, towards the goal of designing a  network that is invariant to rotations.
+While their architecture accommodates these invariances on the sphere and remains fairly efficient, they did not take advantage of a hierarchical pixelisation and use as pixelisation a grid discretisation of the sphere.
 Moreover, the statistical layer, which introduces the invariance, needs to be hand-crafted to capture statistics of interest.
@@
 The pooling operation is simply a permutation invariant aggregation function which does not need to be adapted either.
-The convolution and down-sampling operations however need to be generalized from Euclidean domains to the sphere.
+The convolution and down-sampling operations, however, need to be generalized from Euclidean domains to the sphere.
 
@@
 This pixelisation produces a hierarchical subdivision of a spherical surface where each pixel covers the same surface area as every other pixel.
-A hierarchy is desired for data locality in computer memory.
+A hierarchy is desired for the data locality in the computer memory.
 Equal area is advantageous because white noise generated by the signal receiver gets integrated exactly into white noise in the pixel space.
@@
 
-The lowest possible resolution is given by the base partitioning of the surface into $N_{pix} = 12$ equal sized pixels (right-most sphere in \figref{pooling}).
+The lowest possible resolution is given by the base partitioning of the surface into $N_{pix} = 12$ equal-sized pixels (right-most sphere in \figref{pooling}).
 As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2 \cdot 12 = 2^2 \cdot 12 = 48$ pixels (middle sphere in \figref{pooling}), the third is $N_{pix} = N_{side}^2 \cdot 12 = 4^2 \cdot 12 = 192$ pixels, etc., where $N_{side} = 1, 2, 4, 8, \ldots$ is the grid resolution parameter.
@@
 Indeed, \citet{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity.
-That construction can accommodate any sampling, regular or not.
+While our construction will not exactly respect the setting defined by \citet{belkin2007convergence}, we observe empirically strong evidence of convergence.
 

### 2018-08-12 scnn.tex
small updates

@@
 Contrary to classical signal processing on Euclidean domains, the kernel $h$ has no single representation in the vertex domain and cannot be translated on the graph.
-It can however be \textit{localized} on any vertex $v_i$ by the convolution with a Kronecker delta\footnote{A Kronecker delta is the signal $\b \delta_i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} $\b \delta_i \in \R^{N_{pix}}$.
-The localization operator $\T_i$ reads $\T_i h = h(\L) \b \delta_i = (h(\L))_i$, the $i$th column of $h(\L)$.
+It can however be \textit{localized} on any vertex $v_i$ by the convolution with a Kronecker delta\footnote{A Kronecker delta is the signal $\b \delta^i \in \R^{N_{pix}}$ that is zero everywhere except on vertex $v_i$ where it takes the value one.} $\b \delta^i \in \R^{N_{pix}}$.
+The localization operator $\T_i$ reads $\T_i h = h(\L) \b \delta^i = (h(\L))_i$, the $i$th column of $h(\L)$.
 This localization of the kernel $h$ can be useful to visualize kernels, as explained in~\ref{sec:filter_visualization}.
@@
 \begin{equation} \label{eqn:graph_convolution_spatial}
-	(h(\L) \f)_i = \langle \T_i h(\L), \f \rangle = \langle h(\L) \b \delta_i, \f \rangle.
+	(h(\L) \f)_i = \langle \T_i h(\L), \f \rangle = \langle h(\L) \b \delta^i, \f \rangle.
 \end{equation}

### 2018-08-13 scnn.tex
small edits

@@
 The cost of one such multiplication is $\bO(|\E|)$. By construction of our graph, $|\E| < 8 N_{pix}$ and the overall computational cost of the convolution is thus reduced to $\bO(N_{pix})$ operations.
-That is much more efficient than filtering with spherical harmonics, even tho the HEALPix was designed as an iso-latitude sampling to leverage a fast spherical transform.
+That is much more efficient than filtering with spherical harmonics, even though the HEALPix was designed as an iso-latitude sampling to leverage a fast spherical transform.
 That is especially true for smooth kernels which require a low polynomial degree $K$.
@@
 That compression results in much smaller fully connected layers, which usually contain a significant fraction of trainable parameters of a neural network.
-The invariance and reduced representation should help the network to learn from less samples and to generalize better to unseen data.
+The invariance and reduced representation should help the network to learn from fewer samples and to generalize better to unseen data.
 Yet another advantage is that a network built with such a statistical layer is agnostic to the size of the input data, i.e., it can classify maps which do not have the same number of pixels.
@@
 A first approach, explored by \citet{boomsma2017spherical} for molecular modeling and \citet{su2017sphericalconv, coors2018spherenet} for omnidirectional imaging, is to use a 2D CNN on a discretization of the sphere that is a grid, such as the equirectangular projection (\figref{sphere_grids} left), or a set of grids, such as the cubed-sphere defined by~\citet{ronchi1996cubed} (\figref{sphere_grids} middle).
-As this formulation uses the standard 2D convolution, all the optimizations developed for images can be applied, what make it computationally efficient.
+As this formulation uses the standard 2D convolution, all the optimizations developed for images can be applied, what makes it computationally efficient.
 This approach is applicable to the many pixelizations that are based on a regular subdivision of a base polyhedron, such as HEALPix. Each base polyhedron then forms a grid.
 Care has to be taken to handle boundary conditions: for example by padding a grid with the content of the opposite side (equirectangular) or of the neighboring grids (cubed-sphere, HEALPix).
-That incures some computational losses.
+That incurs some computational losses.
 For samplings that are not equal area, such as the equirectangular projection, the convolution operation can be adjusted to take the induced distortion into account \citep{su2017sphericalconv, coors2018spherenet}.
@@
 Indeed, full rotation invariance has been shown to reduce discriminative power for omnidirectional imaging \citep{coors2018spherenet}.
-Some problems are however intrinsically invariant to rotation, such as the analysis of cosmological maps, or the modeling of atoms and molecules.
+Some problems are, however, intrinsically invariant to rotation, such as the analysis of cosmological maps, or the modeling of atoms and molecules.
 In such cases, directions are arbitrarily defined when setting the origin of the pixelization.
@@
 
-\citet{cohen2018sphericalcnn} and \citet{esteves2017sphericalcnn} addressed the problem of rotation equivariance leveraging the convolution associated to the the 3D rotation group SO(3), with applications to atomization energy regression and 3D model classification, alignment and retrieval.
+\citet{cohen2018sphericalcnn} and \citet{esteves2017sphericalcnn} addressed the problem of rotation equivariance leveraging the convolution associated to the 3D rotation group SO(3), with applications to atomization energy regression and 3D model classification, alignment and retrieval.
 The resulting convolution is performed by (i) a spherical harmonic transform (SHT), i.e., a projection on the spherical harmonics, (ii) a  multiplication in the spectral domain, and (iii) an inverse SHT.
@@
 Accelerated schemes exist for some sampling sets \citep[see][for examples]{mohlenkamp1999fast, rokhlin2006fast, reinecke2013libsharp}.
-The main advantage of this approach is that it provides a mathematically well defined rotation-equivariant network.
+The main advantage of this approach is that it provides a mathematically well-defined rotation-equivariant network.
 Nevertheless, even with accelerated SHTs, the convolutions remain expensive, limiting the practical use of this approach.
-For example with the HEALPix sampling, which was designed to have a fast SHT by being iso-latitude, the computational cost of the SHT is $\bO(N_{pix}^{3/2}) = \bO(N_{side}^3) = \bO(\ell_{max}^3)$, where $\ell_{max}$ is the largest angular frequency\footnote{All pixels are placed on $N_{ring} = 4N_{side}-1 = \bO\left(\sqrt{N_{pix}}\right)$ rings of constant latitude.
+For example, with the HEALPix sampling, which was designed to have a fast SHT by being iso-latitude, the computational cost of the SHT is $\bO(N_{pix}^{3/2}) = \bO(N_{side}^3) = \bO(\ell_{max}^3)$, where $\ell_{max}$ is the largest angular frequency\footnote{All pixels are placed on $N_{ring} = 4N_{side}-1 = \bO\left(\sqrt{N_{pix}}\right)$ rings of constant latitude.
 Each ring has $\bO\left(\sqrt{N_{pix}}\right)$ pixels.
@@
 \citet{kondor2018clebsch} proposed to use the Clebsh-Gordan transform to perform a non-linear transformation in the spectral domain.
-As such, a SHT only has to be performed once at the input of the network and the back and forth SHT between every layer are no longer required.
+As such, a SHT only has to be performed once at the input of the network and the back and forth SHT between every layer is no longer required.
 While this clever trick makes the convolution complexity $\bO(N_{pix})$, the non-linearity scales, to the best of our understanding, as  $\bO(N_{pix}^{3/2})$.
 At the time of writing this paper, computation time is unfortunately not reported, hence making unclear which speed gain is obtained in practice.
-While the convolution in the spectral domain avoid all sampling problems, one of its downside might the lack of natural locality, a property that is naturally obtained by the polynomial approach of graph convolution.
+While the convolution in the spectral domain avoid all sampling problems, one of its downsides might the lack of natural locality, a property that is naturally obtained by the polynomial approach of graph convolution.
 Because the convolution is at the begging of the neural network, we believe that is should focus on local correlations first before exacting more complex structures.
@@
 
-All the above methods can not easily be accelerated when the data lies on a part of the sphere only.
-That is however an important use case in cosmology as measurements are often partial, i.e., full-sky maps are rare.
-One could still fill the unseen part of the sphere with zeros, and avoid to compute empty integrals.
+All the above methods cannot easily be accelerated when the data lies on a part of the sphere only.
+That is, however, an important use case in cosmology as measurements are often partial, i.e., full-sky maps are rare.
+One could still fill the unseen part of the sphere with zeros, and avoid computing empty integrals.
 % on the latitude or longitude for SHTs, on square holes for 2D CNNs
 It is, however, not straightforward to identify empty space, and computations would still be wasted; consider, for example, a ring which mostly contains zeros but a few measurements.
-With graphs however, the computation is done only for the used pixels.
+With graphs, however, the computation is done only for the used pixels.
 While it results in some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}), these can be mitigated by padding with zeros a small area around the measurements.
@@
 The experiment presented here is similar the one by \citet{schmelze2017cosmologicalmodel}.
-The two set of maps were created using the standard cosmological model with two sets of cosmological parameters.
+The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters.
 The classification methods were trained to assign a predicted label using the HEALPix maps.
@@
 	\caption{Convolution kernel (also called filter) $h$ localized in the center and left corner of a surface.
-A filter is localized on pixel $i$ as $\T_i h = h(\L) \b \delta_i$ (see \secref{graph_convolution} and \eqnref{graph_convolution_spatial}).
+A filter is localized on a pixel $i$ as $\T_i h = h(\L) \b \delta_i$ (see \secref{graph_convolution} and \eqnref{graph_convolution_spatial}).
 The graph is built from $1/12^\text{th}$ of the sphere at $N_{side} = 16$.

### 2018-08-14 scnn.tex
affiliations

@@
 
-\author{Nathanaël Perraudin, Michaël Defferrard and Tomasz Kacprzak}
-
-\address{}
+\author[SDSC]{Nathanaël Perraudin}
+\author[EPFL]{Michaël Defferrard}
+\author[ETHZ]{Tomasz Kacprzak}
+
+\address[SDSC]{Swiss Data Science Center (SDSC), Zurich, Switzerland}
+\address[EPFL]{Institute of Electrical Engineering, EPFL, Lausanne, Switzerland}
+\address[ETHZ]{Institute for Particle Physics and Astrophysics, ETHZ, Zurich, Switzerland}
 

### 2018-08-15 scnn.tex
\cdot => \times

@@
 The lowest possible resolution is given by the base partitioning of the surface into $N_{pix} = 12$ equal-sized pixels (right-most sphere in \figref{pooling}).
-As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2 \cdot 12 = 2^2 \cdot 12 = 48$ pixels (middle sphere in \figref{pooling}), the third is $N_{pix} = N_{side}^2 \cdot 12 = 4^2 \cdot 12 = 192$ pixels, etc., where $N_{side} = 1, 2, 4, 8, \ldots$ is the grid resolution parameter.
+As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2 \times 12 = 2^2 \times 12 = 48$ pixels (middle sphere in \figref{pooling}), the third is $N_{pix} = N_{side}^2 \times 12 = 4^2 \times 12 = 192$ pixels, etc., where $N_{side} = 1, 2, 4, 8, \ldots$ is the grid resolution parameter.
 High-resolutions HEALPix maps easily reach millions of pixels.
@@
 In our graph, each pixel $i$ is represented by a node (also called vertex) $v_i \in \V$.
-Each node $v_i$ is then connected to the $8$ (or $7$)\footnote{\label{neighbors}The $12 \cdot 4 = 48$ pixels at the corner of each rhombus of the base dodecahedron only have 7 neighboring pixels.
+Each node $v_i$ is then connected to the $8$ (or $7$)\footnote{\label{neighbors}The $12 \times 4 = 48$ pixels at the corner of each rhombus of the base dodecahedron only have 7 neighboring pixels.
 See Figures~\ref{fig:healpix_graph_4} and~\ref{fig:pooling}.} nodes $v_j$ which represent the neighboring pixels $j$ of pixel $i$, forming edges $(v_i, v_j) \in \E$.
@@
 \end{equation*}
-As such, a GC layer is composed of $F_{in} \cdot F_{out}$ filters, each parameterized by $K$ numbers (see \secref{efficient_convolution}). A bias term $\b b \in \R^{F_{out}}$ is jointly optimized.
+As such, a GC layer is composed of $F_{in} \times F_{out}$ filters, each parameterized by $K$ numbers (see \secref{efficient_convolution}). A bias term $\b b \in \R^{F_{out}}$ is jointly optimized.
 % only if batch normalization is not used
@@
 where $\W \in \R^{F_{out} \times F_{in}}$ and $\b b \in \R^{F_{out}}$ are the parameters to be learned.
-Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last GC (or the output $\Y \in \R^{N_{stat} \times F_{out}}$ of the ST), is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first FC, where $F_{in} = N_{pix} \cdot F_{out}$ (or $N_{stat} \cdot F_{out}$).
+Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last GC (or the output $\Y \in \R^{N_{stat} \times F_{out}}$ of the ST), is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first FC, where $F_{in} = N_{pix} \times F_{out}$ (or $N_{stat} \times F_{out}$).
 

### 2018-08-15 scnn.tex
first pass over the experiments section

@@
 
-% Structure of the section
-% 1) Present the goal
-% 2) Explain briefly the dataset
-% 3) Present the setting
-% 4) Describe the result
-In this section we demonstrate the performance of the spherical neural network on a discrimination problem: the classification of convergence maps into two cosmological model classes.
-These maps are similar to those created with gravitational lensing technique \citep{chang2017curvedsky}.
-The experiment presented here is similar the one by \citet{schmelze2017cosmologicalmodel}.
+The performance of HealpixNet is demonstrated on a discrimination problem: the classification of convergence maps into two cosmological model classes.
+The experiment presented here is similar to the one by \citet{schmelze2017cosmologicalmodel}.
+These maps are similar to those created with gravitational lensing techniques \citep{chang2017curvedsky}.
 The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters.
-The classification methods were trained to assign a predicted label using the HEALPix maps.
-Both our Python implementation\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are available online.
-
-We use the classification scenario in this work.
-Extensions to other tasks, such as regression or segmentation, is also possible; we do not, however, demonstrate it here.
-The regression task will most likely be the most practical cosmological applications, as described in \citep{gupta2018nongaussianinformation,fluri2018deep}.
+The classification methods were trained to predict a label from an HEALPix map.
+Both our Python implementation\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are openly available online.
+Furthermore, Jupyter notebooks demoing the method and problem can be run from your browser without installing anything, thank to Binder.
+
+While we only demonstrate a classification task here, other tasks, such as regression or segmentation, are also possible (c.f. \secref{architecture}).
+The regression task will most likely be the most practical cosmological application, as described in \citet{gupta2018nongaussianinformation} and \citet{fluri2018deep}.
 Implementation of full cosmological inference requires, however, many more simulations, building the likelihood function, and several other auxiliary tasks.
@@
 	\caption{Power spectrum densities of the noiseless maps.
-The maps have been smoothed with a Gaussian kernel of radius $3$ arcmins to remove high frequencies.
-The cosmological models could otherwise have been distinguished by the power spectra alone.}
+		To prevent the cosmological models to be distinguished by their power spectra alone, the maps have been smoothed with a Gaussian kernel of radius $3$ arcmins to remove high frequencies ($\ell>1000$).}
 	\label{fig:psd_sigma3}
@@
 	% \includegraphics[width=0.75\linewidth]{smooth_map_class_1}
-% trim=left botm right top
-\includegraphics[trim=1cm 0cm 0cm 0cm, width=0.49\linewidth]{figures/figure_kappa_diff_model1.pdf}
-% \hfill
+	% trim=left bottom right top
+	\includegraphics[trim=1cm 0cm 0cm 0cm, width=0.49\linewidth]{figure_kappa_diff_model1.pdf}
+	\hfill
 	% \includegraphics[width=0.75\linewidth]{smooth_map_class_2}
-\includegraphics[trim=0cm 0cm 1cm 0cm, width=0.49\linewidth]{figures/figure_kappa_diff_model2.pdf}
+	\includegraphics[trim=0cm 0cm 1cm 0cm, width=0.49\linewidth]{figure_kappa_diff_model2.pdf}
 	\caption{Example maps from two classes to be discriminated. Left: model 1 with $\Omega_m=0.31$ and $\sigma_8=0.82$. Right: model 2 with $\Omega_m=0.26$ and $\sigma_8=0.91$.
-The initial conditions for both simulations were the same, so differences only arise due to different cosmological parameters. \nati{Tomek: Is this correct?}}
+	The initial conditions for both simulations are the same, so differences only arise due to different cosmological parameters.}
 	\label{fig:map_sample}
@@
 The 3D structures are projected using a geometric kernel, value of which depends on the radial distance.
-In gravitational lensing, this kernel is dependent on the radial distances between the observer, the mass plane and the plane of source galaxies \citep[see][for review of gravitational lensing]{bartelman2010gravitationallensing}.
-The redshifts of the sources was set to $z=1$.
-
-We make full sky N-body simulations for two parameter sets for $\Lambda\rm{CDM} $ cosmological model: model 1 ($\Omega_m=0.31, \sigma_8=0.82$) and model 2 ($\Omega_m=0.26, \sigma_8=0.91$), where $\Omega_m$ is the matter density in the universe and $\sigma_8$ is the normalisation of the matter power spectrum.
-Other parameter parameters were set to: Hubble constant $H_0=70 km/s/Mpc$, spectral index $n_s=0.96$, and Baryon density today $\Omega_b=0.05$.
+In gravitational lensing, this kernel is dependent on the radial distances between the observer, the mass plane, and the plane of source galaxies \citep[see][for a review of gravitational lensing]{bartelman2010gravitationallensing}.
+
+We make full sky N-body simulations for two parameter sets of the $\Lambda\rm{CDM}$ cosmological model: model 1 ($\Omega_m=0.31, \sigma_8=0.82$) and model 2 ($\Omega_m=0.26, \sigma_8=0.91$), where $\Omega_m$ is the matter density in the universe and $\sigma_8$ is the normalisation of the matter power spectrum.
+Other parameters are set to: Hubble constant $H_0=70 km/s/Mpc$, spectral index $n_s=0.96$, and Baryon density today $\Omega_b=0.05$.
 The parameters $\Omega_m$ and $\sigma_8$ were chosen to have the same spherical harmonic power spectrum for $\ell<1000$.
 That means that it is very difficult to distinguish between these cosmological models using these maps if this range of scales is used.
-We found that for $\ell>1000$ the differences in power spectrum is $~5\%$.
+We found that the differences in power spectrum is $~5\%$ for $\ell>1000$.
 To remove this information, we additionally smooth the spherical maps with a Gaussian kernel of radius $3$ arcmin.
-The resulting Power Spectrum Density (PSD), computed using the \texttt{anafast} function in the HEALPix package, are displayed in \figref{psd_sigma3}.
-In the pre-processing step, we also remove the mean of each map and down-sample them to a resolution of of $N_{side}=1024$.
-
-The simulations are created using the fast lightcone method described in~\citep{sgier2018fastgeneration}.
-However, we use only a single simulation box, as opposed to two used in that work, as we use source galaxies at lower redshift of $z=1$, instead of $z=1.5$.
+The resulting Power Spectrum Density (PSD), computed using the \texttt{anafast} function of the HEALPix package, are displayed in \figref{psd_sigma3}.
+We also subtract the mean of each map and down-sample them to a resolution of $N_{side}=1024$.
+
+The simulations are created using the fast lightcone method described in \citet{sgier2018fastgeneration}.
+We however use a single simulation box, as opposed to two used in that work, as we use source galaxies at a lower redshift of $z=1$, instead of $z=1.5$.
 As a simulator we use \pkg{L-PICOLA} \citep{howlett2015lpicola}, a fast and approximate code for N-body simulations.
-For each class, we generate $30$ simulations, with both classes having the same initial parameters.
-
-Out of the $60$ simulations, $20$ are kept as the test set.
-\figref{map_sample} shows the full sky simulations and a zoom region for model 1 (top) and model 2 (bottom).
-Initial conditions for these simulations were the same, so the differences in structures can only be attributed to different cosmological parameters used to evolve the particle distribution.
+For each class, we generate $30$ simulations.
+Out of the $60$ simulations, $20$ are kept as the test set, and $20\%$ of the remaining training data is used as a validation set (to monitor the training process and select the hyper-parameters).
+\figref{map_sample} shows the full sky simulations and a zoom region for both models.
+Initial conditions for these simulations are the same, so the differences in structures can only be attributed to different cosmological parameters used to evolve the particle distribution.
 
 \subsection{Problem formulation}
-While the number of maps might sound small for deep learning, the information contained in the maps is very recurrent, allowing us to use parts of the map as samples for our simulation.
-Using the properties of the HEALPix sampling, we can split each maps into $12*o^2$ ($o=1,2,4,\dots$) samples that span a smaller part of the sphere.
+
+\todo{thanks to stationarity, quantity of information is constant. Motivation: partial sky maps. Larger surfaces improve confidence in the prediction, the average trick.}
+All pixels are as informative as any other.
+Stationarity of N-body simulations.
+
+While the number of maps might sound small for deep learning, the information contained in the maps is very redundant, allowing us to use parts of the map as samples for our simulation.
+Using the properties of the HEALPix sampling, we can split each map into $12 \times o^2$ ($o=1,2,4,\dots$) samples that span a smaller part of the sphere.
 % As shown in \figref{part_sphere}, we used $o=1,2,4$ as the resulting samples are large enough to suffer from the effects of the spherical geometry.
@@
 % \end{figure}
-For all the experiments, we work with centered Gaussian noise.
-While the noise model of real mass maps often has a slightly different distribution, Gaussian should be a sufficient model to demonstrate the performance of our method.
-The noise added to our maps had levels spanning the range between 0 and 2  $\times$ the standard deviation of the mass maps.
+
+To make the discrimination harder and the problem more realistic, centered Gaussian noise is added to the simulated maps.
+The standard deviation of the noise varies from $0\times$ (i.e., no noise) to $2\times$ the standard deviation of the noiseless maps.
+While the noise model of real maps often has a slightly different distribution, Gaussian noise should be a sufficient model to demonstrate the performance of our method.
+To avoid over-fitting, random noise is generated during training, so that no two samples are exactly the same (i.e., two samples might be from the same simulation, but the added noise will be different).
+That is a data augmentation scheme, as it creates more training examples than we have simulations.
+% Nati: Not done anymore
+% To improve the stability of the spherical CNN, we slowly increase the amount of noise added to the training data over the iterations.
 
@@
 
-% Nati: Not done anymore
-% To improve the stability of the spherical CNN, we slowly increase the amount of noise added to the training data over the iterations.
-Furthermore in order to avoid over-fitting, the noise is randomly produced during the training process.
-The $20\%$ of the training set that we call \emph{validation set} was left out of the training process and simply used to assess the global performance of the network.
-
-We compare the performance of the spherical CNN against two simple benchmark algorithms.
-The two baselines are based on building features with
-(a) the Power Spectral Densities (PSD) and
-(b) the histogram of pixels in the maps~\cite{patton2017cosmologicalconstraints}.
-After a normalization, those features are then classified using a Support Vector Machine (SVM) with a linear kernel.
-Other kernels did not provide better results, while having significantly worse scaling properties.
-All classifiers are trained with noisy samples.
-For fairness, we augmented the dataset of the baseline algorithm in a similar way as for the network; we created samples by adding new random realizations of the noise.
-We stop adding new samples in the classifier once the validation error converges.
+HealpixNet is compared against two simple yet powerful benchmarks.
+The two baselines are based on features that are (i) the power spectral densities (PSD), and (ii) the histogram of pixels in the maps \citep{patton2017cosmologicalconstraints}.
+After normalization, those features are used by a linear support vector machine (SVM) trained for classification.
+A linear kernel is used as other kernels did not provide better results, while having significantly worse scaling properties.
+For fairness, the training set was augmented in a similar way as for HealpixNet: we created samples by adding new random realizations of the noise.
+We stopped adding new samples to the training data once the validation error converged.
 This process is detailed in \ref{sec:dataset_augmentation}.
-We tune the SVM regularization parameter by cross-validating with the validation set.
-
-\subsection{Selected architecture}
+As for HealpixNet, the SVM regularization hyper-parameter was tuned based on the performance over the validation set.
+
+\subsection{Selected architecture and hyper-parameters}
+%\subsection{Selected network architecture}
 \label{sec:selected_architecture}
@@
 We use batch normalization (BN), pooling (P) and relu non-linearity $\sigma$ for each convolutional layer.
-The order of the convolution kernel was set to $K=5$.
+The degree of the Chebyshev polynomials was set to $K=5$.
 The network can be summarized as
-\begin{equation}
-FCN = SM \circ ST_{\text{mean}} \circ L_6 \circ L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1
-\end{equation}
+\begin{equation*}
+	FCN = SM \circ ST_{\text{mean}} \circ L_6 \circ L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1,
+\end{equation*}
 \begin{center}
 where \hspace{0.5cm} \begin{tabular}{lll}
-   $L_1$ &  $=$ &$ P  \circ \sigma \circ BN  \circ GC_{16}$ \\
-   $L_2$ &  $=$ &$ P  \circ \sigma \circ BN  \circ GC_{32}$ \\
-   $L_3,L_4,L_5$ & $=$ &$ P \circ  \sigma \circ BN  \circ GC_{64}$ \\
-   $L_6$ &  $=$& $ \sigma \circ BN  \circ GC_{2}$ \\
+   $L_1$ &  $=$ &$ P \circ \sigma \circ BN \circ GC_{16}$, \\
+   $L_2$ &  $=$ &$ P \circ \sigma \circ BN \circ GC_{32}$, \\
+   $L_3,L_4,L_5$ & $=$ &$ P \circ \sigma \circ BN \circ GC_{64}$, \\
+   $L_6$ &  $=$& $ \sigma \circ BN \circ GC_{2}$. \\
 \end{tabular}
@@
 \end{equation}
-We use the ADAM optimizer, \cite{kingma2014adam}, with $\beta_1=0.9$, $\beta_2=0.999$ and an initial learning rate of $2e-4$ that is exponentially decreased by $0.999$ at each step.
-All models were trained $80$ epochs with a batch size of $16\times o^2$. With this choice, all models receive an identical amount of data within a batch and were trained with $1920$ gradient steps.
-Training took less than $5$ hours for each model using a single NVIDIA Tesla K20.
+
+We use the Adam optimizer \citep{kingma2014adam} with $\beta_1=0.9$, $\beta_2=0.999$, and an initial learning rate of $2 \times 10^{-4}$ that is exponentially decreased by a multiplication with $0.999$ at each step.
+All models were trained for $80$ epochs, which corresponds to $1920$ steps.
+The batch size is set to $16 \times  o^2$ to keep the amount of supervision used to estimate the gradient identical, irrespective of the chosen order $o$ (the learning rate would otherwise need to be adapted).
+By this choice, HealpixNet is trained with the same amount of information, i.e., the number of pixels, across all variants of the problem.
+Training took approximately $1.5$ hour using a single Nvidia GeForce GTX 1080 Ti ($5$ hours with a Tesla K20).
 % The CPU is probably slow which explain the 5 hours.
-I believe we could be much faster than that by computer less summaries and improving the data.
-But, Michael, is OKAY to have to margin of improvement :-)
+I believe we could be much faster than that by computing less summaries and improving the data.
+But, Michael, it's OKAY to have a margin of improvement.
+:-)
 
@@
 	\caption{
-Classification errors for the 3 different areas of the sphere.
-Green lines show the performance of the two HealpixNet architectures, blue of the PDF+SVM, and red of the histogram+SVM.
-% Green dashed line corresponds to the performance of CNN without the statistical layer.
-The noise level was increased from zero to $2\times$ the standard deviation of the mass map.
+		Classification errors that compare the performance of the fully convolutional (FCN) and the standard convolutional (CNN) variants of the HealpixNet architecture, the support vector machine (SVM) with the power spectral densities (PSDs) as features, and the SVM with histogram as features.
+		The difficulty of the task depends on the level of noise and the size of a sample (that is, the number of pixels that constitute the sample to classify).
+Order 1 corresponds to samples which area is $\frac{1}{12}=8.1\%$ of the sphere, order 2 to $\frac{1}{12 \times 2^2} = 2.1\%$, and order 4 to $\frac{1}{12 \times 4^2} = 0.5\%$.
+The standard deviation of the added Gaussian noise varies from zero to $2\times$ the standard deviation of the noiseless maps.
+		It is clear from those results that the noise makes the problem harder, and that having more pixels available to classify a sample makes the problem easier (the classifier having more evidence to make a decision).
+The FCN variant of HealpixNet beats the CNN variant by exploiting rotation invariance.
+Both variants largely beat the two SVM baselines.
 	}
@@
 \subsection{Filter visualization}
+
 One common visualization for CNN is to observe the shape of the learned filters.
@@
 \section{Augmentation of the dataset for the SVM classifier}
-\label{sec:dataset_augmentation} The original number of samples $480$, $1920$,
+\label{sec:dataset_augmentation}
+
+\todo{better formulation}
+The original number of samples $480$, $1920$,
 $7680$ respectively for order $o=1,2,4$ is considered small to train a deep architecture,
@@
 
-When comparing the network to the baselines, we want to ensure that the SVM classifier has
-access to the same amount of data as the network, i.e, potentially an
-infinite number of samples. Hence, we fit different linear SVM classifiers using
-various training set size until we experimentally observe that
-increasing the amount of data does not improve the accuracy. The validation
-set remain the same and is used for cross-validation to tune the L2
-penalization parameter of SVM. Eventually, we evaluate the final classifier on
-the testing set. An example of the evolution of the training and valdication
-error is shown in \figref{hist_error_evolution}.
+For a fair comparison between HealpixNet and the baselines, we have to ensure that the SVM classifier has access to the same amount of training data as HealpixNet.
+That is potentially an infinite number of samples.
+Hence, we fit different linear SVM classifiers using various training set sizes until we experimentally observe that increasing the amount of training data does not improve performance.
+An example convergence of the training and validation errors is shown in \figref{hist_error_evolution}.
+
+% The validation set remain the same and is used for cross-validation to tune the L2 penalization parameter of SVM.
+% Eventually, we evaluate the final classifier on the test set.
 
@@
 	\includegraphics[width=\linewidth]{hist_error_order2_noise1_5}
-\caption{Evolution curve of the error with respect to the number of training samples for histogram features and a linear classifier (setting: order 2, relative noise level: 1.5).
-The validation error might be slightly below the training error because we use it for cross-validation.}
+	\caption{Error w.r.t.\ the number of training samples for histogram features and the linear SVM (setting: order $o=2$, relative noise level 1.5).
+The error clearly converged and adding more samples will not help.
+The validation error might be slightly below the training error as it is used to select hyper-parameters.}
 	\label{fig:hist_error_evolution}
@@
 
-%% If you have bibdatabase file and want bibtex to generate the
-%% bibitems, please use
-%%
 \section*{Bibliography}
@@
 \endinput
-%%
-%% End of file `elsarticle-template-harv.tex'.

### 2018-08-27 scnn.tex
add a paragraph to explain the results difference between FCN and CNN

@@
 
-% Note that without this graph structure, a fully connected neural network approach would have to be used.
-% Problematically, fully connected neural networks generally scales squarely with their number of inputs.
-% \TK{I don't understand this comment.} \nati{Maybe we should leave it out then. It is not that important.}
+We also observe that the FCN architecture slightly outperforms the CNN one.
+This may seem counterintuitive as the CNN is a generalization of the FCN and hence should provide, at least, equivalently good results.
+Nevertheless, one should not forget that in practice the complexity of the architecture trades with more data requirements and more difficulties in the training.
+We have two interpretations that explains why FCN architecture leads to better performance for two reasons.
+First, the network is almost invariant to rotation on the SO(3) group and hence intrinsically augments the dataset.
+The convergence mass map dataset is likely to be rotational invariant as ...
+\nati{Tomek: could you justify this from a cosmological point of view?}.
+Second, the FCN architecture can be interpreted as a voting procedure where 1) each pixel is being classified using the data in its surroundings, and 2) the average score is computed to determine the class.
+This procedure suits the data as we believe that each class of the dataset is stationary with a small-support radial autocorrelation function.
+\nati{Tomek: can you justify this from a cosmological point of view?} It implies that a pixel can be statistically classified using only its surroundings.
+For other datasets not having these two properties the CNN architecture may be better and one should always, when possible, adapt the architecture to the data.
 
@@
 This work was supported by a grant from the Swiss Data Science Centre (SDCS) under project ID \textit{sd01 - DLOC:  Deep Learning for Observational Cosmology} and grant number 200021\_169130 from the Swiss National Science Foundation.
-\nati{@Tomek: do we need to thank Janis?}
 We would like to thank Jean-François Cardoso for helpful discussions about the spherical harmonics.
+\nati{@Tomek: Raphael?}
 

### 2018-08-28 scnn.tex
changes from last week

@@
 % \documentclass[preprint,12pt,authoryear]{elsarticle}
-\documentclass[final,twocolumn,3p,times,authoryear]{elsarticle}
-
+% \documentclass[final,twocolumn,3p,times,authoryear]{elsarticle}
+% \documentclass[final,twocolumn,3p]{elsarticle}
+\documentclass[final,twocolumn,3p,times,sort&compress]{elsarticle}
 %% Use the option review to obtain double line spacing
@@
 
-%\usepackage{lmodern}
+% TK: This looks OK, but the math is a bit ugly
 \usepackage[T1]{fontenc}
+\usepackage{txfonts} % to remove when done with todo list
+
+% TK: This looks nice but math is spilling out
+% \usepackage{lmodern}
+% \usepackage[T1]{fontenc}
+
+% TK: No difference
+% \usepackage{helvet}
+
 \usepackage[utf8]{inputenc}
@@
 \usepackage{aasmacros}
-
 \usepackage{enumitem} % to remove when done with todo list
+ % to remove when done with todo list
 
@@
 %% for the whole article with \linenumbers.
-%% \usepackage{lineno}
+\usepackage{lineno}
+\linenumbers
 
@@
 \author[ETHZ]{Tomasz Kacprzak}
+\author[ETHZ]{Raphael Sgier(?)}
+% \author{TBD}
 
@@
 Cosmological data often comes in a form of spherical maps, which makes the use of traditional CNNs more complicated.
-The commonly used pixelzation scheme for spherical maps is HEALPix, which uses an equal-area, isolatitude sampling.
+The commonly used pixelzation scheme for spherical maps is Hierarchical Equal Area isoLatitude Pixelisation (HEALPix).
 We present a spherical CNN for analysis of full and partial HEALPix maps, which we call HealpixNet.
@@
 \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-    \item (TK) check text figure 1
-	\item (TK) Related work in cosmo.
+    \item (MD) distinction between CNN and FCN
+    \item (MD) check paragraph on our chosen architecture in the Experiments sections
+    \item (MD) check vertex interpretation in Efficient convolutions. Powers of L are weights of paths.
+    \item (TK) check part sphere notebook and whole sphere
+    \item (NP) Put Raphael in the dataset author.
+    \item (Probably OK) Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
+    \item (Should be done) Check names: we use HealpixNet, HealpixNet (CNN variant), HealpixNet (FCN variant)
+    \item (I think it is OK) (NP) Check the wording.
+Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
+    \item (Everyone should check this) Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
+    \item Check links in footnotes.
+    \item (done!) (NP) Change equation after (2) and check all kroneker
+    \item (done!) (TK) check text figure 1
+    \item (done!) (TK) Related work in cosmo.
 The only cosmological applications of spherical CNNs in the related work are about projection on the tangent plane \citep{schmelze2017cosmologicalmodel, fluri2018deep, gupta2018nongaussianinformation}.
@@
 If none, say it and mention some alternatives, e.g., wavelets?
-	\item (MD) distinction between CNN and FCN
-	\item (MD) check paragraph on our chosen architecture in the Experiments sections
-    \item (MD) check vertex interpretation in Efficient convolutions. Powers of L are weights of paths.
-    \item (TK) check if papers which appear as arxiv were not published in a conference or journal
-    \item (TK) check part sphere notebook and whole sphere
-    \item (TK) read everything
-    \item (NP) Put Raphael in the dataset author. 
+    \item (done!) (TK) check if papers which appear as arxiv were not published in a conference or journal
+    \item (done!) (TK) read everything
+    \item (fail - I checked few fonts here: \url{de.sharelatex.com/learn/Font_typefaces}, but none looked better) (TK) Font: do we have to use times (set in the documentclass)?
+I (MD) find the rendering of math a bit ugly.
+    \item (done!) (TK) fix the bibliography
     \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
-	\item (TK) Example applications for dense prediction (classification and regression) for cosmology (color text in 2.8)
-	\item (Probably OK) Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
-	\item (Should be done) Check names: we use HealpixNet, HealpixNet (CNN variant), HealpixNet (FCN variant)
-    \item (I think it is OK) (NP) Check the wording.
-Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
-	\item (Done) (NP) Change equation after (2) and check all kroneker
-	\item (Everyone should check this) Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
-	\item (TK) Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly.
-    \item (TK) fix the bibliography
-    \item Check links in footnotes.
+    \item (done!) (TK) Example applications for dense prediction (classification and regression) for cosmology (color text in 2.8)
 
@@
 This flexibility might be an advantage to mention.
-In particular, compared to~\citet{cohen2018sphericalcnn} it allows us to do only do the required computation when only a part of the sphere is considered.}
+In particular, compared to~\citep{cohen2018sphericalcnn} it allows us to do only do the required computation when only a part of the sphere is considered.}
 
@@
 A first direction to generalize CNNs to spherical data was to apply a standard 2D CNN to a grid discretisation of the sphere~\citep{boomsma2017spherical,su2017sphericalconv,coors2018spherenet}.
-While this approach uses the well-developed 2D convolution and hierarchical pooling, it is restricted to those specific grid samplings which are highly irregular on the sphere and hence inherently deform the domain where the data is supported.
-A second direction attempted by~\citet{cohen2018sphericalcnn} was to leverage the spherical Fourier transform and to perform the convolution associated to the SO(3) rotation group in the spectral domain, thanks to the convolution theorem.
+While this approach uses the well-developed 2D convolution and hierarchical pooling, it is restricted to specific grid sampling schemes that are highly irregular, and hence inherently deform the domain where the data is supported.
+A second direction attempted by~\citep{cohen2018sphericalcnn} was to leverage the spherical Fourier transform and to perform the convolution associated to the SO(3) rotation group in the spectral domain, thanks to the convolution theorem.
 Contrarily to the first direction, the resulting convolution is rotational equivariant, meaning that a rotation of the input implies the same rotation of the output.
@@
 %(They exist for particular samplings.)
-Finally, the use of a graph to model the discretised sphere was considered by~\citet{khasanova2017graphomni} as well, towards the goal of designing a  network that is invariant to rotations.
-While their architecture accommodates these invariances on the sphere and remains fairly efficient, they did not take advantage of a hierarchical pixelisation and use as pixelisation a grid discretisation of the sphere.
+Finally, the use of a graph to model the discretised sphere was considered by~\citep{khasanova2017graphomni}, towards the goal of designing a network that is invariant to rotations.
+While its architecture accommodates these invariances on the sphere and remains fairly efficient, it did not take advantage of a hierarchical pixelisation and use a simple grid discretisation of the sphere.
 Moreover, the statistical layer, which introduces the invariance, needs to be hand-crafted to capture statistics of interest.
 
+This work is the first to design a spherical convolutional neural network for cosmological applications.
+Previously, several other machine learning algorithms were extended to the sphere, often also including the third, radial direction.
+Most notably, sparsity-based methods were developed, such as wavelets \citep{Leistedt2013flaglets,Leistedt2015spinwavelets}, ridgelets \citep{McEwen2015ridgelet} and curvelets \citep{Chan2017curvelets,Starck2009polarized}.
+
 %\todo{better identify the shortcomings: (i) part of sphere / missing data, (ii) computational efficiency, (iii) equivarience}
-\nati{The part of the sphere/missing data is not really there, but I still do not know how to include it!}
-
-To overcome those shortcomings, we introduce an efficient spherical CNN formulation which uses (i) convolutions on graphs and (ii) hierarchical pooling, while working with the HEALPix sampling.
+% \nati{The part of the sphere/missing data is not really there, but I still do not know how to include it!}
+
+We introduce an efficient spherical CNN formulation which uses (i) convolutions on graphs and (ii) hierarchical pooling, while working with the Hierarchical Equal Area isoLatitude Pixelisation (HEALPix) sampling.
 The main idea is to represent the sphere $S^2$, a 2-dimensional manifold embedded in $\mathbb{R}^3$, as a graph of connected pixels.
@@
 The use of this approach is enabled by recent developments in graph signal processing, where fundamental tools, such as for example the Fourier transform, were defined for graphs \citep{shuman2013emerging}.
-Our approach uses the graph CNN formulation introduced by \citet{defferrard2016convolutional}, which can accommodate any sampling of the sphere.
+Our approach uses the graph CNN formulation introduced by \citep{defferrard2016convolutional}, which can accommodate any sampling of the sphere.
 Using a $k$-nearest neighbours graph, the convolution operation costs $\mathcal{O}(N_{pix})$ operations, where $N_{pix}$ is the number of pixels.
@@
 
-We give a practical demonstration of the application of our package to cosmological model discrimination using convergence maps, similar to the ones used by \citet{schmelze2017cosmologicalmodel}.
+We give a practical demonstration of the application of our package to cosmological model discrimination using maps of projected mass distribution on the sky \citep{chang2017curvedsky}.
+This kind of maps can be created using the gravitational lensing technique \citep[see][for review]{BartelmannSchneider2001weak}.
+Our maps are similar to the ones used by \citep{schmelze2017cosmologicalmodel}.
 In a simplified scenario, we classify convergence maps on parts of a sphere into two cosmological models.
-These models were designed to have the same power spectrum in range $\ell < 1000$.
+These models were designed to have very similar angular power spectrum for the angular wavenumbers $\ell < 1000$.
 We compare the performance of our spherical CNN to a baseline algorithm, an SVM classifier which takes pixel histograms or power spectrum densities (PSDs) of these maps as input.
-The comparison is made as a function of the additive noise level and the used area of the sphere. Results show that our model is better at discriminating the maps and is more resilient to noise.
+The comparison is made as a function of the additive noise level and the area of the sphere used in the analysis.
+% Results show that our model is better at discriminating the maps and is more resilient to noise.
 
@@
 (iv) a pooling operation, and
-(v), optionally,  normalization.\footnote{\citet{ioffe2015batchnorm} have shown that batch normalization helps training. We verified this experimentally in our setting as well.}
+(v), optionally,  normalization.\footnote{\citep{ioffe2015batchnorm} have shown that batch normalization helps training. We verified this experimentally in our setting as well.}
 Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}.
@@
 While our method is applicable to any pixelisation of the sphere, two details depend on the chosen sampling: (i) the choice of neighbours in the construction of the graph, and (ii) the choice of parent nodes when coarsening the graph.
-As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology, our target application, we'll tailor the method to that particular sampling in the subsequent exposition.
+As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology, our target application, we tailor the method to that particular sampling in the subsequent exposition.
 %We'll note in later sections where the method should be adapted for a different sampling.
@@
 
-HEALPix is an acronym for Hierarchical Equal Area isoLatitude Pixelization of a sphere.
-This pixelisation produces a hierarchical subdivision of a spherical surface where each pixel covers the same surface area as every other pixel.
+% HEALPix is an acronym for Hierarchical Equal Area isoLatitude Pixelization of a sphere.
+The HEALPix pixelisation produces a hierarchical subdivision of a spherical surface where each pixel covers the same surface area as every other pixel.
 A hierarchy is desired for the data locality in the computer memory.
@@
 Our graph is constructed as an approximation of the continuous 2D manifold that is the surface of the sphere.
-Indeed, \citet{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity.
-While our construction will not exactly respect the setting defined by \citet{belkin2007convergence}, we observe empirically strong evidence of convergence.
+Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity.
+While our construction will not exactly respect the setting defined by \citep{belkin2007convergence}, we observe empirically strong evidence of convergence.
 
@@
 In the particular case where the Laplacian matrix $\L$ is circulant, $\T_i h$ is a translated version of $\T_j h$ for all $i, j$ and both convolutions are equivalent.
-We refer the reader to \citet[Sec 2.2]{perraudin2017stationary} for a detailed discussion of the connection between translation $T_i$ and localization $\T_i$.
+We refer the reader to \citep[Sec 2.2]{perraudin2017stationary} for a detailed discussion of the connection between translation $T_i$ and localization $\T_i$.
 
@@
 
-Following \citet{defferrard2016convolutional}, we define our filters as Chebyshev polynomials such as the convolution operation becomes
+Following \citep{defferrard2016convolutional}, we define our filters as Chebyshev polynomials such as the convolution operation becomes
 \begin{equation} \label{eqn:graph_convolution_cheby}
@@
 While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
-In practice, we found out in our experiment that Chebyshev polynomials are slightly more stable than the monomials used in~\cite{khasanova2017graphomni}(i.e.
+In practice, we found out in our experiment that Chebyshev polynomials are slightly more stable than the monomials used in~\cite{khasanova2017graphomni} (i.e.
 optimizing directly the $\theta_k$ in \eqnref{graph_convolution_monomial}).
@@
 % The advantage of schemes based on a base polyhedron is that cells are equal-area.
-While that is not required for the convolution operation when modeling with graphs (it can be corrected by setting edge weights appropriately, see \citet{khasanova2017graphomni})
+While that is not required for the convolution operation when modeling with graphs (it can be corrected by setting edge weights appropriately, see \citep{khasanova2017graphomni})
 % nope: can also do a regular pooling on the equirectangular. It preserves the sampling, and the convolution is adapted to the sampling thanks to the edge weights.
@@
 
-Following \citet{khasanova2017tigranet}, we implement an optional statistical layer between the last graph convolutional layer and the first fully connected layer for the neural network.
+Following \citep{khasanova2017tigranet}, we implement an optional statistical layer between the last graph convolutional layer and the first fully connected layer for the neural network.
 This introduces the invariance of the output to isometric transformations, such as rotation of maps on the sphere.
@@
 where $f$ computes $N_{stat}$ statistics which are independent from the size of the map, $N_{pix}$.
-An example is the global average pooling $f(\x) = \esp(\x)$, introduced by \citet{lin2013globalavgpooling}, where $\esp(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} x_i$ is the empirical mean.
+An example is the global average pooling $f(\x) = \esp(\x)$, introduced by \citep{lin2013globalavgpooling}, where $\esp(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} x_i$ is the empirical mean.
 Another example is $f(\x) = [\esp(\x), \var(\x)]\trans$, where $\var(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} (x_i - \esp(\x))^2$ is the empirical variance.
@@
 The statistical layer, defined in \eqnref{stat_layer}, independently transforms each of the $F$ feature maps of the input $\X \in \R^{N_{pix} \times F}$ into $\Y = ST(\X) \in \R^{N_{stat} \times F}$, where $N_{stat}$ is the number of statistics.
-One may even omit the FC layers and directly fed the output of the ST layer into the softmax layer, as proposed by \citet{lin2013globalavgpooling}.
+One may even omit the FC layers and directly fed the output of the ST layer into the softmax layer, as proposed by \citep{lin2013globalavgpooling}.
 In this regime, $N_{stat} = 1$ and $F = N_{classes}$ is the number of classes to discriminate (i.e., the last GC layer outputs as many feature maps as there is classes).
@@
 \end{equation*}
-Such networks are useful for (i) dense regression, such as denoising a map, interpolating missing values, or predicting a density map given the CMB, or (ii) dense classification, such as segmenting galactic clusters in a \todo{xx} map.
-\todo{TK: please find better cosmological applications.
-Maybe some refs?} We emphasize that the use of FC and ST layers is the sole difference between a neural network engineered for global or dense prediction.
+Such networks can be useful for
+(i) dense regression, such as denoising, interpolating missing values, or inpainting a parts of a map \citep{Inoue2008inpainting}, or
+(ii) dense classification, such as segmentation or feature detection \citep{Amsel2007detecting}.
+We emphasize that the use of FC and ST layers is the sole difference between a neural network engineered for global or dense prediction.
 
@@
 Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system.
-Middle: an equiangular cubed-sphere grid, as described in \citet{ronchi1996cubed}.
+Middle: an equiangular cubed-sphere grid, as described in \citep{ronchi1996cubed}.
 Right: graph built from an HEALPix pixelization of half the sphere ($N_{side} = 4$).
-By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[7] Left and middle figures are taken from \citet{boomsma2017spherical}.}
+By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[7] Left and middle figures are taken from \citep{boomsma2017spherical}.}
     \label{fig:sphere_grids}
@@
 
-A first approach, explored by \citet{boomsma2017spherical} for molecular modeling and \citet{su2017sphericalconv, coors2018spherenet} for omnidirectional imaging, is to use a 2D CNN on a discretization of the sphere that is a grid, such as the equirectangular projection (\figref{sphere_grids} left), or a set of grids, such as the cubed-sphere defined by~\citet{ronchi1996cubed} (\figref{sphere_grids} middle).
+A first approach, explored by \citep{boomsma2017spherical} for molecular modeling and \citep{su2017sphericalconv, coors2018spherenet} for omnidirectional imaging, is to use a 2D CNN on a discretization of the sphere that is a grid, such as the equirectangular projection (\figref{sphere_grids} left), or a set of grids, such as the cubed-sphere defined by~\citep{ronchi1996cubed} (\figref{sphere_grids} middle).
 As this formulation uses the standard 2D convolution, all the optimizations developed for images can be applied, what makes it computationally efficient.
@@
 
-\citet{cohen2018sphericalcnn} and \citet{esteves2017sphericalcnn} addressed the problem of rotation equivariance leveraging the convolution associated to the 3D rotation group SO(3), with applications to atomization energy regression and 3D model classification, alignment and retrieval.
+The problem of rotation equivariance was addressed \citep{cohen2018sphericalcnn,esteves2017sphericalcnn} by leveraging the convolution associated to the 3D rotation group SO(3), with applications to atomization energy regression and 3D model classification, alignment and retrieval.
 The resulting convolution is performed by (i) a spherical harmonic transform (SHT), i.e., a projection on the spherical harmonics, (ii) a  multiplication in the spectral domain, and (iii) an inverse SHT.
@@
 In comparison, filtering with our HealpixNet method scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}).
-\citet{kondor2018clebsch} proposed to use the Clebsh-Gordan transform to perform a non-linear transformation in the spectral domain.
+The Clebsh-Gordan transform was proposed \citep{kondor2018clebsch} to perform a non-linear transformation in the spectral domain.
 As such, a SHT only has to be performed once at the input of the network and the back and forth SHT between every layer is no longer required.
@@
 While the convolution in the spectral domain avoid all sampling problems, one of its downsides might the lack of natural locality, a property that is naturally obtained by the polynomial approach of graph convolution.
-Because the convolution is at the begging of the neural network, we believe that is should focus on local correlations first before exacting more complex structures.
+Because the convolution is at the begging of the neural network, we believe that it should focus on local correlations first before exacting more complex structures.
 %\todo{Polynomial formulation enforces locality, which otherwise has to be enforced by smoothness in the spectral domain.}
-%\todo{Pooling in the spectral domain? \citet{esteves2017sphericalcnn} do something.}
+%\todo{Pooling in the spectral domain? \citep{esteves2017sphericalcnn} do something.}
 % While a comparison is theoretically possible, the experiments of~\cite{cohen2018sphericalcnn} are done using the geodesic grid sampling set and do not provide any code for the HEALPix one.
@@
 
-All the above methods cannot easily be accelerated when the data lies on a part of the sphere only.
-That is, however, an important use case in cosmology as measurements are often partial, i.e., full-sky maps are rare.
+All the above methods cannot be easily accelerated when the data lies on a part of the sphere only.
+That is an important use case in cosmology as measurements are often partial, i.e., full-sky maps are rare.
 One could still fill the unseen part of the sphere with zeros, and avoid computing empty integrals.
@@
 
-The use of a graph to model the discretised sphere was also considered by \citet{khasanova2017graphomni} for omnidirectional imaging.
+The use of a graph to model the discretised sphere was also considered by \citep{khasanova2017graphomni} for omnidirectional imaging.
 % The authors map omnidirectional images onto a sphere, with the goal of correcting for distortions induced by the lens, which was used for their acquisition.
-% First, similarly to~\citet{boomsma2017spherical}, they use an equirectangular grid sampling.
+% First, similarly to~\citep{boomsma2017spherical}, they use an equirectangular grid sampling.
 This work is the closest to our method, with three differences.
@@
 Second, they did not take advantage of a hierarchical pixelization of the sphere and resorted to dynamic pooling \citep{kalchbrenner2014dcnn}.
-While that operation is useful for sequences of varying length, such as sentences in language models, it is overkill in our context as it is not local and destroys spatial coherence.
+While that operation is useful for sequences of varying length, such as sentences in language models, it could be impractical in our context, as it is not local and destroys spatial coherence.
 Third, they introduced a statistical layer --- an operation that computes a set of statistics from the last feature maps --- to provide full rotation invariance.
@@
 
-The connection has been made between graph CNNs and group equivariant CNNs by \citet{kondor2018equivariance}, justifying the use of graphs to gain rotation equivariance on the sphere. 
+The connection has been made between graph CNNs and group equivariant CNNs by \citep{kondor2018equivariance}, justifying the use of graphs to gain rotation equivariance on the sphere.
 \todo{More here.}
 
-Many formulations of graph neural networks, reviewed by \citet{bronstein2017review} and \citet{hamilton2017review}, have been proposed.
-For this contribution, we chose the formulation of \citet{defferrard2016convolutional} as its root on strong graph signal processing theory makes the concept of convolutions and filters explicit \citep{shuman2013emerging}.
+Many formulations of graph neural networks, reviewed by \citep{bronstein2017review} and \citep{hamilton2017review}, have been proposed.
+For this contribution, we chose the formulation of \citep{defferrard2016convolutional} as its root on strong graph signal processing theory makes the concept of convolutions and filters explicit \citep{shuman2013emerging}.
 As the convolution is motivated by a multiplication in the graph Fourier spectrum, it is close in spirit, and empirically, to the formulation based on the spherical harmonics, which is the ideal rotation equivariant formulation.
@@
 The performance of HealpixNet is demonstrated on a discrimination problem: the classification of convergence maps into two cosmological model classes.
-The experiment presented here is similar to the one by \citet{schmelze2017cosmologicalmodel}.
+The experiment presented here is similar to the one by \citep{schmelze2017cosmologicalmodel}.
 These maps are similar to those created with gravitational lensing techniques \citep{chang2017curvedsky}.
@@
 While we only demonstrate a classification task here, other tasks, such as regression or segmentation, are also possible (c.f. \secref{architecture}).
-The regression task will most likely be the most practical cosmological application, as described in \citet{gupta2018nongaussianinformation} and \citet{fluri2018deep}.
+The regression task will most likely be the most practical cosmological application, as described in \citep{gupta2018nongaussianinformation} and \citep{fluri2018deep}.
 Implementation of full cosmological inference requires, however, many more simulations, building the likelihood function, and several other auxiliary tasks.
@@
 
-The simulations are created using the fast lightcone method described in \citet{sgier2018fastgeneration}.
+The simulations are created using the fast lightcone method \pkg{UFalcon} described in \citep{sgier2018fastgeneration}.
 We however use a single simulation box, as opposed to two used in that work, as we use source galaxies at a lower redshift of $z=1$, instead of $z=1.5$.
@@
 For each class, we generate $30$ simulations.
-Out of the $60$ simulations, $20$ are kept as the test set, and $20\%$ of the remaining training data is used as a validation set (to monitor the training process and select the hyper-parameters).
+Out of the $60$ simulations, $20$ are kept as the test set, and $20\%$ of the remaining training data is used as a validation set, to monitor the training process and select the hyper-parameters.
 \figref{map_sample} shows the full sky simulations and a zoom region for both models.
@@
 Stationarity of N-body simulations.
-
-While the number of maps might sound small for deep learning, the information contained in the maps is very redundant, allowing us to use parts of the map as samples for our simulation.
+\TK{Not sure what is meant here}
+
+% While the number of maps might sound small for deep learning, the information contained in the maps is very redundant, allowing us to use parts of the map as samples for our simulation.
+As many cosmological applications will use datasets located on part-sphere only, we use parts of the map as independent samples for our analysis.
 Using the properties of the HEALPix sampling, we can split each map into $12 \times o^2$ ($o=1,2,4,\dots$) samples that span a smaller part of the sphere.
@@
 		The difficulty of the task depends on the level of noise and the size of a sample (that is, the number of pixels that constitute the sample to classify).
-Order 1 corresponds to samples which area is $\frac{1}{12}=8.1\%$ of the sphere, order 2 to $\frac{1}{12 \times 2^2} = 2.1\%$, and order 4 to $\frac{1}{12 \times 4^2} = 0.5\%$.
+Order 1 corresponds to samples which area is $1/12=8.1\%$ of the sphere, order 2 to $1/(12 \times 2^2) = 2.1\%$, and order 4 to $1/(12 \times 4^2) = 0.5\%$.
 The standard deviation of the added Gaussian noise varies from zero to $2\times$ the standard deviation of the noiseless maps.
@@
 This is likely due to the fact that the HealpixNet can learn optimal features for the problem and does not rely on hand-designed features.
-
-We observe that the PSD is unable to perform the desired task.
+The accuracy of HealpixNet is $>97\%$ for orders $o=1$ and $o=2$, for all noise levels, and starts to deteriorate for $o=4$, reaching 90\% for the highest noise level.
+
+We observe that the PSD is unable to perform the desired task, with accuracy decreasing significantly for all noisy cases.
 The main reason is that the two different models were designed to have very similar PSDs (see \figref{psd_sigma3}).
-As a result, one needs to use other statistics to solve the problem.
+% As a result, one needs to use other statistics to solve the problem.
 In this case, the histogram features allow for a significant improvement over the PSD ones.
-Unfortunately, while the histogram features contain information about the distribution of pixels, they do not include any spatial information.
+The performance of the histogram features is very good for larger maps and deteriorates for the smaller cases with increased noise level, reaching 80\% at the highest noise level for $o=4$.
+The histogram features contain information about the distribution of pixels, which clearly varies for the two classes.
+They do not, however, include any spatial information.
 In contrast, both the PSD features and the HealpixNet can exploit the spatial information.
@@
 We also observe that the FCN architecture slightly outperforms the CNN one.
-This may seem counterintuitive as the CNN is a generalization of the FCN and hence should provide, at least, equivalently good results.
+This may seem counter-intuitive as the CNN is a generalization of the FCN and hence should provide, at least, equivalently good results.
 Nevertheless, one should not forget that in practice the complexity of the architecture trades with more data requirements and more difficulties in the training.
-We have two interpretations that explains why FCN architecture leads to better performance for two reasons.
+We have two interpretations that explains why FCN architecture leads to better performance.
 First, the network is almost invariant to rotation on the SO(3) group and hence intrinsically augments the dataset.
-The convergence mass map dataset is likely to be rotational invariant as ...
-\nati{Tomek: could you justify this from a cosmological point of view?}.
-Second, the FCN architecture can be interpreted as a voting procedure where 1) each pixel is being classified using the data in its surroundings, and 2) the average score is computed to determine the class.
-This procedure suits the data as we believe that each class of the dataset is stationary with a small-support radial autocorrelation function.
-\nati{Tomek: can you justify this from a cosmological point of view?} It implies that a pixel can be statistically classified using only its surroundings.
+The convergence mass map dataset is likely to be rotational invariant as the mass distribution is homogeneous and isotropic.
+Second, the FCN architecture can be interpreted as a voting procedure where
+(i) each pixel is being classified using the data in its surroundings, and
+(ii) the average score is computed to determine the class.
+This procedure suits the data as we believe that each class of the dataset is stationary with a small-support radial autocorrelation function, again stemming from the homogeneity of the dataset.
+It implies that a pixel can be statistically classified using only its surroundings.
 For other datasets not having these two properties the CNN architecture may be better and one should always, when possible, adapt the architecture to the data.
@@
 \nati{Michael: I am highly uncertain of what should be kept in the following paragraph. Maybe the full paragraph should be left out!}
+\TK{I have a similar impression!}
 While testing the FCN and CNN architectures, we made the following empirical observations.
@@
 We compared the performance of the HealpixNet CNN versus that of two SVM-based classifiers: one trained on the spherical harmonics power spectrum, and the other on the pixel density histogram.
-Notably, HEALPix maintains good classification accuracy even for high noise levels and part-sky areas.
+% Notably, HealpixNet maintains good classification accuracy even for high noise levels and part-sky areas.
+HealpixNet performs better than the angular power spectrum and the histogram classifiers for all considered cases.
+The advantage is small for large, noise-free maps, and grows up to 10\% for smaller, noisier data.
 
@@
 We would like to thank Jean-François Cardoso for helpful discussions about the spherical harmonics.
-\nati{@Tomek: Raphael?}
+We would like to thank Alexandre Refregier, Adam Amara, Thomas Hofmann and Fernando Perez-Cruz for advice and helpful discussions.
+We thank Hamsa Padmanabhan for testing use cases of the code.
 
@@
 \section*{Bibliography}
-\bibliographystyle{elsarticle-harv}
+% \bibliographystyle{elsarticle-harv}
+\bibliographystyle{elsarticle-num}
+\biboptions{sort}
 \bibliography{biblio}

### 2018-08-28 scnn.tex
second pass over the experiments section

@@
 Both our Python implementation\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are openly available online.
-Furthermore, Jupyter notebooks demoing the method and problem can be run from your browser without installing anything, thank to Binder.
-
-While we only demonstrate a classification task here, other tasks, such as regression or segmentation, are also possible (c.f. \secref{architecture}).
+Furthermore, Jupyter notebooks demoing the method and problem can be run from your browser without installing anything.
+
+While we only demonstrate a classification task here, other tasks, such as regression or segmentation, are also possible (see \secref{architecture}).
 The regression task will most likely be the most practical cosmological application, as described in \citep{gupta2018nongaussianinformation} and \citep{fluri2018deep}.
@@
 The resulting Power Spectrum Density (PSD), computed using the \texttt{anafast} function of the HEALPix package, are displayed in \figref{psd_sigma3}.
-We also subtract the mean of each map and down-sample them to a resolution of $N_{side}=1024$.
+We also subtract the mean of each map and down-sample them to a resolution of $N_{side}=1024$, which corresponds to maps of $12 \times 1024^2 \approx 12 \times 10^6$ pixels.
 
@@
 
-\todo{thanks to stationarity, quantity of information is constant. Motivation: partial sky maps. Larger surfaces improve confidence in the prediction, the average trick.}
-All pixels are as informative as any other.
-Stationarity of N-body simulations.
-\TK{Not sure what is meant here}
-
-% While the number of maps might sound small for deep learning, the information contained in the maps is very redundant, allowing us to use parts of the map as samples for our simulation.
-As many cosmological applications will use datasets located on part-sphere only, we use parts of the map as independent samples for our analysis.
-Using the properties of the HEALPix sampling, we can split each map into $12 \times o^2$ ($o=1,2,4,\dots$) samples that span a smaller part of the sphere.
-% As shown in \figref{part_sphere}, we used $o=1,2,4$ as the resulting samples are large enough to suffer from the effects of the spherical geometry.
-The resulting maps are large enough to suffer from the effects of the spherical geometry, and cover 8.3\%, 2.1\% and 0.5\% of the total sphere area for $o=1,2,4$, respectively.
-The areas on the sphere corresponding to these orders can be seen in \figref{pooling}: the pixels in the left, middle and right spheres correspond to $o=4,2,1$, respectively.
-We decided to only report simulation results for this specific setting as spherical cosmological data usually does not span the full sphere.
-Nevertheless, our code includes an example using the full sphere.
+As the distribution of matter in the universe is homogeneous and isotropic, no pixel is more informative than any other.\footnote{Contrast that with images, where the subject of interest is most often around the center of the picture.}
+As such, we can control the difficulty of the classification problem by limiting the number of pixels available to the algorithms, i.e., extracting partial maps from full sky maps.
+Using the properties of HEALPix, we split maps into $12 \times o^2$ ($o=1,2,4,\dots$) independent samples of $(N_{pix} / o)^2$ pixels.
+The resulting partial maps are large enough to suffer from the effects of the spherical geometry, and cover 8.3\% ($\approx 1 \times 10^6$ pixels), 2.1\% ($\approx 260 \times 10^3$ pixels), and 0.5\% ($\approx 65 \times 10^3$ pixels) of the sphere for $o=1,2,4$, respectively.
+Corresponding areas can be seen in \figref{pooling}: the surface of pixels in the left, middle, and right spheres correspond to samples at order $o=4,2,1$, respectively.
+We report results for $o=1,2,4$ only, as full sphere classification is easy at such resolution (perfect classification accuracy is already attainable for $o=1$, see \figref{results}), and many cosmological applications will use datasets located on part-sphere only.
+Our code nonetheless includes an example demoing classification on full spheres of much lower resolution ($N_{side} = 64$).
 
@@
 To make the discrimination harder and the problem more realistic, centered Gaussian noise is added to the simulated maps.
-The standard deviation of the noise varies from $0\times$ (i.e., no noise) to $2\times$ the standard deviation of the noiseless maps.
+The standard deviation of the noise varies from zero (i.e., no noise) to $2\times$ the standard deviation of pixel's values in the noiseless maps.
 While the noise model of real maps often has a slightly different distribution, Gaussian noise should be a sufficient model to demonstrate the performance of our method.
@@
 
-We build a robust classifier, which automatically discriminates between the two classes in the presence of noise.
-We check the classification performance as a function of the area used, the order $o$, and the relative level of the noise added to the map.
-
 HealpixNet is compared against two simple yet powerful benchmarks.
-The two baselines are based on features that are (i) the power spectral densities (PSD), and (ii) the histogram of pixels in the maps \citep{patton2017cosmologicalconstraints}.
+The two baselines are based on features that are (i) the power spectral densities (PSD) of maps, and (ii) the histogram of pixels in the maps \citep{patton2017cosmologicalconstraints}.
 After normalization, those features are used by a linear support vector machine (SVM) trained for classification.
@@
 As for HealpixNet, the SVM regularization hyper-parameter was tuned based on the performance over the validation set.
-
-\subsection{Selected architecture and hyper-parameters}
+The classification accuracy of HealpixNet and both baselines was checked as a function of the used area (the order $o$), and the relative level of additive noise.
+
+\subsection{Network architecture and hyper-parameters}
 %\subsection{Selected network architecture}
+%\subsection{Methods} % baselines and HealpixNet together
 \label{sec:selected_architecture}
 
-The choice of a particular HealpixNet architecture highly depends on the problem at hand.
-Convolution layers construct \emph{almost} rotational equivariant features and the statistical layer can turn them into rotational invariant ones.
-In our case, we are trying to discriminate samples of two cosmological maps.
-Hence, we assume that each pixel carries some information about the distribution.
-Our principal architecture is a fully convolutional network referred as the FCN variant of HealpixNet.
-Thanks to 6 graph convolution layers (GC sizes: 16, 32, 64, 64, 64, 2) we first build the statistical evidence of each distribution for each pixel of a down-sampled sphere.
-The last graph convolution layer is composed of 2 channels as we have 2 distributions.
-Then we use a statistical 'mean' layer (SL) to average the evidence for each distribution and we compute the probabilities thanks to a softmax layer (SM).
-We use batch normalization (BN), pooling (P) and relu non-linearity $\sigma$ for each convolutional layer.
-The degree of the Chebyshev polynomials was set to $K=5$.
-The network can be summarized as
-\begin{equation*}
-	FCN = SM \circ ST_{\text{mean}} \circ L_6 \circ L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1,
+As discussed in \secref{variants}, the choice of an HealpixNet variant depends on the data and task at hand.
+For our problem, where we assume that each pixel carries the same quantity of information about the cosmological model, a rotation invariant FCN architecture should be best.
+The chosen network is defined as
+\begin{equation*}
+	FCN = SM \circ ST_{\text{mean}} \circ GC_2 \circ L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1,
 \end{equation*}
 \begin{center}
-where \hspace{0.5cm} \begin{tabular}{lll}
-   $L_1$ &  $=$ &$ P \circ \sigma \circ BN \circ GC_{16}$, \\
-   $L_2$ &  $=$ &$ P \circ \sigma \circ BN \circ GC_{32}$, \\
-   $L_3,L_4,L_5$ & $=$ &$ P \circ \sigma \circ BN \circ GC_{64}$, \\
-   $L_6$ &  $=$& $ \sigma \circ BN \circ GC_{2}$. \\
+with \hspace{0.5cm} \begin{tabular}{lll}
+   $L_1$ &  $=$ &$ P_4 \circ \sigma \circ BN \circ GC_{16}$, \\
+   $L_2$ &  $=$ &$ P_4 \circ \sigma \circ BN \circ GC_{32}$, \\
+   $L_3,L_4,L_5$ & $=$ &$ P_4 \circ \sigma \circ BN \circ GC_{64}$, \\
 \end{tabular}
 \end{center}
-Thanks to its statistical layer, the FCN architecture is close invariant to rotation.
-We also tried a more traditional architecture, where the statistical and last convolutional layers are replaced by a fully connected layer.
-Hence we end up with a convolutional neural network (CNN) that is not invariant to rotation anymore.
-The network is referred as CNN variant of HealpixNet and can be summarized as
-\begin{equation}
-CNN = SM \circ \sigma \circ FC_2 \circ L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1.
-\end{equation}
-
-We use the Adam optimizer \citep{kingma2014adam} with $\beta_1=0.9$, $\beta_2=0.999$, and an initial learning rate of $2 \times 10^{-4}$ that is exponentially decreased by a multiplication with $0.999$ at each step.
+where $GC_k$ indicates a graph convolutional layer with $k$ output feature maps, $P_4$ is a pooling layer which divides the number of pixels by 4, $\sigma$ is a ReLU, and the Chebyshev polynomials are of degree $K=5$.
+
+For comparison, we tried the more conventional CNN variant, where the classification is performed by a fully connected layer from the last feature maps instead of the average of local classifications.
+This architecture is not invariant to rotation.
+The network is defined as
+\begin{equation*}
+	CNN = SM \circ FC_2 \circ L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1,
+\end{equation*}
+where $FC_2$ denotes a fully connected layer with two output neurons.
+Architectures were chosen over their performance on the validation set.
+
+The Adam optimizer \citep{kingma2014adam} with $\beta_1=0.9$, $\beta_2=0.999$ was used with an initial learning rate of $2 \times 10^{-4}$ that is exponentially decreased by a multiplication with $0.999$ at each step.
 All models were trained for $80$ epochs, which corresponds to $1920$ steps.
@@
 Training took approximately $1.5$ hour using a single Nvidia GeForce GTX 1080 Ti ($5$ hours with a Tesla K20).
-% The CPU is probably slow which explain the 5 hours.
-I believe we could be much faster than that by computing less summaries and improving the data.
-But, Michael, it's OKAY to have a margin of improvement.
-:-)
+% Could probably be faster with a better input pipeline.
 
@@
 	\caption{
-		Classification errors that compare the performance of the fully convolutional (FCN) and the standard convolutional (CNN) variants of the HealpixNet architecture, the support vector machine (SVM) with the power spectral densities (PSDs) as features, and the SVM with histogram as features.
+		Classification accuracy of the fully convolutional (FCN) variant of HealpixNet, the standard convolutional (CNN) variant of HealpixNet, the support vector machine (SVM) with the power spectral density (PSD) as features, and the SVM with the histogram as features.
 		The difficulty of the task depends on the level of noise and the size of a sample (that is, the number of pixels that constitute the sample to classify).
-Order 1 corresponds to samples which area is $1/12=8.1\%$ of the sphere, order 2 to $1/(12 \times 2^2) = 2.1\%$, and order 4 to $1/(12 \times 4^2) = 0.5\%$.
-The standard deviation of the added Gaussian noise varies from zero to $2\times$ the standard deviation of the noiseless maps.
+Order $o=1$ corresponds to samples which area is $\frac{1}{12}=8.1\%$ of the sphere, order $o=2$ to $\frac{1}{12 \times 2^2} = 2.1\%$, and order $o=4$ to $\frac{1}{12 \times 4^2} = 0.5\%$.
+The standard deviation of the added Gaussian noise varies from zero to $2\times$ the standard deviation of pixel's values in the noiseless maps.
 		It is clear from those results that the noise makes the problem harder, and that having more pixels available to classify a sample makes the problem easier (the classifier having more evidence to make a decision).
-The FCN variant of HealpixNet beats the CNN variant by exploiting rotation invariance.
+The FCN variant of HealpixNet beats the CNN variant by being invariant to rotation.
 Both variants largely beat the two SVM baselines.
@@
 
-\figref{results} presents the results for $5$ different noise levels and $3$ different sample areas.
-HealpixNet (FCN and CNN) has a significant lead for all levels of noise and sample areas.
-In particular, the difference seems to increase as the problem becomes more complex; as the order is increased, there is less information in each sample.
-This is likely due to the fact that the HealpixNet can learn optimal features for the problem and does not rely on hand-designed features.
-The accuracy of HealpixNet is $>97\%$ for orders $o=1$ and $o=2$, for all noise levels, and starts to deteriorate for $o=4$, reaching 90\% for the highest noise level.
-
-We observe that the PSD is unable to perform the desired task, with accuracy decreasing significantly for all noisy cases.
-The main reason is that the two different models were designed to have very similar PSDs (see \figref{psd_sigma3}).
-% As a result, one needs to use other statistics to solve the problem.
-In this case, the histogram features allow for a significant improvement over the PSD ones.
-The performance of the histogram features is very good for larger maps and deteriorates for the smaller cases with increased noise level, reaching 80\% at the highest noise level for $o=4$.
+\figref{results} compares the classification accuracy of HealpixNet (FCN and CNN variants) and the two baselines across five noise levels and three sample sizes.
+We indeed observe that the problem is made more difficult as the sample size decreases, and the noise increases.
+As less pixels are available to make a decision about a sample, the algorithms have access to less information and make more mistakes.
+As the noise increases, the useful information gets diluted in irrelevant data, i.e., the signal-to-noise ratio (SNR) diminishes.
+
+As the cosmological parameters were chosen for the maps to have similar PSDs (see \figref{psd_sigma3}), it is reassuring to observe that an SVM with those as features has difficulties discriminating the models.
+Other statistics are therefor needed to solve the problem. Using histograms as features gives a significant improvement.
+Performance is very good for larger maps and deteriorates for the smaller cases with increased noise level, reaching 80\% at the highest noise level for $o=4$.
 The histogram features contain information about the distribution of pixels, which clearly varies for the two classes.
 They do not, however, include any spatial information.
-In contrast, both the PSD features and the HealpixNet can exploit the spatial information.
-
-We also observe that the FCN architecture slightly outperforms the CNN one.
-This may seem counter-intuitive as the CNN is a generalization of the FCN and hence should provide, at least, equivalently good results.
-Nevertheless, one should not forget that in practice the complexity of the architecture trades with more data requirements and more difficulties in the training.
-We have two interpretations that explains why FCN architecture leads to better performance.
-First, the network is almost invariant to rotation on the SO(3) group and hence intrinsically augments the dataset.
-The convergence mass map dataset is likely to be rotational invariant as the mass distribution is homogeneous and isotropic.
-Second, the FCN architecture can be interpreted as a voting procedure where
-(i) each pixel is being classified using the data in its surroundings, and
-(ii) the average score is computed to determine the class.
+HealpixNet (both the FCN and CNN variants) shows superior performance over all configurations.
+The gap even widens as the problem becomes more difficult.
+This is likely due to HealpixNet learning features that are adapted to the problem instead of relying on hand-designed features.
+The accuracy of HealpixNet is $>97\%$ for orders $o=1$ and $o=2$, for all noise levels, and starts to deteriorate for $o=4$, reaching 90\% for the highest noise level.
+
+We also observe that the FCN variant slightly outperforms the CNN.
+This may seem counterintuitive as the CNN is a generalization of the FCN and hence should provide, at least, equivalently good results.
+Nevertheless, one should not forget that in practice the complexity of the architecture trades with more data requirements and more training difficulties.
+Two interpretations explain why the FCN variant leads to better performance. First, the FCN is almost invariant to rotation on the SO(3) group and hence intrinsically augments the dataset.
+The convergence mass map dataset is invariant to rotation as the mass distribution is homogeneous and isotropic.
+Second, the FCN can be interpreted as a voting procedure where (i) each pixel is being classified using the data in its surroundings, and (ii) the average score is computed to determine the class.
 This procedure suits the data as we believe that each class of the dataset is stationary with a small-support radial autocorrelation function, again stemming from the homogeneity of the dataset.
 It implies that a pixel can be statistically classified using only its surroundings.
-For other datasets not having these two properties the CNN architecture may be better and one should always, when possible, adapt the architecture to the data.
-
-\nati{Michael: I am highly uncertain of what should be kept in the following paragraph. Maybe the full paragraph should be left out!}
-\TK{I have a similar impression!}
-While testing the FCN and CNN architectures, we made the following empirical observations.
-First, Chebyshev polynomial seems more stable than monomials ($\theta_k$ in \eqnref{graph_convolution_monomial}), in the sense that the training loss had a more monotone decrease.
-Nevertheless once the network is trained, we could not observe a significant accuracy difference.
-Second, using a statistical layer (FCN) to get equivariant features slightly improved the accuracy in our problem.
-We tried $4$ different layers `mean', `variance', `mean + variance' and `histogram'.
-The `mean', `histogram' and `mean + variance' were providing the same level of accuracy, with pure `variance' being slightly worse. Hence we chose to simply use the `mean' statistic.
-Third, adding fully connected layers after the statistical layer does not improve the performance, but lead to models requiring more training steps and regularization.
-Fourth, using $\ell_2$ regularization does not help either with the performance or the training of the models.
-Fifth, we recommend initializing the Chebyshev coefficients with a centered Gaussian distribution with standard deviation $\sqrt{2/(F * (K + 0.5))}$, where $K$ is the Chebyshev order and $F$ the number of input channels.
-This standard deviation has the property to keep the energy of the signal more or less at the same level between the different layers.
+The CNN variant may however be better for data not having this property, and one should always adapt the architecture to the data and task.
+
+While testing the FCN and CNN variants, we made the following empirical observations.
+First, training was more stable (in the sense that the loss had a more monotone decrease) when using Chebyshev polynomials, as in \eqnref{graph_convolution_cheby}, rather than monomials, as in \eqnref{graph_convolution_monomial}.
+Nevertheless, we could not observe a significant difference in accuracy after convergence.
+Second, using $\ell_2$ regularization does not help either with performance or training of the models, mostly because the models are not over-fitting.
+Third, we recommend initializing the Chebyshev coefficients with a centered Gaussian distribution with standard deviation $\sqrt{2/(F_{in} \times (K + 0.5))}$, where $K$ is the degree of the Chebyshev polynomials and $F_{in}$ the number of input channels.
+This standard deviation has the property to keep the energy of the signal more or less constant across layers.
+\todo{Nath: cite the paper you read about that?}
 % Nati to Michael: The problem with the previous claim is that it depends on the non-linarity. Furthermore, does it make sense to make such a claim if we use batch norm?
-Eventually, we observe that rescaling the Laplacian eigenvalues between $[-a,a]$, where $1<a\leq1$ significantly helps to stabilize the optimization. For our experiment we use $a=0.75$.
+Finally, we observe that scaling the Laplacian's eigenvalues between $[-a, a]$, where $0 < a \leq 1$, significantly helps in stabilizing the optimization. We use $a = 0.75$ in our experiments.
 
@@
 
-One common visualization for CNN is to observe the shape of the learned filters.
-Since our construction leads to almost (up to the sampling irregularities) spherical filters, we plot in \figref{learned_filter} both the radial profile and a gnomonic projection on a plane of a random selection of learned filters.
-The filters are selected from the last layer of the network corresponding the experiment with order $o=2$ for a relative noise level of $2$.
-Nevertheless, all networks presented visually similar gnomonic and profile patterns.
-% The gnomonic projection clearly exibits the sampling issue of HEALPix.
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{section_filter_last}
+	\\
+	\includegraphics[width=\linewidth]{gnonomic_filter_last}
+	\caption{Random selection of 24 learned filters from the fifth spherical convolutional layer $L_5$. Top: section. Bottom: gnomonic view.}
+	\label{fig:learned_filter}
+\end{figure}
+
+A common visualization to introspect and try to understand how a CNN function is to look at the learned filters.
+Since our construction leads to almost (up to sampling irregularities) spherical filters, we plot in \figref{learned_filter} both the radial profile and a gnomonic projection on a plane of a random selection of learned filters from the last layer of the network.
+While those particular filters were obtained from the experiment with order $o=2$ and a relative noise level of $2$, all trained networks presented visually similar gnomonic and profile patterns.
+% The gnomonic projection clearly exhibits the sampling issue of HEALPix.
 % \TK{what issue? Commenting out for now}
 Details of how the convolution kernels are plotted are described in \ref{sec:filter_visualization}.
-While it is usually difficult to interpret the shape of the filters in the context of the type of data, we can notice that they often have a ``peak'' like structures.
+While it is usually difficult to interpret the shape of the filters, especially given the type of data, we can notice that they often have a ``peak'' like structure.
 An example of filter interpretation was demonstrated in \citep{Ribli2018learningfrom}.
-% \todo{Tomek: can you say something about the filters.}
-% \TK{Done}
-% Nati: Note that filer are almost not evolving during the training process.
+% Nati: Note that filter are almost not evolving during the training process.
 It is not surprising as our architecture is likely to be overparametrized.
 If we want to have interpretable filters, we probably have to use a much smaller architecture.
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.47\linewidth]{section_filter_last}
-	\hfill
-	\includegraphics[width=0.45\linewidth]{gnonomic_filter_last}
-	\caption{24 learned filters selected from the fifth spherical convolutional layer $L_5$. Left: section. Right: gnonomic view.}
-	\label{fig:learned_filter}
-\end{figure*}
-
-% \section{Discussion}
-
-% Because of the spherical domain, the method presented here restricts the shape of the filters learned by the network to be radial.
-% While this may be a less general design compared to the one used by conventional CNNs on flat images, we found it to still work efficiently for our test cases.
-% The layered structure of the network can partially compensate for that.
-% Further generalizations to non-radial filters may be possible [cite?]\TK{update here}, but we leave it to future work.
-
-% \nati{Should the discussion be merged with the result section?}
-% \TK{I think yes!}
 

### 2018-08-28 scnn.tex
use 'very' less often

@@
 % TBD if we include it
-% This approach is very efficient computationally than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
-An advantage of this representation is that the convolution operations with this approach are very efficient, which enables the algorithm to run very fast.
+% This approach is computationally more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
+An advantage of this representation is that the convolution operations with this approach are efficient, which enables the algorithm to run fast.
 We demonstrate the method on a classification problem of mass maps from two cosmological models and compare the performance of the CNN with that of two baseline classifiers, based on the power spectrum and pixel density histogram.
@@
 \citep{schmelze2017cosmologicalmodel,luciesmith2018machinelearning,gupta2018nongaussianinformation,gillet2018deeplearning,hassan2018reionizationmodels,aragoncalvo2018classyfyinglarge,ciuca2017cnnstring,ravanbakhsh2017estimating}.
-This is possible as CNNs have the capacity to build very rich models and capture complicated, non-linear patterns, which are often present in the data.
+This is possible as CNNs have the capacity to build rich models and capture complicated, non-linear patterns, which are often present in the data.
 
@@
 The parameters $\Omega_m$ and $\sigma_8$ were chosen to have the same spherical harmonic power spectrum for $\ell<1000$.
-That means that it is very difficult to distinguish between these cosmological models using these maps if this range of scales is used.
+That means that it is difficult to distinguish between these cosmological models using these maps if this range of scales is used.
 We found that the differences in power spectrum is $~5\%$ for $\ell>1000$.
@@
 We demonstrate that the neural network systematically and significantly outperforms our benchmark methods on an example problem of cosmological model discrimination with weak lensing mass maps, designed similarly to \citep{schmelze2017cosmologicalmodel}.
-The maps were produced from two cosmological models with varying $\sigma_8$ and $\Omega_m$, chosen to follow the typical weak lensing degeneracy in these parameters, so that the power spectra for these models are very similar.
+The maps were produced from two cosmological models with varying $\sigma_8$ and $\Omega_m$, chosen to follow the typical weak lensing degeneracy in these parameters, so that the power spectra for these models are similar.
 We compared the performance of the HealpixNet CNN versus that of two SVM-based classifiers: one trained on the spherical harmonics power spectrum, and the other on the pixel density histogram.

### 2018-08-28 scnn.tex
nside
no hyperlink draft
todo

@@
 \usepackage{url}
-% \usepackage{hyperref}
-\usepackage[draft]{hyperref}
+\usepackage{hyperref}
 \usepackage{graphicx,array} \graphicspath{{figures/}}
@@
 \usepackage{enumitem} % to remove when done with todo list
- % to remove when done with todo list
 
@@
     \item (MD) distinction between CNN and FCN
-    \item (MD) check paragraph on our chosen architecture in the Experiments sections
+	\item (TK) Can we use HEALPix in the name? Check with the main author of HEALPix. MD: what about DeepCosmo or CosmoNet? NP: cosmological data is not necessarily spherical.
+	\item (TK) Check use of British vs American English. Check use of tense.
+	\item (MD) remove statistical layer
+	\item (MD) distinction between CNN and FCN => Variants subsection
     \item (MD) check vertex interpretation in Efficient convolutions. Powers of L are weights of paths.
@@
     \item (Probably OK) Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
-    \item (Should be done) Check names: we use HealpixNet, HealpixNet (CNN variant), HealpixNet (FCN variant)
     \item (I think it is OK) (NP) Check the wording.
@@
     \item (done!) (TK) Example applications for dense prediction (classification and regression) for cosmology (color text in 2.8)
-
+	\item (done!) (MD) check paragraph on our chosen architecture in the Experiments sections
 \end{itemize}
@@
 and (right) simulated weak lensing convergence map (dimensionless) simulated with DES DR1 mask \citep{des2018dr1}.
-These maps were pixelised using \texttt{nside}=512.
+These maps were pixelised using $N_{side} = 512$.
 The CMB and weak lensing mass maps were smoothed with Gaussian kernels with FWHM=1 deg, and the galaxy count map with FWHM=0.5 deg.

### 2018-08-28 scnn.tex
crop figures

@@
     % \includegraphics[width=\linewidth]{architecture}
-	\includegraphics[width=\linewidth]{figure_architecture_v3.pdf}
+	\includegraphics[width=\linewidth]{figure_architecture_v3}
 	\caption{Overall network architecture, showing here two convolutional layers acting as feature extractors followed by a fully connected layer with softmax acting as the classifier.
@@
 
-\begin{figure*}
-\includegraphics[width=\linewidth]{figures/figure_example_maps.pdf}
-\caption{Exmaple maps on the sphere:
+\begin{figure}
+\includegraphics[width=\linewidth]{figure_example_maps}
+\caption{Example maps on the sphere:
 (left) the CMB temperature (K) map from Planck \citep{planck2015overview}, with galactic plane masked,
@@
 \label{fig:example_maps}
-\end{figure*}
+\end{figure}
 
@@
     % \includegraphics[width=\linewidth]{pooling}
-	\includegraphics[trim=1.1cm 0cm 0cm 0cm, width=\linewidth]{figures/figure_pooling_svg.pdf}
+	\includegraphics[width=\linewidth]{figure_pooling_svg}
 	\caption{Two levels of coarsening and pooling: groups of 4 cells are merged into one, then the data on them is summarized in one. The coarsest cell covers $1/12$ of the sphere.}
@@
 	% trim=left bottom right top
-	\includegraphics[trim=1cm 0cm 0cm 0cm, width=0.49\linewidth]{figure_kappa_diff_model1.pdf}
+	\includegraphics[width=0.48\linewidth]{figure_kappa_diff_model1}
 	\hfill
 	% \includegraphics[width=0.75\linewidth]{smooth_map_class_2}
-	\includegraphics[trim=0cm 0cm 1cm 0cm, width=0.49\linewidth]{figure_kappa_diff_model2.pdf}
+	\includegraphics[width=0.48\linewidth]{figure_kappa_diff_model2}
 	\caption{Example maps from two classes to be discriminated. Left: model 1 with $\Omega_m=0.31$ and $\sigma_8=0.82$. Right: model 2 with $\Omega_m=0.26$ and $\sigma_8=0.91$.

### 2018-08-30 scnn.tex
network architectures

@@
 \usepackage{aasmacros}
+\usepackage{booktabs}
 \usepackage{enumitem} % to remove when done with todo list
@@
 
-\subsection{Graph convolutional neural network}
-\label{sec:architecture}
+\subsection{Layers}
 
@@
 
-Given a map $\X \in \R^{N_{pix} \times F_{in}}$, a neural network for global prediction is computing $\y = NN_\theta(\X) \in R^{F_{out}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
-Two example networks for global classification, a CNN and a FCN, are
-\begin{align*}
-	NN &= SM \circ FC \circ \sigma \circ FC \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC, \\
-	NN &= \underbrace{SM \circ ST \circ \sigma \circ GC}_{\text{classifier}} \circ \underbrace{\sigma \circ GC \circ P \circ \sigma \circ BN \circ GC}_{\text{feature extractor}},
-\end{align*}
-where $\circ$ denotes composition, i.e., $(f \circ g)(x) = f(g(x))$.
-The number of features $F_{in}$ depends on the data at hand.
+\subsection{Network architectures}
+\label{sec:architecture}
+
+Given a map $\X \in \R^{N_{pix} \times F_{in}}$, a neural network computes $NN_\theta(\X)$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
+The number of input features $F_{in}$ depends on the data.
 For the CMB radiation temperature, $F_{in} = 1$.
@@
 $F_{in}$ might also be the number of slices in the radial direction.
-The number of predictions $F_{out}$ is either equal to the number of classes $N_{classes}$ for a classification task, or the number of variables to be predicted for a regression task.
+
+\begin{table}
+	\centering
+	\begin{tabular}{@{ } l r@{ $\in$ }l @{\hspace{0.8em}} r@{ $\in$ }l @{ }}
+		\toprule
+		 & \multicolumn{2}{c}{Classification} & \multicolumn{2}{c}{Regression} \\
+		%\midrule
+		Global & $NN_\theta(\X)$ & $\R^{N_{classes}}$ & $NN_\theta(\X)$ & $\R^{F_{out}}$ \\
+		Dense & $NN_\theta(\X)$ & $\R^{N_{pix} \times N_{classes}}$ & $NN_\theta(\X)$ & $\R^{N_{pix} \times F_{out}}$ \\
+		\bottomrule
+	\end{tabular}
+	\caption{The output's size of the neural network $NN_\theta(\X)$ depends on the task to be solved.
+$N_{pix}$ is the number of pixels in a HEALPix map, $N_{classes}$ is the number of classes in a classification task, and $F_{out}$ is the number of variables to be predicted in a regression task.
+The output size of a global task does not depend on the input size, whereas a dense task asks for one prediction per pixel.
+A classification task asks for discrete (or probabilistic) predictions, whereas a regression task asks for continuous variables.}
+	\label{tab:tasks}
+\end{table}
+
+HealpixNet can perform dense or global predictions, for regression or classification.
 A typical global classification task is to classify maps into cosmological model classes \citep{schmelze2017cosmologicalmodel}.
 A typical global regression task is to infer the parameters of a cosmological model  from maps \citep{fluri2018deep,gupta2018nongaussianinformation}.
-Dense prediction, i.e., predicting $F_{out}$ values per pixel, is obtained by omitting ST and FC layers (P layers, if used, have to be inverted via up-sampling in an encoder-decoder architecture).
-An example network for dense regression is
-\begin{equation*}
-	\Y = NN(\X) = (GC \circ \sigma \circ BN \circ GC)(\X) \in \R^{N_{pix} \times F_{out}}.
-\end{equation*}
-Such networks can be useful for
-(i) dense regression, such as denoising, interpolating missing values, or inpainting a parts of a map \citep{Inoue2008inpainting}, or
-(ii) dense classification, such as segmentation or feature detection \citep{Amsel2007detecting}.
-We emphasize that the use of FC and ST layers is the sole difference between a neural network engineered for global or dense prediction.
+Some dense regression tasks are denoising, interpolation of missing values, or inpainting parts of a map \citep{Inoue2008inpainting}.
+Segmentation and feature detection \citep{Amsel2007detecting} are examples of dense classification tasks.
+The output's size of the neural network depends on the task. See \tabref{tasks}.
+
+% FCN for dense
+
+Fully convolutional networks (FCNs) have been introduced by  \citep{long2015fcn} and are mostly used for the semantic segmentation of images, a dense classification task.
+An example FCN for dense regression is
+\begin{equation*}
+	\Y = NN_\theta(\X) = (GC \circ \sigma \circ BN \circ GC)(\X) \in \R^{N_{pix} \times F_{out}},
+\end{equation*}
+where $\circ$ denotes composition, i.e., $(f \circ g)(\cdot) = f(g(\cdot))$.
+If P layers are used, they have to be inverted via up-sampling in an encoder-decoder architecture.
+
+The set of input pixels which influence the value of an output pixel forms a \textit{receptive field}.
+That field is isotropic and local, i.e., it forms a disk centered around the output pixel.
+Its radius is influenced by the polynomial order $K$ of GC layers (setting how far the convolution operation looks around), and the down-sampling factor of P layers if any.
+Its radius should be large enough to capture statistics of interest.
+For example, there is a limit on how small a partial sky observation can be to give any clue about cosmological parameters.
+On the other hand, looking at the whole sky is often superfluous and waste computations, as most interactions are local.
+% most data generating processes have a small-support autocorrelation function.
+A data and task dependent trade-off is to be found.
+Note here that while global predictions use, by definition, the whole sky, dense predictions are not necessarily local.
+
+By treating each output pixel independently and in parallel, this architecture is a principled way to perform rotation equivariant operations.
+Rotation equivariance means that the rotation operation commutes with the neural network, i.e., if the input is rotated, the output is rotated the same way.\footnote{Small errors will however appear as GC layers are not exactly equivariant due to the small discrepancy between the graph Fourier modes and the spherical harmonics.
+See \ref{sec:comparison_spherical_harmonics}.}
+
+% FCN for global
+
+Global tasks can be solved by averaging dense predictions \citep{lin2013globalavgpooling, springenberg2014allconv}.
+Global averaging is computed by the layer $AV: \R^{N_{pix} \times F} \rightarrow \R^F$.
+% good performance was demonstrated for object recognition in images \citep{springenberg2014allconv}.
+Doing so assumes the data is locally independent, and form different observations of an unknown process.
+Averaging over independent observations is a common trick to reduce variance.\footnote{The variance of the averaged prediction is $\sigma^2 / n$, where $\sigma$ is the variance over one observation and $n$ is the number of independent observations.}
+An example FCN for global regression is
+\begin{equation*}
+	NN = AV \circ GC \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC.
+\end{equation*}
+Here, the FCN predicts parameters for many overlapping parts of the sky in parallel, then average those predictions to get one set of parameters for the whole sky.
+Global predictions are made invariant to rotation on the SO(3) group by averaging dense equivariant predictions.
+Rotation invariance means that rotating the input does not impact the prediction.
+
+% CNN for global
+
+By replacing the average by a FC layer, one gets the standard convolutional neural network (CNN), which is a generalization of the FCN.
+Indeed, the AV layer is a FC layer where all the entries of $\W$ in \eqnref{fc_layer} are equal to $1/N_{pix}$ and $\b b = \b 0$.
+By dropping rotation invariance, CNNs learn where to put attention on the domain. 
+That is useful when pixels are not of the same importance, with respect to the task.
+For example, on images, the subject of interest is most often around the center of the picture.
+Hence, those pixels are more predictive than the ones in the periphery when considering image classification.
+On the sphere, location is important when analyzing weather data on the Earth for example, as oceans and mountains play different roles.
+An example of such an architecture is
+\begin{equation*}
+	NN = FC \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC.
+\end{equation*}
+
+For tasks that are rotation invariant, FCNs need less training data as the rotation symmetry is backed in the architecture and need not be learned.
+Than can be seen as intrinsic data augmentation, as a CNN would need to see many rotated versions of the same data to learn the invariance.
+% Contrast the number of parameters to be learned in a FC layer versus the static AV layer.
+% FCNs are more sample efficient.
+Moreover, FCNs can accommodate maps with a varying number of pixels.
+As such, CNNs should only be used if rotation invariance is undesired.
+
+% classification
+
+All the above architectures can be used for classification (instead of regression) by appending a SM layer.
+An example FCN for global classification is therefore
+\begin{equation*}
+	NN = SM \circ AV \circ GC \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC.
+\end{equation*}
+Similarly, we emphasize that the use of FC and AV layers is the sole difference between a neural network engineered for global or dense prediction.
+
+%\subsection{Learning}
+\subsection{Training}
+%\subsection{Optimization}
 
@@
 
-As discussed in \secref{variants}, the choice of an HealpixNet variant depends on the data and task at hand.
+As discussed in \secref{architecture}, the choice of a network architecture depends on the data and task at hand.
 For our problem, where we assume that each pixel carries the same quantity of information about the cosmological model, a rotation invariant FCN architecture should be best.
@@
 \end{center}
-where $GC_k$ indicates a graph convolutional layer with $k$ output feature maps, $P_4$ is a pooling layer which divides the number of pixels by 4, $\sigma$ is a ReLU, and the Chebyshev polynomials are of degree $K=5$.
-
-For comparison, we tried the more conventional CNN variant, where the classification is performed by a fully connected layer from the last feature maps instead of the average of local classifications.
+where $GC_F$ indicates a graph convolutional layer with $F$ output feature maps, $P_4$ is a pooling layer that divides the number of pixels by 4, $\sigma$ is a ReLU, and the Chebyshev polynomials in \eqnref{graph_convolution_cheby} are of degree $K=5$.
+The layers $L_1$ to $L_5$ build the statistical evidence to classify each pixel of a down-sampled sphere.
+The last GC layer acts as a linear classifier and outputs two (non-normalized) predictions.
+The AV layer averages these predictions.
+Probabilities are computed by the SM layer.
+
+For comparison, we tried the more conventional CNN architecture, where the classification is performed by a fully connected layer from the last feature maps instead of the average of local classifications.
 This architecture is not invariant to rotation.
-The network is defined as
-\begin{equation*}
-	CNN = SM \circ FC_2 \circ L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1,
-\end{equation*}
-where $FC_2$ denotes a fully connected layer with two output neurons.
-Architectures were chosen over their performance on the validation set.
+The selected network is defined as
+\begin{equation*}
+	CNN = \underbrace{SM \circ FC_2}_{\text{classifier}} \circ \underbrace{L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1}_{\text{feature extractor}},
+\end{equation*}
+where $FC_2$ denotes a fully connected layer with two outputs.
+Architectures were selected over their performance on the validation set.
 
@@
 
-We also observe that the FCN variant slightly outperforms the CNN.
-This may seem counterintuitive as the CNN is a generalization of the FCN and hence should provide, at least, equivalently good results.
-Nevertheless, one should not forget that in practice the complexity of the architecture trades with more data requirements and more training difficulties.
-Two interpretations explain why the FCN variant leads to better performance. First, the FCN is almost invariant to rotation on the SO(3) group and hence intrinsically augments the dataset.
-The convergence mass map dataset is invariant to rotation as the mass distribution is homogeneous and isotropic.
-Second, the FCN can be interpreted as a voting procedure where (i) each pixel is being classified using the data in its surroundings, and (ii) the average score is computed to determine the class.
-This procedure suits the data as we believe that each class of the dataset is stationary with a small-support radial autocorrelation function, again stemming from the homogeneity of the dataset.
-It implies that a pixel can be statistically classified using only its surroundings.
-The CNN variant may however be better for data not having this property, and one should always adapt the architecture to the data and task.
+As expected, we observe that the FCN slightly outperforms the CNN.
+This may seem counterintuitive as the CNN is a generalization of the FCN and hence should be able to learn the same function and provide at least equivalently good results.
+Nevertheless, as discussed in \secref{architecture}, the larger number of parameters incurred by the increased flexibility requires more training data to learn the rotation symmetry.
+The superior performance of the FCN is an empirical validation that these maps are stationary with a small-support radial autocorrelation function, stemming from the fact that the mass distribution is homogeneous and isotropic.
+It also implies that this classification problem is invariant to rotation.
+Hence, a pixel can be statistically classified using only its surrounding, and those local predictions can be averaged to vote for a global consensus.
+The CNN variant may however be better for data not having this property, and one should always adapt the architecture to the data and task (see \secref{architecture}).
 

### 2018-08-30 scnn.tex
full sky => whole sky

@@
 
-We make full sky N-body simulations for two parameter sets of the $\Lambda\rm{CDM}$ cosmological model: model 1 ($\Omega_m=0.31, \sigma_8=0.82$) and model 2 ($\Omega_m=0.26, \sigma_8=0.91$), where $\Omega_m$ is the matter density in the universe and $\sigma_8$ is the normalisation of the matter power spectrum.
+We make whole sky N-body simulations for two parameter sets of the $\Lambda\rm{CDM}$ cosmological model: model 1 ($\Omega_m=0.31, \sigma_8=0.82$) and model 2 ($\Omega_m=0.26, \sigma_8=0.91$), where $\Omega_m$ is the matter density in the universe and $\sigma_8$ is the normalisation of the matter power spectrum.
 Other parameters are set to: Hubble constant $H_0=70 km/s/Mpc$, spectral index $n_s=0.96$, and Baryon density today $\Omega_b=0.05$.
@@
 Out of the $60$ simulations, $20$ are kept as the test set, and $20\%$ of the remaining training data is used as a validation set, to monitor the training process and select the hyper-parameters.
-\figref{map_sample} shows the full sky simulations and a zoom region for both models.
+\figref{map_sample} shows the whole sky simulations and a zoom region for both models.
 Initial conditions for these simulations are the same, so the differences in structures can only be attributed to different cosmological parameters used to evolve the particle distribution.
@@
 As the distribution of matter in the universe is homogeneous and isotropic, no pixel is more informative than any other.\footnote{Contrast that with images, where the subject of interest is most often around the center of the picture.}
-As such, we can control the difficulty of the classification problem by limiting the number of pixels available to the algorithms, i.e., extracting partial maps from full sky maps.
+As such, we can control the difficulty of the classification problem by limiting the number of pixels available to the algorithms, i.e., extracting partial maps from whole sky maps.
 Using the properties of HEALPix, we split maps into $12 \times o^2$ ($o=1,2,4,\dots$) independent samples of $(N_{pix} / o)^2$ pixels.

### 2018-08-30 scnn.tex
small edits to experiments

@@
 For our problem, where we assume that each pixel carries the same quantity of information about the cosmological model, a rotation invariant FCN architecture should be best.
-The chosen network is defined as
-\begin{equation*}
-	FCN = SM \circ ST_{\text{mean}} \circ GC_2 \circ L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1,
+The selected network is defined as
+\begin{equation*}
+	FCN = \underbrace{SM \circ AV \circ GC_2}_{\text{classifier}} \circ \underbrace{L_5 \circ L_4 \circ L_3 \circ L_2 \circ L_1}_{\text{feature extractor}},
 \end{equation*}
@@
 
+In all our experiments, we saw no sign of over-fitting.
+With more data, HealpixNet can probably do even better.
+The fact that the CNN lags behind the FCN is another sign of lack of data.
+
 While testing the FCN and CNN variants, we made the following empirical observations.
-First, training was more stable (in the sense that the loss had a more monotone decrease) when using Chebyshev polynomials, as in \eqnref{graph_convolution_cheby}, rather than monomials, as in \eqnref{graph_convolution_monomial}.
+First, training was more stable (in the sense that the loss decreased more smoothly) when using Chebyshev polynomials, as in \eqnref{graph_convolution_cheby}, rather than monomials, as in \eqnref{graph_convolution_monomial}.
 Nevertheless, we could not observe a significant difference in accuracy after convergence.
@@
 	\includegraphics[width=\linewidth]{gnonomic_filter_last}
-	\caption{Random selection of 24 learned filters from the fifth spherical convolutional layer $L_5$. Top: section. Bottom: gnomonic view.}
+	\caption{Random selection of 24 learned filters from the fifth spherical convolutional layer $L_5$. Top: section. Bottom: gnomonic projection.}
 	\label{fig:learned_filter}
@@
 Since our construction leads to almost (up to sampling irregularities) spherical filters, we plot in \figref{learned_filter} both the radial profile and a gnomonic projection on a plane of a random selection of learned filters from the last layer of the network.
-While those particular filters were obtained from the experiment with order $o=2$ and a relative noise level of $2$, all trained networks presented visually similar gnomonic and profile patterns.
+While those particular filters were obtained from the experiment with order $o=2$ and a relative noise level of $2$, all trained networks presented visually similar patterns.
 % The gnomonic projection clearly exhibits the sampling issue of HEALPix.

### 2018-08-30 scnn.tex
would like to thank => thank

@@
 This work was supported by a grant from the Swiss Data Science Centre (SDCS) under project ID \textit{sd01 - DLOC:  Deep Learning for Observational Cosmology} and grant number 200021\_169130 from the Swiss National Science Foundation.
-We would like to thank Jean-François Cardoso for helpful discussions about the spherical harmonics.
-We would like to thank Alexandre Refregier, Adam Amara, Thomas Hofmann and Fernando Perez-Cruz for advice and helpful discussions.
+We thank Jean-François Cardoso for helpful discussions about the spherical harmonics.
+We thank Alexandre Refregier, Adam Amara, Thomas Hofmann and Fernando Perez-Cruz for advice and helpful discussions.
 We thank Hamsa Padmanabhan for testing use cases of the code.

### 2018-08-31 scnn.tex
remove statistical layer

@@
 
-\subsection{Statistical layer}
-\label{sec:stat_layer}
+% The statistical layer was used in the end. The FCN is a more principled approach.
+
+% \subsection{Statistical layer}
 % Or Global pooling?
 
-Following \citep{khasanova2017tigranet}, we implement an optional statistical layer between the last graph convolutional layer and the first fully connected layer for the neural network.
-This introduces the invariance of the output to isometric transformations, such as rotation of maps on the sphere.
-The role of the layer is to compute global and location independent statistics from feature maps.
-Besides providing invariance, the layer drastically compresses the representation of the data as the number of computed statistics $N_{stat}$ is usually much smaller than the size of the map $N_{pix}$.
+% Following \citep{khasanova2017tigranet}, we implement an optional statistical layer between the last graph convolutional layer and the first fully connected layer for the neural network.
+% This introduces the invariance of the output to isometric transformations, such as rotation of maps on the sphere.
+% The role of the layer is to compute global and location independent statistics from feature maps.
+% Besides providing invariance, the layer drastically compresses the representation of the data as the number of computed statistics $N_{stat}$ is usually much smaller than the size of the map $N_{pix}$.
 That compression results in much smaller fully connected layers, which usually contain a significant fraction of trainable parameters of a neural network.
-The invariance and reduced representation should help the network to learn from fewer samples and to generalize better to unseen data.
+% The invariance and reduced representation should help the network to learn from fewer samples and to generalize better to unseen data.
 Yet another advantage is that a network built with such a statistical layer is agnostic to the size of the input data, i.e., it can classify maps which do not have the same number of pixels.
 Indeed, such global summarization is invariant to node permutation and is commonly used along graph convolutions to classify graphs of varying sizes \citep{duvenaud2015gcn, li2015gatedgnn}.
-
-Given a feature map $\x \in \R^{N_{pix}}$, the statistical layer is defined as
-\begin{equation} \label{eqn:stat_layer}
-	\y = f(\x) \in \R^{N_{stat}},
-\end{equation}
-where $f$ computes $N_{stat}$ statistics which are independent from the size of the map, $N_{pix}$.
+%
+% Given a feature map $\x \in \R^{N_{pix}}$, the statistical layer is defined as
+% \begin{equation} \label{eqn:stat_layer}
+% 	\y = f(\x) \in \R^{N_{stat}},
+% \end{equation}
+% where $f$ computes $N_{stat}$ statistics which are independent from the size of the map, $N_{pix}$.
 An example is the global average pooling $f(\x) = \esp(\x)$, introduced by \citep{lin2013globalavgpooling}, where $\esp(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} x_i$ is the empirical mean.
 Another example is $f(\x) = [\esp(\x), \var(\x)]\trans$, where $\var(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} (x_i - \esp(\x))^2$ is the empirical variance.
-Other statistical layers are also possible.
-In particular, we also implement a \emph{learned histogram} statistic \citep{wang2016learnhist}.
-Other approaches, which we did not implement, may include applying different diffusion on the final maps to obtain statistics at different scales, as proposed by \citep{khasanova2017tigranet}.
+% Other statistical layers are also possible.
+% In particular, we also implement a \emph{learned histogram} statistic \citep{wang2016learnhist}.
+% Other approaches, which we did not implement, may include applying different diffusion on the final maps to obtain statistics at different scales, as proposed by \citep{khasanova2017tigranet}.
 
@@
 
-Neural networks are constructed as stacks of layers which sequentially transform the data from its raw representation to a decision on the class label.
-Our architecture, pictured in \figref{architecture}, is composed of many layers.
+Neural networks are constructed as stacks of layers which sequentially transform the data from its raw representation to some predictions.
+% decision on the class label
+The general HealpixNet architecture, pictured in \figref{architecture}, is composed of many layers.
 The convolutional part, the head of the neural network, is composed of graph convolutional layers (GC), pooling layers (P), and batch normalization layers (BN).
-The tail is composed of multiple fully connected layers (FC) followed by a softmax layer (SM).
-A statistical layer (ST) is optionally inserted between the convolutional head and the fully connected tail.
+The tail is composed of multiple fully connected layers (FC) followed by an optional softmax layer (SM).
+% A statistical layer (ST) is optionally inserted between the convolutional head and the fully connected tail.
 
@@
 
-The statistical layer, defined in \eqnref{stat_layer}, independently transforms each of the $F$ feature maps of the input $\X \in \R^{N_{pix} \times F}$ into $\Y = ST(\X) \in \R^{N_{stat} \times F}$, where $N_{stat}$ is the number of statistics.
+% The statistical layer, defined in \eqnref{stat_layer}, independently transforms each of the $F$ feature maps of the input $\X \in \R^{N_{pix} \times F}$ into $\Y = ST(\X) \in \R^{N_{stat} \times F}$, where $N_{stat}$ is the number of statistics.
 One may even omit the FC layers and directly fed the output of the ST layer into the softmax layer, as proposed by \citep{lin2013globalavgpooling}.
@@
 Moreover, FCNs can accommodate maps with a varying number of pixels.
+% agnostic to the size of the input data, i.e., it can classify maps which do not have the same number of pixels.
+Such global summarization as the AV layer is commonly used along graph convolutions to classify graphs of varying sizes (as it is invariant to node permutation) \citep{duvenaud2015gcn, li2015gatedgnn}.
 As such, CNNs should only be used if rotation invariance is undesired.
@@
 Third, they introduced a statistical layer --- an operation that computes a set of statistics from the last feature maps --- to provide full rotation invariance.
-We propose to use the idea of fully convolutional networks (FCNs) instead (see \secref{selected_architecture}).
+We propose to use the idea of fully convolutional networks (FCNs) instead (see \secref{architecture}).
 While statistics have to be hand-chosen to capture relevant information for the task, the filters in a FCN are trained end-to-end to capture relevant information.
@@
 %\subsection{Methods} % baselines and HealpixNet together
-\label{sec:selected_architecture}
 

### 2018-08-31 scnn.tex
small edit
size comparison with imagenet

@@
 
-A FC layer takes as input $\x \in \R^{F_{in}}$ and outputs
-\begin{equation*}
-	\y = FC(\x) = \b W \x + \b b \in \R^{F_{out}} ,
-\end{equation*}
+The layer $FC: \R^{F_{in}} \rightarrow \R^{F_{out}}$ is defined as
+\begin{equation} \label{eqn:fc_layer}
+	\y = FC(\x) = \b W \x + \b b ,
+\end{equation}
 where $\W \in \R^{F_{out} \times F_{in}}$ and $\b b \in \R^{F_{out}}$ are the parameters to be learned.
@@
 
-In all our experiments, we saw no sign of over-fitting.
+We saw no sign of over-fitting in any of our experiments.
 With more data, HealpixNet can probably do even better.
 The fact that the CNN lags behind the FCN is another sign of lack of data.
+ImageNet, the largest dataset for visual object recognition, features about 900 billion pixels ($14 \times 10^6 \times 256^2$), to be compared with the 750 millions pixels ($60 \times 12 \times 1024^2$) of our dataset.
 

### 2018-08-31 scnn.tex
update todo

@@
 \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-    \item (MD) distinction between CNN and FCN
 	\item (TK) Can we use HEALPix in the name? Check with the main author of HEALPix. MD: what about DeepCosmo or CosmoNet? NP: cosmological data is not necessarily spherical.
 	\item (TK) Check use of British vs American English. Check use of tense.
-	\item (MD) remove statistical layer
-	\item (MD) distinction between CNN and FCN => Variants subsection
-    \item (MD) check vertex interpretation in Efficient convolutions. Powers of L are weights of paths.
+	\item (TK) Larger text on figure 2. I (MD) made it one column wide instead of two as it's more an illustration than a central figure to our exposition.
+    \item (MD) check vertex interpretation in Efficient convolutions. Powers of L are weights of paths. We deal with neighborhoods rather than individual nodes.
+	\item (MD) Figure 4: speed for multiple lmax.
     \item (TK) check part sphere notebook and whole sphere
@@
     \item Check links in footnotes.
-    \item (done!) (NP) Change equation after (2) and check all kroneker
-    \item (done!) (TK) check text figure 1
-    \item (done!) (TK) Related work in cosmo.
-The only cosmological applications of spherical CNNs in the related work are about projection on the tangent plane \citep{schmelze2017cosmologicalmodel, fluri2018deep, gupta2018nongaussianinformation}.
-Aren't there applications in cosmology for the other (c.f.
-related work section) approaches?
-Most of them are illustrated in omnidirectional imagery.
-If none, say it and mention some alternatives, e.g., wavelets?
-    \item (done!) (TK) check if papers which appear as arxiv were not published in a conference or journal
-    \item (done!) (TK) read everything
 	\item (fail - I checked few fonts here: \url{de.sharelatex.com/learn/Font_typefaces}, but none looked better) (TK) Font: do we have to use times (set in the documentclass)?
 I (MD) find the rendering of math a bit ugly.
-    \item (done!) (TK) fix the bibliography
-    \item (done!) (TK) add small description of maps\_downsampled\_64.npz in the whole\_sphere notebook. \nati{We need to talk about that.}
-    \item (done!) (TK) Example applications for dense prediction (classification and regression) for cosmology (color text in 2.8)
-	\item (done!) (MD) check paragraph on our chosen architecture in the Experiments sections
+MD: lmodern is better, but can we use it (w.r.t.\ journal policy)?
+If equations split out, we can try to arrange them.
+We should also check which font size we can / have to use.
 \end{itemize}

### 2018-08-31 scnn.tex
an HEALPix => a HEALPix

@@
 Middle: an equiangular cubed-sphere grid, as described in \citep{ronchi1996cubed}.
-Right: graph built from an HEALPix pixelization of half the sphere ($N_{side} = 4$).
+Right: graph built from a HEALPix pixelization of half the sphere ($N_{side} = 4$).
 By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[7] Left and middle figures are taken from \citep{boomsma2017spherical}.}
@@
 The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters.
-The classification methods were trained to predict a label from an HEALPix map.
+The classification methods were trained to predict a label from a HEALPix map.
 Both our Python implementation\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are openly available online.

### 2018-08-31 scnn.tex
a pass on the related work

@@
 By treating each output pixel independently and in parallel, this architecture is a principled way to perform rotation equivariant operations.
-Rotation equivariance means that the rotation operation commutes with the neural network, i.e., if the input is rotated, the output is rotated the same way.\footnote{Small errors will however appear as GC layers are not exactly equivariant due to the small discrepancy between the graph Fourier modes and the spherical harmonics.
+Rotation equivariance means that the rotation operation commutes with the neural network, i.e., a rotation of the input implies the same rotation of the output.\footnote{Small errors will however appear as GC layers are not exactly equivariant due to the small discrepancy between the graph Fourier modes and the spherical harmonics.
 See \ref{sec:comparison_spherical_harmonics}.}
@@
 Right: graph built from a HEALPix pixelization of half the sphere ($N_{side} = 4$).
-By construction, each node has 8 neighbors, except the highlighted ones which have only 7.\footnotemark[7] Left and middle figures are taken from \citep{boomsma2017spherical}.}
+By construction, each node has eight neighbors, except the highlighted ones which have only seven.\footnotemark[4] Left and middle figures are taken from \citep{boomsma2017spherical}.}
     \label{fig:sphere_grids}
@@
 That incurs some computational losses.
-For samplings that are not equal area, such as the equirectangular projection, the convolution operation can be adjusted to take the induced distortion into account \citep{su2017sphericalconv, coors2018spherenet}.
+For samplings that are not equal area, such as the equirectangular projection, the convolution operation should be adjusted to take the induced distortion into account \citep{su2017sphericalconv, coors2018spherenet}.
 % Furthermore, the grid requirement makes it impossible for the convolution to capture the spherical properties of the domain, i.e., the cubed-sphere sampling is by definition adapted to a cube and not to a sphere.
-Nope, the graph can adapt to any sampling.
+% MD: Nope, the graph can adapt to any sampling. And we're not arguing about sampling schemes.
 
@@
 Direction is well defined and matters for some applications, such as the analysis of weather and climate data on the Earth (north, south, east, west), and omnidirectional imaging (up, down).
-Indeed, full rotation invariance has been shown to reduce discriminative power for omnidirectional imaging \citep{coors2018spherenet}.
-Some problems are, however, intrinsically invariant to rotation, such as the analysis of cosmological maps, or the modeling of atoms and molecules.
+Indeed, rotation invariance has been shown to reduce discriminative power for omnidirectional imaging \citep{coors2018spherenet}.
+Some problems are, however, intrinsically invariant (or equivariant) to rotation.
+Examples include the analysis of cosmological maps, and the modeling of atoms and molecules.
 In such cases, directions are arbitrarily defined when setting the origin of the pixelization.
-A rotation equivariant convolution, i.e., a rotation of the input implies the same rotation in the output, thus has to be isotropic.
+Therefore, a convolution operation has to be isotropic to be equivariant to rotation.
 
@@
 
-The problem of rotation equivariance was addressed \citep{cohen2018sphericalcnn,esteves2017sphericalcnn} by leveraging the convolution associated to the 3D rotation group SO(3), with applications to atomization energy regression and 3D model classification, alignment and retrieval.
+Rotation equivariance was addressed by leveraging the convolution associated to the 3D rotation group SO(3), with applications to atomization energy regression and 3D model classification, alignment and retrieval \citep{cohen2018sphericalcnn,esteves2017sphericalcnn}.
 The resulting convolution is performed by (i) a spherical harmonic transform (SHT), i.e., a projection on the spherical harmonics, (ii) a  multiplication in the spectral domain, and (iii) an inverse SHT.
-Hence the computational cost of a convolution is dominated by the two SHTs.
-A naive implementation of the SHT costs $\bO(N_{pix}^2)$ operations, where $N_{pix}$ is the number of pixels.
 Note the similarity with the naive graph convolution defined in \eqnref{graph_convolution_fourier}.
-Accelerated schemes exist for some sampling sets \citep[see][for examples]{mohlenkamp1999fast, rokhlin2006fast, reinecke2013libsharp}.
-The main advantage of this approach is that it provides a mathematically well-defined rotation-equivariant network.
-Nevertheless, even with accelerated SHTs, the convolutions remain expensive, limiting the practical use of this approach.
-For example, with the HEALPix sampling, which was designed to have a fast SHT by being iso-latitude, the computational cost of the SHT is $\bO(N_{pix}^{3/2}) = \bO(N_{side}^3) = \bO(\ell_{max}^3)$, where $\ell_{max}$ is the largest angular frequency\footnote{All pixels are placed on $N_{ring} = 4N_{side}-1 = \bO\left(\sqrt{N_{pix}}\right)$ rings of constant latitude.
+Likewise, the computational cost of a convolution is dominated by the two SHTs, and a naive implementation of the SHT costs $\bO(N_{pix}^2)$ operations.
+Accelerated schemes however exist for some sampling sets \citep[see][for examples]{mohlenkamp1999fast, rokhlin2006fast, reinecke2013libsharp}.
+The convolutions remain nevertheless expensive, limiting the practical use of this approach.
+For example with HEALPix, which was designed to have a fast SHT by being iso-latitude, the computational cost of the SHT is $\bO(N_{pix}^{3/2}) = \bO(N_{side}^3) = \bO(\ell_{max}^3)$, where $\ell_{max}$ is the largest angular frequency \citep{gorski2005healpix, reinecke2013libsharp}.\footnote{All pixels are placed on $N_{ring} = 4N_{side}-1 = \bO\left(\sqrt{N_{pix}}\right)$ rings of constant latitude.
 Each ring has $\bO\left(\sqrt{N_{pix}}\right)$ pixels.
 Thanks to this iso-latitude property, the SHT is computed using recurrence relations for Legendre polynomials on co-latitude and fast Fourier transforms (FFTs) on longitude.
-The computational cost is thus $\sqrt{N_{pix}}$ FFTs for a total cost of $\bO\left( N_{pix} \log \sqrt{N_{pix}} \right)$, plus $\sqrt{N_{pix}}$ matrix multiplications of size $\sqrt{N_{pix}}$ for a total cost of $\bO\left(N_{pix}^{3/2}\right)$.}
-\citep{gorski2005healpix, reinecke2013libsharp}.
-In comparison, filtering with our HealpixNet method scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}).
-The Clebsh-Gordan transform was proposed \citep{kondor2018clebsch} to perform a non-linear transformation in the spectral domain.
-As such, a SHT only has to be performed once at the input of the network and the back and forth SHT between every layer is no longer required.
-While this clever trick makes the convolution complexity $\bO(N_{pix})$, the non-linearity scales, to the best of our understanding, as  $\bO(N_{pix}^{3/2})$.
-At the time of writing this paper, computation time is unfortunately not reported, hence making unclear which speed gain is obtained in practice.
-While the convolution in the spectral domain avoid all sampling problems, one of its downsides might the lack of natural locality, a property that is naturally obtained by the polynomial approach of graph convolution.
-Because the convolution is at the begging of the neural network, we believe that it should focus on local correlations first before exacting more complex structures.
-%\todo{Polynomial formulation enforces locality, which otherwise has to be enforced by smoothness in the spectral domain.}
-%\todo{Pooling in the spectral domain? \citep{esteves2017sphericalcnn} do something.}
+The computational cost is thus $\sqrt{N_{pix}}$ FFTs for a total cost of $\bO\left( N_{pix} \log \sqrt{N_{pix}} \right)$, plus $\sqrt{N_{pix}}$ matrix multiplications of size $\sqrt{N_{pix}}$ for a total cost of $\bO\left(N_{pix}^{3/2}\right)$ operations.}
+The Clebsh-Gordan transform can be used to perform the non-linear transformation in the spectral domain \citep{kondor2018clebsch}.
+As such, the SHT is only performed once on the input (no back and forth SHT between each layer).
+While this clever trick lowers the complexity of the convolution to $\bO(N_{pix})$, the non-linearity is $\bO(N_{pix}^{3/2})$.
+This work is another indication that there might be a $\bO(N_{pix}^{3/2})$ computational lower bound for the proper treatment of rotation equivariance with the spherical harmonics.
+In comparison, HealpixNet scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}), at the expense of not being exactly equivariant (see \ref{sec:comparison_spherical_harmonics}).
+Being a mathematically well-defined rotation equivariant network is the main advantage of methods based on spherical harmonics.
+See \citep{kondor2018equivariance} for a rigorous treatment of convolution and equivariance in neural networks.
+
+While defining the convolution in the spectral domain avoids all sampling issues, filters so defined are not naturally localized in the original domain.
+Localization is desired for the transformation to be stable to local deformation \citep{mallat2012scattering}, and most interactions in the data are local anyway.
+A straightforward way to impose locality in the original domain is to impose smoothness in the spectral domain, by Heisenberg's uncertainty principle.
+A more elegant approach is to define filters that are provably localized.
+The filters defined in \eqnref{graph_convolution_monomial} and \eqnref{graph_convolution_cheby}, by being polynomials of the Laplacian, are of this kind.
+% \todo{Pooling in the spectral domain? \citep{esteves2017sphericalcnn} do something.}
 % While a comparison is theoretically possible, the experiments of~\cite{cohen2018sphericalcnn} are done using the geodesic grid sampling set and do not provide any code for the HEALPix one.
@@
 All the above methods cannot be easily accelerated when the data lies on a part of the sphere only.
-That is an important use case in cosmology as measurements are often partial, i.e., full-sky maps are rare.
+That is an important use case in cosmology as measurements are often partial, i.e., whole sky maps are rare.
 One could still fill the unseen part of the sphere with zeros, and avoid computing empty integrals.
 % on the latitude or longitude for SHTs, on square holes for 2D CNNs
-It is, however, not straightforward to identify empty space, and computations would still be wasted; consider, for example, a ring which mostly contains zeros but a few measurements.
-With graphs, however, the computation is done only for the used pixels.
+It is, however, not straightforward to identify empty space, and computations would still be wasted.
+Consider, for example, a ring which mostly contains zeros but a few measurements.
+With graphs, however, computations are only performed for used pixels.
 While it results in some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}), these can be mitigated by padding with zeros a small area around the measurements.
 
-The use of a graph to model the discretised sphere was also considered by \citep{khasanova2017graphomni} for omnidirectional imaging.
+The use of a graph to model the discretised sphere was also considered for omnidirectional imaging \citep{khasanova2017graphomni}.
 % The authors map omnidirectional images onto a sphere, with the goal of correcting for distortions induced by the lens, which was used for their acquisition.
@@
 Second, they did not take advantage of a hierarchical pixelization of the sphere and resorted to dynamic pooling \citep{kalchbrenner2014dcnn}.
-While that operation is useful for sequences of varying length, such as sentences in language models, it could be impractical in our context, as it is not local and destroys spatial coherence.
-Third, they introduced a statistical layer --- an operation that computes a set of statistics from the last feature maps --- to provide full rotation invariance.
+While that operation has proved its worth to pool sequences of varying length, such as sentences in language models, it is undesired in our context as it is not local and destroys spatial coherence.
+Third, they introduced a statistical layer --- an operation that computes a set of statistics from the last feature maps --- to provide invariance to rotation.
 We propose to use the idea of fully convolutional networks (FCNs) instead (see \secref{architecture}).
 While statistics have to be hand-chosen to capture relevant information for the task, the filters in a FCN are trained end-to-end to capture relevant information.
-
-The connection has been made between graph CNNs and group equivariant CNNs by \citep{kondor2018equivariance}, justifying the use of graphs to gain rotation equivariance on the sphere.
-\todo{More here.}
 
@@
 
-We show that the modeling the discretised sphere by a graph enables an efficient convolution operation on HEALPix sampling.
+We show that modeling the discretised sphere by a graph enables an efficient convolution operation on HEALPix sampling.
 Graph-based representation of the sphere can display small imprecisions in rotation invariance, the result of which is that an action of a graph filter slightly depends on the location.
@@
 Third, counter-intuitively, some eigenvectors will be localized~\citep{perraudin2018global}, i.e, they will span a small part of the sphere.
+Those discrepancies result in a convolution operation that is not exactly equivariant to rotation.
 Nevertheless, our experiments suggest that these downsides do not have an important effect on the convolution nor hinder the performance of the neural network.

### 2018-09-03 scnn.tex
efficient convolutions: vertex interpretation & Cheby vs monomials

@@
 	\item (TK) Larger text on figure 2. I (MD) made it one column wide instead of two as it's more an illustration than a central figure to our exposition.
-    \item (MD) check vertex interpretation in Efficient convolutions. Powers of L are weights of paths. We deal with neighborhoods rather than individual nodes.
 	\item (MD) Figure 4: speed for multiple lmax.
@@
 While \eqnref{graph_convolution_fourier} is a theoretically well justified definition of the convolution of a graph signal $\f$ by a kernel $h$, it is computationally cumbersome.
-As no general Fast Fourier Transform (FFT) exist for graphs, the execution of the Fourier transform by multiplication of the signal $\f$ by the dense matrix $\U$ costs $\bO(N_{pix}^2)$ operations.
+As no efficient and general fast Fourier transform (FFT) exists for graphs \citep{le2018fgft}, the execution of the Fourier transform by multiplication of the signal $\f$ by the dense matrix $\U$ costs $\bO(N_{pix}^2)$ operations.
 % \footnote{See \citep{le2018fgft} for a comparison between the polynomial definition of filters presented here and a class of fast graph Fourier transforms based on the approximation of the Fourier basis $\U$ by a product of sparse matrices.}
-%\TK{I would just cite the paper, we have not introduced the polynomials at this stage yet.}
-In a CNN, this operation has to be performed for each training step: forward and backward.
-% As current training procedures are not data-efficient and require a lot of samples, a quadratic computational cost in the sample size is a .
-%\TK{what does "data-efficient mean"? removing for now}
+% TK: I would just cite the paper, we have not introduced the polynomials at this stage yet.
+In a neural network, this operation has to be performed for each forward and backward pass.
 As current training procedures require processing of many samples, it would be very slow to perform them for a quadratic computational cost in the sample size.
@@
 
-Fortunately, both of these computational issues can be overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parametrised by $K+1$ coefficients $\theta$.
-In that specific case, the filtering operation \eqnref{graph_convolution_fourier} becomes
+Fortunately, both of these computational issues are overcome by defining the convolution kernel $h$ as a polynomial $h_\theta(\lambda) = \sum_{k=0}^K \theta_k \lambda^k$ of degree $K$ parametrised by $K+1$ coefficients $\theta$.
+The filtering operation \eqnref{graph_convolution_fourier} becomes
 \begin{equation} \label{eqn:graph_convolution_monomial}
@@
 \end{equation}
-an operation requiring $k$ multiplications of the graph Laplacian matrix $\L$.
-In our case, the Laplacian is extremely sparse, with $8-9$ entries per line, making the filtering operation for a fixed $K$ linear in the number of pixel $N_{pix}$.
-% Moreover, here happens the transition from filtering in the spectral domain to filtering in the vertex domain.
-This operation is performed in the vertex domain.
-The matrix $\L^k$ captures $k$-neighborhoods of each pixel, i.e., $(\L^k)_{ij}$ is non-zero if and only if nodes $v_i$ and $v_j$ are connected by a path of length $k$.
-As such, filtering with a polynomial convolution kernel can be interpreted in the pixel (vertex) domain as a weighted linear combination of the pixels neighbors values.
-The weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$.
-We note that restricting the graph convolutional kernel to a polynomial is similar to restricting the classical Euclidean signal-domain convolution to a patch.
-In the classical setting, the convolution with a patch is simply a weighted sum of the neighbors with the weights defined by the patch.
-Similarly, each lines of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an "irregular patch of radius $K$" for our irregular domain.
-% \todo{Better vertex domain explanation.
-% \nati{I gave it a try. Should we take a single vertex and explain what heppens to it? Note that I suppressed the following paragraph. }}
-% \TK{For me it's understandable:)}
-
-% To make the parallel with classical Euclidean signal-domain convolution, i.e., filtering by multiplying the signal with translated versions of a patch, we here match our filter at the level of neighborhoods\footnote{The 1-neighborhood of a node is the set of nodes which are directly connected to it.
-The 2-neighborhood is the set of nodes which are connected through paths of length 2.} rather than individual nodes.
-That is required as there is no notion of ordering in a general graph.
-For example, in a classical convolution on the grid, the relative ordering of vertices is up, down, left, and right.
-There is no such ordering on the sphere either, especially if irregularly sampled.
-
-Following \citep{defferrard2016convolutional}, we define our filters as Chebyshev polynomials such as the convolution operation becomes
+% NP: Should we take a single vertex and explain what happens to it?
+where $\L^k$ captures $k$-neighborhoods.\footnote{The 1-neighborhood of a node is the set of nodes that are directly connected to it.
+The $k$-neighborhood of a node is the set of nodes that are connected to it through paths of length $k$.}
+The entry $(\L^k)_{ij}$ is the sum of all weighted paths of length $k$ between nodes $v_i$ and $v_j$, where the weight of a path is the multiplication of all the edge weights on the path.
+Hence, it is non-zero if and only if nodes $v_i$ and $v_j$ are connected by at least one path of length $k$.
+Filtering with a polynomial convolution kernel can thus be interpreted in the pixel (vertex) domain as a weighted linear combination of neighboring pixel values.
+In the classical setting, convolutions are also weighted local sums.
+The weights are however given by the filter coefficients only, and there is one coefficient per pixel in the patch.
+In the graph setting, the weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$, and there is one coefficient per neighborhood, not node.
+That defines radial filters, which value only depends on the distance to the center, not the direction.
+It is required as there is no way to order and match nodes from the same neighborhood in a general graph.
+The number of nodes in a neighborhood most often even vary from node to node.
+While it may seem odd to restrict filters to be 1D while the sphere is 2D, radial filters are direction-less and result in rotation equivariant convolutions.
+We note that restricting the graph convolutional kernel to a polynomial is similar to restricting the classical euclidean convolution to a fixed-size patch.
+Similarly, each line of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an irregular patch of radius $K$.
+
+Following \citep{defferrard2016convolutional}, we define our filters as Chebyshev polynomials.
+The filtering operation \eqnref{graph_convolution_fourier} becomes
 \begin{equation} \label{eqn:graph_convolution_cheby}
@@
 \end{equation}
-where $\tL = \frac{2}{\lambda_{max}} \L - \b{I} = -\frac{2}{\lambda_{max}} \D^{-1/2} \W \D^{-1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\b \Lambda}$ in $[-1, 1]$ and $T_k(\cdot)$ is the Chebyshev polynomial of degree $k$, defined by the recursive relation $T_k(\tL) = 2\tL T_{k-1}(\tL) - T_{k-2}(\tL)$, $T_1(\tL) = \tL$, $T_0(\tL) = \b{I}$.
-While definitions \eqnref{graph_convolution_monomial} and \eqnref{graph_convolution_cheby} both allow the representation of the same set of filters, Chebyshev polynomials are preferred as they form an orthogonal basis on the interval $[-1, 1]$.
-Moreover, they factor out $\tL^{k-2}$ from $T_k(\tL)$, e.g., the 3-neighborhood is not mixed with the 5-neighborhood.
-That results in easier learning when optimizing the parameters $\theta$.
-Finally, the coefficients can be computed such as the truncated Chebyshev expansions gives an approximate minimax polynomial of a given filter \citep{hammond2011wavelets}.
-While that is irrelevant when learning filters, it is useful when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
-In practice, we found out in our experiment that Chebyshev polynomials are slightly more stable than the monomials used in~\cite{khasanova2017graphomni} (i.e.
-optimizing directly the $\theta_k$ in \eqnref{graph_convolution_monomial}).
-We believe that this is due to their orthogonality (as explained above) and uniformity\footnote{The amplitude of Chebyshev polynomials is more or less constant over the domain $[-1, 1]$ independently of the order $k$.
-On the contrary the amplitude of $x^k$ is very different for $|x|\approx 0$ and $|x| \approx 1$.}.
-% \nati{I added a sentence and I think we should not give much more details here. If we do an experiment, we can comment in the experiment section.}
-% \todo{(i) scale of $\theta_k$: they are mostly uniform for Chebyshev polynomials, end exploding for monomials. Though SGD implicitly imposes a uniform prior on the learned parameters.}
-% \todo{(ii) numerical stability of $\L^k \f$ v.s. $T_k(\L) \f$}
-% \todo{(iii) in the code, initialize $\theta_k$ with stdev adapted to $F_{in}$ and $K$}
-
-Exploiting the recursive formulation of Chebyshev polynomials, evaluating \eqnref{graph_convolution_cheby} requires $\bO(K)$ multiplications of the dense vector $\f$ with the sparse matrix $\tL$.
-The cost of one such multiplication is $\bO(|\E|)$. By construction of our graph, $|\E| < 8 N_{pix}$ and the overall computational cost of the convolution is thus reduced to $\bO(N_{pix})$ operations.
-That is much more efficient than filtering with spherical harmonics, even though the HEALPix was designed as an iso-latitude sampling to leverage a fast spherical transform.
+where $\tL = \frac{2}{\lambda_{max}} \L - \b{I} = -\frac{2}{\lambda_{max}} \D^{-1/2} \W \D^{-1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\b \Lambda}$ in $[-1, 1]$.
+$T_k(\cdot)$ is the Chebyshev polynomial of degree $k$ defined by the recursive relation $T_k(\tL) = 2\tL T_{k-1}(\tL) - T_{k-2}(\tL)$, $T_1(\tL) = \tL$, $T_0(\tL) = \b{I}$.
+While definitions \eqnref{graph_convolution_monomial} and \eqnref{graph_convolution_cheby} both allow the representation of the same filters, we found in our experiments that optimizing $\theta$ in \eqnref{graph_convolution_cheby} is slightly more stable than $\theta$ in \eqnref{graph_convolution_monomial}.
+We believe that this is due to (i) their almost orthogonality in the spectral and spatial domains, and (ii) their uniformity.\footnote{The amplitude of the Chebyshev polynomials $T_k(x)$ is mostly constant over the domain $[-1, 1]$, independently of the order $k$.
+On the contrary, the amplitude of the monomials $x^k$ is very different for $|x|\approx 0$ and $|x| \approx 1$.}
+% MD: SGD implicitly imposes a uniform prior on the learned parameters.
+% Moreover, they factor out $\tL^{k-2}$ from $T_k(\tL)$, e.g., the 3-neighborhood is not mixed with the 5-neighborhood.
+% That results in an easier optimization of the parameters $\theta$.
+Moreover, the coefficients can be computed such as the truncated Chebyshev expansions is an approximate minimax polynomial of a given filter \citep{hammond2011wavelets}.
+While that is irrelevant when learning filters, it is useful for example when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
+% \todo{numerical stability of $\L^k \f$ v.s. $T_k(\L) \f$}
+% NP: we should not give much more details here. If we do an experiment, we can comment in the experiment section.}
+Finally, note that while the graph convolution \eqnref{graph_convolution_fourier} is motivated in the spectral domain, definitions \eqnref{graph_convolution_monomial} and \eqnref{graph_convolution_cheby} are implementations in the vertex domain.
+
+Exploiting the recursive formulation of Chebyshev polynomials, evaluating \eqnref{graph_convolution_cheby} requires $\bO(K)$ multiplications of the vector $\f$ with the sparse matrix $\tL$.
+% In our case, the Laplacian is extremely sparse, with 8 to 9 entries per line (out of $N_{pix}$).
+The cost of one such multiplication is $\bO(|\E| + |\V|)$.
+By construction of our graph, $|\E| < 8 N_{pix}$ and the overall computational cost of the convolution reduces to $\bO(N_{pix})$ operations.
+That is much more efficient than filtering with spherical harmonics, even though HEALPix was designed as an iso-latitude sampling that has a fast spherical transform.
 That is especially true for smooth kernels which require a low polynomial degree $K$.
 \figref{filtering_speed} compares the speed of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
-A naive implementation of our method is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively, than using the spherical harmonic transform implemented by the highly optimized library used by HEALPix, \pkg{libsharp} \citep{reinecke2013libsharp}.
+A naive implementation of our method is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively, than using the spherical harmonic transform implemented by the highly optimized \pkg{libsharp} \citep{reinecke2013libsharp} library used by HEALPix.
 

### 2018-09-03 scnn.tex
fix links in footnotes

@@
     \item (Everyone should check this) Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
-    \item Check links in footnotes.
 	\item (fail - I checked few fonts here: \url{de.sharelatex.com/learn/Font_typefaces}, but none looked better) (TK) Font: do we have to use times (set in the documentclass)?
@@
 The classification methods were trained to predict a label from a HEALPix map.
-Both our Python implementation\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are openly available online.
+Both our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are openly available online.
 Furthermore, Jupyter notebooks demoing the method and problem can be run from your browser without installing anything.
@@
 The main product of this contribution is HealpixNet: a small and easy-to-use python package for spherical analysis of cosmological data.
-The code and data used in this work are publicly available\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}.
+The code and data used in this work are publicly available{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}}.
 The code was designed in a way to enable straightforward modifications of the architectures, so that HealpixNet can easily be used for a number of typical machine learning tasks, such as classification, regression, or segmentation.

### 2018-09-03 scnn.tex
many edits in introduction

@@
 	\includegraphics[width=\linewidth]{figure_architecture_v3}
-	\caption{Overall network architecture, showing here two convolutional layers acting as feature extractors followed by a fully connected layer with softmax acting as the classifier.
-    %\nati{add the stat layer?}
-    %\TK{added stats layer to figure text, hope that's OK}
+	\caption{Overall network architecture, showing here three convolutional layers acting as feature extractors followed by three fully connected layers with softmax acting as the classifier.
     A convolutional layer is based on five operations: convolution, non-linearity, batch normalization, down-sampling, and pooling.
@@
 	Graphs are versatile data structures which can model any sampling, even irregular or partial.
-Second, we propose to exploit a hierarchical pixelization of the sphere for the pooling operation.
+	Second, we propose to exploit a hierarchical pixelization of the sphere for the down-sampling operation.
 	It allows the network to analyze the data at multiple scales while preserving the spatial localization of features.
-This figure shows a network which operates on the whole sphere.
-The process is, however, the same when working with parts of sphere, except that the graph is only built for the part of interest.}
+	This figure shows a network that operates on the whole sphere.
+	The process is the same when working with partial observations, except that the graph is only built for the region of interest.}
 	\label{fig:architecture}
@@
 
-%\subsection{Motivation}
+% Structure:
+  % High-level intro
+  % Desiderata for a method
+  % Related methods / previous work
+  % Our method
+  % Experiments
 
@@
 \citep{schmelze2017cosmologicalmodel,luciesmith2018machinelearning,gupta2018nongaussianinformation,gillet2018deeplearning,hassan2018reionizationmodels,aragoncalvo2018classyfyinglarge,ciuca2017cnnstring,ravanbakhsh2017estimating}.
-This is possible as CNNs have the capacity to build rich models and capture complicated, non-linear patterns, which are often present in the data.
-
-% \TK{I would move the discussion about this to a later place in the paper}
-% Convolutional Neural Networks (CNNs) are particularly well suited for analysis of cosmological data due to the translation invariance built into their architecture.
-% Indeed, sky maps are rotation invariant, which means that rotating maps on the sphere doesn't change their interpretation.
-% Only the statistics of the maps is relevant.
-% The location of the map on the sky is always fixed (by where the telescope was looking), and most of the models tested are homogeneous and isotropic (the cosmological principle).
-% As such, learned weights can be shared across the sphere: the network does not have to relearn to detect objects or features at every spatial location.
-
-% \todo{@Tomek: can you explain why we care about parts of the sphere? (that is an advantage of the graph model over the spherical harmonics)}
-% \todo{@Tomek: How is the data acquired?
-Do telescopes and satellites take measurements according to the HEALPix sampling?
-(it is also an advantage of our method to be agnostic to the sampling, which might be useful to researchers working with missing data or different models)}
-% \nati{@Tomek: I think what Michael has in mind is that the graph approach is very versatile and extendable.
-It can be used with other samplings (even irregular ones) or only part of the sphere.
-This flexibility might be an advantage to mention.
-In particular, compared to~\citep{cohen2018sphericalcnn} it allows us to do only do the required computation when only a part of the sphere is considered.}
-
-So far these algorithms have mostly been demonstrated on Euclidean domains, such as flat images.
-Perhaps the most straightforward approach to the analysis of spherical data is to divide it into small chunks and project those on flat 2D surfaces.
-% \todo{Tune according to the story in the related work.}
-While this approach has been demonstrated to work \citep{fluri2018deep,gupta2018nongaussianinformation,schmelze2017cosmologicalmodel,gillet2018deeplearning}, it may be more natural for some applications and accurate to work directly on the sphere.
+This is possible as neural networks have the capacity to build rich models and capture complicated, non-linear patterns, which are often present in the data.
+CNNs are particularly well suited for analysis of cosmological data as their trainable weights are shared across the domain, i.e., the network does not have to relearn to detect objects or features at every spatial location.
+
+So far these algorithms have mostly been demonstrated on Euclidean domains, such as images.
 The main challenge in designing a CNN on the sphere is to define a convolution operation that is suitable for this domain, while taking care of the necessary irregular sampling.
-Furthermore, to be able to train the network efficiently, the convolution has to be performed fast.
-Another important feature is for a CNN to be able to work on subpart of the sphere, as for many cosmological observations cover only a part of the sky.
+Moreover, the designed convolution, and resulting neural network, should possess the following three key characteristics.
+First, the convolution should be equivariant to rotation, meaning that a rotation of the input implies the same rotation of the output.
+Sky maps are rotation invariant: rotating maps on the sphere doesn't change their interpretation.
+Only the statistics of the maps are relevant.
+Depending on the task, we want the CNN to be either equivariant or invariant to rotation.
+Second, to be able to train the network in reasonable time, the convolution has to be computationally efficient.
+Third, a CNN should work well on parts of the sphere, as many cosmological observations cover only a part of the sky.
 For ground-based observations this can be due to limited visibility of the sky from a particular telescope location, and for space-based instruments due to masking of the galactic plane area (see for example \figref{example_maps}).
@@
 % cohen2017convolutional (ICML workshop) and cohen2018sphericalcnn (ICLR best paper) are redundant
-A first direction to generalize CNNs to spherical data was to apply a standard 2D CNN to a grid discretisation of the sphere~\citep{boomsma2017spherical,su2017sphericalconv,coors2018spherenet}.
-While this approach uses the well-developed 2D convolution and hierarchical pooling, it is restricted to specific grid sampling schemes that are highly irregular, and hence inherently deform the domain where the data is supported.
-A second direction attempted by~\citep{cohen2018sphericalcnn} was to leverage the spherical Fourier transform and to perform the convolution associated to the SO(3) rotation group in the spectral domain, thanks to the convolution theorem.
-Contrarily to the first direction, the resulting convolution is rotational equivariant, meaning that a rotation of the input implies the same rotation of the output.
-This is an important property as translation invariance is probably one of the main reasons why classic CNNs are successful in the first place.
-Nevertheless, this approach is computationally expensive even if a fast spherical Fourier transforms is used.
-%(They exist for particular samplings.)
-Finally, the use of a graph to model the discretised sphere was considered by~\citep{khasanova2017graphomni}, towards the goal of designing a network that is invariant to rotations.
-While its architecture accommodates these invariances on the sphere and remains fairly efficient, it did not take advantage of a hierarchical pixelisation and use a simple grid discretisation of the sphere.
-Moreover, the statistical layer, which introduces the invariance, needs to be hand-crafted to capture statistics of interest.
-
-This work is the first to design a spherical convolutional neural network for cosmological applications.
-Previously, several other machine learning algorithms were extended to the sphere, often also including the third, radial direction.
-Most notably, sparsity-based methods were developed, such as wavelets \citep{Leistedt2013flaglets,Leistedt2015spinwavelets}, ridgelets \citep{McEwen2015ridgelet} and curvelets \citep{Chan2017curvelets,Starck2009polarized}.
-
-%\todo{better identify the shortcomings: (i) part of sphere / missing data, (ii) computational efficiency, (iii) equivarience}
-% \nati{The part of the sphere/missing data is not really there, but I still do not know how to include it!}
-
-We introduce an efficient spherical CNN formulation which uses (i) convolutions on graphs and (ii) hierarchical pooling, while working with the Hierarchical Equal Area isoLatitude Pixelisation (HEALPix) sampling.
-The main idea is to represent the sphere $S^2$, a 2-dimensional manifold embedded in $\mathbb{R}^3$, as a graph of connected pixels.
-The length (or weight) of the shortest path between two pixels is an approximation of the geodesic distance between them on the manifold.
-The use of this approach is enabled by recent developments in graph signal processing, where fundamental tools, such as for example the Fourier transform, were defined for graphs \citep{shuman2013emerging}.
-Our approach uses the graph CNN formulation introduced by \citep{defferrard2016convolutional}, which can accommodate any sampling of the sphere.
+One direction to generalize CNNs to spherical data is to apply a standard 2D CNN to a grid discretisation of the sphere~\citep{boomsma2017spherical,su2017sphericalconv,coors2018spherenet}.
+An alternative is to divide the sphere into small chunks and project those on flat 2D surfaces \citep{fluri2018deep,gupta2018nongaussianinformation,schmelze2017cosmologicalmodel,gillet2018deeplearning}.
+While these approaches use the well-developed 2D convolution and hierarchical pooling, they are not equivariant to rotation.
+Another direction is to leverage the spherical Fourier transform and to perform the convolution associated to the SO(3) rotation group in the spectral domain, thanks to the convolution theorem \citep{cohen2018sphericalcnn, esteves2017sphericalcnn}.
+While the resulting convolution is equivariant to rotation, this approach is computationally expensive, even if a fast spherical Fourier transform is used.
+Moreover, all those methods cannot be much accelerated when maps only span a part of the sky.
+
+% MD: I don't see what the following brings to the paper.
+% This work is the first to design a spherical convolutional neural network for cosmological applications.
+% Previously, several other machine learning algorithms were extended to the sphere, often also including the third, radial direction.
+% Most notably, sparsity-based methods were developed, such as wavelets \citep{Leistedt2013flaglets,Leistedt2015spinwavelets}, ridgelets \citep{McEwen2015ridgelet} and curvelets \citep{Chan2017curvelets,Starck2009polarized}.
+
+Our spherical CNN leverages convolutions on graphs and hierarchical pooling to address all three identified shortcomings: (i) rotation equivariance, (ii) computational efficiency, and (iii) partial sky observations.
+The main idea is to model the discretised sphere as a graph of connected pixels: the length of the shortest path between two pixels is an approximation of the geodesic distance between them.
+This approach is enabled by recent developments in graph signal processing, where fundamental tools, such as the Fourier transform, were defined for graphs \citep{shuman2013emerging}.
+The graph convolution has been explored previously for omnidirectional imaging \citep{khasanova2017graphomni}, with a different down-sampling operation.
+Our pooling strategy exploits a hierarchical pixelisation of the sphere to analyse the data at multiple scales.
+% Compared with~\citep{khasanova2017graphomni}, our work does not need hand-chosen statistics nor dynamic pooling.
+We use the graph CNN formulation introduced in \citep{defferrard2016convolutional}, which can accommodate any sampling of the sphere.
+As the Equal Area isoLatitude Pixelisation (HEALPix)~\citep{gorski2005healpix} is the most popular sampling used in cosmology and astrophysics, we tailored the method to that particular sampling and call it HealpixNet.
+HealpixNet is however easily used with other samplings as only two elements depend on it: (i) the choice of neighboring pixels when building the graph, and (ii) the choice of parent pixels when building the hierarchy.
+The flexibility of modeling the data domain with a graph allows to easily model data that spans only a part of the sphere, or data that is not uniformly sampled.
 Using a $k$-nearest neighbours graph, the convolution operation costs $\mathcal{O}(N_{pix})$ operations, where $N_{pix}$ is the number of pixels.
-This is the lowest possible complexity for a convolution operation without approximations (e.g., by sketching).
-The flexibility of modeling the data domain with a graph allows to easily model data that spans only a part of the sphere, or data that is not uniformly sampled.
-Our hierarchical pooling strategy exploits a hierarchical pixelisation of the manifold to analyse the data at multiple scales.
-% Such hierarchical pixelisations of the sphere have been well studied.
-
-In this work we present and release HealpixNet\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}, an algorithm and software package which implements an efficient CNN on HEALPix maps.
-It is implemented with \pkg{TensorFlow} \citep{abadi2016tensorflow} and is intended to be easy to use out-of-the-box for cosmological applications.
+This is the lowest possible complexity for a convolution without approximations.
 HealpixNet is readily apt to solve four tasks: (i) global classification (i.e., predict a class from a map), (ii) global regression (i.e., predict a set of parameters from a map), (iii) dense classification (i.e., predict a class for each pixel of a map), and (iv) dense regression, (i.e., predict a set of maps from a map).
-As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology and astrophysics, we tailored our method to that particular sampling.
-The elements of the graph that depend on the sampling are:
-(i) the choice of neighboring pixels when building the graph, and
-(ii) the choice of parent pixels when building the hierarchy of layers.
-% It is also possible to use multiple HEALPix maps within our framework and use datasets in form of ``shells''.
-% These shells can span the radial direction, so that a tomographic analysis can be performed, or different frequencies, in case of data from observations in radio frequencies.
-% \nati{I do not know about that last point.
-Yes we can do it.
-But a) we did not do it and b) the filter will be spherical in all directions includeding the radial one...
-I am not sure this is a disirable features.}
-% \todo{I think you got it wrong there. I guess the idea is that each shell would be a feature map, i.e., the graph signal would be multi-dimensional.}
-% \TK{OK, let's talk about it.}
+Input data are spherical maps with a single value per pixel, such as the CMB temperature, or multiple values per pixel, such as surveys at multiple radio frequencies.
+
 %\nati{I am not sure this goes there...} Other recently developed sampling methods include \citep{mcewen2011novelsampling}, where exact sampling theorem for equiangular MW sampling was presented.
 
-We give a practical demonstration of the application of our package to cosmological model discrimination using maps of projected mass distribution on the sky \citep{chang2017curvedsky}.
+We give a practical demonstration of HealpixNet on cosmological model discrimination using maps of projected mass distribution on the sky \citep{chang2017curvedsky}.
 This kind of maps can be created using the gravitational lensing technique \citep[see][for review]{BartelmannSchneider2001weak}.
 Our maps are similar to the ones used by \citep{schmelze2017cosmologicalmodel}.
-In a simplified scenario, we classify convergence maps on parts of a sphere into two cosmological models.
-These models were designed to have very similar angular power spectrum for the angular wavenumbers $\ell < 1000$.
-We compare the performance of our spherical CNN to a baseline algorithm, an SVM classifier which takes pixel histograms or power spectrum densities (PSDs) of these maps as input.
+In a simplified scenario, we classify partial convergence maps into two cosmological models.
+These models were designed to have very similar angular power spectrum.
+We compare the performance of HealpixNet to a baseline algorithm: an SVM classifier that takes pixel histograms or power spectrum densities (PSDs) of these maps as input.
 The comparison is made as a function of the additive noise level and the area of the sphere used in the analysis.
-% Results show that our model is better at discriminating the maps and is more resilient to noise.
-
-The paper is organized as follows.
-In \secref{related}, we describe existing approaches to convolutions on spheres, graphs, and manifolds.
-\secref{method} exposes the construction of a graph given the HEALPix sampling of a sphere and defines the convolution operation.
-Finally, \secref{experiments} presents our experimental results on the weak lensing mass map classification problem. There we compare our method to two standard benchmarks and show its superiority.
+Results show that our model is always better at discriminating the maps, especially in the presence of noise.
+HealpixNet is implemented with \pkg{TensorFlow} \citep{abadi2016tensorflow} and is intended to be easy to use out-of-the-box for cosmological applications.
+Code and examples are available online.{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}}
+
+% MD: I usually find those paragraphs boring and skip them when reading. Our intro is long enough already. Feel free to add it back if you think it's necessary.
+%The paper is organized as follows.
+%In \secref{related_work}, we describe existing approaches to convolutions on spheres, graphs, and manifolds.
+%\secref{method} exposes the construction of a graph given the HEALPix sampling of a sphere and defines the convolution operation.
+%Finally, \secref{experiments} presents our experimental results on the weak lensing mass map classification problem. There we compare our method to two standard benchmarks and show its superiority.
 %We conclude in \secref{conclusion}.
@@
 
-On regular Euclidean domains, such as 1-dimensional time series or 2-dimensional images, a convolution can be efficiently implemented by sliding a localized convolution kernel (for example a patch of 5x5 pixels) in the signal domain.
+On regular Euclidean domains, such as 1-dimensional time series or 2-dimensional images, a convolution can be efficiently implemented by sliding a localized convolution kernel (for example a patch of $5 \times 5$ pixels) in the signal domain.
 Likewise, down-sampling can be achieved by taking one pixel out of $n$.
@@
 The implementation, however, does not need a direct access to the spectrum, which is computationally more efficient (see \secref{efficient_convolution}).
-% We will therefore use the spectral domain to define the convolutions
-% \footnote{Note that we only use the spectrum to define the convolution.
-% The implementation however does not need a direct access to the spectrum, which is computationally much more efficient. See \secref{efficient_convolution}.}
-% \TK{moving footnote to the main text }
 The gist of our method is to define the convolution operation on a sphere using a graph, and the down-sampling operation using a hierarchical pixelisation of the sphere.
@@
 
-Our graph is constructed as an approximation of the continuous 2D manifold that is the surface of the sphere.
+Our graph is constructed as an approximation of sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$,
 Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity.
@@
 Similarly, each line of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an irregular patch of radius $K$.
+Hence, filters designed as polynomials of the Laplacian have local support in the vertex domain.
 
@@
 \section{Related work}
-\label{sec:related}
+\label{sec:related_work}
 
@@
 We propose to use the idea of fully convolutional networks (FCNs) instead (see \secref{architecture}).
-While statistics have to be hand-chosen to capture relevant information for the task, the filters in a FCN are trained end-to-end to capture relevant information.
+While statistics have to be hand-chosen to capture relevant information for the task, the filters in a FCN are trained end-to-end to capture it.
 

### 2018-09-04 scnn.tex
edits on the conclusion

@@
 
-In this contribution we presented HealpixNet: a spherical convolutional neural network for the HEALPix sampling.
-The core of our method is the use of a graph to represent the pixel grid on the sphere.
-This allows us to leverage the advantages of the graph convolution; it is both efficient, with a complexity of $\mathcal{O}(N_{pix})$, and flexible, which allows to work only on a part of the sphere.
-Spherical properties of the domain are still captured well.
-The method presented here restricts the shape of the filters learned by the network to be radial.
-While this may be a less general design compared to the one used by conventional CNNs on flat images, we found it to still work efficiently for our test cases.
-The layered structure of the network can partially compensate for that.
-% Further generalizations to non-radial filters may be possible [cite?]\TK{update here}, but we leave it to future work.
+The main product of this contribution is HealpixNet, a small and easy-to-use python package for the spherical analysis of cosmological data.
+The code was designed so that HealpixNet can easily be used for typical machine learning tasks, such as classification and regression, both dense and global.
+% dense: segmentation tasks, such as masking, flagging, or object detection
+The core of our method is the use of a graph to represent the discretised sphere.
+This allows us to leverage the advantages of the graph convolution.
+It is both efficient, with a complexity of $\bO(N_{pix})$, and flexible, which allows HealpixNet to efficiently work on parts of the sphere.
+The spherical properties of the domain are well captured: the graph Fourier modes are close to the spherical harmonics.
+Filters are restricted to be radial for the convolution operation to be equivariant to rotation.
+HealpixNet can then be made either equivariant or invariant to rotation.
+Equivariance is not perfect as small imprecisions due to the sampling cause the action of a graph filter to slightly depend on the location.
+That is however not an issue in practice.
 
@@
 The maps were produced from two cosmological models with varying $\sigma_8$ and $\Omega_m$, chosen to follow the typical weak lensing degeneracy in these parameters, so that the power spectra for these models are similar.
-We compared the performance of the HealpixNet CNN versus that of two SVM-based classifiers: one trained on the spherical harmonics power spectrum, and the other on the pixel density histogram.
-% Notably, HealpixNet maintains good classification accuracy even for high noise levels and part-sky areas.
-HealpixNet performs better than the angular power spectrum and the histogram classifiers for all considered cases.
+We compared the performance of HealpixNet versus that of two SVM classifiers: one trained on the spherical harmonics power spectrum, and the other on the pixel density histogram.
+HealpixNet performs better than the two baselines for all considered cases.
 The advantage is small for large, noise-free maps, and grows up to 10\% for smaller, noisier data.
 
-We show that modeling the discretised sphere by a graph enables an efficient convolution operation on HEALPix sampling.
-Graph-based representation of the sphere can display small imprecisions in rotation invariance, the result of which is that an action of a graph filter slightly depends on the location.
-For applications that can tolerate this property, a graph-based representation may be a worthwhile alternative.
-For example, a machine learning based cosmological inference algorithm can in principle tolerate this property, as it requires the simulations to be represented the same way as observations anyway.
-This way, imperfections in representation will affect the simulations and real data in the same way, and will not cause biases in the analysis result.
-
-The main product of this contribution is HealpixNet: a small and easy-to-use python package for spherical analysis of cosmological data.
-The code and data used in this work are publicly available{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}}.
-The code was designed in a way to enable straightforward modifications of the architectures, so that HealpixNet can easily be used for a number of typical machine learning tasks, such as classification, regression, or segmentation.
-Notably, for a problem of cosmological parameter estimation \citep{fluri2018deep,gupta2018nongaussianinformation}, it is easy to replace the classification loss task with a regression loss.
-It should also be possible use dense layer for an output and perform segmentation tasks, such as masking, flagging, or object detection.
+Spherical CNNs are so far mostly used for omnidirectional imaging.
+Many scientific fields, such as weather or climate modelling, would however benefit from an efficient and versatile spherical CNN.
+With this work, we hope to demonstrate and help democratize the use of those tools for spherical data analysis.
+% Fields: planets, molecules?, atoms.
 
 As a future work, it would be interesting to further investigate the link between the graph Fourier basis and the spherical harmonics.
-Furthermore, the influence of the irregular sampling on the rotational equivariance should be quantified empirically and ideally bounded theoretically.
-Further comparison of HealpixNet to other spherical CNN algorithms, with different sampling schemes, would also be worthwhile.
-
-% Hence, it relaxes the iso-latitude constraint on sampling schemes who aim to enable fast convolutions.
-% \TK{I would move the info about possible relaxation of the iso-latitude thing to a separate paragraph at the end on conclusions - future prospects?}
-% this relaxation might enable researchers to consider sampling sets with different properties.
-% \TK{this I don't understand}
+Furthermore, the influence of irregular sampling on the convolution's equivariance to rotation should be empirically quantified and ideally theoretically bounded.
+Further comparison of HealpixNet to other spherical CNN formulations, with different sampling schemes, would also be worthwhile.
+
+The fact that a graph representation of the disretised sphere enables an efficient convolution relaxes the iso-latitude constraint on the design of sampling schemes who aim to enable fast convolutions.
+In the long term, it might enable researchers to consider sampling schemes with different trade-offs, or remove the need for schemes and interpolation altogether and simply consider the positions at which measures were taken.
 
@@
 
-This work was supported by a grant from the Swiss Data Science Centre (SDCS) under project ID \textit{sd01 - DLOC:  Deep Learning for Observational Cosmology} and grant number 200021\_169130 from the Swiss National Science Foundation.
+This work was supported by a grant from the Swiss Data Science Centre (SDCS) under project \textit{DLOC:  Deep Learning for Observational Cosmology} and grant number 200021\_169130 from the Swiss National Science Foundation.
 We thank Jean-François Cardoso for helpful discussions about the spherical harmonics.

### 2018-09-04 scnn.tex
a pass on the abstract

@@
 \author[ETHZ]{Raphael Sgier(?)}
-% \author{TBD}
 
@@
 %Convolutional Neural Networks (CNNs) are becoming an important analysis tool in cosmology and astrophysics.
-% Michaël: useful info? To me this is not an argument for our approach. Maybe we have to expand it?
+% MD: useful info? To me this is not an argument for our approach. Maybe we have to expand it?
 
 % Architectures are then designed similarly to the classical CNNs used for image analysis.
-% HealpixCNN (???) uses Tensorflow as the underlying engine and can utilize most of it functionalities.
-% Michaël: not relevant for the abstract in my opinion
-
-Convolutional Neural Networks (CNNs) are now a cornerstone of the Deep Learning toolbox and have led to many breakthroughs in Artificial Intelligence.
+% HealpixNet uses Tensorflow as the underlying engine and can utilize most of it functionalities.
+% MD: not relevant for the abstract in my opinion
+
+Convolutional Neural Networks (CNNs) are a cornerstone of the Deep Learning toolbox and have led to many breakthroughs in Artificial Intelligence.
 So far, these networks have mostly been developed for regular Euclidean domains such as those supporting images, audio, or video.
 Because of their success, CNN-based methods are becoming increasingly popular in Cosmology.
-Cosmological data often comes in a form of spherical maps, which makes the use of traditional CNNs more complicated.
-The commonly used pixelzation scheme for spherical maps is Hierarchical Equal Area isoLatitude Pixelisation (HEALPix).
+Cosmological data often comes as spherical maps, which make the use of traditional CNNs more complicated.
+The commonly used pixelization scheme for spherical maps is the Hierarchical Equal Area isoLatitude Pixelisation (HEALPix).
 We present a spherical CNN for analysis of full and partial HEALPix maps, which we call HealpixNet.
-We construct a spherical CNNs by representing the sphere as a graph.
+The spherical CNN is constructed by representing the sphere as a graph.
 Graphs are versatile data structures which can represent pairwise relationships between objects or act as a discrete representation of a continuous manifold.
-Using the graph-based representation, we define many of the standard CNN operations, such as convolution and pooling, with filters restricted to being radial.
+Using the graph-based representation, we define many of the standard CNN operations, such as convolution and pooling.
+With filters restricted to being radial, our convolutions are equivariant to rotation on the sphere, and HealpixNet can be made invariant or equivariant to rotation.
 This way, HealpixNet is a special case of a graph CNN, tailored to the HEALPix sampling of the sphere.
 % TBD if we include it
-% This approach is computationally more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
-An advantage of this representation is that the convolution operations with this approach are efficient, which enables the algorithm to run fast.
+This approach is computationally more efficient than using spherical harmonics to perform convolutions.
+% An advantage of the graph representation is that the convolution operations are efficient, which enables the CNN to run fast.
 We demonstrate the method on a classification problem of mass maps from two cosmological models and compare the performance of the CNN with that of two baseline classifiers, based on the power spectrum and pixel density histogram.
-Our experimental result shows that the performance of HealpixNet to always be better or equal to both of these baselines.
+Our experimental results show that the performance of HealpixNet is always superior or equal to both of these baselines.
 For high noise levels and for data covering only a smaller fraction of the sphere, HealpixNet achieves typically 10\% better classification accuracy than those baselines.
-Finally, we propose a visualization of filters learned by the HealpixNet from the mass maps as some analysis tool for the neural network.
-Code and examples are available at \todo{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}.
+Finally, we show how learned filters can be visualized to introspect the neural network.
+Code, data, and examples are available at \url{https://github.com/SwissDataScienceCenter/HealpixNet}.
 

### 2018-09-04 scnn.tex
new todo
no line numbers by default
small edit

@@
 \usepackage{lineno}
-\linenumbers
+% \linenumbers
 
@@
 
-%% \linenumbers
-
 \section*{TODO list}
@@
     \item (NP) Put Raphael in the dataset author.
+	\item (NP \& MD) Move the git repository, rename the classes, check the links.
     \item (Probably OK) Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
@@
 (iv) a pooling operation, and
-(v), optionally,  normalization.\footnote{\citep{ioffe2015batchnorm} have shown that batch normalization helps training. We verified this experimentally in our setting as well.}
+(v), optionally,  normalization.\footnote{Batch normalization has been shown to help training \citep{ioffe2015batchnorm}. We verified this experimentally in our setting as well.}
 Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}.

### 2018-09-19 scnn.tex
disable hyperlinks to prevent cross-page link failures
added appendix about convergence maps and simulation setup

@@
 \usepackage{enumitem} % to remove when done with todo list
+
+\hypersetup{draft}
+% Disable hyperlinks to prevent cross-page link failures.
+% Remove when done with the writing.
+% https://www.overleaf.com/help/246-what-does-slash-pdfendlink-ended-up-in-different-nesting-level-than-slash-pdfstartlink-mean
 
@@
 The simulations are created using the fast lightcone method \pkg{UFalcon} described in \citep{sgier2018fastgeneration}.
-We however use a single simulation box, as opposed to two used in that work, as we use source galaxies at a lower redshift of $z=1$, instead of $z=1.5$.
+A brief overview about the map making procedure used in \pkg{UFalcon} is given in \recref{convergence_mass_maps} and the specific simulation setup is given in \recref{simulation_setup}.
+We however use a single simulation box, as opposed to two used in that work, as we use source galaxies at a lower redshift of $z=0.8$, instead of $z=1.5$.
 As a simulator we use \pkg{L-PICOLA} \citep{howlett2015lpicola}, a fast and approximate code for N-body simulations.
@@
 
+\section{Convergence Mass Maps}
+\label{sec:convergence_mass_maps}
+
+In the following we describe the weak lensing map-making pipeline \pkg{UFalcon} (ultra fast lightcone) developed in \citep{sgier2018fastgeneration} and how it has been used to generate data used in the present work.
+The data consist of two-dimensional convergence maps on the full sphere, which represent the dimensionless, weighted and projected mass along the light of sight and determines the lensing of source galaxies an observer located on earth would see.
+
+The matter content of the universe consists mostly of dark matter and is therefore mainly responsible for the large scale structure evolution of the universe.
+The effect of weak gravitational lensing, in which the light from distant galaxies is lensed by the matter distribution between the observer and the sources, is therefore dominated by dark matter \citep[see][for a review of gravitational lensing]{bartelman2010gravitationallensing}.
+In order to obtain a convergence map characterising the gravitational lensing of distance sources, one has to start with accurate simulations of the dark matter distribution.
+This is achieved through cosmological N-Body simulations, which evolve a chosen number of dark matter particles $N_\mathrm{part}^\mathrm{sim}$ within a specific simulation volume $V_\mathrm{sim}$ under the influence of gravity across cosmic time-scales.
+The simulation outputs the positions of the particles at user-specific time-steps.
+These time-steps correspond to redshifts $z$, by which the spectrum is shifted the observer would measure.
+A redshift of $z=0$ correspond to the present time and higher redshifts to earlier times.
+
+Since the convergence map characterises the dark matter lenses at different redshifts, one has to first construct a lightcone.
+The lightcone represents the volume of the universe around the observer, where the radius represents the distance the light from distant galaxies at different times and locations has to travel to the observer.
+Therefore, the particles outputted at different redshifts (time-steps) of the simulation are concentrically arranged in shells of constant redshift around the observer (each redshift $z$ corresponds to a comoving distance away from the observer $\chi(z)$), which is located at redshift $z=0$ (see Figure \ref{sketch_lightcone_simulation}).
+The shells are then weighted by a weak lensing specific weight $W_b$ and projected onto the sphere for each pixel $\theta_\mathrm{pix}$, resulting in a convergence map
+\begin{equation}
+\kappa (\theta_\mathrm{pix}) \sim \sum_b W_b \frac{V_\mathrm{sim}}{N_\mathrm{part}^\mathrm{sim}} \frac{n_p (\theta_\mathrm{pix}, \Delta \chi_b)}{\mathcal{D}^2 (z_b)}  \, ,
+\end{equation}
+where $n_p$ represents the number of particles in a specific pixel on the shell $\Delta \chi_b$. The convergence map depends on the cosmological parameters.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{sketch_lightcone_simulation}
+	\caption{Left: Dark matter density field simulated using L-PICOLA for specific cosmological parameters.
+Right: Sketch of the lightcone constructed by arranging particles at different redshifts in concentric shells around the observer located at $z=0$.}
+	\label{fig:sketch_lightcone_simulation}
+\end{figure}
+
+\section{Simulation Setup}
+\label{sec:simulation_setup}
+
+The data is generated for the present analysis is based on the fast approximate N-Body simulation code \pkg{L-PICOLA} \citep{howlett2015lpicola}.
+For our purposes, we chose a simulation volume $V_\mathrm{sim} = (4200 \, h^{-1}\, \mathrm{Mpc})^3$, a total number of particles $N_\mathrm{part}^\mathrm{sim} = 1024^3$ placed on a mesh of size $N_\mathrm{mesh}^\mathrm{sim} = 2048^3$.
+The simulation was then performed 30 times with different seeds for each of the two $\Lambda$CDM cosmological models described in section \secref{data} covering a redshift range from $z = 0.1$ to $z = 0.8$.
+The \pkg{L-PICOLA} were performed in lightcone mode, where the simulation output is already arranged as a lightcone.
+Here we chose a redshift-shell thickness of $\Delta z = 0.01$.
+
 \section*{Bibliography}

### 2018-09-21 scnn.tex
bugfix when referencing to appendix

@@
 The simulations are created using the fast lightcone method \pkg{UFalcon} described in \citep{sgier2018fastgeneration}.
-A brief overview about the map making procedure used in \pkg{UFalcon} is given in \recref{convergence_mass_maps} and the specific simulation setup is given in \recref{simulation_setup}.
+A brief overview about the map making procedure used in \pkg{UFalcon} is given in \ref{sec:convergence_mass_maps} and the specific simulation setup is given in \ref{sec:simulation_setup}.
 We however use a single simulation box, as opposed to two used in that work, as we use source galaxies at a lower redshift of $z=0.8$, instead of $z=1.5$.

### 2018-10-19 scnn.tex
small edit
small changes

@@
 
-\title{HealpixNet: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications}
+\title{DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications}
 % \title{Efficient Spherical ConvNet with Graph Convolutions for Cosmological Applications}
@@
 \author[ETHZ]{Tomasz Kacprzak}
-\author[ETHZ]{Raphael Sgier(?)}
+\author[ETHZ]{Raphael Sgier}
 
@@
 	\item (TK) Can we use HEALPix in the name? Check with the main author of HEALPix. MD: what about DeepCosmo or CosmoNet? NP: cosmological data is not necessarily spherical.
+	\nati{No answer from the people. Let us go for DeepSphere. Graphsphere???}
 	\item (TK) Check use of British vs American English. Check use of tense.
-	\item (TK) Larger text on figure 2. I (MD) made it one column wide instead of two as it's more an illustration than a central figure to our exposition.
-	\item (MD) Figure 4: speed for multiple lmax.
+	\item (MD) Figure 4: speed for multiple lmax. Not doing it.
     \item (TK) check part sphere notebook and whole sphere
-    \item (NP) Put Raphael in the dataset author.
 	\item (NP \& MD) Move the git repository, rename the classes, check the links.
-    \item (Probably OK) Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
-    \item (I think it is OK) (NP) Check the wording.
-Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
     \item (Everyone should check this) Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.

### 2018-10-19 scnn.tex
updated info about the dataset

--- 2018-09-21 scnn.tex
@@
 
-\begin{figure}
+\begin{figure*}
 \includegraphics[width=\linewidth]{figure_example_maps}
@@
 \label{fig:example_maps}
-\end{figure}
+\end{figure*}
 
@@
 The classification methods were trained to predict a label from a HEALPix map.
-Both our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are openly available online.
+% Both our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are openly available online.
 Furthermore, Jupyter notebooks demoing the method and problem can be run from your browser without installing anything.
+Our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}} to reproduce those experiments are openly available online.
+The data is available upon request from the cosmology group\footnote{\url{www.cosmology.ethz.ch}}.
+Furthermore, Jupyter notebooks demos can be run from your browser without installing anything.
 

### 2018-10-19 scnn.tex
renamed to DeepSphere

@@
 The commonly used pixelization scheme for spherical maps is the Hierarchical Equal Area isoLatitude Pixelisation (HEALPix).
-We present a spherical CNN for analysis of full and partial HEALPix maps, which we call HealpixNet.
+We present a spherical CNN for analysis of full and partial HEALPix maps, which we call DeepSphere.
 The spherical CNN is constructed by representing the sphere as a graph.
@@
 Using the graph-based representation, we define many of the standard CNN operations, such as convolution and pooling.
-With filters restricted to being radial, our convolutions are equivariant to rotation on the sphere, and HealpixNet can be made invariant or equivariant to rotation.
-This way, HealpixNet is a special case of a graph CNN, tailored to the HEALPix sampling of the sphere.
+With filters restricted to being radial, our convolutions are equivariant to rotation on the sphere, and DeepSphere can be made invariant or equivariant to rotation.
+This way, DeepSphere is a special case of a graph CNN, tailored to the HEALPix sampling of the sphere.
 % TBD if we include it
@@
 We demonstrate the method on a classification problem of mass maps from two cosmological models and compare the performance of the CNN with that of two baseline classifiers, based on the power spectrum and pixel density histogram.
-Our experimental results show that the performance of HealpixNet is always superior or equal to both of these baselines.
-For high noise levels and for data covering only a smaller fraction of the sphere, HealpixNet achieves typically 10\% better classification accuracy than those baselines.
+Our experimental results show that the performance of DeepSphere is always superior or equal to both of these baselines.
+For high noise levels and for data covering only a smaller fraction of the sphere, DeepSphere achieves typically 10\% better classification accuracy than those baselines.
 Finally, we show how learned filters can be visualized to introspect the neural network.
-Code, data, and examples are available at \url{https://github.com/SwissDataScienceCenter/HealpixNet}.
+Code, data, and examples are available at \url{https://github.com/SwissDataScienceCenter/DeepSphere}.
 
@@
 % A popular format for spherical maps is HEALPix, which uses an equal-area, isolatitude sampling.
-% Hence, we present a spherical CNN for analysis of full and partial HEALPix maps, which we call HealpixNet.
+% Hence, we present a spherical CNN for analysis of full and partial HEALPix maps, which we call DeepSphere.
 % \nati{I am not that we should talk about pooling in the abstract.
@@
 % While the convolution on arbitrary graphs has mostly been sorted out, a general pooling operation has not been discovered so far.
-% As such, while HealpixNet is a special case of a graph CNN, it is tailored to the HEALPix sampling of the sphere.
+% As such, while DeepSphere is a special case of a graph CNN, it is tailored to the HEALPix sampling of the sphere.
 % This approach is computationally much more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
-% The filters learned by the HealpixNet are restricted to being radial.
+% The filters learned by the DeepSphere are restricted to being radial.
 % Michaël: not necessary in the abstract?
@@
 % A standard benchmark for that problem is to train an SVM on the histograms of map pixel values. Another is to use the power spectral density instead.
-% HealpixNet achieves \todo{xx\%} better accuracy than those baselines, is more robust to noise, and is \todo{faster?}.
+% DeepSphere achieves \todo{xx\%} better accuracy than those baselines, is more robust to noise, and is \todo{faster?}.
 % Code and examples are available at \todo{\url{https://github.com/xxx}}.
@@
 Spherical Convolutional Neural Network \sep
-HealpixNet \sep
+DeepSphere \sep
 Graph CNN \sep
@@
 We use the graph CNN formulation introduced in \citep{defferrard2016convolutional}, which can accommodate any sampling of the sphere.
-As the Equal Area isoLatitude Pixelisation (HEALPix)~\citep{gorski2005healpix} is the most popular sampling used in cosmology and astrophysics, we tailored the method to that particular sampling and call it HealpixNet.
-HealpixNet is however easily used with other samplings as only two elements depend on it: (i) the choice of neighboring pixels when building the graph, and (ii) the choice of parent pixels when building the hierarchy.
+As the Equal Area isoLatitude Pixelisation (HEALPix)~\citep{gorski2005healpix} is the most popular sampling used in cosmology and astrophysics, we tailored the method to that particular sampling and call it DeepSphere.
+DeepSphere is however easily used with other samplings as only two elements depend on it: (i) the choice of neighboring pixels when building the graph, and (ii) the choice of parent pixels when building the hierarchy.
 The flexibility of modeling the data domain with a graph allows to easily model data that spans only a part of the sphere, or data that is not uniformly sampled.
@@
 This is the lowest possible complexity for a convolution without approximations.
-HealpixNet is readily apt to solve four tasks: (i) global classification (i.e., predict a class from a map), (ii) global regression (i.e., predict a set of parameters from a map), (iii) dense classification (i.e., predict a class for each pixel of a map), and (iv) dense regression, (i.e., predict a set of maps from a map).
+DeepSphere is readily apt to solve four tasks: (i) global classification (i.e., predict a class from a map), (ii) global regression (i.e., predict a set of parameters from a map), (iii) dense classification (i.e., predict a class for each pixel of a map), and (iv) dense regression, (i.e., predict a set of maps from a map).
 Input data are spherical maps with a single value per pixel, such as the CMB temperature, or multiple values per pixel, such as surveys at multiple radio frequencies.
@@
 
-We give a practical demonstration of HealpixNet on cosmological model discrimination using maps of projected mass distribution on the sky \citep{chang2017curvedsky}.
+We give a practical demonstration of DeepSphere on cosmological model discrimination using maps of projected mass distribution on the sky \citep{chang2017curvedsky}.
 This kind of maps can be created using the gravitational lensing technique \citep[see][for review]{BartelmannSchneider2001weak}.
@@
 These models were designed to have very similar angular power spectrum.
-We compare the performance of HealpixNet to a baseline algorithm: an SVM classifier that takes pixel histograms or power spectrum densities (PSDs) of these maps as input.
+We compare the performance of DeepSphere to a baseline algorithm: an SVM classifier that takes pixel histograms or power spectrum densities (PSDs) of these maps as input.
 The comparison is made as a function of the additive noise level and the area of the sphere used in the analysis.
 Results show that our model is always better at discriminating the maps, especially in the presence of noise.
-HealpixNet is implemented with \pkg{TensorFlow} \citep{abadi2016tensorflow} and is intended to be easy to use out-of-the-box for cosmological applications.
-Code and examples are available online.{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}}
+DeepSphere is implemented with \pkg{TensorFlow} \citep{abadi2016tensorflow} and is intended to be easy to use out-of-the-box for cosmological applications.
+Code and examples are available online.{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/DeepSphere}}}
 
@@
 % decision on the class label
-The general HealpixNet architecture, pictured in \figref{architecture}, is composed of many layers.
+The general DeepSphere architecture, pictured in \figref{architecture}, is composed of many layers.
 The convolutional part, the head of the neural network, is composed of graph convolutional layers (GC), pooling layers (P), and batch normalization layers (BN).
@@
 
-HealpixNet can perform dense or global predictions, for regression or classification.
+DeepSphere can perform dense or global predictions, for regression or classification.
 A typical global classification task is to classify maps into cosmological model classes \citep{schmelze2017cosmologicalmodel}.
@@
 This work is another indication that there might be a $\bO(N_{pix}^{3/2})$ computational lower bound for the proper treatment of rotation equivariance with the spherical harmonics.
-In comparison, HealpixNet scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}), at the expense of not being exactly equivariant (see \ref{sec:comparison_spherical_harmonics}).
+In comparison, DeepSphere scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}), at the expense of not being exactly equivariant (see \ref{sec:comparison_spherical_harmonics}).
 Being a mathematically well-defined rotation equivariant network is the main advantage of methods based on spherical harmonics.
@@
 By interwinding graph convolutional layers and recurrent layers \citep{seo2016gcrn}, they can for example model structured time series such as traffic on road networks \citep{li2018traffic}, or recursively complete matrices for recommendation \citep{monti2017recommendation}.
-Another trend, parallel to the modeling of structured data, is the use of graph neural networks for relational reasoning \citep{battaglia2018review}.
+Another trend, parallel to the modelling of structured data, is the use of graph neural networks for relational reasoning \citep{battaglia2018review}.
 % scientifically and industrially motivated applications
@@
 
-The performance of HealpixNet is demonstrated on a discrimination problem: the classification of convergence maps into two cosmological model classes.
+The performance of DeepSphere is demonstrated on a discrimination problem: the classification of convergence maps into two cosmological model classes.
 The experiment presented here is similar to the one by \citep{schmelze2017cosmologicalmodel}.
@@
 The classification methods were trained to predict a label from a HEALPix map.
-% Both our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are openly available online.
+% Both our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/DeepSphere}}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are openly available online.
 Furthermore, Jupyter notebooks demoing the method and problem can be run from your browser without installing anything.
-Our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}} to reproduce those experiments are openly available online.
+Our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/DeepSphere}}} to reproduce those experiments are openly available online.
 The data is available upon request from the cosmology group\footnote{\url{www.cosmology.ethz.ch}}.
@@
 The simulations are created using the fast lightcone method \pkg{UFalcon} described in \citep{sgier2018fastgeneration}.
-A brief overview about the map making procedure used in \pkg{UFalcon} is given in \ref{sec:convergence_mass_maps} and the specific simulation setup is given in \ref{sec:simulation_setup}.
+A brief overview about the map making procedure used in \pkg{UFalcon} as well as the simulation parameters are given in Appendix~\ref{sec:convergence_mass_maps}.
 We however use a single simulation box, as opposed to two used in that work, as we use source galaxies at a lower redshift of $z=0.8$, instead of $z=1.5$.
@@
 
-HealpixNet is compared against two simple yet powerful benchmarks.
+DeepSphere is compared against two simple yet powerful benchmarks.
 The two baselines are based on features that are (i) the power spectral densities (PSD) of maps, and (ii) the histogram of pixels in the maps \citep{patton2017cosmologicalconstraints}.
@@
 A linear kernel is used as other kernels did not provide better results, while having significantly worse scaling properties.
-For fairness, the training set was augmented in a similar way as for HealpixNet: we created samples by adding new random realizations of the noise.
+For fairness, the training set was augmented in a similar way as for DeepSphere: we created samples by adding new random realizations of the noise.
 We stopped adding new samples to the training data once the validation error converged.
 This process is detailed in \ref{sec:dataset_augmentation}.
-As for HealpixNet, the SVM regularization hyper-parameter was tuned based on the performance over the validation set.
-The classification accuracy of HealpixNet and both baselines was checked as a function of the used area (the order $o$), and the relative level of additive noise.
+As for DeepSphere, the SVM regularization hyper-parameter was tuned based on the performance over the validation set.
+The classification accuracy of DeepSphere and both baselines was checked as a function of the used area (the order $o$), and the relative level of additive noise.
 
@@
 %\subsection{Selected network architecture}
-%\subsection{Methods} % baselines and HealpixNet together
+%\subsection{Methods} % baselines and DeepSphere together
 
@@
 The batch size is set to $16 \times  o^2$ to keep the amount of supervision used to estimate the gradient identical, irrespective of the chosen order $o$ (the learning rate would otherwise need to be adapted).
-By this choice, HealpixNet is trained with the same amount of information, i.e., the number of pixels, across all variants of the problem.
+By this choice, DeepSphere is trained with the same amount of information, i.e., the number of pixels, across all variants of the problem.
 Training took approximately $1.5$ hour using a single Nvidia GeForce GTX 1080 Ti ($5$ hours with a Tesla K20).
@@
 	\caption{
-		Classification accuracy of the fully convolutional (FCN) variant of HealpixNet, the standard convolutional (CNN) variant of HealpixNet, the support vector machine (SVM) with the power spectral density (PSD) as features, and the SVM with the histogram as features.
+		Classification accuracy of the fully convolutional (FCN) variant of DeepSphere, the standard convolutional (CNN) variant of DeepSphere, the support vector machine (SVM) with the power spectral density (PSD) as features, and the SVM with the histogram as features.
 		The difficulty of the task depends on the level of noise and the size of a sample (that is, the number of pixels that constitute the sample to classify).
@@
 		It is clear from those results that the noise makes the problem harder, and that having more pixels available to classify a sample makes the problem easier (the classifier having more evidence to make a decision).
-The FCN variant of HealpixNet beats the CNN variant by being invariant to rotation.
+The FCN variant of DeepSphere beats the CNN variant by being invariant to rotation.
 Both variants largely beat the two SVM baselines.
@@
 
-\figref{results} compares the classification accuracy of HealpixNet (FCN and CNN variants) and the two baselines across five noise levels and three sample sizes.
+\figref{results} compares the classification accuracy of DeepSphere (FCN and CNN variants) and the two baselines across five noise levels and three sample sizes.
 We indeed observe that the problem is made more difficult as the sample size decreases, and the noise increases.
@@
 They do not, however, include any spatial information.
-HealpixNet (both the FCN and CNN variants) shows superior performance over all configurations.
+DeepSphere (both the FCN and CNN variants) shows superior performance over all configurations.
 The gap even widens as the problem becomes more difficult.
-This is likely due to HealpixNet learning features that are adapted to the problem instead of relying on hand-designed features.
-The accuracy of HealpixNet is $>97\%$ for orders $o=1$ and $o=2$, for all noise levels, and starts to deteriorate for $o=4$, reaching 90\% for the highest noise level.
+This is likely due to DeepSphere learning features that are adapted to the problem instead of relying on hand-designed features.
+The accuracy of DeepSphere is $>97\%$ for orders $o=1$ and $o=2$, for all noise levels, and starts to deteriorate for $o=4$, reaching 90\% for the highest noise level.
 
@@
 We saw no sign of over-fitting in any of our experiments.
-With more data, HealpixNet can probably do even better.
+With more data, DeepSphere can probably do even better.
 The fact that the CNN lags behind the FCN is another sign of lack of data.
@@
 
-The main product of this contribution is HealpixNet, a small and easy-to-use python package for the spherical analysis of cosmological data.
-The code was designed so that HealpixNet can easily be used for typical machine learning tasks, such as classification and regression, both dense and global.
+The main product of this contribution is DeepSphere, a small and easy-to-use python package for the spherical analysis of cosmological data.
+The code was designed so that DeepSphere can easily be used for typical machine learning tasks, such as classification and regression, both dense and global.
 % dense: segmentation tasks, such as masking, flagging, or object detection
@@
 This allows us to leverage the advantages of the graph convolution.
-It is both efficient, with a complexity of $\bO(N_{pix})$, and flexible, which allows HealpixNet to efficiently work on parts of the sphere.
+It is both efficient, with a complexity of $\bO(N_{pix})$, and flexible, which allows DeepSphere to efficiently work on parts of the sphere.
 The spherical properties of the domain are well captured: the graph Fourier modes are close to the spherical harmonics.
 Filters are restricted to be radial for the convolution operation to be equivariant to rotation.
-HealpixNet can then be made either equivariant or invariant to rotation.
+DeepSphere can then be made either equivariant or invariant to rotation.
 Equivariance is not perfect as small imprecisions due to the sampling cause the action of a graph filter to slightly depend on the location.
@@
 The maps were produced from two cosmological models with varying $\sigma_8$ and $\Omega_m$, chosen to follow the typical weak lensing degeneracy in these parameters, so that the power spectra for these models are similar.
-We compared the performance of HealpixNet versus that of two SVM classifiers: one trained on the spherical harmonics power spectrum, and the other on the pixel density histogram.
-HealpixNet performs better than the two baselines for all considered cases.
+We compared the performance of DeepSphere versus that of two SVM classifiers: one trained on the spherical harmonics power spectrum, and the other on the pixel density histogram.
+DeepSphere performs better than the two baselines for all considered cases.
 The advantage is small for large, noise-free maps, and grows up to 10\% for smaller, noisier data.
@@
 Furthermore, the influence of irregular sampling on the convolution's equivariance to rotation should be empirically quantified and ideally theoretically bounded.
-Further comparison of HealpixNet to other spherical CNN formulations, with different sampling schemes, would also be worthwhile.
+Further comparison of DeepSphere to other spherical CNN formulations, with different sampling schemes, would also be worthwhile.
 
@@
 
-For a fair comparison between HealpixNet and the baselines, we have to ensure that the SVM classifier has access to the same amount of training data as HealpixNet.
+For a fair comparison between DeepSphere and the baselines, we have to ensure that the SVM classifier has access to the same amount of training data as DeepSphere.
 That is potentially an infinite number of samples.
@@
 
-In the following we describe the weak lensing map-making pipeline \pkg{UFalcon} (ultra fast lightcone) developed in \citep{sgier2018fastgeneration} and how it has been used to generate data used in the present work.
-The data consist of two-dimensional convergence maps on the full sphere, which represent the dimensionless, weighted and projected mass along the light of sight and determines the lensing of source galaxies an observer located on earth would see.
-
-The matter content of the universe consists mostly of dark matter and is therefore mainly responsible for the large scale structure evolution of the universe.
-The effect of weak gravitational lensing, in which the light from distant galaxies is lensed by the matter distribution between the observer and the sources, is therefore dominated by dark matter \citep[see][for a review of gravitational lensing]{bartelman2010gravitationallensing}.
-In order to obtain a convergence map characterising the gravitational lensing of distance sources, one has to start with accurate simulations of the dark matter distribution.
+In the following we describe the weak lensing map-making pipeline \pkg{UFalcon} (ultra fast lightcone) developed in \citep{sgier2018fastgeneration} and the way it was used to generate data for this work.
+The data consist of two-dimensional mass maps on the full sphere, which represent the dimensionless, weighted and projected mass along the light of sight.
+The matter content of the universe consists mostly of dark matter.
+This kind of projected mass maps are typically measured using the weak gravitational lensing technique.
+Gravitational lensing occurs when images of distant galaxies are distorted by the matter clumps between the galaxy and the observer, which act as lenses.
+Measurements of the small, spatially coherent distortions of galaxy images can be used to infer the matter density between the observer and the background galaxies.
+\citep[see][for a review of gravitational lensing]{bartelman2010gravitationallensing}.
+
+In order to obtain a convergence map characterising the gravitational lensing of distance sources, one has to start with simulations of the dark matter distribution.
 This is achieved through cosmological N-Body simulations, which evolve a chosen number of dark matter particles $N_\mathrm{part}^\mathrm{sim}$ within a specific simulation volume $V_\mathrm{sim}$ under the influence of gravity across cosmic time-scales.
@@
 The lightcone represents the volume of the universe around the observer, where the radius represents the distance the light from distant galaxies at different times and locations has to travel to the observer.
-Therefore, the particles outputted at different redshifts (time-steps) of the simulation are concentrically arranged in shells of constant redshift around the observer (each redshift $z$ corresponds to a comoving distance away from the observer $\chi(z)$), which is located at redshift $z=0$ (see Figure \ref{sketch_lightcone_simulation}).
+Therefore, the particles outputted at different redshifts (time-steps) of the simulation are concentrically arranged in shells of constant redshift around the observer (each redshift $z$ corresponds to a comoving distance away from the observer $\chi(z)$), which is located at redshift $z=0$ (see Figure \ref{fig:sketch_lightcone_simulation}).
 The shells are then weighted by a weak lensing specific weight $W_b$ and projected onto the sphere for each pixel $\theta_\mathrm{pix}$, resulting in a convergence map
@@
 
-\section{Simulation Setup}
-\label{sec:simulation_setup}
-
 The data is generated for the present analysis is based on the fast approximate N-Body simulation code \pkg{L-PICOLA} \citep{howlett2015lpicola}.

### 2018-10-23 scnn.tex
remove todolist

@@
 
-\section*{TODO list}
-\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-	\item (TK) Can we use HEALPix in the name? Check with the main author of HEALPix. MD: what about DeepCosmo or CosmoNet? NP: cosmological data is not necessarily spherical.
-	\nati{No answer from the people. Let us go for DeepSphere. Graphsphere???}
-	\item (TK) Check use of British vs American English. Check use of tense.
-	\item (MD) Figure 4: speed for multiple lmax. Not doing it.
-    \item (TK) check part sphere notebook and whole sphere
-	\item (NP \& MD) Move the git repository, rename the classes, check the links.
-    \item (Everyone should check this) Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
-	\item (fail - I checked few fonts here: \url{de.sharelatex.com/learn/Font_typefaces}, but none looked better) (TK) Font: do we have to use times (set in the documentclass)?
+% \section*{TODO list}
+% \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
+% 	\item (TK) Can we use HEALPix in the name? Check with the main author of HEALPix. MD: what about DeepCosmo or CosmoNet? NP: cosmological data is not necessarily spherical.
+% 	\nati{No answer from the people. Let us go for DeepSphere. Graphsphere???}
+% 	\item (TK) Check use of British vs American English. Check use of tense.
+% 	\item (MD) Figure 4: speed for multiple lmax. Not doing it.
+%     \item (TK) check part sphere notebook and whole sphere
+% 	\item (NP \& MD) Move the git repository, rename the classes, check the links.
+%     \item (Everyone should check this) Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
+% 	\item (fail - I checked few fonts here: \url{de.sharelatex.com/learn/Font_typefaces}, but none looked better) (TK) Font: do we have to use times (set in the documentclass)?
 I (MD) find the rendering of math a bit ugly.
@@
 We should also check which font size we can / have to use.
-\end{itemize}
+% \end{itemize}
 

### 2018-10-23 scnn.tex
small modification
final pass over the paper

@@
 The spherical CNN is constructed by representing the sphere as a graph.
-Graphs are versatile data structures which can represent pairwise relationships between objects or act as a discrete representation of a continuous manifold.
+Graphs are versatile data structures that can represent pairwise relationships between objects or act as a discrete representation of a continuous manifold.
 Using the graph-based representation, we define many of the standard CNN operations, such as convolution and pooling.
@@
 Finally, we show how learned filters can be visualized to introspect the neural network.
-Code, data, and examples are available at \url{https://github.com/SwissDataScienceCenter/DeepSphere}.
+Code and examples are available at \url{https://github.com/SwissDataScienceCenter/DeepSphere}.
 
@@
 First, the convolution should be equivariant to rotation, meaning that a rotation of the input implies the same rotation of the output.
-Sky maps are rotation invariant: rotating maps on the sphere doesn't change their interpretation.
-Only the statistics of the maps are relevant.
+Sky maps are rotation invariant: rotating maps on the sphere doesn't change their interpretation, as only the statistics of the maps are relevant.
 Depending on the task, we want the CNN to be either equivariant or invariant to rotation.
@@
 For ground-based observations this can be due to limited visibility of the sky from a particular telescope location, and for space-based instruments due to masking of the galactic plane area (see for example \figref{example_maps}).
+
+\begin{figure*}
+\includegraphics[width=\linewidth]{figure_example_maps}
+\caption{Example maps on the sphere:
+(left) the CMB temperature (K) map from Planck \citep{planck2015overview}, with galactic plane masked,
+(middle) map of galaxy number counts (number of galaxies per arcmin$^2$) in SDSS DR14 \citep{abolfathi2017sdssDR14},
+and (right) simulated weak lensing convergence map (dimensionless) simulated with DES DR1 mask \citep{des2018dr1}.
+These maps were pixelised using $N_{side} = 512$.
+The CMB and weak lensing mass maps were smoothed with Gaussian kernels with FWHM=1 deg, and the galaxy count map with FWHM=0.5 deg.
+}
+\label{fig:example_maps}
+\end{figure*}
 
@@
 We use the graph CNN formulation introduced in \citep{defferrard2016convolutional}, which can accommodate any sampling of the sphere.
-As the Equal Area isoLatitude Pixelisation (HEALPix)~\citep{gorski2005healpix} is the most popular sampling used in cosmology and astrophysics, we tailored the method to that particular sampling and call it DeepSphere.
+As the Equal Area isoLatitude Pixelisation (HEALPix)~\citep{gorski2005healpix} is a popular sampling used in cosmology and astrophysics, we tailored the method to that particular sampling and call it DeepSphere.
 DeepSphere is however easily used with other samplings as only two elements depend on it: (i) the choice of neighboring pixels when building the graph, and (ii) the choice of parent pixels when building the hierarchy.
@@
 %\nati{I am not sure this goes there...} Other recently developed sampling methods include \citep{mcewen2011novelsampling}, where exact sampling theorem for equiangular MW sampling was presented.
-
 We give a practical demonstration of DeepSphere on cosmological model discrimination using maps of projected mass distribution on the sky \citep{chang2017curvedsky}.
@@
 DeepSphere is implemented with \pkg{TensorFlow} \citep{abadi2016tensorflow} and is intended to be easy to use out-of-the-box for cosmological applications.
-Code and examples are available online.{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/DeepSphere}}}
+Code and examples are available online.{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/DeepSphere/}}}
 
@@
 % \end{itemize}
-
-\begin{figure*}
-\includegraphics[width=\linewidth]{figure_example_maps}
-\caption{Example maps on the sphere:
-(left) the CMB temperature (K) map from Planck \citep{planck2015overview}, with galactic plane masked,
-(middle) map of galaxy number counts (number of galaxies per arcmin$^2$) in SDSS DR14 \citep{abolfathi2017sdssDR14},
-and (right) simulated weak lensing convergence map (dimensionless) simulated with DES DR1 mask \citep{des2018dr1}.
-These maps were pixelised using $N_{side} = 512$.
-The CMB and weak lensing mass maps were smoothed with Gaussian kernels with FWHM=1 deg, and the galaxy count map with FWHM=0.5 deg.
-}
-\label{fig:example_maps}
-\end{figure*}
 
@@
 The simplicity of the spherical form belies the intricacy of global analysis on the sphere.
-There is no known point set which achieves the analogue of uniform sampling in Euclidean space and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions.
+There is no known point set that achieves the analogue of uniform sampling in Euclidean space and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions.
 Any existing proposition of practical schemes for the discrete treatment of such functions on the sphere introduces some systematic error dependent on the global properties of the point set.
 While our method is applicable to any pixelisation of the sphere, two details depend on the chosen sampling: (i) the choice of neighbours in the construction of the graph, and (ii) the choice of parent nodes when coarsening the graph.
-As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology, our target application, we tailor the method to that particular sampling in the subsequent exposition.
+As HEALPix~\citep{gorski2005healpix} is our target application, we tailor the method to that particular sampling in the subsequent exposition.
+\figref{example_maps} shows three examples of HEALPix maps: the Cosmic Microwave Background \citep{planck2015overview}, galaxies found in Sloan Digital Sky Survey Data Release 14 \citep{abolfathi2017sdssDR14}, and an example simulated mass map on the footprint of Dark Energy Survey Data Release 1 \citep{des2018dr1}.
 %We'll note in later sections where the method should be adapted for a different sampling.
 
-HEALPix is a particular case of a more general class of schemes which are based on a hierarchical subdivision of a base polyhedron.
+HEALPix is a particular case of a more general class of schemes based on a hierarchical subdivision of a base polyhedron.
 %Many discretized maps of the sphere are based on a hierarchical subdivision of a base polyhedron.
@@
 High-resolutions HEALPix maps easily reach millions of pixels.
-\figref{example_maps} shows two examples of HEALPix maps: the Cosmic Microwave Background \citep{planck2015overview}, galaxies found in Sloan Digital Sky Survey Data Release 14 \citep{abolfathi2017sdssDR14}, and an example simulated mass map on the footprint of Dark Energy Survey Data Release 1 \citep{des2018dr1}.
+% \figref{example_maps} shows two examples of HEALPix maps: the Cosmic Microwave Background \citep{planck2015overview}, galaxies found in Sloan Digital Sky Survey Data Release 14 \citep{abolfathi2017sdssDR14}, and an example simulated mass map on the footprint of Dark Energy Survey Data Release 1 \citep{des2018dr1}.
 
@@
 In the graph setting, the weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$, and there is one coefficient per neighborhood, not node.
-That defines radial filters, which value only depends on the distance to the center, not the direction.
+That defines radial filters, values of which depend only on the distance to the center, and not on the direction.
 It is required as there is no way to order and match nodes from the same neighborhood in a general graph.
@@
 Its radius should be large enough to capture statistics of interest.
-For example, there is a limit on how small a partial sky observation can be to give any clue about cosmological parameters.
+For example, a small a partial sky observation can provide only limited information of cosmological relevance.
 On the other hand, looking at the whole sky is often superfluous and waste computations, as most interactions are local.
@@
 Doing so assumes the data is locally independent, and form different observations of an unknown process.
-Averaging over independent observations is a common trick to reduce variance.\footnote{The variance of the averaged prediction is $\sigma^2 / n$, where $\sigma$ is the variance over one observation and $n$ is the number of independent observations.}
+Averaging over independent observations is a common way to reduce variance.
+% \footnote{The variance of the averaged prediction is $\sigma^2 / n$, where $\sigma$ is the variance over one observation and $n$ is the number of independent observations.}
+% TK: no need for this footnote, it should be general knwoledged for the readers of this journal
 An example FCN for global regression is
@@
 
-A first approach, explored by \citep{boomsma2017spherical} for molecular modeling and \citep{su2017sphericalconv, coors2018spherenet} for omnidirectional imaging, is to use a 2D CNN on a discretization of the sphere that is a grid, such as the equirectangular projection (\figref{sphere_grids} left), or a set of grids, such as the cubed-sphere defined by~\citep{ronchi1996cubed} (\figref{sphere_grids} middle).
+A first approach, explored by \citep{boomsma2017spherical} for molecular modeling and \citep{su2017sphericalconv, coors2018spherenet} for omnidirectional imaging, is to use a 2D CNN on a discretization of the sphere that is a grid, such as the equirectangular projection (\figref{sphere_grids}, left panel), or a set of grids, such as the cubed-sphere defined by~\citep{ronchi1996cubed} (\figref{sphere_grids},  middle panel).
 As this formulation uses the standard 2D convolution, all the optimizations developed for images can be applied, what makes it computationally efficient.
@@
 By this choice, DeepSphere is trained with the same amount of information, i.e., the number of pixels, across all variants of the problem.
-Training took approximately $1.5$ hour using a single Nvidia GeForce GTX 1080 Ti ($5$ hours with a Tesla K20).
+Training took approximately $1.5$ hour using a single Nvidia GeForce GTX 1080 Ti and $5$ hours with a Tesla K20.
 % Could probably be faster with a better input pipeline.
@@
 Hence, a pixel can be statistically classified using only its surrounding, and those local predictions can be averaged to vote for a global consensus.
-The CNN variant may however be better for data not having this property, and one should always adapt the architecture to the data and task (see \secref{architecture}).
-
-We saw no sign of over-fitting in any of our experiments.
-With more data, DeepSphere can probably do even better.
-The fact that the CNN lags behind the FCN is another sign of lack of data.
-ImageNet, the largest dataset for visual object recognition, features about 900 billion pixels ($14 \times 10^6 \times 256^2$), to be compared with the 750 millions pixels ($60 \times 12 \times 1024^2$) of our dataset.
+The CNN variant, however, may be better for data that does not have this property, as the architecture should always be adapted to the data and task (see \secref{architecture}).
+% and one should always adapt the architecture to the data and task (see \secref{architecture}).
+
+% We saw no sign of over-fitting in any of our experiments.
+% With more data, DeepSphere can probably do even better.
+% The fact that the CNN lags behind the FCN is another sign of lack of data.
+% ImageNet, the largest dataset for visual object recognition, features about 900 billion pixels ($14 \times 10^6 \times 256^2$), to be compared with the 750 millions pixels ($60 \times 12 \times 1024^2$) of our dataset.
+% TK: removing this paragraph, sounds too spectulative <- not strictly necessary for the paper
 
@@
 Details of how the convolution kernels are plotted are described in \ref{sec:filter_visualization}.
-While it is usually difficult to interpret the shape of the filters, especially given the type of data, we can notice that they often have a ``peak'' like structure.
+While it is usually difficult to interpret the shape of the filters, especially given the type of data, we can notice that they often have a ``peak''-like structure.
 An example of filter interpretation was demonstrated in \citep{Ribli2018learningfrom}.
@@
 
-The main product of this contribution is DeepSphere, a small and easy-to-use python package for the spherical analysis of cosmological data.
+We present DeepSphere, a novel convolutional neural network defined on the sphere with HEALPix sampling, designed for the analysis of the cosmological data.
+We publish the code as a small and easy-to-use python package.
 The code was designed so that DeepSphere can easily be used for typical machine learning tasks, such as classification and regression, both dense and global.
@@
 $7680$ respectively for order $o=1,2,4$ is considered small to train a deep architecture,
-especially when one desire to build a noise robust
-classifier. As a result, we use a classical dataset augmentation technique.
+especially when one desire to build a classifier that is robust to noise.
+As a result, we use a classical dataset augmentation technique.
 Before entering the network for training each sample is added a random

### 2018-10-23 scnn.tex
removed comments from latex

@@
 
-%Convolutional Neural Networks (CNNs) are becoming an important analysis tool in cosmology and astrophysics.
-% MD: useful info? To me this is not an argument for our approach. Maybe we have to expand it?
-
-% Architectures are then designed similarly to the classical CNNs used for image analysis.
-% HealpixNet uses Tensorflow as the underlying engine and can utilize most of it functionalities.
-% MD: not relevant for the abstract in my opinion
-
 Convolutional Neural Networks (CNNs) are a cornerstone of the Deep Learning toolbox and have led to many breakthroughs in Artificial Intelligence.
@@
 This way, DeepSphere is a special case of a graph CNN, tailored to the HEALPix sampling of the sphere.
-% TBD if we include it
 This approach is computationally more efficient than using spherical harmonics to perform convolutions.
-% An advantage of the graph representation is that the convolution operations are efficient, which enables the CNN to run fast.
 We demonstrate the method on a classification problem of mass maps from two cosmological models and compare the performance of the CNN with that of two baseline classifiers, based on the power spectrum and pixel density histogram.
@@
 
-%As a response to that fact, we are witnessing an increasing interest in the generalization of CNNs to graphs.
-% Graphs are versatile data structures which can represent pairwise relationships between objects or act as a discrete representation of a continuous manifold.
-% In this paper we take the latter view and represent a sampled sphere as a graph, for which we define the convolution and pooling operations.
-% Spherical maps appear in many applications, such as the study of phenomena on the Earth for meteorologists or on the sky for cosmologists.
-% A popular format for spherical maps is HEALPix, which uses an equal-area, isolatitude sampling.
-% Hence, we present a spherical CNN for analysis of full and partial HEALPix maps, which we call DeepSphere.
-% \nati{I am not that we should talk about pooling in the abstract.
-Another angle would be to say that HEALPix sampling is well suited for spherical CNN with graphs as a) it is very regular => the graph capture well the spherical structure of the Manifold and b) pooling is natural.}
-% While the convolution on arbitrary graphs has mostly been sorted out, a general pooling operation has not been discovered so far.
-% As such, while DeepSphere is a special case of a graph CNN, it is tailored to the HEALPix sampling of the sphere.
-% This approach is computationally much more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
-% The filters learned by the DeepSphere are restricted to being radial.
-% Michaël: not necessary in the abstract?
-% We demonstrate the method on a classification problem of mass maps from two cosmological models.
-% \nati{Should we specify what are the baselines? I think not.}
-% A standard benchmark for that problem is to train an SVM on the histograms of map pixel values. Another is to use the power spectral density instead.
-% DeepSphere achieves \todo{xx\%} better accuracy than those baselines, is more robust to noise, and is \todo{faster?}.
-% Code and examples are available at \todo{\url{https://github.com/xxx}}.
 \end{abstract}
@@
 
-% \section*{TODO list}
-% \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
-% 	\item (TK) Can we use HEALPix in the name? Check with the main author of HEALPix. MD: what about DeepCosmo or CosmoNet? NP: cosmological data is not necessarily spherical.
-% 	\nati{No answer from the people. Let us go for DeepSphere. Graphsphere???}
-% 	\item (TK) Check use of British vs American English. Check use of tense.
-% 	\item (MD) Figure 4: speed for multiple lmax. Not doing it.
-%     \item (TK) check part sphere notebook and whole sphere
-% 	\item (NP \& MD) Move the git repository, rename the classes, check the links.
-%     \item (Everyone should check this) Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
-% 	\item (fail - I checked few fonts here: \url{de.sharelatex.com/learn/Font_typefaces}, but none looked better) (TK) Font: do we have to use times (set in the documentclass)?
-I (MD) find the rendering of math a bit ugly.
-MD: lmodern is better, but can we use it (w.r.t.\ journal policy)?
-If equations split out, we can try to arrange them.
-We should also check which font size we can / have to use.
-% \end{itemize}
-
 \begin{figure*}
 	\centering
-    % \includegraphics[width=\linewidth]{architecture}
 	\includegraphics[width=\linewidth]{figure_architecture_v3}
@@
 
-% Structure:
-  % High-level intro
-  % Desiderata for a method
-  % Related methods / previous work
-  % Our method
-  % Experiments
-
 Cosmological and astrophysical data often come in the form of spherical sky maps.
@@
 
-% cohen2017convolutional (ICML workshop) and cohen2018sphericalcnn (ICLR best paper) are redundant
 One direction to generalize CNNs to spherical data is to apply a standard 2D CNN to a grid discretisation of the sphere~\citep{boomsma2017spherical,su2017sphericalconv,coors2018spherenet}.
@@
 
-% MD: I don't see what the following brings to the paper.
-% This work is the first to design a spherical convolutional neural network for cosmological applications.
-% Previously, several other machine learning algorithms were extended to the sphere, often also including the third, radial direction.
-% Most notably, sparsity-based methods were developed, such as wavelets \citep{Leistedt2013flaglets,Leistedt2015spinwavelets}, ridgelets \citep{McEwen2015ridgelet} and curvelets \citep{Chan2017curvelets,Starck2009polarized}.
-
 Our spherical CNN leverages convolutions on graphs and hierarchical pooling to address all three identified shortcomings: (i) rotation equivariance, (ii) computational efficiency, and (iii) partial sky observations.
@@
 Our pooling strategy exploits a hierarchical pixelisation of the sphere to analyse the data at multiple scales.
-% Compared with~\citep{khasanova2017graphomni}, our work does not need hand-chosen statistics nor dynamic pooling.
 We use the graph CNN formulation introduced in \citep{defferrard2016convolutional}, which can accommodate any sampling of the sphere.
@@
 
-%\nati{I am not sure this goes there...} Other recently developed sampling methods include \citep{mcewen2011novelsampling}, where exact sampling theorem for equiangular MW sampling was presented.
 We give a practical demonstration of DeepSphere on cosmological model discrimination using maps of projected mass distribution on the sky \citep{chang2017curvedsky}.
@@
 
-% MD: I usually find those paragraphs boring and skip them when reading. Our intro is long enough already. Feel free to add it back if you think it's necessary.
-%The paper is organized as follows.
-%In \secref{related_work}, we describe existing approaches to convolutions on spheres, graphs, and manifolds.
-%\secref{method} exposes the construction of a graph given the HEALPix sampling of a sphere and defines the convolution operation.
-%Finally, \secref{experiments} presents our experimental results on the weak lensing mass map classification problem. There we compare our method to two standard benchmarks and show its superiority.
-%We conclude in \secref{conclusion}.
-
-% Cite the following papers:
-% \begin{itemize}
-%     \item HEALPix paper \citep{gorski2005healpix}
-%     \item First DES mass maps \citep{chang2017curvedsky}
-%     \item HEALPix convolutions with asymetric beams \citep{mitra2011fastpixel}
-%     \item Mass mapping on the sphere \citep{wallis2017mappingdark}
-%     \item Wavelets on the sphere \citep{leistedt2016wavelet} and ball \citep{leistedt2012exactwavelets}
-%     \item Planck main result \citep{planck2015cosmologicalparameters,komatsu2011sevenyear}
-%     \item HI map \citep{HI4PI2016fullskyHI,}
-%     \item more radio maps from Adam+Hamsa \citep{santos2015cosmologySKA}
-%     \item more astro science on the sphere, what other survey make maps?
-%     \item alternative sampling on the sphere \citep{mcewen2011novelsampling} MW sampling
-%     \item cite kids tomographic power spectrum \citep{koehlinger2017kidstomographic}
-% \end{itemize}
-
-% \subsection{Potential applications}
-%   \assign{Tomek, Nathanaël, Michaël}
-
-% The analysis of spherical cosmological data, such as the cosmic microwave background \cite{...}, as done in \cite{he2018analysis}, is the target application of our method.
-
-% While our method was developed with cosmology in mind, it can easily target any problem where data live on a sphere.
-Examples include, but are certainly not limited to, (i) efficient compression and decompression of \ang{360} videos (see \cite{su2017learning}), (ii) \todo{data analysis on planets?
-(climate, forecasting, temperature, wind)}, (iii) \todo{particle physics?
-(jets on detectors, but they are usually cylindrical)}, (iv) \todo{applications in Cohen's papers?}.
-
-% Finally, not that those neural networks are not restricted to the sphere and can be applied to any problem where we have data on a graph, such as social, biological or infrastructure networks [some citations, e.g.
-brain Alzeihmer, particle physics, computer graphics].
-% the convolution is not restricted to the sphere, the coarsening/pooling is
-
 \section{Method}
 \label{sec:method}
-% \begin{itemize}
-%   \item We build a graph using the healpix sampling
-%   \item Define Fourier transform and show that the harmonics are visually close to the spherical harmonics
-%   \item Define spherical convolution using the graph Fourier transform and show heat diffusion example
-%   \item Show the limits of the approach and explain why we cannot have a perfect spherical convolution with this technique
-% \end{itemize}
 
@@
 
-% \begin{figure}
-%     \centering
-%     \begin{subfigure}[b]{0.45\linewidth}
-%         \centering
-%         \includegraphics[width=\linewidth]{exampleEarthTopo}
-%         \caption{}
-%         \label{fig:example_earth}
-%     \end{subfigure}
-%     \hfill
-%     \begin{subfigure}[b]{0.45\linewidth}
-%         \centering
-%         \includegraphics[width=\linewidth]{exampleCMB}
-%         \caption{}
-%         \label{fig:example_cmb}
-%     \end{subfigure}
-%     \caption[]{Example of (a) an Earth topography map composed of \textasciitilde 3 million pixels (\textasciitilde 7 arcmin resolution) and (b) a model of the Cosmic Microwave Background (CMB) radiation temperature anisotropy, composed of \textasciitilde 13 million pixels (\textasciitilde 3.4 arcmin resolution).\footnotemark}
-%     \label{fig:example_maps}
-% \end{figure}
-
 Before doing any numerical analysis on the sphere, one first has to choose a tessellation, i.e., an exhaustive partition of the sphere into finite area elements, where the data under study is quantized.
@@
 \figref{example_maps} shows three examples of HEALPix maps: the Cosmic Microwave Background \citep{planck2015overview}, galaxies found in Sloan Digital Sky Survey Data Release 14 \citep{abolfathi2017sdssDR14}, and an example simulated mass map on the footprint of Dark Energy Survey Data Release 1 \citep{des2018dr1}.
-%We'll note in later sections where the method should be adapted for a different sampling.
 
 HEALPix is a particular case of a more general class of schemes based on a hierarchical subdivision of a base polyhedron.
-%Many discretized maps of the sphere are based on a hierarchical subdivision of a base polyhedron.
 Another example is the geodesic grids which are based on geodesic polyhedrons, i.e., polyhedrons made of triangular faces.
@@
 
-% HEALPix is an acronym for Hierarchical Equal Area isoLatitude Pixelization of a sphere.
 The HEALPix pixelisation produces a hierarchical subdivision of a spherical surface where each pixel covers the same surface area as every other pixel.
@@
 High-resolutions HEALPix maps easily reach millions of pixels.
-% \figref{example_maps} shows two examples of HEALPix maps: the Cosmic Microwave Background \citep{planck2015overview}, galaxies found in Sloan Digital Sky Survey Data Release 14 \citep{abolfathi2017sdssDR14}, and an example simulated mass map on the footprint of Dark Energy Survey Data Release 1 \citep{des2018dr1}.
 
@@
 \figref{healpix_graph_4} shows a graph constructed from the HEALPix sampling of a sphere.
-
-% mdeff: Why not $1/d$? See Pascal's paper
-% nati: The question is: is $1/d$ also good when we have 7/8 neighbors instead of 4?
-Practically, we can also use $1/d$, but that means changing the code and re-runing the experiment.
-We probably do not have to change any parameter though...
-@mdeff: do you think we should try this for this paper?
-Or we keep that for the next one.
-% mdeff: I tried and the eigenvectors and eigenvalues are mostly the same.
-To me, there is no point in trying for trying.
-We should rather come up with a definition of distance that will make the eigenvectors closer to the real spherical harmonics.
-% Agreed: I added a reference to Pascal paper.
 
@@
 where $T_i g[j] = g[i-j]$ is, up to a flip, a translation operator.
-% nati: I think now the indexing is clear and will not confuse with the rest of the paper.
 Similarly as \eqnref{graph_convolution_spatial}, the convolution of the signal $f$ by a kernel $g$ is the scalar product of $f$ with translated versions $T_i g$ of the kernel $g$.
-% Signals and kernels are the same thing in classical signal processing precisely because there exists a proper definition of translation.
-% For Michael: I know what you mean here, but it is slightly more complicated than that.
 Additionally, it turns out that the localization operator $\T_i h$ is a generalization of the translation operator on graphs.
@@
 As no efficient and general fast Fourier transform (FFT) exists for graphs \citep{le2018fgft}, the execution of the Fourier transform by multiplication of the signal $\f$ by the dense matrix $\U$ costs $\bO(N_{pix}^2)$ operations.
-% \footnote{See \citep{le2018fgft} for a comparison between the polynomial definition of filters presented here and a class of fast graph Fourier transforms based on the approximation of the Fourier basis $\U$ by a product of sparse matrices.}
-% TK: I would just cite the paper, we have not introduced the polynomials at this stage yet.
 In a neural network, this operation has to be performed for each forward and backward pass.
@@
 \end{equation}
-% NP: Should we take a single vertex and explain what happens to it?
 where $\L^k$ captures $k$-neighborhoods.\footnote{The 1-neighborhood of a node is the set of nodes that are directly connected to it.
@@
 On the contrary, the amplitude of the monomials $x^k$ is very different for $|x|\approx 0$ and $|x| \approx 1$.}
-% MD: SGD implicitly imposes a uniform prior on the learned parameters.
-% Moreover, they factor out $\tL^{k-2}$ from $T_k(\tL)$, e.g., the 3-neighborhood is not mixed with the 5-neighborhood.
-% That results in an easier optimization of the parameters $\theta$.
 Moreover, the coefficients can be computed such as the truncated Chebyshev expansions is an approximate minimax polynomial of a given filter \citep{hammond2011wavelets}.
 While that is irrelevant when learning filters, it is useful for example when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
-% \todo{numerical stability of $\L^k \f$ v.s. $T_k(\L) \f$}
-% NP: we should not give much more details here. If we do an experiment, we can comment in the experiment section.}
 Finally, note that while the graph convolution \eqnref{graph_convolution_fourier} is motivated in the spectral domain, definitions \eqnref{graph_convolution_monomial} and \eqnref{graph_convolution_cheby} are implementations in the vertex domain.
@@
 Exploiting the recursive formulation of Chebyshev polynomials, evaluating \eqnref{graph_convolution_cheby} requires $\bO(K)$ multiplications of the vector $\f$ with the sparse matrix $\tL$.
-% In our case, the Laplacian is extremely sparse, with 8 to 9 entries per line (out of $N_{pix}$).
 The cost of one such multiplication is $\bO(|\E| + |\V|)$.
@@
 
-% The advantage of schemes based on a base polyhedron is that cells are equal-area.
-While that is not required for the convolution operation when modeling with graphs (it can be corrected by setting edge weights appropriately, see \citep{khasanova2017graphomni})
-% nope: can also do a regular pooling on the equirectangular. It preserves the sampling, and the convolution is adapted to the sampling thanks to the edge weights.
-
 \begin{figure}
@@
 
-% The statistical layer was used in the end. The FCN is a more principled approach.
-
-% \subsection{Statistical layer}
-% Or Global pooling?
-
-% Following \citep{khasanova2017tigranet}, we implement an optional statistical layer between the last graph convolutional layer and the first fully connected layer for the neural network.
-% This introduces the invariance of the output to isometric transformations, such as rotation of maps on the sphere.
-% The role of the layer is to compute global and location independent statistics from feature maps.
-% Besides providing invariance, the layer drastically compresses the representation of the data as the number of computed statistics $N_{stat}$ is usually much smaller than the size of the map $N_{pix}$.
-That compression results in much smaller fully connected layers, which usually contain a significant fraction of trainable parameters of a neural network.
-% The invariance and reduced representation should help the network to learn from fewer samples and to generalize better to unseen data.
-Yet another advantage is that a network built with such a statistical layer is agnostic to the size of the input data, i.e., it can classify maps which do not have the same number of pixels.
-Indeed, such global summarization is invariant to node permutation and is commonly used along graph convolutions to classify graphs of varying sizes \citep{duvenaud2015gcn, li2015gatedgnn}.
-%
-% Given a feature map $\x \in \R^{N_{pix}}$, the statistical layer is defined as
-% \begin{equation} \label{eqn:stat_layer}
-% 	\y = f(\x) \in \R^{N_{stat}},
-% \end{equation}
-% where $f$ computes $N_{stat}$ statistics which are independent from the size of the map, $N_{pix}$.
-An example is the global average pooling $f(\x) = \esp(\x)$, introduced by \citep{lin2013globalavgpooling}, where $\esp(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} x_i$ is the empirical mean.
-Another example is $f(\x) = [\esp(\x), \var(\x)]\trans$, where $\var(\x) = \frac{1}{N_{pix}} \sum_{i=1}^{N_{pix}} (x_i - \esp(\x))^2$ is the empirical variance.
-% Other statistical layers are also possible.
-% In particular, we also implement a \emph{learned histogram} statistic \citep{wang2016learnhist}.
-% Other approaches, which we did not implement, may include applying different diffusion on the final maps to obtain statistics at different scales, as proposed by \citep{khasanova2017tigranet}.
-
 \subsection{Layers}
@@
 Neural networks are constructed as stacks of layers which sequentially transform the data from its raw representation to some predictions.
-% decision on the class label
 The general DeepSphere architecture, pictured in \figref{architecture}, is composed of many layers.
@@
 The tail is composed of multiple fully connected layers (FC) followed by an optional softmax layer (SM).
-% A statistical layer (ST) is optionally inserted between the convolutional head and the fully connected tail.
-
-% As such, we will not mention the non-linearity in the description of our architectures.
 A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer where it is set to the identity.
@@
 As such, a GC layer is composed of $F_{in} \times F_{out}$ filters, each parameterized by $K$ numbers (see \secref{efficient_convolution}). A bias term $\b b \in \R^{F_{out}}$ is jointly optimized.
-% only if batch normalization is not used
 
@@
 The empirical expectation $\esp(\x_i) \in \R$ and variance $\var(\x_i) \in \R$ are taken across training examples and pixels.
-% the action of gamma can be done by the filters of the next layer
-
-% The statistical layer, defined in \eqnref{stat_layer}, independently transforms each of the $F$ feature maps of the input $\X \in \R^{N_{pix} \times F}$ into $\Y = ST(\X) \in \R^{N_{stat} \times F}$, where $N_{stat}$ is the number of statistics.
-One may even omit the FC layers and directly fed the output of the ST layer into the softmax layer, as proposed by \citep{lin2013globalavgpooling}.
-In this regime, $N_{stat} = 1$ and $F = N_{classes}$ is the number of classes to discriminate (i.e., the last GC layer outputs as many feature maps as there is classes).
 
@@
 
-% FCN for dense
-
 Fully convolutional networks (FCNs) have been introduced by  \citep{long2015fcn} and are mostly used for the semantic segmentation of images, a dense classification task.
@@
 On the other hand, looking at the whole sky is often superfluous and waste computations, as most interactions are local.
-% most data generating processes have a small-support autocorrelation function.
 A data and task dependent trade-off is to be found.
@@
 
-% FCN for global
-
 Global tasks can be solved by averaging dense predictions \citep{lin2013globalavgpooling, springenberg2014allconv}.
 Global averaging is computed by the layer $AV: \R^{N_{pix} \times F} \rightarrow \R^F$.
-% good performance was demonstrated for object recognition in images \citep{springenberg2014allconv}.
 Doing so assumes the data is locally independent, and form different observations of an unknown process.
 Averaging over independent observations is a common way to reduce variance.
-% \footnote{The variance of the averaged prediction is $\sigma^2 / n$, where $\sigma$ is the variance over one observation and $n$ is the number of independent observations.}
-% TK: no need for this footnote, it should be general knwoledged for the readers of this journal
 An example FCN for global regression is
@@
 Rotation invariance means that rotating the input does not impact the prediction.
-
-% CNN for global
 
@@
 Than can be seen as intrinsic data augmentation, as a CNN would need to see many rotated versions of the same data to learn the invariance.
-% Contrast the number of parameters to be learned in a FC layer versus the static AV layer.
-% FCNs are more sample efficient.
 Moreover, FCNs can accommodate maps with a varying number of pixels.
@@
 
-% classification
-
 All the above architectures can be used for classification (instead of regression) by appending a SM layer.
@@
 
-%\subsection{Learning}
 \subsection{Training}
-%\subsection{Optimization}
 
@@
 For samplings that are not equal area, such as the equirectangular projection, the convolution operation should be adjusted to take the induced distortion into account \citep{su2017sphericalconv, coors2018spherenet}.
-% Furthermore, the grid requirement makes it impossible for the convolution to capture the spherical properties of the domain, i.e., the cubed-sphere sampling is by definition adapted to a cube and not to a sphere.
-% MD: Nope, the graph can adapt to any sampling. And we're not arguing about sampling schemes.
 
@@
 Therefore, a convolution operation has to be isotropic to be equivariant to rotation.
-
-% Moreover, when different grids require different filters as their orientation is not compatible.
-% => same as for tangent planes
 
@@
 The filters defined in \eqnref{graph_convolution_monomial} and \eqnref{graph_convolution_cheby}, by being polynomials of the Laplacian, are of this kind.
-% \todo{Pooling in the spectral domain? \citep{esteves2017sphericalcnn} do something.}
-% While a comparison is theoretically possible, the experiments of~\cite{cohen2018sphericalcnn} are done using the geodesic grid sampling set and do not provide any code for the HEALPix one.
-Hence, a practical comparison is not possible.
 
@@
 One could still fill the unseen part of the sphere with zeros, and avoid computing empty integrals.
-% on the latitude or longitude for SHTs, on square holes for 2D CNNs
 It is, however, not straightforward to identify empty space, and computations would still be wasted.
@@
 The use of a graph to model the discretised sphere was also considered for omnidirectional imaging \citep{khasanova2017graphomni}.
-% The authors map omnidirectional images onto a sphere, with the goal of correcting for distortions induced by the lens, which was used for their acquisition.
-% First, similarly to~\citep{boomsma2017spherical}, they use an equirectangular grid sampling.
 This work is the closest to our method, with three differences.
@@
 As the convolution is motivated by a multiplication in the graph Fourier spectrum, it is close in spirit, and empirically, to the formulation based on the spherical harmonics, which is the ideal rotation equivariant formulation.
-% and study its equivariance properties.
-
-% Main interpretations: GSP, Bronstein manifold tangent plane, message passing, permutation invariant aggregation, spatial ordering and matching
 
@@
 Another trend, parallel to the modelling of structured data, is the use of graph neural networks for relational reasoning \citep{battaglia2018review}.
-% scientifically and industrially motivated applications
 
@@
 The classification methods were trained to predict a label from a HEALPix map.
-% Both our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/DeepSphere}}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are openly available online.
-Furthermore, Jupyter notebooks demoing the method and problem can be run from your browser without installing anything.
 Our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/DeepSphere}}} to reproduce those experiments are openly available online.
@@
 	\centering
-	% \includegraphics[width=0.75\linewidth]{smooth_map_class_1}
-	% trim=left bottom right top
 	\includegraphics[width=0.48\linewidth]{figure_kappa_diff_model1}
 	\hfill
-	% \includegraphics[width=0.75\linewidth]{smooth_map_class_2}
 	\includegraphics[width=0.48\linewidth]{figure_kappa_diff_model2}
@@
 
-% \begin{figure}
-% \centering
-% \includegraphics[width=\linewidth]{part_sphere}
-% \caption{Three parts of the sphere with different sizes. Blue: $o=1$. Green: order $o=2$. Yellow: order $o=4$.}
-% \label{fig:part_sphere}
-% \end{figure}
-
 To make the discrimination harder and the problem more realistic, centered Gaussian noise is added to the simulated maps.
@@
 That is a data augmentation scheme, as it creates more training examples than we have simulations.
-% Nati: Not done anymore
-% To improve the stability of the spherical CNN, we slowly increase the amount of noise added to the training data over the iterations.
 
@@
 \subsection{Network architecture and hyper-parameters}
-%\subsection{Selected network architecture}
-%\subsection{Methods} % baselines and DeepSphere together
 
@@
 Training took approximately $1.5$ hour using a single Nvidia GeForce GTX 1080 Ti and $5$ hours with a Tesla K20.
-% Could probably be faster with a better input pipeline.
 
@@
 The CNN variant, however, may be better for data that does not have this property, as the architecture should always be adapted to the data and task (see \secref{architecture}).
-% and one should always adapt the architecture to the data and task (see \secref{architecture}).
-
-% We saw no sign of over-fitting in any of our experiments.
-% With more data, DeepSphere can probably do even better.
-% The fact that the CNN lags behind the FCN is another sign of lack of data.
-% ImageNet, the largest dataset for visual object recognition, features about 900 billion pixels ($14 \times 10^6 \times 256^2$), to be compared with the 750 millions pixels ($60 \times 12 \times 1024^2$) of our dataset.
-% TK: removing this paragraph, sounds too spectulative <- not strictly necessary for the paper
 
@@
 While those particular filters were obtained from the experiment with order $o=2$ and a relative noise level of $2$, all trained networks presented visually similar patterns.
-% The gnomonic projection clearly exhibits the sampling issue of HEALPix.
-% \TK{what issue? Commenting out for now}
 Details of how the convolution kernels are plotted are described in \ref{sec:filter_visualization}.
@@
 An example of filter interpretation was demonstrated in \citep{Ribli2018learningfrom}.
-% Nati: Note that filter are almost not evolving during the training process.
-It is not surprising as our architecture is likely to be overparametrized.
-If we want to have interpretable filters, we probably have to use a much smaller architecture.
 
@@
 The code was designed so that DeepSphere can easily be used for typical machine learning tasks, such as classification and regression, both dense and global.
-% dense: segmentation tasks, such as masking, flagging, or object detection
 The core of our method is the use of a graph to represent the discretised sphere.
@@
 With this work, we hope to demonstrate and help democratize the use of those tools for spherical data analysis.
-% Fields: planets, molecules?, atoms.
 
@@
   Relative difference between graph convolution and spherical smoothing: $10.4$\%, $4.8$\%, $3.8$\%.
-% nati: I commented this issue as this is already in appendix and it will go a bit too far. We will not do an appendix of appendix :-).
-% \todo{The main issue with our filters is that their shape depends on the localization.
-It would be nice to measure the expectation and variance of the error over all locations.
-That would show how severe the distortion is.}
-% \nati{Let us keep that for the next paper. I am quite sure, it is negligible in this particular case.}
 }
@@
 \todo{not ideal tho as the graph convolution depends on the localization}
-
-% \section{Filter visualization}
-% \label{sec:filter_visualization}
 
@@
 We plot the section of the convoluted Kroneker.
-% To do so, we convolve a Kroneker on the equator and use the equator for our section as shown in~\figref{index_section}.
 To do so, we convolve a Kroneker on the nodes along the equator and use the equator for our section.
 Note that, because of the small irregularities in the HEALPix sampling, the second and the third methods are subject to small variations depending on the chosen position of the Kroneker.
-
-% \begin{figure}
-% \centering
-% \includegraphics[width=0.6\linewidth]{index_plotting_order20_nside16}
-% \caption{Indexes selected for the section ploting of \figref{gaussian_filters_visualization} middle. The delta was placed on the yellow node.}
-% \label{fig:index_section}
-% \end{figure}
 
@@
 
-% The validation set remain the same and is used for cross-validation to tune the L2 penalization parameter of SVM.
-% Eventually, we evaluate the final classifier on the test set.
-
 \begin{figure}
@@
 \section*{Bibliography}
-% \bibliographystyle{elsarticle-harv}
 \bibliographystyle{elsarticle-num}

### 2018-10-24 scnn.tex
edits following comments from Andreas

@@
 
-\hypersetup{draft}
+% \hypersetup{draft}
 % Disable hyperlinks to prevent cross-page link failures.
@@
 Cosmological information contained in these maps is usually extracted using summary statistics, such as the power spectra or higher order correlation functions.
-Convolutional Neural Networks (CNN) have been proposed as an alternative analysis tool in cosmology thanks to its ability to automatically design relevant statistics to maximise the precision of the parameter estimation
+Convolutional Neural Networks (CNNs) have been proposed as an alternative analysis tool in cosmology thanks to their ability to automatically design relevant statistics to maximise the precision of the parameter estimation
 \citep{schmelze2017cosmologicalmodel,luciesmith2018machinelearning,gupta2018nongaussianinformation,gillet2018deeplearning,hassan2018reionizationmodels,aragoncalvo2018classyfyinglarge,ciuca2017cnnstring,ravanbakhsh2017estimating}.
-This is possible as neural networks have the capacity to build rich models and capture complicated, non-linear patterns, which are often present in the data.
-CNNs are particularly well suited for analysis of cosmological data as their trainable weights are shared across the domain, i.e., the network does not have to relearn to detect objects or features at every spatial location.
+This is possible as neural networks have the capacity to build rich models and capture complicated non-linear patterns often present in the data.
+CNNs are particularly well suited for the analysis of cosmological data as their trainable weights are shared across the domain, i.e., the network does not have to relearn to detect objects or features at every spatial location.
 
@@
 The main challenge in designing a CNN on the sphere is to define a convolution operation that is suitable for this domain, while taking care of the necessary irregular sampling.
-Moreover, the designed convolution, and resulting neural network, should possess the following three key characteristics.
+Moreover, the designed convolution and resulting neural network should possess the following three key characteristics.
 First, the convolution should be equivariant to rotation, meaning that a rotation of the input implies the same rotation of the output.
@@
 
-One direction to generalize CNNs to spherical data is to apply a standard 2D CNN to a grid discretisation of the sphere~\citep{boomsma2017spherical,su2017sphericalconv,coors2018spherenet}.
+Three ways of generalizing CNNs to spherical data have been pursued.
+One approach is to apply a standard 2D CNN to a grid discretisation of the sphere~\citep{boomsma2017spherical,su2017sphericalconv,coors2018spherenet}.
 An alternative is to divide the sphere into small chunks and project those on flat 2D surfaces \citep{fluri2018deep,gupta2018nongaussianinformation,schmelze2017cosmologicalmodel,gillet2018deeplearning}.
 While these approaches use the well-developed 2D convolution and hierarchical pooling, they are not equivariant to rotation.
-Another direction is to leverage the spherical Fourier transform and to perform the convolution associated to the SO(3) rotation group in the spectral domain, thanks to the convolution theorem \citep{cohen2018sphericalcnn, esteves2017sphericalcnn}.
+Another way is to leverage the spherical Fourier transform and to perform the convolution associated to the SO(3) rotation group in the spectral domain, thanks to the convolution theorem \citep{cohen2018sphericalcnn, esteves2017sphericalcnn}.
 While the resulting convolution is equivariant to rotation, this approach is computationally expensive, even if a fast spherical Fourier transform is used.
@@
 The main idea is to model the discretised sphere as a graph of connected pixels: the length of the shortest path between two pixels is an approximation of the geodesic distance between them.
-This approach is enabled by recent developments in graph signal processing, where fundamental tools, such as the Fourier transform, were defined for graphs \citep{shuman2013emerging}.
-The graph convolution has been explored previously for omnidirectional imaging \citep{khasanova2017graphomni}, with a different down-sampling operation.
-Our pooling strategy exploits a hierarchical pixelisation of the sphere to analyse the data at multiple scales.
-We use the graph CNN formulation introduced in \citep{defferrard2016convolutional}, which can accommodate any sampling of the sphere.
-As the Equal Area isoLatitude Pixelisation (HEALPix)~\citep{gorski2005healpix} is a popular sampling used in cosmology and astrophysics, we tailored the method to that particular sampling and call it DeepSphere.
+% This approach is enabled by recent developments in graph signal processing, where fundamental tools, such as the Fourier transform, were defined for graphs \citep{shuman2013emerging}.
+% The graph convolution has been explored previously for omnidirectional imaging \citep{khasanova2017graphomni}, with a different down-sampling operation.
+We use the graph CNN formulation introduced in \citep{defferrard2016convolutional}, and a pooling strategy that exploits a hierarchical pixelisation of the sphere to analyse the data at multiple scales.
+As the Equal Area isoLatitude Pixelisation (HEALPix)~\citep{gorski2005healpix} is a popular sampling used in cosmology and astrophysics, we tailored the method to that particular sampling.
 DeepSphere is however easily used with other samplings as only two elements depend on it: (i) the choice of neighboring pixels when building the graph, and (ii) the choice of parent pixels when building the hierarchy.
@@
 Our maps are similar to the ones used by \citep{schmelze2017cosmologicalmodel}.
-In a simplified scenario, we classify partial convergence maps into two cosmological models.
+In a simplified scenario, we classify partial sky convergence maps into two cosmological models.
 These models were designed to have very similar angular power spectrum.
@@
 \end{equation}
-where $h(\bLambda)$ is a diagonal matrix where $h(\bLambda)_{ii} = h(\bLambda_{ii})$, and $h(\bLambda) \hat{\f}$ is the spectral representation of $\f$ after filtering.
+where $h(\bLambda)$ is a diagonal matrix where $h(\bLambda)_{ii} = h(\bLambda_{ii})$.
 
@@
 
-In \ref{sec:heat_diffusion}, we show that the diffusion of heat on a graph can be expressed as the convolution of an initial condition $f$ with a heat kernel $h$.
-It should hopefully shed some light on the meaning of the convolution on a graph.
+To shed some light on the meaning of the convolution on a graph, we show in \ref{sec:heat_diffusion} that the diffusion of heat on a graph can be expressed as the convolution of an initial condition $\f$ with a heat kernel $h$.
 
@@
 
-While \eqnref{graph_convolution_fourier} is a theoretically well justified definition of the convolution of a graph signal $\f$ by a kernel $h$, it is computationally cumbersome.
+While \eqnref{graph_convolution_fourier} is a well justified definition of the convolution, it is computationally cumbersome.
 As no efficient and general fast Fourier transform (FFT) exists for graphs \citep{le2018fgft}, the execution of the Fourier transform by multiplication of the signal $\f$ by the dense matrix $\U$ costs $\bO(N_{pix}^2)$ operations.
 In a neural network, this operation has to be performed for each forward and backward pass.
-As current training procedures require processing of many samples, it would be very slow to perform them for a quadratic computational cost in the sample size.
+As current training procedures require processing of many samples, that would be very slow.
 Moreover, the eigen-decomposition of the Laplacian $\L$ is needed to obtain the Fourier basis $\U$ in the first place.
@@
 That defines radial filters, values of which depend only on the distance to the center, and not on the direction.
-It is required as there is no way to order and match nodes from the same neighborhood in a general graph.
-The number of nodes in a neighborhood most often even vary from node to node.
+% It is required as there is no way to order and match nodes from the same neighborhood.
+% The number of nodes in a neighborhood most often even vary from node to node.
 While it may seem odd to restrict filters to be 1D while the sphere is 2D, radial filters are direction-less and result in rotation equivariant convolutions.
-We note that restricting the graph convolutional kernel to a polynomial is similar to restricting the classical euclidean convolution to a fixed-size patch.
+We note that restricting the graph convolutional kernel to a polynomial is similar to restricting the classical Euclidean convolution to a fixed-size patch.
 Similarly, each line of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an irregular patch of radius $K$.
@@
 On the contrary, the amplitude of the monomials $x^k$ is very different for $|x|\approx 0$ and $|x| \approx 1$.}
-Moreover, the coefficients can be computed such as the truncated Chebyshev expansions is an approximate minimax polynomial of a given filter \citep{hammond2011wavelets}.
-While that is irrelevant when learning filters, it is useful for example when smoothing a signal on the sphere by filtering it with an approximated low-pass filter.
 Finally, note that while the graph convolution \eqnref{graph_convolution_fourier} is motivated in the spectral domain, definitions \eqnref{graph_convolution_monomial} and \eqnref{graph_convolution_cheby} are implementations in the vertex domain.
@@
 
+\subsection{2D convolutional neural networks}
+
 \begin{figure}
@@
 
+\subsection{Spherical neural networks}
+
 Rotation equivariance was addressed by leveraging the convolution associated to the 3D rotation group SO(3), with applications to atomization energy regression and 3D model classification, alignment and retrieval \citep{cohen2018sphericalcnn,esteves2017sphericalcnn}.
@@
 While this clever trick lowers the complexity of the convolution to $\bO(N_{pix})$, the non-linearity is $\bO(N_{pix}^{3/2})$.
-This work is another indication that there might be a $\bO(N_{pix}^{3/2})$ computational lower bound for the proper treatment of rotation equivariance with the spherical harmonics.
+This work is another indication that there might be a $\Omega(N_{pix}^{3/2})$ computational lower bound for the proper treatment of rotation equivariance with the spherical harmonics.
 In comparison, DeepSphere scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}), at the expense of not being exactly equivariant (see \ref{sec:comparison_spherical_harmonics}).
@@
 One could still fill the unseen part of the sphere with zeros, and avoid computing empty integrals.
-It is, however, not straightforward to identify empty space, and computations would still be wasted.
-Consider, for example, a ring which mostly contains zeros but a few measurements.
+It is, however, not straightforward to identify empty space, and computations would still be wasted (for example on a ring that mostly contains zeros but a few measurements).
 With graphs, however, computations are only performed for used pixels.
 While it results in some distortions due to border effects (see \figref{border_effects} and \ref{sec:border_effects}), these can be mitigated by padding with zeros a small area around the measurements.
+
+\subsection{Graph neural networks}
 
@@
 Our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/DeepSphere}}} to reproduce those experiments are openly available online.
-The data is available upon request from the cosmology group\footnote{\url{www.cosmology.ethz.ch}}.
-Furthermore, Jupyter notebooks demos can be run from your browser without installing anything.
+The data is available upon request from the cosmology group.\footnote{\url{http://www.cosmology.ethz.ch}}
 
@@
 
-Convergence maps represent the dimensionless distribution of over- and underdensities of mass in the universe, projected on the sky plane.
-The 3D structures are projected using a geometric kernel, value of which depends on the radial distance.
+Convergence maps represent the dimensionless distribution of over- and under-densities of mass in the universe, projected on the sky plane.
+The 3D structures are projected using a geometric kernel, the value of which depends on the radial distance.
 In gravitational lensing, this kernel is dependent on the radial distances between the observer, the mass plane, and the plane of source galaxies \citep[see][for a review of gravitational lensing]{bartelman2010gravitationallensing}.
@@
 Other parameters are set to: Hubble constant $H_0=70 km/s/Mpc$, spectral index $n_s=0.96$, and Baryon density today $\Omega_b=0.05$.
-The parameters $\Omega_m$ and $\sigma_8$ were chosen to have the same spherical harmonic power spectrum for $\ell<1000$.
-That means that it is difficult to distinguish between these cosmological models using these maps if this range of scales is used.
+The parameters $\Omega_m$ and $\sigma_8$ were chosen for the maps to have the same spherical harmonic power spectrum.
+That means that it is difficult to distinguish between these cosmological models.
 We found that the differences in power spectrum is $~5\%$ for $\ell>1000$.
@@
 We however use a single simulation box, as opposed to two used in that work, as we use source galaxies at a lower redshift of $z=0.8$, instead of $z=1.5$.
-As a simulator we use \pkg{L-PICOLA} \citep{howlett2015lpicola}, a fast and approximate code for N-body simulations.
+\pkg{L-PICOLA} \citep{howlett2015lpicola} is used for fast and approximate N-body simulations.
 For each class, we generate $30$ simulations.
@@
 As the cosmological parameters were chosen for the maps to have similar PSDs (see \figref{psd_sigma3}), it is reassuring to observe that an SVM with those as features has difficulties discriminating the models.
-Other statistics are therefor needed to solve the problem. Using histograms as features gives a significant improvement.
+Other statistics are therefore needed to solve the problem. Using histograms as features gives a significant improvement.
 Performance is very good for larger maps and deteriorates for the smaller cases with increased noise level, reaching 80\% at the highest noise level for $o=4$.
@@
 Each pixel on the plot is the dot product between one spherical harmonic and one graph Fourier mode $\b u_i$.
-The plot clearly shows how the subspaces are aligned: modes and harmonics which correspond to different degrees $\ell$ are mostly orthogonal to each other, while modes and harmonics which correspond to the same degree $\ell$ are linearly dependent.
+The plot clearly shows how the subspaces are aligned: modes and harmonics that correspond to different degrees $\ell$ are mostly orthogonal to each other, while modes and harmonics that correspond to the same degree $\ell$ are linearly dependent.
 There are $2 \ell + 1$ orders per degree $\ell$.
-Moreover, we see that the Fourier modes have the correct symmetries, indicated by the perfect orthogonality between even and odd functions.}
+Moreover, we see that the Fourier modes have the correct symmetries, indicated by the perfect orthogonality between even and odd functions.
+For example, the modes corresponding to $\ell=7$ are perfectly orthogonal to the harmonics corresponding to $\ell=0,2,4,6,8$.}
 	\label{fig:subspace_harmonics_eigenvectors}

### 2018-10-24 scnn.tex
fix todos in appendices C and D

@@
 exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
-The fact that the graph convolution is not exactly rotational equivariant is probably compensated by the fact that in a neural network setting the convolution kernels are learned.
-\todo{not ideal tho as the graph convolution depends on the localization}
+In a neural network setting, the fact that the graph convolution is not exactly equivariant to rotation is probably compensated by the fact that convolution kernels are learned.
 
@@
 
-\todo{better formulation}
-The original number of samples $480$, $1920$,
-$7680$ respectively for order $o=1,2,4$ is considered small to train a deep architecture,
-especially when one desire to build a classifier that is robust to noise.
-As a result, we use a classical dataset augmentation technique.
-Before entering the network for training each sample is added a random
-realization of Gaussian noise. The effect is twofold. First, the network never
-ends up seeing the same sample and is less likely to over-fit the training set.
-Second the trained network will be robust to Gaussian noise.
+% The original number of samples $480$, $1920$, $7680$ respectively for order $o=1,2,4$ is considered small to train a deep architecture.
+
+For the trained network to be robust to noise, we employ the following data augmentation technique: a random realization of Gaussian noise is added to each sample before it is fed to the neural network.
+Besides robustness to noise, the network is less likely to over-fit the training set as it never sees the same sample twice.
 
@@
 That is potentially an infinite number of samples.
-Hence, we fit different linear SVM classifiers using various training set sizes until we experimentally observe that increasing the amount of training data does not improve performance.
+Hence, we fit different classifiers using various training set sizes until we experimentally observe that increasing the amount of training data does not improve performance.
 An example convergence of the training and validation errors is shown in \figref{hist_error_evolution}.

### 2018-10-25 scnn.tex
changed affiliationg
filtering speed at multiple lmax

@@
 \address[EPFL]{Institute of Electrical Engineering, EPFL, Lausanne, Switzerland}
-\address[ETHZ]{Institute for Particle Physics and Astrophysics, ETHZ, Zurich, Switzerland}
+\address[ETHZ]{Institute for Particle Physics and Astrophysics, ETH Zurich, Switzerland}
 
@@
     \caption{Comparison of filtering speed for Gaussian smoothing of maps of various sizes.
-    The fast spherical harmonic transform (SHT) is implemented by the \texttt{healpy} Python package (via the \texttt{healpy.sphtfunc.smoothing} function with $\ell_{max} = 3 N_{side} - 1$, the default).
+    The fast spherical harmonic transform (SHT) is implemented by the \texttt{healpy} Python package (via the \texttt{healpy.sphtfunc.smoothing} function).
     The graph filtering is defined by \eqnref{graph_convolution_cheby} and implemented with the \texttt{numpy} and \texttt{scipy} Python packages.
@@
 \figref{filtering_speed} compares the speed of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
-A naive implementation of our method is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively, than using the spherical harmonic transform implemented by the highly optimized \pkg{libsharp} \citep{reinecke2013libsharp} library used by HEALPix.
+A naive implementation of our method is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively, than using the spherical harmonic transform at $\ell_{max} = 3 N_{side}$ implemented by the highly optimized \pkg{libsharp} \citep{reinecke2013libsharp} library used by HEALPix.
 

### 2018-10-25 scnn.tex
last todo + fix figures

@@
 
-\begin{figure}
+\begin{figure}[t!]
 	\centering
@@
 
-\begin{figure}
+\begin{figure}[t!]
     \centering
@@
 Third, we recommend initializing the Chebyshev coefficients with a centered Gaussian distribution with standard deviation $\sqrt{2/(F_{in} \times (K + 0.5))}$, where $K$ is the degree of the Chebyshev polynomials and $F_{in}$ the number of input channels.
-This standard deviation has the property to keep the energy of the signal more or less constant across layers.
-\todo{Nath: cite the paper you read about that?}
+This standard deviation has the property to keep the energy of the signal more or less constant across layers\footnote{We derived this rule from the Chebyshev polynomial equations and some empirical experiments.}.
 % Nati to Michael: The problem with the previous claim is that it depends on the non-linarity. Furthermore, does it make sense to make such a claim if we use batch norm?
@@
 
-\subsection{Filter visualization}
-
 \begin{figure}
 	\centering
-	\includegraphics[width=\linewidth]{section_filter_last}
-	\\
-	\includegraphics[width=\linewidth]{gnonomic_filter_last}
+	\includegraphics[width=0.85\linewidth]{section_filter_last}
+	\vspace{0.5cm}\\
+	\includegraphics[width=0.85\linewidth]{gnonomic_filter_last}
 	\caption{Random selection of 24 learned filters from the fifth spherical convolutional layer $L_5$. Top: section. Bottom: gnomonic projection.}
@@
 \end{figure}
+
+\subsection{Filter visualization}
 
@@
 
-\begin{figure}
+\begin{figure}[ht!]
 	\centering
@@
 
-\begin{figure}
+\begin{figure}[ht!]
   \centering
@@
 
-\begin{figure}
+\begin{figure}[ht!]
 \centering

### 2018-10-26 scnn.tex
few modifications

@@
 Because of their success, CNN-based methods are becoming increasingly popular in Cosmology.
-Cosmological data often comes as spherical maps, which make the use of traditional CNNs more complicated.
+Cosmological data often comes as spherical maps, which make the use of the traditional CNNs more complicated.
 The commonly used pixelization scheme for spherical maps is the Hierarchical Equal Area isoLatitude Pixelisation (HEALPix).
@@
 This approach is computationally more efficient than using spherical harmonics to perform convolutions.
-We demonstrate the method on a classification problem of mass maps from two cosmological models and compare the performance of the CNN with that of two baseline classifiers, based on the power spectrum and pixel density histogram.
+We demonstrate the method on a classification problem of weak lensing mass maps from two cosmological models and compare the performance of the CNN with that of two baseline classifiers, based on the power spectrum and pixel density histogram.
 Our experimental results show that the performance of DeepSphere is always superior or equal to both of these baselines.
@@
 Third, a CNN should work well on parts of the sphere, as many cosmological observations cover only a part of the sky.
-For ground-based observations this can be due to limited visibility of the sky from a particular telescope location, and for space-based instruments due to masking of the galactic plane area (see for example \figref{example_maps}).
+For ground-based observations this can be due to limited visibility of the sky from a particular telescope location, and for space-based instruments due to masking of the galactic plane area (see \figref{example_maps} for example maps).
 
@@
 
-Our spherical CNN leverages convolutions on graphs and hierarchical pooling to address all three identified shortcomings: (i) rotation equivariance, (ii) computational efficiency, and (iii) partial sky observations.
+Our spherical CNN leverages convolutions on graphs and hierarchical pooling to achieve the following properties: (i) rotation equivariance, (ii) computational efficiency, and (iii) partial sky observations.
 The main idea is to model the discretised sphere as a graph of connected pixels: the length of the shortest path between two pixels is an approximation of the geodesic distance between them.
@@
 As the Equal Area isoLatitude Pixelisation (HEALPix)~\citep{gorski2005healpix} is a popular sampling used in cosmology and astrophysics, we tailored the method to that particular sampling.
-DeepSphere is however easily used with other samplings as only two elements depend on it: (i) the choice of neighboring pixels when building the graph, and (ii) the choice of parent pixels when building the hierarchy.
+DeepSphere is, however, easily used with other samplings as only two elements depend on it: (i) the choice of neighboring pixels when building the graph, and (ii) the choice of parent pixels when building the hierarchy.
 The flexibility of modeling the data domain with a graph allows to easily model data that spans only a part of the sphere, or data that is not uniformly sampled.
@@
 Equivariance is not perfect as small imprecisions due to the sampling cause the action of a graph filter to slightly depend on the location.
-That is however not an issue in practice.
+However, we do not expect that to cause problems for practical application
 
@@
 These border effects can, however, be mitigated by padding with zeros a small area around the part of interest.
+Moreover, as long as the training data comes from simulations with the same applied mask, we do not expect these effects to cause problems for the analysis.
 

### 2018-11-02 scnn.tex
coma
typo

@@
 \end{equation*}
-is a measure of the variation of the eigenvector $\b u_i$ is on the graph defined by the Laplacian $\L$.
-
-Figure \figref{graph_harmonics} shows the Fourier modes of a HEALPix graph, created using the graph construction described above.
+is a measure of the variation of the eigenvector $\b u_i$ on the graph defined by the Laplacian $\L$.
+
+\figref{graph_harmonics} shows the Fourier modes of a HEALPix graph, created using the graph construction described above.
 The graph Fourier modes resemble the spherical harmonics.
@@
 Equivariance is not perfect as small imprecisions due to the sampling cause the action of a graph filter to slightly depend on the location.
-However, we do not expect that to cause problems for practical application
+However, we do not expect that to cause problems for practical applications.
 
@@
 The lightcone represents the volume of the universe around the observer, where the radius represents the distance the light from distant galaxies at different times and locations has to travel to the observer.
-Therefore, the particles outputted at different redshifts (time-steps) of the simulation are concentrically arranged in shells of constant redshift around the observer (each redshift $z$ corresponds to a comoving distance away from the observer $\chi(z)$), which is located at redshift $z=0$ (see Figure \ref{fig:sketch_lightcone_simulation}).
+Therefore, the particles outputted at different redshifts (time-steps) of the simulation are concentrically arranged in shells of constant redshift around the observer (each redshift $z$ corresponds to a comoving distance away from the observer $\chi(z)$), which is located at redshift $z=0$ (see \figref{sketch_lightcone_simulation}).
 The shells are then weighted by a weak lensing specific weight $W_b$ and projected onto the sphere for each pixel $\theta_\mathrm{pix}$, resulting in a convergence map

### 2018-11-14 scnn.tex
typo

@@
 
-Our graph is constructed as an approximation of sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$,
+Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
 Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity.

### 2018-12-05 rebuttal.tex
add rebutall

\documentclass[12pt,a4paper]{article}
\usepackage{longtable}
\usepackage[LGR,T1]{fontenc}
\usepackage{lscape}
%\usepackage{pdfsync}
\usepackage{multirow}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{lastpage}
\usepackage{afterpage}
\usepackage{lettrine}
\usepackage{color,soul}
\usepackage[dvipsnames]{xcolor}
\usepackage{colortbl}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{titlesec}

%Palatino font
%\usepackage{pxfonts}
%\usepackage{libertine}
\usepackage[scaled=0.88]{beraserif}
\usepackage[scaled=0.85]{berasans}
\usepackage[scaled=0.84]{beramono}
\usepackage{mathpazo}
%\linespread{1.05}
\usepackage[T1,small,euler-digits]{eulervm}

\usepackage[nomessages]{fp}

 \definecolor{bleuUCLclair}{rgb}{.09, 0.569, 1}
\definecolor{bleuUCLfonce}{rgb}{ .13, .52, .86}
\definecolor{redBurn}{rgb}{.91, 0.29, 0.08}

\usepackage[colorlinks=true,urlcolor=redBurn,linkcolor=black]{hyperref}
\addtolength{\topmargin}{-1.5cm}
\addtolength{\textheight}{1.5cm}
\addtolength{\textwidth}{2cm}
\addtolength{\footskip}{2cm}
\setlength{\evensidemargin}{-0.5cm}
\setlength{\oddsidemargin}{-0.5cm}
\setlength{\arrayrulewidth}{0.25pt}

\renewcommand{\baselinestretch}{1.1} % Interligne

\newenvironment{maliste}%
{ \begin{list}%
	{\textcolor{bleuUCLfonce}{$\bullet$}\hspace{0.5cm}}%
	{\setlength{\labelwidth}{50pt}%
	 \setlength{\leftmargin}{25pt}%
	 \setlength{\itemsep}{30pt}}}%
{ \end{list} }

%\renewcommand{\headrulewidth}{0.0pt}
%\newcommand{\clearemptydoublepage}{%
%	\newpage{\pagestyle{empty}\cleardoublepage}}

%section like title in longtable
\newcommand{\seclong}[1]{\multicolumn{2}{@{}l}{{\Large\sffamily #1}} 
\vspace{0.5cm}
\\}

%enumerate on two columns
\newcounter{listlong}
\newcommand{\newlistlong}{\setcounter{listlong}{1}}
\newcommand{\iteml}[1]{%
\hspace{4.5cm}\textcolor{redBurn}{\arabic{listlong}}\stepcounter{listlong}%
&%
#1%

\\%
}

%left in column
\newcommand{\lcol}[1]{%
\begin{minipage}[t]{.35\textwidth}%

#1%

\end{minipage}%
}

\title{\vspace{-1cm}
\begin{flushleft} {\sffamily Rebuttal for paper \emph{Paper Number} }\end{flushleft}}
\date{\vspace{-1.7cm}\begin{flushleft}\sffamily DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications, Nathanaël Perraudin, Michaël Defferrard, Tomasz Kacprzak, Raphael Sgier \end{flushleft}}

\pagestyle{fancy} 
\fancyhf{}
\fancyfoot[R]{\sffamily\thepage\ / \pageref{LastPage}}
  \fancyfoot[L]{ }

\fancypagestyle{plain}{%
  \fancyhf{}%
  \fancyfoot[R]{\sffamily\thepage\ / \pageref{LastPage}}
  \fancyfoot[L]{ }
}

\renewcommand{\headrulewidth}{0.0pt}

\newcommand{\hlc}[2][yellow]{ {\sethlcolor{#1} \hl{#2}} }

\titleformat{\section}
  {\bfseries\scshape}{Reviewer \# \thesection}{1em}{}

\titleformat{\subsection}
  {\normalfont\scshape}{Comment \# \thesubsection}{1em}{}

\usepackage[framemethod=default]{mdframed}
%\mdfsetup{skipabove=\topskip,skipbelow=\topskip}

\global\mdfdefinestyle{comment}{%
     linecolor=red,linewidth=0.1cm,%
     leftmargin=-0.5cm,rightmargin=-0.5cm, innerleftmargin=0.4cm,innerrightmargin=0.4cm,
     topline=false,bottomline=false
}

\global\mdfdefinestyle{manuscript}{%
     linecolor=gray!20,linewidth=0.05cm,backgroundcolor=gray!20,%
     leftmargin=-0.5cm,rightmargin=-0.5cm, innerleftmargin=0.4cm,innerrightmargin=0.4cm
}

  \renewcommand{\subsectionautorefname}{Comment}

\newcommand{\nati}[1]{{\color[rgb]{.1,.6,.1}{NP: #1}}}
\newcommand{\TK}[1]{{\color{red}{TK: #1}}}
\newcommand{\todo}[1]{{\color[rgb]{.6,.1,.6}{TODO: #1}}}

\begin{document}
\maketitle

% Note: it is very convenient to refer to other comments using the referencing system of \LaTeX, such as here see  \autoref{comment:errorEq2}.

The authors would like to thank the reviewers for their comments, which significantly helped improving the manuscript. We believe we have addressed all the issues raised in the following rebuttal. 
%  For each comment, we have first highlighted the issue, then we provided an answer, and finally we described how the manuscript was adjusted.

\section*{Answer to the editor}

\begin{mdframed}[style=comment] 
Thank you for submitting your manuscript to Astronomy and Computing. I have received comments from reviewers on your manuscript. Your paper should become acceptable for publication pending suitable minor revision and modification of the article in light of the appended reviewer comments.  In particular, there is a request from a reviewer to have access to the data used in your analysis.

Though this is designated a minor revision, there are quite a few points that need to be addressed before the paper is acceptable for publication.  When resubmitting your manuscript, please carefully consider all issues mentioned in the reviewers' comments, outline every change made point by point, and provide suitable rebuttals for any comments not addressed.
\end{mdframed}

\todo{Answer to editor}

\section{}

\subsection{}

\begin{mdframed}[style=comment] 
I have read with great interest the paper by Perraudin and collaborators presenting a methodology (and the associated code) for performing deep machine learning on the sphere using novel algorithms.

The paper is well-written, and the results are clearly presented. The litterature as well as the advantages and limitations of new and existing algorithms are discussed thoroughly and fairly. I recommend this paper for publication, provided the following comments are addressed.
\end{mdframed}

\todo{Thanks the reviewer}

\subsection{}
\begin{mdframed}[style=comment] 
One fairly significant concern I have is how convincing the application to other machine learning algorithms is. The authors compare deep sphere to a SVM classifier, in the case of distinguising from two cosmological models from density maps. This classification is obviously a simplification of what would be done in real comsological analyses, but is sufficient for the purpose of demonstration here. However, the metrics adopted do not clearly highlight the superiority of DeepSphere. The SVM takes pixel histograms or power spectrum densities (PSDs) of each input map. It is not surprising that DeepSphere outperforms them given that it takes the whole map as input. Histograms and PSDs are very restrictive compressions of the data - dropping a lot of spatial information. An SVM or even a standard fully connected neural network (NN) would perform a lot better. It is unclear how that would compare to DeepSphere. But I would certainly expect DeepSphere to be a lot easier to train and have many fewer parameters, which I think is the key advantage that needs to be highlighted here. This is analogous to comparing a standard convolutional NN to a standard fully-connected NN. With appropriate depth both will extract the same information and perform equally well. But of course the CNN has fewer parameters and is easier to train since its structure naturally extracts spatial information. One wouldn't compare the CNN to a SVM trained on pixel histograms or PSDs, since those would not have access to the same information. It would be more natural to compare the CNN and the NN trained on the same maps, and examine the number of parameters, the time and number of examples needed for training to achieve the same performance, etc. This would truly highlight how the structure of the NN is a key advantage.
\end{mdframed}

\todo{General answer:
\begin{itemize}
  \item `An SVM or even a standard fully connected neural network (NN) would perform a lot better.'
  a) I think that SVM fails (I think this this an overfitting problem. This is the case at least for the noiseless case, TO CHECK)
  b) NN is computationally not even possible, or it would have to be a very striped down version of the network... We can actually try...
  \item The reviewer is correct with respect of the number of parameters
\end{itemize}
We should probably add to comparing curves SVM and fully connected
}

\subsection{}
\begin{mdframed}[style=comment] 
Page 4: "There is no known point set that achieves the analogue of uniform sampling in Euclidean space and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions." This is ambigious. There exists multiple schemes for performing exact SHT on band-limited signals. Those sampling are more efficient than healpix - often in terms of number of pixels, and sometimes in terms of performance of the spherical harmonic transforms - and more accurate since the transform is exact (at least numerically - so typical errors are machine precision). Healpix transforms are only exact to 1e-7 when using iterative schemes, and that depends on Nside and lmax. Please clarify this paragraph. Obviously healpix is very advantageous for the pooling and other operations that take advantage of its hierarchical nature. This is well discussed in the paper - in particular how the fast graph algorithms could accomodate other sampling schemes.
\end{mdframed}

\todo{We have updated the manuscript to

\begin{mdframed}[style=manuscript] 
blabla
\end{mdframed}
}

\subsection{}
\begin{mdframed}[style=comment] 
"Our graph is constructed as an approximation of sphere S2, a 2D manifold embedded in R3, Indeed, [33] showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity. While our construction will not exactly respect the setting defined by [33], we observe empirically strong evidence of convergence." This paragraph is unclear. Could you please add a few words to clarify what the approach of 33 is? 
\end{mdframed}

\todo{We added

\begin{mdframed}[style=manuscript] 
blabla
\end{mdframed}}

\subsection{}

\begin{mdframed}[style=comment] 
Figure 3: What was resolution used for those maps? Does the projection of the eigenvectors depend on the resolution and band-limit? 
\end{mdframed}

\todo{Answer}

\subsection{}
\begin{mdframed}[style=comment] 
Page 7: "That is much more efficient than filtering with spherical harmonics, even though HEALPix was de- signed as an iso-latitude sampling that has a fast spherical transform. That is especially true for smooth kernels which require a low polynomial degree K. Figure 4 compares the speed of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here. A naive implementation of our method is ten to twenty times faster for Nside = 2048, with K = 20 and K = 5, respectively, than using the spherical harmonic transform at lmax = 3Nside implemented by the highly optimized libsharp [38] library used by HEALPix." This is not so clear. Is the graph method also performing a Gaussian smoothing with the same characteristics? If so, what are those? How precise is the graph convolution approximating the true harmonic-space Gaussian convolution in this case? This is relevant since some approximations (for instance when analyzing cosmic microwave background data) require high-precision Gaussian smoothing. Finally, is lipsharp optimizing Gaussian smoothing in any way?
\end{mdframed}
\todo{Answer}

\section{}

\begin{mdframed}[style=comment] 
First of all, I would like to thank the authors for writing such a well thought out paper on such an interesting method.

The paper contains an extremely well described technique for performing convolutions on the sphere by first transforming the sphere into pixel space using graphs and then using graph-based convolutional filters that are radially symmetric. These convolutions are then used in neural networks, with an example showing classification of different cosmological scenarios directly from convergence maps. There are several benefits to this method over previously described neural networks on spheres (such as using spherical harmonics, which is slow, or using 2D CNNs, which has to learn to deal with distortions from the projection). I found the approximation of the graph approaching spherical harmonics extremely fascinating and will certainly looking more into this myself in the future!

I will happily recommend this paper for publication. Firstly though, I would like access to the data (privately rather than via emailing the group) so that I can check the notebooks thoroughly. The notebooks are extremely well written but I would like to run them first. As well as this I think there are a few extra applications which will improve the manuscript further, and make the method more appealing for users. I would recommend that these ideas are at least seriously considered by the authors and hopefully implemented: 
\end{mdframed}

\todo{Thank the reviewer + give him access to data}

\subsection{}

\begin{mdframed}[style=comment] 
The first, and most important is an example using masks. Since the authors mention how their method should in principle work well with masks, especially in comparison to HEALPix and Clebsh-Gordan transform spherical harmonic methods I think that it would be extremely enlightening to present this work, probably in the form of a performance vs. time plot. With this being done, the informational content of a masked version of the cosmological application could easily be included. This would, I'm sure, be attractive to the cosmological community as well as the ML community who are always looking for good ways to deal with masked data.
\end{mdframed}
\nati{I do not think we can practically compare with Clebsh-Gordan transform. We need to explain that to the reviewer. This is a sensitive point.}

\subsection{}

\begin{mdframed}[style=comment] 
Secondly, using only SVM as a comparison might skew how well this technique appears to works in a deep learning setting. In principle (and I say this not knowing for sure) 2D CNNs should probably be able to work as well as DeepSphere (although no where near as elegantly) by taking in a projected 2D image of the sky and using *loads* of filters to learn about the distortion at different parts of the projected sky. It would be interesting (and I think a fairly easy test) to check how well DeepSphere performs against a 2D CNN on projections. 
\end{mdframed}
\nati{This is something we should be abble to do. Actually, since we used 1/12 of the sphere, all the pixel grids we use are somehow squared. @Tomek, do you know if we can use directly that as a projection? Or do you know how to do the projection? What happen if the traditional 2D CNN is as good as our technique?}

\begin{mdframed}[style=comment] 
Similarly, I think it would useful to check how well the DeepSphere CNN does against the FCN when the input data is rotated randomly during training - I imagine that the results should match or probably exceed the FCN results and I think this would be a neat little test which doesn't involve needing extra data, just more augmentation.
\end{mdframed}
\nati{Problem here is that rotation is not simple on a sphere. So it will be very slow... In theory, I believe that CNN will match FCN. What shall we do?}

\subsection*{Minor comment}

\begin{mdframed}[style=comment] 
I should say, even though I made the above comments, I thought the paper was really excellent and well written. There were a couple of very minor points which I would like the authors to expand slightly on or consider.
\end{mdframed}

\subsection{}
\begin{mdframed}[style=comment] 
While our construction will not exactly respect the setting defined by [33], we observe empirically strong evidence of convergence.

- Could you add a plot comparing the graph Laplacian as a function of number of pixels and the Laplace-Beltrami operator so the reader can explicitly see the convergence?
\end{mdframed}

\todo{Very good question: but too complex answer for this paper. This is kept for a future contribution. + explain why}

\subsection{}

\begin{mdframed}[style=comment] 
We found out that the one proposed above works well for our purpose, and did not investigate other approaches, leaving it to future work.

- Are you really going to search through different weighting schemes in future work? I would be interested if you were, but could you speculate on what you expect to achieve by looking at different ones?
\end{mdframed}

\todo{Yes, it is likely that we are, + graph learning?}

\subsection{}
\begin{mdframed}[style=comment] 
Thanks to the softmax, the output $\bf{y}\in\mathbb{R}^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the probability that the input sample belongs to class $i$.

- This is a common misconception which is incorrect and needs restating. It is *not* a probability distribution for the class, rather it is a discretised conditional distribution for the class given both the data and the weights and biases of the trained network. One way to see that the value of $y_i$ cannot be considered a probability (which implies P(y|x), i.e. the probability of a class given the data) is that if the network is untrained, would you retrieve back the correct probability? It's wholly dependent on the network.
\end{mdframed}
\nati{I totally agree with the reviewer, but I think this is only a formulation issue. By the way, this mean that the reviewer is knowledgable with ML, and may be Bayesian. He might be working on another spherical approach.}

\subsection{}
\begin{mdframed}[style=comment] 
For example, on images, the subject of interest is most often around the center of the picture. (Also... Contrast that with images, where the subject of interest is most often around the center of the picture.)

- I don't see that this is general at all, only if you are considering say, preprocessed postage stamps of galaxies. I can't think of many other cases in modern machine learning where the images contain the informative part only in the centre of an image. I do agree that the informative part is often localised though. Maybe this should be updated. 
\end{mdframed}
\todo{Answer}

\subsection{}
% Than can be seen as intrinsic data augmentation, as a CNN would need to see many rotated versions of the same data to learn the invariance.

%  - I think you mean "This" rather than "Than". I think, however, you are making a more important point here than you realise. It is not really "intrinsic data augmentation" but rather building a NN to suit your purposes. This should be done by the entire community as, at the moment, too many people blindly build their networks without considering their data and then struggle to get the best results out. The symmetries of the data should be the first thing to influence architecture of a network, exactly as you have reasoned. You might want to add a statement about how you know what your symmetries are and thus, you know how to build a well reasoned network which is more likely to work (and that other should do the same).

% As such, the SHT is only performed once on the input (no back and forth SHT between each layer). While this clever trick lowers the complexity of the convolution to $\mathcal{O}(N_{pix})$, the non-linearity is $\mathcal{O}(N^{3/2}_{pix})$.

%  - I don't understand what the difference is between the convolution and the "non-linearity". I think this sentence either needs explaining further. Is the process $\mathcal{O}(N_{pix})$ or $\mathcal{O}(N^{3/2}_{pix})$?

% When mentioning that you are 10 to 20 times faster than the SHT it should be noted that libsharp has amazing distributed mpi functionality which helps, although of course your method is genuinely lower order computationally (and can be distributed simply on a GPU).

% In Appendix A. (my personal favourite part) could you measure the percent difference that different eigenvectors differ from the spherical harmonics due to incomplete discretisation of the sphere, perhaps plotting side by side plots like Figure 3, but with SH too (or their differences). By the way, Figure A.12 is placed in the wrong section.

% In Appendix C. is there a connection between $t$ and $\sigma$ that you can make, or do you just fit them to be similar? If you just fit them to be similar I'm not sure where the relative differences come from. If they are related, however, then the relative differences make sense, but I can't see what the connection is.

% A question that I would like to know personally, are you thinking about a future upgrade to non-radial kernels?

% Finally, I noticed a few points in the text where there were typos or things which were difficult to follow and I have put a note of them below and tried to correct them as much as I can so that you don't have to put too much effort in - I can't wait to see this paper published. Sorry that the list is so extensive (I'm a bit of a stickler for details and trying to write papers concisely):

% Convolutional Neural Networks (CNNs) have been proposed as an alternative analysis tool in cosmology thanks to their ability to automatically design relevant statistics to maximise the precision of the parameter estimation [9–16].

%  - There are many of us in the community who are not overly keen on "precision" of parameter estimation being the target for machine learning. Rather, we would prefer robustness of parameter estimation. It might be worth changing this sentence a bit so as not to upset some of the referenced authors ;)

% When you have multiple = in equations could you split them on to separate lines? This would make the logical steps for following the equations a lot clearer.

% You change a lot between "node", "vertex" and "pixel". Could you stick to one of these? I think that "vertex" or "pixel" makes the most sense ("pixel" due to the HEALPix pixelisation of the maps or vertex because of the use of the $v$ notation). Node is quite confusing in several places because there is an inherent connection between node and neuron in ML literature, and since there is swapping between the three different terms it's a little hard to keep track.

% You change between math font and text font for the names of your layers when inside and outside of equations. It would look a lot neater sticking with one choice. (Sorry, that seems quite petty and I don't mean it to be).

% In Appendix C. you talk about Kroneker a lot, but earlier you talk about Kroneker $\delta$ (which is it's correct name). It's probably worth sticking with the full name.

% Sky maps are rotation invariant: rotating maps on the sphere doesn’t change their interpretation, as only the statistics of the maps are relevant.

%  - I think that you mean that rotating maps on the sphere doesn't change their interpretation *when* only the statistics of the maps are relevant. Say you wanted to compare the NGC against the SGC, then rotating the map would obviously change the results.

% The flexibility of modelling the data domain with a graph allows to easily model data that spans only a part of the sphere, or data that is not uniformly sampled.

%  - I think you're missing a "one" after allows. "The flexibility of modelling the data domain with a graph allows one to easily model data that spans only a part of the sphere, or data that is not uniformly sampled."

% This kind of maps can be created using the gravitational lensing technique [see 29, for review]

%  - It should be "These" and not "This". "These kind of maps can be created using the gravitational lensing technique [see 29, for review]"

% A CNN is composed of the following main building blocks [31]: (i) a convolution, (ii) a non-linearity, (iii) a down-sampling operation, (iv) a pooling operation, and (v), optionally, normalization.

%  - I think that this is generalising a CNN a bit too much. In my mind (and in my personal uses of CNNs) steps (iii) and (iv) are not always necessary either. Perhaps you want to say that you wish to tackle common tasks which often arise in CNNs: i) convolution, (ii) non-linearity, (iii) down-sampling operation, (iv) pooling operation, and (v), optionally, normalisation.

% Likewise, down-sampling can be achieved by taking one pixel out of n.

%  - I'm afraid I don't understand what this means at all, could you rephrase it?

% A rhombus is a quadrilateral whose four sides all have the same length.

%  - I'm not sure that this really needs to be said.

% As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2\times12=2^2\times12=48$ pixels (middle sphere in Figure 5), the third is $N_{pix} = N_{side}^2\times12=42\times12=192$ pixels, etc., where $N_side =1,2,4,8,\dots$ is the grid resolution parameter.

%  - Might it be more concise to write "The resolution changes as $N_{pix} = N^2_{side}\times12$ such that $N_{pix} = 48$ for $N_{side} = 2$ and $N_{pix} = 192$ with $N_{side}=3$."

% ... is a measure of the variation of the eigenvector $\boldsymbol{u}_i$ is on the graph defined by the Laplacian L.

%  - I don't think the "is" after $\boldsymbol{u}_i$ should be there.

% Given the convolution kernel $h:\mathbb{R}_+ \to \mathbb{R}$,a signal $f\in\mathbb{R}^{N_{pix}}$ on the graph is filtered as

%  - You don't mention what $\mathbb{R}_+$ is or why $h$ defines that map.

% This localization of the kernel $h$ can be useful to visualize kernels, as explained in Appendix C.

%  - Most of Appendix C is not involved with the localisation of the kernel so it might be worth expanding this sentence to "This localisation of the kernel $h$ can be useful to visualise kernels, as shown in an example of heat diffusion presented Appendix C. " Also, it is a little odd that Appendix C is mentioned before Appendix B in the text.

% However, when considering only parts of the sphere, one can observe important border effects (see Figure B.13 and Appendix B).

%  - I would just refer the reader to the appendix rather than the figure and the appendix. It is a bit more concise. "However, when considering only parts of the sphere, one can observe important border effects (see Appendix B)."

% ... where $T_ig[j] = g[i − j]$ is, up to a flip, a translation operator.

%  - I don't understand what you mean by a "flip", a change of sign, the inversion of the kernel?

% Similarly as (2), the convolution of the signal $f$ by a kernel $g$ is the scalar product of $f$ with translated versions $T_ig$ of the kernel $g$.

%  - I think this should be "As with equation (2)" or "Similarly, as in equation (2)" but I can't tell which. Also, it would be really useful if you referred to equations by "equation (x)" rather than just "(x)" throughout - much easier to read that way.

% The 1-neighborhood of a node is the set of nodes that are directly connected to it. The k-neighborhood of a node is the set of nodes that are connected to it through paths of length k.

%  - I'm a little confused here, I think the neighbourhood is every pixel which is closer than the distance of some pixel. The value of k would then be the length of the set of ordered distances for all pixels up to this pixel. Is that correct? For example, take a 3x3 square (on Euclidean space for simplicity), if the central pixel has coordinates (0, 0) then the 1-neighbourhood would be all pixels at a length of 1 pixel or less, i.e. (-1, 0), (+1, 0), (0, -1) and (0, +1) who are all at the same distance so the set of distances is {1} pixel and the length of the set is 1. The 2-neighbourhood would then be all pixels which were a distance $\sqrt{2}$ pixels or less away, i.e. (-1, 0), (+1, 0), (0, -1), (0, +1), (-1, -1), (-1, +1), (+1, -1), (+1, +1) so the set of distances would be {1, $\sqrt{2}$} pixels and the length of the set is 2. Is this correct? If so k is not a length. If this is not correct, I think I misunderstand something and so this should be updated in the text.

% Similarly, each line of the matrix $\sum_{k=0}^&#x10fc04;K\theta_k\boldsymbol{L}^k$ defines an irregular patch of radius $K$.

%  - What do you mean by "line"? Is it a row or a column or something else which I've misunderstood?

% ... where $\tilde{\boldsymbol{L}}= \frac{2}{\lambda_{max}}\boldsymbol{L}−\boldsymbol{I}=−\frac{2}{\lambda_{max}}\boldsymbol{D}^{−1/2}\boldsymbol{W}\boldsymbol{D}^{−1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\Lambda}$ in [−1, 1].

%  - Could you put the equation in its own 2 line align environment to make it easier to read?

% By construction of our graph, $|\mathcal{E}| < 8N_{pix}$ and the overall computational cost of the convolution reduces to $\mathcal{O}(N_{pix})$ operations. That is much more efficient than filtering with spherical harmonics, even though HEALPix was designed as an iso-latitude sampling that has a fast spherical transform.

%  - This could be written as "By construction of our graph, $|\mathcal{E}| < 8N_{pix}$ and the overall computational cost of the convolution reduces to $\mathcal{O}(N_{pix})$ operations and as such is much more efficient than filtering with spherical harmonics, even though HEALPix was designed as an iso-latitude sampling that has a fast spherical transform." to make it easier to read.

% That is especially true for smooth kernels which require a low polynomial degree K.

%  - It is unclear what "That" refers to. If making the above change then "That" could be changed to "This" and it would make sense.

% Coarsening can be naturally designed for hierarchical pixelisation schemes, as each subdivision divides a cell in an equal number of child sub-cells.

%  - I think you mean "where" instead of "as"

% Coarsening is the reverse operation: merging the sub-cells toward the goal of summarizing the data supported on them.

%  - This has an unusual syntax which makes it difficult to follow. I think you mean something like "To coarsen, the sub-cells are merged to summarise the data supported on them."

% Given a map $\boldsymbol{x}\in\mathbb{R}^{N_{pix}}$, pooling defines $\boldsymbol{y}\in\mathbb{R}^{N'_{pix}}$ such as

%  - It should be "such that" not "such as". "Given a map $\boldsymbol{x}\in\mathbb{R}^{N_{pix}}$, pooling defines $\boldsymbol{y}\in\mathbb{R}^{N'_{pix}}$ such that"

% ... where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix}/N'_{pix}$ is the down-sampling factor, which for HEALPix is $|\mathcal{C}(i)| = N_{pix}/N'_{pix} = (N_{side} / N'_{side})^2 = 4^p$.

%  - Can you explain what $p$ is and it would probably be worth splitting this equation into a multi-line align environment for clarity.

% The tail is composed of multiple fully connected layers (FC) followed by an optional softmax layer (SM).

%  - This needs to be expanded to state "The tail is composed of multiple fully connected layers (FC) followed by an optional softmax layer (SM) if the network is used for discrete classification."

% A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer where it is set to the identity.

%  - Why specify this is identity? It could take any activation - you have already mentioned that it could be a softmax.

% The rectified linear unit (ReLU) $\sigma(\cdot) = \textrm{max}(\cdot, 0)$ is a common choice.

%  - Is this the choice you adopt? You should mention that you do, if you indeed do.

% Note that the output $\boldsymbol{Y}\in\mathbb{R}^{N_{pix}\times F_{out}}$ of the last GC (or the output $\boldsymbol{Y}\in\mathbb{R}^{N_{stat}\times F_{out}}$ of the ST), ...

%  - What is ST, you don't mention it before and only once after?

% The output’s size of the neural network depends on the task.

%  - It would be more correct to write "The size of the output of the neural network depends on the task."

% Its radius should be large enough to capture statistics of interest.

%  - I think you mean the radius of the kernel. Perhaps this could be rewritten.

% For example, a small a partial sky observation can provide only limited information of cosmological relevance.

%  - There is just a little mix up in this sentence, maybe a copy and paste accident.

% The cost (or loss) function $C(\boldsymbol{Y},\bar{\boldsymbol{Y}}) = C(NN_\theta(\boldsymbol{X}),\bar{\boldsymbol{Y})$ measures how good the prediction $\boldsymbol{Y}$ is for sample $\boldsymbol{X}$, given the ground truth $\bar{\boldsymbol{Y}}$.

%  - This is true for supervised learning only and should be stated.

% For global prediction, the cost is as if $N_{pix} = 1$.

%  - I think this should be "For global prediction $N_{pix} = 1$."

% We emphasize that the cost function and the SM layer is the sole difference between a neural network engineered for classification or regression.

%  - This should be "We emphasise that the cost function and the SM layer are the sole differences between a neural network engineered for classification or regression."

% The goal of learning is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = E\left[&#x10fc06;C\left(&#x10fc00;NN_\theta(\boldsymbol{X}),\bar{\boldsymbol{Y}}\right)\right]$&#x10fc01;&#x10fc07;.

%  - It is the goal of training, not of learning (in common parlance anyway). Also, you should say that E[] is the expectation rather than leaving people to guess according to the next sentence.

% The optimization is performed by computing an error gradient w.r.t. all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):

%  - This sentence is just a bit turned upside-down, it should be "The optimisation is performed by computing an error gradient w.r.t. all the parameters and updating each parameter via back propagation using a form of stochastic gradient descent (SGD):"

% As this formulation uses the standard 2D convolution, all the optimizations developed for images can be applied, what makes it computationally efficient.

%  - It should be "which makes it computationally efficient" instead of "what". (It's possibly "that" and not "which", but I'm never sure which ;))

% A straightforward way to impose locality in the original domain is to impose smoothness in the spectral domain, by Heisenberg’s uncertainty principle.

%  - What do you mean by "by Heisenberg’s uncertainty principle." That seemed to come out of nowhere. This needs explaining further.

% All the above methods cannot be easily accelerated when the data lies on a part of the sphere only.

%  - You mention your method as part of the "above methods", but then you go on to say that using graphs does allow you to accelerate the method when data is only on part of the sphere.

% By interwinding graph convolutional layers and recurrent layers [65], they can for example model structured time series such as traffic on road networks [66], or recursively complete matrices for recommendation [67].

%  - I'm not sure what interwinding is, I guess you mean by making GC recurrent, or do you mean using GC and then RL separately? Either way there should be commas around "for example".

% To prevent the cosmological models to be distinguished by their power spectra alone, the maps have been smoothed with a Gaussian kernel of radius 3 arcmins to remove high frequencies ($\ell$ > 1000).

%  - This should be "To prevent the cosmological models from being distinguished by their power spectra alone the maps have been smoothed with a Gaussian kernel of radius 3 arcmins to remove high frequencies ($\ell$ > 1000).

% The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters.

%  - Can you add that you are going to describe the details more thoroughly in section 4.1.

% Implementation of full cosmological inference requires, however, many more simulations, building the likelihood function, and several other auxiliary tasks.

%  - Unless you have a cheap neural network based likelihood-free method ;)

% For each class, we generate 30 simulations.

%  - Just mention that there are two classes again, to make it clear that "class" means "cosmology".

% That is a data augmentation scheme, as it creates more training examples than we have simulations.

%  - I think that you should introduce the Gaussian noise paragraph by stating that you perform data augmentation via the addition of randomly drawn Gaussian noise, rather than talking about the random noise first and then explaining that the reason is for data augmentation. ML specialists in particular will be happier with the addition of noise for DA (as will cosmologists I think).

% Probabilities are computed by the SM layer.

%  - As explained above, these are not probabilities, they are class predictions from the network.

% As less pixels are available to make a decision about a sample, the algorithms have access to less information and make more mistakes.

%  - Should be "As fewer pixels...". Also, "makes more mistakes" kind of anthropomorphises the network too much. Perhaps "have access to less information and thus cannot classify as well".

% This standard deviation has the property to keep the energy of the signal more or less constant across layers

%  - Should be "of keeping" instead of "to keep". "This standard deviation has the property of keeping the energy of the signal more or less constant across layers"

% We derived this rule from the Chebyshev polynomial equations and some empirical experiments.

%  - This is a bit loose, can you explain further and add a citation if you didn't do the experiments yourself?

% Figure 10: Random selection of 24 learned filters from the fifth spherical convolutional layer L5. Top: section. Bottom: gnomonic projection.

%  - There is not enough information in this caption. Can you explain that there is some obvious peak structure. I think a colourbar on the gnomonic projection would be useful too.

% The fact that a graph representation of the disretised sphere enables an efficient convolution relaxes the iso-latitude constraint on the design of sampling schemes who aim to enable fast convolutions.

%  - It should be "discretised" and also "who" should be "which" (or "that", I'm not actually sure myself)

% In the long term, it might enable researchers to consider sampling schemes with different trade-offs, or remove the need for schemes and interpolation altogether and simply consider the positions at which measures were taken.

%  - What is "it" here? DeepSphere or graph networks or something else?

% We believe that it might be the case for a different construction of the graph (fully connected) and that a proof could be built on top of the work of [33]. That is, however, out of the scope of this contribution.

%  - What makes you believe this? If you don't want to mention it in this paper, please don't speculate a "belief". I might just be reading the sentence incorrectly, but it makes me a little uncomfortable when there is no evidence backing that up. If you have some evidence then it's worth presenting it.

% In this case, the graph setting used through this contribution correspond to assume reflective border conditions.

%  - It should be "assumed". "In this case, the graph setting used through this contribution correspond to assumed reflective border conditions."

% Nevertheless, dealing working with a subpart of the sphere, its border slightly affects the convolution.

%  - There is a superfluous word (dealing/working). I think this would read better as "Nevertheless, when working with only a part of the sphere, the border slightly affects the convolution."

% These border effects can, however, be mitigated by padding with zeros a small area around the part of interest.

%  - Are they really mitigated? Surely there are still effects but you are happy with the level?

% Furthermore, this result is another sign that the constructed graph is able to capture the spherical structure of the HEALPix sampling.

%  - What does "this" refer to?

% In a neural network setting, the fact that the graph convolution is not exactly equivariant to rotation is probably compensated by the fact that convolution kernels are learned.

%  - I think is might be another one of the most important points in the paper which allows you to justify why not being exact (like a spherical harmonic transform) is acceptable. If I were you I'd move this into the main body of the paper.

% We then plot the result with a gnomonic projection.

%  - Can you add in Figure C.16 here. "We then plot the result with a gnomonic projection, as shown in Figure C.16". Also, why do you choose a gnomonic projection? In fact, with plots C.16 and C.17 I would make them a single plot (as in Figure. 10),

% We plot the section of the convoluted Kroneker.

%  - It should be "convolved" and probably stick with "Kroneker $\delta$". Also, why are you plotting this? What does it show? Can you go into a bit more detail?

% The error clearly converged and adding more samples will not help.

%  - I think this should be "converges such that" rather than "converged and". And rather than "help" I think "improve convergence further" is more descriptive.

% The validation error might be slightly below the training error as it is used to select hyper-parameters.

%  - I don't understand this statement. It could be that there is accidentally more correlation in the validation set, but I'm not sure what you mean by "it is used to select hyper-parameters" or why that would explain why there is less error in the validation set. Can you think about this further (and perhaps check for the amount of information in that data set compared to the training set)?

% The data is generated for the present analysis is based on the fast approximate N-Body simulation code L-PICOLA [71].

%  - The first "is" is superfluous.

% Finally, after all these little points, I just want to congratulate the authors again on a great paper. It was a pleasure reading it. I will be sure to be using this method in the near future!

\end{document}

### 2018-12-05 rebuttal.tex
rebutall with author comments

@@
 \subsection{}
-% Than can be seen as intrinsic data augmentation, as a CNN would need to see many rotated versions of the same data to learn the invariance.
+\begin{mdframed}[style=comment] 
+Than can be seen as intrinsic data augmentation, as a CNN would need to see many rotated versions of the same data to learn the invariance.
 
-%  - I think you mean "This" rather than "Than".
+- I think you mean "This" rather than "Than".
 I think, however, you are making a more important point here than you realise.
@@
 You might want to add a statement about how you know what your symmetries are and thus, you know how to build a well reasoned network which is more likely to work (and that other should do the same).
+\end{mdframed}
+\todo{Answer}
 
-% As such, the SHT is only performed once on the input (no back and forth SHT between each layer).
+\subsection{}
+\begin{mdframed}[style=comment] 
+As such, the SHT is only performed once on the input (no back and forth SHT between each layer).
 While this clever trick lowers the complexity of the convolution to $\mathcal{O}(N_{pix})$, the non-linearity is $\mathcal{O}(N^{3/2}_{pix})$.
 
-%  - I don't understand what the difference is between the convolution and the "non-linearity".
+- I don't understand what the difference is between the convolution and the "non-linearity".
 I think this sentence either needs explaining further.
 Is the process $\mathcal{O}(N_{pix})$ or $\mathcal{O}(N^{3/2}_{pix})$?
+\end{mdframed}
+\todo{Answer}
 
-% When mentioning that you are 10 to 20 times faster than the SHT it should be noted that libsharp has amazing distributed mpi functionality which helps, although of course your method is genuinely lower order computationally (and can be distributed simply on a GPU).
+\subsection{}
+\begin{mdframed}[style=comment] 
+When mentioning that you are 10 to 20 times faster than the SHT it should be noted that libsharp has amazing distributed mpi functionality which helps, although of course your method is genuinely lower order computationally (and can be distributed simply on a GPU).
+\end{mdframed}
+\todo{Answer}
 
-% In Appendix A.
+\subsection{}
+\begin{mdframed}[style=comment] 
+In Appendix A.
 (my personal favourite part) could you measure the percent difference that different eigenvectors differ from the spherical harmonics due to incomplete discretisation of the sphere, perhaps plotting side by side plots like Figure 3, but with SH too (or their differences).
 By the way, Figure A.12 is placed in the wrong section.
+\end{mdframed}
+\todo{Answer + compute the ratio of outside block energy (see Fig. A.12)}
 
-% In Appendix C.
+\subsection{}
+\begin{mdframed}[style=comment] 
+In Appendix C.
 is there a connection between $t$ and $\sigma$ that you can make, or do you just fit them to be similar?
@@
 If they are related, however, then the relative differences make sense, but I can't see what the connection is.
+\end{mdframed}
+\todo{Answer + probably}
 
-% A question that I would like to know personally, are you thinking about a future upgrade to non-radial kernels?
+\subsection{}
+\begin{mdframed}[style=comment] 
+A question that I would like to know personally, are you thinking about a future upgrade to non-radial kernels?
+\end{mdframed}
+\todo{Yes, but it is complicated with graphs}
 
-% Finally, I noticed a few points in the text where there were typos or things which were difficult to follow and I have put a note of them below and tried to correct them as much as I can so that you don't have to put too much effort in - I can't wait to see this paper published.
+\subsection{Details}
+\begin{mdframed}[style=comment] 
+Finally, I noticed a few points in the text where there were typos or things which were difficult to follow and I have put a note of them below and tried to correct them as much as I can so that you don't have to put too much effort in - I can't wait to see this paper published.
 Sorry that the list is so extensive (I'm a bit of a stickler for details and trying to write papers concisely):
+\end{mdframed}
 
-% Convolutional Neural Networks (CNNs) have been proposed as an alternative analysis tool in cosmology thanks to their ability to automatically design relevant statistics to maximise the precision of the parameter estimation [9–16].
+\begin{mdframed}[style=comment] 
+Convolutional Neural Networks (CNNs) have been proposed as an alternative analysis tool in cosmology thanks to their ability to automatically design relevant statistics to maximise the precision of the parameter estimation [9–16].
 
-%  - There are many of us in the community who are not overly keen on "precision" of parameter estimation being the target for machine learning.
+- There are many of us in the community who are not overly keen on "precision" of parameter estimation being the target for machine learning.
 Rather, we would prefer robustness of parameter estimation.
 It might be worth changing this sentence a bit so as not to upset some of the referenced authors ;)
+\end{mdframed}
+\todo{Answer}
 
-% When you have multiple = in equations could you split them on to separate lines? This would make the logical steps for following the equations a lot clearer.
+\begin{mdframed}[style=comment] 
+When you have multiple = in equations could you split them on to separate lines? This would make the logical steps for following the equations a lot clearer.
+\end{mdframed}
+\todo{Answer}
 
-% You change a lot between "node", "vertex" and "pixel".
+\begin{mdframed}[style=comment] 
+You change a lot between "node", "vertex" and "pixel".
 Could you stick to one of these?
@@
 Node is quite confusing in several places because there is an inherent connection between node and neuron in ML literature, and since there is swapping between the three different terms it's a little hard to keep track.
+\end{mdframed}
+\todo{Answer}
 
-% You change between math font and text font for the names of your layers when inside and outside of equations.
+\begin{mdframed}[style=comment] 
+You change between math font and text font for the names of your layers when inside and outside of equations.
 It would look a lot neater sticking with one choice.
 (Sorry, that seems quite petty and I don't mean it to be).
+\end{mdframed}
+\todo{Answer}
 
-% In Appendix C. you talk about Kroneker a lot, but earlier you talk about Kroneker $\delta$ (which is it's correct name). It's probably worth sticking with the full name.
+\begin{mdframed}[style=comment] 
+In Appendix C. you talk about Kroneker a lot, but earlier you talk about Kroneker $\delta$ (which is it's correct name). It's probably worth sticking with the full name.
+\end{mdframed}
+\todo{Answer}
 
-% Sky maps are rotation invariant: rotating maps on the sphere doesn’t change their interpretation, as only the statistics of the maps are relevant.
+\begin{mdframed}[style=comment] 
+Sky maps are rotation invariant: rotating maps on the sphere doesn’t change their interpretation, as only the statistics of the maps are relevant.
+- I think that you mean that rotating maps on the sphere doesn't change their interpretation *when* only the statistics of the maps are relevant.
+Say you wanted to compare the NGC against the SGC, then rotating the map would obviously change the results.
+\end{mdframed}
+\todo{Answer}
 
-%  - I think that you mean that rotating maps on the sphere doesn't change their interpretation *when* only the statistics of the maps are relevant.
-Say you wanted to compare the NGC against the SGC, then rotating the map would obviously change the results.
+\begin{mdframed}[style=comment] 
+The flexibility of modelling the data domain with a graph allows to easily model data that spans only a part of the sphere, or data that is not uniformly sampled.
 
-% The flexibility of modelling the data domain with a graph allows to easily model data that spans only a part of the sphere, or data that is not uniformly sampled.
+- I think you're missing a "one" after allows.
+"The flexibility of modelling the data domain with a graph allows one to easily model data that spans only a part of the sphere, or data that is not uniformly sampled."
+\end{mdframed}
+\todo{Answer}
 
-%  - I think you're missing a "one" after allows.
-"The flexibility of modelling the data domain with a graph allows one to easily model data that spans only a part of the sphere, or data that is not uniformly sampled."
+\begin{mdframed}[style=comment] 
+This kind of maps can be created using the gravitational lensing technique [see 29, for review]
 
-% This kind of maps can be created using the gravitational lensing technique [see 29, for review]
+- It should be "These" and not "This". "These kind of maps can be created using the gravitational lensing technique [see 29, for review]"
+\end{mdframed}
+\todo{Answer}
 
-%  - It should be "These" and not "This". "These kind of maps can be created using the gravitational lensing technique [see 29, for review]"
+\begin{mdframed}[style=comment] 
+A CNN is composed of the following main building blocks [31]: (i) a convolution, (ii) a non-linearity, (iii) a down-sampling operation, (iv) a pooling operation, and (v), optionally, normalization.
 
-% A CNN is composed of the following main building blocks [31]: (i) a convolution, (ii) a non-linearity, (iii) a down-sampling operation, (iv) a pooling operation, and (v), optionally, normalization.
-
-%  - I think that this is generalising a CNN a bit too much.
+- I think that this is generalising a CNN a bit too much.
 In my mind (and in my personal uses of CNNs) steps (iii) and (iv) are not always necessary either.
 Perhaps you want to say that you wish to tackle common tasks which often arise in CNNs: i) convolution, (ii) non-linearity, (iii) down-sampling operation, (iv) pooling operation, and (v), optionally, normalisation.
+\end{mdframed}
+\todo{Answer}
 
-% Likewise, down-sampling can be achieved by taking one pixel out of n.
+\begin{mdframed}[style=comment] 
+Likewise, down-sampling can be achieved by taking one pixel out of n.
 
-%  - I'm afraid I don't understand what this means at all, could you rephrase it?
+- I'm afraid I don't understand what this means at all, could you rephrase it?
+\end{mdframed}
+\todo{Answer}
 
-% A rhombus is a quadrilateral whose four sides all have the same length.
+\begin{mdframed}[style=comment] 
+A rhombus is a quadrilateral whose four sides all have the same length.
 
-%  - I'm not sure that this really needs to be said.
+- I'm not sure that this really needs to be said.
+\end{mdframed}
+\todo{Answer}
 
-% As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2\times12=2^2\times12=48$ pixels (middle sphere in Figure 5), the third is $N_{pix} = N_{side}^2\times12=42\times12=192$ pixels, etc., where $N_side =1,2,4,8,\dots$ is the grid resolution parameter.
+\begin{mdframed}[style=comment] 
+As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2\times12=2^2\times12=48$ pixels (middle sphere in Figure 5), the third is $N_{pix} = N_{side}^2\times12=42\times12=192$ pixels, etc., where $N_side =1,2,4,8,\dots$ is the grid resolution parameter.
 
-%  - Might it be more concise to write "The resolution changes as $N_{pix} = N^2_{side}\times12$ such that $N_{pix} = 48$ for $N_{side} = 2$ and $N_{pix} = 192$ with $N_{side}=3$."
+- Might it be more concise to write "The resolution changes as $N_{pix} = N^2_{side}\times12$ such that $N_{pix} = 48$ for $N_{side} = 2$ and $N_{pix} = 192$ with $N_{side}=3$."
+\end{mdframed}
+\todo{Answer}
 
-% ... is a measure of the variation of the eigenvector $\boldsymbol{u}_i$ is on the graph defined by the Laplacian L.
+\begin{mdframed}[style=comment] 
+... is a measure of the variation of the eigenvector $\bf{u}_i$ is on the graph defined by the Laplacian L.
 
-%  - I don't think the "is" after $\boldsymbol{u}_i$ should be there.
+ - I don't think the "is" after $\bf{u}_i$ should be there.
+\end{mdframed}
+\todo{Answer}
 
-% Given the convolution kernel $h:\mathbb{R}_+ \to \mathbb{R}$,a signal $f\in\mathbb{R}^{N_{pix}}$ on the graph is filtered as
+\begin{mdframed}[style=comment] 
+Given the convolution kernel $h:\mathbb{R}_+ \to \mathbb{R}$,a signal $f\in\mathbb{R}^{N_{pix}}$ on the graph is filtered as
 
-%  - You don't mention what $\mathbb{R}_+$ is or why $h$ defines that map.
+- You don't mention what $\mathbb{R}_+$ is or why $h$ defines that map.
+\end{mdframed}
+\todo{Answer}
 
-% This localization of the kernel $h$ can be useful to visualize kernels, as explained in Appendix C.
+\begin{mdframed}[style=comment] 
+This localization of the kernel $h$ can be useful to visualize kernels, as explained in Appendix C.
 
-%  - Most of Appendix C is not involved with the localisation of the kernel so it might be worth expanding this sentence to "This localisation of the kernel $h$ can be useful to visualise kernels, as shown in an example of heat diffusion presented Appendix C.
+ - Most of Appendix C is not involved with the localisation of the kernel so it might be worth expanding this sentence to "This localisation of the kernel $h$ can be useful to visualise kernels, as shown in an example of heat diffusion presented Appendix C.
 " Also, it is a little odd that Appendix C is mentioned before Appendix B in the text.
+\end{mdframed}
+\todo{Answer}
 
-% However, when considering only parts of the sphere, one can observe important border effects (see Figure B.13 and Appendix B).
+\begin{mdframed}[style=comment] 
+However, when considering only parts of the sphere, one can observe important border effects (see Figure B.13 and Appendix B).
 
-%  - I would just refer the reader to the appendix rather than the figure and the appendix.
+- I would just refer the reader to the appendix rather than the figure and the appendix.
 It is a bit more concise.
 "However, when considering only parts of the sphere, one can observe important border effects (see Appendix B)."
+\end{mdframed}
+\todo{Answer}
 
-% ... where $T_ig[j] = g[i − j]$ is, up to a flip, a translation operator.
+\begin{mdframed}[style=comment] 
+... where $T_ig[j] = g[i − j]$ is, up to a flip, a translation operator.
 
-%  - I don't understand what you mean by a "flip", a change of sign, the inversion of the kernel?
+ - I don't understand what you mean by a "flip", a change of sign, the inversion of the kernel?
+\end{mdframed}
+\todo{Answer}
 
-% Similarly as (2), the convolution of the signal $f$ by a kernel $g$ is the scalar product of $f$ with translated versions $T_ig$ of the kernel $g$.
+\begin{mdframed}[style=comment] 
+Similarly as (2), the convolution of the signal $f$ by a kernel $g$ is the scalar product of $f$ with translated versions $T_ig$ of the kernel $g$.
 
-%  - I think this should be "As with equation (2)" or "Similarly, as in equation (2)" but I can't tell which.
+- I think this should be "As with equation (2)" or "Similarly, as in equation (2)" but I can't tell which.
 Also, it would be really useful if you referred to equations by "equation (x)" rather than just "(x)" throughout - much easier to read that way.
+\end{mdframed}
+\todo{Answer}
 
-% The 1-neighborhood of a node is the set of nodes that are directly connected to it. The k-neighborhood of a node is the set of nodes that are connected to it through paths of length k.
+\begin{mdframed}[style=comment] 
+The 1-neighborhood of a node is the set of nodes that are directly connected to it. The k-neighborhood of a node is the set of nodes that are connected to it through paths of length k.
 
-%  - I'm a little confused here, I think the neighbourhood is every pixel which is closer than the distance of some pixel.
+- I'm a little confused here, I think the neighbourhood is every pixel which is closer than the distance of some pixel.
 The value of k would then be the length of the set of ordered distances for all pixels up to this pixel.
@@
 If this is not correct, I think I misunderstand something and so this should be updated in the text.
+\end{mdframed}
+\todo{Answer}
 
-% Similarly, each line of the matrix $\sum_{k=0}^&#x10fc04;K\theta_k\boldsymbol{L}^k$ defines an irregular patch of radius $K$.
+\begin{mdframed}[style=comment] 
+Similarly, each line of the matrix $\sum_{k=0}^K\theta_k\bf{L}^k$ defines an irregular patch of radius $K$.
 
-%  - What do you mean by "line"? Is it a row or a column or something else which I've misunderstood?
+ - What do you mean by "line"? Is it a row or a column or something else which I've misunderstood?
+\end{mdframed}
+\todo{Answer}
 
-% ...
-where $\tilde{\boldsymbol{L}}= \frac{2}{\lambda_{max}}\boldsymbol{L}−\boldsymbol{I}=−\frac{2}{\lambda_{max}}\boldsymbol{D}^{−1/2}\boldsymbol{W}\boldsymbol{D}^{−1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\Lambda}$ in [−1, 1].
+\begin{mdframed}[style=comment] 
+... where $\tilde{\bf{L}}= \frac{2}{\lambda_{max}}\bf{L}−\bf{I}=−\frac{2}{\lambda_{max}}\bf{D}^{−1/2}\bf{W}\bf{D}^{−1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\Lambda}$ in [−1, 1].
 
-%  - Could you put the equation in its own 2 line align environment to make it easier to read?
+ - Could you put the equation in its own 2 line align environment to make it easier to read?
+\end{mdframed}
+\todo{Answer}
 
-% By construction of our graph, $|\mathcal{E}| < 8N_{pix}$ and the overall computational cost of the convolution reduces to $\mathcal{O}(N_{pix})$ operations.
+\begin{mdframed}[style=comment] 
+By construction of our graph, $|\mathcal{E}| < 8N_{pix}$ and the overall computational cost of the convolution reduces to $\mathcal{O}(N_{pix})$ operations.
 That is much more efficient than filtering with spherical harmonics, even though HEALPix was designed as an iso-latitude sampling that has a fast spherical transform.
 
-%  - This could be written as "By construction of our graph, $|\mathcal{E}| < 8N_{pix}$ and the overall computational cost of the convolution reduces to $\mathcal{O}(N_{pix})$ operations and as such is much more efficient than filtering with spherical harmonics, even though HEALPix was designed as an iso-latitude sampling that has a fast spherical transform." to make it easier to read.
+- This could be written as "By construction of our graph, $|\mathcal{E}| < 8N_{pix}$ and the overall computational cost of the convolution reduces to $\mathcal{O}(N_{pix})$ operations and as such is much more efficient than filtering with spherical harmonics, even though HEALPix was designed as an iso-latitude sampling that has a fast spherical transform." to make it easier to read.
+\end{mdframed}
+\todo{Answer}
 
-% That is especially true for smooth kernels which require a low polynomial degree K.
+\begin{mdframed}[style=comment] 
+That is especially true for smooth kernels which require a low polynomial degree K.
 
-%  - It is unclear what "That" refers to. If making the above change then "That" could be changed to "This" and it would make sense.
+- It is unclear what "That" refers to. If making the above change then "That" could be changed to "This" and it would make sense.
+\end{mdframed}
+\todo{Answer}
 
-% Coarsening can be naturally designed for hierarchical pixelisation schemes, as each subdivision divides a cell in an equal number of child sub-cells.
+\begin{mdframed}[style=comment] 
+Coarsening can be naturally designed for hierarchical pixelisation schemes, as each subdivision divides a cell in an equal number of child sub-cells.
 
-%  - I think you mean "where" instead of "as"
+- I think you mean "where" instead of "as"
+\end{mdframed}
+\todo{Answer}
 
-% Coarsening is the reverse operation: merging the sub-cells toward the goal of summarizing the data supported on them.
+\begin{mdframed}[style=comment] 
+Coarsening is the reverse operation: merging the sub-cells toward the goal of summarizing the data supported on them.
 
-%  - This has an unusual syntax which makes it difficult to follow. I think you mean something like "To coarsen, the sub-cells are merged to summarise the data supported on them."
+- This has an unusual syntax which makes it difficult to follow. I think you mean something like "To coarsen, the sub-cells are merged to summarise the data supported on them."
+\end{mdframed}
+\todo{Answer}
 
-% Given a map $\boldsymbol{x}\in\mathbb{R}^{N_{pix}}$, pooling defines $\boldsymbol{y}\in\mathbb{R}^{N'_{pix}}$ such as
+\begin{mdframed}[style=comment] 
+Given a map $\bf{x}\in\mathbb{R}^{N_{pix}}$, pooling defines $\bf{y}\in\mathbb{R}^{N'_{pix}}$ such as
 
-%  - It should be "such that" not "such as". "Given a map $\boldsymbol{x}\in\mathbb{R}^{N_{pix}}$, pooling defines $\boldsymbol{y}\in\mathbb{R}^{N'_{pix}}$ such that"
+- It should be "such that" not "such as". "Given a map $\bf{x}\in\mathbb{R}^{N_{pix}}$, pooling defines $\bf{y}\in\mathbb{R}^{N'_{pix}}$ such that"
+\end{mdframed}
+\todo{Answer}
 
-% ...
+\begin{mdframed}[style=comment] 
+...
 where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix}/N'_{pix}$ is the down-sampling factor, which for HEALPix is $|\mathcal{C}(i)| = N_{pix}/N'_{pix} = (N_{side} / N'_{side})^2 = 4^p$.
 
-%  - Can you explain what $p$ is and it would probably be worth splitting this equation into a multi-line align environment for clarity.
+- Can you explain what $p$ is and it would probably be worth splitting this equation into a multi-line align environment for clarity.
+\end{mdframed}
+\todo{Answer}
 
-% The tail is composed of multiple fully connected layers (FC) followed by an optional softmax layer (SM).
+\begin{mdframed}[style=comment] 
+The tail is composed of multiple fully connected layers (FC) followed by an optional softmax layer (SM).
 
-%  - This needs to be expanded to state "The tail is composed of multiple fully connected layers (FC) followed by an optional softmax layer (SM) if the network is used for discrete classification."
+- This needs to be expanded to state "The tail is composed of multiple fully connected layers (FC) followed by an optional softmax layer (SM) if the network is used for discrete classification."
+\end{mdframed}
+\todo{Answer}
 
-% A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer where it is set to the identity.
+\begin{mdframed}[style=comment] 
+A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer where it is set to the identity.
 
-%  - Why specify this is identity? It could take any activation - you have already mentioned that it could be a softmax.
+- Why specify this is identity? It could take any activation - you have already mentioned that it could be a softmax.
+\end{mdframed}
+\todo{Answer}
 
-% The rectified linear unit (ReLU) $\sigma(\cdot) = \textrm{max}(\cdot, 0)$ is a common choice.
+\begin{mdframed}[style=comment] 
+The rectified linear unit (ReLU) $\sigma(\cdot) = \textrm{max}(\cdot, 0)$ is a common choice.
 
-%  - Is this the choice you adopt? You should mention that you do, if you indeed do.
+- Is this the choice you adopt? You should mention that you do, if you indeed do.
+\end{mdframed}
+\todo{Answer}
 
-% Note that the output $\boldsymbol{Y}\in\mathbb{R}^{N_{pix}\times F_{out}}$ of the last GC (or the output $\boldsymbol{Y}\in\mathbb{R}^{N_{stat}\times F_{out}}$ of the ST), ...
+\begin{mdframed}[style=comment] 
+Note that the output $\bf{Y}\in\mathbb{R}^{N_{pix}\times F_{out}}$ of the last GC (or the output $\bf{Y}\in\mathbb{R}^{N_{stat}\times F_{out}}$ of the ST), ...
 
-%  - What is ST, you don't mention it before and only once after?
+- What is ST, you don't mention it before and only once after?
+\end{mdframed}
+\todo{Answer}
 
-% The output’s size of the neural network depends on the task.
+\begin{mdframed}[style=comment] 
+The output’s size of the neural network depends on the task.
 
-%  - It would be more correct to write "The size of the output of the neural network depends on the task."
+- It would be more correct to write "The size of the output of the neural network depends on the task."
+\end{mdframed}
+\todo{Answer}
 
-% Its radius should be large enough to capture statistics of interest.
+\begin{mdframed}[style=comment] 
+Its radius should be large enough to capture statistics of interest.
 
-%  - I think you mean the radius of the kernel. Perhaps this could be rewritten.
+- I think you mean the radius of the kernel. Perhaps this could be rewritten.
+\end{mdframed}
+\todo{Answer}
 
-% For example, a small a partial sky observation can provide only limited information of cosmological relevance.
+\begin{mdframed}[style=comment] 
+For example, a small a partial sky observation can provide only limited information of cosmological relevance.
 
-%  - There is just a little mix up in this sentence, maybe a copy and paste accident.
+- There is just a little mix up in this sentence, maybe a copy and paste accident.
+\end{mdframed}
+\todo{Answer}
 
-% The cost (or loss) function $C(\boldsymbol{Y},\bar{\boldsymbol{Y}}) = C(NN_\theta(\boldsymbol{X}),\bar{\boldsymbol{Y})$ measures how good the prediction $\boldsymbol{Y}$ is for sample $\boldsymbol{X}$, given the ground truth $\bar{\boldsymbol{Y}}$.
+\begin{mdframed}[style=comment] 
+The cost (or loss) function $C(\bf{Y},\bar{\bf{Y}}) = C(NN_\theta(\bf{X}),\bar{\bf{Y}})$ measures how good the prediction $\bf{Y}$ is for sample $\bf{X}$, given the ground truth $\bar{\bf{Y}}$.
 
-%  - This is true for supervised learning only and should be stated.
+- This is true for supervised learning only and should be stated.
+\end{mdframed}
+\todo{Answer}
 
-% For global prediction, the cost is as if $N_{pix} = 1$.
+\begin{mdframed}[style=comment] 
+For global prediction, the cost is as if $N_{pix} = 1$.
 
-%  - I think this should be "For global prediction $N_{pix} = 1$."
+- I think this should be "For global prediction $N_{pix} = 1$."
+\end{mdframed}
+\todo{Answer}
 
-% We emphasize that the cost function and the SM layer is the sole difference between a neural network engineered for classification or regression.
+\begin{mdframed}[style=comment] 
+We emphasize that the cost function and the SM layer is the sole difference between a neural network engineered for classification or regression.
 
-%  - This should be "We emphasise that the cost function and the SM layer are the sole differences between a neural network engineered for classification or regression."
+- This should be "We emphasise that the cost function and the SM layer are the sole differences between a neural network engineered for classification or regression."
+\end{mdframed}
+\todo{Answer}
 
-% The goal of learning is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = E\left[&#x10fc06;C\left(&#x10fc00;NN_\theta(\boldsymbol{X}),\bar{\boldsymbol{Y}}\right)\right]$&#x10fc01;&#x10fc07;.
+\begin{mdframed}[style=comment] 
+The goal of learning is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = E\left[C\left(NN_\theta(\bf{X}),\bar{\bf{Y}}\right)\right]$.
 
-%  - It is the goal of training, not of learning (in common parlance anyway). Also, you should say that E[] is the expectation rather than leaving people to guess according to the next sentence.
+- It is the goal of training, not of learning (in common parlance anyway). Also, you should say that E[] is the expectation rather than leaving people to guess according to the next sentence.
+\end{mdframed}
+\todo{Answer}
 
-% The optimization is performed by computing an error gradient w.r.t. all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
+\begin{mdframed}[style=comment] 
+The optimization is performed by computing an error gradient w.r.t. all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
 
-%  - This sentence is just a bit turned upside-down, it should be "The optimisation is performed by computing an error gradient w.r.t.
+- This sentence is just a bit turned upside-down, it should be "The optimisation is performed by computing an error gradient w.r.t.
 all the parameters and updating each parameter via back propagation using a form of stochastic gradient descent (SGD):"
+\end{mdframed}
+\todo{Answer}
 
-% As this formulation uses the standard 2D convolution, all the optimizations developed for images can be applied, what makes it computationally efficient.
+\begin{mdframed}[style=comment] 
+As this formulation uses the standard 2D convolution, all the optimizations developed for images can be applied, what makes it computationally efficient.
 
-%  - It should be "which makes it computationally efficient" instead of "what". (It's possibly "that" and not "which", but I'm never sure which ;))
+- It should be "which makes it computationally efficient" instead of "what". (It's possibly "that" and not "which", but I'm never sure which ;))
+\end{mdframed}
+\todo{Answer}
 
-% A straightforward way to impose locality in the original domain is to impose smoothness in the spectral domain, by Heisenberg’s uncertainty principle.
+\begin{mdframed}[style=comment] 
+A straightforward way to impose locality in the original domain is to impose smoothness in the spectral domain, by Heisenberg’s uncertainty principle.
 
-%  - What do you mean by "by Heisenberg’s uncertainty principle." That seemed to come out of nowhere. This needs explaining further.
+- What do you mean by "by Heisenberg’s uncertainty principle." That seemed to come out of nowhere. This needs explaining further.
+\end{mdframed}
+\todo{Answer}
 
-% All the above methods cannot be easily accelerated when the data lies on a part of the sphere only.
+\begin{mdframed}[style=comment] 
+All the above methods cannot be easily accelerated when the data lies on a part of the sphere only.
 
-%  - You mention your method as part of the "above methods", but then you go on to say that using graphs does allow you to accelerate the method when data is only on part of the sphere.
+- You mention your method as part of the "above methods", but then you go on to say that using graphs does allow you to accelerate the method when data is only on part of the sphere.
+\end{mdframed}
+\todo{Answer}
 
-% By interwinding graph convolutional layers and recurrent layers [65], they can for example model structured time series such as traffic on road networks [66], or recursively complete matrices for recommendation [67].
+\begin{mdframed}[style=comment] 
+By interwinding graph convolutional layers and recurrent layers [65], they can for example model structured time series such as traffic on road networks [66], or recursively complete matrices for recommendation [67].
 
-%  - I'm not sure what interwinding is, I guess you mean by making GC recurrent, or do you mean using GC and then RL separately? Either way there should be commas around "for example".
+- I'm not sure what interwinding is, I guess you mean by making GC recurrent, or do you mean using GC and then RL separately? Either way there should be commas around "for example".
+\end{mdframed}
+\todo{Answer}
 
-% To prevent the cosmological models to be distinguished by their power spectra alone, the maps have been smoothed with a Gaussian kernel of radius 3 arcmins to remove high frequencies ($\ell$ > 1000).
+\begin{mdframed}[style=comment] 
+To prevent the cosmological models to be distinguished by their power spectra alone, the maps have been smoothed with a Gaussian kernel of radius 3 arcmins to remove high frequencies ($\ell$ > 1000).
 
-%  - This should be "To prevent the cosmological models from being distinguished by their power spectra alone the maps have been smoothed with a Gaussian kernel of radius 3 arcmins to remove high frequencies ($\ell$ > 1000).
+- This should be "To prevent the cosmological models from being distinguished by their power spectra alone the maps have been smoothed with a Gaussian kernel of radius 3 arcmins to remove high frequencies ($\ell$ > 1000).
+\end{mdframed}
+\todo{Answer}
 
-% The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters.
+\begin{mdframed}[style=comment] 
+The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters.
 
-%  - Can you add that you are going to describe the details more thoroughly in section 4.1.
+- Can you add that you are going to describe the details more thoroughly in section 4.1.
+\end{mdframed}
+\todo{Answer}
 
-% Implementation of full cosmological inference requires, however, many more simulations, building the likelihood function, and several other auxiliary tasks.
+\begin{mdframed}[style=comment] 
+Implementation of full cosmological inference requires, however, many more simulations, building the likelihood function, and several other auxiliary tasks.
 
-%  - Unless you have a cheap neural network based likelihood-free method ;)
+- Unless you have a cheap neural network based likelihood-free method ;)
+\end{mdframed}
+\todo{Answer}
 
-% For each class, we generate 30 simulations.
+\begin{mdframed}[style=comment] 
+For each class, we generate 30 simulations.
 
-%  - Just mention that there are two classes again, to make it clear that "class" means "cosmology".
+- Just mention that there are two classes again, to make it clear that "class" means "cosmology".
+\end{mdframed}
+\todo{Answer}
 
-% That is a data augmentation scheme, as it creates more training examples than we have simulations.
+\begin{mdframed}[style=comment] 
+That is a data augmentation scheme, as it creates more training examples than we have simulations.
 
-%  - I think that you should introduce the Gaussian noise paragraph by stating that you perform data augmentation via the addition of randomly drawn Gaussian noise, rather than talking about the random noise first and then explaining that the reason is for data augmentation.
+- I think that you should introduce the Gaussian noise paragraph by stating that you perform data augmentation via the addition of randomly drawn Gaussian noise, rather than talking about the random noise first and then explaining that the reason is for data augmentation.
 ML specialists in particular will be happier with the addition of noise for DA (as will cosmologists I think).
+\end{mdframed}
+\todo{Answer}
 
-% Probabilities are computed by the SM layer.
+\begin{mdframed}[style=comment] 
+Probabilities are computed by the SM layer.
 
-%  - As explained above, these are not probabilities, they are class predictions from the network.
+- As explained above, these are not probabilities, they are class predictions from the network.
+\end{mdframed}
+\todo{Answer}
 
-% As less pixels are available to make a decision about a sample, the algorithms have access to less information and make more mistakes.
+\begin{mdframed}[style=comment] 
+As less pixels are available to make a decision about a sample, the algorithms have access to less information and make more mistakes.
 
-%  - Should be "As fewer pixels...". Also, "makes more mistakes" kind of anthropomorphises the network too much. Perhaps "have access to less information and thus cannot classify as well".
+- Should be "As fewer pixels...". Also, "makes more mistakes" kind of anthropomorphises the network too much. Perhaps "have access to less information and thus cannot classify as well".
+\end{mdframed}
+\todo{Answer}
 
-% This standard deviation has the property to keep the energy of the signal more or less constant across layers
+\begin{mdframed}[style=comment] 
+This standard deviation has the property to keep the energy of the signal more or less constant across layers
 
-%  - Should be "of keeping" instead of "to keep". "This standard deviation has the property of keeping the energy of the signal more or less constant across layers"
+- Should be "of keeping" instead of "to keep". "This standard deviation has the property of keeping the energy of the signal more or less constant across layers"
+\end{mdframed}
+\todo{Answer}
 
-% We derived this rule from the Chebyshev polynomial equations and some empirical experiments.
+\begin{mdframed}[style=comment] 
+We derived this rule from the Chebyshev polynomial equations and some empirical experiments.
 
-%  - This is a bit loose, can you explain further and add a citation if you didn't do the experiments yourself?
+- This is a bit loose, can you explain further and add a citation if you didn't do the experiments yourself?
+\end{mdframed}
+\todo{Answer}
 
-% Figure 10: Random selection of 24 learned filters from the fifth spherical convolutional layer L5. Top: section. Bottom: gnomonic projection.
+\begin{mdframed}[style=comment] 
+Figure 10: Random selection of 24 learned filters from the fifth spherical convolutional layer L5. Top: section. Bottom: gnomonic projection.
 
-%  - There is not enough information in this caption. Can you explain that there is some obvious peak structure. I think a colourbar on the gnomonic projection would be useful too.
+- There is not enough information in this caption. Can you explain that there is some obvious peak structure. I think a colourbar on the gnomonic projection would be useful too.
+\end{mdframed}
+\todo{Answer}
 
-% The fact that a graph representation of the disretised sphere enables an efficient convolution relaxes the iso-latitude constraint on the design of sampling schemes who aim to enable fast convolutions.
+\begin{mdframed}[style=comment] 
+The fact that a graph representation of the disretised sphere enables an efficient convolution relaxes the iso-latitude constraint on the design of sampling schemes who aim to enable fast convolutions.
 
-%  - It should be "discretised" and also "who" should be "which" (or "that", I'm not actually sure myself)
+- It should be "discretised" and also "who" should be "which" (or "that", I'm not actually sure myself)
+\end{mdframed}
+\todo{Answer}
 
-% In the long term, it might enable researchers to consider sampling schemes with different trade-offs, or remove the need for schemes and interpolation altogether and simply consider the positions at which measures were taken.
+\begin{mdframed}[style=comment] 
+In the long term, it might enable researchers to consider sampling schemes with different trade-offs, or remove the need for schemes and interpolation altogether and simply consider the positions at which measures were taken.
 
-%  - What is "it" here? DeepSphere or graph networks or something else?
+- What is "it" here? DeepSphere or graph networks or something else?
+\end{mdframed}
+\todo{Answer}
 
-% We believe that it might be the case for a different construction of the graph (fully connected) and that a proof could be built on top of the work of [33].
+\begin{mdframed}[style=comment] 
+We believe that it might be the case for a different construction of the graph (fully connected) and that a proof could be built on top of the work of [33].
 That is, however, out of the scope of this contribution.
 
-%  - What makes you believe this?
+- What makes you believe this?
 If you don't want to mention it in this paper, please don't speculate a "belief".
@@
 If you have some evidence then it's worth presenting it.
+\end{mdframed}
+\todo{Answer}
 
-% In this case, the graph setting used through this contribution correspond to assume reflective border conditions.
+\begin{mdframed}[style=comment] 
+In this case, the graph setting used through this contribution correspond to assume reflective border conditions.
 
-%  - It should be "assumed". "In this case, the graph setting used through this contribution correspond to assumed reflective border conditions."
+- It should be "assumed". "In this case, the graph setting used through this contribution correspond to assumed reflective border conditions."
+\end{mdframed}
+\todo{Answer}
 
-% Nevertheless, dealing working with a subpart of the sphere, its border slightly affects the convolution.
+\begin{mdframed}[style=comment] 
+Nevertheless, dealing working with a subpart of the sphere, its border slightly affects the convolution.
 
-%  - There is a superfluous word (dealing/working). I think this would read better as "Nevertheless, when working with only a part of the sphere, the border slightly affects the convolution."
+- There is a superfluous word (dealing/working). I think this would read better as "Nevertheless, when working with only a part of the sphere, the border slightly affects the convolution."
+\end{mdframed}
+\todo{Answer}
 
-% These border effects can, however, be mitigated by padding with zeros a small area around the part of interest.
+\begin{mdframed}[style=comment] 
+These border effects can, however, be mitigated by padding with zeros a small area around the part of interest.
 
-%  - Are they really mitigated? Surely there are still effects but you are happy with the level?
+- Are they really mitigated? Surely there are still effects but you are happy with the level?
+\end{mdframed}
+\todo{Answer}
 
-% Furthermore, this result is another sign that the constructed graph is able to capture the spherical structure of the HEALPix sampling.
+\begin{mdframed}[style=comment] 
+Furthermore, this result is another sign that the constructed graph is able to capture the spherical structure of the HEALPix sampling.
 
-%  - What does "this" refer to?
+- What does "this" refer to?
+\end{mdframed}
+\todo{Answer}
 
-% In a neural network setting, the fact that the graph convolution is not exactly equivariant to rotation is probably compensated by the fact that convolution kernels are learned.
+\begin{mdframed}[style=comment] 
+In a neural network setting, the fact that the graph convolution is not exactly equivariant to rotation is probably compensated by the fact that convolution kernels are learned.
 
-%  - I think is might be another one of the most important points in the paper which allows you to justify why not being exact (like a spherical harmonic transform) is acceptable.
+- I think is might be another one of the most important points in the paper which allows you to justify why not being exact (like a spherical harmonic transform) is acceptable.
 If I were you I'd move this into the main body of the paper.
+\end{mdframed}
+\todo{Answer}
 
-% We then plot the result with a gnomonic projection.
+\begin{mdframed}[style=comment] 
+We then plot the result with a gnomonic projection.
 
-%  - Can you add in Figure C.16 here.
+- Can you add in Figure C.16 here.
 "We then plot the result with a gnomonic projection, as shown in Figure C.16".
@@
 10),
+\end{mdframed}
+\todo{Answer}
 
-% We plot the section of the convoluted Kroneker.
+\begin{mdframed}[style=comment] 
+We plot the section of the convoluted Kroneker.
 
-%  - It should be "convolved" and probably stick with "Kroneker $\delta$". Also, why are you plotting this? What does it show? Can you go into a bit more detail?
+- It should be "convolved" and probably stick with "Kroneker $\delta$". Also, why are you plotting this? What does it show? Can you go into a bit more detail?
+\end{mdframed}
+\todo{Answer}
 
-% The error clearly converged and adding more samples will not help.
+\begin{mdframed}[style=comment] 
+The error clearly converged and adding more samples will not help.
 
-%  - I think this should be "converges such that" rather than "converged and". And rather than "help" I think "improve convergence further" is more descriptive.
+- I think this should be "converges such that" rather than "converged and". And rather than "help" I think "improve convergence further" is more descriptive.
+\end{mdframed}
+\todo{Answer}
 
-% The validation error might be slightly below the training error as it is used to select hyper-parameters.
+\begin{mdframed}[style=comment] 
+The validation error might be slightly below the training error as it is used to select hyper-parameters.
 
-%  - I don't understand this statement.
+- I don't understand this statement.
 It could be that there is accidentally more correlation in the validation set, but I'm not sure what you mean by "it is used to select hyper-parameters" or why that would explain why there is less error in the validation set.
 Can you think about this further (and perhaps check for the amount of information in that data set compared to the training set)?
+\end{mdframed}
+\todo{Answer}
 
-% The data is generated for the present analysis is based on the fast approximate N-Body simulation code L-PICOLA [71].
+\begin{mdframed}[style=comment] 
+The data is generated for the present analysis is based on the fast approximate N-Body simulation code L-PICOLA [71].
 
-%  - The first "is" is superfluous.
+- The first "is" is superfluous.
+\end{mdframed}
+\todo{Answer}
 
-% Finally, after all these little points, I just want to congratulate the authors again on a great paper. It was a pleasure reading it. I will be sure to be using this method in the near future!
+\subsection{}
+
+\begin{mdframed}[style=comment]
+
+Finally, after all these little points, I just want to congratulate the authors again on a great paper. It was a pleasure reading it. I will be sure to be using this method in the near future!
+\end{mdframed}
+\todo{Final thanks + contact us?}
 

### 2018-12-07 rebuttal.tex
pre-screen reviewer 1

@@
 
-\todo{General answer:
+\todo{Assigned: @nati, @michael
+General answer:
 \begin{itemize}
   \item `An SVM or even a standard fully connected neural network (NN) would perform a lot better.'
-  a) I think that SVM fails (I think this this an overfitting problem. This is the case at least for the noiseless case, TO CHECK)
+  a) I think that SVM fails (I think this this an overfitting problem.
+This is the case at least for the noiseless case, TO CHECK) I was able to run SVM, it works, but the result is pretty bad.
+TODO: do a full experiment.
   b) NN is computationally not even possible, or it would have to be a very striped down version of the network... We can actually try...
+  The input number of pixel for our order $1$ is $1024^2$ which severly limits the number of neurons that can be used in a fully connected architecture.
+For the first layer, we were only able to $128$ neurons before hitting an out of memory errors.
+In this setting, with an relative amount of noise of 0.5, we were unable to find regularization setting for the network such that it would actually classify the validation set.
+Note that all calssifiers performed well in this particular setting.
+Similar conclusion were observed with other setting, even when increasing the number of neurons for order $2$ and $4$.
   \item The reviewer is correct with respect of the number of parameters
@@
 
-\todo{We have updated the manuscript to
-
+\todo{Assigned to: @all whoever can answer this question. I just do not know the answer.
 \begin{mdframed}[style=manuscript] 
@@
 
-\todo{We added
-
+\todo{Assigned: @nati 
+We added
 \begin{mdframed}[style=manuscript] 
@@
 
-\todo{Answer}
+\todo{@nati
+We were actually limited in resolution when computing the graph Fourier eigenvectors as diagonalizing the Laplacian matrix scales as $O(N_{pix}^3)$.
+Hence we used a resolution of $N_{side}=16$.
+The information has been added to the paper.
+We believe that, with the correct weighting scheme the graph eigenvectors may converge toward the spherical harmonics as the resolution increases.
+We also believe that the eigenvector associated with the lowest $\ell$ "converges first".
+}
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assigned: @nati,
+Tocheck: @tomek, @michael
+\begin{itemize}
+  \item No here we only care about filter speed. 
+  \item Filters do not have to be the same as they are learned anyway by the network.
+  \item Replacing healpix filtering with graph filtering might be possible (suggested by Appendix C and fig 14), but is probably not usable when precision is required. It is left for futur work.
+\end{itemize}
+}
 

### 2018-12-07 scnn.tex
pre-screen reviewer 1

@@
 	\includegraphics[width=\linewidth]{eigenvectors}
-	\caption{The first 16 eigenvectors of the graph Laplacian, an equivalent of Fourier modes, of a graph constructed from the HEALPix sampling of the sphere.
+	\caption{The first 16 eigenvectors of the graph Laplacian, an equivalent of Fourier modes, of a graph constructed from the HEALPix sampling of the sphere \nati{($N_{side}=16$)}.
     Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$ and order $|m|=(0,1)$, eigenvectors 4--8 with degree $\ell=2$ and order $|m|=(0,1,2)$, and eigenvectors 9--15 with degree $\ell=3$ and order $|m|=(0,1,2,3)$.
@@
 \begin{equation}
-  \L \b{f}(t) = \tau \partial_t \b{f}(t),
+  \tau \L \b{f}(t) = - \partial_t \b{f}(t),
   \label{eqn:heat_equation}
@@
 \begin{equation*}
-  \b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U\trans \g{f}(0) = K_t(\L) \b{f}(0),
+  \b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda \tau t} \U\trans \g{f}(0) = K_t(\L) \b{f}(0),
 \end{equation*}

### 2019-01-24 rebuttal.tex
going through the rebuttal

--- 2018-12-05 rebuttal.tex
@@
 
-\todo{Thanks the reviewer}
+Dear reviewer, we thank you for reading our paper and providing comments.
+They have helped us improving our manuscript.
+In this rebuttal, you can find a detailed answer to all the points you mentioned.
 
@@
 
-\todo{General answer:
-\begin{itemize}
-  \item `An SVM or even a standard fully connected neural network (NN) would perform a lot better.'
-  a) I think that SVM fails (I think this this an overfitting problem. This is the case at least for the noiseless case, TO CHECK)
-  b) NN is computationally not even possible, or it would have to be a very striped down version of the network... We can actually try...
-  \item The reviewer is correct with respect of the number of parameters
-\end{itemize}
-We should probably add to comparing curves SVM and fully connected
-}
+\todo{Assigned: @nati, @michael}
+The intuition of the reviewer is correct, theorectially using the raw data, \emph{an SVM or even a standard fully connected neural network (NN) would perform a lot better.} In practice, this those models are limited by the computational power and the dataset size.
+
+We had actually tried training an SVM on the raw data but were unable to obtain over $60\%$ accuracy in cases where all the other models were close to $100\%$.
+The classifier would either overfit or be over-regularized.
+For that reason, we decided, not to report the SVM results in the paper.
+\nati{FYI, I did try again to be entirely sure about it.}
+
+A model based on a fully connected neural network, as suggested by the reviewer, will contains a very large amount of weights severly limiting what can be tested with conventional hardware.
+In our case the input number of pixels (for order $1$) is $1024^2$ which severly limits the number of neurons that can be used in the architecture.
+For the completeness of this answer, we did try a fully connected NN.
+Practially, in the first layer, we were only able to $128$ neurons before hitting an out of memory errors.
+In this setting, with an relative amount of noise of $0.5$, we were unable to regularize the network such that it would actually classify the validation set.
+Note that all calssifiers performed well (close to $100\%$ accuracy) in this particular setting.
+Similar conclusion were observed with other setting, even when increasing the number of neurons for small part of the sphere (order $2$ and $4$).
+
+This being said, the reviewer comment is justified and we will add these information to the paper.
+
+\todo{Add it in the paper... Make clear that CNN is so much better than fully connected + say that SVM on he raw features does not work.}
 
@@
 
-\todo{We have updated the manuscript to
+\todo{Assigned to: @all whoever can answer this question. I just do not know the answer.
 
+We clarified the sentence with this:
 \begin{mdframed}[style=manuscript] 
@@
 
-\todo{We added
+\todo{Assigned: @nati, @michael}
 
+We tried to clarify the paragraph in the following manner:
 \begin{mdframed}[style=manuscript] 
-blabla
-\end{mdframed}}
+Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
+Indeed, \cite{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the Manifold and a fully connected graph built with exponentially decaying weights.
+While our construction will not exactly respect the setting defined by \cite{belkin2007convergence} (the sampling is not uniform and the graph is not fully connected), we observe empirically strong evidence of convergence.
+\end{mdframed}
+We are aware that this particular point could be more detailled.
+Nevertheless, we believe that a deeper discussion does not belong to this paper.
+In fact, we are currently investigating the convergence question with the goal of obtaining better graph constructions or rotational equivariance results.
 
@@
 
-\todo{Answer}
+\todo{Assigned: @nati}
+We were actually limited in resolution when computing the graph Fourier eigenvectors as diagonalizing the Laplacian matrix scales as $O(N_{pix}^3)$.
+Hence we used a resolution of $N_{side}=16$.
+The information has been added to the paper.
+
+Since we do not have any convergence result yet, we are not usure about how the projection error evolves.
+However, if there is convergence (and we believe there is), then the eigenvector associated with the lowest $\ell$ probably converge first.
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assigned: @nati,
+Tocheck: @tomek, @michael
+}
+
+In the experiment shown if Figure 4, we only care about speed and not about the filter itself (we could have taken any filter).
+The main reason is that in the context of neural network, filters will be learned anyway.
+Libsharp is probably not optimized for Gaussian smoothing, but this experiment should not be limted to Gaussian filter.
+We intend to report on the general filter speed and use conveniently a Gaussian.
+
+We note that, the reviewer question is interesting.
+Replacing spherical filtering (using the harmonic decomposition) with graph filtering might be possible in the future as suggested by Appendix C and fig 14.
+Our feeling is that in its current state, it probably does not have the required precision to be usable in a high precision setting.
+Nevertheless, theoretical improvement on the convergence side could definitly makes it competitive.
 
@@
 
-\todo{Thank the reviewer + give him access to data}
+\todo{Assigned @Tomek
+\begin{itemize}
+  \item Thank the reviewer
+  \item give him access to data
+\end{itemize}}
 
@@
 \end{mdframed}
-\nati{I do not think we can practically compare with Clebsh-Gordan transform. We need to explain that to the reviewer. This is a sensitive point.}
+\todo{Assigned: @Michael, @Nati}
+\nati{I do not think we can practically compare with Clebsh-Gordan transform. There is no code for the paper of Kondor. We can write the theoretical complexity. This is a sensitive point.}
 
@@
 \end{mdframed}
-\nati{This is something we should be abble to do.
+\todo{Assigned: @Nati, @Michael, @Tomek}
+\nati{
+This is something we should be able to do.
 Actually, since we used 1/12 of the sphere, all the pixel grids we use are somehow squared.
-@Tomek, do you know if we can use directly that as a projection?
-Or do you know how to do the projection?
-What happen if the traditional 2D CNN is as good as our technique?}
+I am now using this as a projection.
+@Tomek, do you know if this is ok?
+Or do you know how to do the projection in a simple and efficient manner?
+I am trying to make the comparizon right now
+More important, I think that traditional 2D CNNs will be as good as our algorithm. We should be very careful in the way we formulate this in our answer and in the paper.}
 
@@
 \end{mdframed}
-\nati{Problem here is that rotation is not simple on a sphere. So it will be very slow... In theory, I believe that CNN will match FCN. What shall we do?}
+\nati{@Nati, @Michael, @Tomek
+
+Problem here is that rotation is not simple on a sphere, it will probably be slow and I will have to break a lot of code to do it.
+Nevertheless, I believe that in theory, CNN will match FCN when we do enought rotation. Should we answer that? @mMichael: what do you think?
+}
 
@@
 
-\todo{Very good question: but too complex answer for this paper. This is kept for a future contribution. + explain why}
+\todo{Dear reviewer, this is an excellente question. We have have made the choice to takle quantitatively and theoretically the subject of convergence because of its complexity.
+
+Very good question: but too complex answer for this paper. This is kept for a future contribution. + explain why}
 
@@
 
+\clearpage
+\newpage
+
+\bibliographystyle{elsarticle-num}
+\bibliography{biblio}
+
 \end{document}

### 2019-01-24 scnn.tex
going through the rebuttal

@@
 
-Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
-Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity.
-While our construction will not exactly respect the setting defined by \citep{belkin2007convergence}, we observe empirically strong evidence of convergence.
+\nati{Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
+Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the Manifold and a fully connected graph built with exponentially decaying weights.
+While our construction will not exactly respect the setting defined by \citep{belkin2007convergence} (the sampling is not uniform and the graph is not fully connected), we observe empirically strong evidence of convergence.}
 

### 2019-01-26 rebuttal.tex
going further in the rebuttal

@@
 \documentclass[12pt,a4paper]{article}
+\usepackage[utf8]{inputenc}
+
 \usepackage{longtable}
@@
 
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{siunitx}
+\usepackage{bm}
+
  \definecolor{bleuUCLclair}{rgb}{.09, 0.569, 1}
@@
 \newcommand{\todo}[1]{{\color[rgb]{.6,.1,.6}{TODO: #1}}}
+
+\newcommand{\figref}[1]{Figure~\ref{fig:#1}}
+\newcommand{\tabref}[1]{Table~\ref{tab:#1}}
+\newcommand{\secref}[1]{Section~\ref{sec:#1}}
+%\newcommand{\secref}[1]{\S\ref{sec:#1}}
+\newcommand{\eqnref}[1]{(\ref{eqn:#1})}
+
+\renewcommand{\b}[1]{{\bm{#1}}}   % bold symbol
+
+% MATH SYMBOLS
+\newcommand{\1}{\b{1}}              % all-ones vector
+\newcommand{\0}{\b{0}}              % all-zero vector
+\newcommand{\g}[1]{\b{#1}}
+\newcommand{\G}{\mathcal{G}}
+\newcommand{\V}{\mathcal{V}}
+\newcommand{\E}{\mathcal{E}}
+\newcommand{\C}{\mathcal{C}}
+\newcommand{\B}{\mathcal{B}}
+\renewcommand{\L}{\b{L}}
+\newcommand{\tL}{\tilde{\L}}
+\newcommand{\W}{\b{W}}
+\newcommand{\I}{\b{I}}
+\newcommand{\D}{\b{D}}
+\newcommand{\U}{\b{U}}
+\newcommand{\x}{\b{x}}
+\newcommand{\X}{\b{X}}
+\newcommand{\y}{\b{y}}
+\newcommand{\Y}{\b{Y}}
+\newcommand{\bu}{\b{u}}
+\newcommand{\f}{\b{f}}
+\newcommand{\trans}{^\intercal}
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\bLambda}{\b{\Lambda}}
+\newcommand{\blambda}{\b{\lambda}}
+\newcommand{\bO}{\mathcal{O}}
+\newcommand{\T}{\mathcal{T}}
+\DeclareMathOperator*{\esp}{E}
+\DeclareMathOperator*{\var}{Var}
+\DeclareMathOperator*{\vect}{vec}
+\DeclareMathOperator*{\argmin}{arg \, min}
+\newcommand{\pkg}[1]{\texttt{#1}}
 
@@
 \todo{Assigned: @Michael, @Nati}
-\nati{I do not think we can practically compare with Clebsh-Gordan transform. There is no code for the paper of Kondor. We can write the theoretical complexity. This is a sensitive point.}
+Our implementation is actually already working with a mask, we choose to use parts of $1/12$, $1/48$ and $1/192$ of the total sphere.
+Our main motivation was to build a "large" dataset with a relatively low number of cosmological maps.
+In term of neural network, the availlable implementation of \cite{cohen2018sphericalcnn,kondor2018clebsch} for spherical CNNs and Clebsh-Gordan CNNs are not scalable enough to be trained on the cosmological maps dataset and do not use the HEALPix sampling.
+Hence a comparison with thee methods requires a different setting, which far beyond the scope of our contribution.
+Nevertheless, this comparizon is important and we preparing a second contribution where it will be conducted.
+
+\nati{We could compare the price of one convolution. What do you think? We can write the theoretical complexity. This is a sensitive point! }
 
@@
 \todo{Assigned: @Nati, @Michael, @Tomek}
-\nati{
-This is something we should be able to do.
-Actually, since we used 1/12 of the sphere, all the pixel grids we use are somehow squared.
+
+\nati{\textbf{Very important point!!!}
+\begin{itemize}
+  \item We will do this comparizon...
+  \item Since we used 1/12 of the sphere, all the pixel grids we use are somehow squared.
 I am now using this as a projection.
@@
 Or do you know how to do the projection in a simple and efficient manner?
-I am trying to make the comparizon right now
-More important, I think that traditional 2D CNNs will be as good as our algorithm. We should be very careful in the way we formulate this in our answer and in the paper.}
+  \item I think that traditional 2D CNNs will be as good as our algorithm. We should be very careful in the way we formulate this in our answer and in the paper.
+\end{itemize}
+}
 
@@
 \end{mdframed}
-\nati{@Nati, @Michael, @Tomek
-
-Problem here is that rotation is not simple on a sphere, it will probably be slow and I will have to break a lot of code to do it.
-Nevertheless, I believe that in theory, CNN will match FCN when we do enought rotation. Should we answer that? @mMichael: what do you think?
+\todo{Assigned: @Nati, @Michael, @Tomek}
+
+Theoretically, providing that the FCN and the CNN have the same modelization power (i.e, the FCN does not have more or larger layers) and assuming the convolution would be Truly invariant to rotation, the CNN could never exceed the FCN for truly rotational invariant data.
+However, assuming enought augmentation (as suggested by the reviewer) and training, the CNN should get to the level of the FCN.
+In practice, this would require more training as the CNN has to learn the invariance.
+The point of defining a FCN instead of a CNN is to avoid the complexity of making this augmention.
+Hence we did not implement it.
+Nevertheless, it is an interesting point worth discussion in the paper.
+We updated the manuscript accordingly.
+\todo{Do it}
+
+\nati{
+Technically, testing this is complicated as rotation on HEALPix are complicated and expensive. We probably will have to break a lot of code to do it.
+
+@Michael: what do you think?
 }
@@
 \end{mdframed}
+Thank you very much for your comments. We adressed them to the best we could.
 
@@
 
-\todo{Dear reviewer, this is an excellente question. We have have made the choice to takle quantitatively and theoretically the subject of convergence because of its complexity.
-
-Very good question: but too complex answer for this paper. This is kept for a future contribution. + explain why}
+This is a good question and a fair request.
+Problematically, we cannot provide such a plot without solving the theoretical problem first.
+Indeed to experimentally show convergence, we need to actually build a series of graph Laplacian that converges toward the Laplace Beltrami operator.
+This far more complicated than building one Laplacian and observe some similarities between the two operators.
+
+This is actually a problem we are currently investigating. We plan to make a separate contribution.
 
@@
 
-\todo{Yes, it is likely that we are, + graph learning?}
+Yes we are investigating the question of graph weights.
+As suggested in the previous, the weighting scheme used is very important for our laplacian to approach the true Laplace Beltrami operator.
+Using a more appropriate weighting scheme, one could hope for a more rotational invariant convolution and a faster convergence rate of the opertor.
+\nati{@michael, how much shall we say here?}
 
@@
 \end{mdframed}
-\nati{I totally agree with the reviewer, but I think this is only a formulation issue.
-By the way, this mean that the reviewer is knowledgable with ML, and may be Bayesian.
-He might be working on another spherical approach.}
+
+We agree with the reviewer. We actually misformulate the this sentence. We have reformulate it as:
+\begin{mdframed}[style=manuscript] 
+Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the confidence of the network that the input sample belongs to class $i$.
+Note that in general, this probability distribution does not correspond to the true posterior distribution $p(y|x)$.
+\end{mdframed}
+
+\nati{By the way, this mean that the reviewer is knowledgable with ML, and may be Bayesian. He might be working on another spherical approach.}
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assigned: @michael}
 
@@
 \end{mdframed}
-\todo{Answer}
+In the work of \cite{kondor2018clebsch}, the convolution is perfomed in the spectral (harmonic) domain with a simple Adamar product.
+Instead of recomposing the signal and applying a traditional non-linearity such as "relu" in the pixel domain, \cite{kondor2018clebsch} propose to apply directly a Clebsch–Gordan product in the spectral domain.
+As a non-linear operation preserving the rotation equivariance, it is considered as the non-linearity of the neural network.
+
+We have modified the manuscript as:
+\begin{mdframed}[style=manuscript] 
+While this clever trick lowers the complexity of the convolution (Adamar product in the spectral domain) to $\bO(N_{pix})$, the non-linearity (Clebsch–Gordan product) is $\bO(N_{pix}^{3/2})$.
+\end{mdframed}
+\nati{Should we be more clear in the paper?}
 
@@
 \end{mdframed}
-\todo{Answer}
+When comparing the speed, we used a single core CPU implemention of the graph convolution. We believe that this comparizon is fair.
+\nati{Is this sufficent?}
 
@@
 \end{mdframed}
-\todo{Answer + probably}
+
+In the current version of the manuscript and the code, we simply fitted a few $t$ to match the different $\sigma$.
+In theory, there should be a connection between the two values providing the graph Laplacian has converged toward the Laplace Beltrami operator.
+Again, this is left for a futur contribution.
 
@@
 \end{mdframed}
-\todo{Yes, but it is complicated with graphs}
+We are thinking about it.
+However, as the graph framework we are using only works with radial filters, it is not a simple question.
+One simple trick to make network sensitive to direction is to add a per channel fully connected layers.
+We are currently investigating other potential graph techniques that would lead to non-radial kernels.
 
@@
 \end{mdframed}
+\todo{Assigned @tomek. 
+This reviewer really spend the time. We should say something.}
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assigned: @tomek, @michael}
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assigned: @tomek}
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assigned: @all}
+\nati{What do you think? This avoid repetition. But we could be more consistent...}
 
@@
 \end{mdframed}
-\todo{Answer}
+Thank you for the suggestion. We have made the paper consistent.
+\nati{@all, when you read the paper, please check that I did not forget some of them. Every layer has be changed to math symbole as we use them like function. For example SM becomes $SM$.}
 
@@
 \end{mdframed}
-\todo{Answer}
+We have modified the manuscript according to the reviewer suggestion.
 
@@
 \end{mdframed}
-\todo{Answer}
+This sentence has been reformulated as:
+\begin{mdframed}[style=manuscript] 
+We consider the sky maps rotationial invariant as in our case rotating maps on the sphere doesn't change their interpretation since only the statistics of the maps are relevant.
+\end{mdframed}
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{assigned: @tomek}
+\nati{I am not sure of the english here.}
 
@@
 \end{mdframed}
-\todo{Answer}
+Thank you for spotting this mistake.
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{assigned: @michael}
 
@@
 \end{mdframed}
-\todo{Answer}
+This has been rephrased as:
+\begin{mdframed}[style=manuscript] 
+Likewise, down-sampling can be achieved by keeping one pixel every $n$ pixels with $n=2$ being very common.
+\end{mdframed}
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{assigned: @tomek}
 
@@
 \end{mdframed}
-\todo{Answer}
+This has been corrected.
 
@@
 \end{mdframed}
-\todo{Answer}
+\nati{This seems clear to me. Specifying what $\mathbb{R}_+$ is would be a bit too much I believe. @all -> is it also for you?}
 
@@
 \end{mdframed}
-\todo{Answer}
+We followed both of the reviewer suggestions.
 
@@
 \end{mdframed}
-\todo{Answer}
-
-\begin{mdframed}[style=comment] 
-... where $T_ig[j] = g[i − j]$ is, up to a flip, a translation operator.
+We changed the manuscript according to the reviewer suggestion.
+
+\begin{mdframed}[style=comment] 
+... where $T_ig[j]=g[i-j]$ is, up to a flip, a translation operator.
 
@@
 \end{mdframed}
-\todo{Answer}
+
+We updated the manuscript using:
+\begin{mdframed}[style=manuscript] 
+where $T_i g[j] = g[i-j]$ is, up to a flip ($g[i-j]$ instead of $g[i+j]$), a translation operator.
+\end{mdframed}
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assign: @michael, @tomek}
+\nati{I do not know what we should do.}
 
@@
 \end{mdframed}
-\todo{Answer}
-
-\begin{mdframed}[style=comment] 
-... where $\tilde{\bf{L}}= \frac{2}{\lambda_{max}}\bf{L}−\bf{I}=−\frac{2}{\lambda_{max}}\bf{D}^{−1/2}\bf{W}\bf{D}^{−1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\Lambda}$ in [−1, 1].
+We mean "column" and have corrected the manuscript.
+
+\begin{mdframed}[style=comment] 
+... where $\tilde{\bf{L}}= \frac{2}{\lambda_{max}}\bf{L}-\bf{I}=-\frac{2}{\lambda_{max}}\bf{D}^{-1/2}\bf{W}\bf{D}^{-1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\Lambda}$ in [-1, 1].
 
@@
 \end{mdframed}
-\todo{Answer}
+Inspired by the reviewer suggestion, we changed the layout of that equation.
 
@@
 \end{mdframed}
-\todo{Answer}
+Thanks for the suggestion. We changed the manuscript.
 
@@
 \end{mdframed}
-\todo{Answer}
+Thanks for spotting this.
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assigned: @tomek}
+\nati{I think the "as" is correct here. We use it for "because". Not sure...}
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assigned: @tomek}
+\nati{I prefer the version we have. But I leave it up to you to decide.}
 
@@
 \end{mdframed}
-\todo{Answer}
+Thank you for spotting this mistake. We have corrected the manuscript.
 
@@
 \end{mdframed}
-\todo{Answer}
+In fact, $p$ is defined as $p=\log_2(N_{side} / N'_{side})$. We have updated the manuscript with this clarification and with an equation environnment.
 
@@
 \end{mdframed}
-\todo{Answer}
+We have followed the reviewer suggestion.
 
@@
 \end{mdframed}
-\todo{Answer}
+We have removed the identity specification.
+\begin{mdframed}[style=manuscript] 
+A non-linear function $\sigma(\cdot)$ is applied after every linear $GC$ and $FC$ layer, except for the last $FC$ layer. 
+\end{mdframed}
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assigned: michael}
 
@@
 \end{mdframed}
-\todo{Answer}
+We agree with the reviewer and have updated the manuscript.
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assigned: @all}
+\nati{The manuscript seems clear to me. But let me know if you think otherwise.}
 
@@
 \end{mdframed}
-\todo{Answer}
+Thanks for spotting it. We have fixed this mistake.
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assigned: @michael, @nati}
+\nati{In an unsupervised setting, this can just not be computed... Specifying it seems redundant to me.}
 
@@
 \end{mdframed}
-\todo{Answer}
+We thank the reviewer for spotting this mistake. We have updated the manuscript.
 

### 2019-01-26 scnn.tex
going further in the rebuttal

@@
 First, the convolution should be equivariant to rotation, meaning that a rotation of the input implies the same rotation of the output.
-Sky maps are rotation invariant: rotating maps on the sphere doesn't change their interpretation, as only the statistics of the maps are relevant.
+\nati{We consider the sky maps rotationial invariant as in our case rotating maps on the sphere doesn't change their interpretation since only the statistics of the maps are relevant.}
 Depending on the task, we want the CNN to be either equivariant or invariant to rotation.
@@
 We give a practical demonstration of DeepSphere on cosmological model discrimination using maps of projected mass distribution on the sky \citep{chang2017curvedsky}.
-This kind of maps can be created using the gravitational lensing technique \citep[see][for review]{BartelmannSchneider2001weak}.
+These kind of maps can be created using the gravitational lensing technique \citep[see][for review]{BartelmannSchneider2001weak}.
 Our maps are similar to the ones used by \citep{schmelze2017cosmologicalmodel}.
@@
 On regular Euclidean domains, such as 1-dimensional time series or 2-dimensional images, a convolution can be efficiently implemented by sliding a localized convolution kernel (for example a patch of $5 \times 5$ pixels) in the signal domain.
-Likewise, down-sampling can be achieved by taking one pixel out of $n$.
+\nati{Likewise, down-sampling can be achieved by keeping one pixel every $n$ pixels with $n=2$ being very common.}
 Because of the irregular sampling, there is no straightforward way to define a convolution on the sphere directly in the pixel domain; convolutions are most often performed using spherical harmonics.
@@
 The localization operator $\T_i$ reads $\T_i h = h(\L) \b \delta^i = (h(\L))_i$, the $i$th column of $h(\L)$.
-This localization of the kernel $h$ can be useful to visualize kernels, as explained in~\ref{sec:filter_visualization}.
+This localization of the kernel $h$ can be useful to visualize kernels, as shown in an example of heat diffusion presented in~\ref{sec:filter_visualization}.
 If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another.
 While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular.
-However, when considering only parts of the sphere, one can observe important border effects (see \figref{border_effects} and~\ref{sec:border_effects}).
+However, when considering only parts of the sphere, one can observe important border effects (see ~\ref{sec:border_effects}).
 
@@
 \end{equation*}
-where $T_i g[j] = g[i-j]$ is, up to a flip, a translation operator.
+where $T_i g[j] = g[i-j]$ is, up to a flip ($g[i-j]$ instead of $g[i+j]$), a translation operator.
 Similarly as \eqnref{graph_convolution_spatial}, the convolution of the signal $f$ by a kernel $g$ is the scalar product of $f$ with translated versions $T_i g$ of the kernel $g$.
@@
 We note that restricting the graph convolutional kernel to a polynomial is similar to restricting the classical Euclidean convolution to a fixed-size patch.
-Similarly, each line of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an irregular patch of radius $K$.
+Similarly, each column of the matrix $\sum_{k=0}^K \theta_k \L^k$ defines an irregular patch of radius $K$.
 Hence, filters designed as polynomials of the Laplacian have local support in the vertex domain.
@@
 \end{equation}
-where $\tL = \frac{2}{\lambda_{max}} \L - \b{I} = -\frac{2}{\lambda_{max}} \D^{-1/2} \W \D^{-1/2}$ is the rescaled Laplacian with eigenvalues $\tilde{\b \Lambda}$ in $[-1, 1]$.
+where 
+\begin{equation*}
+\tL = \frac{2}{\lambda_{max}} \L - \b{I} = -\frac{2}{\lambda_{max}} \D^{-1/2} \W \D^{-1/2}
+\end{equation*}
+is the rescaled Laplacian with eigenvalues $\tilde{\b \Lambda}$ in $[-1, 1]$.
 $T_k(\cdot)$ is the Chebyshev polynomial of degree $k$ defined by the recursive relation $T_k(\tL) = 2\tL T_{k-1}(\tL) - T_{k-2}(\tL)$, $T_1(\tL) = \tL$, $T_0(\tL) = \b{I}$.
@@
 The cost of one such multiplication is $\bO(|\E| + |\V|)$.
-By construction of our graph, $|\E| < 8 N_{pix}$ and the overall computational cost of the convolution reduces to $\bO(N_{pix})$ operations.
-That is much more efficient than filtering with spherical harmonics, even though HEALPix was designed as an iso-latitude sampling that has a fast spherical transform.
-That is especially true for smooth kernels which require a low polynomial degree $K$.
+By construction of our graph, $|\E| < 8 N_{pix}$ and the overall computational cost of the convolution reduces to $\bO(N_{pix})$ operations and as such is much more efficient than filtering with spherical harmonics, even though HEALPix was designed as an iso-latitude sampling that has a fast spherical transform.
+This is especially true for smooth kernels which require a low polynomial degree $K$.
 \figref{filtering_speed} compares the speed of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
@@
 Pooling refers to the operation that summarizes the data supported on the merged sub-cells in one parent cell.
-Given a map $\x \in \R^{N_{pix}}$, pooling defines $\y \in \R^{N'_{pix}}$ such as
+Given a map $\x \in \R^{N_{pix}}$, pooling defines $\y \in \R^{N'_{pix}}$ such that
 \begin{equation} \label{eqn:pooling}
@@
 \end{equation}
-where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix} / {N'_{pix}}$ is the down-sampling factor, which for HEALPix is $| \C(i) | = N_{pix} / {N_{pix}}' = (N_{side} / N'_{side})^2 = 4^p$.
+where $f$ is a function which operates on sets (possibly of varying sizes) and $N_{pix} / {N'_{pix}}$ is the down-sampling factor, which for HEALPix is 
+\begin{equation*}
+| \C(i) | = N_{pix} / {N_{pix}}' = (N_{side} / N'_{side})^2 = 4^p,
+\end{equation*}
+where $p=\log_2(N_{side} / N'_{side})$.
 That operation is often taken to be the maximum value, but it can be any permutation invariant operation, such as a sum or an average.
@@
 The general DeepSphere architecture, pictured in \figref{architecture}, is composed of many layers.
-The convolutional part, the head of the neural network, is composed of graph convolutional layers (GC), pooling layers (P), and batch normalization layers (BN).
-The tail is composed of multiple fully connected layers (FC) followed by an optional softmax layer (SM).
-A non-linear function $\sigma(\cdot)$ is applied after every linear GC and FC layer, except for the last FC layer where it is set to the identity.
+The convolutional part, the head of the neural network, is composed of graph convolutional layers ($GC$), pooling layers ($P$), and batch normalization layers ($BN$).
+The tail is composed of multiple fully connected layers ($FC$) followed by an optional softmax layer ($SM$) if the network is used for discrete classification.
+A non-linear function $\sigma(\cdot)$ is applied after every linear $GC$ and $FC$ layer, except for the last $FC$ layer.
 That operation is point-wise, i.e., $y_{ij} = \sigma(x_{ij})$ and $y_i = \sigma(x_i)$ for matrices $\X, \Y$ and vectors $\x, \y$.
@@
 
-Given a matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$, a GC layer computes $\Y = GC(\X) = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels (and nodes), $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
+Given a matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$, a $GC$ layer computes $\Y = GC(\X) = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels (and nodes), $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
 Using the efficient graph convolution from \eqnref{graph_convolution_cheby}, each output feature map is computed as
@@
 \end{equation*}
-As such, a GC layer is composed of $F_{in} \times F_{out}$ filters, each parameterized by $K$ numbers (see \secref{efficient_convolution}). A bias term $\b b \in \R^{F_{out}}$ is jointly optimized.
+As such, a $GC$ layer is composed of $F_{in} \times F_{out}$ filters, each parameterized by $K$ numbers (see \secref{efficient_convolution}). A bias term $\b b \in \R^{F_{out}}$ is jointly optimized.
 
@@
 where $\W \in \R^{F_{out} \times F_{in}}$ and $\b b \in \R^{F_{out}}$ are the parameters to be learned.
-Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last GC (or the output $\Y \in \R^{N_{stat} \times F_{out}}$ of the ST), is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first FC, where $F_{in} = N_{pix} \times F_{out}$ (or $N_{stat} \times F_{out}$).
+Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last $GC$ (or the output $\Y \in \R^{N_{stat} \times F_{out}}$ of the $ST$), is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first $FC$, where $F_{in} = N_{pix} \times F_{out}$ (or $N_{stat} \times F_{out}$).
 
 The softmax layer is the last layer in a neural network engineered for classification.
-Given the output $\x \in \R^{N_{classes}}$ of the last FC (or ST), called the logits in the deep learning literature, the softmax layer outputs $\y = SM(\x)$ such that
+Given the output $\x \in \R^{N_{classes}}$ of the last $FC$ (or $ST$), called the logits in the deep learning literature, the softmax layer outputs $\y = SM(\x)$ such that
 \begin{equation*}
@@
 where $N_{classes}$ is the number of classes to discriminate.
-Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the probability that the input sample belongs to class $i$.
-This last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.
+\nati{Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the confidence of the network that the input sample belongs to class $i$.
+Note that in general, this probability distribution does not correspond to the true posterior distribution $p(y|x)$.} This last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.
 
@@
 Segmentation and feature detection \citep{Amsel2007detecting} are examples of dense classification tasks.
-The output's size of the neural network depends on the task. See \tabref{tasks}.
+The size of the output of the neural network depends on the task. See \tabref{tasks}.
 
@@
 That field is isotropic and local, i.e., it forms a disk centered around the output pixel.
-Its radius is influenced by the polynomial order $K$ of GC layers (setting how far the convolution operation looks around), and the down-sampling factor of P layers if any.
+Its radius is influenced by the polynomial order $K$ of $GC$ layers (setting how far the convolution operation looks around), and the down-sampling factor of P layers if any.
 Its radius should be large enough to capture statistics of interest.
-For example, a small a partial sky observation can provide only limited information of cosmological relevance.
+For example, a partial sky observation can provide only limited information of cosmological relevance.
 On the other hand, looking at the whole sky is often superfluous and waste computations, as most interactions are local.
@@
 By treating each output pixel independently and in parallel, this architecture is a principled way to perform rotation equivariant operations.
-Rotation equivariance means that the rotation operation commutes with the neural network, i.e., a rotation of the input implies the same rotation of the output.\footnote{Small errors will however appear as GC layers are not exactly equivariant due to the small discrepancy between the graph Fourier modes and the spherical harmonics.
+Rotation equivariance means that the rotation operation commutes with the neural network, i.e., a rotation of the input implies the same rotation of the output.\footnote{Small errors will however appear as $GC$ layers are not exactly equivariant due to the small discrepancy between the graph Fourier modes and the spherical harmonics.
 See \ref{sec:comparison_spherical_harmonics}.}
@@
 
-By replacing the average by a FC layer, one gets the standard convolutional neural network (CNN), which is a generalization of the FCN.
-Indeed, the AV layer is a FC layer where all the entries of $\W$ in \eqnref{fc_layer} are equal to $1/N_{pix}$ and $\b b = \b 0$.
+By replacing the average by a $FC$ layer, one gets the standard convolutional neural network (CNN), which is a generalization of the FCN.
+Indeed, the $AV$ layer is a $FC$ layer where all the entries of $\W$ in \eqnref{fc_layer} are equal to $1/N_{pix}$ and $\b b = \b 0$.
 By dropping rotation invariance, CNNs learn where to put attention on the domain.
@@
 \begin{equation*}
-	NN = FC \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC.
+	NN = FC \circ \sigma \circ F \circ P \circ \sigma \circ BN \circ GC.
 \end{equation*}
@@
 % agnostic to the size of the input data, i.e., it can classify maps which do not have the same number of pixels.
-Such global summarization as the AV layer is commonly used along graph convolutions to classify graphs of varying sizes (as it is invariant to node permutation) \citep{duvenaud2015gcn, li2015gatedgnn}.
+Such global summarization as the $AV$ layer is commonly used along graph convolutions to classify graphs of varying sizes (as it is invariant to node permutation) \citep{duvenaud2015gcn, li2015gatedgnn}.
 As such, CNNs should only be used if rotation invariance is undesired.
 
-All the above architectures can be used for classification (instead of regression) by appending a SM layer.
+All the above architectures can be used for classification (instead of regression) by appending a $SM$ layer.
 An example FCN for global classification is therefore
@@
 \end{equation*}
-Similarly, we emphasize that the use of FC and AV layers is the sole difference between a neural network engineered for global or dense prediction.
+Similarly, we emphasize that the use of $FC$ and $AV$ layers is the sole difference between a neural network engineered for global or dense prediction.
 
@@
 Again, take $N_{pix} = 1$ for global regression.
-We emphasize that the cost function and the SM layer is the sole difference between a neural network engineered for classification or regression.
+We emphasize that the cost function and the $SM$ layer are the sole differences between a neural network engineered for classification or regression.
 
@@
 As such, the SHT is only performed once on the input (no back and forth SHT between each layer).
-While this clever trick lowers the complexity of the convolution to $\bO(N_{pix})$, the non-linearity is $\bO(N_{pix}^{3/2})$.
+\nati{While this clever trick lowers the complexity of the convolution (Adamar product in the spectral domain) to $\bO(N_{pix})$, the non-linearity (Clebsch–Gordan product) is $\bO(N_{pix}^{3/2})$.}
 This work is another indication that there might be a $\Omega(N_{pix}^{3/2})$ computational lower bound for the proper treatment of rotation equivariance with the spherical harmonics.
@@
 The layers $L_1$ to $L_5$ build the statistical evidence to classify each pixel of a down-sampled sphere.
-The last GC layer acts as a linear classifier and outputs two (non-normalized) predictions.
-The AV layer averages these predictions.
-Probabilities are computed by the SM layer.
+The last $GC$ layer acts as a linear classifier and outputs two (non-normalized) predictions.
+The $AV$ layer averages these predictions.
+Probabilities are computed by the $SM$ layer.
 
@@
 
-\section{Border effects}
-\label{sec:border_effects}
-
-One should not forget that a significant part of our analysis is done with a full sphere and that in practice we often use only part of the graph as the data may be incomplete (see \figref{example_maps}).
-In this case, the graph setting used through this contribution correspond to assume reflective border conditions.
-It is irrelevant when working on the complete sphere as this surface has no border. Nevertheless, dealing working with a subpart of the sphere, its border slightly affects the convolution.
-As depicted in \figref{border_effects}, a filter localized near the border of a part of the sphere (via $h(\L) \b \delta_i$) no longer has an isotropic profile.
-These border effects can, however, be mitigated by padding with zeros a small area around the part of interest.
-Moreover, as long as the training data comes from simulations with the same applied mask, we do not expect these effects to cause problems for the analysis.
-
-\begin{figure}[ht!]
-	\centering
-	\includegraphics[width=\linewidth]{border_effects}
-	\caption{Convolution kernel (also called filter) $h$ localized in the center and left corner of a surface.
-A filter is localized on a pixel $i$ as $\T_i h = h(\L) \b \delta_i$ (see \secref{graph_convolution} and \eqnref{graph_convolution_spatial}).
-The graph is built from $1/12^\text{th}$ of the sphere at $N_{side} = 16$.
-The filter is not isotropic anymore when localized on the left corner due to border effects.
-The graph representation of a manifold assumes reflective border conditions.}
-	\label{fig:border_effects}
-\end{figure}
-
 \section{Example: heat diffusion}
@@
 As a second visualization, we observe the kernel directly on the sphere.
-As the kernel $K_t$ is defined in the graph spectral domain, we convolve a Kroneker to obtain a representation on the sphere.
+As the kernel $K_t$ is defined in the graph spectral domain, we convolve a Kroneker $\delta$  to obtain a representation on the sphere.
 We then plot the result with a gnomonic projection.
 For our third visualization, we leverage the fact that we are working on the sphere and hence theoretically have  spherical filters (up to the irregularities of the sampling).
-We plot the section of the convoluted Kroneker.
-To do so, we convolve a Kroneker on the nodes along the equator and use the equator for our section.
-Note that, because of the small irregularities in the HEALPix sampling, the second and the third methods are subject to small variations depending on the chosen position of the Kroneker.
+We plot the section of the convoluted Kroneker $\delta$ .
+To do so, we convolve a Kroneker $\delta$ on the nodes along the equator and use the equator for our section.
+Note that, because of the small irregularities in the HEALPix sampling, the second and the third methods are subject to small variations depending on the chosen position of the Kroneker $\delta$ .
+
+\section{Border effects}
+\label{sec:border_effects}
+
+One should not forget that a significant part of our analysis is done with a full sphere and that in practice we often use only part of the graph as the data may be incomplete (see \figref{example_maps}).
+In this case, the graph setting used through this contribution correspond to assume reflective border conditions.
+It is irrelevant when working on the complete sphere as this surface has no border. Nevertheless, dealing working with a subpart of the sphere, its border slightly affects the convolution.
+As depicted in \figref{border_effects}, a filter localized near the border of a part of the sphere (via $h(\L) \b \delta_i$) no longer has an isotropic profile.
+These border effects can, however, be mitigated by padding with zeros a small area around the part of interest.
+Moreover, as long as the training data comes from simulations with the same applied mask, we do not expect these effects to cause problems for the analysis.
+
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=\linewidth]{border_effects}
+	\caption{Convolution kernel (also called filter) $h$ localized in the center and left corner of a surface.
+A filter is localized on a pixel $i$ as $\T_i h = h(\L) \b \delta_i$ (see \secref{graph_convolution} and \eqnref{graph_convolution_spatial}).
+The graph is built from $1/12^\text{th}$ of the sphere at $N_{side} = 16$.
+The filter is not isotropic anymore when localized on the left corner due to border effects.
+The graph representation of a manifold assumes reflective border conditions.}
+	\label{fig:border_effects}
+\end{figure}
 

### 2019-01-27 rebuttal.tex
end of the first pass

@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assign:  @nati, @michael. \nati{@micheal, please check carefully this one, also in the text, I am not sure my notation is correct}}
+
+According to us, the goal of training is to minimize the emprical risk, which does not contain the expectation.
+On the contrary, the goal of learning is to minimize the expected risk, i.e.
+we additionally do not want to overfit the training set.
+Hence we left "learning" in the text.
+Nevertheless, we specified the expectation operator.
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assign: @nati, @michael, \nati{again I disagree with the reviewer}}
+
+We are not sure, we understand the reviewer.
+Back-propagation is a technique to compute the gradients and not to perform the update of the parameter.
+The latter is done with SGD.
+So we believe that the original formulation of our sentence is more accurate than the reviewer proposition.
 
@@
 \end{mdframed}
-\todo{Answer}
+This mistake has been corrected.
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assigned: @all}
+
+\nati{The reviewer is correct.
+Our justification is shaddy.
+I am not sure how to make this clear, without writting too much.
+It is kind of a general consent that smoothness in one domain implies loclization in the other.
+The reason is that for the continuous Fourier transform, we have:
+\begin{equation*}
+\widehat{f(t\cdot)}(\omega)=\frac{1}{t}\hat{f}\left(\frac{\omega}{t}\right). 
+\end{equation*}
+Hence by concentrating $f$ in the time domain, i.e. making $t$ smaller, we also reduce the derivative of $\widehat{f(t\cdot)}$ in the spectral domain, making it smoother.
+Heisenberg uncertainty principle bounds the concentration in both domains simultaneously, i.e. we have (to be checked if added to the paper)
+\begin{equation*}
+\text{var}({f})\text{var}({\hat{f}}) \geq \frac{1}{16 \pi^2}
+\end{equation*}
+Hence the theorem says that you cannot concentrate abritrarily in one domain without de-concentrating in the other.
+
+Now the question is: how do we fix the text? Also Heisenberg does not exist in the discrete case...
+}
 
@@
 \end{mdframed}
-\todo{Answer}
+Indeed, our method can be applied only on a part or the sphere. We have corrected the text.
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assign @michael}
 
@@
 \end{mdframed}
-\todo{Answer}
+We have corrected this formulation according to the reviewer suggestion.
 
@@
 \end{mdframed}
-\todo{Answer}
+We have updated the manuscript accordingly.
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assigned @Tomek}
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assign: @Tomek}
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assign: @all}
+\nati{I think that the primary goal of adding noise is the make the problem harder, and show robust prediction, not the make the dataset larger...
+Hence I disagree with the reviewer.
+What do you think?}
+
+The primary goal of the noise addition is the make the problem harder and show robust prediction. We use it to augment our dataset as well. Hence we believe that the correct formulation is suitable.
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assigned @michael}
+\nati{Should we simply say "normalized network score"? I do not know...}
 
@@
 \end{mdframed}
-\todo{Answer}
+We followed the reviewer suggestions.
 
@@
 \end{mdframed}
-\todo{Answer}
+We corrected the manuscript.
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assign: @nati, @michael}
+\nati{We would need an appendix to do that. It is the last figure of the figures notebook (expected filter). I could spend two hours and write some equation... @michael, what do you think?}
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assign: @all}
+\nati{The problem is that random filters are picky as well and look very similar. Should we say that? I to not think a colorbar is necessary since there is number on the top plot. Do you agree?}
+
+We decided to not add a colorbar as scale information is already present in the top plot of the figure.
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assign: @tomek -> \nati{I corrected it with "which". Do you agree? }}
 
@@
 \end{mdframed}
-\todo{Answer}
+"it" refer to "graphs" in general. We have updated the manuscript.
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{Assign: @nati, @michael}
 
@@
 \end{mdframed}
-\todo{Answer}
+\todo{@assign: Tomek}
 
@@
 \end{mdframed}
-\todo{Answer}
+We have corrected this mistake according the reviewer suggestion.
 
@@
 \end{mdframed}
-\todo{Answer}
+We have clarifed the sentence as:
+\begin{mdframed}[style=manuscript] 
+Furthermore, the harmonics ressemblance is another sign that the constructed graph is able to capture the spherical
+structure of the HEALPix sampling. 
+\end{mdframed}
 
@@
 
-- I think is might be another one of the most important points in the paper which allows you to justify why not being exact (like a spherical harmonic transform) is acceptable.
+- I think it might be another one of the most important points in the paper which allows you to justify why not being exact (like a spherical harmonic transform) is acceptable.
 If I were you I'd move this into the main body of the paper.
 \end{mdframed}
-\todo{Answer}
+\todo{Assign: @all, \nati{What do you think? I had the feeling we already have that in the main body of the paper. I cannot remember where though.}}
 
@@
 \end{mdframed}
-\todo{Answer}
+We have merged the three plot a an signal figure and adapted the text reference accordingly.
 
@@
 \end{mdframed}
-\todo{Answer}
+We build this plot in order to show the section of the filter. We believe that it might be easier to read than the gnomonic projection. We have modified the text as:
+\begin{mdframed}[style=manuscript] 
+For our third visualization (bottom), our goal is to plot the section of a filter.
+This visualization might be convenient as we theoretically have spherical filters (up to the irregularities of the sampling).
+The idea is to plot the section of the convolved Kroneker $\delta$.
+\end{mdframed}
 
@@
 \end{mdframed}
-\todo{Answer}
+We changed the sentence to:
+\begin{mdframed}[style=manuscript] 
+The error clearly converged such that adding more samples will not improve the classifier.
+\end{mdframed}
 
@@
 \end{mdframed}
-\todo{Answer}
+\nati{
+We changed the sentence as:
+\begin{mdframed}[style=manuscript] 
+The validation error might be slightly below the training error as the validation set is used to select hyper-parameters.
+\end{mdframed}
+For linear SVM, there is one hyper-parameter to tune. As we select the hyperparameter with the lowest validation error, it is possible that the validation error is lower than the training error.}
 
@@
 \end{mdframed}
-\todo{Final thanks + contact us?}
+We would like to thank the reviewer again for his exceptionally detailed review.
+We really appreciate his effort and the time he invested in his answers.
+His is welcome to contact us for additional information or discussion when the publication will be over.
 

### 2019-01-27 scnn.tex
end of the first pass

@@
 
-The goal of learning is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = \esp \left[ C \left( NN_\theta(\X), \bar \Y \right) \right]$.
+\nati{The goal of learning is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = \esp \left[ C \left( NN_\theta(\X), \bar \Y \right) \right]$, where $\esp$ is the expectation over the joint distribution $(\X, \bar \Y)$.}
 In general, that expectation cannot be computed as the data distribution is unknown.
@@
 A first approach, explored by \citep{boomsma2017spherical} for molecular modeling and \citep{su2017sphericalconv, coors2018spherenet} for omnidirectional imaging, is to use a 2D CNN on a discretization of the sphere that is a grid, such as the equirectangular projection (\figref{sphere_grids}, left panel), or a set of grids, such as the cubed-sphere defined by~\citep{ronchi1996cubed} (\figref{sphere_grids},  middle panel).
-As this formulation uses the standard 2D convolution, all the optimizations developed for images can be applied, what makes it computationally efficient.
+As this formulation uses the standard 2D convolution, all the optimizations developed for images can be applied, which makes it computationally efficient.
 This approach is applicable to the many pixelizations that are based on a regular subdivision of a base polyhedron, such as HEALPix. Each base polyhedron then forms a grid.
@@
 
-All the above methods cannot be easily accelerated when the data lies on a part of the sphere only.
+\nati{All the presented methods, but our, cannot be easily accelerated when the data lies on a part of the sphere only.}
 That is an important use case in cosmology as measurements are often partial, i.e., whole sky maps are rare.
@@
 These maps are similar to those created with gravitational lensing techniques \citep{chang2017curvedsky}.
-The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters.
+The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters (see \secref{data} for details).
 The classification methods were trained to predict a label from a HEALPix map.
@@
 	\caption{Power spectrum densities of the noiseless maps.
-		To prevent the cosmological models to be distinguished by their power spectra alone, the maps have been smoothed with a Gaussian kernel of radius $3$ arcmins to remove high frequencies ($\ell>1000$).}
+		To prevent the cosmological models from being distinguished by their power spectra alone, the maps have been smoothed with a Gaussian kernel of radius $3$ arcmins to remove high frequencies ($\ell>1000$).}
 	\label{fig:psd_sigma3}
@@
 We indeed observe that the problem is made more difficult as the sample size decreases, and the noise increases.
-As less pixels are available to make a decision about a sample, the algorithms have access to less information and make more mistakes.
+As fewer pixels are available to make a decision about a sample, the algorithms have access to less information and thus cannot classify as well.
 As the noise increases, the useful information gets diluted in irrelevant data, i.e., the signal-to-noise ratio (SNR) diminishes.
@@
 Third, we recommend initializing the Chebyshev coefficients with a centered Gaussian distribution with standard deviation $\sqrt{2/(F_{in} \times (K + 0.5))}$, where $K$ is the degree of the Chebyshev polynomials and $F_{in}$ the number of input channels.
-This standard deviation has the property to keep the energy of the signal more or less constant across layers\footnote{We derived this rule from the Chebyshev polynomial equations and some empirical experiments.}.
+This standard deviation has the property of keeping the energy of the signal more or less constant across layers\footnote{We derived this rule from the Chebyshev polynomial equations and some empirical experiments.}.
 % Nati to Michael: The problem with the previous claim is that it depends on the non-linarity. Furthermore, does it make sense to make such a claim if we use batch norm?
@@
 
-The fact that a graph representation of the disretised sphere enables an efficient convolution relaxes the iso-latitude constraint on the design of sampling schemes who aim to enable fast convolutions.
-In the long term, it might enable researchers to consider sampling schemes with different trade-offs, or remove the need for schemes and interpolation altogether and simply consider the positions at which measures were taken.
+The fact that a graph representation of the discretised sphere enables an efficient convolution relaxes the iso-latitude constraint on the design of sampling schemes which aim to enable fast convolutions.
+In the long term, graphs might enable researchers to consider sampling schemes with different trade-offs, or remove the need for schemes and interpolation altogether and simply consider the positions at which measures were taken.
 
@@
 
-Furthermore, this result is another sign that the constructed graph is able to capture the spherical
+Furthermore, the harmonics ressemblance is another sign that the constructed graph is able to capture the spherical
 structure of the HEALPix sampling. In some applications, where the
@@
 \centering
-\includegraphics[width=\linewidth]{gaussian_filters_spectral}
-\caption{Visualization of the convolution kernel $K_t(x)=e^{-\tau t x}$ in spectral domain.}
-\vspace{0.3in}
-\includegraphics[width=\linewidth]{gaussian_filters_gnomonic}
-\caption{Visualization of the convolution kernel $K_t(x)=e^{-\tau t x}$: cross-section of the kernel through the pixels along the equator.}
-\vspace{0.3in}
-\includegraphics[width=\linewidth]{gaussian_filters_section}
-\caption{Visualization of the convolution kernel $K_t(x)=e^{-\tau t x}$ in a gnomonic projection.}
+\includegraphics[width=\linewidth]{gaussian_filters_spectral}\\
+\vspace{0.2in}
+\includegraphics[width=\linewidth]{gaussian_filters_gnomonic}\\
+\vspace{0.2in}
+\hspace{0.3cm}\includegraphics[width=0.95\linewidth]{gaussian_filters_section}
+\caption{\nati{Visualization of the convolution kernel $K_t(x)=e^{-\tau t x}$.
+(top) Spectral domain.
+(middle) Cross-section of the kernel through the pixels along the equator.
+(bottom) Gnomonic projection.}}
 \label{fig:gaussian_filters_visualization}
@@
 In \figref{gaussian_filters_visualization}, we further leverage this example to present the three visualizations of a HEALPix graph convolution kernel.
-We remember that the convolution kernel resulting from the heat diffusion is defined as $K_t(x)=e^{-\tau t x}$. For our visualization, we simply plot this function, i.e., we evaluate $K_t$
+We remember that the convolution kernel resulting from the heat diffusion is defined as $K_t(x)=e^{-\tau t x}$. For our (top) visualization, we simply plot this function, i.e., we evaluate $K_t$
 at the graph eigenvalues $\text{diag}(\bLambda)$. Note that, the lower eigenvalues $\lambda$ correspond to the lower frequencies, i.e., the spectral mode with less variation.
-As a second visualization, we observe the kernel directly on the sphere.
+As a second visualization (middle), we observe the kernel directly on the sphere.
 As the kernel $K_t$ is defined in the graph spectral domain, we convolve a Kroneker $\delta$  to obtain a representation on the sphere.
 We then plot the result with a gnomonic projection.
-For our third visualization, we leverage the fact that we are working on the sphere and hence theoretically have  spherical filters (up to the irregularities of the sampling).
-We plot the section of the convoluted Kroneker $\delta$ .
+\nati{For our third visualization (bottom), our goal is to plot the section of a filter.
+This visualization might be convenient as we theoretically have spherical filters (up to the irregularities of the sampling).
+The idea is to plot the section of the convolved Kroneker $\delta$.}
 To do so, we convolve a Kroneker $\delta$ on the nodes along the equator and use the equator for our section.
@@
 In this case, the graph setting used through this contribution correspond to assume reflective border conditions.
-It is irrelevant when working on the complete sphere as this surface has no border. Nevertheless, dealing working with a subpart of the sphere, its border slightly affects the convolution.
+It is irrelevant when working on the complete sphere as this surface has no border. Nevertheless, when working with a subpart of the sphere, its border slightly affects the convolution.
 As depicted in \figref{border_effects}, a filter localized near the border of a part of the sphere (via $h(\L) \b \delta_i$) no longer has an isotropic profile.
@@
 	\caption{Error w.r.t.\ the number of training samples for histogram features and the linear SVM (setting: order $o=2$, relative noise level 1.5).
-The error clearly converged and adding more samples will not help.
-The validation error might be slightly below the training error as it is used to select hyper-parameters.}
+The error clearly converged such that adding more samples will not improve the classifier.
+The validation error might be slightly below the training error as the validation set is used to select hyper-parameters.}
 	\label{fig:hist_error_evolution}
@@
 
-The data is generated for the present analysis is based on the fast approximate N-Body simulation code \pkg{L-PICOLA} \citep{howlett2015lpicola}.
+The data generated for the present analysis is based on the fast approximate N-Body simulation code \pkg{L-PICOLA} \citep{howlett2015lpicola}.
 For our purposes, we chose a simulation volume $V_\mathrm{sim} = (4200 \, h^{-1}\, \mathrm{Mpc})^3$, a total number of particles $N_\mathrm{part}^\mathrm{sim} = 1024^3$ placed on a mesh of size $N_\mathrm{mesh}^\mathrm{sim} = 2048^3$.

### 2019-01-27 rebuttal.tex
after a small second pass

@@
 
-The authors would like to thank the reviewers for their comments, which significantly helped improving the manuscript. We believe we have addressed all the issues raised in the following rebuttal. 
+The authors would like to thank the reviewers for their comments, which significantly helped improve the manuscript. We believe we have addressed all the issues raised in the following rebuttal. 
 %  For each comment, we have first highlighted the issue, then we provided an answer, and finally we described how the manuscript was adjusted.
@@
 
-Dear reviewer, we thank you for reading our paper and providing comments.
-They have helped us improving our manuscript.
-In this rebuttal, you can find a detailed answer to all the points you mentioned.
+Dear reviewer, we thank you for reading our paper and providing comments. They have helped us improve our manuscript. In this rebuttal, you can find a detailed answer to all the points you mentioned.
 
@@
 \todo{Assigned: @nati, @michael}
-The intuition of the reviewer is correct, theorectially using the raw data, \emph{an SVM or even a standard fully connected neural network (NN) would perform a lot better.} In practice, this those models are limited by the computational power and the dataset size.
-
-We had actually tried training an SVM on the raw data but were unable to obtain over $60\%$ accuracy in cases where all the other models were close to $100\%$.
-The classifier would either overfit or be over-regularized.
-For that reason, we decided, not to report the SVM results in the paper.
+The intuition of the reviewer is correct.
+Theoretically, using the raw data, \emph{an SVM or even a standard fully connected neural network (NN) would perform a lot better.} In practice, this those models are limited by the computational power and the dataset size.
+
+We actually tried training an SVM on the raw data but were unable to obtain over $60\%$ accuracy in the easiest cases where all the other tested models were close to $100\%$.
+Practically, the classifier would either overfit or be over-regularized.
+For that reason, we decided, not to report the raw-data SVM results in the paper.
 \nati{FYI, I did try again to be entirely sure about it.}
 
-A model based on a fully connected neural network, as suggested by the reviewer, will contains a very large amount of weights severly limiting what can be tested with conventional hardware.
-In our case the input number of pixels (for order $1$) is $1024^2$ which severly limits the number of neurons that can be used in the architecture.
+A model based on a fully connected neural network, as suggested by the reviewer, contains a very large number of weights which severely restricts what can be tested with conventional hardware.
+In our case the input number of pixels (for order $1$) is $1024^2$ which limits the number of neurons that can be used in the architecture.
 For the completeness of this answer, we did try a fully connected NN.
-Practially, in the first layer, we were only able to $128$ neurons before hitting an out of memory errors.
-In this setting, with an relative amount of noise of $0.5$, we were unable to regularize the network such that it would actually classify the validation set.
-Note that all calssifiers performed well (close to $100\%$ accuracy) in this particular setting.
-Similar conclusion were observed with other setting, even when increasing the number of neurons for small part of the sphere (order $2$ and $4$).
-
-This being said, the reviewer comment is justified and we will add these information to the paper.
-
-\todo{Add it in the paper... Make clear that CNN is so much better than fully connected + say that SVM on he raw features does not work.}
+Practically, in the first layer, we were only able to $128$ neurons before hitting an out of memory errors.
+In this setting, with a relative amount of noise of $0.5$, we were unable to regularize the network such that it would actually classify the validation set.
+Note that all reported classifiers performed well (close to $100\%$ accuracy) in this particular setting.
+Similar conclusions were observed with other settings.
+%Furthermore, the harmonic resemblance is another sign that the constructed graph is able to capture the spherical
+structure of the HEALPix sampling. , even when increasing the number of neurons for small part of the sphere (order $2$ and $4$).
+
+This being said, the reviewer comment is justified and we will add this information to the paper.
+
+\todo{Add it in the paper... Make clear that CNN is so much better than fully connected + say that SVM on the raw features does not work.}
 
@@
 Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
-Indeed, \cite{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the Manifold and a fully connected graph built with exponentially decaying weights.
+Indeed, \cite{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the manifold and a fully connected graph built with exponentially decaying weights.
 While our construction will not exactly respect the setting defined by \cite{belkin2007convergence} (the sampling is not uniform and the graph is not fully connected), we observe empirically strong evidence of convergence.
 \end{mdframed}
-We are aware that this particular point could be more detailled.
+We are aware that this particular point could be more detailed.
 Nevertheless, we believe that a deeper discussion does not belong to this paper.
@@
 
-Since we do not have any convergence result yet, we are not usure about how the projection error evolves.
-However, if there is convergence (and we believe there is), then the eigenvector associated with the lowest $\ell$ probably converge first.
+Since we do not have any convergence result yet, we are not sure about how the projection error evolves.
+However, if there is convergence (and we believe there is), then the eigenvectors associated with the lowest $\ell$ probably converge first.
 
@@
 
-In the experiment shown if Figure 4, we only care about speed and not about the filter itself (we could have taken any filter).
-The main reason is that in the context of neural network, filters will be learned anyway.
-Libsharp is probably not optimized for Gaussian smoothing, but this experiment should not be limted to Gaussian filter.
-We intend to report on the general filter speed and use conveniently a Gaussian.
+In the experiment shown if Figure 4, we only care about speed and not about the filter itself (we could have chosen any filter).
+The main reason is that in the context of neural networks, filters will be learned and hence is not predefined.
+While, libsharp is probably not optimized for Gaussian smoothing, in this experiment we intend to report on the general filter speed and use conveniently a Gaussian.
 
@@
 Our feeling is that in its current state, it probably does not have the required precision to be usable in a high precision setting.
-Nevertheless, theoretical improvement on the convergence side could definitly makes it competitive.
+Nevertheless, theoretical improvement on the convergence side could potentially make it competitive.
 
@@
 Our main motivation was to build a "large" dataset with a relatively low number of cosmological maps.
-In term of neural network, the availlable implementation of \cite{cohen2018sphericalcnn,kondor2018clebsch} for spherical CNNs and Clebsh-Gordan CNNs are not scalable enough to be trained on the cosmological maps dataset and do not use the HEALPix sampling.
-Hence a comparison with thee methods requires a different setting, which far beyond the scope of our contribution.
-Nevertheless, this comparizon is important and we preparing a second contribution where it will be conducted.
+In terms of neural network, the available implementation of \cite{cohen2018sphericalcnn,kondor2018clebsch} for spherical CNNs and Clebsh-Gordan CNNs are not scalable enough to be trained on the cosmological maps dataset and do not use the HEALPix sampling.
+Hence a comparison with these methods requires a different setting, which far beyond the scope of our contribution.
+Nevertheless, this comparison is important and we are preparing a second contribution where it will be conducted.
 
@@
 \begin{itemize}
-  \item We will do this comparizon...
+  \item We can do this comparison...
   \item Since we used 1/12 of the sphere, all the pixel grids we use are somehow squared.
@@
 
-Theoretically, providing that the FCN and the CNN have the same modelization power (i.e, the FCN does not have more or larger layers) and assuming the convolution would be Truly invariant to rotation, the CNN could never exceed the FCN for truly rotational invariant data.
-However, assuming enought augmentation (as suggested by the reviewer) and training, the CNN should get to the level of the FCN.
+Theoretically, providing that the FCN and the CNN have the same modelisation power (i.e, the FCN does not have more or larger layers) and assuming the convolution would be truly invariant to rotation, the CNN could never exceed the FCN for truly rotational invariant data.
+However, assuming enough augmentation (as suggested by the reviewer) and training, the CNN should get to the level of the FCN.
 In practice, this would require more training as the CNN has to learn the invariance.
-The point of defining a FCN instead of a CNN is to avoid the complexity of making this augmention.
+The point of defining a FCN instead of a CNN is to avoid the complexity of augmenting the dataset.
 Hence we did not implement it.
@@
 \end{mdframed}
-Thank you very much for your comments. We adressed them to the best we could.
+Thank you very much for your comments. We addressed them to the best we could.
 
@@
 Problematically, we cannot provide such a plot without solving the theoretical problem first.
-Indeed to experimentally show convergence, we need to actually build a series of graph Laplacian that converges toward the Laplace Beltrami operator.
+Indeed to experimentally show convergence, we actually need to build a series of graph Laplacian that converges toward the Laplace Beltrami operator.
 This far more complicated than building one Laplacian and observe some similarities between the two operators.
@@
 
-Yes we are investigating the question of graph weights.
-As suggested in the previous, the weighting scheme used is very important for our laplacian to approach the true Laplace Beltrami operator.
-Using a more appropriate weighting scheme, one could hope for a more rotational invariant convolution and a faster convergence rate of the opertor.
+Yes, we are investigating the question of graph weights.
+As suggested in the previous comment, the weighting scheme used is very important for the graph Laplacian to approach the true Laplace Beltrami operator.
+Using a more appropriate weighting scheme, one could hope for a more rotational invariant convolution and a faster convergence rate of the operator.
 \nati{@michael, how much shall we say here?}
@@
 
-We agree with the reviewer. We actually misformulate the this sentence. We have reformulate it as:
+We agree with the reviewer. We actually misformulate this sentence. We have reformulated it as:
 \begin{mdframed}[style=manuscript] 
@@
 \end{mdframed}
-In the work of \cite{kondor2018clebsch}, the convolution is perfomed in the spectral (harmonic) domain with a simple Adamar product.
-Instead of recomposing the signal and applying a traditional non-linearity such as "relu" in the pixel domain, \cite{kondor2018clebsch} propose to apply directly a Clebsch–Gordan product in the spectral domain.
+In the work of \cite{kondor2018clebsch}, the convolution is performed in the spectral (harmonic) domain with a simple Adamar product.
+Instead of recomposing the signal and applying a traditional non-linearity such as "relu" in the pixel domain, \cite{kondor2018clebsch} proposes to directly apply a Clebsch–Gordan product in the spectral domain.
 As a non-linear operation preserving the rotation equivariance, it is considered as the non-linearity of the neural network.
@@
 \end{mdframed}
-\nati{Should we be more clear in the paper?}
+\nati{Should we be clearer in the paper?}
 
@@
 \end{mdframed}
-When comparing the speed, we used a single core CPU implemention of the graph convolution. We believe that this comparizon is fair.
-\nati{Is this sufficent?}
+When comparing the speed, we used a single-core CPU implementation of the graph convolution. We believe that this comparison is fair.
+\nati{Is this sufficient?}
 
@@
 \end{mdframed}
-\todo{Answer + compute the ratio of outside block energy (see Fig. A.12)}
+\todo{Assigned: @nati, @michael}
+We added a figure showing the percentage of mis-alignment with the spherical harmonics. We also moved Figure A.12 in the correct subsection.
+
+\begin{center}
+\includegraphics[width=0.5\linewidth]{figures/subspace_alignment_percentage.pdf}
+\end{center}
 
@@
 However, as the graph framework we are using only works with radial filters, it is not a simple question.
-One simple trick to make network sensitive to direction is to add a per channel fully connected layers.
+One simple trick to make the network sensitive to direction is to add a per-channel fully connected layers.
 We are currently investigating other potential graph techniques that would lead to non-radial kernels.
@@
 \todo{Assigned @tomek. 
-This reviewer really spend the time. We should say something.}
+This reviewer really spend the time. Should we say something here?}
 
@@
 \todo{Assigned: @tomek}
+\nati{I personally think it is better without separating the lines}
 
@@
 Thank you for the suggestion. We have made the paper consistent.
-\nati{@all, when you read the paper, please check that I did not forget some of them. Every layer has be changed to math symbole as we use them like function. For example SM becomes $SM$.}
+\nati{@all, when you read the paper, please check that I did not forget some of them. Every layer has been changed to math symbols as we use them like function. For example, SM becomes $SM$.}
 
@@
 \begin{mdframed}[style=manuscript] 
-We consider the sky maps rotationial invariant as in our case rotating maps on the sphere doesn't change their interpretation since only the statistics of the maps are relevant.
+We consider the sky maps rotational invariant as in our case rotating maps on the sphere doesn't change their interpretation since only the statistics of the maps are relevant.
 \end{mdframed}
@@
 \end{mdframed}
-Thank you for spotting this mistake.
+Thank you for spotting this mistake. We updated the manuscript.
 
@@
 \end{mdframed}
-In fact, $p$ is defined as $p=\log_2(N_{side} / N'_{side})$. We have updated the manuscript with this clarification and with an equation environnment.
+In fact, $p$ is defined as $p=\log_2(N_{side} / N'_{side})$. We have updated the manuscript with this clarification and with an equation environment.
 
@@
 \end{mdframed}
-\todo{Assigned: michael}
+\todo{Assigned: @michael}
 
@@
 \end{mdframed}
-\todo{Assign:  @nati, @michael. \nati{@micheal, please check carefully this one, also in the text, I am not sure my notation is correct}}
-
-According to us, the goal of training is to minimize the emprical risk, which does not contain the expectation.
+\todo{Assign:  @nati, @michael. \nati{@micheal, please check this one carefully, also in the text, I am not sure my notation is correct}}
+
+According to us, the goal of training is to minimize the empirical risk, which does not contain the expectation.
 On the contrary, the goal of learning is to minimize the expected risk, i.e.
@@
 Our justification is shaddy.
-I am not sure how to make this clear, without writting too much.
-It is kind of a general consent that smoothness in one domain implies loclization in the other.
+I am not sure how to make this clear, without writing too much.
+It is kind of a general consent that smoothness in one domain implies localization in the other.
 The reason is that for the continuous Fourier transform, we have:
@@
 \end{equation*}
-Hence the theorem says that you cannot concentrate abritrarily in one domain without de-concentrating in the other.
+Hence the theorem says that you cannot concentrate arbitrarily in one domain without de-concentrating in the other.
 
@@
 \todo{Assign: @nati, @michael}
-\nati{We would need an appendix to do that. It is the last figure of the figures notebook (expected filter). I could spend two hours and write some equation... @michael, what do you think?}
+\nati{We would need an appendix to do that. It is the last figure of the figure’s notebook (expected filter). I could spend two hours and write some equation... @michael, what do you think?}
 
@@
 \todo{Assign: @all}
-\nati{The problem is that random filters are picky as well and look very similar. Should we say that? I to not think a colorbar is necessary since there is number on the top plot. Do you agree?}
-
-We decided to not add a colorbar as scale information is already present in the top plot of the figure.
+\nati{The problem is that random filters are picky as well and look very similar.
+Should we say that?
+I do not think a colorbar is necessary since there are numbered axes on the top plots.
+Do you agree?}
+
+We decided not to add a colorbar as scale information is already present in the top plot of the figure.
 
@@
 \end{mdframed}
-We have corrected this mistake according the reviewer suggestion.
+We have corrected this mistake according to the reviewer suggestion.
 
@@
 \begin{mdframed}[style=manuscript] 
-Furthermore, the harmonics ressemblance is another sign that the constructed graph is able to capture the spherical
+Furthermore, the harmonic resemblance is another sign that the constructed graph is able to capture the spherical
 structure of the HEALPix sampling. 
@@
 \end{mdframed}
-\todo{Assign: @all, \nati{What do you think? I had the feeling we already have that in the main body of the paper. I cannot remember where though.}}
+\todo{Assign: @all, \nati{What do you think? I had the feeling we already have that in the main body of the paper. I cannot remember where, though.}}
 
@@
 \end{mdframed}
-We have merged the three plot a an signal figure and adapted the text reference accordingly.
+Inspired by the reviewer comment, we have merged the three plots in a single figure and adapted the text accordingly.
 

### 2019-01-27 scnn.tex
after a small second pass

@@
 \nati{Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
-Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the Manifold and a fully connected graph built with exponentially decaying weights.
+Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the manifold and a fully connected graph built with exponentially decaying weights.
 While our construction will not exactly respect the setting defined by \citep{belkin2007convergence} (the sampling is not uniform and the graph is not fully connected), we observe empirically strong evidence of convergence.}
@@
 By interwinding graph convolutional layers and recurrent layers \citep{seo2016gcrn}, they can for example model structured time series such as traffic on road networks \citep{li2018traffic}, or recursively complete matrices for recommendation \citep{monti2017recommendation}.
-Another trend, parallel to the modelling of structured data, is the use of graph neural networks for relational reasoning \citep{battaglia2018review}.
+Another trend, parallel to the modeling of structured data, is the use of graph neural networks for relational reasoning \citep{battaglia2018review}.
 
@@
 Spherical CNNs are so far mostly used for omnidirectional imaging.
-Many scientific fields, such as weather or climate modelling, would however benefit from an efficient and versatile spherical CNN.
+Many scientific fields, such as weather or climate modeling, would however benefit from an efficient and versatile spherical CNN.
 With this work, we hope to demonstrate and help democratize the use of those tools for spherical data analysis.
@@
 	\includegraphics[width=\linewidth]{subspace_harmonics_eigenvectors}
-	\caption{Correspondence between the subspaces spanned by the graph Fourier modes and the spherical harmonics.
+	\includegraphics[width=\linewidth]{figures/subspace_alignment_percentage.pdf}
+	\caption{Top: Correspondence between the subspaces spanned by the graph Fourier modes and the spherical harmonics.
 Each pixel on the plot is the dot product between one spherical harmonic and one graph Fourier mode $\b u_i$.
@@
 Moreover, we see that the Fourier modes have the correct symmetries, indicated by the perfect orthogonality between even and odd functions.
-For example, the modes corresponding to $\ell=7$ are perfectly orthogonal to the harmonics corresponding to $\ell=0,2,4,6,8$.}
+For example, the modes corresponding to $\ell=7$ are perfectly orthogonal to the harmonics corresponding to $\ell=0,2,4,6,8$.
+	\nati{Bottom: Evolution of the allignement of the graph Fourier mode and the spherical harmonics for with respect of the speherical harmonic index $\ell$.
+It is the percentage of energy contained in the diagonal blocks of the correlation matrix plotted on top.}}
 	\label{fig:subspace_harmonics_eigenvectors}
@@
 \end{figure}
-
-Furthermore, the harmonics ressemblance is another sign that the constructed graph is able to capture the spherical
+Furthermore, the harmonic resemblance is another sign that the constructed graph is able to capture the spherical
 structure of the HEALPix sampling. In some applications, where the

### 2019-02-25 rebuttal.tex
fix makefile
trim whitespace
comment 1.2

@@
 \usepackage{longtable}
-\usepackage[LGR,T1]{fontenc}
+\usepackage[utf8]{inputenc}
+%\usepackage[T1]{fontenc}
 \usepackage{lscape}
@@
 \newcommand{\nati}[1]{{\color[rgb]{.1,.6,.1}{NP: #1}}}
+\newcommand{\mdeff}[1]{{\color[rgb]{.1,.6,.1}{MD: #1}}}
 \newcommand{\TK}[1]{{\color{red}{TK: #1}}}
@@
 
-Dear reviewer, we thank you for reading our paper and providing comments. They have helped us improve our manuscript. In this rebuttal, you can find a detailed answer to all the points you mentioned.
+Dear reviewer, we thank you for your time and comments. The manuscript improved thanks to your feedback. In this rebuttal, you can find a detailed answer to all the points you mentioned.
 
@@
 
-\todo{Assigned: @nati, @michael}
-The intuition of the reviewer is correct.
-Theoretically, using the raw data, \emph{an SVM or even a standard fully connected neural network (NN) would perform a lot better.} In practice, this those models are limited by the computational power and the dataset size.
-
-We actually tried training an SVM on the raw data but were unable to obtain over $60\%$ accuracy in the easiest cases where all the other tested models were close to $100\%$.
+We agree that the ML algorithms should be tested on the same input data for a fair comparison.
+%In practice, those models are limited by the computational power and the dataset size.
+
+We did try to train an SVM on the raw data but were unable to obtain over $60\%$ accuracy in the easiest cases, where every other tested model is close to $100\%$.
 Practically, the classifier would either overfit or be over-regularized.
-For that reason, we decided, not to report the raw-data SVM results in the paper.
-\nati{FYI, I did try again to be entirely sure about it.}
-
-A model based on a fully connected neural network, as suggested by the reviewer, contains a very large number of weights which severely restricts what can be tested with conventional hardware.
+We hence decided not to report the raw-data SVM results in the paper.
+This information has been added to the manuscript.
+% \nati{FYI, I did try again to be entirely sure about it.}
+
+While fully-connected NNs (FCNNs) generalize CNNs, they don't perform as well as CNNs on tasks where the symmetries exploited by the CNN are relevant.\footnote{For cosmological data on the sphere, a desired symmetry, highlighted in the introduction, is for the model to be invariant to rotations.}
+That is similar to our comparison of the FCN and CNN variants.
+While the CNN is a generalization, it doesn't perform as well as the FCN.
+In practice, the large number of parameters required by a FCNN severely restricts what can be tested on conventional hardware.
 In our case the input number of pixels (for order $1$) is $1024^2$ which limits the number of neurons that can be used in the architecture.
-For the completeness of this answer, we did try a fully connected NN.
-Practically, in the first layer, we were only able to $128$ neurons before hitting an out of memory errors.
-In this setting, with a relative amount of noise of $0.5$, we were unable to regularize the network such that it would actually classify the validation set.
-Note that all reported classifiers performed well (close to $100\%$ accuracy) in this particular setting.
-Similar conclusions were observed with other settings.
-%Furthermore, the harmonic resemblance is another sign that the constructed graph is able to capture the spherical
-structure of the HEALPix sampling. , even when increasing the number of neurons for small part of the sphere (order $2$ and $4$).
-
-This being said, the reviewer comment is justified and we will add this information to the paper.
-
-\todo{Add it in the paper... Make clear that CNN is so much better than fully connected + say that SVM on the raw features does not work.}
+For completeness, we tried a FCNN and were only able to squeeze $128$ neurons in the first layer before hitting an out-of-memory error.
+With this architecture and a relative amount of noise of $0.5$, we were unable to regularize the network such that it would classify the validation set.
+(Remember that all reported classifiers obtained close to $100\%$ accuracy in this setting.) Similar conclusions were observed with other settings.
+%Furthermore, the harmonic resemblance is another sign that the constructed graph is able to capture the spherical structure of the HEALPix sampling, even when increasing the number of neurons for small part of the sphere (order $2$ and $4$).
 

### 2019-02-25 scnn.tex
trim whitespace
comment 1.2

@@
 
+It may seem unfair to compare DeepSphere, who has access to raw pixels, with SVMs who only see limited features (histograms and PSDs).
+We however trained an SVM on the raw pixels and were unable to obtain over $60\%$ accuracy in the easiest cases (i.e., noiseless).
+(Remember that every other tested model is close to $100\%$ in that setting.)
+% TODO: provide an explanation why?
+
 As expected, we observe that the FCN slightly outperforms the CNN.
@@
 That is, however, out of the scope of this contribution.
-Third, counter-intuitively, some eigenvectors will be localized~\citep{perraudin2018global}, i.e, they will span a small part of the sphere.
+Third, counter-intuitively, some eigenvectors will be localized~\citep{perraudin2018global}, i.e., they will span a small part of the sphere.
 Those discrepancies result in a convolution operation that is not exactly equivariant to rotation.

### 2019-02-25 rebuttal.tex
comment 1.2

@@
 
-Dear reviewer, we thank you for your time and comments. The manuscript improved thanks to your feedback. In this rebuttal, you can find a detailed answer to all the points you mentioned.
+Dear reviewer, we thank you for your time and thorough comments. The manuscript improved thanks to your feedback. You can find a detailed answer to all the points you mentioned in this rebuttal.
 
@@
 
-We did try to train an SVM on the raw data but were unable to obtain over $60\%$ accuracy in the easiest cases, where every other tested model is close to $100\%$.
+We did try to train an SVM on the raw data but were unable to obtain over $60\%$ accuracy in the three noiseless cases, which is far behind every other tested model.
 Practically, the classifier would either overfit or be over-regularized.
 We hence decided not to report the raw-data SVM results in the paper.
-This information has been added to the manuscript.
+This information has now been added to the manuscript.
 % \nati{FYI, I did try again to be entirely sure about it.}

### 2019-02-25 scnn.tex
comment 1.2

@@
 It may seem unfair to compare DeepSphere, who has access to raw pixels, with SVMs who only see limited features (histograms and PSDs).
-We however trained an SVM on the raw pixels and were unable to obtain over $60\%$ accuracy in the easiest cases (i.e., noiseless).
-(Remember that every other tested model is close to $100\%$ in that setting.)
-% TODO: provide an explanation why?
+We however trained an SVM on the raw pixels and were unable to obtain over $60\%$ accuracy in any of the three noiseless cases.
 

### 2019-02-25 scnn.tex
comment 1.3

@@
 Before doing any numerical analysis on the sphere, one first has to choose a tessellation, i.e., an exhaustive partition of the sphere into finite area elements, where the data under study is quantized.
-The simplicity of the spherical form belies the intricacy of global analysis on the sphere.
-There is no known point set that achieves the analogue of uniform sampling in Euclidean space and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions.
-Any existing proposition of practical schemes for the discrete treatment of such functions on the sphere introduces some systematic error dependent on the global properties of the point set.
+%The simplicity of the spherical form belies the intricacy of global analysis on the sphere.
+%There is no known point set that achieves the analogue of uniform sampling in Euclidean space and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions.
+%Any existing proposition of practical schemes for the discrete treatment of such functions on the sphere introduces some systematic error dependent on the global properties of the point set.
 While our method is applicable to any pixelisation of the sphere, two details depend on the chosen sampling: (i) the choice of neighbours in the construction of the graph, and (ii) the choice of parent nodes when coarsening the graph.

### 2019-02-25 rebuttal.tex
comment 1.3
comment 1.4

@@
 
-\todo{Assigned to: @all whoever can answer this question. I just do not know the answer.
-
-We clarified the sentence with this:
-\begin{mdframed}[style=manuscript]
-blabla
-\end{mdframed}
-}
+That is right.
+Thanks for pointing it out.
+The confusion was due to our ignorance.
+We removed the part about exact SHTs from the paragraph as we don't need to make such a point.
+%\mdeff{That sentence mostly came from \url{https://healpix.jpl.nasa.gov/html/intronode2.htm}.}
+%\mdeff{uniform sampling == same distance between all neighboring pixels}
 
@@
 \end{mdframed}
-
-\todo{Assigned: @nati, @michael}
 
@@
 Indeed, \cite{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the manifold and a fully connected graph built with exponentially decaying weights.
-While our construction will not exactly respect the setting defined by \cite{belkin2007convergence} (the sampling is not uniform and the graph is not fully connected), we observe empirically strong evidence of convergence.
-\end{mdframed}
-We are aware that this particular point could be more detailed.
-Nevertheless, we believe that a deeper discussion does not belong to this paper.
-In fact, we are currently investigating the convergence question with the goal of obtaining better graph constructions or rotational equivariance results.
+While our construction does not exactly respect their setting (the sampling is not uniform and the graph is not fully connected), we empirically observe a strong correspondence between the eigenmodes of both Laplacians (see Appendix A).
+\end{mdframed}
+
+While this particular point deserves more details, we believe that a deeper discussion does not belong to this paper.
+In fact, we are currently investigating this convergence with the goal of constructing better graphs whose Fourier modes would converge to (or even be equivalent to) the spherical harmonics.
 

### 2019-02-25 scnn.tex
comment 1.4

@@
 Before doing any numerical analysis on the sphere, one first has to choose a tessellation, i.e., an exhaustive partition of the sphere into finite area elements, where the data under study is quantized.
-%The simplicity of the spherical form belies the intricacy of global analysis on the sphere.
-%There is no known point set that achieves the analogue of uniform sampling in Euclidean space and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions.
+The simplicity of the spherical form belies the intricacy of global analysis on the sphere: there is no known point set that achieves the analogue of uniform sampling in Euclidean space.
+% and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions.
 %Any existing proposition of practical schemes for the discrete treatment of such functions on the sphere introduces some systematic error dependent on the global properties of the point set.
@@
 
-\nati{Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
+Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
 Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the manifold and a fully connected graph built with exponentially decaying weights.
-While our construction will not exactly respect the setting defined by \citep{belkin2007convergence} (the sampling is not uniform and the graph is not fully connected), we observe empirically strong evidence of convergence.}
+While our construction does not exactly respect their setting (the sampling is not uniform and the graph is not fully connected), we empirically observe a strong correspondence between the eigenmodes of both Laplacians (see \ref{sec:comparison_spherical_harmonics}).
 

### 2019-02-25 rebuttal.tex
comment 1.5

@@
 
-\todo{Assigned: @nati}
-We were actually limited in resolution when computing the graph Fourier eigenvectors as diagonalizing the Laplacian matrix scales as $O(N_{pix}^3)$.
-Hence we used a resolution of $N_{side}=16$.
+Those maps have been produced with a resolution of $N_{side}=16$.
 The information has been added to the paper.
+(High resolution is costly as diagonalizing the Laplacian matrix scales as $O(N_{pix}^3)$.)
 
 Since we do not have any convergence result yet, we are not sure about how the projection error evolves.
-However, if there is convergence (and we believe there is), then the eigenvectors associated with the lowest $\ell$ probably converge first.
+However, if there is convergence (and we believe there is), the eigenvectors associated with the lowest $\ell$ probably converge first.
 

### 2019-02-25 scnn.tex
comment 1.5

@@
 	\includegraphics[width=\linewidth]{eigenvectors}
-	\caption{The first 16 eigenvectors of the graph Laplacian, an equivalent of Fourier modes, of a graph constructed from the HEALPix sampling of the sphere \nati{($N_{side}=16$)}.
+	\caption{The first 16 eigenvectors of the graph Laplacian, an equivalent of Fourier modes, of a graph constructed from the HEALPix sampling of the sphere ($N_{side}=16$).
     Eigenvectors 1--3 could be associated with spherical harmonics of degree $\ell=1$ and order $|m|=(0,1)$, eigenvectors 4--8 with degree $\ell=2$ and order $|m|=(0,1,2)$, and eigenvectors 9--15 with degree $\ell=3$ and order $|m|=(0,1,2,3)$.
-    Nevertheless, the graph eigenvectors are only approximating spherical harmonics.}
+    Nevertheless, graph eigenvectors are only approximating spherical harmonics.}
 	\label{fig:graph_harmonics}

### 2019-02-25 scnn.tex
rewording of appendix C

@@
 
-One should not forget that a significant part of our analysis is done with a full sphere and that in practice we often use only part of the graph as the data may be incomplete (see \figref{example_maps}).
-In this case, the graph setting used through this contribution correspond to assume reflective border conditions.
-It is irrelevant when working on the complete sphere as this surface has no border. Nevertheless, when working with a subpart of the sphere, its border slightly affects the convolution.
-As depicted in \figref{border_effects}, a filter localized near the border of a part of the sphere (via $h(\L) \b \delta_i$) no longer has an isotropic profile.
+The graph setting used throughout this contribution corresponds to assuming reflective border conditions.
+While that is irrelevant when working on the complete sphere (as it has no border), it slightly affects the convolution operation when only a part of the sphere is considered.
+As depicted in \figref{border_effects}, a filter localized near a border (via $h(\L) \b \delta_i$) is no longer isotropic.
 These border effects can, however, be mitigated by padding with zeros a small area around the part of interest.
-Moreover, as long as the training data comes from simulations with the same applied mask, we do not expect these effects to cause problems for the analysis.
+We however do not expect these effects to cause any problem as long as the data samples cover the same area.
 
@@
 	\includegraphics[width=\linewidth]{border_effects}
-	\caption{Convolution kernel (also called filter) $h$ localized in the center and left corner of a surface.
-A filter is localized on a pixel $i$ as $\T_i h = h(\L) \b \delta_i$ (see \secref{graph_convolution} and \eqnref{graph_convolution_spatial}).
-The graph is built from $1/12^\text{th}$ of the sphere at $N_{side} = 16$.
-The filter is not isotropic anymore when localized on the left corner due to border effects.
-The graph representation of a manifold assumes reflective border conditions.}
+	\caption{Convolution kernel (also called filter) localized in the center and left corner of a graph built from $1/12^\text{th}$ of the sphere at $N_{side} = 16$.
+		A filter $h$ is localized on a pixel $i$ as $\T_i h = h(\L) \b \delta_i$ (see \secref{graph_convolution}, equation~\eqnref{graph_convolution_spatial}).
+	The filter is not isotropic anymore when localized on the corner as the graph representation of a manifold assumes reflective border conditions.}
 	\label{fig:border_effects}

### 2019-02-25 rebuttal.tex
comment 1.6

@@
 \end{mdframed}
-\todo{Assigned: @nati,
-Tocheck: @tomek, @michael
-}
-
-In the experiment shown if Figure 4, we only care about speed and not about the filter itself (we could have chosen any filter).
-The main reason is that in the context of neural networks, filters will be learned and hence is not predefined.
-While, libsharp is probably not optimized for Gaussian smoothing, in this experiment we intend to report on the general filter speed and use conveniently a Gaussian.
-
-We note that, the reviewer question is interesting.
-Replacing spherical filtering (using the harmonic decomposition) with graph filtering might be possible in the future as suggested by Appendix C and fig 14.
-Our feeling is that in its current state, it probably does not have the required precision to be usable in a high precision setting.
-Nevertheless, theoretical improvement on the convergence side could potentially make it competitive.
+
+The experiment whose result is reported in Figure 4 is intended to report filtering speed, independently of the chosen filter (we used a Gaussian for convenience).
+While libsharp is probably not optimizing Gaussian smoothing in particular (w.r.t. filtering with any other filter), it is a highly optimized library for SHT.
+We don't care about the approximation quality as, in the context of neural networks, filters are learned.
+That is, graph filters are not approximating any predefined true harmonic-space filters anyway.
+It is however true that replacing spherical filtering (using the SHT) with graph filtering is an interesting prospect (in terms of speed) that might be possible in the future as suggested by Appendix B (Figure B.13).
+We feel that, in its current state, graph filtering is probably not a good enough approximation to be usable when high-precision filtering is required.
+Nevertheless, theoretical improvements on a potential equivalence (or convergence) of the Laplacian eigenvectors to the spherical harmonics (see our answer to comment 1.4) could potentially make it competitive.
 

### 2019-02-25 rebuttal.tex
thanks reviewers

@@
 
-Dear reviewer, we thank you for your time and thorough comments. The manuscript improved thanks to your feedback. You can find a detailed answer to all the points you mentioned in this rebuttal.
+Dear reviewer, we thank you for your time and thorough comments.
+The manuscript improved thanks to your feedback.
+You'll find an answer to all the points you mentioned in this rebuttal.
 
@@
 
-\todo{Assigned @Tomek
-\begin{itemize}
-  \item Thank the reviewer
-  \item give him access to data
-\end{itemize}}
+\todo{@Tomek: give him access to data}
+
+Dear reviewer, we would like to thank you back for your time, your good words, and your thorough review.
+The manuscript substantially improved thanks to your work.
+You'll find an answer to all the points you mentioned in this rebuttal.
 

### 2019-02-26 rebuttal.tex
comment 2.1

@@
 \end{mdframed}
-\todo{Assigned: @Michael, @Nati}
-Our implementation is actually already working with a mask, we choose to use parts of $1/12$, $1/48$ and $1/192$ of the total sphere.
-Our main motivation was to build a "large" dataset with a relatively low number of cosmological maps.
-In terms of neural network, the available implementation of \cite{cohen2018sphericalcnn,kondor2018clebsch} for spherical CNNs and Clebsh-Gordan CNNs are not scalable enough to be trained on the cosmological maps dataset and do not use the HEALPix sampling.
+
+We agree with the reviewer that an example with an irregular mask is the most missed.
+A performance versus time plot would indeed be a great way to present such a comparison.
+As the reviewer hints at, this example would be better presented in the light of a comparison to other formulations of spherical CNNs.
+While such a comparison would without any doubt be insightful on many aspects (not only for masked data, but also on the role of isotropic filters or the importance of rotation equivariance), it is better carried out on diverse datasets and tasks, and deserves, in our opinion, a follow-up paper to be properly addressed.
+The point of this paper was (1) to show that spherical CNNs are a great model for cosmological applications, and (2) that a graph-based spherical CNN has certain undeniable advantages.
+As hinted in the conclusion, we are actively working on a more thorough comparison of graph-based and SHT-based spherical CNNs.
+
+On the practical side, a proper comparison requires to either modify the available implementations of \cite{cohen2018sphericalcnn,esteves2017sphericalcnn,kondor2018clebsch} to use the HEALPix sampling, or to transform the cosmological maps to the sampling schemes they support.
+Moreover, implementing the pooling operation for irregular masks is not trivial.
+All in all, that is a tremendous amount of engineering work that we preferred to defer.
+
+Keep in mind that, while they are not irregular masks, we already use $1/12$, $1/48$, and $1/192$ parts of the sphere for training and inference.
+While an SHT-based method needs to consider the whole sphere to work with this data, our graph-based method only considers the used part (and still takes the curvature of the surface into account).
+The computational advantage of doing so has been added to Figure 4.
+As stated above, the performance comparison will however have to wait our follow-up work.
+% Our main motivation was to build a "large" dataset with a relatively low number of cosmological maps.
+
+% In terms of neural network, the available implementation of \cite{cohen2018sphericalcnn,kondor2018clebsch} for spherical CNNs and Clebsh-Gordan CNNs are not scalable enough to be trained on the cosmological maps dataset and do not use the HEALPix sampling.
 Hence a comparison with these methods requires a different setting, which far beyond the scope of our contribution.
-Nevertheless, this comparison is important and we are preparing a second contribution where it will be conducted.
-
-\nati{We could compare the price of one convolution. What do you think? We can write the theoretical complexity. This is a sensitive point! }
+
+%\nati{We could compare the price of one convolution. What do you think? We can write the theoretical complexity. This is a sensitive point!}
+
+\mdeff{measure the computational time of filtering on a 1/12, 1/48 or 1/192 of the sphere with the graph.
+Add the result to Figure 4 and compare with filtering of the full sphere (with SHT and graph).}
 

### 2019-02-26 rebuttal.tex
comment 2.2

@@
 \end{mdframed}
+
 \todo{Assigned: @Nati, @Michael, @Tomek}
+
+\todo{experiment in prograss by nati}
 
@@
   \item I think that traditional 2D CNNs will be as good as our algorithm. We should be very careful in the way we formulate this in our answer and in the paper.
+\end{itemize}
+}
+
+\mdeff{Agreed that we should do at least one thing they asked for.
+\begin{itemize}
+	\item Testing on the 1/12 of the sphere is not what he asked for. On one hand, a global projection would exhibit more distortion. On the other, we never use the whole sphere.
+	\item Keep in mind that there is no orientation that is consistent for the 12 base faces (i.e., where is up?).
+	\item Agreed that the performance should be very similar. Both are doing local computations. And locally (3 to 5 pixels across), the sphere is isomorphic to an Euclidean plane.
+	\item The only difference, in my opinion, would be due to the anisotropic filters the 2D CNN has access to.
+	\item Not sure we should include this result in the main paper. Hard to justify in the story, especially as a comparison with alternative spherical CNNs is missing. Let's see the results.
 \end{itemize}

### 2019-02-26 rebuttal.tex
comment 2.3

@@
 While such a comparison would without any doubt be insightful on many aspects (not only for masked data, but also on the role of isotropic filters or the importance of rotation equivariance), it is better carried out on diverse datasets and tasks, and deserves, in our opinion, a follow-up paper to be properly addressed.
-The point of this paper was (1) to show that spherical CNNs are a great model for cosmological applications, and (2) that a graph-based spherical CNN has certain undeniable advantages.
+The point of this paper was (i) to show that spherical CNNs are a great model for cosmological applications, and (ii) that a graph-based spherical CNN has certain undeniable advantages.
 As hinted in the conclusion, we are actively working on a more thorough comparison of graph-based and SHT-based spherical CNNs.
@@
 
+\subsection{}
+
 \begin{mdframed}[style=comment]
@@
 \end{mdframed}
-\todo{Assigned: @Nati, @Michael, @Tomek}
-
-Theoretically, providing that the FCN and the CNN have the same modelisation power (i.e, the FCN does not have more or larger layers) and assuming the convolution would be truly invariant to rotation, the CNN could never exceed the FCN for truly rotational invariant data.
-However, assuming enough augmentation (as suggested by the reviewer) and training, the CNN should get to the level of the FCN.
-In practice, this would require more training as the CNN has to learn the invariance.
-The point of defining a FCN instead of a CNN is to avoid the complexity of augmenting the dataset.
-Hence we did not implement it.
-Nevertheless, it is an interesting point worth discussion in the paper.
-We updated the manuscript accordingly.
-\todo{Do it}
-
-\nati{
-Technically, testing this is complicated as rotation on HEALPix are complicated and expensive. We probably will have to break a lot of code to do it.
-
-@Michael: what do you think?
-}
+
+That comparison is not warranted.
+% or justified. pointless is maybe too aggressive
+There are two ways to deal with symmetries one wants to be invariant to: (i) build them into the architecture of the model, or (ii) augment the dataset such that a (more general) model learns them ``brute-force''.
+With respect to rotation invariance, the FCN architecture is of the first kind, while the CNN is of the second kind.
+Assuming the task is truly invariant to said symmetry,\footnote{As argued in the introduction, cosmological maps are rotation invariant.} the performance of the first kind of models would be exactly the same as without augmentation, while the second kind would only catch up after seeing enough data to learn the invariance.
+That is a waste of resources which is only justified if it's not possible to back the desired invariance in the architecture.
+We updated the manuscript to more precisely reflect this argumentation.
+
+% \nati{Technically, testing this is complicated as rotation on HEALPix are complicated and expensive. We probably will have to break a lot of code to do it.
+% @Michael: what do you think?}
+% \mdeff{Agreed.}
 

### 2019-02-26 scnn.tex
comment 2.3

@@
 
-For tasks that are rotation invariant, FCNs need less training data as the rotation symmetry is backed in the architecture and need not be learned.
+There are in general two ways to deal with symmetries one wants to be invariant to: (i) build them into the architecture, or (ii) augment the dataset such that a (more general) model learns them.
+With respect to rotation invariance, the FCN architecture is of the first kind, while the CNN is of the second kind.
+For tasks that are rotation invariant, FCNs hence need less training data as the rotation symmetry is backed in the architecture and need not be learned.
 Than can be seen as intrinsic data augmentation, as a CNN would need to see many rotated versions of the same data to learn the invariance.
@@
 The simulations are created using the fast lightcone method \pkg{UFalcon} described in \citep{sgier2018fastgeneration}.
-A brief overview about the map making procedure used in \pkg{UFalcon} as well as the simulation parameters are given in Appendix~\ref{sec:convergence_mass_maps}.
+A brief overview about the map making procedure used in \pkg{UFalcon} as well as the simulation parameters are given in \ref{sec:convergence_mass_maps}.
 We however use a single simulation box, as opposed to two used in that work, as we use source galaxies at a lower redshift of $z=0.8$, instead of $z=1.5$.

### 2019-02-26 scnn.tex
thanks reviewers in paper

@@
 
-This work was supported by a grant from the Swiss Data Science Centre (SDCS) under project \textit{DLOC:  Deep Learning for Observational Cosmology} and grant number 200021\_169130 from the Swiss National Science Foundation.
+This work was supported by a grant from the Swiss Data Science Center (SDCS) under project \textit{DLOC:  Deep Learning for Observational Cosmology} and grant number 200021\_169130 from the Swiss National Science Foundation (SNSF).
 We thank Jean-François Cardoso for helpful discussions about the spherical harmonics.
-We thank Alexandre Refregier, Adam Amara, Thomas Hofmann and Fernando Perez-Cruz for advice and helpful discussions.
+We thank Alexandre Refregier, Adam Amara, Thomas Hofmann, and Fernando Perez-Cruz for advice and helpful discussions.
 We thank Hamsa Padmanabhan for testing use cases of the code.
+Finally, we thank the two anonymous reviewers who provided extensive feedback that greatly improved the quality of this paper.
 

### 2019-02-26 rebuttal.tex
rebuttal: paper number

@@
 \title{\vspace{-1cm}
-\begin{flushleft} {\sffamily Rebuttal for paper \emph{Paper Number} }\end{flushleft}}
+\begin{flushleft} {\sffamily Rebuttal for paper \emph{ASCOM\_2018\_119} }\end{flushleft}}
 \date{\vspace{-1.7cm}\begin{flushleft}\sffamily DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications, Nathanaël Perraudin, Michaël Defferrard, Tomasz Kacprzak, Raphael Sgier \end{flushleft}}
@@
 
-The authors would like to thank the reviewers for their comments, which significantly helped improve the manuscript. We believe we have addressed all the issues raised in the following rebuttal.
-%  For each comment, we have first highlighted the issue, then we provided an answer, and finally we described how the manuscript was adjusted.
+The authors would like to thank the reviewers for their time and comments, which significantly helped improve the manuscript.
+We believe we addressed all the raised issues in the following rebuttal.
 

### 2019-02-26 rebuttal.tex
comment 2.4

@@
 
-This is a good question and a fair request.
-Problematically, we cannot provide such a plot without solving the theoretical problem first.
-Indeed to experimentally show convergence, we actually need to build a series of graph Laplacian that converges toward the Laplace Beltrami operator.
-This far more complicated than building one Laplacian and observe some similarities between the two operators.
-
-This is actually a problem we are currently investigating. We plan to make a separate contribution.
+Good point.
+To experimentally show convergence, we would need to build a series of graph Laplacians that converges to the Laplace-Beltrami operator.
+This is complicated and requires to solve the theoretical problem first.
+Hence, we built one Laplacian and observed some similarities between the two operators instead.
+We agree that our wording was unfortunate and have modified the manuscript to mean that we empirically observed a strong correspondence rather than a proper convergence.
+The convergence (or even exact correspondence) is a problem we are currently investigating and plan to release as a separate contribution.
+See also comment 1.4 and our answer there.
+
+\todo{the new figure A.12 is maybe a weak proof of convergence}
+
+\mdeff{@nati, what do you think?}
 

### 2019-02-26 rebuttal.tex
comment 2.5

@@
 
-Yes, we are investigating the question of graph weights.
-As suggested in the previous comment, the weighting scheme used is very important for the graph Laplacian to approach the true Laplace Beltrami operator.
-Using a more appropriate weighting scheme, one could hope for a more rotational invariant convolution and a faster convergence rate of the operator.
-\nati{@michael, how much shall we say here?}
+Yes, we are investigating how to best set the edge weights (the sole degree of freedom when building a graph).
+The question is: what edge weights should be set such that the graph Laplacian converges (or is equivalent) to the Laplace-Beltrami (up to a certain bandwidth).
+Ideally, that should work for any sampling of the sphere.
+(Equivalently, the Fourier modes converge or are equivalent to the spherical harmonics.)
+A proof of convergence or equivalence would allow a graph convolution that is truly equivariant to rotation.
+Moreover, it would enable to do high-precision filtering using the graph rather than the SHT (for speed).
+See also comment 1.6 and our answer there.
+
+% \nati{@michael, how much shall we say here?}
+% \mdeff{I like to be open. It's mostly written in the paper anyway.}
 
@@
 \end{mdframed}
+
+Thanks for the clarification.
 

### 2019-02-26 scnn.tex
comment 2.5

@@
 
-As a future work, it would be interesting to further investigate the link between the graph Fourier basis and the spherical harmonics.
-Furthermore, the influence of irregular sampling on the convolution's equivariance to rotation should be empirically quantified and ideally theoretically bounded.
-Further comparison of DeepSphere to other spherical CNN formulations, with different sampling schemes, would also be worthwhile.
+As future work, it would be interesting to further investigate the relation between the graph Fourier basis and the spherical harmonics.
+The goal would be to find edge weights such that the graph Laplacian converges (or is equivalent) to the Laplace-Beltrami (up to a certain bandwidth).
+Ideally, that should work for any sampling of the sphere.
+That would enable a truly rotation equivariant graph convolution and high-precision filtering using the graph rather than the SHT (for speed).
+% Furthermore, the influence of irregular sampling on the convolution's equivariance to rotation should be empirically quantified and ideally theoretically bounded.
+Finally, a comparison of DeepSphere to other spherical CNN formulations, with different sampling schemes, would be worthwhile.
 

### 2019-02-26 rebuttal.tex
comment 2.6

@@
 
-Thanks for the clarification.
-
-We agree with the reviewer. We actually misformulate this sentence. We have reformulated it as:
-\begin{mdframed}[style=manuscript]
-Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the confidence of the network that the input sample belongs to class $i$.
-Note that in general, this probability distribution does not correspond to the true posterior distribution $p(y|x)$.
-\end{mdframed}
-
-\nati{By the way, this mean that the reviewer is knowledgable with ML, and may be Bayesian. He might be working on another spherical approach.}
+Thanks for making it precise. We completely agree and updated the manuscript accordingly.
+
+% \nati{By the way, this mean that the reviewer is knowledgeable with ML, and may be Bayesian. He might be working on another spherical approach.}
+% \mdeff{The guy likes to be precise.}
 

### 2019-02-26 scnn.tex
comment 2.6

@@
 where $N_{classes}$ is the number of classes to discriminate.
-\nati{Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a probability distribution over the classes, i.e., $y_i$ is the confidence of the network that the input sample belongs to class $i$.
-Note that in general, this probability distribution does not correspond to the true posterior distribution $p(y|x)$.} This last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.
+Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a discretised conditional distribution for the class given the data and trained parameters.
+That is, $y_i$ is the confidence of the network that the input sample belongs to class $i$.
+% Note that in general, this probability distribution does not correspond to the true posterior distribution $p(y|x)$.
+This last layer is actually normalizing $\x$ into $\y$ such that $\| \y \|_1 = \sum_i y_i = 1$.
 
@@
 
-A first approach, explored by \citep{boomsma2017spherical} for molecular modeling and \citep{su2017sphericalconv, coors2018spherenet} for omnidirectional imaging, is to use a 2D CNN on a discretization of the sphere that is a grid, such as the equirectangular projection (\figref{sphere_grids}, left panel), or a set of grids, such as the cubed-sphere defined by~\citep{ronchi1996cubed} (\figref{sphere_grids},  middle panel).
+A first approach, explored by \citep{boomsma2017spherical} for molecular modeling and \citep{su2017sphericalconv, coors2018spherenet} for omnidirectional imaging, is to use a 2D CNN on a discretisation of the sphere that is a grid, such as the equirectangular projection (\figref{sphere_grids}, left panel), or a set of grids, such as the cubed-sphere defined by~\citep{ronchi1996cubed} (\figref{sphere_grids},  middle panel).
 As this formulation uses the standard 2D convolution, all the optimizations developed for images can be applied, which makes it computationally efficient.

### 2019-02-26 rebuttal.tex
comment 2.7

@@
 \end{mdframed}
-\todo{Assigned: @michael}
+
+Think of the MNIST digits, cells in biomedical imaging, faces on portraits, etc.
+Most photographers prefer the subject of interest to be centered.
+Then, what's important is not that the informative part is only in the center, but that a fully connected layer allows a network to focus its attention on the domain.
+With average pooling, all pixels are equal.
 

### 2019-02-27 rebuttal.tex
updated rebuttal

@@
 The paper is well-written, and the results are clearly presented.
-The litterature as well as the advantages and limitations of new and existing algorithms are discussed thoroughly and fairly.
+The literature as well as the advantages and limitations of new and existing algorithms are discussed thoroughly and fairly.
 I recommend this paper for publication, provided the following comments are addressed.
@@
 One fairly significant concern I have is how convincing the application to other machine learning algorithms is.
-The authors compare deep sphere to a SVM classifier, in the case of distinguising from two cosmological models from density maps.
-This classification is obviously a simplification of what would be done in real comsological analyses, but is sufficient for the purpose of demonstration here.
+The authors compare deep sphere to a SVM classifier, in the case of distinguishing from two cosmological models from density maps.
+This classification is obviously a simplification of what would be done in real cosmological analyses, but is sufficient for the purpose of demonstration here.
 However, the metrics adopted do not clearly highlight the superiority of DeepSphere.
@@
 We agree that the ML algorithms should be tested on the same input data for a fair comparison.
+\TK{PS and histograms are standard statistics used by the cosmology community for analysing real data. This is why we chose it as the reference point.
+The single step of moving away from these hand-picked statistics to ML approaches is already interesting for physicists.
+It would be indeed interesting to compare the performance of the CNN to other ML-based algorithms, but we belive it is a major undertaking if to be conducted fairly.
+Given that the our method gives significant advantage over the traditional statistics used in cosmology, we believe that the current scope of the paper is already interesting for cosmologists.
+We would be keen to leave more detailed comparisons of ML-algorithms for future work.
+}
 %In practice, those models are limited by the computational power and the dataset size.
@@
 \begin{mdframed}[style=comment]
-Page 4: "There is no known point set that achieves the analogue of uniform sampling in Euclidean space and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions." This is ambigious.
+Page 4: "There is no known point set that achieves the analogue of uniform sampling in Euclidean space and allows exact and invertible discrete spherical harmonic decompositions of arbitrary but band-limited functions." This is ambiguous.
 There exists multiple schemes for performing exact SHT on band-limited signals.
@@
 Obviously healpix is very advantageous for the pooling and other operations that take advantage of its hierarchical nature.
-This is well discussed in the paper - in particular how the fast graph algorithms could accomodate other sampling schemes.
+This is well discussed in the paper - in particular how the fast graph algorithms could accommodate other sampling schemes.
 \end{mdframed}
@@
 
-\todo{@Tomek: give him access to data}
-
 Dear reviewer, we would like to thank you back for your time, your good words, and your thorough review.
@@
 You'll find an answer to all the points you mentioned in this rebuttal.
+
+The data is available on request in Zenodo, but the access is not anonymous.
+For the special purpose of the review, we put the data from Zenodo in the cloud storage.
+It can be access by a public link:
+https://polybox.ethz.ch/index.php/s/Oi2NjdF8dnMdwot
+The link will expire on 31 March.
+The password is "DeepSphere101".
+Please do not share these details to anyone, or do not use it for purposes other than the review.
 
@@
 \todo{Assigned: @Nati, @Michael, @Tomek}
+\TK{makes sense to me.}
 
@@
 }
+\TK{I would be tempted to leave it to future work! It is an interesting comparison, but requires more work and it brings only a bit more to already awesome paper.}
 
@@
 We updated the manuscript to more precisely reflect this argumentation.
+\TK{Seems a bit strong to me.. maybe we would write it in a softer language?}
 
@@
 This reviewer really spend the time. Should we say something here?}
+\TK{Thank you very much for taking the time for making these corrections. We find them very helpful and improving the quality of the paper.
+We implemented most of them, see below.}
 
@@
 \todo{Assigned: @tomek, @michael}
+\TK{not sure what do to here.. will people get upset? "Precision" is commonly used in cosmology}
 
@@
 \nati{I personally think it is better without separating the lines}
+\TK{Thank you for the suggestion, normally we would adopt it, but the paper is already quite long, and breaking up the lines in equations would make it even longer. So we decided against it.}
 
@@
 \nati{What do you think? This avoid repetition. But we could be more consistent...}
+\TK{Agreed. Do you want to make the change @nati?}
 
@@
 \end{mdframed}
-\todo{assigned: @tomek}
-\nati{I am not sure of the english here.}
+\TK{Thank you for the suggestion, we updated the text.}
 
@@
 \end{mdframed}
-\todo{assigned: @tomek}
+\TK{Thank you for the suggestion, we updated the text.}
 
@@
 \end{mdframed}
-\todo{Assign: @michael, @tomek}
-\nati{I do not know what we should do.}
+% \todo{Assign: @michael, @tomek}
+% \nati{I do not know what we should do.}
+Thank you for your suggestion.
+Ideally we would replace equation references such as "(1)" with "Equation (1)", but given the large number of equation references, we would prefer to stick with a short-form to avoid lengthening the paper further.
 
@@
 \end{mdframed}
-\todo{Assigned: @tomek}
-\nati{I think the "as" is correct here. We use it for "because". Not sure...}
+% \todo{Assigned: @tomek}
+% \nati{I think the "as" is correct here. We use it for "because". Not sure...}
+\TK{Thank you for the suggestion, we adopted it.}
 
@@
 \end{mdframed}
-\todo{Assigned: @tomek}
-\nati{I prefer the version we have. But I leave it up to you to decide.}
+% \todo{Assigned: @tomek}
+% \nati{I prefer the version we have. But I leave it up to you to decide.}
+\TK{We updated the text as suggested.}
 
@@
 \end{mdframed}
-\todo{Assigned @Tomek}
+\TK{Indeed. We added a word "typically" to reflect that there may be cases like this.}
 
@@
 \end{mdframed}
-\todo{Assign: @Tomek}
+% \todo{Assign: @Tomek}
+\TK{Updated the sentence.}
 
@@
 What do you think?}
+\TK{This is an interesting observation.
+The noise is introduced to make the case realistic, as the mass map data in reality is always very noisy.
+It is convenient that this fact can be used for data augmentation too and make the ML problem easier to solve.
+As these two facts are connected, we prefer to leave the sentence as is.}
 
@@
 \todo{Assign: @tomek -> \nati{I corrected it with "which". Do you agree? }}
+\TK{Sounds good to me.}
 
@@
 \todo{@assign: Tomek}
+\TK{Thank you for pointing it out, we believe that the original intended meaning is better reflected as is now.}
 

### 2019-02-27 scnn.tex
updated rebuttal

@@
 DeepSphere is, however, easily used with other samplings as only two elements depend on it: (i) the choice of neighboring pixels when building the graph, and (ii) the choice of parent pixels when building the hierarchy.
-The flexibility of modeling the data domain with a graph allows to easily model data that spans only a part of the sphere, or data that is not uniformly sampled.
+The flexibility of modeling the data domain with a graph allows one to easily model data that spans only a part of the sphere, or data that is not uniformly sampled.
 Using a $k$-nearest neighbours graph, the convolution operation costs $\mathcal{O}(N_{pix})$ operations, where $N_{pix}$ is the number of pixels.
@@
 The lowest possible resolution is given by the base partitioning of the surface into $N_{pix} = 12$ equal-sized pixels (right-most sphere in \figref{pooling}).
-As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2 \times 12 = 2^2 \times 12 = 48$ pixels (middle sphere in \figref{pooling}), the third is $N_{pix} = N_{side}^2 \times 12 = 4^2 \times 12 = 192$ pixels, etc., where $N_{side} = 1, 2, 4, 8, \ldots$ is the grid resolution parameter.
+% As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2 \times 12 = 2^2 \times 12 = 48$ pixels (middle sphere in \figref{pooling}), the third is $N_{pix} = N_{side}^2 \times 12 = 4^2 \times 12 = 192$ pixels, etc., where $N_{side} = 1, 2, 4, 8, \ldots$ is the grid resolution parameter.
+The resolution changes as $N_{pix} = N^2_{side}\times12$ such that $N_{pix} = 48$ for $N_{side} = 2$ and $N_{pix} = 192$ with $N_{side}=3$.
 High-resolutions HEALPix maps easily reach millions of pixels.
@@
 
-Coarsening can be naturally designed for hierarchical pixelisation schemes, as each subdivision divides a cell in an equal number of child sub-cells.
-Coarsening is the reverse operation: merging the sub-cells toward the goal of summarizing the data supported on them.
+Coarsening can be naturally designed for hierarchical pixelisation schemes, where each subdivision divides a cell in an equal number of child sub-cells.
+% Coarsening is the reverse operation: merging the sub-cells toward the goal of summarizing the data supported on them.
+To coarsen, the sub-cells are merged to summarise the data supported on them.
 Merging cells lead to a coarser graph.
@@
 The regression task will most likely be the most practical cosmological application, as described in \citep{gupta2018nongaussianinformation} and \citep{fluri2018deep}.
-Implementation of full cosmological inference requires, however, many more simulations, building the likelihood function, and several other auxiliary tasks.
+Implementation of full cosmological inference typically requires, however, many more simulations, building the likelihood function, and several other auxiliary tasks.
 The classification problem is much more straightforward to implement and execute, and can be used to fairly compare the accuracy of the algorithm against benchmarks \citep{schmelze2017cosmologicalmodel}.
@@
 \pkg{L-PICOLA} \citep{howlett2015lpicola} is used for fast and approximate N-body simulations.
-For each class, we generate $30$ simulations.
+We generate $30$ simulations for each of the two classes.
 Out of the $60$ simulations, $20$ are kept as the test set, and $20\%$ of the remaining training data is used as a validation set, to monitor the training process and select the hyper-parameters.

### 2019-03-01 rebuttal.tex
comment 2.8

@@
 That is a waste of resources which is only justified if it's not possible to back the desired invariance in the architecture.
+The reviewer himself makes that point in comment 2.8: ``building a NN to suit your purposes''.
 We updated the manuscript to more precisely reflect this argumentation.
@@
 Then, what's important is not that the informative part is only in the center, but that a fully connected layer allows a network to focus its attention on the domain.
-With average pooling, all pixels are equal.
+With average pooling, all pixels are treated equally.
 
@@
 \end{mdframed}
-\todo{Assigned: @michael}
+
+Thanks for pointing out the typo, we fixed it.
+We do realize it's an important point, and agree that some people apply architectures to a different problem they have been devised for without much thoughts.
+A large chunk of our paper is actually about using an appropriate NN architecture.
+The point you suggest us adding is actually made in the Experiments section, where we describe the data and task, and motivate the architecture choice.
+We wanted the Method section to be more generic.
+% Note that the task plays a role as well (i.e., two different tasks on the same data might benefit from different architectures).
+% \mdeff{that's in contradiction with his comment 2.3 where he asks us to do data augmentation with the CNN}
 

### 2019-03-01 rebuttal.tex
comment 2.9

@@
 \end{mdframed}
-In the work of \cite{kondor2018clebsch}, the convolution is performed in the spectral (harmonic) domain with a simple Adamar product.
-Instead of recomposing the signal and applying a traditional non-linearity such as "relu" in the pixel domain, \cite{kondor2018clebsch} proposes to directly apply a Clebsch–Gordan product in the spectral domain.
-As a non-linear operation preserving the rotation equivariance, it is considered as the non-linearity of the neural network.
-
-We have modified the manuscript as:
-\begin{mdframed}[style=manuscript]
-While this clever trick lowers the complexity of the convolution (Adamar product in the spectral domain) to $\bO(N_{pix})$, the non-linearity (Clebsch–Gordan product) is $\bO(N_{pix}^{3/2})$.
-\end{mdframed}
-\nati{Should we be clearer in the paper?}
+
+In \cite{kondor2018clebsch}, the convolution is performed in the spectral (harmonic) domain with a simple Hadamard product.
+Instead of recomposing the signal and applying a traditional non-linearity such as the ReLU in the pixel domain, \cite{kondor2018clebsch} proposes to apply a Clebsch–Gordan product in the spectral domain.
+(As a non-linear operation preserving rotation equivariance, it is considered as the non-linearity of the NN.)
+Their convolution costs $\mathcal{O}(N_{pix})$, and their non-linearity costs $\mathcal{O}(N^{3/2}_{pix})$.
+Stacking those layers result in a NN of overall $\mathcal{O}(N^{3/2}_{pix})$ time complexity.
+We clarified the sentence.
 

### 2019-03-01 scnn.tex
comment 2.8
comment 2.9

@@
 For tasks that are rotation invariant, FCNs hence need less training data as the rotation symmetry is backed in the architecture and need not be learned.
-Than can be seen as intrinsic data augmentation, as a CNN would need to see many rotated versions of the same data to learn the invariance.
+This can be seen as intrinsic data augmentation, as a CNN would need to see many rotated versions of the same data to learn the invariance.
 Moreover, FCNs can accommodate maps with a varying number of pixels.
@@
 The computational cost is thus $\sqrt{N_{pix}}$ FFTs for a total cost of $\bO\left( N_{pix} \log \sqrt{N_{pix}} \right)$, plus $\sqrt{N_{pix}}$ matrix multiplications of size $\sqrt{N_{pix}}$ for a total cost of $\bO\left(N_{pix}^{3/2}\right)$ operations.}
-The Clebsh-Gordan transform can be used to perform the non-linear transformation in the spectral domain \citep{kondor2018clebsch}.
-As such, the SHT is only performed once on the input (no back and forth SHT between each layer).
-\nati{While this clever trick lowers the complexity of the convolution (Adamar product in the spectral domain) to $\bO(N_{pix})$, the non-linearity (Clebsch–Gordan product) is $\bO(N_{pix}^{3/2})$.}
+While the Clebsh-Gordan transform can be leveraged to avoid SHTs between layers (it does a non-linear transformation in the spectral domain), the transform itself costs $\bO(N_{pix}^{3/2})$, for no reduction of overall complexity \citep{kondor2018clebsch}.
 This work is another indication that there might be a $\Omega(N_{pix}^{3/2})$ computational lower bound for the proper treatment of rotation equivariance with the spherical harmonics.

### 2019-03-01 rebuttal.tex
comment 2.10

@@
 \end{mdframed}
-When comparing the speed, we used a single-core CPU implementation of the graph convolution. We believe that this comparison is fair.
-\nati{Is this sufficient?}
+
+True.
+In the experiment, both were compared on a single core.
+They might however scale differently given one can be distributed through MPI and the other on a GPU.
+The manuscript was updated.
 

### 2019-03-01 scnn.tex
comment 2.10

@@
 \figref{filtering_speed} compares the speed of low-pass filtering for Gaussian smoothing using the spherical harmonics and the graph-based method presented here.
-A naive implementation of our method is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively, than using the spherical harmonic transform at $\ell_{max} = 3 N_{side}$ implemented by the highly optimized \pkg{libsharp} \citep{reinecke2013libsharp} library used by HEALPix.
+On a single core, a naive implementation of our method is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively, than using the spherical harmonic transform at $\ell_{max} = 3 N_{side}$ implemented by the highly optimized \pkg{libsharp} \citep{reinecke2013libsharp} library used by HEALPix.
+Note that the two might however scale differently, given that \pkg{libsharp} can be distributed on CPUs through MPI while our method can be distributed on GPUs by \pkg{TensorFlow}.
 

### 2019-03-03 rebuttal.tex
small modification reviewer 1

@@
 
-\todo{Answer to editor}
+Dear Editor,
+
+Thanks for handling our submission.
+We have revised our manuscript following many of the reviewer suggestions.
+We believe that it is now ready for publication.
+Currenlty, the dataset can be accessed simply via Zenodo.
+While this process is not anonymons, we provide in this rebuttal (Comment \#2) a special link for the reviewers to access it is anonymously.
+
+We thank the reviewers for taking the time to review our manuscript and for their constructive comments. We have answered
+
+\newpage
 
@@
 
-Dear reviewer, we thank you for your time and thorough comments.
+Dear reviewer,
+
+we thank you for your time and thorough comments.
 The manuscript improved thanks to your feedback.
@@
 We agree that the ML algorithms should be tested on the same input data for a fair comparison.
-\TK{PS and histograms are standard statistics used by the cosmology community for analysing real data. This is why we chose it as the reference point.
-The single step of moving away from these hand-picked statistics to ML approaches is already interesting for physicists.
+
+We performed the comparizon with these features at it reflects the two-steps traditional way in classic machine learning: a) designing features b) using a method a ``simple'' classifier.
+Deep learning changed this this tactic with networks that learn the features directly from the raw data.
+The PS and histograms were chosen because they are standard statistics used by the cosmology community for analysing real data. 
+This is why we chose it as the reference point.
+In fact, the single step of moving away from these hand-picked statistics to ML approaches is already interesting for physicists.
 It would be indeed interesting to compare the performance of the CNN to other ML-based algorithms, but we belive it is a major undertaking if to be conducted fairly.
@@
 We would be keen to leave more detailed comparisons of ML-algorithms for future work.
-}
+
 %In practice, those models are limited by the computational power and the dataset size.
 
-We did try to train an SVM on the raw data but were unable to obtain over $60\%$ accuracy in the three noiseless cases, which is far behind every other tested model.
+This beeing said, we did try to train an SVM on the raw data, but were unable to obtain over $60\%$ accuracy in the three noiseless cases, which is far behind every other tested model.
 Practically, the classifier would either overfit or be over-regularized.
@@
 Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
-Indeed, \cite{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the manifold and a fully connected graph built with exponentially decaying weights.
-While our construction does not exactly respect their setting (the sampling is not uniform and the graph is not fully connected), we empirically observe a strong correspondence between the eigenmodes of both Laplacians (see Appendix A).
+Indeed, \cite{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing random uniform sampling of the manifold and a fully connected graph built with exponentially decaying weights.
+While our construction does not exactly respect their setting (the sampling is deterministic and the graph is not fully connected), we empirically observe a strong correspondence between the eigenmodes of both Laplacians (see Appendix A).
 \end{mdframed}
@@
 While this particular point deserves more details, we believe that a deeper discussion does not belong to this paper.
-In fact, we are currently investigating this convergence with the goal of constructing better graphs whose Fourier modes would converge to (or even be equivalent to) the spherical harmonics.
+In fact, we are currently investigating this convergence with the goal of constructing better graphs whose Fourier modes would converge to 
+% (or even be equivalent to) 
+the spherical harmonics.
 
@@
 Since we do not have any convergence result yet, we are not sure about how the projection error evolves.
-However, if there is convergence (and we believe there is), the eigenvectors associated with the lowest $\ell$ probably converge first.
+However, if there is convergence (and we believe there is providing the correct set of graph weight is selected), the eigenvectors associated with the lowest $\ell$ probably converge first.
 
@@
 \section{}
-
+\label{sec:dataset}
 \begin{mdframed}[style=comment]

### 2019-03-03 scnn.tex
small modification reviewer 1

@@
 Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
-Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the manifold and a fully connected graph built with exponentially decaying weights.
-While our construction does not exactly respect their setting (the sampling is not uniform and the graph is not fully connected), we empirically observe a strong correspondence between the eigenmodes of both Laplacians (see \ref{sec:comparison_spherical_harmonics}).
+Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing random uniform sampling of the manifold and a fully connected graph built with exponentially decaying weights.
+While our construction does not exactly respect their setting (the sampling is deterministic and the graph is not fully connected), we empirically observe a strong correspondence between the eigenmodes of both Laplacians (see \ref{sec:comparison_spherical_harmonics}).
 

### 2019-03-04 rebuttal.tex
comment 2.2

@@
 \todo{Assigned: @Nati, @Michael, @Tomek}
-\TK{makes sense to me.}
-
-\todo{experiment in prograss by nati}
-
-\nati{\textbf{Very important point!!!}
-\begin{itemize}
-  \item We can do this comparison...
-  \item Since we used 1/12 of the sphere, all the pixel grids we use are somehow squared.
+\nati{Please check if you like what I did in light of the discussion we had.}
+
+We share the opinion of the reviewer when he says that 2D CNNs should probably work as well as DeepSphere, ``by taking in a projected 2D image of the sky and using *loads* of filters to learn about the distortion at different parts of the projected sky.'' Hence we decided to add a new experiment in the paper.
+
+Nevertheless, making a comparison is technically not as trivial as it may seems. 
+Problematically a radial projection is computationally expensive to the point where, because of the dataset augmentation, it becomes significantly more expensive than the actual training of the network.
+Hence, we decided to use the geometrical properties of HEALPix to create a ``special'' projection. 
+In the HEALPix sampling, the sphere is first separated into $12$ parts that are then subdivided into $4$ recursively.
+Eventually, each of these $12$ part resembles a square grid. 
+As the problem we are solving only involve one of these 12 parts, we can use this natural structure to simply re-assign each HEALPix pixel to one of a 2 dimensional grid of size $N_{sides} \times N_{sides}$.
+This operation is computationally very cheap and probably spread quite evenly across the resulting image. 
+This projection has recently been used for a CNN in cosmology in the very recent work \cite{krachmalnicoff2019convolutional}.
+
+As we believe that this projection is the optimal one to use a traditonal CNN for application, we performed the experiment using it.
+
+Our expectation were similar with the one of the reviewer, but the results did surprise us as the performance of the traditional CNN did in general not match DeepSphere, \nati{(see Figure 9 of the manuscript)}.
+It can probably be explained by the fact that 2DCNN breaks the rotational invariance of the data. 
+The problem comes from the fact that the projection introduce a distortion in the geometry and the network has to learn a correct weighting scheme to compensate for it. 
+Unfortunately, this operation waste many parameters, reducing the modelization power of the network and requires large amount of training data which is not fully available.
+Note that, when visualizing the learned convolution kernels, we observed that they were not radial.
+
+% \TK{makes sense to me.}
+
+% \todo{experiment in prograss by nati}
+
+% \nati{\textbf{Very important point!!!}
+% \begin{itemize}
+%   \item We can do this comparison...
+%   \item Since we used 1/12 of the sphere, all the pixel grids we use are somehow squared.
 I am now using this as a projection.
@@
 Or do you know how to do the projection in a simple and efficient manner?
-  \item I think that traditional 2D CNNs will be as good as our algorithm. We should be very careful in the way we formulate this in our answer and in the paper.
-\end{itemize}
-}
-\TK{I would be tempted to leave it to future work! It is an interesting comparison, but requires more work and it brings only a bit more to already awesome paper.}
-
-\mdeff{Agreed that we should do at least one thing they asked for.
-\begin{itemize}
-	\item Testing on the 1/12 of the sphere is not what he asked for. On one hand, a global projection would exhibit more distortion. On the other, we never use the whole sphere.
-	\item Keep in mind that there is no orientation that is consistent for the 12 base faces (i.e., where is up?).
-	\item Agreed that the performance should be very similar. Both are doing local computations. And locally (3 to 5 pixels across), the sphere is isomorphic to an Euclidean plane.
-	\item The only difference, in my opinion, would be due to the anisotropic filters the 2D CNN has access to.
-	\item Not sure we should include this result in the main paper. Hard to justify in the story, especially as a comparison with alternative spherical CNNs is missing. Let's see the results.
-\end{itemize}
-}
+%   \item I think that traditional 2D CNNs will be as good as our algorithm. We should be very careful in the way we formulate this in our answer and in the paper.
+% \end{itemize}
+% }
+% \TK{I would be tempted to leave it to future work! It is an interesting comparison, but requires more work and it brings only a bit more to already awesome paper.}
+
+% \mdeff{Agreed that we should do at least one thing they asked for.
+% \begin{itemize}
+% 	\item Testing on the 1/12 of the sphere is not what he asked for. On one hand, a global projection would exhibit more distortion. On the other, we never use the whole sphere.
+% 	\item Keep in mind that there is no orientation that is consistent for the 12 base faces (i.e., where is up?).
+% 	\item Agreed that the performance should be very similar. Both are doing local computations. And locally (3 to 5 pixels across), the sphere is isomorphic to an Euclidean plane.
+% 	\item The only difference, in my opinion, would be due to the anisotropic filters the 2D CNN has access to.
+% 	\item Not sure we should include this result in the main paper. Hard to justify in the story, especially as a comparison with alternative spherical CNNs is missing. Let's see the results.
+% \end{itemize}
+% }
 
@@
 \end{mdframed}
-We would like to thank the reviewer again for his exceptionally detailed review.
-We really appreciate his effort and the time he invested in his answers.
-His is welcome to contact us for additional information or discussion when the publication will be over.
+We would like to thank the reviewer again for his exceptionally detailed review. We really appreciate his effort and the time he invested in his answers. 
+He is welcome to contact us for additional information or discussion when the publication process will be over.
 

### 2019-03-04 scnn.tex
comment 2.2

@@
 
+\nati{
+Additionally, we compare DeepSphere to a traditional 2-dimensional convolutional neural network (2DCNN). 
+To do so, the samples are first transformed into a square image before being fed into the 2DCNN. 
+As described in \ref{sec:projection}, we use the geometrical properties of HEALPix to construct an efficient and simple projection of the samples. 
+Note that during the review process another spherical CNN architecture using exploiting this property appeared \cite{krachmalnicoff2019convolutional}. 
+We used convolution kernel of size $5\times 5$ and reduced the number of filters in order to match the number of variables between DeepSphere and the 2DCNN.
+}
+\nati{Say something about the number of parameters/fitlers. }
+
 \subsection{Network architecture and hyper-parameters}
@@
 
-\figref{results} compares the classification accuracy of DeepSphere (FCN and CNN variants) and the two baselines across five noise levels and three sample sizes.
+\figref{results} compares the classification accuracy of DeepSphere (FCN and CNN variants), the 2DCNN and the two baselines across five noise levels and three sample sizes.
 We indeed observe that the problem is made more difficult as the sample size decreases, and the noise increases.
@@
 We however trained an SVM on the raw pixels and were unable to obtain over $60\%$ accuracy in any of the three noiseless cases.
+
+\nati{
+To our surprise, the traditional 2DCNN did not match the performance of DeepSphere. 
+It can probably be explained by the fact that 2DCNN breaks the rotational invariance of the data. 
+The problem comes from the fact that the projection introduce a distortion in the geometry and the network has to learn a correct weighting scheme to compensate for it. 
+Unfortunately, this operation waste many parameters, reducing the modelization power of the network and requires large amount of training data which is not fully available.
+Note that, when visualizing the learned convolution kernels, we observed that they were not radial. 
+}
 
@@
 
+\nati{
+\section{Maps projection onto a 2-dimensional plane}
+\label{sec:projection}
+In order to compare the DeepSphere architecture with a traditional 2d-CNN, we need to project the spherical data onto a plane. 
+Problematically a radial projection is computationally expensive to the point where, because of the dataset augmentation, it becomes significantly more expensive than the actual training of the network.
+Hence, we decided to use the geometrical properties of HEALPix to create a ``special'' projection. 
+In the HEALPix sampling, the sphere is first separated into $12$ parts that are then subdivided into $4$ recursively.
+Eventually, each of these $12$ part resembles a square grid. 
+To visually see it, we refer the reader to \figref{border_effects}.
+As the problem we are solving only involve one of these 12 parts, we can use this natural structure to simply re-assign each HEALPix pixel to one of a 2 dimensional grid of size $N_{sides} \times N_{sides}$.
+This operation is computationally very cheap and probably spread quite evenly across the resulting image. 
+This projection has recently been used for a CNN in cosmology in the very recent work \cite{krachmalnicoff2019convolutional}.  
+}
+
 \section{Augmentation of the dataset for the SVM classifier}

### 2019-03-04 rebuttal.tex
updated rebuttal?

@@
 \begin{mdframed}[style=comment]
-Convolutional Neural Networks (CNNs) have been proposed as an alternative analysis tool in cosmology thanks to their ability to automatically design relevant statistics to maximise the precision of the parameter estimation [9–16].
+Convolutional Neural Networks (CNNs) have been proposed as an alternative analysis tool in cosmology thanks to their ability to automatically design relevant statistics to maximise the precision of the parameter estimation, while maintaining robustness to noise [9–16].
 
@@
 \end{mdframed}
-\todo{Assigned: @tomek, @michael}
-\TK{not sure what do to here.. will people get upset? "Precision" is commonly used in cosmology}
+Thank you for this comment. Precision, understood as the final size of the posterior distribution on the measured parameters (including systematic errors), is the key interest of cosmology analysis.
+The robustness to noise is also crucial, as demonstrated in [9]. We expanded the sentence to include this.
+% \todo{Assigned: @tomek, @michael}
+% \TK{not sure what do to here.. will people get upset? "Precision" is commonly used in cosmology}
 

### 2019-03-04 scnn.tex
updated rebuttal?

@@
 Convolutional Neural Networks (CNNs) have been proposed as an alternative analysis tool in cosmology thanks to their ability to automatically design relevant statistics to maximise the precision of the parameter estimation
-\citep{schmelze2017cosmologicalmodel,luciesmith2018machinelearning,gupta2018nongaussianinformation,gillet2018deeplearning,hassan2018reionizationmodels,aragoncalvo2018classyfyinglarge,ciuca2017cnnstring,ravanbakhsh2017estimating}.
+\citep{schmelze2017cosmologicalmodel,luciesmith2018machinelearning,gupta2018nongaussianinformation,gillet2018deeplearning,hassan2018reionizationmodels,aragoncalvo2018classyfyinglarge,ciuca2017cnnstring,ravanbakhsh2017estimating}, while maintaining robustness to noise.
 This is possible as neural networks have the capacity to build rich models and capture complicated non-linear patterns often present in the data.

### 2019-03-04 rebuttal.tex
some modification

--- 2019-03-04 rebuttal.tex
@@
 
-Our expectation were similar with the one of the reviewer, but the results did surprise us as the performance of the traditional CNN did in general not match DeepSphere, \nati{(see Figure 9 of the manuscript)}.
+Our expectation were similar with the one of the reviewer, but the results did surprise us as the performance of the traditional CNN did in general not match DeepSphere, (see Figure 9 of the manuscript).
 It can probably be explained by the fact that 2DCNN breaks the rotational invariance of the data. 
@@
 
-That comparison is not warranted.
+% That comparison is not warranted.
 % or justified. pointless is maybe too aggressive
+We do not believe this comparizon is useful because of the following theoretical reason
 There are two ways to deal with symmetries one wants to be invariant to: (i) build them into the architecture of the model, or (ii) augment the dataset such that a (more general) model learns them ``brute-force''.
@@
 Assuming the task is truly invariant to said symmetry,\footnote{As argued in the introduction, cosmological maps are rotation invariant.} the performance of the first kind of models would be exactly the same as without augmentation, while the second kind would only catch up after seeing enough data to learn the invariance.
-That is a waste of resources which is only justified if it's not possible to back the desired invariance in the architecture.
-The reviewer himself makes that point in comment 2.8: ``building a NN to suit your purposes''.
+% That is a waste of resources which is only justified if it's not possible to back the desired invariance in the architecture.
+Augmentation is only justified if it's not possible to back the desired invariance in the architecture.
+% The reviewer himself makes that point in comment 2.8: ``building a NN to suit your purposes''.
 We updated the manuscript to more precisely reflect this argumentation.
+
 \TK{Seems a bit strong to me.. maybe we would write it in a softer language?}
+\nati{Now it is OK. But is it still strong enough. We should only point reviewer incoherence if necessary.}
 
@@
 
-\mdeff{@nati, what do you think?}
+\mdeff{@nati, what do you think?} \nati{I like it. I totally agree with the new wording.}
 
@@
 \end{mdframed}
-\todo{Assigned @tomek.
-This reviewer really spend the time. Should we say something here?}
-\TK{Thank you very much for taking the time for making these corrections. We find them very helpful and improving the quality of the paper.
-We implemented most of them, see below.}
+Thank you very much for taking the time for making these corrections. We find them very helpful and improving the quality of the paper.
+We implemented most of them, see below.
 
@@
 \end{mdframed}
-\todo{Assigned: @tomek, @michael}
+\todo{Assigned: @tomek}
 \TK{not sure what do to here.. will people get upset? "Precision" is commonly used in cosmology}
@@
 \end{mdframed}
-\todo{Assigned: @tomek}
-\nati{I personally think it is better without separating the lines}
-\TK{Thank you for the suggestion, normally we would adopt it, but the paper is already quite long, and breaking up the lines in equations would make it even longer. So we decided against it.}
+Thank you for the suggestion, normally we would adopt it, but the paper is already quite long, and breaking up the lines in equations would make it even longer. So we decided against it.
 
@@
 \end{mdframed}
-\todo{Assigned: @all}
-\nati{What do you think? This avoid repetition. But we could be more consistent...}
-\TK{Agreed. Do you want to make the change @nati?}
+We agree with the reviewer that using different term for the same notion can be confusing for the reader. 
+Nevertheless, while ``a node'' and ``a vertex'' are synonyms refering to a graph part, ``a pixel'' is a different concept refering to a point of the (spherical) sampling.
+As a result, we decided to keep the ``vertex'' and ``pixel''.
+% \todo{Assigned: @all}
+% \nati{What do you think? This avoid repetition. But we could be more consistent...}
+% \TK{Agreed. Do you want to make the change @nati?}
 
@@
 \end{mdframed}
-\TK{Thank you for the suggestion, we updated the text.}
+Thank you for the suggestion, we updated the text.
 

### 2019-03-04 scnn.tex
some modification

--- 2019-03-04 scnn.tex
@@
 %Any existing proposition of practical schemes for the discrete treatment of such functions on the sphere introduces some systematic error dependent on the global properties of the point set.
-While our method is applicable to any pixelisation of the sphere, two details depend on the chosen sampling: (i) the choice of neighbours in the construction of the graph, and (ii) the choice of parent nodes when coarsening the graph.
+While our method is applicable to any pixelisation of the sphere, two details depend on the chosen sampling: (i) the choice of neighbours in the construction of the graph, and (ii) the choice of parent vertices when coarsening the graph.
 As HEALPix~\citep{gorski2005healpix} is our target application, we tailor the method to that particular sampling in the subsequent exposition.
@@
 
-From the HEALPix pixelization, we build a weighted undirected graph $\G = (\V, \E, \W)$, where $\V$ is the set of $N_{pix} = |\V|$ nodes, $\E$ is the set of edges, and $\W$ is the weighted adjacency matrix.
-In our graph, each pixel $i$ is represented by a node (also called vertex) $v_i \in \V$.
-Each node $v_i$ is then connected to the $8$ (or $7$)\footnote{\label{neighbors}The $12 \times 4 = 48$ pixels at the corner of each rhombus of the base dodecahedron only have 7 neighboring pixels.
-See Figures~\ref{fig:healpix_graph_4} and~\ref{fig:pooling}.} nodes $v_j$ which represent the neighboring pixels $j$ of pixel $i$, forming edges $(v_i, v_j) \in \E$.
+From the HEALPix pixelization, we build a weighted undirected graph $\G = (\V, \E, \W)$, where $\V$ is the set of $N_{pix} = |\V|$ vertices, $\E$ is the set of edges, and $\W$ is the weighted adjacency matrix.
+In our graph, each pixel $i$ is represented by a vertex (also called vertex) $v_i \in \V$.
+Each vertex $v_i$ is then connected to the $8$ (or $7$)\footnote{\label{neighbors}The $12 \times 4 = 48$ pixels at the corner of each rhombus of the base dodecahedron only have 7 neighboring pixels.
+See Figures~\ref{fig:healpix_graph_4} and~\ref{fig:pooling}.} vertices $v_j$ which represent the neighboring pixels $j$ of pixel $i$, forming edges $(v_i, v_j) \in \E$.
 Given those edges, we define the weighted adjacency matrix $\W \in \R^{N_{pix} \times N_{pix}}$ as
@@
 that can be used to define a Fourier basis on the graph. Here $\D$ is the diagonal
-matrix where $\D_{ii} = \b{d}_i$ and $\b{d}_i = \sum_j \W_{ij}$ is the weighted degree of node $v_i$. By construction, the Laplacian is symmetric positive
+matrix where $\D_{ii} = \b{d}_i$ and $\b{d}_i = \sum_j \W_{ij}$ is the weighted degree of vertex $v_i$. By construction, the Laplacian is symmetric positive
 semi-definite and hence can be decomposed as $\L = \U \bLambda \U\trans$, where $\U = [\b u_1, \ldots, \b u_{N_{pix}}]$ is an
@@
 This localization of the kernel $h$ can be useful to visualize kernels, as shown in an example of heat diffusion presented in~\ref{sec:filter_visualization}.
-If the graph is not regular, i.e., all nodes do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one node to another.
+If the graph is not regular, i.e., all vertices do not have the same number of neighbors, and all distances are not equal, the effect of the kernel will slightly differ from one vertex to another.
 While there is no perfect sampling of the sphere, these differences are negligible as the structure of the whole graph is very regular.
@@
 \end{equation}
-where $\L^k$ captures $k$-neighborhoods.\footnote{The 1-neighborhood of a node is the set of nodes that are directly connected to it.
-The $k$-neighborhood of a node is the set of nodes that are connected to it through paths of length $k$.}
-The entry $(\L^k)_{ij}$ is the sum of all weighted paths of length $k$ between nodes $v_i$ and $v_j$, where the weight of a path is the multiplication of all the edge weights on the path.
-Hence, it is non-zero if and only if nodes $v_i$ and $v_j$ are connected by at least one path of length $k$.
+where $\L^k$ captures $k$-neighborhoods.\footnote{The 1-neighborhood of a vertex is the set of vertices that are directly connected to it.
+The $k$-neighborhood of a vertex is the set of vertices that are connected to it through paths of length $k$.}
+The entry $(\L^k)_{ij}$ is the sum of all weighted paths of length $k$ between vertices $v_i$ and $v_j$, where the weight of a path is the multiplication of all the edge weights on the path.
+Hence, it is non-zero if and only if vertices $v_i$ and $v_j$ are connected by at least one path of length $k$.
 Filtering with a polynomial convolution kernel can thus be interpreted in the pixel (vertex) domain as a weighted linear combination of neighboring pixel values.
@@
 The weights are however given by the filter coefficients only, and there is one coefficient per pixel in the patch.
-In the graph setting, the weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$, and there is one coefficient per neighborhood, not node.
+In the graph setting, the weights are determined by the filter coefficients $\theta$ and the Laplacian $\L$, and there is one coefficient per neighborhood, not vertex.
 That defines radial filters, values of which depend only on the distance to the center, and not on the direction.
-% It is required as there is no way to order and match nodes from the same neighborhood.
-% The number of nodes in a neighborhood most often even vary from node to node.
+% It is required as there is no way to order and match vertices from the same neighborhood.
+% The number of vertices in a neighborhood most often even vary from vertex to vertex.
 While it may seem odd to restrict filters to be 1D while the sphere is 2D, radial filters are direction-less and result in rotation equivariant convolutions.
@@
 Merging cells lead to a coarser graph.
-Coarsening defines $\C(i)$, the set of children of node $v_i$.
+Coarsening defines $\C(i)$, the set of children of vertex $v_i$.
 For the HEALPix subdivision scheme, the number of children is constant, i.e., $| \C(i) | = 4^p \ \forall i$, for some $p$.
@@
 
-Given a matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$, a $GC$ layer computes $\Y = GC(\X) = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels (and nodes), $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
+Given a matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$, a $GC$ layer computes $\Y = GC(\X) = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels (and vertices), $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features.
 Using the efficient graph convolution from \eqnref{graph_convolution_cheby}, each output feature map is computed as
@@
 % agnostic to the size of the input data, i.e., it can classify maps which do not have the same number of pixels.
-Such global summarization as the $AV$ layer is commonly used along graph convolutions to classify graphs of varying sizes (as it is invariant to node permutation) \citep{duvenaud2015gcn, li2015gatedgnn}.
+Such global summarization as the $AV$ layer is commonly used along graph convolutions to classify graphs of varying sizes (as it is invariant to vertex permutation) \citep{duvenaud2015gcn, li2015gatedgnn}.
 As such, CNNs should only be used if rotation invariance is undesired.
@@
 Right: graph built from a HEALPix pixelization of half the sphere ($N_{side} = 4$).
-By construction, each node has eight neighbors, except the highlighted ones which have only seven.\footnotemark[4] Left and middle figures are taken from \citep{boomsma2017spherical}.}
+By construction, each vertex has eight neighbors, except the highlighted ones which have only seven.\footnotemark[4] Left and middle figures are taken from \citep{boomsma2017spherical}.}
     \label{fig:sphere_grids}
@@
 The idea is to plot the section of the convolved Kroneker $\delta$.}
-To do so, we convolve a Kroneker $\delta$ on the nodes along the equator and use the equator for our section.
+To do so, we convolve a Kroneker $\delta$ on the vertices along the equator and use the equator for our section.
 Note that, because of the small irregularities in the HEALPix sampling, the second and the third methods are subject to small variations depending on the chosen position of the Kroneker $\delta$ .

### 2019-03-04 rebuttal.tex

@@
 \end{mdframed}
-\todo{Assigned: @tomek}
-\TK{not sure what do to here.. will people get upset? "Precision" is commonly used in cosmology}
+
+Thank you for this comment. Precision, understood as the final size of the posterior distribution on the measured parameters (including systematic errors), is the key interest of cosmology analysis.
+The robustness to noise is also crucial, as demonstrated in [9]. We expanded the sentence to include this.
+% \todo{Assigned: @tomek, @michael}
+% \TK{not sure what do to here.. will people get upset? "Precision" is commonly used in cosmology}
 

### 2019-03-04 rebuttal.tex
typos

@@
 We believe that it is now ready for publication.
-Currenlty, the dataset can be accessed simply via Zenodo.
-While this process is not anonymons, we provide in this rebuttal (Comment \#2) a special link for the reviewers to access it is anonymously.
+Currently, the dataset can be accessed simply via Zenodo.
+While this process is not anonymous, we provide in this rebuttal (Comment \#2) a special link for the reviewers to access it is anonymously.
 
@@
 
-We performed the comparizon with these features at it reflects the two-steps traditional way in classic machine learning: a) designing features b) using a method a ``simple'' classifier.
+We performed the comparison with these features at it reflects the two-steps traditional way in classic machine learning: a) designing features b) using a method a ``simple'' classifier.
 Deep learning changed this this tactic with networks that learn the features directly from the raw data.
@@
 
-This beeing said, we did try to train an SVM on the raw data, but were unable to obtain over $60\%$ accuracy in the three noiseless cases, which is far behind every other tested model.
+This being said, we did try to train an SVM on the raw data, but were unable to obtain over $60\%$ accuracy in the three noiseless cases, which is far behind every other tested model.
 Practically, the classifier would either overfit or be over-regularized.
@@
 
-As we believe that this projection is the optimal one to use a traditonal CNN for application, we performed the experiment using it.
+As we believe that this projection is the optimal one to use a traditional CNN for application, we performed the experiment using it.
 
@@
 % or justified. pointless is maybe too aggressive
-We do not believe this comparizon is useful because of the following theoretical reason
+We do not believe this comparison is useful because of the following theoretical reason
 There are two ways to deal with symmetries one wants to be invariant to: (i) build them into the architecture of the model, or (ii) augment the dataset such that a (more general) model learns them ``brute-force''.
@@
 \nati{The reviewer is correct.
-Our justification is shaddy.
+Our justification is shady.
 I am not sure how to make this clear, without writing too much.

### 2019-03-04 rebuttal.tex
before lunch

--- 2019-03-04 rebuttal.tex
@@
 \begin{mdframed}[style=comment]
-To prevent the cosmological models to be distinguished by their power spectra alone, the maps have been smoothed with a Gaussian kernel of radius 3 arcmins to remove high frequencies ($\ell$ > 1000).
-
-- This should be "To prevent the cosmological models from being distinguished by their power spectra alone the maps have been smoothed with a Gaussian kernel of radius 3 arcmins to remove high frequencies ($\ell$ > 1000).
+To prevent the cosmological models to be distinguished by their power spectra alone, the maps have been smoothed with a Gaussian kernel of radius 3 arcmins to remove high frequencies ($\ell> 1000$ ).
+
+- This should be "To prevent the cosmological models from being distinguished by their power spectra alone the maps have been smoothed with a Gaussian kernel of radius 3 arcmins to remove high frequencies ($\ell> 1000$ ).
 \end{mdframed}

### 2019-03-04 rebuttal.tex
small edits

@@
 \end{mdframed}
-\nati{This seems clear to me. Specifying what $\mathbb{R}_+$ is would be a bit too much I believe. @all -> is it also for you?}
+We are not sure what the reviewer means here. $\mathbb{R}_+$ is the ensemble of the real positive numbers and $h$ is simply a function that maps any positive real numbers to another real number.
+
+\nati{This seems clear to me. Specifying what $\mathbb{R}_+$ is would be a bit too much I believe. @all, is it also for you?}
 
@@
 \end{mdframed}
+% Here the notion of neighboorhood is defined in the context of graphs. Hence there is no coordinates to compute distances.
+
 \todo{Assigned: @michael}

### 2019-03-04 rebuttal.tex
details fixes

@@
 % \nati{I think the "as" is correct here. We use it for "because". Not sure...}
-\TK{Thank you for the suggestion, we adopted it.}
+Thank you for the suggestion, we adopted it.
 
@@
 % \nati{I prefer the version we have. But I leave it up to you to decide.}
-\TK{We updated the text as suggested.}
+We updated the text as suggested.
 
@@
 \end{mdframed}
-\TK{Indeed. We added a word "typically" to reflect that there may be cases like this.}
+Indeed. We added a word "typically" to reflect that there may be cases like this.
 
@@
 \end{mdframed}
-\todo{Assign: @tomek -> \nati{I corrected it with "which". Do you agree? }}
-\TK{Sounds good to me.}
+We followed the reviewer suggestion (and we went for ``which''). 
+% \todo{Assign: @tomek -> \nati{I corrected it with "which". Do you agree? }}
+% \TK{Sounds good to me.}
 
@@
 \todo{Assign: @nati, @michael}
+As already mentioned in this rebuttal, our belief comes from the fact that we are working on this. 
+Nevertheless, we agree with the reviewer that a scientific article should not contains speculations. 
+Hence, we removed that suggestion from the manuscript.
 
@@
 \end{mdframed}
-\todo{@assign: Tomek}
-\TK{Thank you for pointing it out, we believe that the original intended meaning is better reflected as is now.}
+Thank you for pointing it out, we believe that the original intended meaning is better reflected as is now.
 
@@
 \todo{Assign: @nati, @michael}
+With the zero padding, the border effects become similar to the ones in traditional CNNs. 
+This information has been added to the manuscript.
 

### 2019-03-04 scnn.tex
details fixes

@@
 Hence, the fact that the Laplacian eigenvalues are grouped in blocks of size $2\ell + 1$ is a hint that the graph eigenvectors approximate the spherical harmonics.
-In order to push the comparison one step further, we show the correspondence (scalar product) between the subspaces spanned by the graph Fourier modes and the spherical harmonics in \figref{subspace_harmonics_eigenvectors}.
+In order to push the comparison one step further, we show the correspondence (scalar product) between the subspaces spanned by the graph Fourier modes and the spherical ha, however, out of the scope of this contribution.rmonics in \figref{subspace_harmonics_eigenvectors}.
 The block-diagonal structure of the matrix, as opposed to diagonal, results the fact that the phase of the graph eigenvector is not aligned with the one of the spherical harmonics.
@@
 Second, as the resolution is increased with $N_{side} \rightarrow \infty$ and $N_{pix} \rightarrow \infty$, we are still unsure if the eigenvectors would converge towards the spherical harmonics.
-We believe that it might be the case for a different construction of the graph (fully connected) and that a proof could be built on top of the work of~\cite{belkin2007convergence}.
+% We believe that it might be the case for a different construction of the graph (fully connected) and that a proof could be built on top of the work of~\cite{belkin2007convergence}.
 That is, however, out of the scope of this contribution.
+The theoretical study of the convergence is, however, out of the scope of this contribution.
 Third, counter-intuitively, some eigenvectors will be localized~\citep{perraudin2018global}, i.e., they will span a small part of the sphere.
@@
 These border effects can, however, be mitigated by padding with zeros a small area around the part of interest. 
+In this case, they are similar to the border effects in traditional CNNs.
 We however do not expect these effects to cause any problem as long as the data samples cover the same area.

### 2019-03-04 rebuttal.tex
rebutta
some more comments adressed

@@
 \end{mdframed}
+We followed the reviewer suggestion.
+
+\begin{mdframed}[style=comment]
+Note that the output $\bf{Y}\in\mathbb{R}^{N_{pix}\times F_{out}}$ of the last GC (or the output $\bf{Y}\in\mathbb{R}^{N_{stat}\times F_{out}}$ of the ST), ...
+
+- What is ST, you don't mention it before and only once after?
+\end{mdframed}
 \todo{Assigned: @michael}
@@
 \begin{mdframed}[style=comment]
-Note that the output $\bf{Y}\in\mathbb{R}^{N_{pix}\times F_{out}}$ of the last GC (or the output $\bf{Y}\in\mathbb{R}^{N_{stat}\times F_{out}}$ of the ST), ...
-
-- What is ST, you don't mention it before and only once after?
+The output’s size of the neural network depends on the task.
+
+- It would be more correct to write "The size of the output of the neural network depends on the task."
+\end{mdframed}
+We agree with the reviewer and have updated the manuscript.
+
+\begin{mdframed}[style=comment]
+Its radius should be large enough to capture statistics of interest.
+
+- I think you mean the radius of the kernel. Perhaps this could be rewritten.
+\end{mdframed}
+\todo{Assign: @tomek}
+\todo{To check: @all}
+\nati{The manuscript seems clear to me. But let me know if you think otherwise.}
+
+\begin{mdframed}[style=comment]
+For example, a small a partial sky observation can provide only limited information of cosmological relevance.
+
+- There is just a little mix up in this sentence, maybe a copy and paste accident.
+\end{mdframed}
+Thanks for spotting it. We have fixed this mistake.
+
+\begin{mdframed}[style=comment]
+The cost (or loss) function $C(\bf{Y},\bar{\bf{Y}}) = C(NN_\theta(\bf{X}),\bar{\bf{Y}})$ measures how good the prediction $\bf{Y}$ is for sample $\bf{X}$, given the ground truth $\bar{\bf{Y}}$.
+
+- This is true for supervised learning only and should be stated.
+\end{mdframed}
+\todo{To check: @michael}
+We are not sure this specification is necessary as this cost cannot be computed in an unsupervised setting. We decided to not change the text.
+% \nati{In an unsupervised setting, this can just not be computed... Specifying it seems redundant to me.}
+
+\begin{mdframed}[style=comment]
+For global prediction, the cost is as if $N_{pix} = 1$.
+
+- I think this should be "For global prediction $N_{pix} = 1$."
 \end{mdframed}
 \todo{Assigned: @michael}
-
-\begin{mdframed}[style=comment]
-The output’s size of the neural network depends on the task.
-
-- It would be more correct to write "The size of the output of the neural network depends on the task."
-\end{mdframed}
-We agree with the reviewer and have updated the manuscript.
-
-\begin{mdframed}[style=comment]
-Its radius should be large enough to capture statistics of interest.
-
-- I think you mean the radius of the kernel. Perhaps this could be rewritten.
-\end{mdframed}
-\todo{Assigned: @all}
-\nati{The manuscript seems clear to me. But let me know if you think otherwise.}
-
-\begin{mdframed}[style=comment]
-For example, a small a partial sky observation can provide only limited information of cosmological relevance.
-
-- There is just a little mix up in this sentence, maybe a copy and paste accident.
-\end{mdframed}
-Thanks for spotting it. We have fixed this mistake.
-
-\begin{mdframed}[style=comment]
-The cost (or loss) function $C(\bf{Y},\bar{\bf{Y}}) = C(NN_\theta(\bf{X}),\bar{\bf{Y}})$ measures how good the prediction $\bf{Y}$ is for sample $\bf{X}$, given the ground truth $\bar{\bf{Y}}$.
-
-- This is true for supervised learning only and should be stated.
-\end{mdframed}
-\todo{Assigned: @michael, @nati}
-\nati{In an unsupervised setting, this can just not be computed... Specifying it seems redundant to me.}
-
-\begin{mdframed}[style=comment]
+\nati{Here I do really understand this: the text reads:
+
+\textit{For a classification task, the cost is usually taken to be the cross-entropy
+\begin{equation*}
+	C(\Y, \bar \Y) = - \sum_{i=1}^{N_{pix}} \sum_{j=1}^{N_{classes}} \bar y_{ij} \log(y_{ij}),
+\end{equation*}
+where $\bar \Y \in \R^{N_{pix} \times N_{classes}}$ is the ground truth label indicator, i.e., $\bar y_{ij} = 1$ if pixel $i$ of sample $\X$ belongs to class $j$ and is zero otherwise.
 For global prediction, the cost is as if $N_{pix} = 1$.
-
-- I think this should be "For global prediction $N_{pix} = 1$."
-\end{mdframed}
-\todo{Assigned: @michael}
+For a regression task, a common choice is the mean squared error (MSE)}
+
+If you do a global prediction, you ar for sure in a regression task right? So I guess the two last sentence should be merged.
+}
 
@@
 \end{mdframed}
-\todo{Assign:  @nati, @michael. \nati{@micheal, please check this one carefully, also in the text, I am not sure my notation is correct}}
+\todo{Assign:  @nati, @michael. \nati{@Michael, please check this one carefully, also in the text, I am not sure my notation is correct}}
 
@@
 \end{mdframed}
-\todo{Assign: @nati, @michael, \nati{again I disagree with the reviewer}}
+\todo{To check: @michael, \nati{again I disagree with the reviewer}}
 
@@
 \end{mdframed}
-\todo{Assigned: @all}
-
-\nati{The reviewer is correct.
+\todo{To check: @all}
+
+The link with the Heisenberg's uncertainty principle does exist but it too complex to explain shortly.
+Hence we decided to remove the ``by Heisenberg’s uncertainty principle'' and keep the rest of the sentence as a general Fourier analysis recipe.
+% \todo{Assigned: @all}
+
+% \nati{The reviewer is correct.
 Our justification is shady.
@@
 The reason is that for the continuous Fourier transform, we have:
-\begin{equation*}
-\widehat{f(t\cdot)}(\omega)=\frac{1}{t}\hat{f}\left(\frac{\omega}{t}\right).
-\end{equation*}
-Hence by concentrating $f$ in the time domain, i.e. making $t$ smaller, we also reduce the derivative of $\widehat{f(t\cdot)}$ in the spectral domain, making it smoother.
-Heisenberg uncertainty principle bounds the concentration in both domains simultaneously, i.e. we have (to be checked if added to the paper)
-\begin{equation*}
-\text{var}({f})\text{var}({\hat{f}}) \geq \frac{1}{16 \pi^2}
-\end{equation*}
-Hence the theorem says that you cannot concentrate arbitrarily in one domain without de-concentrating in the other.
-
-Now the question is: how do we fix the text? Also Heisenberg does not exist in the discrete case...
-}
+% \begin{equation*}
+% \widehat{f(t\cdot)}(\omega)=\frac{1}{t}\hat{f}\left(\frac{\omega}{t}\right).
+% \end{equation*}
+% Hence by concentrating $f$ in the time domain, i.e. making $t$ smaller, we also reduce the derivative of $\widehat{f(t\cdot)}$ in the spectral domain, making it smoother.
+% Heisenberg uncertainty principle bounds the concentration in both domains simultaneously, i.e. we have (to be checked if added to the paper)
+% \begin{equation*}
+% \text{var}({f})\text{var}({\hat{f}}) \geq \frac{1}{16 \pi^2}
+% \end{equation*}
+% Hence the theorem says that you cannot concentrate arbitrarily in one domain without de-concentrating in the other.
+
+% Now the question is: how do we fix the text? Also Heisenberg does not exist in the discrete case...
+% }
 
@@
 \end{mdframed}
-\todo{Assign @michael}
+Thank you for spotting this. We added the necessary commas. We also change the word ``interwinding'' with ``combining''.
 
@@
 % \todo{Assign: @Tomek}
-\TK{Updated the sentence.}
+We updated the sentence following the reviewer suggestion.
+\nati{@Tomek, do you think it is fine that we do not say that class==comoslogy? It think so.}
 
@@
 \end{mdframed}
-\todo{Assign: @all}
-\nati{I think that the primary goal of adding noise is the make the problem harder, and show robust prediction, not the make the dataset larger...
+\todo{To check: @all}
+% \nati{I think that the primary goal of adding noise is the make the problem harder, and show robust prediction, not the make the dataset larger...
 Hence I disagree with the reviewer.
 What do you think?}
-\TK{This is an interesting observation.
+% \TK{This is an interesting observation.
 The noise is introduced to make the case realistic, as the mass map data in reality is always very noisy.
@@
 
-The primary goal of the noise addition is the make the problem harder and show robust prediction. We use it to augment our dataset as well. Hence we believe that the correct formulation is suitable.
+% The primary goal of the noise addition is the make the problem harder and show robust prediction. We use it to augment our dataset as well. Hence we believe that the correct formulation is suitable.
+
+This is an interesting observation.
+The noise is introduced to make the case realistic, as the mass map data in reality is always very noisy.
+It is convenient that this fact can be used for data augmentation too and make the ML problem solvable even with a small amount of initial simulation.
+As these two facts are connected, we prefer to leave the sentence as is.
 
@@
 \end{mdframed}
-\todo{Assigned @michael}
-\nati{Should we simply say "normalized network score"? I do not know...}
+\todo{To check: @michael}
+% \nati{Should we simply say "normalized network score"? I do not know...}
+
+We changed the manuscript to:
+\begin{mdframed}[style=comment]
+The normalized network scores are computed by the $SM$ layer.
+\end{mdframed}
 
@@
 \end{mdframed}
-\todo{Assign: @nati, @michael}
-\nati{We would need an appendix to do that. It is the last figure of the figure’s notebook (expected filter). I could spend two hours and write some equation... @michael, what do you think?}
+% \todo{Assign: @nati, @michael}
+% \nati{We would need an appendix to do that. It is the last figure of the figure’s notebook (expected filter). I could spend two hours and write some equation... @michael, what do you think?}
+We updated the section with a citation and some extra information.
+\begin{mdframed}[style=manuscript]
+We derived this rule from the Chebyshev polynomial equations and some empirical experiments.
+Following the principle presented in \cite{glorot2010understanding}, we searched for the initialisation scheme keeping the expected amplitude of the signal constant through the different layers of the neural network.
+\end{mdframed}
 

### 2019-03-04 scnn.tex
added sentence to cpaiton on filters
some more comments adressed

@@
 That operation is point-wise, i.e., $y_{ij} = \sigma(x_{ij})$ and $y_i = \sigma(x_i)$ for matrices $\X, \Y$ and vectors $\x, \y$.
-The rectified linear unit (ReLU) $\sigma(\cdot) = \max(\cdot, 0)$ is a common choice.
+The rectified linear unit (ReLU) $\sigma(\cdot) = \max(\cdot, 0)$ is a common choice and is the one we adopted for this contribution.
 
@@
 That field is isotropic and local, i.e., it forms a disk centered around the output pixel.
-Its radius is influenced by the polynomial order $K$ of $GC$ layers (setting how far the convolution operation looks around), and the down-sampling factor of P layers if any.
+Its radius is influenced by the polynomial order $K$ of $GC$ layers (setting how far the convolution operation looks around), and the down-sampling factor of $P$ layers if any.
 Its radius should be large enough to capture statistics of interest.
@@
 Localization is desired for the transformation to be stable to local deformation \citep{mallat2012scattering}, and most interactions in the data are local anyway.
-A straightforward way to impose locality in the original domain is to impose smoothness in the spectral domain, by Heisenberg's uncertainty principle.
+A straightforward way to impose locality in the original domain is to impose smoothness in the spectral domain.
+% , by Heisenberg's uncertainty principle.
 A more elegant approach is to define filters that are provably localized.
@@
 Thanks to their versatility, graph neural networks have been used in a variety of tasks, such as identifying diseases from brain connectivity networks \citep{ktena2018metriclearning} or population graphs \citep{parisot2017disease}, designing drugs using molecular graphs \citep{hop2018drugdesign}, segmenting 3D point clouds \citep{qi2017pointcloudsegmentation}, optimizing shapes to be aerodynamic \citep{baque2018shape}, and many more.
-By interwinding graph convolutional layers and recurrent layers \citep{seo2016gcrn}, they can for example model structured time series such as traffic on road networks \citep{li2018traffic}, or recursively complete matrices for recommendation \citep{monti2017recommendation}.
+By combining graph convolutional layers and recurrent layers \citep{seo2016gcrn}, they can, for example, model structured time series such as traffic on road networks \citep{li2018traffic}, or recursively complete matrices for recommendation \citep{monti2017recommendation}.
 Another trend, parallel to the modeling of structured data, is the use of graph neural networks for relational reasoning \citep{battaglia2018review}.
@@
 The $AV$ layer averages these predictions.
-Probabilities are computed by the $SM$ layer.
+The normalized network scores are computed by the $SM$ layer.
 
@@
 Third, we recommend initializing the Chebyshev coefficients with a centered Gaussian distribution with standard deviation $\sqrt{2/(F_{in} \times (K + 0.5))}$, where $K$ is the degree of the Chebyshev polynomials and $F_{in}$ the number of input channels.
-This standard deviation has the property of keeping the energy of the signal more or less constant across layers\footnote{We derived this rule from the Chebyshev polynomial equations and some empirical experiments.}.
+This standard deviation has the property of keeping the energy of the signal more or less constant across layers\footnote{We derived this rule from the Chebyshev polynomial equations and some empirical experiments.
+\nati{Following the principle presented in \cite{glorot2010understanding}, we searched for the initialisation scheme keeping the expected amplitude of the signal constant through the different layers of the neural network.}}.
 % Nati to Michael: The problem with the previous claim is that it depends on the non-linarity. Furthermore, does it make sense to make such a claim if we use batch norm?

### 2019-03-04 rebuttal.tex
update comments some more

@@
 \todo{assigned: @michael}
+\nati{I do not know what to say. I just do not care what is the definition of a CNN.}
 
@@
 \end{mdframed}
-\todo{assigned: @michael}
+We agree with the reviewer and updated the manuscript accordingly.
+% \todo{assigned: @michael}
 
@@
 \end{mdframed}
-% Here the notion of neighboorhood is defined in the context of graphs. Hence there is no coordinates to compute distances.
-
-\todo{Assigned: @michael}
+\todo{To check: @michael}
+
+Here, the notion of neighboorhood is defined in the context of graphs.
+As there is no coordinates to compute distances in this context, one way to define the distance between two vertices is to count the number of edges in the shortest path between these two vertices.
+To clarify this point, we added more context in the manuscript:
+
+\begin{mdframed}[style=manuscript]
+In the context of graph, one way to define the distance between two vertices is to count the number of edges in the shortest path between these two vertices.
+Hence, we define the 1-neighborhood of a vertex as the set of vertices that are directly connected to it.
+The $k$-neighborhood of a vertex is the set of vertices that are connected to it through paths of length $k$.
+\end{mdframed}
 
@@
 \end{mdframed}
-\todo{Assigned: @michael}
+We thank the reviewer for spotting this. Indeed $ST$ was not defined. In the manuscript, we have replaced $ST$ by statistical layer.
 
@@
 \todo{Assign: @all}
-\nati{The problem is that random filters are picky as well and look very similar.
+% \nati{The problem is that random filters are picky as well and look very similar.
 Should we say that?
@@
 Do you agree?}
+\TK{Added sentence}
 

### 2019-03-04 scnn.tex
update comments some more

@@
 A counter-example is the equirectangular projection, which is not constructed from a base polyhedron, although it can be subdivided.
-In the particular HEALPix case, the base is a rhombic dodecahedron, i.e., a polyhedron made from 12 congruent rhombic faces.\footnote{A rhombus is a quadrilateral whose four sides all have the same length.}
+In the particular HEALPix case, the base is a rhombic dodecahedron, i.e., a polyhedron made from 12 congruent rhombic faces.
+% \footnote{A rhombus is a quadrilateral whose four sides all have the same length.}
 See \figref{pooling} for an illustration of the base rhombic dodecahedron and its subdivisions.
@@
 \end{equation}
-where $\L^k$ captures $k$-neighborhoods.\footnote{The 1-neighborhood of a vertex is the set of vertices that are directly connected to it.
+where $\L^k$ captures $k$-neighborhoods.\footnote{In the context of graph, one way to define the distance between two vertices is to count the number of edges in the shortest path between these two vertices.
+Hence, we define the 1-neighborhood of a vertex as the set of vertices that are directly connected to it.
 The $k$-neighborhood of a vertex is the set of vertices that are connected to it through paths of length $k$.}
@@
 where $\W \in \R^{F_{out} \times F_{in}}$ and $\b b \in \R^{F_{out}}$ are the parameters to be learned.
-Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last $GC$ (or the output $\Y \in \R^{N_{stat} \times F_{out}}$ of the $ST$), is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first $FC$, where $F_{in} = N_{pix} \times F_{out}$ (or $N_{stat} \times F_{out}$).
+Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last $GC$ (or the output $\Y \in \R^{N_{stat} \times F_{out}}$ of the statistical layer), is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first $FC$, where $F_{in} = N_{pix} \times F_{out}$ (or $N_{stat} \times F_{out}$).
 
 The softmax layer is the last layer in a neural network engineered for classification.
-Given the output $\x \in \R^{N_{classes}}$ of the last $FC$ (or $ST$), called the logits in the deep learning literature, the softmax layer outputs $\y = SM(\x)$ such that
+Given the output $\x \in \R^{N_{classes}}$ of the last $FC$ (or statistical layer), called the logits in the deep learning literature, the softmax layer outputs $\y = SM(\x)$ such that
 \begin{equation*}
@@
 	\includegraphics[width=0.85\linewidth]{gnonomic_filter_last}
-	\caption{Random selection of 24 learned filters from the fifth spherical convolutional layer $L_5$. Top: section. Bottom: gnomonic projection.}
+	\caption{Random selection of 24 learned filters from the fifth spherical convolutional layer $L_5$. Top: section. Bottom: gnomonic projection.
+	The structure in the filters resembles peaks, which is not unexpected, given that the convergence maps largely consist of concentrated clumps.}
 	\label{fig:learned_filter}

### 2019-03-04 rebuttal.tex
update comments some more
end nati pass
typo

@@
 We performed the comparison with these features at it reflects the two-steps traditional way in classic machine learning: a) designing features b) using a method a ``simple'' classifier.
-Deep learning changed this this tactic with networks that learn the features directly from the raw data.
+Deep learning changed this tactic with networks that learn the features directly from the raw data.
 The PS and histograms were chosen because they are standard statistics used by the cosmology community for analysing real data.
@@
 Do you agree?}
-\TK{Added sentence}
+% \TK{Added sentence}
 
 We decided not to add a colorbar as scale information is already present in the top plot of the figure.
+We added a small explanation for the peak structure
+\begin{mdframed}[style=comment]
+The structure in the filters resembles peaks, which is not unexpected, given that the convergence maps largely consist of concentrated clumps.
+\end{mdframed}
 

### 2019-03-04 scnn.tex
updated radius info

@@
 That field is isotropic and local, i.e., it forms a disk centered around the output pixel.
-Its radius is influenced by the polynomial order $K$ of $GC$ layers (setting how far the convolution operation looks around), and the down-sampling factor of $P$ layers if any.
-Its radius should be large enough to capture statistics of interest.
+The radius of this filter is influenced by the polynomial order $K$ of $GC$ layers (setting how far the convolution operation looks around), and the down-sampling factor of $P$ layers, if any.
+This radius should be large enough to capture statistics of interest.
 For example, a partial sky observation can provide only limited information of cosmological relevance.

### 2019-03-04 rebuttal.tex
updated radius info
fix last comments

--- 2019-03-04 rebuttal.tex
@@
 \end{mdframed}
-\todo{assigned: @michael}
-\nati{I do not know what to say. I just do not care what is the definition of a CNN.}
+We agree with the reviewer that (iii) and (iv) are also optional. Hence we reformulated this sentence as:
+\begin{mdframed}[style=manuscript]
+A CNN is composed of the following main building blocks~\cite{lecun1998cnn}:
+(i) a convolution,
+(ii) a non-linearity.
+Optionally, some CNN also have
+(iii) a down-sampling operation,
+(iv) a pooling operation, and
+(v) a normalization.
+\end{mdframed}
 
@@
 \end{mdframed}
-\todo{Assigned: @michael}
-\nati{Here I do really understand this: the text reads:
-
-\textit{For a classification task, the cost is usually taken to be the cross-entropy
-\begin{equation*}
-	C(\Y, \bar \Y) = - \sum_{i=1}^{N_{pix}} \sum_{j=1}^{N_{classes}} \bar y_{ij} \log(y_{ij}),
-\end{equation*}
-where $\bar \Y \in \R^{N_{pix} \times N_{classes}}$ is the ground truth label indicator, i.e., $\bar y_{ij} = 1$ if pixel $i$ of sample $\X$ belongs to class $j$ and is zero otherwise.
-For global prediction, the cost is as if $N_{pix} = 1$.
-For a regression task, a common choice is the mean squared error (MSE)}
-
-If you do a global prediction, you ar for sure in a regression task right? So I guess the two last sentence should be merged.
-}
+\todo{To check: @michael}
+
+We changed the text as:
+\begin{mdframed}[style=manuscript]
+For global prediction, we have $N_{pix} = 1$.
+\end{mdframed}
 
@@
 We changed the manuscript to:
-\begin{mdframed}[style=comment]
+\begin{mdframed}[style=manuscript]
 The normalized network scores are computed by the $SM$ layer.
@@
 Do you agree?}
-\TK{Added sentence}
+% \TK{Added sentence}
 
 We decided not to add a colorbar as scale information is already present in the top plot of the figure.
+We added a small explanation for the peak structure
+\begin{mdframed}[style=manuscript]
+The structure in the filters resembles peaks, which is not unexpected, given that the convergence maps largely consist of concentrated clumps.
+\end{mdframed}
 
@@
 \end{mdframed}
-\todo{Assign: @all, \nati{What do you think? I had the feeling we already have that in the main body of the paper. I cannot remember where, though.}}
+We thank the reviewer for this suggestion.
+We agree it is an important point, especially when one discuss the rotation equivariance.
+Nevertheless, since almost all of this discussion is done in Appendix, it complicated to bring it to the main body of the paper without moving a significant part of the Appendix as well.
+\todo{To check: @all}
 

### 2019-03-04 scnn.tex
fix last comments

--- 2019-03-04 scnn.tex
@@
 (i) a convolution,
-(ii) a non-linearity,
+(ii) a non-linearity.
+Optionally, some CNN also have
 (iii) a down-sampling operation,
 (iv) a pooling operation, and
-(v), optionally,  normalization.\footnote{Batch normalization has been shown to help training \citep{ioffe2015batchnorm}. We verified this experimentally in our setting as well.}
+(v) a normalization.\footnote{Batch normalization has been shown to help training \citep{ioffe2015batchnorm}. We verified this experimentally in our setting as well.}
 Our architecture is depicted in~\figref{architecture} and discussed in greater details in \secref{architecture}.
@@
 where $\bar \Y \in \R^{N_{pix} \times N_{classes}}$ is the ground truth label indicator, i.e., $\bar y_{ij} = 1$ if pixel $i$ of sample $\X$ belongs to class $j$ and is zero otherwise. 
-For global prediction, the cost is as if $N_{pix} = 1$.
+For global prediction, we have $N_{pix} = 1$.
 For a regression task, a common choice is the mean squared error (MSE)
@@
 }
-\nati{Say something about the number of parameters/fitlers. }
 

### 2019-03-04 rebuttal.tex
comment 2.11

@@
 \end{mdframed}
-\todo{Assigned: @nati, @michael}
-We added a figure showing the percentage of mis-alignment with the spherical harmonics. We also moved Figure A.12 in the correct subsection.
-
-\begin{center}
-\includegraphics[width=0.5\linewidth]{figures/subspace_alignment_percentage.pdf}
-\end{center}
+
+% (To plot the difference between the graph eigenvectors and the spherical harmonics on the sphere, one would have to align the subspaces.) Impossible to rotate arbitrarily on HEALPix.
+We cannot compare individual eigenvectors and spherical harmonics because of arbitration rotations.
+While any rotation of the basis of a subspace (the space spanned by the eigenvectors and harmonics corresponding to a given degree $\ell$) doesn't alter the spanned subspace, the difference between the basis vectors before and after the rotation can be 100\%.
+
+Your suggestion however made us realize that figure A.12 was not ideal in comparing the eigenvectors to the spherical harmonics.
+As such, we replaced it with another that we hope is clearer.
+We also moved Figure A.12 in the correct subsection.
 
@@
 \end{mdframed}
-\todo{Assign: @tomek}
-\todo{To check: @all}
-\nati{The manuscript seems clear to me. But let me know if you think otherwise.}
+% \todo{Assign: @tomek}
+% \todo{To check: @all}
+% \nati{The manuscript seems clear to me. But let me know if you think otherwise.}
+We updated the text slightly.
 

### 2019-03-04 scnn.tex
comment 2.11

@@
 \label{sec:comparison_spherical_harmonics}
+
 The first 16 eigenvectors $[\b u_1, \ldots, \b u_{16}]$ of the graph Laplacian $\L$, forming the lower part of the graph Fourier basis $\U$, are shown in \figref{graph_harmonics}.
@@
 Hence, the fact that the Laplacian eigenvalues are grouped in blocks of size $2\ell + 1$ is a hint that the graph eigenvectors approximate the spherical harmonics.
-In order to push the comparison one step further, we show the correspondence (scalar product) between the subspaces spanned by the graph Fourier modes and the spherical ha, however, out of the scope of this contribution.rmonics in \figref{subspace_harmonics_eigenvectors}.
-The block-diagonal structure of the matrix, as opposed to diagonal, results the fact that the phase of the graph eigenvector is not aligned with the one of the spherical harmonics.
+In order to push the comparison one step further, we show the correspondence between the subspaces spanned by the graph Fourier modes and the spherical harmonics in \figref{subspace_harmonics_eigenvectors}.
+%The block-diagonal structure of the matrix, as opposed to diagonal, results the fact that the phase of the graph eigenvector is not aligned with the one of the spherical harmonics.
+
+\begin{figure}[t!]
+	\centering
+	\includegraphics[width=\linewidth]{graph_eigenvalues}
+	\caption{The eigenvalues $\bLambda$ of the graph Laplacian $\L = \U \bLambda \U\trans$, which corresponds to squared frequencies, are clearly organized in groups.
+Each group corresponds to a degree $\ell$ of the spherical harmonics.
+Each degree has $2\ell + 1$ orders.
+See also \figref{graph_harmonics}.}
+	\label{fig:graph_eigenvalues}
+\end{figure}
+
+\begin{figure}[t!]
+	\centering
+	\includegraphics[width=\linewidth]{subspace_harmonics_eigenvectors_v2}
+	\caption{Correspondence between the subspaces spanned by the graph Fourier modes and the spherical harmonics.
+		% No real convergence with increasing Nside.
+		Row $j$ is the sum of the (normalized) power spectral densities (PSDs), computed by the SHT, of the $2j+1$ graph Fourier modes $\b u_i$ identified with degree $j$.
+		(\figref{graph_eigenvalues} shows how Fourier modes can be identified to spherical degrees.)
+		The PSD is computed for degrees $\ell=0$ to $\ell = 3 N_{side} -1$.
+		Pixel $k$ in row $j$ measures the energy in frequency band $k$ of the graph Fourier modes identified to be part of band $j$.
+		The matrix should ideally be the identity.
+		While not the case, the plot shows how the subspaces agree: the subspaces spanned by the Fourier modes correspond to those spanned by the spherical harmonics in the low frequencies, while the Fourier modes leak towards adjacent frequency bands in the high frequencies.
+		While there is a systematic error, the Fourier modes agree at higher frequencies as $N_{side}$ increases.}
+		\label{fig:subspace_harmonics_eigenvectors}
+\end{figure}
 
 While these indications show that the constructed graph Fourier basis approximates well the spherical harmonics, one should not forget that the small irregularities in the sampling (non-constant number of neighboring pixels and varying distance between pixels, see \figref{healpix_graph_4}) have an important effect on the graph Fourier modes.
-First, we believe that they are responsible for energy leaking outside of the block diagonal in \figref{subspace_harmonics_eigenvectors}.
+First, we believe that they are responsible for energy leaking across frequency bands in \figref{subspace_harmonics_eigenvectors}.
 Second, as the resolution is increased with $N_{side} \rightarrow \infty$ and $N_{pix} \rightarrow \infty$, we are still unsure if the eigenvectors would converge towards the spherical harmonics.
@@
 Nevertheless, our experiments suggest that these downsides do not have an important effect on the convolution nor hinder the performance of the neural network.
-
-\begin{figure}[ht!]
-	\centering
-	\includegraphics[width=\linewidth]{graph_eigenvalues}
-	\caption{The eigenvalues $\bLambda$ of the graph Laplacian $\L = \U \bLambda \U\trans$, which corresponds to squared frequencies, are clearly organized in groups.
-Each group corresponds to a degree $\ell$ of the spherical harmonics.
-Each degree has $2\ell + 1$ orders.
-See also \figref{graph_harmonics}.}
-	\label{fig:graph_eigenvalues}
-\end{figure}
-
-\begin{figure}[ht!]
-	\centering
-	\includegraphics[width=\linewidth]{subspace_harmonics_eigenvectors}
-	\includegraphics[width=\linewidth]{figures/subspace_alignment_percentage.pdf}
-	\caption{Top: Correspondence between the subspaces spanned by the graph Fourier modes and the spherical harmonics.
-Each pixel on the plot is the dot product between one spherical harmonic and one graph Fourier mode $\b u_i$.
-The plot clearly shows how the subspaces are aligned: modes and harmonics that correspond to different degrees $\ell$ are mostly orthogonal to each other, while modes and harmonics that correspond to the same degree $\ell$ are linearly dependent.
-There are $2 \ell + 1$ orders per degree $\ell$.
-Moreover, we see that the Fourier modes have the correct symmetries, indicated by the perfect orthogonality between even and odd functions.
-For example, the modes corresponding to $\ell=7$ are perfectly orthogonal to the harmonics corresponding to $\ell=0,2,4,6,8$.
-	\nati{Bottom: Evolution of the allignement of the graph Fourier mode and the spherical harmonics for with respect of the speherical harmonic index $\ell$.
-It is the percentage of energy contained in the diagonal blocks of the correlation matrix plotted on top.}}
-	\label{fig:subspace_harmonics_eigenvectors}
-\end{figure}
 

### 2019-03-04 rebuttal.tex
comment 2.12
comment 2.13

@@
 In theory, there should be a connection between the two values providing the graph Laplacian has converged toward the Laplace Beltrami operator.
-Again, this is left for a futur contribution.
+Again, this is left for a future contribution.
 
@@
 \end{mdframed}
-We are thinking about it.
-However, as the graph framework we are using only works with radial filters, it is not a simple question.
-One simple trick to make the network sensitive to direction is to add a per-channel fully connected layers.
-We are currently investigating other potential graph techniques that would lead to non-radial kernels.
+We thought about it but are not sure that it would be beneficial.
+%The main difficulty is that a graph is not intrinsically oriented.
+%However, as the graph framework we are using only works with radial filters, it is not a simple question.
+%A simple trick to make the network sensitive to direction is to add a per-channel fully connected layer.
+%We are currently investigating other potential graph techniques that would lead to non-radial kernels.
 

### 2019-03-04 scnn.tex
some more changes

@@
 Cosmological information contained in these maps is usually extracted using summary statistics, such as the power spectra or higher order correlation functions.
-Convolutional Neural Networks (CNNs) have been proposed as an alternative analysis tool in cosmology thanks to their ability to automatically design relevant statistics to maximise the precision of the parameter estimation
+Convolutional Neural Networks (CNNs) have been proposed as an alternative analysis tool in cosmology thanks to their ability to automatically design relevant statistics to maximise the precision\footnote{Here, the word ``precision'' is to be understood as the final size of the posterior distribution on the measured parameters (including systematic errors).} of the parameter estimation
 \citep{schmelze2017cosmologicalmodel,luciesmith2018machinelearning,gupta2018nongaussianinformation,gillet2018deeplearning,hassan2018reionizationmodels,aragoncalvo2018classyfyinglarge,ciuca2017cnnstring,ravanbakhsh2017estimating}, while maintaining robustness to noise.
@@
 \nati{
-Additionally, we compare DeepSphere to a traditional 2-dimensional convolutional neural network (2DCNN).
-To do so, the samples are first transformed into a square image before being fed into the 2DCNN.
+Additionally, we compare DeepSphere to a traditional 2-dimensional convolutional neural network (2D ConvNet).
+To do so, the samples are first transformed into a square image before being fed into the 2D ConvNet.
 As described in \ref{sec:projection}, we use the geometrical properties of HEALPix to construct an efficient and simple projection of the samples.
 Note that during the review process another spherical CNN architecture using exploiting this property appeared \cite{krachmalnicoff2019convolutional}.
-We used convolution kernel of size $5\times 5$ and reduced the number of filters in order to match the number of variables between DeepSphere and the 2DCNN.
+We used convolution kernel of size $5\times 5$ and reduced the number of filters in order to match the number of variables between DeepSphere and the 2D ConvNet.
 }
@@
 	\caption{
-		Classification accuracy of the fully convolutional (FCN) variant of DeepSphere, the standard convolutional (CNN) variant of DeepSphere, the support vector machine (SVM) with the power spectral density (PSD) as features, and the SVM with the histogram as features.
+		Classification accuracy of the fully convolutional (DeepSphere FCN) variant of DeepSphere, the standard convolutional (DeepSphere CNN) variant of DeepSphere, the fully convolutional ConvNet (2D ConvNet FCN), the standard convolutional ConvNet (2D ConvNet CNN), the support vector machine (SVM) with the power spectral density (PSD) as features, and the SVM with the histogram as features.
 		The difficulty of the task depends on the level of noise and the size of a sample (that is, the number of pixels that constitute the sample to classify).
@@
 	\caption{Correspondence between the subspaces spanned by the graph Fourier modes and the spherical harmonics.
+		The correspondance is computed in two steps. (i) We compute the PSD of each graph eigenvector.
+		(ii) As, for each harmonic index $\ell$, there is $2\ell+1$ spherical harmonics, we sum the contribution of the corresponding $2\ell+1$ graph eigenvectors. 
 		% No real convergence with increasing Nside.
-		Row $j$ is the sum of the (normalized) power spectral densities (PSDs), computed by the SHT, of the $2j+1$ graph Fourier modes $\b u_i$ identified with degree $j$.
-		(\figref{graph_eigenvalues} shows how Fourier modes can be identified to spherical degrees.)
-		The PSD is computed for degrees $\ell=0$ to $\ell = 3 N_{side} -1$.
-		Pixel $k$ in row $j$ measures the energy in frequency band $k$ of the graph Fourier modes identified to be part of band $j$.
+		% Row $j$ is the sum of the (normalized) power spectral densities (PSDs), computed by the SHT, of the $2j+1$ graph Fourier modes $\b u_i$ identified with degree $j$.
+		% (\figref{graph_eigenvalues} shows how Fourier modes can be identified to spherical degrees.)
+		% The PSD is computed for degrees $\ell=0$ to $\ell = 3 N_{side} -1$.
+		% Pixel $k$ in row $j$ measures the energy in frequency band $k$ of the graph Fourier modes identified to be part of band $j$.
 		The matrix should ideally be the identity.

### 2019-03-04 rebuttal.tex
some more changes
comment 2.14 (details) part 1

@@
 \end{mdframed}
-Thank you very much for taking the time for making these corrections. We find them very helpful and improving the quality of the paper.
+
+Thank you very much for taking the time for making these corrections.
+We found them very helpful in improving the quality of the paper.
 We implemented most of them, see below.
@@
 
-Thank you for this comment. Precision, understood as the final size of the posterior distribution on the measured parameters (including systematic errors), is the key interest of cosmology analysis.
-The robustness to noise is also crucial, as demonstrated in [9]. We expanded the sentence to include this.
-% \todo{Assigned: @tomek, @michael}
+Precision, understood as the final size of the posterior distribution on the measured parameters (including systematic errors), is the key interest of cosmology analysis.
+The robustness to noise is also crucial, as demonstrated in [9].
+%We expanded the sentence to include this.
+We added a footnote to specify this.
 % \TK{not sure what do to here.. will people get upset? "Precision" is commonly used in cosmology}
@@
 \end{mdframed}
+
 Thank you for the suggestion, normally we would adopt it, but the paper is already quite long, and breaking up the lines in equations would make it even longer. So we decided against it.
@@
 \begin{mdframed}[style=comment]
-You change a lot between "node", "vertex" and "pixel".
+You change a lot between ``node'', ``vertex'' and ``pixel''.
 Could you stick to one of these?
-I think that "vertex" or "pixel" makes the most sense ("pixel" due to the HEALPix pixelisation of the maps or vertex because of the use of the $v$ notation).
+I think that ``vertex'' or ``pixel'' makes the most sense (``pixel'' due to the HEALPix pixelisation of the maps or vertex because of the use of the $v$ notation).
 Node is quite confusing in several places because there is an inherent connection between node and neuron in ML literature, and since there is swapping between the three different terms it's a little hard to keep track.
 \end{mdframed}
-We agree with the reviewer that using different term for the same notion can be confusing for the reader.
-Nevertheless, while ``a node'' and ``a vertex'' are synonyms refering to a graph part, ``a pixel'' is a different concept refering to a point of the (spherical) sampling.
-As a result, we decided to keep the ``vertex'' and ``pixel''.
-% \todo{Assigned: @all}
+
+We agree that using different terms for the same notion can confuse readers.
+While ``node'' and ``vertex'' are synonyms in referring to the elements of a graph, a ``pixel'' is a different concept referring to a point of the (spherical) sampling.
+A pixel can be represented by a vertex, but they are not the same.
+As such, we decided to replace all occurrences of ``node'' with ``vertex'' but keep the two concepts of ``vertex'' and ``pixel'' separate.
+
 % \nati{What do you think? This avoid repetition. But we could be more consistent...}
 % \TK{Agreed. Do you want to make the change @nati?}
+% \mdeff{Agreed. Node is the same as vertex. Pixel is not necessarily.}
 
@@
 \end{mdframed}
-Thank you for the suggestion. We have made the paper consistent.
-\nati{@all, when you read the paper, please check that I did not forget some of them. Every layer has been changed to math symbols as we use them like function. For example, SM becomes $SM$.}
+We have made the paper consistent by using a math font for layer names.
+%\nati{@all, when you read the paper, please check that I did not forget some of them. Every layer has been changed to math symbols as we use them like function. For example, SM becomes $SM$.}
+%\mdeff{Agreed. I checked and fixed one missing.}
 
@@
 \end{mdframed}
-We have modified the manuscript according to the reviewer suggestion.
+We have modified the manuscript according to the suggestion.
 
@@
 \end{mdframed}
-This sentence has been reformulated as:
-\begin{mdframed}[style=manuscript]
-We consider the sky maps rotational invariant as in our case rotating maps on the sphere doesn't change their interpretation since only the statistics of the maps are relevant.
-\end{mdframed}
+True.
+Equivariance is desired in such a case (rather than invariance).
+We clarified the sentence.
 
@@
 \end{mdframed}
-Thank you for the suggestion, we updated the text.
+Thank you for the suggestion. We updated the text.
 
@@
 \end{mdframed}
-We agree with the reviewer that (iii) and (iv) are also optional. Hence we reformulated this sentence as:
-\begin{mdframed}[style=manuscript]
-A CNN is composed of the following main building blocks~\cite{lecun1998cnn}:
-(i) a convolution,
-(ii) a non-linearity.
-Optionally, some CNN also have
-(iii) a down-sampling operation,
-(iv) a pooling operation, and
-(v) a normalization.
-\end{mdframed}
+We agree that (iii) and (iv) are optional and updated the sentence accordingly.
 
@@
 \end{mdframed}
-This has been rephrased as:
-\begin{mdframed}[style=manuscript]
-Likewise, down-sampling can be achieved by keeping one pixel every $n$ pixels with $n=2$ being very common.
-\end{mdframed}
+We rephrased it.
 
@@
 \end{mdframed}
-We agree with the reviewer and updated the manuscript accordingly.
-% \todo{assigned: @michael}
+Agreed. We removed the footnote.
 
@@
 \begin{mdframed}[style=comment]
-Given the convolution kernel $h:\mathbb{R}_+ \to \mathbb{R}$,a signal $f\in\mathbb{R}^{N_{pix}}$ on the graph is filtered as
+Given the convolution kernel $h:\mathbb{R}_+ \to \mathbb{R}$, a signal $f\in\mathbb{R}^{N_{pix}}$ on the graph is filtered as
 
@@
 \end{mdframed}
-We are not sure what the reviewer means here. $\mathbb{R}_+$ is the ensemble of the real positive numbers and $h$ is simply a function that maps any positive real numbers to another real number.
-
-\nati{This seems clear to me. Specifying what $\mathbb{R}_+$ is would be a bit too much I believe. @all, is it also for you?}
+We are not sure what the reviewer means here.
+$\mathbb{R}_+$ is the ensemble of the real positive numbers and $h$ is a function that maps any positive real number to a real number.
+We think that $\mathbb{R}_+$ is a common enough notation to not require being explicitly defined.
+
+%\nati{This seems clear to me. Specifying what $\mathbb{R}_+$ is would be a bit too much I believe. @all, is it also for you?}
+%\mdeff{That is also quite clear to me.}
 
@@
 \end{mdframed}
-We followed both of the reviewer suggestions.
+We followed both suggestions.
 
@@
 \end{mdframed}
-We changed the manuscript according to the reviewer suggestion.
+We followed the suggestion.
 

### 2019-03-04 scnn.tex
comment 2.14 (details) part 1

@@
 First, the convolution should be equivariant to rotation, meaning that a rotation of the input implies the same rotation of the output.
-\nati{We consider the sky maps rotationial invariant as in our case rotating maps on the sphere doesn't change their interpretation since only the statistics of the maps are relevant.}
-Depending on the task, we want the CNN to be either equivariant or invariant to rotation.
+Sky maps are rotation equivariant: rotating a map on the sphere doesn’t change its interpretation.
+Depending on the task, we want the CNN to be either equivariant or invariant to rotation.\footnote{When only the statistics of the maps are relevant, they are rotation invariant.}
 Second, to be able to train the network in reasonable time, the convolution has to be computationally efficient.
@@
 (i) a convolution,
-(ii) a non-linearity.
-Optionally, some CNN also have
+(ii) a non-linearity, and, optionally,
 (iii) a down-sampling operation,
@@
 On regular Euclidean domains, such as 1-dimensional time series or 2-dimensional images, a convolution can be efficiently implemented by sliding a localized convolution kernel (for example a patch of $5 \times 5$ pixels) in the signal domain.
-\nati{Likewise, down-sampling can be achieved by keeping one pixel every $n$ pixels with $n=2$ being very common.}
 Because of the irregular sampling, there is no straightforward way to define a convolution on the sphere directly in the pixel domain; convolutions are most often performed using spherical harmonics.
@@
 The implementation, however, does not need a direct access to the spectrum, which is computationally more efficient (see \secref{efficient_convolution}).
+
+Down-sampling is achieved on regular Euclidean domains by keeping one pixel every $n$ pixels in every dimension.
+That is again not a suitable strategy on the sphere because of the irregular sampling.
+
 The gist of our method is to define the convolution operation on a sphere using a graph, and the down-sampling operation using a hierarchical pixelisation of the sphere.
@@
 The lowest possible resolution is given by the base partitioning of the surface into $N_{pix} = 12$ equal-sized pixels (right-most sphere in \figref{pooling}).
-% As each pixel is subdivided in four, the second coarser resolution is $N_{pix} = N_{side}^2 \times 12 = 2^2 \times 12 = 48$ pixels (middle sphere in \figref{pooling}), the third is $N_{pix} = N_{side}^2 \times 12 = 4^2 \times 12 = 192$ pixels, etc., where $N_{side} = 1, 2, 4, 8, \ldots$ is the grid resolution parameter.
-The resolution changes as $N_{pix} = N^2_{side}\times12$ such that $N_{pix} = 48$ for $N_{side} = 2$ and $N_{pix} = 192$ with $N_{side}=3$.
-High-resolutions HEALPix maps easily reach millions of pixels.
+The resolution changes as $N_{pix} = 12 N^2_{side}$ such that $N_{pix} = 48$ for $N_{side} = 2$ and $N_{pix} = 192$ for $N_{side} = 3$.
+High-resolutions maps easily reach millions of pixels.
 
@@
 where $\circ$ denotes composition, i.e., $(f \circ g)(\cdot) = f(g(\cdot))$.
-If P layers are used, they have to be inverted via up-sampling in an encoder-decoder architecture.
+If $P$ layers are used, they have to be inverted via up-sampling in an encoder-decoder architecture.
 
@@
 As a second visualization (middle), we observe the kernel directly on the sphere.
-As the kernel $K_t$ is defined in the graph spectral domain, we convolve a Kroneker $\delta$  to obtain a representation on the sphere.
+As the kernel $K_t$ is defined in the graph spectral domain, we convolve a Kronecker $\delta$ to obtain a representation on the sphere.
 We then plot the result with a gnomonic projection.
@@
 This visualization might be convenient as we theoretically have spherical filters (up to the irregularities of the sampling).
-The idea is to plot the section of the convolved Kroneker $\delta$.}
-To do so, we convolve a Kroneker $\delta$ on the vertices along the equator and use the equator for our section.
-Note that, because of the small irregularities in the HEALPix sampling, the second and the third methods are subject to small variations depending on the chosen position of the Kroneker $\delta$ .
+The idea is to plot the section of the convolved Kronecker $\delta$.}
+To do so, we convolve a Kronecker $\delta$ on the vertices along the equator and use the equator for our section.
+Note that, because of the small irregularities in the HEALPix sampling, the second and the third methods are subject to small variations depending on the chosen position of the Kronecker $\delta$.
 

### 2019-03-04 rebuttal.tex
comment 2.14 (details) part 2

@@
 \end{mdframed}
-
-We updated the manuscript using:
-\begin{mdframed}[style=manuscript]
-where $T_i g[j] = g[i-j]$ is, up to a flip ($g[i-j]$ instead of $g[i+j]$), a translation operator.
-\end{mdframed}
+We precised the meaning of a flip.
 
@@
 \end{mdframed}
-% \todo{Assign: @michael, @tomek}
 % \nati{I do not know what we should do.}
-Thank you for your suggestion.
 Ideally we would replace equation references such as "(1)" with "Equation (1)", but given the large number of equation references, we would prefer to stick with a short-form to avoid lengthening the paper further.
+% \mdeff{Agree to not introduce more words.}
 
@@
 \end{mdframed}
-\todo{To check: @michael}
-
-Here, the notion of neighboorhood is defined in the context of graphs.
-As there is no coordinates to compute distances in this context, one way to define the distance between two vertices is to count the number of edges in the shortest path between these two vertices.
-To clarify this point, we added more context in the manuscript:
-
-\begin{mdframed}[style=manuscript]
-In the context of graph, one way to define the distance between two vertices is to count the number of edges in the shortest path between these two vertices.
-Hence, we define the 1-neighborhood of a vertex as the set of vertices that are directly connected to it.
-The $k$-neighborhood of a vertex is the set of vertices that are connected to it through paths of length $k$.
-\end{mdframed}
+
+The neighborhood is defined in the general context of graphs, where vertices don't necessarily have coordinates.
+One way to define a distance between two vertices is to count the number of edges in the shortest path between them.
+We clarified this point.
 
@@
 \end{mdframed}
-We mean "column" and have corrected the manuscript.
+We mean ``column'' and have updated the manuscript.
 
@@
 \end{mdframed}
-In fact, $p$ is defined as $p=\log_2(N_{side} / N'_{side})$. We have updated the manuscript with this clarification and with an equation environment.
+$p$ was introduced to highlight the fact that the coarsening factor is a power of 4 by construction of HEALPix.
+It is defined as $p=\log_2(N_{side} / N'_{side})$.
+We have updated the manuscript with this clarification and with an equation environment.
 
@@
 \end{mdframed}
-We have followed the reviewer suggestion.
+We followed the suggestion.
 
@@
 We have removed the identity specification.
-\begin{mdframed}[style=manuscript]
-A non-linear function $\sigma(\cdot)$ is applied after every linear $GC$ and $FC$ layer, except for the last $FC$ layer.
-\end{mdframed}
 
@@
 \end{mdframed}
-We followed the reviewer suggestion.
+We followed the suggestion.
 
@@
 \end{mdframed}
-We thank the reviewer for spotting this. Indeed $ST$ was not defined. In the manuscript, we have replaced $ST$ by statistical layer.
+Thanks for spotting this.
+It was a leftover from an earlier draft.
 
@@
 \end{mdframed}
-We agree with the reviewer and have updated the manuscript.
+We followed the suggestion.
 
@@
 % \nati{The manuscript seems clear to me. But let me know if you think otherwise.}
-We updated the text slightly.
+% \mdeff{Radius of the field, not kernel or filter.}
+We updated the text.
 

### 2019-03-04 scnn.tex
comment 2.14 (details) part 2

@@
 \end{equation*}
-where $T_i g[j] = g[i-j]$ is, up to a flip ($g[i-j]$ instead of $g[i+j]$), a translation operator.
+where $T_i g[j] = g[i-j]$ is, up to a flip (i.e., $g[i-j]$ instead of $g[i+j]$), a translation operator.
 Similarly as \eqnref{graph_convolution_spatial}, the convolution of the signal $f$ by a kernel $g$ is the scalar product of $f$ with translated versions $T_i g$ of the kernel $g$.
@@
 \end{equation}
-where $\L^k$ captures $k$-neighborhoods.\footnote{In the context of graph, one way to define the distance between two vertices is to count the number of edges in the shortest path between these two vertices.
-Hence, we define the 1-neighborhood of a vertex as the set of vertices that are directly connected to it.
-The $k$-neighborhood of a vertex is the set of vertices that are connected to it through paths of length $k$.}
+where $\L^k$ captures $k$-neighborhoods.
 The entry $(\L^k)_{ij}$ is the sum of all weighted paths of length $k$ between vertices $v_i$ and $v_j$, where the weight of a path is the multiplication of all the edge weights on the path.
-Hence, it is non-zero if and only if vertices $v_i$ and $v_j$ are connected by at least one path of length $k$.
+Hence, it is non-zero if and only if vertices $v_i$ and $v_j$ are connected by at least one path of length $k$.\footnote{The length of a path between two vertices defines a distance on the graph.}
 Filtering with a polynomial convolution kernel can thus be interpreted in the pixel (vertex) domain as a weighted linear combination of neighboring pixel values.
@@
 That operation is point-wise, i.e., $y_{ij} = \sigma(x_{ij})$ and $y_i = \sigma(x_i)$ for matrices $\X, \Y$ and vectors $\x, \y$.
-The rectified linear unit (ReLU) $\sigma(\cdot) = \max(\cdot, 0)$ is a common choice and is the one we adopted for this contribution.
+The rectified linear unit (ReLU) $\sigma(\cdot) = \max(\cdot, 0)$ is a common choice, and is the one we adopted in this contribution.
 
@@
 where $\W \in \R^{F_{out} \times F_{in}}$ and $\b b \in \R^{F_{out}}$ are the parameters to be learned.
-Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last $GC$ (or the output $\Y \in \R^{N_{stat} \times F_{out}}$ of the statistical layer), is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first $FC$, where $F_{in} = N_{pix} \times F_{out}$ (or $N_{stat} \times F_{out}$).
+Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last $GC$ is vectorized as $\x = \vect(\X) \in \R^{F_{in}}$ before being fed to the first $FC$, where $F_{in} = N_{pix} \times F_{out}$.
 
 The softmax layer is the last layer in a neural network engineered for classification.
-Given the output $\x \in \R^{N_{classes}}$ of the last $FC$ (or statistical layer), called the logits in the deep learning literature, the softmax layer outputs $\y = SM(\x)$ such that
+Given the output $\x \in \R^{N_{classes}}$ of the last $FC$, called the logits in the deep learning literature, the softmax layer outputs $\y = SM(\x)$ such that
 \begin{equation*}
@@
 That field is isotropic and local, i.e., it forms a disk centered around the output pixel.
-The radius of this filter is influenced by the polynomial order $K$ of $GC$ layers (setting how far the convolution operation looks around), and the down-sampling factor of $P$ layers, if any.
+The field's radius is influenced by the polynomial order $K$ of $GC$ layers (setting how far the convolution operation looks around), and the down-sampling factor of $P$ layers, if any.
 This radius should be large enough to capture statistics of interest.

### 2019-03-04 rebuttal.tex
comment 2.14 (details) part 3

@@
 \end{mdframed}
+
 Thank you very much for your comments. We addressed them to the best we could.
@@
 \end{mdframed}
+
 We thought about it but are not sure that it would be beneficial.
@@
 \end{mdframed}
+
 We have made the paper consistent by using a math font for layer names.
@@
 \end{mdframed}
+
 We have modified the manuscript according to the suggestion.
@@
 \end{mdframed}
+
 True.
@@
 \end{mdframed}
+
 Thank you for the suggestion. We updated the text.
@@
 \end{mdframed}
+
 Thank you for spotting this mistake. We updated the manuscript.
@@
 \end{mdframed}
+
 We agree that (iii) and (iv) are optional and updated the sentence accordingly.
@@
 \end{mdframed}
+
 We rephrased it.
@@
 \end{mdframed}
+
 Agreed. We removed the footnote.
@@
 \end{mdframed}
+
 Thank you for the suggestion, we updated the text.
@@
 \end{mdframed}
+
 This has been corrected.
@@
 \end{mdframed}
+
 We are not sure what the reviewer means here.
@@
 \end{mdframed}
+
 We followed both suggestions.
@@
 \end{mdframed}
+
 We followed the suggestion.
@@
 \end{mdframed}
+
 We precised the meaning of a flip.
@@
 \end{mdframed}
+
 % \nati{I do not know what we should do.}
@@
 \end{mdframed}
+
 We mean ``column'' and have updated the manuscript.
@@
 \end{mdframed}
+
 Inspired by the reviewer suggestion, we changed the layout of that equation.
@@
 \end{mdframed}
+
 Thanks for the suggestion. We changed the manuscript.
@@
 \end{mdframed}
+
 Thanks for spotting this.
@@
 \end{mdframed}
+
 % \todo{Assigned: @tomek}
@@
 \end{mdframed}
+
 Thank you for spotting this mistake. We have corrected the manuscript.
@@
 \end{mdframed}
+
 $p$ was introduced to highlight the fact that the coarsening factor is a power of 4 by construction of HEALPix.
@@
 \end{mdframed}
+
 We have removed the identity specification.
@@
 \end{mdframed}
+
 % \todo{Assign: @tomek}
@@
 \end{mdframed}
+
 Thanks for spotting it. We have fixed this mistake.
@@
 \end{mdframed}
-\todo{To check: @michael}
-We are not sure this specification is necessary as this cost cannot be computed in an unsupervised setting. We decided to not change the text.
+
+We do not think it is necessary to specify that this is true for supervised learning only.
+The phrase ``ground truth'' should be sufficient to indicate that.
+%This cost cannot be computed in an unsupervised setting anyway.
 % \nati{In an unsupervised setting, this can just not be computed... Specifying it seems redundant to me.}
+% \todo{To check: @michael}
+% \mdeff{Agreed. The whole paper is about supervized learning anyway.}
 
@@
 \end{mdframed}
-\todo{To check: @michael}
-
-We changed the text as:
+
+We changed the text to:
 \begin{mdframed}[style=manuscript]
@@
 
+%\todo{To check: @michael}
+%\mdeff{Agreed.}
+
 \begin{mdframed}[style=comment]
@@
 \end{mdframed}
-We thank the reviewer for spotting this mistake. We have updated the manuscript.
+
+We followed the suggestion.
 
@@
 \end{mdframed}
-\todo{Assign:  @nati, @michael. \nati{@Michael, please check this one carefully, also in the text, I am not sure my notation is correct}}
-
-According to us, the goal of training is to minimize the empirical risk, which does not contain the expectation.
-On the contrary, the goal of learning is to minimize the expected risk, i.e.
-we additionally do not want to overfit the training set.
-Hence we left "learning" in the text.
-Nevertheless, we specified the expectation operator.
+
+% According to us, the goal of training is to minimize the empirical risk, which does not contain the expectation.
+% On the contrary, the goal of learning is to minimize the expected risk, i.e., we additionally do not want to overfit the training set.
+% Hence we left ``learning'' in the text.
+% Nevertheless, we specified the expectation operator.
+% \nati{@Michael, please check this one carefully, also in the text, I am not sure my notation is correct}
+% \mdeff{Debatable. I can see overfitting as an anti-goal of training. Doesn't matter much to me. Agreeing with him is simpler. Hence:}
+We followed the suggestions.
 
@@
 \end{mdframed}
-\todo{To check: @michael, \nati{again I disagree with the reviewer}}
-
+
+% \todo{To check: @michael, \nati{again I disagree with the reviewer}}
+% \mdeff{Agree with Nathanaël.}
 We are not sure, we understand the reviewer.
-Back-propagation is a technique to compute the gradients and not to perform the update of the parameter.
+Back-propagation is a technique to compute gradients, not to update the parameters.
 The latter is done with SGD.
-So we believe that the original formulation of our sentence is more accurate than the reviewer proposition.
+We believe that the original formulation is more accurate than proposition.
 
@@
 \end{mdframed}
+
 This mistake has been corrected.
@@
 \end{mdframed}
-\todo{To check: @all}
-
-The link with the Heisenberg's uncertainty principle does exist but it too complex to explain shortly.
-Hence we decided to remove the ``by Heisenberg’s uncertainty principle'' and keep the rest of the sentence as a general Fourier analysis recipe.
-% \todo{Assigned: @all}
+
+We added the general idea behind the Heisenberg's uncertainty principle.
+% \mdeff{I prefer to leave "by Heisenberg [...]". Readers will otherwise wonder why the recipe... I borrowed the text from your below justification.}
+
+% The link with the Heisenberg's uncertainty principle does exist but is too complex to explain shortly.
+% We decided to remove ``by Heisenberg’s uncertainty principle'' and keep the rest of the sentence as a general Fourier analysis recipe.
 
@@
 \end{mdframed}
-Indeed, our method can be applied only on a part or the sphere. We have corrected the text.
+
+Indeed.
+We corrected the text.
 
@@
 \end{mdframed}
-Thank you for spotting this. We added the necessary commas. We also change the word ``interwinding'' with ``combining''.
+
+Thanks for spotting this.
+We added the necessary commas and changed ``interwinding'' for ``combining''.
 
@@
 \end{mdframed}
+
 We have corrected this formulation according to the reviewer suggestion.
@@
 \end{mdframed}
+
 We have updated the manuscript accordingly.
@@
 \end{mdframed}
+
 Indeed. We added a word "typically" to reflect that there may be cases like this.
@@
 \end{mdframed}
+
 % \todo{Assign: @Tomek}
@@
 \end{mdframed}
+
 \todo{To check: @all}
@@
 \end{mdframed}
+
 \todo{To check: @michael}
@@
 \end{mdframed}
+
 We followed the reviewer suggestions.
@@
 \end{mdframed}
+
 We corrected the manuscript.
@@
 \end{mdframed}
+
 % \todo{Assign: @nati, @michael}
@@
 \end{mdframed}
+
 \todo{Assign: @all}
@@
 \end{mdframed}
+
 We followed the reviewer suggestion (and we went for ``which'').
@@
 \end{mdframed}
+
 "it" refer to "graphs" in general. We have updated the manuscript.

### 2019-03-04 scnn.tex
comment 2.14 (details) part 3

@@
 
-\nati{The goal of learning is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = \esp \left[ C \left( NN_\theta(\X), \bar \Y \right) \right]$, where $\esp$ is the expectation over the joint distribution $(\X, \bar \Y)$.}
+The goal of training is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = \esp \left[ C \left( NN_\theta(\X), \bar \Y \right) \right]$, where $\esp$ is the expectation over the joint distribution $(\X, \bar \Y)$.
 In general, that expectation cannot be computed as the data distribution is unknown.
@@
 Localization is desired for the transformation to be stable to local deformation \citep{mallat2012scattering}, and most interactions in the data are local anyway.
-A straightforward way to impose locality in the original domain is to impose smoothness in the spectral domain.
-% , by Heisenberg's uncertainty principle.
+A straightforward way to impose locality in the original domain is to impose smoothness in the spectral domain, by Heisenberg's uncertainty principle.\footnote{Heisenberg's uncertainty principle states that a filter cannot be arbitrarily concentrated in one domain without being de-concentrated in the other.}
 A more elegant approach is to define filters that are provably localized.
@@
 
-\nati{All the presented methods, but our, cannot be easily accelerated when the data lies on a part of the sphere only.}
+All the presented 2D and spherical CNNs cannot be easily accelerated when the data lies on a part of the sphere only.
 That is an important use case in cosmology as measurements are often partial, i.e., whole sky maps are rare.

### 2019-03-04 rebuttal.tex
comment 2.14 (details) part 4

@@
 
-We have corrected this formulation according to the reviewer suggestion.
+We followed the suggestion.
 
@@
 
-% \todo{Assign: @Tomek}
-We updated the sentence following the reviewer suggestion.
-\nati{@Tomek, do you think it is fine that we do not say that class==comoslogy? It think so.}
+We followed the suggestion.
+
+% \nati{@Tomek, do you think it is fine that we do not say that class==comoslogy? It think so.}
+% \mdeff{I think it's two cosmologies as it's two sets of parameters. Adding again two classes is enough.}
 
@@
 
-\todo{To check: @all}
 % \nati{I think that the primary goal of adding noise is the make the problem harder, and show robust prediction, not the make the dataset larger...
@@
 
-This is an interesting observation.
-The noise is introduced to make the case realistic, as the mass map data in reality is always very noisy.
-It is convenient that this fact can be used for data augmentation too and make the ML problem solvable even with a small amount of initial simulation.
+This is an interesting observation. The noise is introduced to make the case realistic, as the mass map data in reality is always very noisy.
+It is convenient that this fact can be used for data augmentation too. % and make the ML problem solvable even with a small amount of simulations.
 As these two facts are connected, we prefer to leave the sentence as is.
@@
 
-\todo{To check: @michael}
 % \nati{Should we simply say "normalized network score"? I do not know...}
-
-We changed the manuscript to:
-\begin{mdframed}[style=manuscript]
-The normalized network scores are computed by the $SM$ layer.
-\end{mdframed}
+% \mdeff{SM normalizes the predictions}
+
+We updated the sentence.
 
@@
 
-We followed the reviewer suggestions.
+We followed the suggestions.
 
@@
 
-We corrected the manuscript.
+We followed the suggestion.
 
@@
 % \nati{We would need an appendix to do that. It is the last figure of the figure’s notebook (expected filter). I could spend two hours and write some equation... @michael, what do you think?}
+
 We updated the section with a citation and some extra information.
-\begin{mdframed}[style=manuscript]
-We derived this rule from the Chebyshev polynomial equations and some empirical experiments.
-Following the principle presented in \cite{glorot2010understanding}, we searched for the initialisation scheme keeping the expected amplitude of the signal constant through the different layers of the neural network.
-\end{mdframed}
 
@@
 
-\todo{Assign: @all}
 % \nati{The problem is that random filters are picky as well and look very similar.
@@
 We decided not to add a colorbar as scale information is already present in the top plot of the figure.
-We added a small explanation for the peak structure
-\begin{mdframed}[style=manuscript]
-The structure in the filters resembles peaks, which is not unexpected, given that the convergence maps largely consist of concentrated clumps.
-\end{mdframed}
+We added a small explanation for the peak structure.
 
@@
 
-We followed the reviewer suggestion (and we went for ``which'').
+We followed the suggestions.
+
 % \todo{Assign: @tomek -> \nati{I corrected it with "which". Do you agree? }}
@@
 \end{mdframed}
-\todo{Assign: @nati, @michael}
+
 As already mentioned in this rebuttal, our belief comes from the fact that we are working on this.
-Nevertheless, we agree with the reviewer that a scientific article should not contains speculations.
-Hence, we removed that suggestion from the manuscript.
+Nevertheless, we agree that a scientific article should not contain speculations.
+We removed that speculation.
 
@@
 \end{mdframed}
-Thank you for pointing it out, we believe that the original intended meaning is better reflected as is now.
+
+We followed the suggestion.
 
@@
 \end{mdframed}
-We have corrected this mistake according to the reviewer suggestion.
+
+We corrected the wording.
 
@@
 \end{mdframed}
-\todo{Assign: @nati, @michael}
+
 With the zero padding, the border effects become similar to the ones in traditional CNNs.
@@
 \end{mdframed}
-We have clarifed the sentence as:
-\begin{mdframed}[style=manuscript]
-Furthermore, the harmonic resemblance is another sign that the constructed graph is able to capture the spherical
-structure of the HEALPix sampling.
-\end{mdframed}
+
+We precised it.
 

### 2019-03-04 scnn.tex
comment 2.14 (details) part 4

@@
 The layers $L_1$ to $L_5$ build the statistical evidence to classify each pixel of a down-sampled sphere.
-The last $GC$ layer acts as a linear classifier and outputs two (non-normalized) predictions.
-The $AV$ layer averages these predictions.
-The normalized network scores are computed by the $SM$ layer.
+The last $GC$ layer acts as a linear classifier and outputs two predictions.
+The $AV$ layer averages these predictions and the $SM$ layer normalizes them.
 
@@
 Third, we recommend initializing the Chebyshev coefficients with a centered Gaussian distribution with standard deviation $\sqrt{2/(F_{in} \times (K + 0.5))}$, where $K$ is the degree of the Chebyshev polynomials and $F_{in}$ the number of input channels.
-This standard deviation has the property of keeping the energy of the signal more or less constant across layers\footnote{We derived this rule from the Chebyshev polynomial equations and some empirical experiments.
-\nati{Following the principle presented in \cite{glorot2010understanding}, we searched for the initialisation scheme keeping the expected amplitude of the signal constant through the different layers of the neural network.}}.
+This standard deviation has the property of keeping the energy of the signal more or less constant across layers.\footnote{We derived this rule from the Chebyshev polynomial equations, the principles presented in \cite{glorot2010understanding}, and some empirical experiments.}
 % Nati to Michael: The problem with the previous claim is that it depends on the non-linarity. Furthermore, does it make sense to make such a claim if we use batch norm?
+% MD: I don't know... But that's not too important.
 Finally, we observe that scaling the Laplacian's eigenvalues between $[-a, a]$, where $0 < a \leq 1$, significantly helps in stabilizing the optimization. We use $a = 0.75$ in our experiments.
@@
 That is, however, out of the scope of this contribution.
-The theoretical study of the convergence is, however, out of the scope of this contribution.
+The theoretical study of those phenomenons is left as future work.
 Third, counter-intuitively, some eigenvectors will be localized~\citep{perraudin2018global}, i.e., they will span a small part of the sphere.
@@
 \end{figure}
-Furthermore, the harmonic resemblance is another sign that the constructed graph is able to capture the spherical
-structure of the HEALPix sampling. In some applications, where the
-exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
+
+Furthermore, the harmonic resemblance is another sign that the constructed graph is able to capture the spherical structure of the HEALPix sampling.
+In some applications, where the exactitude of the convolution is not a requirement, such as de-noising, graph convolution could be used instead of using the spherical harmonics.
 In a neural network setting, the fact that the graph convolution is not exactly equivariant to rotation is probably compensated by the fact that convolution kernels are learned.
@@
 
-The graph setting used throughout this contribution corresponds to assuming reflective border conditions.
+The graph setting used throughout this contribution corresponds to assumed reflective border conditions.
 While that is irrelevant when working on the complete sphere (as it has no border), it slightly affects the convolution operation when only a part of the sphere is considered.
 As depicted in \figref{border_effects}, a filter localized near a border (via $h(\L) \b \delta_i$) is no longer isotropic.
-These border effects can, however, be mitigated by padding with zeros a small area around the part of interest.
-In this case, they are similar to the border effects in traditional CNNs.
+These border effects can, however, be mitigated by padding with zeros a small area around the part of interest (in which case they become similar to border effects in classical CNNs).
 We however do not expect these effects to cause any problem as long as the data samples cover the same area.

### 2019-03-04 rebuttal.tex
last pass upto comment 2.2

--- 2019-03-04 rebuttal.tex
@@
 While the CNN is a generalization, it doesn't perform as well as the FCN.
+We agree that show this in practice would be a great addition to the paper.
+Nevertheless, we were unable to make FCNN reach a baseline performance.
 In practice, the large number of parameters required by a FCNN severely restricts what can be tested on conventional hardware.
@@
 (Remember that all reported classifiers obtained close to $100\%$ accuracy in this setting.) Similar conclusions were observed with other settings.
+These results were not included as they simply too far from the SVM classifiers.
 %Furthermore, the harmonic resemblance is another sign that the constructed graph is able to capture the spherical structure of the HEALPix sampling, even when increasing the number of neurons for small part of the sphere (order $2$ and $4$).
@@
 Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
-Indeed, \cite{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing random uniform sampling of the manifold and a fully connected graph built with exponentially decaying weights.
+Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the manifold and a fully connected graph built with exponentially decaying weights.
 While our construction does not exactly respect their setting (the sampling is deterministic and the graph is not fully connected), we empirically observe a strong correspondence between the eigenmodes of both Laplacians (see Appendix A).
@@
 That is, graph filters are not approximating any predefined true harmonic-space filters anyway.
-It is however true that replacing spherical filtering (using the SHT) with graph filtering is an interesting prospect (in terms of speed) that might be possible in the future as suggested by Appendix B (Figure B.13).
+It is, however, true that replacing spherical filtering (using the SHT) with graph filtering is an interesting prospect (in terms of speed) that might be possible in the future as suggested by Appendix B (Figure B.13).
 We feel that, in its current state, graph filtering is probably not a good enough approximation to be usable when high-precision filtering is required.
-Nevertheless, theoretical improvements on a potential equivalence (or convergence) of the Laplacian eigenvectors to the spherical harmonics (see our answer to comment 1.4) could potentially make it competitive.
+Nevertheless, theoretical improvements on a potential equivalence (or convergence) of the Laplacian eigenvectors to the spherical harmonics (see our answer to the comment 1.4) could potentially make it competitive.
 
@@
 
-\todo{Assigned: @Nati, @Michael, @Tomek}
-\nati{Please check if you like what I did in light of the discussion we had.}
-
-We share the opinion of the reviewer when he says that 2D CNNs should probably work as well as DeepSphere, ``by taking in a projected 2D image of the sky and using *loads* of filters to learn about the distortion at different parts of the projected sky.'' Hence we decided to add a new experiment in the paper.
+%\todo{Assigned: @Nati, @Michael, @Tomek}
+%\nati{Please check if you like what I did in light of the discussion we had.}
+
+We share the opinion of the reviewer when he says that 2D convolution neural networks (2D ConvNet) should probably work as well as DeepSphere ``by taking in a projected 2D image of the sky and using *loads* of filters to learn about the distortion at different parts of the projected sky.'' Hence we decided to add a new experiment in the paper.
 
@@
 In the HEALPix sampling, the sphere is first separated into $12$ parts that are then subdivided into $4$ recursively.
-Eventually, each of these $12$ part resembles a square grid.
+Eventually, each of these $12$ parts resembles a square grid.
 As the problem we are solving only involve one of these 12 parts, we can use this natural structure to simply re-assign each HEALPix pixel to one of a 2 dimensional grid of size $N_{sides} \times N_{sides}$.
-This operation is computationally very cheap and probably spread quite evenly across the resulting image.
-This projection has recently been used for a CNN in cosmology in the very recent work \cite{krachmalnicoff2019convolutional}.
-
-As we believe that this projection is the optimal one to use a traditional CNN for application, we performed the experiment using it.
-
-Our expectation were similar with the one of the reviewer, but the results did surprise us as the performance of the traditional CNN did in general not match DeepSphere, (see Figure 9 of the manuscript).
+This operation is computationally very cheap and probably spread the projection error relatively evenly across the resulting image.
+We note that, this projection has recently been used for a CNN in cosmology in the very recent work \cite{krachmalnicoff2019convolutional}.
+%As we believe that this projection is the optimal one to use a traditional CNN for applications, we performed the experiment using it.
+
+Our expectation were alligned with the one of the reviewer, but the results did surprise us as the performance of the traditional CNN did in general not match DeepSphere, (see Figure 9 of the manuscript).
 It can probably be explained by the fact that 2DCNN breaks the rotational invariance of the data.
@@
 Note that, when visualizing the learned convolution kernels, we observed that they were not radial.
+We did not use *loads* of filters as suggested by the reviewer as the optimization was challenging and we already had to regularize significantly the network. 
+While adding more filters, did improve slightly the performance (never to the level of DeepSphere), it made the optimization even more challenging to the point where we could not obtain consistent results if we were to restart the training process.
+Eventually, we decided to report the results for the architecture with the same number of parameters as DeepSphere.
 

### 2019-03-04 scnn.tex
last pass upto comment 2.2

--- 2019-03-04 scnn.tex
@@
 Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
-Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing random uniform sampling of the manifold and a fully connected graph built with exponentially decaying weights.
+Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the manifold and a fully connected graph built with exponentially decaying weights.
 While our construction does not exactly respect their setting (the sampling is deterministic and the graph is not fully connected), we empirically observe a strong correspondence between the eigenmodes of both Laplacians (see \ref{sec:comparison_spherical_harmonics}).
@@
 \nati{
-To our surprise, the traditional 2DCNN did not match the performance of DeepSphere.
-It can probably be explained by the fact that 2DCNN breaks the rotational invariance of the data.
+To our surprise, the traditional 2D ConvNet did not match the performance of DeepSphere.
+It can probably be explained by the fact that the 2D ConvNet breaks the rotational invariance of the data.
 The problem comes from the fact that the projection introduce a distortion in the geometry and the network has to learn a correct weighting scheme to compensate for it.
@@
 \label{sec:projection}
-In order to compare the DeepSphere architecture with a traditional 2d-CNN, we need to project the spherical data onto a plane.
+In order to compare the DeepSphere architecture with a 2D ConvNet, we need to project the spherical data onto a plane.
 Problematically a radial projection is computationally expensive to the point where, because of the dataset augmentation, it becomes significantly more expensive than the actual training of the network.
@@
 In the HEALPix sampling, the sphere is first separated into $12$ parts that are then subdivided into $4$ recursively.
-Eventually, each of these $12$ part resembles a square grid.
+Eventually, each of these $12$ parts resembles a square grid.
 To visually see it, we refer the reader to \figref{border_effects}.
-As the problem we are solving only involve one of these 12 parts, we can use this natural structure to simply re-assign each HEALPix pixel to one of a 2 dimensional grid of size $N_{sides} \times N_{sides}$.
+As the problem we are solving only involve one of these $12$ parts, we can use this natural structure to simply re-assign each HEALPix pixel to one of a 2 dimensional grid of size $N_{sides} \times N_{sides}$.
 This operation is computationally very cheap and probably spread quite evenly across the resulting image.

### 2019-03-04 rebuttal.tex
last pass upto comment 2.2

@@
 Our graph is constructed as an approximation of the sphere $S^2$, a 2D manifold embedded in $\mathbb{R}^3$.
-Indeed, \citep{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the manifold and a fully connected graph built with exponentially decaying weights.
+Indeed, \cite{belkin2007convergence} showed that the graph Laplacian converges to the Laplace-Beltrami when the number of pixels goes to infinity providing uniform sampling of the manifold and a fully connected graph built with exponentially decaying weights.
 While our construction does not exactly respect their setting (the sampling is deterministic and the graph is not fully connected), we empirically observe a strong correspondence between the eigenmodes of both Laplacians (see Appendix A).

### 2019-03-04 rebuttal.tex
comment 2.14 (details) part 5

@@
 \end{mdframed}
-We thank the reviewer for this suggestion.
-We agree it is an important point, especially when one discuss the rotation equivariance.
-Nevertheless, since almost all of this discussion is done in Appendix, it complicated to bring it to the main body of the paper without moving a significant part of the Appendix as well.
-\todo{To check: @all}
+
+Thanks for the suggestion.
+We adopted it.
+
+% \todo{To check: @all}
+% \mdeff{I added a similar sentence in the related work section.}
+
+% We agree it is an important point, especially when one discusses rotation equivariance.
+% However, since almost all of this discussion is done in the appendix, it is complicated to bring this point to the main body without moving a significant part of the appendix as well.
 
@@
 \end{mdframed}
+
 Inspired by the reviewer comment, we have merged the three plots in a single figure and adapted the text accordingly.
@@
 \end{mdframed}
-We build this plot in order to show the section of the filter. We believe that it might be easier to read than the gnomonic projection. We have modified the text as:
-\begin{mdframed}[style=manuscript]
-For our third visualization (bottom), our goal is to plot the section of a filter.
-This visualization might be convenient as we theoretically have spherical filters (up to the irregularities of the sampling).
-The idea is to plot the section of the convolved Kroneker $\delta$.
-\end{mdframed}
+
+This plot shows the section of the filter.
+We believe that it might be easier to read than the gnomonic projection, as the filter is isotropic.
+We have modified the text.
 
@@
 \end{mdframed}
+
 We changed the sentence to:
@@
 \end{mdframed}
-\nati{
-We changed the sentence as:
-\begin{mdframed}[style=manuscript]
-The validation error might be slightly below the training error as the validation set is used to select hyper-parameters.
-\end{mdframed}
-For linear SVM, there is one hyper-parameter to tune. As we select the hyperparameter with the lowest validation error, it is possible that the validation error is lower than the training error.}
+
+% We changed the sentence as:
+% \begin{mdframed}[style=manuscript]
+% The validation error might be slightly below the training error as the validation set is used to select hyper-parameters.
+% \end{mdframed}
+
+For linear SVM, there is one hyper-parameter to tune. As we select the hyperparameter with the lowest validation error, it is possible that the validation error is lower than the training error.
 
@@
 \end{mdframed}
-We would like to thank the reviewer again for his exceptionally detailed review. We really appreciate his effort and the time he invested in his answers.
-He is welcome to contact us for additional information or discussion when the publication process will be over.
+
+We would like to thank the reviewer again for his exceptionally detailed review.
+We really appreciate his effort and the time he invested in his answers.
+He is welcome to contact us again for additional information or for a discussion post-publication.
 

### 2019-03-04 rebuttal.tex
2.11 done

--- 2019-03-04 rebuttal.tex
@@
 % or justified. pointless is maybe too aggressive
-We do not believe this comparison is useful because of the following theoretical reason
+We do not believe this comparison is useful because of the following theoretical reason.
 There are two ways to deal with symmetries one wants to be invariant to: (i) build them into the architecture of the model, or (ii) augment the dataset such that a (more general) model learns them ``brute-force''.
@@
 
-\TK{Seems a bit strong to me.. maybe we would write it in a softer language?}
-\nati{Now it is OK. But is it still strong enough. We should only point reviewer incoherence if necessary.}
+%\TK{Seems a bit strong to me.. maybe we would write it in a softer language?}
+%\nati{Now it is OK. But is it still strong enough. We should only point reviewer incoherence if necessary.}
 
@@
 Hence, we built one Laplacian and observed some similarities between the two operators instead.
-We agree that our wording was unfortunate and have modified the manuscript to mean that we empirically observed a strong correspondence rather than a proper convergence.
+We agree that our wording was unfortunate and we have modified the manuscript to mean that we empirically observed a strong correspondence rather than a proper convergence.
 The convergence (or even exact correspondence) is a problem we are currently investigating and plan to release as a separate contribution.
@@
 
-\todo{the new figure A.12 is maybe a weak proof of convergence}
-
-\mdeff{@nati, what do you think?} \nati{I like it. I totally agree with the new wording.}
+%\todo{the new figure A.12 is maybe a weak proof of convergence}
+
+%\mdeff{@nati, what do you think?} \nati{I like it. I totally agree with the new wording.}
 
@@
 Thanks for pointing out the typo, we fixed it.
-We do realize it's an important point, and agree that some people apply architectures to a different problem they have been devised for without much thoughts.
+We do realize it's an important point, and agree that some people apply architectures to a different problem they have been devised for without much thought.
 A large chunk of our paper is actually about using an appropriate NN architecture.
@@
 In the experiment, both were compared on a single core.
-They might however scale differently given one can be distributed through MPI and the other on a GPU.
+They might, however, scale differently given one can be distributed through MPI and the other on a GPU.
 The manuscript was updated.

### 2019-03-04 scnn.tex

@@
 In comparison, DeepSphere scales as $\bO(N_{pix})$ (see \secref{efficient_convolution}), at the expense of not being exactly equivariant (see \ref{sec:comparison_spherical_harmonics}).
-Being a mathematically well-defined rotation equivariant network is the main advantage of methods based on spherical harmonics.
+Being a mathematically well-defined rotation equivariant network is the main advantage of methods based on spherical harmonics, though the fact that convolution kernels are learned probably compensates for inexact equivariance.
 See \citep{kondor2018equivariance} for a rigorous treatment of convolution and equivariance in neural networks.
@@
 While the graph convolution remains different from the spherical convolution, this small experiment shows that, providing the correct parameters, the graph convolution can approximate the spherical convolution.
-For additional insights about the graph kernel $K_t$, we refer to the \figref{gaussian_filters_visualization}.
-% and~\ref{sec:filter_visualization}.
+\figref{gaussian_filters_visualization} should give more insights about the graph kernel $K_t$.
 
@@
 
-\begin{figure}[ht!]
-\centering
-\includegraphics[width=\linewidth]{gaussian_filters_spectral}\\
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=\linewidth]{gaussian_filters_spectral} \\
 	\vspace{0.2in}
-\includegraphics[width=\linewidth]{gaussian_filters_gnomonic}\\
+	\includegraphics[width=\linewidth]{gaussian_filters_gnomonic} \\
 	\vspace{0.2in}
-\hspace{0.3cm}\includegraphics[width=0.95\linewidth]{gaussian_filters_section}
-\caption{\nati{Visualization of the convolution kernel $K_t(x)=e^{-\tau t x}$.
-(top) Spectral domain.
-(middle) Cross-section of the kernel through the pixels along the equator.
-(bottom) Gnomonic projection.}}
+	\includegraphics[width=\linewidth]{gaussian_filters_section}
+	\caption{Visualization of the convolution kernel $K_t(x)=e^{-\tau t x}$. Top: spectral domain. Middle: gnomonic projection. Bottom: cross-section along the equator.}
 	\label{fig:gaussian_filters_visualization}
@@
 
-In \figref{gaussian_filters_visualization}, we further leverage this example to present the three visualizations of a HEALPix graph convolution kernel.
-We remember that the convolution kernel resulting from the heat diffusion is defined as $K_t(x)=e^{-\tau t x}$. For our (top) visualization, we simply plot this function, i.e., we evaluate $K_t$
-at the graph eigenvalues $\text{diag}(\bLambda)$. Note that, the lower eigenvalues $\lambda$ correspond to the lower frequencies, i.e., the spectral mode with less variation.
-As a second visualization (middle), we observe the kernel directly on the sphere.
-As the kernel $K_t$ is defined in the graph spectral domain, we convolve a Kronecker $\delta$ to obtain a representation on the sphere.
-We then plot the result with a gnomonic projection.
-\nati{For our third visualization (bottom), our goal is to plot the section of a filter.
-This visualization might be convenient as we theoretically have spherical filters (up to the irregularities of the sampling).
-The idea is to plot the section of the convolved Kronecker $\delta$.}
-To do so, we convolve a Kronecker $\delta$ on the vertices along the equator and use the equator for our section.
-Note that, because of the small irregularities in the HEALPix sampling, the second and the third methods are subject to small variations depending on the chosen position of the Kronecker $\delta$.
+We further leverage this example to present three visualizations of a convolution kernel.
+The first visualization (\figref{gaussian_filters_visualization}, top) is a plot of the kernel function, i.e., it shows $K_t$ evaluated at the graph eigenvalues $\text{diag}(\bLambda)$.
+% and~\ref{sec:filter_visualization}.
+Note that small eigenvalues $\lambda$ correspond to small frequencies, i.e., to spectral modes of low variation.
+The second visualization (\figref{gaussian_filters_visualization}, middle) shows the kernel localized on the sphere (gnomonic projection).
+As the kernel $K_t$ is defined in the graph spectral domain, it was convolved with a Kronecker $\delta$ to obtain a representation on the sphere (see \secref{graph_convolution}).
+The third visualization (\figref{gaussian_filters_visualization}, bottom) plots the section of the filter.
+This visualization might be easier to read as the filters are isotropic (up to the irregularities of the sampling).
+The plot is obtained by convolving a Kronecker $\delta$ on the vertices along the equator.
+Note that, because of the small irregularities in the HEALPix sampling, the second and third methods are subject to small variations depending on the chosen position of the Kronecker $\delta$.
 
@@
 The error clearly converged such that adding more samples will not improve the classifier.
-The validation error might be slightly below the training error as the validation set is used to select hyper-parameters.}
+The validation error might be slightly below the training error as it was used to select the hyper-parameters.}
 	\label{fig:hist_error_evolution}

### 2019-03-04 rebuttal.tex
finish rebuttal reading
wording in rebuttal

@@
 
-Dear Editor,
-
-Thanks for handling our submission.
-We have revised our manuscript following many of the reviewer suggestions.
-We believe that it is now ready for publication.
-Currently, the dataset can be accessed simply via Zenodo.
-While this process is not anonymous, we provide in this rebuttal (Comment \#2) a special link for the reviewers to access it is anonymously.
-
-We thank the reviewers for taking the time to review our manuscript and for their constructive comments. We have answered
+We thank the editor for handling our submission and organizing the peer-review process.
+We have revised our manuscript following the suggestions of the reviewers.
+We believe that we addressed most requests and that the manuscript is now ready for publication.
+We thank the reviewers for taking the time to review our manuscript and provide constructive comments that improved the quality of our contribution.
+
+Currently, access to the dataset can be requested via Zenodo.
+As this process is not anonymous, we provide in this rebuttal (comment \#2) a link for the reviewers to access it anonymously.
 
@@
 
-Dear reviewer,
-
-we thank you for your time and thorough comments.
+Dear reviewer, we thank you for your time and thorough comments.
 The manuscript improved thanks to your feedback.
@@
 \subsection{}
+
 \begin{mdframed}[style=comment]
@@
 % or justified. pointless is maybe too aggressive
-We do not believe this comparison is useful because of the following theoretical reason.
+We do not believe this comparison is useful because of the following reason.
 There are two ways to deal with symmetries one wants to be invariant to: (i) build them into the architecture of the model, or (ii) augment the dataset such that a (more general) model learns them ``brute-force''.
 With respect to rotation invariance, the FCN architecture is of the first kind, while the CNN is of the second kind.
-Assuming the task is truly invariant to said symmetry,\footnote{As argued in the introduction, cosmological maps are rotation invariant.} the performance of the first kind of models would be exactly the same as without augmentation, while the second kind would only catch up after seeing enough data to learn the invariance.
+Assuming the task is truly invariant to said symmetry,\footnote{As argued in the introduction, cosmological maps are rotation invariant or equivariant.} the performance of the first kind of models would be exactly the same as without augmentation, while the second kind would only catch up after seeing enough data to learn the invariance.
 % That is a waste of resources which is only justified if it's not possible to back the desired invariance in the architecture.
 Augmentation is only justified if it's not possible to back the desired invariance in the architecture.
-% The reviewer himself makes that point in comment 2.8: ``building a NN to suit your purposes''.
+As the reviewer writes in comment 2.8, we should be ``building a NN to suit [our] purposes''.
 We updated the manuscript to more precisely reflect this argumentation.
@@
 
-\subsection*{Minor comment}
+\subsection*{Minor comments}
 
@@
 As such, we replaced it with another that we hope is clearer.
+This new figure should satisfy your request.
 We also moved Figure A.12 in the correct subsection.
@@
 In theory, there should be a connection between the two values providing the graph Laplacian has converged toward the Laplace Beltrami operator.
-Again, this is left for a future contribution.
+% Again, this is left for a future contribution.
 
@@
 We thought about it but are not sure that it would be beneficial.
+We are also unsure about the proper way to do it.
 %The main difficulty is that a graph is not intrinsically oriented.
@@
 \subsection{Details}
+
 \begin{mdframed}[style=comment]

### 2019-03-05 scnn.tex
update the figures

@@
     Both are executed on a single core.
-	The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3) = \bO(N_{pix}^{3/2})$ for the spherical harmonics, where $\ell_{max}$ is the largest angular frequency.}
+	The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3) = \bO(N_{pix}^{3/2})$ for the spherical harmonics, where $\ell_{max}$ is the largest angular frequency.
+	The timings for the partial graphs correspond to the convolution on only a fraction (1/12, 1/48, 1/192) of the sphere. This illustrates how graph convolution scales with $N_{pix}$.
+	}
     \label{fig:filtering_speed}
@@
 On a single core, a naive implementation of our method is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively, than using the spherical harmonic transform at $\ell_{max} = 3 N_{side}$ implemented by the highly optimized \pkg{libsharp} \citep{reinecke2013libsharp} library used by HEALPix.
+We also observe an important gain for graph convolution if it only needs to process only a subpart of the sphere. 
+This gain is the direct reflection of the graph convolution complexity proportional to $N_{pix}$.
 Note that the two might however scale differently, given that \pkg{libsharp} can be distributed on CPUs through MPI while our method can be distributed on GPUs by \pkg{TensorFlow}.

### 2019-03-05 rebuttal.tex
remove the fixed comment
finish comment 2.2 (+ some details)

@@
 
-\mdeff{measure the computational time of filtering on a 1/12, 1/48 or 1/192 of the sphere with the graph.
+%\mdeff{measure the computational time of filtering on a 1/12, 1/48 or 1/192 of the sphere with the graph.
 Add the result to Figure 4 and compare with filtering of the full sphere (with SHT and graph).}
@@
 
-%\todo{Assigned: @Nati, @Michael, @Tomek}
 %\nati{Please check if you like what I did in light of the discussion we had.}
 
-We share the opinion of the reviewer when he says that 2D convolution neural networks (2D ConvNet) should probably work as well as DeepSphere ``by taking in a projected 2D image of the sky and using *loads* of filters to learn about the distortion at different parts of the projected sky.'' Hence we decided to add a new experiment in the paper.
-
-Nevertheless, making a comparison is technically not as trivial as it may seems.
-Problematically a radial projection is computationally expensive to the point where, because of the dataset augmentation, it becomes significantly more expensive than the actual training of the network.
-Hence, we decided to use the geometrical properties of HEALPix to create a ``special'' projection.
-In the HEALPix sampling, the sphere is first separated into $12$ parts that are then subdivided into $4$ recursively.
-Eventually, each of these $12$ parts resembles a square grid.
-As the problem we are solving only involve one of these 12 parts, we can use this natural structure to simply re-assign each HEALPix pixel to one of a 2 dimensional grid of size $N_{sides} \times N_{sides}$.
-This operation is computationally very cheap and probably spread the projection error relatively evenly across the resulting image.
-We note that, this projection has recently been used for a CNN in cosmology in the very recent work \cite{krachmalnicoff2019convolutional}.
-%As we believe that this projection is the optimal one to use a traditional CNN for applications, we performed the experiment using it.
-
-Our expectation were alligned with the one of the reviewer, but the results did surprise us as the performance of the traditional CNN did in general not match DeepSphere, (see Figure 9 of the manuscript).
-It can probably be explained by the fact that 2DCNN breaks the rotational invariance of the data.
-The problem comes from the fact that the projection introduce a distortion in the geometry and the network has to learn a correct weighting scheme to compensate for it.
-Unfortunately, this operation waste many parameters, reducing the modelization power of the network and requires large amount of training data which is not fully available.
-Note that, when visualizing the learned convolution kernels, we observed that they were not radial.
-We did not use *loads* of filters as suggested by the reviewer as the optimization was challenging and we already had to regularize significantly the network. 
-While adding more filters, did improve slightly the performance (never to the level of DeepSphere), it made the optimization even more challenging to the point where we could not obtain consistent results if we were to restart the training process.
+We decided to add this experiment.
+Note that making this comparison was technically not as trivial as it may seem because of the 2D projection (see Appendix D).
+We shared the opinion of the reviewer that a 2D CNN should probably work as well as DeepSphere ``by taking in a projected 2D image of the sky and using *loads* of filters to learn about the distortion at different parts of the projected sky.''
+We were however positively surprised by the results: the performance of the 2D CNN did in general not match DeepSphere (see Figure 9 and the new paragraph is section 4.5).
+
+We did however not use *loads* of filters as suggested by the reviewer.
+% the optimization was challenging and we already had to regularize significantly the network.
+While adding more filters did improve slightly the performance (never to the level of DeepSphere), it made the optimization more challenging to the point where we could not obtain consistent results if we were to restart the training process.
 Eventually, we decided to report the results for the architecture with the same number of parameters as DeepSphere.

### 2019-03-05 scnn.tex
finish comment 2.2 (+ some details)

--- 2019-03-04 scnn.tex
@@
 Convolutional Neural Networks (CNNs) are a cornerstone of the Deep Learning toolbox and have led to many breakthroughs in Artificial Intelligence.
-So far, these networks have mostly been developed for regular Euclidean domains such as those supporting images, audio, or video.
+So far, these neural networks (NNs) have mostly been developed for regular Euclidean domains such as those supporting images, audio, or video.
 Because of their success, CNN-based methods are becoming increasingly popular in Cosmology.
@@
 This approach is computationally more efficient than using spherical harmonics to perform convolutions.
-We demonstrate the method on a classification problem of weak lensing mass maps from two cosmological models and compare the performance of the CNN with that of two baseline classifiers, based on the power spectrum and pixel density histogram.
-Our experimental results show that the performance of DeepSphere is always superior or equal to both of these baselines.
-For high noise levels and for data covering only a smaller fraction of the sphere, DeepSphere achieves typically 10\% better classification accuracy than those baselines.
-Finally, we show how learned filters can be visualized to introspect the neural network.
+We demonstrate the method on a classification problem of weak lensing mass maps from two cosmological models and compare its performance with that of three baseline classifiers, two based on the power spectrum and pixel density histogram, and a classical 2D CNN.
+Our experimental results show that the performance of DeepSphere is always superior or equal to the baselines.
+For high noise levels and for data covering only a smaller fraction of the sphere, DeepSphere achieves typically 10\% better classification accuracy than the baselines.
+Finally, we show how learned filters can be visualized to introspect the NN.
 Code and examples are available at \url{https://github.com/SwissDataScienceCenter/DeepSphere}.
@@
 	\includegraphics[width=\linewidth]{figure_architecture_v3}
-	\caption{Overall network architecture, showing here three convolutional layers acting as feature extractors followed by three fully connected layers with softmax acting as the classifier.
+	\caption{Overall NN architecture, showing here three convolutional layers acting as feature extractors followed by three fully connected layers with softmax acting as the classifier.
     A convolutional layer is based on five operations: convolution, non-linearity, batch normalization, down-sampling, and pooling.
@@
 	Second, we propose to exploit a hierarchical pixelization of the sphere for the down-sampling operation.
-	It allows the network to analyze the data at multiple scales while preserving the spatial localization of features.
-	This figure shows a network that operates on the whole sphere.
+	It allows the NN to analyze the data at multiple scales while preserving the spatial localization of features.
+	This figure shows a aetwork that operates on the whole sphere.
 	The process is the same when working with partial observations, except that the graph is only built for the region of interest.}
@@
 \citep{schmelze2017cosmologicalmodel,luciesmith2018machinelearning,gupta2018nongaussianinformation,gillet2018deeplearning,hassan2018reionizationmodels,aragoncalvo2018classyfyinglarge,ciuca2017cnnstring,ravanbakhsh2017estimating}, while maintaining robustness to noise.
-This is possible as neural networks have the capacity to build rich models and capture complicated non-linear patterns often present in the data.
+This is possible as neural networks (NNs) have the capacity to build rich models and capture complicated non-linear patterns often present in the data.
 CNNs are particularly well suited for the analysis of cosmological data as their trainable weights are shared across the domain, i.e., the network does not have to relearn to detect objects or features at every spatial location.
@@
 The main challenge in designing a CNN on the sphere is to define a convolution operation that is suitable for this domain, while taking care of the necessary irregular sampling.
-Moreover, the designed convolution and resulting neural network should possess the following three key characteristics.
+Moreover, the designed convolution and resulting NN should possess the following three key characteristics.
 First, the convolution should be equivariant to rotation, meaning that a rotation of the input implies the same rotation of the output.
@@
 These models were designed to have very similar angular power spectrum.
-We compare the performance of DeepSphere to a baseline algorithm: an SVM classifier that takes pixel histograms or power spectrum densities (PSDs) of these maps as input.
+We compare the performance of DeepSphere to three baselines: a 2D CNN, and an SVM classifier that takes pixel histograms or power spectrum densities (PSDs) of these maps as input.
 The comparison is made as a function of the additive noise level and the area of the sphere used in the analysis.
@@
     Both are executed on a single core.
-	The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3) = \bO(N_{pix}^{3/2})$ for the spherical harmonics, where $\ell_{max}$ is the largest angular frequency.}
+	The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3) = \bO(N_{pix}^{3/2})$ for the spherical harmonics, where $\ell_{max}$ is the largest angular frequency.
+	The timings for the partial graphs correspond to a convolution on two fractions (1/12 and 1/192) of the sphere, and illustrates the $\bO(N_{pix})$ scaling of graph convolutions.
+	}
     \label{fig:filtering_speed}
@@
 As no efficient and general fast Fourier transform (FFT) exists for graphs \citep{le2018fgft}, the execution of the Fourier transform by multiplication of the signal $\f$ by the dense matrix $\U$ costs $\bO(N_{pix}^2)$ operations.
-In a neural network, this operation has to be performed for each forward and backward pass.
+In a NN, this operation has to be performed for each forward and backward pass.
 As current training procedures require processing of many samples, that would be very slow.
@@
 On a single core, a naive implementation of our method is ten to twenty times faster for $N_{side} = 2048$, with $K=20$ and $K=5$, respectively, than using the spherical harmonic transform at $\ell_{max} = 3 N_{side}$ implemented by the highly optimized \pkg{libsharp} \citep{reinecke2013libsharp} library used by HEALPix.
+The further important speed-up of graph convolutions on fractions of the sphere is a direct reflection of the $\bO(N_{pix})$ complexity.
+On graphs, you only pay for the pixels that you use.
 Note that the two might however scale differently, given that \pkg{libsharp} can be distributed on CPUs through MPI while our method can be distributed on GPUs by \pkg{TensorFlow}.
@@
 The general DeepSphere architecture, pictured in \figref{architecture}, is composed of many layers.
-The convolutional part, the head of the neural network, is composed of graph convolutional layers ($GC$), pooling layers ($P$), and batch normalization layers ($BN$).
+The convolutional part, the head of the NN, is composed of graph convolutional layers ($GC$), pooling layers ($P$), and batch normalization layers ($BN$).
 The tail is composed of multiple fully connected layers ($FC$) followed by an optional softmax layer ($SM$) if the network is used for discrete classification.
@@
 
-The softmax layer is the last layer in a neural network engineered for classification.
+The softmax layer is the last layer in a NN engineered for classification.
 Given the output $\x \in \R^{N_{classes}}$ of the last $FC$, called the logits in the deep learning literature, the softmax layer outputs $\y = SM(\x)$ such that
@@
 where $N_{classes}$ is the number of classes to discriminate.
-Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a neural network is a discretised conditional distribution for the class given the data and trained parameters.
+Thanks to the softmax, the output $\y \in \R^{N_{classes}}$ of a NN is a discretised conditional distribution for the class given the data and trained parameters.
 That is, $y_i$ is the confidence of the network that the input sample belongs to class $i$.
@@
 Segmentation and feature detection \citep{Amsel2007detecting} are examples of dense classification tasks.
-The size of the output of the neural network depends on the task. See \tabref{tasks}.
+The size of the output of the NN depends on the task. See \tabref{tasks}.
 
@@
 By treating each output pixel independently and in parallel, this architecture is a principled way to perform rotation equivariant operations.
-Rotation equivariance means that the rotation operation commutes with the neural network, i.e., a rotation of the input implies the same rotation of the output.\footnote{Small errors will however appear as $GC$ layers are not exactly equivariant due to the small discrepancy between the graph Fourier modes and the spherical harmonics.
+Rotation equivariance means that the rotation operation commutes with the NN, i.e., a rotation of the input implies the same rotation of the output.\footnote{Small errors will however appear as $GC$ layers are not exactly equivariant due to the small discrepancy between the graph Fourier modes and the spherical harmonics.
 See \ref{sec:comparison_spherical_harmonics}.}
@@
 \end{equation*}
-Similarly, we emphasize that the use of $FC$ and $AV$ layers is the sole difference between a neural network engineered for global or dense prediction.
+Similarly, we emphasize that the use of $FC$ and $AV$ layers is the sole difference between a NN engineered for global or dense prediction.
 
@@
 Again, take $N_{pix} = 1$ for global regression.
-We emphasize that the cost function and the $SM$ layer are the sole differences between a neural network engineered for classification or regression.
-
-The goal of training is to find the parameters $\theta$ of the neural network that minimize the risk $R(\theta) = \esp \left[ C \left( NN_\theta(\X), \bar \Y \right) \right]$, where $\esp$ is the expectation over the joint distribution $(\X, \bar \Y)$.
+We emphasize that the cost function and the $SM$ layer are the sole differences between a NN engineered for classification or regression.
+
+The goal of training is to find the parameters $\theta$ of the NN that minimize the risk $R(\theta) = \esp \left[ C \left( NN_\theta(\X), \bar \Y \right) \right]$, where $\esp$ is the expectation over the joint distribution $(\X, \bar \Y)$.
 In general, that expectation cannot be computed as the data distribution is unknown.
@@
 Being a mathematically well-defined rotation equivariant network is the main advantage of methods based on spherical harmonics, though the fact that convolution kernels are learned probably compensates for inexact equivariance.
-See \citep{kondor2018equivariance} for a rigorous treatment of convolution and equivariance in neural networks.
+See \citep{kondor2018equivariance} for a rigorous treatment of convolution and equivariance in NNs.
 
@@
 
-DeepSphere is compared against two simple yet powerful benchmarks.
+\subsection{Baselines}
+
+DeepSphere is first compared against two simple yet powerful benchmarks.
 The two baselines are based on features that are (i) the power spectral densities (PSD) of maps, and (ii) the histogram of pixels in the maps \citep{patton2017cosmologicalconstraints}.
@@
 
-\nati{
-Additionally, we compare DeepSphere to a traditional 2-dimensional convolutional neural network (2D ConvNet).
-To do so, the samples are first transformed into a square image before being fed into the 2D ConvNet.
-As described in \ref{sec:projection}, we use the geometrical properties of HEALPix to construct an efficient and simple projection of the samples.
-Note that during the review process another spherical CNN architecture using exploiting this property appeared \cite{krachmalnicoff2019convolutional}.
-We used convolution kernel of size $5\times 5$ and reduced the number of filters in order to match the number of variables between DeepSphere and the 2D ConvNet.
-}
+DeepSphere is further compared to a classical CNN for 2D Euclidean grids, later referred to as 2D ConvNet.
+To be fed into the 2D ConvNet, samples have to be transformed into flat images.
+As described in \ref{sec:projection}, we use the property that HEALPix is defined as the subdivision of 12 square surfaces to efficiently project the spherical maps.
+This property has been independently exploited (while this paper was under review) to define another spherical CNN \cite{krachmalnicoff2019convolutional}.
+In our experiments, we used the same architecture as DeepSphere (described in \secref{hyper_parameters}), with convolution kernels of size $5 \times 5$ and an $\ell2$ weight decay with a weight of 3 as regularization.
+The number of filters was reduced in order to match the number of trainable parameters between DeepSphere and the 2D ConvNet.
+(A larger architecture resulted in unstable training for a marginal performance gain.)
 
 \subsection{Network architecture and hyper-parameters}
+\label{sec:hyper_parameters}
 
@@
 	\caption{
-		Classification accuracy of the fully convolutional (DeepSphere FCN) variant of DeepSphere, the standard convolutional (DeepSphere CNN) variant of DeepSphere, the fully convolutional ConvNet (2D ConvNet FCN), the standard convolutional ConvNet (2D ConvNet CNN), the support vector machine (SVM) with the power spectral density (PSD) as features, and the SVM with the histogram as features.
+		Classification accuracy of the fully convolutional variant of DeepSphere (DeepSphere FCN), the standard convolutional variant of DeepSphere (DeepSphere CNN), the fully convolutional 2D ConvNet (2D ConvNet FCN), the standard 2D ConvNet (2D ConvNet CNN), the support vector machine (SVM) with the power spectral density (PSD) as features, and the SVM with the histogram as features.
 		The difficulty of the task depends on the level of noise and the size of a sample (that is, the number of pixels that constitute the sample to classify).
@@
 The FCN variant of DeepSphere beats the CNN variant by being invariant to rotation.
-Both variants largely beat the two SVM baselines.
+Both variants largely beat the 2D ConvNet and the two SVM baselines.
 	}
@@
 
-\figref{results} compares the classification accuracy of DeepSphere (FCN and CNN variants), the 2DCNN and the two baselines across five noise levels and three sample sizes.
+\figref{results} compares the classification accuracy of DeepSphere (FCN and CNN variants), and the three baselines across five noise levels and three sample sizes.
 We indeed observe that the problem is made more difficult as the sample size decreases, and the noise increases.
@@
 DeepSphere (both the FCN and CNN variants) shows superior performance over all configurations.
-The gap even widens as the problem becomes more difficult.
+The gap widens as the problem becomes more difficult.
 This is likely due to DeepSphere learning features that are adapted to the problem instead of relying on hand-designed features.
@@
 
-\nati{
-To our surprise, the traditional 2D ConvNet did not match the performance of DeepSphere.
-It can probably be explained by the fact that the 2D ConvNet breaks the rotational invariance of the data.
-The problem comes from the fact that the projection introduce a distortion in the geometry and the network has to learn a correct weighting scheme to compensate for it.
-Unfortunately, this operation waste many parameters, reducing the modelization power of the network and requires large amount of training data which is not fully available.
-Note that, when visualizing the learned convolution kernels, we observed that they were not radial.
-}
-
-As expected, we observe that the FCN slightly outperforms the CNN.
+The 2D ConvNet fairs in-between the SVMs and DeepSphere.
+Its relatively low performance probably come from the following drawbacks.
+First, it does not exploit the rotational invariance of the problem.
+We observed that the learned convolution kernels were not radial.
+Second, the 2D projection distorts the geometry, and the NN has to learn to compensate for it, which comparatively requires more training data.
+% uses parameters and wastes expressiveness.
+
+As expected, the FCN variants outperform the CNN variants (both for DeepSphere and the 2D ConvNet).
 This may seem counterintuitive as the CNN is a generalization of the FCN and hence should be able to learn the same function and provide at least equivalently good results.
@@
 
-While testing the FCN and CNN variants, we made the following empirical observations.
+While testing the FCN and CNN variants of DeepSphere, we made the following empirical observations.
 First, training was more stable (in the sense that the loss decreased more smoothly) when using Chebyshev polynomials, as in \eqnref{graph_convolution_cheby}, rather than monomials, as in \eqnref{graph_convolution_monomial}.
@@
 Third, we recommend initializing the Chebyshev coefficients with a centered Gaussian distribution with standard deviation $\sqrt{2/(F_{in} \times (K + 0.5))}$, where $K$ is the degree of the Chebyshev polynomials and $F_{in}$ the number of input channels.
-This standard deviation has the property of keeping the energy of the signal more or less constant across layers.\footnote{We derived this rule from the Chebyshev polynomial equations, the principles presented in \cite{glorot2010understanding}, and some empirical experiments.}
+This standard deviation has the property of keeping the energy of the signal more or less constant across layers.\footnote{We derived this rule from the principles presented in \cite{glorot2010understanding}, the Chebyshev polynomial equations, and some empirical experiments.}
 % Nati to Michael: The problem with the previous claim is that it depends on the non-linarity. Furthermore, does it make sense to make such a claim if we use batch norm?
@@
 
-We present DeepSphere, a novel convolutional neural network defined on the sphere with HEALPix sampling, designed for the analysis of the cosmological data.
-We publish the code as a small and easy-to-use python package.
-The code was designed so that DeepSphere can easily be used for typical machine learning tasks, such as classification and regression, both dense and global.
+We present DeepSphere, a convolutional neural network defined on the sphere with HEALPix sampling, designed for the analysis of cosmological data.
+The main contributions of this paper are (i) to show that spherical CNNs are a great NN architecture for cosmological applications, and (ii) that a graph-based spherical CNN has certain undeniable advantages.
 The core of our method is the use of a graph to represent the discretised sphere.
 This allows us to leverage the advantages of the graph convolution.
-It is both efficient, with a complexity of $\bO(N_{pix})$, and flexible, which allows DeepSphere to efficiently work on parts of the sphere.
+It is both efficient, with a complexity of $\bO(N_{pix})$, and flexible, which allows DeepSphere to efficiently work on a partial sphere.
 The spherical properties of the domain are well captured: the graph Fourier modes are close to the spherical harmonics.
@@
 However, we do not expect that to cause problems for practical applications.
-
-We demonstrate that the neural network systematically and significantly outperforms our benchmark methods on an example problem of cosmological model discrimination with weak lensing mass maps, designed similarly to \citep{schmelze2017cosmologicalmodel}.
+% In general, we encourage practitioners to adapt the architectures of NNs to the data and task, typically by considering the symmetries of the data.
+% Maybe in CNN vs FCN discussion.
+
+We demonstrate that DeepSphere systematically and significantly outperforms three benchmark methods on an example problem of cosmological model discrimination with weak lensing mass maps, designed similarly to \citep{schmelze2017cosmologicalmodel}.
 The maps were produced from two cosmological models with varying $\sigma_8$ and $\Omega_m$, chosen to follow the typical weak lensing degeneracy in these parameters, so that the power spectra for these models are similar.
-We compared the performance of DeepSphere versus that of two SVM classifiers: one trained on the spherical harmonics power spectrum, and the other on the pixel density histogram.
-DeepSphere performs better than the two baselines for all considered cases.
+We compared the performance of DeepSphere versus that of a classical 2D CNN and two SVM classifiers (one trained on the spherical harmonics power spectrum, and the other on the pixel density histogram).
+DeepSphere performs better than the three baselines for all considered cases.
 The advantage is small for large, noise-free maps, and grows up to 10\% for smaller, noisier data.
@@
 Spherical CNNs are so far mostly used for omnidirectional imaging.
-Many scientific fields, such as weather or climate modeling, would however benefit from an efficient and versatile spherical CNN.
+Many scientific fields, such as weather or climate modelling, would however benefit from an efficient and versatile spherical CNN.
 With this work, we hope to demonstrate and help democratize the use of those tools for spherical data analysis.
+We publish the code as a small and easy-to-use python package.
+The code was designed so that DeepSphere can easily be used for typical machine learning tasks, such as classification and regression, both dense and global.
 
@@
 Those discrepancies result in a convolution operation that is not exactly equivariant to rotation.
-Nevertheless, our experiments suggest that these downsides do not have an important effect on the convolution nor hinder the performance of the neural network.
+Nevertheless, our experiments suggest that these downsides do not have an important effect on the convolution nor hinder the performance of the NN.
 
@@
 
-\nati{
-\section{Maps projection onto a 2-dimensional plane}
+\section{Projection onto a 2D plane}
 \label{sec:projection}
-In order to compare the DeepSphere architecture with a 2D ConvNet, we need to project the spherical data onto a plane.
-Problematically a radial projection is computationally expensive to the point where, because of the dataset augmentation, it becomes significantly more expensive than the actual training of the network.
-Hence, we decided to use the geometrical properties of HEALPix to create a ``special'' projection.
-In the HEALPix sampling, the sphere is first separated into $12$ parts that are then subdivided into $4$ recursively.
-Eventually, each of these $12$ parts resembles a square grid.
-To visually see it, we refer the reader to \figref{border_effects}.
-As the problem we are solving only involve one of these $12$ parts, we can use this natural structure to simply re-assign each HEALPix pixel to one of a 2 dimensional grid of size $N_{sides} \times N_{sides}$.
-This operation is computationally very cheap and probably spread quite evenly across the resulting image.
-This projection has recently been used for a CNN in cosmology in the very recent work \cite{krachmalnicoff2019convolutional}.
-}
+
+In order to compare the DeepSphere architecture with a 2D CNN, we needed to project the spherical maps onto a plane.
+A radial projection is computationally so expensive that, because of data augmentation, it is significantly more expensive than the actual training of the NN.
+Hence, we decided to leverage the geometrical properties of HEALPix to create another projection.
+Remember that HEALPix models the sphere as $12$ pixels that are then subdivided into $4$ recursively.
+Eventually, each of these $12$ bases resembles a square grid.
+See \figref{border_effects} to visualize it.
+As our classification problem involves a twelfth of the sphere at most, we can use this natural structure to simply assign each HEALPix pixel to a pixel of a 2D grid of size $N_{sides} \times N_{sides}$.
+This operation is computationally cheap and probably spreads the projection error relatively evenly across the resulting image.
+This projection has actually been independently proposed (while this paper was under review) for a spherical CNN on HEALPix for cosmology \cite{krachmalnicoff2019convolutional}.
 
@@
 
-For the trained network to be robust to noise, we employ the following data augmentation technique: a random realization of Gaussian noise is added to each sample before it is fed to the neural network.
+For the trained network to be robust to noise, we employ the following data augmentation technique: a random realization of Gaussian noise is added to each sample before it is fed to the NN.
 Besides robustness to noise, the network is less likely to over-fit the training set as it never sees the same sample twice.

### 2019-03-06 scnn.tex
power spectrum density => power spectral density

@@
 These models were designed to have very similar angular power spectrum.
-We compare the performance of DeepSphere to three baselines: a 2D CNN, and an SVM classifier that takes pixel histograms or power spectrum densities (PSDs) of these maps as input.
+We compare the performance of DeepSphere to three baselines: a 2D CNN, and an SVM classifier that takes pixel histograms or power spectral densities (PSDs) of these maps as input.
 The comparison is made as a function of the additive noise level and the area of the sphere used in the analysis.
@@
 	\includegraphics[width=\linewidth]{psd_sigma3}
-	\caption{Power spectrum densities of the noiseless maps.
+	\caption{Power spectral densities of the noiseless maps.
 		To prevent the cosmological models from being distinguished by their power spectra alone, the maps have been smoothed with a Gaussian kernel of radius $3$ arcmins to remove high frequencies ($\ell>1000$).}
@@
 To remove this information, we additionally smooth the spherical maps with a Gaussian kernel of radius $3$ arcmin.
-The resulting Power Spectrum Density (PSD), computed using the \texttt{anafast} function of the HEALPix package, are displayed in \figref{psd_sigma3}.
+The resulting power spectral density (PSD), computed using the \texttt{anafast} function of the HEALPix package, are displayed in \figref{psd_sigma3}.
 We also subtract the mean of each map and down-sample them to a resolution of $N_{side}=1024$, which corresponds to maps of $12 \times 1024^2 \approx 12 \times 10^6$ pixels.
@@
 DeepSphere is first compared against two simple yet powerful benchmarks.
-The two baselines are based on features that are (i) the power spectral densities (PSD) of maps, and (ii) the histogram of pixels in the maps \citep{patton2017cosmologicalconstraints}.
+The two baselines are based on features that are (i) the power spectral densities (PSDs) of maps, and (ii) the histogram of pixels in the maps \citep{patton2017cosmologicalconstraints}.
 After normalization, those features are used by a linear support vector machine (SVM) trained for classification.

### 2019-03-06 scnn.tex
fix footnote number

@@
 Right: graph built from a HEALPix pixelization of half the sphere ($N_{side} = 4$).
-By construction, each vertex has eight neighbors, except the highlighted ones which have only seven.\footnotemark[4] Left and middle figures are taken from \citep{boomsma2017spherical}.}
+By construction, each vertex has eight neighbors, except the highlighted ones which have only seven.\footnotemark[5] Left and middle figures are taken from \citep{boomsma2017spherical}.}
     \label{fig:sphere_grids}

### 2019-03-06 scnn.tex
point to the zenodo repository

@@
 The classification methods were trained to predict a label from a HEALPix map.
-Our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/DeepSphere}}} to reproduce those experiments are openly available online.
-The data is available upon request from the cosmology group.\footnote{\url{http://www.cosmology.ethz.ch}}
+Our Python implementation to reproduce those experiments is openly available online.{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/DeepSphere}}}
+The data is available upon request.\footnote{\url{https://doi.org/10.5281/zenodo.1303272}}
 

### 2019-03-06 scnn.tex
add a paragraph to argument why we don't compare to other spherical CNNs

@@
 	The theoretical cost of filtering on the graph is $\bO(K N_{pix})$ and $\bO(\ell_{max}^3) = \bO(N_{pix}^{3/2})$ for the spherical harmonics, where $\ell_{max}$ is the largest angular frequency.
-	The timings for the partial graphs correspond to a convolution on two fractions (1/12 and 1/192) of the sphere, and illustrates the $\bO(N_{pix})$ scaling of graph convolutions.
+	The timings for the partial graphs correspond to a convolution on two fractions ($1/12$ and $1/192$) of the sphere, and illustrates the $\bO(N_{pix})$ scaling of graph convolutions.
 	}
@@
 We also subtract the mean of each map and down-sample them to a resolution of $N_{side}=1024$, which corresponds to maps of $12 \times 1024^2 \approx 12 \times 10^6$ pixels.
+As shown by the occupied spectrum (\figref{psd_sigma3}), a larger resolution would waste memory and computation, while a lower resolution would destroy information.
 
@@
 As such, we can control the difficulty of the classification problem by limiting the number of pixels available to the algorithms, i.e., extracting partial maps from whole sky maps.
-Using the properties of HEALPix, we split maps into $12 \times o^2$ ($o=1,2,4,\dots$) independent samples of $(N_{pix} / o)^2$ pixels.
+Using the properties of HEALPix, we split maps into $12 \times o^2$ independent samples of $(N_{pix} / o)^2$ pixels (for $o=1,2,4,\dots$).
 The resulting partial maps are large enough to suffer from the effects of the spherical geometry, and cover 8.3\% ($\approx 1 \times 10^6$ pixels), 2.1\% ($\approx 260 \times 10^3$ pixels), and 0.5\% ($\approx 65 \times 10^3$ pixels) of the sphere for $o=1,2,4$, respectively.
 Corresponding areas can be seen in \figref{pooling}: the surface of pixels in the left, middle, and right spheres correspond to samples at order $o=4,2,1$, respectively.
-We report results for $o=1,2,4$ only, as full sphere classification is easy at such resolution (perfect classification accuracy is already attainable for $o=1$, see \figref{results}), and many cosmological applications will use datasets located on part-sphere only.
-Our code nonetheless includes an example demoing classification on full spheres of much lower resolution ($N_{side} = 64$).
+We report results for $o=1,2,4$ only, as full sphere classification is easy at such resolution (perfect classification accuracy is already obtained at $o=1$, see \figref{results}).
+% any cosmological applications will use datasets located on part-sphere only. % MD: we made this point already
+The published code nonetheless includes an example demoing classification on full spheres of lower resolution ($N_{side} = 64$).
 
@@
 (A larger architecture resulted in unstable training for a marginal performance gain.)
+
+Ideally, we would compare DeepSphere to alternative spherical CNNs like \citep{cohen2018sphericalcnn} and \citep{esteves2017sphericalcnn}.
+There are however two issues with that comparison.
+First, these CNNs were developed for the equirectangular sampling.
+An option is to modify the available implementations to use HEALPix, which is a major undertaking due to their complexity.
+Another option is to transform the cosmological maps to the equirectangular sampling, which is of disputable usefulness as the field is unlikely to use that sampling.
+% nefieldfully to not introduce artifacts
+Second, those methods, based on SHTs, only work on the full sphere (at least in their current state).
+As shown in \figref{filtering_speed}, using the full sphere at a resolution of $N_{side} = 1024$ would result in a slow-down of multiple orders of magnitude compared to using a partial graph.\footnote{Note that the authors report results for maps of at most $(2 \times 128)^2 = 65,536$ pixels \citep{cohen2018sphericalcnn, esteves2017sphericalcnn}.
+That is the size of our smallest partial map, while the largest is of approximately one million pixels.}
+For those reasons and because we think that a proper comparison is better carried out on diverse datasets and tasks, we leave it as future work.
 

### 2019-03-19 scnn.tex
cite paper which could not use Cohen's spherical CNN for CMB analysis

@@
 Another option is to transform the cosmological maps to the equirectangular sampling, which is of disputable usefulness as the field is unlikely to use that sampling.
-% nefieldfully to not introduce artifacts
+% transformation must be carefully handled to not introduce artifacts
 Second, those methods, based on SHTs, only work on the full sphere (at least in their current state).
-As shown in \figref{filtering_speed}, using the full sphere at a resolution of $N_{side} = 1024$ would result in a slow-down of multiple orders of magnitude compared to using a partial graph.\footnote{Note that the authors report results for maps of at most $(2 \times 128)^2 = 65,536$ pixels \citep{cohen2018sphericalcnn, esteves2017sphericalcnn}.
+As shown in \figref{filtering_speed}, using the full sphere at a resolution of $N_{side} = 1024$ would result in a slow-down of multiple orders of magnitude compared to using a partial graph.
+The authors of \citep{he2018cmbdl} could not use \citep{cohen2018sphericalcnn} for CMB analysis because of that.\footnote{Note that reported results in \citep{cohen2018sphericalcnn} and \citep{esteves2017sphericalcnn} are for maps of at most $(2 \times 128)^2 = 65,536$ pixels.
 That is the size of our smallest partial map, while the largest is of approximately one million pixels.}

### 2019-03-25 scnn.tex
typo
edits to subspace correspondence

@@
 	It allows the NN to analyze the data at multiple scales while preserving the spatial localization of features.
-	This figure shows a aetwork that operates on the whole sphere.
+	This figure shows a network that operates on the whole sphere.
 	The process is the same when working with partial observations, except that the graph is only built for the region of interest.}
@@
 	\caption{Correspondence between the subspaces spanned by the graph Fourier modes and the spherical harmonics.
-		The correspondance is computed in two steps. (i) We compute the PSD of each graph eigenvector.
-		(ii) As, for each harmonic index $\ell$, there is $2\ell+1$ spherical harmonics, we sum the contribution of the corresponding $2\ell+1$ graph eigenvectors.
+		%The correspondence is computed in two steps.
+		First, we compute the power spectral density (PSD) of each graph eigenvector.
+		Second, as there is $2\ell+1$ spherical harmonics for each harmonic index $\ell$, we sum the contributions of the corresponding $2\ell+1$ graph eigenvectors.
 		% No real convergence with increasing Nside.
@@
 		% Pixel $k$ in row $j$ measures the energy in frequency band $k$ of the graph Fourier modes identified to be part of band $j$.
-		The matrix should ideally be the identity.
-		While not the case, the plot shows how the subspaces agree: the subspaces spanned by the Fourier modes correspond to those spanned by the spherical harmonics in the low frequencies, while the Fourier modes leak towards adjacent frequency bands in the high frequencies.
+		The matrix shows how the subspaces agree: the subspaces spanned by the Fourier modes correspond to those spanned by the spherical harmonics in the low frequencies, and the Fourier modes leak towards adjacent frequency bands at higher frequencies.
 		While there is a systematic error, the Fourier modes agree at higher frequencies as $N_{side}$ increases.}

### 2019-03-25 scnn.tex
harmonic index => degree

@@
 		First, we compute the power spectral density (PSD) of each graph eigenvector.
-		Second, as there is $2\ell+1$ spherical harmonics for each harmonic index $\ell$, we sum the contributions of the corresponding $2\ell+1$ graph eigenvectors.
+		Second, as there is $2\ell+1$ spherical harmonics for each degree $\ell$, we sum the contributions of the corresponding $2\ell+1$ graph eigenvectors.
 		% No real convergence with increasing Nside.

### 2019-03-26 scnn.tex
cite PyGSP
architecture figure: spatial summarization

@@
 DeepSphere is implemented with \pkg{TensorFlow} \citep{abadi2016tensorflow} and is intended to be easy to use out-of-the-box for cosmological applications.
+Many plots and co PyGSP \citep{pygsp} for computations and plots.
+The Python Graph Signal Processing package (PyGSP) \citep{pygsp} is used to build graphs, compute the Laplacian and Fourier basis, and perform graph convolutions.
 Code and examples are available online.{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/DeepSphere/}}}
@@
 		%The correspondence is computed in two steps.
-		First, we compute the power spectral density (PSD) of each graph eigenvector.
+		First, we compute the power spectral density (PSD) of each graph eigenvector with the SHT.
 		Second, as there is $2\ell+1$ spherical harmonics for each degree $\ell$, we sum the contributions of the corresponding $2\ell+1$ graph eigenvectors.
@@
 		% Pixel $k$ in row $j$ measures the energy in frequency band $k$ of the graph Fourier modes identified to be part of band $j$.
-		The matrix shows how the subspaces agree: the subspaces spanned by the Fourier modes correspond to those spanned by the spherical harmonics in the low frequencies, and the Fourier modes leak towards adjacent frequency bands at higher frequencies.
-		While there is a systematic error, the Fourier modes agree at higher frequencies as $N_{side}$ increases.}
+		The matrix shows how the subspaces align: the Fourier modes span the same subspaces as the spherical harmonics in the low frequencies, and the Fourier modes leak towards adjacent frequency bands at higher frequencies.
+		While there is a systematic error, the Fourier modes align at higher frequencies as $N_{side}$ increases.}
 		\label{fig:subspace_harmonics_eigenvectors}
